### 2021-08-04 documentos/notas/notas_ja.tex

\section{CP from eigenvalues} % {{{
% Intro {{{
Choi matrix's eigenvalues of a 1-qubit Pauli Channel are
\begin{align}
\lambda_{\mu}=1+\sum_{j=1}^3a_j^{\mu}\tau_j
\hspace{35pt}
\mu=0,1,2,3;
\hspace{35pt}
a_j^{\mu}=\left\{ \begin{array}{rl}
             1, & \mu=j \lor \mu=0\\
             -1, & \mu\neq j
             \end{array}
   \right..
\end{align}
Therefore, the inequalities needed to be sattisfied for a 1-qubit 
unital Pauli channel in order to be CP may be expressed in the 
following compact expression:
\begin{equation}
\sum_{j=0}^3a_j^{\mu}\tau_j\geq -1,
\hspace{35pt}
\mu=1,2,3;
\hspace{35pt}
a_j^{\mu}=\left\{ \begin{array}{rl}
             1, & \mu=j\\
             -1, & \mu\neq j
             \end{array}
   \right..
\end{equation}

Now, Choi matrix's eigenvalues of an n-qubit Pauli Channel are
\begin{align}\label{eq:eigvals-PCE}
\lambda_{\mu_1,\ldots,\mu_n}=1+
\sum_{\underset{(j_1,\ldots,j_n\neq0)}{j_1,\ldots,j_n=0}}^3
a_{j_1}^{\mu_1}\ldots a_{j_n}^{\mu_n}\tau_{j_1,\ldots,j_n}
\hspace{35pt}
\mu_l&=0,1,2,3,\nonumber\\
a_{j_l}^{\mu_l}&=\left\{ \begin{array}{rl}
             1, & \mu_l=j_l \lor j_l=0\lor \mu_1,\ldots,\mu_n=0\\
             -1, & \mu_l\neq j_l
             \end{array}
   \right..
\end{align}

Therefore, the inequalities needed to be sattisfied for the CP are
\begin{equation}\label{eq:inequalities-PCE}
\sum_{\underset{(j_1,\ldots,j_n\neq0)}{j_1,\ldots,j_n=0}}^3
a_{j_1}^{\mu_1}\ldots a_{j_n}^{\mu_n}\tau_{j_1,\ldots,j_n}
\geq
-1,
\hspace{35pt}
\mu_l=0,1,2,3;
\hspace{35pt}
a_{j_l}^{\mu_l}=\left\{ \begin{array}{rl}
             1, & \mu_l=j_l \lor j_l=0\\
             -1, & \mu_l\neq j_l
             \end{array}
   \right.,
\end{equation}
where we used that $\lambda_{0,\ldots,0}$ is always non-negative.
% }}}
\subsection{Another observation from this} % {{{
Choi's matrix of 2 qubits is diagonal in Pauli product basis
(Kraus operators). Does this follow in the general case???? 
% }}}
% }}}
\section{General characterisation of PCE quantum channels} % {{{
\subsubsection*{To avoid confusion} % {{{
\cpnote{Igual el canal totalmente despolarizante y el estado totalmente mixto 
tendrían el mismo diagrama. Quiza el borde se puede ser de diferente color
}
\janote{Me gustaría discutir antes si igual vale la pena hacer la distinción.
Dado que al final la distinción sólo es una ayuda que se me ocurrió para 
explicar gráficamente el procedimiento de la concatenación.}
The figures we've been using (columns, boards, cubes) may represent
both PCE operations (dynamics) and density matrices (kinematics). We
will make a distinction between both representations with colors.
B$\&$W represent PCE operations, and colored figures represent 
density matrices in Pauli products basis.
\begin{figure}
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=3cm]{PCEoperation}
\caption{PCE operation that erases all Pauli components except 
for $r_{0,0}$, $r_{1,1}$, $r_{1,3}$, and $r_{0,3}$.}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=3cm]{state}
\caption{Density matrix in Pauli basis with all components equal
to zero except for $r_{0,0}$, $r_{1,1}$, $r_{1,3}$, and $r_{0,3}$.}
\end{subfigure}
\end{figure}
% }}}

\subsection*{Hypothesis} % {{{
Let us denote $\PCE{n}$ the set of all PCE quantum channels for 
$n$ qubits.
\begin{conj}{}
There exists a set $\Gamma_n\subset\PCE{n}$ that is sufficient (and 
necessary?) to generate the rest of elements in $\PCE{n}$ as 
concatenations of different elements in $\Gamma_n$.
\end{conj}

Let us consider $\E_j\in\Gamma_n$ $(j=1,\ldots,4^{n}-1)$,
and $\Lambda\in\PCE{n}$. All $\Lambda$ are a composition of 
$\E_j$,
\begin{equation}\label{eq:PCE-characterization}
\underbrace{\E_{j_{2n}}\ldots\E_{j_1}}_{k\text{ elements}}=\Lambda,
\hspace{20pt}
j_l\neq j_{l+1},
\hspace{20pt}
k=1,\ldots,2n.
\end{equation}
% }}}
\subsection*{A way to find $\Gamma$} % {{{
PCE quantum channels in $\Gamma_n$ may be found as the quantum 
channels defined by the the coefficients $a_j^{\mu}$ of the $\tau_i$
in the eigenvalues expression of Choi matrix, with $a^{k}_{k}=0$ 
(instead of -1). Let us show the 2-qubits case as an example to illustrate this. 
The eigenvalues of Choi matrix of 2-qubits Pauli Channel are
\begin{align}
\lambda_{1}&=
 \tau _{0,0}+\tau _{0,1}-\tau _{0,2}-\tau _{0,3}+\tau _{1,0}+\tau _{1,1}-\tau _{1,2}-\tau
   _{1,3}-\tau _{2,0}-\tau _{2,1}+\tau _{2,2}+\tau _{2,3}-\tau _{3,0}-\tau _{3,1}+\tau
   _{3,2}+\tau _{3,3} \nonumber \\
\lambda_{2}&=   
 \tau _{0,0}-\tau _{0,1}-\tau _{0,2}+\tau _{0,3}+\tau _{1,0}-\tau _{1,1}-\tau _{1,2}+\tau
   _{1,3}-\tau _{2,0}+\tau _{2,1}+\tau _{2,2}-\tau _{2,3}-\tau _{3,0}+\tau _{3,1}+\tau
   _{3,2}-\tau _{3,3} \nonumber \\
\lambda_{3}&=
 \tau _{0,0}-\tau _{0,1}+\tau _{0,2}-\tau _{0,3}+\tau _{1,0}-\tau _{1,1}+\tau _{1,2}-\tau
   _{1,3}-\tau _{2,0}+\tau _{2,1}-\tau _{2,2}+\tau _{2,3}-\tau _{3,0}+\tau _{3,1}-\tau
   _{3,2}+\tau _{3,3} \nonumber \\
\lambda_{4}&=
 \tau _{0,0}+\tau _{0,1}+\tau _{0,2}+\tau _{0,3}+\tau _{1,0}+\tau _{1,1}+\tau _{1,2}+\tau
   _{1,3}-\tau _{2,0}-\tau _{2,1}-\tau _{2,2}-\tau _{2,3}-\tau _{3,0}-\tau _{3,1}-\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{5}&=
 \tau _{0,0}+\tau _{0,1}-\tau _{0,2}-\tau _{0,3}-\tau _{1,0}-\tau _{1,1}+\tau _{1,2}+\tau
   _{1,3}-\tau _{2,0}-\tau _{2,1}+\tau _{2,2}+\tau _{2,3}+\tau _{3,0}+\tau _{3,1}-\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{6}&=
 \tau _{0,0}-\tau _{0,1}-\tau _{0,2}+\tau _{0,3}-\tau _{1,0}+\tau _{1,1}+\tau _{1,2}-\tau
   _{1,3}-\tau _{2,0}+\tau _{2,1}+\tau _{2,2}-\tau _{2,3}+\tau _{3,0}-\tau _{3,1}-\tau
   _{3,2}+\tau _{3,3}\nonumber \\
\lambda_{7}&=
 \tau _{0,0}-\tau _{0,1}+\tau _{0,2}-\tau _{0,3}-\tau _{1,0}+\tau _{1,1}-\tau _{1,2}+\tau
   _{1,3}-\tau _{2,0}+\tau _{2,1}-\tau _{2,2}+\tau _{2,3}+\tau _{3,0}-\tau _{3,1}+\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{8}&=   
 \tau _{0,0}+\tau _{0,1}+\tau _{0,2}+\tau _{0,3}-\tau _{1,0}-\tau _{1,1}-\tau _{1,2}-\tau
   _{1,3}-\tau _{2,0}-\tau _{2,1}-\tau _{2,2}-\tau _{2,3}+\tau _{3,0}+\tau _{3,1}+\tau
   _{3,2}+\tau _{3,3}\nonumber \\
\lambda_{9}&=   
 \tau _{0,0}+\tau _{0,1}-\tau _{0,2}-\tau _{0,3}-\tau _{1,0}-\tau _{1,1}+\tau _{1,2}+\tau
   _{1,3}+\tau _{2,0}+\tau _{2,1}-\tau _{2,2}-\tau _{2,3}-\tau _{3,0}-\tau _{3,1}+\tau
   _{3,2}+\tau _{3,3}\nonumber \\
\lambda_{10}&=   
 \tau _{0,0}-\tau _{0,1}-\tau _{0,2}+\tau _{0,3}-\tau _{1,0}+\tau _{1,1}+\tau _{1,2}-\tau
   _{1,3}+\tau _{2,0}-\tau _{2,1}-\tau _{2,2}+\tau _{2,3}-\tau _{3,0}+\tau _{3,1}+\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{11}&=   
 \tau _{0,0}-\tau _{0,1}+\tau _{0,2}-\tau _{0,3}-\tau _{1,0}+\tau _{1,1}-\tau _{1,2}+\tau
   _{1,3}+\tau _{2,0}-\tau _{2,1}+\tau _{2,2}-\tau _{2,3}-\tau _{3,0}+\tau _{3,1}-\tau
   _{3,2}+\tau _{3,3}\nonumber \\
\lambda_{12}&=   
 \tau _{0,0}+\tau _{0,1}+\tau _{0,2}+\tau _{0,3}-\tau _{1,0}-\tau _{1,1}-\tau _{1,2}-\tau
   _{1,3}+\tau _{2,0}+\tau _{2,1}+\tau _{2,2}+\tau _{2,3}-\tau _{3,0}-\tau _{3,1}-\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{13}&=   
 \tau _{0,0}+\tau _{0,1}-\tau _{0,2}-\tau _{0,3}+\tau _{1,0}+\tau _{1,1}-\tau _{1,2}-\tau
   _{1,3}+\tau _{2,0}+\tau _{2,1}-\tau _{2,2}-\tau _{2,3}+\tau _{3,0}+\tau _{3,1}-\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{14}&=   
 \tau _{0,0}-\tau _{0,1}-\tau _{0,2}+\tau _{0,3}+\tau _{1,0}-\tau _{1,1}-\tau _{1,2}+\tau
   _{1,3}+\tau _{2,0}-\tau _{2,1}-\tau _{2,2}+\tau _{2,3}+\tau _{3,0}-\tau _{3,1}-\tau
   _{3,2}+\tau _{3,3}\nonumber \\
\lambda_{15}&=   
 \tau _{0,0}-\tau _{0,1}+\tau _{0,2}-\tau _{0,3}+\tau _{1,0}-\tau _{1,1}+\tau _{1,2}-\tau
   _{1,3}+\tau _{2,0}-\tau _{2,1}+\tau _{2,2}-\tau _{2,3}+\tau _{3,0}-\tau _{3,1}+\tau
   _{3,2}-\tau _{3,3}\nonumber \\
\lambda_{16}&=  
 \tau _{0,0}+\tau _{0,1}+\tau _{0,2}+\tau _{0,3}+\tau _{1,0}+\tau _{1,1}+\tau _{1,2}+\tau
   _{1,3}+\tau _{2,0}+\tau _{2,1}+\tau _{2,2}+\tau _{2,3}+\tau _{3,0}+\tau _{3,1}+\tau
   _{3,2}+\tau _{3,3}. 
\end{align}

Now, taking all $\tau_{i,j}$ with coefficients $-1$ equal to zero 
one is led to 16 elements of $\PCE{2}$ (one for each eigenvalue): \newline

\includegraphics[width=\textwidth]{2Q-fundamentals}

The first 15 elements are the elements of $\Gamma_2$.

For the sake
of completeness let us show how to construct all elements in $\PCE{2}$
from $\Gamma_2$. Recall that $\PCE{2}$ can be ordered in 
equivalence classes with PCE quantum channels that are 
connected via particle swaps and local permutations 
of basis.

\begin{itemize}
\item \textbf{8 components:} 
\begin{itemize}
\item C$_1^8$: $\E_{13}$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C81} \\ 
 & \includegraphics[width=2.2cm]{ruleC81} & 
\end{tabular}

\item C$_2^8$: $\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
\end{tabular} 
\end{itemize}

\item \textbf{4 components:} \newline
\begin{itemize}
\item C$_1^4$: $\E_{15}\E_{13}$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C81} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C41}\\ 
 & \includegraphics[width=2.2cm]{ruleC81} &  
 & \includegraphics[width=2.2cm]{ruleC81_2} &\\ 
\end{tabular}

\item C$_2^4$: $\E_{13}\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C42}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
 & \includegraphics[width=2.2cm]{ruleC81} &\\ 
\end{tabular}

\pagebreak
\item C$_3^4$: $\E_{15}\E_{1}$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C43}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
 & \includegraphics[width=2.2cm]{ruleC81_2} &\\ 
\end{tabular}

\item C$_4^4$: $\E_7\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{4comp}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
 & \includegraphics[width=2.2cm]{8To4} &\\ 
\end{tabular} 
\end{itemize}

\item \textbf{2 components:}\newline
\begin{itemize}
\item C$_1^2$: $\E_{15}\E_{14}\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C43}
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C21}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
 & \includegraphics[width=2.2cm]{semefue} &
 & \includegraphics[width=2.2cm]{ruleC81_2} &\\ 
\end{tabular}

\item C$_2^2$: $\E_6\E_7\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm} m{2cm} m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{id}  
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{8comp} 
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{4comp}
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{C22}\\ 
 & \includegraphics[width=2.2cm]{16To8} &  
 & \includegraphics[width=2.2cm]{8To4} &
 & \includegraphics[width=2.2cm]{otroTambien}\\ 
\end{tabular}
\end{itemize}

\pagebreak
\item \textbf{1 component:} $\E_9\E_6\E_7\E_1$\newline
\begin{tabular}{m{2cm} m{2cm} m{2cm}}
\includegraphics[width=2.2cm]{C22}
& \hspace{0.8cm}$\longrightarrow$ 
& \includegraphics[width=2.2cm]{depolarizing} \\ 
 & \includegraphics[width=2.2cm]{otro} &  \\ 
\end{tabular}
\end{itemize}

\begin{conj}
Only $n$ elements in $\Gamma_n$ are sufficient to generate the 
remaining elements.
\end{conj}
% }}}
\subsection{Numerical Results} % {{{
Hypothesis 1 has strong numerical support. The search for PCE quantum
channels has been done in two different ways:
\begin{enumerate}
\item Using the inequalities in \eqref{eq:inequalities-PCE} to test CP of 
all PCE operations (even the ones that do not follow the power-of-2 rule).
\item Using hypoteshis 1.
\end{enumerate}
Both methods have analyzed the cases of 1, 2, 3 and partially 4 qubits. 
Both of them get the same results.

\begin{figure}
  \centering
  \includegraphics[width=.6\textwidth]{cuadro}
\end{figure}
% }}}
% }}}
\section{Things to do and questions to answer} % {{{
\begin{enumerate}
\item This characterization may explain the power-of-2 rule. 
It is quite obvious (in the figures representation) that the concatenation
always erases half of the number of non-zero components. A proof 
for that is missing.
\item Analytic proof for \eqref{eq:inequalities-PCE}. 
\item Analytic proof that \eqref{eq:PCE-characterization} is necessary 
and sufficient to find all elements in $\PCE{n}$.
\item Analytic proof that taking $-1\to 0$ for $a_k^k$ leads to CP.
I suggest using particle swaps and local basis permutation in order 
to reduce the problem to $n$ inequalities.
\item Find a way to count PCE channels.
\end{enumerate}
% }}}

\section{Progress}
\subsection{An idea to prove equation \eqref{eq:eigvals-PCE}}
A density matrix of 1 qubit in Pauli matrices basis is written as
\begin{align}
\rho=\frac{1}{2}\sum_{i=0}^3r_i\sigma_i,
\end{align}
where $\sigma_i$ are a $2\times2$ identity plus Pauli matrices.
For 2 qubits, in the general case, the density matrix cannot be written as
\begin{align}\label{eq:2qubits-densityM-PauliBasis-separable}
\rho&=\frac{1}{4}\qty(\sum_{i=0}^3r_i\sigma_i
\ot
\sum_{j=0}^3r_j\sigma_j)
\end{align}
because a 2-qubits state is not separable, in general. Therefore, 
the density matrix is written as
\begin{align}
\rho=\frac{1}{4}\sum_{i,j=0}^3r_{i,j}\sigma_{i,j}.
\end{align}
In some sense, expanding 
\eqref{eq:2qubits-densityM-PauliBasis-separable}
\begin{align}
\frac{1}{4}\qty(\sum_{i=0}^3r_i\sigma_i
\ot
\sum_{j=0}^3r_j\sigma_j)
&=\frac{1}{4}\qty(
\1_{4}\ot\1_{4}+\1\ot\sum_{j=1}^3r_j\sigma_j+
\sum_{i=1}^3r_i\sigma_i\ot\1+
\sum_{i=1}^3r_i\sigma_i\ot\sum_{j=1}^3r_j\sigma_j
)
\end{align}
makes us a hint realize that, in the general case, the components
of 2-qubits density matrix in tensor products of Pauli matrices basis are
\begin{align}
r_ir_j&\to r_{i.j},&\ r_i&\to r_{i,0},&\ r_j &\to r_{0,j}.
\end{align}
It follows that $n$-quits density matrix is
\begin{align}
\rho=\frac{1}{2^n}\sum_{j_1,\ldots,j_n=0}^3
r_{j_1,\ldots,j_n}\sigma_{j_1}\ot\ldots\ot\sigma_{j_n},
\end{align}
therefore,
\begin{align}
\label{eq:general-comp-of-density-matrix-in-Pauli-matrices-basis}
r_{j_1}\ldots r_{j_k}\ldots r_{j_n}&\to r_{j_1,\ldots,j_n}, &
r_{j_k}&\to r_{0,\ldots,j_k,\ldots,0},
\end{align}
where 
\begin{align}
r_{j_1}\ldots r_{j_k}\ldots r_{j_n}&\neq r_{j_1,\ldots,j_n}, &
r_{j_k}&\neq r_{0,\ldots,j_k,\ldots,0},
\end{align}

Now, the state $\rho_{\E}$ isomorphic to the Choi matrix $D_{\E}$
(is this written ok?) of a 1-qubit PCE channel~$\E$~is
\begin{align}
\rho_{\E}&=\sum_{i=0}^3\lambda_i \dyad{\sigma_i}{\sigma_i},
\end{align}
where $\ket{\sigma_i}$ are the vectorized $\sigma_i$ and
$\lambda_i$ are (this has been shown analytically)
\begin{align}\label{eq:eigvals-1q-choi}
\lambda_0&=\frac{1}{4}\qty(1+\tau_1+\tau_2+\tau_3), &
\lambda_1&=\frac{1}{4}\qty(1+\tau_1-\tau_2-\tau_3),\nonumber\\
\lambda_2&=\frac{1}{4}\qty(1-\tau_1+\tau_2-\tau_3), &
\lambda_3&=\frac{1}{4}\qty(1-\tau_1-\tau_2+\tau_3).
\end{align}

I claim that, in the same sense of 
\eqref{eq:general-comp-of-density-matrix-in-Pauli-matrices-basis},
the eigenvalues of $\rho_{\E}$ of $n$-qubits PCE quantum channel
$\E$ are of the form
\begin{align}
\lambda_{j_1}\ldots \lambda_{j_k}\ldots \lambda_{j_n}
&\to\lambda_{j_1,\ldots,j_n}, &
\lambda_{j_k}&\to\lambda_{0,\ldots,j_k,\ldots,0},
\end{align}
where $\lambda_k$ are the eigenvalues \eqref{eq:eigvals-1q-choi}.

\section{Number of PCE channels by the ratio of components 
left invariant}
\begin{itemize}
\item 1$/$2 of total components invariant:
\begin{align}
4^n-1
\end{align}

\item 1$/$4 of total components invariant:
\begin{align}
\frac{\binom{4^n-1}{2}}{3},
\end{align}

\item 1$/$8 of total components invariant:
\begin{align}
\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28}
\end{align}

\item 1$/$16 of total components invariant:
\begin{align}
\frac{\binom{4^n-1}{4}-35\qty(\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28})}{840}
\end{align}
\end{itemize}

\begin{table}[h!]
\tiny
\begin{tabular}{llllccccccclll}
{\color[HTML]{FF0000} \textbf{1}} &                       &                           &                                & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}               & \cellcolor[HTML]{FCE5CD}\textbf{1}   & \textbf{3}                             & \textbf{1}                              & \multicolumn{1}{l}{}                    & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
{\color[HTML]{FF0000} \textbf{2}} &                       &                           &                                & \multicolumn{1}{l}{} & \cellcolor[HTML]{FCE5CD}\textbf{1} & \cellcolor[HTML]{CFE2F3}\textbf{15}  & \cellcolor[HTML]{FCE5CD}\textbf{35}    & \textbf{15}                             & \textbf{1}                              & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
{\color[HTML]{FF0000} \textbf{3}} &                       &                           &                                & \textbf{1}           & \textbf{63}                        & \cellcolor[HTML]{FCE5CD}\textbf{651} & \cellcolor[HTML]{CFE2F3}\textbf{1,395} & \cellcolor[HTML]{FCE5CD}\textbf{651}    & \textbf{63}                             & \textbf{1}                          &                                                       &                                    &                                \\
{\color[HTML]{FF0000} \textbf{4}} &                       &                           & \multicolumn{1}{c}{\textbf{1}} & \textbf{255}         & \textbf{10,795}                    & 97,155                               & \cellcolor[HTML]{FCE5CD}200,787        & \cellcolor[HTML]{CFE2F3}\textbf{97,155} & \cellcolor[HTML]{FCE5CD}\textbf{10,795} & \textbf{255}                        & \multicolumn{1}{c}{\textbf{1}}                        &                                    &                                \\
{\color[HTML]{FF0000} \textbf{5}} &                       & \multicolumn{1}{c}{1}     & \multicolumn{1}{c}{1,023}      & 174,251              & 6,347,715                          & 53,743,987                           & \multicolumn{1}{l}{}                   & \cellcolor[HTML]{FCE5CD}53,743,987      & \cellcolor[HTML]{CFE2F3}6,347,715       & \cellcolor[HTML]{FCE5CD}174,251     & \multicolumn{1}{c}{\textbf{1,023}}                    & \multicolumn{1}{c}{\textbf{1}}     &                                \\
{\color[HTML]{FF0000} \textbf{6}} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{4,095} & \multicolumn{1}{c}{2,794,155}  & 408,345,795          & 13,910,980,083                     & \multicolumn{1}{l}{}                 & \multicolumn{1}{l}{}                   & \multicolumn{1}{l}{}                    & \cellcolor[HTML]{FCE5CD}13,910,980,083  & \cellcolor[HTML]{CFE2F3}408,345,795 & \multicolumn{1}{c}{\cellcolor[HTML]{FCE5CD}2,794,155} & \multicolumn{1}{c}{\textbf{4,095}} & \multicolumn{1}{c}{\textbf{1}}
\end{tabular}
\end{table}

\section{2 qubits: hermanitos}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{hermanitos}
  \caption{Los hermanitos de 2 qubits. La fila de arriba muestra al hermano 
  mayor del canal que tiene exactamente abajo.}
  \label{•}
\end{figure}

Estos hermanitos tienen la siguiente forma
\begin{align}
\Phi=\E_i\ot \E_j+\qty(\1-\E_i)\ot \qty(\1-\E_j),
\end{align}
donde $\E_i$ son el canal identidad y los 3 canales PCE que mapean 
la esfera de Bloch hacia alguno de los 3 ejes cartesianos.

En general, un canal cuántico PCE $\phi$ que deja invariantes únicamente 
dos componentes, $\tau_{0,\ldots,0}$ y otra $\tau_{j_1,\ldots,j_n}$,
tiene un `hermano mayor PCE' $\Phi$ que deja invariantes $4^n-1$
componentes que es de la forma
\begin{align}
\Phi=\sum_{i=0}^{i\leq n/2}
\sum_{j\in \mathcal{S}_{2i}^n}
\bigotimes_{j_i=1}^n\Omega{j_i},
\end{align}
donde $\mathcal{S}_{2i}^n$ es el conjunto que contiene 
a todos los subconjuntos con $2i$ elementos del 
conjunto \newline $\{ 1,2,3,\ldots,n \}$ y
\begin{align}
\Omega_{j_i}= \left\{ \begin{array}{rc}
             \E_{j_i}, & j_i \notin j \\
             \1 -\E_{j_i}, & j_i \in j.
             \end{array}
   \right.
\end{align}

For example, let us elaborate the example for the 3 and 4 qubits 
generators. First, the PCE generators for 3 qubits are
\begin{align}
\Phi_{j_1,j_2,j_3}=& \sum_{i=0}^{i\leq 3/2}
\sum_{j\in \mathcal{S}_{2i}^3}
\bigotimes_{j_i=1}^3\Omega{j_i} \nonumber \\
=&\ \Ej{1}\ot\Ej{2}\ot\Ej{3} + \id{1}\ot\id{2}\ot\Ej{3} \\
&+ \id{1}\ot\Ej{2}\ot\id{3} + \Ej{1}\ot\id{2}\ot\id{3}. \nonumber
\end{align}
The 4 qubits PCE generators are
\begin{align}
\Phi_{j_1,j_2,j_3,j_4}=& \sum_{i=0}^{i\leq 2}
\sum_{j\in \mathcal{S}_{2i}^4}
\bigotimes_{j_i=1}^4\Omega{j_i} \nonumber \\
=&\ \Ej{1}\ot\Ej{2}\ot\Ej{3}\ot\Ej{4} + 
\qty(\1-\Ej{1})\ot\qty(\1-\Ej{2})\ot\Ej{3}\ot\Ej{4} \nonumber \\
&+ \qty(\1-\Ej{1})\ot\Ej{2}\ot\qty(\1-\Ej{3})\ot\Ej{4}
+ \qty(\1-\Ej{1})\ot\Ej{2}\ot\Ej{3}\ot\qty(\1-\Ej{4}) \\
&+ \Ej{1}\ot\qty(\1-\Ej{2})\ot\qty(\1-\Ej{3})\ot\Ej{4}
+ \Ej{1}\ot\qty(\1-\Ej{2})\ot\Ej{3}\ot\qty(\1-\Ej{4}) \nonumber \\
&+ \Ej{1}\ot\Ej{2}\ot\qty(\1-\Ej{3})\ot\qty(\1-\Ej{4}) \nonumber \\
&+ \id{1}\ot\id{2}\ot\id{3}\ot\id{4}. \nonumber
\end{align}

### 2021-08-12 documentos/notas/notas_carlos.tex
Reset error count between rows. herpderp

\section{Krauss}

In order to study the Krauss operators corresponding to PCE's, it is enough to study 
the ones corresponding to generators, that is, the ones that leave 
have of the components invariant.

As a historical fact, the Krauss operators corresponding to one single qubit PCEs
are 
\begin{equation}
\{\openone/\sqrt2, \sigma_i/\sqrt2\}
\label{}
\end{equation}
(corresponding to the operation that leaves the component $\sigma_i$ invariant), 
see Eq. 8.95 of Chuang's book.  Visual inspection of the Krauss operators 
of two qubit PCEG (PCE generators) lead to the ansatz that 
the appropriate Krauss operators are 
\begin{equation}
\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma^{(k)}_{i_k}\right)/\sqrt2\right\}. 
\label{}
\end{equation}

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
\begin{equation}
\sigma_i \sigma_j \sigma_i =a^i_{j} \sigma_j,
\label{}
\end{equation}
with $a$ the matrix that appears in 
\eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
\eref{} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},

Counting, mostrar qe el numero de bichos que aparecen ahi coincide con el numero de generadores.

Show that they are unique

### 2021-08-12 documentos/notas/notas_carlos.tex
Don't tell me you're too blind to see

@@
 \{\openone/\sqrt2, \sigma_i/\sqrt2\}
-\label{}
+\label{eq:kraus:PCE}
 \end{equation}
@@
 \begin{equation}
-\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma^{(k)}_{i_k}\right)/\sqrt2\right\}. 
+\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
 \label{}
@@
 \eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
-\eref{} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},
+\eref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},
+\begin{align}
+\mcM[\rho] &= 
+\frac{\openone}{\sqrt{2}} \rho\frac{\openone}{\sqrt{2}} 
+ + 
+\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
+\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
+&=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
+&=\frac12 \rho
++ \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
+&=
+\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
+\end{align}
+However, $(1+\prod_k a^{i_k}_{j_k})/2$ is 0 or 1, proving the channel is a PCE.
 
-Counting, mostrar qe el numero de bichos que aparecen ahi coincide con el numero de generadores.
+We still have to show that except for $i_1=\cdots=i_n=0$, half of the numbers 
+$(1+\prod_k a^{i_k}_{j_k})/2=1$, or equivalently, half of $\prod_k a^{i_k}_{j_k}=1$. 
+Consider a particular $l$ such that $i_l \ne 0$. This will make half of 
+the $\prod_k a^{i_k}_{j_k}$ 1 and half $-1$ (for fixed $l$). This also implies 
+that half of the correlations of the density matrix are erased and half preserved 
+so the channel is a PCEG.
 
-Show that they are unique
+Notice also that different choices of sets $\{i_k \}$ lead to different channels. This
+can be seen noticing that if two channels were the same, this would imply that
+the matrix representation of the corresponding superoperator of 
+$\bigotimes_k \sigma_{i_k} \cdot \bigotimes_k \sigma_{i_k} $ would have to be
+the same which is clearly false.
+
+Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
+generator. This notation is based on the action on each individual qubit. (ii) Counting the
+number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
+from other arguments.

### 2021-08-19 documentos/notas/notas_ja.tex
Reset error count between rows. herpderp
diagonalización de la matriz de Choi de qutrits con GellMann

@@
-\section{CP from eigenvalues} % {{{
+\section{Eigenvalues of PCE operations' Choi matrix} % {{{
 % Intro {{{
@@
 % }}}
-\section{General characterisation of PCE quantum channels} % {{{
+\section{A general characterization of PCE quantum channels} % {{{
 \subsubsection*{To avoid confusion} % {{{
@@
 always erases half of the number of non-zero components. A proof 
-for that is missing.
-\item Analytic proof for \eqref{eq:inequalities-PCE}. 
+for that is missing. \janote{This is well explained with the vector spaces.}
+\item Analytic proof for \eqref{eq:eigvals-PCE}. \janote{Alejo's proof.} 
 \item Analytic proof that \eqref{eq:PCE-characterization} is necessary 
-and sufficient to find all elements in $\PCE{n}$.
-\item Analytic proof that taking $-1\to 0$ for $a_k^k$ leads to CP.
+and sufficient to find all elements in $\PCE{n}$. \janote{Francois' vector spaces.}
+\item Analytic proof that taking $-1\to 0$ for $a_k^k$ leads to CP. \janote{Francois'
+general procedure to find PCE channels.}
 I suggest using particle swaps and local basis permutation in order 
 to reduce the problem to $n$ inequalities.
-\item Find a way to count PCE channels.
+\item Find a way to count PCE channels. \janote{Also from Francois' vector spaces.}
 \end{enumerate}
@@
 
-\section{Progress}
-\subsection{An idea to prove equation \eqref{eq:eigvals-PCE}}
-A density matrix of 1 qubit in Pauli matrices basis is written as
-\begin{align}
-\rho=\frac{1}{2}\sum_{i=0}^3r_i\sigma_i,
-\end{align}
-where $\sigma_i$ are a $2\times2$ identity plus Pauli matrices.
-For 2 qubits, in the general case, the density matrix cannot be written as
-\begin{align}\label{eq:2qubits-densityM-PauliBasis-separable}
-\rho&=\frac{1}{4}\qty(\sum_{i=0}^3r_i\sigma_i
-\ot
-\sum_{j=0}^3r_j\sigma_j)
-\end{align}
-because a 2-qubits state is not separable, in general. Therefore, 
-the density matrix is written as
-\begin{align}
-\rho=\frac{1}{4}\sum_{i,j=0}^3r_{i,j}\sigma_{i,j}.
-\end{align}
-In some sense, expanding 
-\eqref{eq:2qubits-densityM-PauliBasis-separable}
-\begin{align}
-\frac{1}{4}\qty(\sum_{i=0}^3r_i\sigma_i
-\ot
-\sum_{j=0}^3r_j\sigma_j)
-&=\frac{1}{4}\qty(
-\1_{4}\ot\1_{4}+\1\ot\sum_{j=1}^3r_j\sigma_j+
-\sum_{i=1}^3r_i\sigma_i\ot\1+
-\sum_{i=1}^3r_i\sigma_i\ot\sum_{j=1}^3r_j\sigma_j
-)
-\end{align}
-makes us a hint realize that, in the general case, the components
-of 2-qubits density matrix in tensor products of Pauli matrices basis are
-\begin{align}
-r_ir_j&\to r_{i.j},&\ r_i&\to r_{i,0},&\ r_j &\to r_{0,j}.
-\end{align}
-It follows that $n$-quits density matrix is
-\begin{align}
-\rho=\frac{1}{2^n}\sum_{j_1,\ldots,j_n=0}^3
-r_{j_1,\ldots,j_n}\sigma_{j_1}\ot\ldots\ot\sigma_{j_n},
-\end{align}
-therefore,
-\begin{align}
-\label{eq:general-comp-of-density-matrix-in-Pauli-matrices-basis}
-r_{j_1}\ldots r_{j_k}\ldots r_{j_n}&\to r_{j_1,\ldots,j_n}, &
-r_{j_k}&\to r_{0,\ldots,j_k,\ldots,0},
-\end{align}
-where 
-\begin{align}
-r_{j_1}\ldots r_{j_k}\ldots r_{j_n}&\neq r_{j_1,\ldots,j_n}, &
-r_{j_k}&\neq r_{0,\ldots,j_k,\ldots,0},
-\end{align}
-
-Now, the state $\rho_{\E}$ isomorphic to the Choi matrix $D_{\E}$
-(is this written ok?) of a 1-qubit PCE channel~$\E$~is
-\begin{align}
-\rho_{\E}&=\sum_{i=0}^3\lambda_i \dyad{\sigma_i}{\sigma_i},
-\end{align}
-where $\ket{\sigma_i}$ are the vectorized $\sigma_i$ and
-$\lambda_i$ are (this has been shown analytically)
-\begin{align}\label{eq:eigvals-1q-choi}
-\lambda_0&=\frac{1}{4}\qty(1+\tau_1+\tau_2+\tau_3), &
-\lambda_1&=\frac{1}{4}\qty(1+\tau_1-\tau_2-\tau_3),\nonumber\\
-\lambda_2&=\frac{1}{4}\qty(1-\tau_1+\tau_2-\tau_3), &
-\lambda_3&=\frac{1}{4}\qty(1-\tau_1-\tau_2+\tau_3).
-\end{align}
-
-I claim that, in the same sense of 
-\eqref{eq:general-comp-of-density-matrix-in-Pauli-matrices-basis},
-the eigenvalues of $\rho_{\E}$ of $n$-qubits PCE quantum channel
-$\E$ are of the form
-\begin{align}
-\lambda_{j_1}\ldots \lambda_{j_k}\ldots \lambda_{j_n}
-&\to\lambda_{j_1,\ldots,j_n}, &
-\lambda_{j_k}&\to\lambda_{0,\ldots,j_k,\ldots,0},
-\end{align}
-where $\lambda_k$ are the eigenvalues \eqref{eq:eigvals-1q-choi}.
-
 \section{Number of PCE channels by the ratio of components 
 left invariant}
-\begin{itemize}
-\item 1$/$2 of total components invariant:
-\begin{align}
-4^n-1
-\end{align}
+%\begin{itemize}
+%\item 1$/$2 of total components invariant:
+%\begin{align}
+%4^n-1
+%\end{align}
+%
+%\item 1$/$4 of total components invariant:
+%\begin{align}
+%\frac{\binom{4^n-1}{2}}{3},
+%\end{align}
+%
+%\item 1$/$8 of total components invariant:
+%\begin{align}
+%\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28}
+%\end{align}
+%
+%\item 1$/$16 of total components invariant:
+%\begin{align}
+%\frac{\binom{4^n-1}{4}-35\qty(\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28})}{840}
+%\end{align}
+%\end{itemize}
+%
+%\begin{table}[h!]
+%\tiny
+%\begin{tabular}{llllccccccclll}
+%{\color[HTML]{FF0000} \textbf{1}} &                       &                           &                                & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}               & \cellcolor[HTML]{FCE5CD}\textbf{1}   & \textbf{3}                             & \textbf{1}                              & \multicolumn{1}{l}{}                    & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
+%{\color[HTML]{FF0000} \textbf{2}} &                       &                           &                                & \multicolumn{1}{l}{} & \cellcolor[HTML]{FCE5CD}\textbf{1} & \cellcolor[HTML]{CFE2F3}\textbf{15}  & \cellcolor[HTML]{FCE5CD}\textbf{35}    & \textbf{15}                             & \textbf{1}                              & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
+%{\color[HTML]{FF0000} \textbf{3}} &                       &                           &                                & \textbf{1}           & \textbf{63}                        & \cellcolor[HTML]{FCE5CD}\textbf{651} & \cellcolor[HTML]{CFE2F3}\textbf{1,395} & \cellcolor[HTML]{FCE5CD}\textbf{651}    & \textbf{63}                             & \textbf{1}                          &                                                       &                                    &                                \\
+%{\color[HTML]{FF0000} \textbf{4}} &                       &                           & \multicolumn{1}{c}{\textbf{1}} & \textbf{255}         & \textbf{10,795}                    & 97,155                               & \cellcolor[HTML]{FCE5CD}200,787        & \cellcolor[HTML]{CFE2F3}\textbf{97,155} & \cellcolor[HTML]{FCE5CD}\textbf{10,795} & \textbf{255}                        & \multicolumn{1}{c}{\textbf{1}}                        &                                    &                                \\
+%{\color[HTML]{FF0000} \textbf{5}} &                       & \multicolumn{1}{c}{1}     & \multicolumn{1}{c}{1,023}      & 174,251              & 6,347,715                          & 53,743,987                           & \multicolumn{1}{l}{}                   & \cellcolor[HTML]{FCE5CD}53,743,987      & \cellcolor[HTML]{CFE2F3}6,347,715       & \cellcolor[HTML]{FCE5CD}174,251     & \multicolumn{1}{c}{\textbf{1,023}}                    & \multicolumn{1}{c}{\textbf{1}}     &                                \\
+%{\color[HTML]{FF0000} \textbf{6}} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{4,095} & \multicolumn{1}{c}{2,794,155}  & 408,345,795          & 13,910,980,083                     & \multicolumn{1}{l}{}                 & \multicolumn{1}{l}{}                   & \multicolumn{1}{l}{}                    & \cellcolor[HTML]{FCE5CD}13,910,980,083  & \cellcolor[HTML]{CFE2F3}408,345,795 & \multicolumn{1}{c}{\cellcolor[HTML]{FCE5CD}2,794,155} & \multicolumn{1}{c}{\textbf{4,095}} & \multicolumn{1}{c}{\textbf{1}}
+%\end{tabular}
+%\end{table}
 
-\item 1$/$4 of total components invariant:
-\begin{align}
-\frac{\binom{4^n-1}{2}}{3},
-\end{align}
+From Francois' manuscript on the PCE's he states that it can be 
+proved from the vector spaces' idea that the number of PCE channels 
+of $N$ qubits $\mathcal{S}_{N,K}$ that leave $K$ Pauli components invariant is:
+\begin{equation}
+\mathcal{S}_{N,K}=\prod_{m=0}^{K-1}\frac{2^{2N-m}-1}{2^{K-m}-1}.
+\end{equation}
 
-\item 1$/$8 of total components invariant:
-\begin{align}
-\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28}
-\end{align}
-
-\item 1$/$16 of total components invariant:
-\begin{align}
-\frac{\binom{4^n-1}{4}-35\qty(\frac{\binom{4^n-1}{3}-\binom{4^n-1}{2}/3}{28})}{840}
-\end{align}
-\end{itemize}
-
-\begin{table}[h!]
-\tiny
-\begin{tabular}{llllccccccclll}
-{\color[HTML]{FF0000} \textbf{1}} &                       &                           &                                & \multicolumn{1}{l}{} & \multicolumn{1}{l}{}               & \cellcolor[HTML]{FCE5CD}\textbf{1}   & \textbf{3}                             & \textbf{1}                              & \multicolumn{1}{l}{}                    & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
-{\color[HTML]{FF0000} \textbf{2}} &                       &                           &                                & \multicolumn{1}{l}{} & \cellcolor[HTML]{FCE5CD}\textbf{1} & \cellcolor[HTML]{CFE2F3}\textbf{15}  & \cellcolor[HTML]{FCE5CD}\textbf{35}    & \textbf{15}                             & \textbf{1}                              & \multicolumn{1}{l}{}                &                                                       &                                    &                                \\
-{\color[HTML]{FF0000} \textbf{3}} &                       &                           &                                & \textbf{1}           & \textbf{63}                        & \cellcolor[HTML]{FCE5CD}\textbf{651} & \cellcolor[HTML]{CFE2F3}\textbf{1,395} & \cellcolor[HTML]{FCE5CD}\textbf{651}    & \textbf{63}                             & \textbf{1}                          &                                                       &                                    &                                \\
-{\color[HTML]{FF0000} \textbf{4}} &                       &                           & \multicolumn{1}{c}{\textbf{1}} & \textbf{255}         & \textbf{10,795}                    & 97,155                               & \cellcolor[HTML]{FCE5CD}200,787        & \cellcolor[HTML]{CFE2F3}\textbf{97,155} & \cellcolor[HTML]{FCE5CD}\textbf{10,795} & \textbf{255}                        & \multicolumn{1}{c}{\textbf{1}}                        &                                    &                                \\
-{\color[HTML]{FF0000} \textbf{5}} &                       & \multicolumn{1}{c}{1}     & \multicolumn{1}{c}{1,023}      & 174,251              & 6,347,715                          & 53,743,987                           & \multicolumn{1}{l}{}                   & \cellcolor[HTML]{FCE5CD}53,743,987      & \cellcolor[HTML]{CFE2F3}6,347,715       & \cellcolor[HTML]{FCE5CD}174,251     & \multicolumn{1}{c}{\textbf{1,023}}                    & \multicolumn{1}{c}{\textbf{1}}     &                                \\
-{\color[HTML]{FF0000} \textbf{6}} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{4,095} & \multicolumn{1}{c}{2,794,155}  & 408,345,795          & 13,910,980,083                     & \multicolumn{1}{l}{}                 & \multicolumn{1}{l}{}                   & \multicolumn{1}{l}{}                    & \cellcolor[HTML]{FCE5CD}13,910,980,083  & \cellcolor[HTML]{CFE2F3}408,345,795 & \multicolumn{1}{c}{\cellcolor[HTML]{FCE5CD}2,794,155} & \multicolumn{1}{c}{\textbf{4,095}} & \multicolumn{1}{c}{\textbf{1}}
-\end{tabular}
-\end{table}
-
-\section{2 qubits: hermanitos}
+\section{Rainbow correspondence}
 \begin{figure}

### 2021-08-20 documentos/notas/notas_carlos.tex

@@
-\section{Krauss}
+\section{Kraus}
 
-In order to study the Krauss operators corresponding to PCE's, it is enough to study 
+In order to study the Kraus operators corresponding to PCE's, it is enough to study 
 the ones corresponding to generators, that is, the ones that leave 
@@
 
-As a historical fact, the Krauss operators corresponding to one single qubit PCEs
+As a historical fact, the Kraus operators corresponding to one single qubit PCEs
 are 
 \begin{equation}
-\{\openone/\sqrt2, \sigma_i/\sqrt2\}
+\{\1/\sqrt2, \sigma_i/\sqrt2\}
 \label{eq:kraus:PCE}
@@
 (corresponding to the operation that leaves the component $\sigma_i$ invariant), 
-see Eq. 8.95 of Chuang's book.  Visual inspection of the Krauss operators 
+see Eq. 8.95 of Chuang's book.  Visual inspection of the Kraus operators 
 of two qubit PCEG (PCE generators) lead to the ansatz that 
-the appropriate Krauss operators are 
+the appropriate Kraus operators are 
 \begin{equation}
-\left\{\openone/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
+\left\{\1/\sqrt2, \left(\bigotimes_k \sigma_{i_k}\right)/\sqrt2\right\}. 
 \label{}
@@
 with $a$ the matrix that appears in 
-\eref{eq:eigvals-PCE}. Next, consider the action of a channel with Krauss representation 
-\eref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eref{eq:nqubit:bloch},
+\eqref{eq:eigvals-PCE}. Next, consider the action of a channel with Kraus representation 
+\eqref{eq:kraus:PCE} on an $n$ qubit system with Bloch sphere representation \eqref{eq:nqubit:bloch},
 \begin{align}
-\mcM[\rho] &= 
-\frac{\openone}{\sqrt{2}} \rho\frac{\openone}{\sqrt{2}} 
+M[\rho] &= 
+\frac{\1}{\sqrt{2}} \rho\frac{\1}{\sqrt{2}} 
  + 

### 2021-08-20 documentos/notas/qutrits.tex

\section{Eigenvalues of GellMann component erasing operations' Choi matrix}
Es de nuestro interés investigar si los eigenvalores de la matriz de Choi de
las operaciones de GellMann que borran componentes (GMCE) de sistemas de qutrits son 
una función lineal de los elementos $\tau_{j_1,\ldots,j_n}=0,1$ de las operaciones GMCE.
Numéricamente, podemos chequear esto con la expresión
\begin{align}\label{eq:linearity_eigv_ChoiMatrix}
P^{-1}D_{\E}\qty[c \vec{\tau}_1+\vec{\tau}_2]P=P^{-1}\qty(cD_{\E}[\vec{\tau}_1]+D_{\E}[\vec{\tau}_2])P,
\end{align}
donde $D_{\E}[\vec{\tau}_i]$ es la matriz de Choi de una operación GMCE con los 1's
y 0's en el vector $\vec{\tau}_i$ y $P$ la matriz de cambio de base a la base en la que 
$D_{\E}[\vec{\tau}_i]$ es diagonal. Un requisito necesario para que exista $P$ en
\eqref{eq:linearity_eigv_ChoiMatrix} es que las matrices $D_{\E}\qty[c \vec{\tau}_1+\vec{\tau}_2]$,
$D_{\E}[\vec{\tau}_1]$ y $D_{\E}[\vec{\tau}_2]$ deben conmutar todas entre sí. No obstante, 
este no es el caso para las operaciones GMCE. En el archivo \texttt{qutrits.nb}, que se 
encuentra en la dirección \texttt{mathematica/} en el repositorio se encuentra 
desarrollado que las matrices $D_{\E}\qty[c \vec{\tau}_1+\vec{\tau}_2]$, 
$D_{\E}[\vec{\tau}_1]$ y $D_{\E}[\vec{\tau}_2]$ no conmutan.

### 2021-08-23 documentos/generators.tex
dividiendo en archivos y demas cosas

\section{Generators} % {{{
\begin{itemize}
\item Clasificacion de los generadores, es decir que para dos qubits, lo podemos indicar con la acción sobre cada qubit individual
\item Quizá mostrar algunas propiedades de simetrías. 
\end{itemize}
% }}}

### 2021-08-23 documentos/intro.tex
dividiendo en archivos y demas cosas

\section{Introduction} % {{{
Several PRA articles go straight into matter. I guess we will write what we have to write
% }}}

### 2021-08-23 documentos/kraus.tex
dividiendo en archivos y demas cosas

\section{Kraus operators and decoherence} % {{{

\begin{itemize}
\item Construct the Kraus operators, and relate to decoherence, for PCEG
\item Play with non PCEG PCEs
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en particular para todos los canales (sistema central + ambiente). Seria de buscar dilataciones sencillas y razonables por lo menos a los canales generadores.
\end{itemize}

% }}}

### 2021-08-23 documentos/math.tex
dividiendo en archivos y demas cosas

\section{Mathematical derivation} % {{{

{Vector space, mathematical derivation of properties}

\begin{itemize}
\item Diagonalización de la matriz de Choi de los canales de Pauli, es decir prueba da la $a$
\item Prueba de que la a diagonaliza \afnote{Breve descripción de detalles importantes. Cálculos en un Apéndice?}
\item Canales PCE como espacios vectoriales
\item Regla de $2^k$
\item Tamaño de las diferentes clases que borran un numero fijo de componentes
y tambien nota de qeu son igual entre complementarios: computo del numero de bases dada una dimension de subespacios vectoriales, aqui entra la formula del binomial-q.
\item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
\item \ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}
\end{itemize}

% }}}

### 2021-08-23 documentos/pce.tex
dividiendo en archivos y demas cosas

\section{PCE Maps} % {{{
\subsection{Quantum channels}
\subsection{Single qubit projective maps} % {{{
\ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos mapas proyectivos, hay mapas proyectivos no unitales}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Also, maybe the Kraus operators.
\item Also some relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE, maybe give some two qubit examples
to illustrate non-trivial points. 
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
\item \afnote{Relación con canales citados en \cite{Siudzinska2020}?}
\end{itemize}
% }}}
\begin{itemize}
\item Give a formal definition of the PCE, maybe give some two qubit examples
to illustrate non-trivial points. 
\item This will serve to bring the derivation a bit more down to earth. 
\item Visualizacion y ejemplos?
\item Notar lo de los generadores y como sale la estructura jerárquica 
\item Son positivas todas las matrices de densidad que resultan de aplicar un
mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
sucede para $n$ qubits.}
\end{itemize}
% }}}

### 2021-08-23 documentos/math.tex
the magic is real

@@
 \begin{itemize}
-\item Diagonalización de la matriz de Choi de los canales de Pauli, es decir prueba da la $a$
-\item Prueba de que la a diagonaliza \afnote{Breve descripción de detalles importantes. Cálculos en un Apéndice?}
-\item Canales PCE como espacios vectoriales
+\item Diagonalización de la matriz de Choi de los canales de Pauli, es decir
+prueba da la $\sa$ \todo{Alejo escribe esta parte. Dejelo aca todo y luego si acaso 
+pasamos cosas al apendice. Caso general}
+% \item Prueba de que la a diagonaliza \afnote{Breve descripción de detalles importantes. Cálculos en un Apéndice?}
+\item Canales PCE como espacios vectoriales \todo{Francois escribe}
 \item Regla de $2^k$
 \item Tamaño de las diferentes clases que borran un numero fijo de componentes
-y tambien nota de qeu son igual entre complementarios: computo del numero de bases dada una dimension de subespacios vectoriales, aqui entra la formula del binomial-q.
+y tambien nota de qeu son igual entre complementarios: computo del numero de
+bases dada una dimension de subespacios vectoriales, aqui entra la formula del
+binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
 \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.

### 2021-08-23 documentos/pce.tex
the magic is real

@@
 \subsection{Quantum channels}
-\subsection{Single qubit projective maps} % {{{
-\ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos mapas proyectivos, hay mapas proyectivos no unitales}
+\subsection{Single qubit case} % {{{
+% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
+% mapas proyectivos, hay mapas proyectivos no unitales}
+\todo{David escribe una primera version y luego Carlos itera}
 \begin{itemize}
 \item The single qubit case, describe some of the features.
-\item Also, maybe the Kraus operators.
-\item Also some relation with decoherence. 
+\item Single qubit Kraus operators.
+\item Single qubit relation with decoherence. 
 \end{itemize}
@@
 \begin{itemize}
-\item Give a formal definition of the PCE, maybe give some two qubit examples
-to illustrate non-trivial points. 
+\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
+\item Give some two qubit examples to illustrate non-trivial points with examples
+(isualizacion y ejemplos)
+\todo{Jose Alfredo escribe}
 \item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
-\item \afnote{Relación con canales citados en \cite{Siudzinska2020}?}
+y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
+que mover si es que necesitamos herramientas que discutiremos mas adelante para
+hacer notar la diferencia}
 \end{itemize}
 % }}}
-\begin{itemize}
-\item Give a formal definition of the PCE, maybe give some two qubit examples
-to illustrate non-trivial points. 
-\item This will serve to bring the derivation a bit more down to earth. 
-\item Visualizacion y ejemplos?
-\item Notar lo de los generadores y como sale la estructura jerárquica 
-\item Son positivas todas las matrices de densidad que resultan de aplicar un
-mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
-te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
-sucede para $n$ qubits.}
-\end{itemize}
+% \begin{itemize}
+% \item Son positivas todas las matrices de densidad que resultan de aplicar un
+% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
+% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
+% sucede para $n$ qubits.}
+% \end{itemize}
 % }}}

### 2021-08-24 documentos/generators.tex
the magic is real
Continued development...

@@
 \section{Generators} % {{{
+\todo{Francois escribe una primera version del primer punto, y luego quizá Jose
+Alfredo o Carlos la terminan}
+
+We have the matrix 
+\begin{equation}
+\sa=\left(
+\begin{array}{cccc}
+1 &1 &1   &1   \\
+ 1 & 1  & -1&-1   \\
+1  & -1  & 1 & -1\\
+1&-1&-1&1  
+\end{array}
+\right)=\frac12\sa^{-1}.
+\label{eq:1}
+\end{equation}
+and further define the matrix
+\begin{equation}
+\san=\left(\sa\right)^{\otimes N}
+\label{eq:1a}
+\end{equation}
+We look for those vectors $\vec\sigma$ consisting of 0's and 1's such that 
+\begin{equation}
+\san\vec\sigma=2^N\vec p
+\label{eq:3}
+\end{equation}
+where $\vec p$ is a vector with positive entries. Here $\vec\sigma$ is a $4^N$ dimensional vector of 0's
+and 1's. We number the entries of $\vec\sigma$ 
+by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq4$.
+The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
+the expression (\ref{eq:3}) satisfies
+\begin{equation}
+\left(
+\san_{\vec\alpha\vec\beta}
+\right)
+\sigma_\beta=2^Np_{\vec\alpha}
+\label{eq:4}
+\end{equation}
+where
+\begin{equation}
+\left(
+\san_{\vec\alpha\vec\beta}
+\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+\label{eq:5}
+\end{equation}
+
+From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
+\begin{equation}
+\sigma_\alpha=\left(
+\san_{\vec\alpha\vec\beta}
+\right)p_\beta
+\label{eq:6}
+\end{equation}
+which we analyze iteratively. We shall essentially use the fact that
+\begin{equation}
+p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
+\label{eq:7}
+\end{equation}
+
+Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
+of multi-indices $\Phi(\vec\alpha)$ as follows
+\begin{equation}
+\Phi(\vec\alpha):=\left\{
+\vec\beta:\san_{\vec\alpha\vec\beta}=1
+\right\}=\left\{
+\vec\beta:
+\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+=1
+\right\}
+\label{eq:8}
+\end{equation}
+If we now assume that $\sigma_{\vec\alpha}=1$, it follows from subtracting the two combined equations
+\begin{subequations}
+\begin{eqnarray}
+\sum_{\vec\beta}p_{\vec\beta}&=&1
+\label{eq:9a}\\
+\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\sigma_{\vec\alpha}=1
+\end{eqnarray}
+\label{eq:9}
+\end{subequations}
+that for all $\vec\beta\notin\Phi(\vec\alpha)$
+\begin{eqnarray}
+p_{\vec\beta}=0.
+\label{eq:10}
+\end{eqnarray}
+Thus, if $\sigma_{\vec\alpha}=1$, then $\sigma_{\vec\gamma}$
+and $\sigma_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
+\begin{equation}
+\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
+\label{eq:11}
+\end{equation}
+holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
+to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
+
+% If this condition is fulfilled and $\sigma_{\vec\alpha}=1$, then
+%\begin{subequations}
+%\begin{eqnarray}
+%\sigma_{\vec\gamma}&=&\sum_{\vec\beta}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
+%\label{eq:10na}
+%\\
+%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
+%\label{eq:10nb}
+%\\
+%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
+%\label{eq:10nc}
+%\\
+%&=&\sum_{\vec\beta}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
+%\label{eq:10nd}
+%\\
+%&=&\sigma_{\vec{\gamma^\prime}}
+%\label{eq:10ne}
+%\end{eqnarray}
+%\label{eq:10n}
+%\end{subequations}
+%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
+%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).
+
+Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
+When such a connection exists, $\sigma_{\vec\alpha}=1$ implies 
+$\sigma_{\vec\gamma}=\sigma_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.
+
+Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
+\begin{equation}
+\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+\label{eq:12}
+\end{equation}
+This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
+\begin{equation}
+\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
+\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
+\label{eq:13}
+\end{equation}
+Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
+the above relation must hold individually for every index. Thus we have, 
+that, for all $1\leq k\leq N$, $\gamma_k$
+and $\gamma_k^\prime$ are connected by
+\begin{equation}
+\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
+\label{eq:14}
+\end{equation}
+for all $0\leq\beta\leq3$. This is equivalently expressed as 
+\begin{equation}
+\gamma_k^\prime=\alpha\oplus{}\gamma_k
+\label{eq:15}
+\end{equation}
+where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.
+
+\begin{figure}
+\begin{center}
+\begin{tabular}{| c | c c c c |}
+\hline
+$\oplus{}$ & 0 & 1& 2 & 3\\
+\hline
+0 & 0 & 1 & 2 & 3\\
+1 & 1 & 0 & 3 & 2\\
+2 & 2 & 3 & 0 & 1 \\
+3 &3 & 2 & 1 & 0\\
+\hline
+\end{tabular}
+\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
+is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
+neutral element is $0$. This is the reason for choosing an additive notation for the operation
+defined in (\ref{eq:14}).
+}
+\label{tab:1}
+\end{center}
+\end{figure}
+
+Note further that if we perform the identification
+\begin{subequations}
+\begin{eqnarray}
+0&\to&(0,0)\label{eq:identa}\\
+1&\to&(0,1)\label{eq:identb}\\
+2&\to&(1,0)\label{eq:identc}\\
+3&\to&(1,1)\label{eq:identd}
+\end{eqnarray}
+\label{eq:ident}
+\end{subequations}
+then the $\oplus$ operation reduces to simple vector addition in
+binary arithmetic. If we therefore denote by $\overline{\alpha}$
+the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
+the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
+as
+\begin{equation}
+\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
+\label{eq:17}
+\end{equation}
+where the addition sign here refers to ordinary binary vector addition.
+
+From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
+for which $\sigma_{\overline\gamma}=1$, is closed under binary vector addition, in other words, it
+forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
+$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
+\begin{equation}
+\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
+\label{eq:14b}
+\end{equation}
+then by the preceding considerations, $\sigma_{\overline\gamma^\prime}$ is equal to $\sigma_{\overline\gamma}$
+and thus equal to one.
+
+So we may now proceed to generate all solutions: we start out from the solution having $\sigma_{\vec0}=1$, with
+everything else $0$. We may then successively switch $\sigma$'s to $1$ for various values of $\vec\alpha$, 
+taking care immediately to set equal to one the values of $\sigma$ that correspond to values of $\vec\beta$
+generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).
+
+A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
+set all $\sigma_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
+subspace of the set of all indices, then the vector $\vec\sigma$ indeed has an image which is a vector with 
+only positive components.
+
+%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
+%componentwise
+%\begin{equation}
+%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
+%\label{eq:16}
+%\end{equation}
+%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.
+
+%If $\sigma_{\vec\alpha}=1$, then it follows from the above that 
+%for all $\gamma$
+%\begin{equation}
+%\sigma_{\vec\gamma}=\sigma_{\vec\alpha\oplus{}\vec\gamma}.
+%\label{eq:17}
+%\end{equation}
+
+%Now take an arbitrary $\vec{\alpha}_1$ and set $\sigma_{\vec{\alpha}_1}=1$. This immediately imposes the
+%relationship
+%\begin{equation}
+%\sigma_{\vec\gamma}=\sigma_{\alp1\oplus{}\vec\gamma}
+%\label{eq:18}
+%\end{equation}
+%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\sigma$
+%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
+%and $\sigma_{\vec0}$ is one by convention. 
+%
+%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
+%that is automatically equal to $\sigma_{\alp1}$. Set $\sigma_{\alp2}=1$. We obviously must also set $\sigma_{\alp2\oplus\alp1}=1$,
+%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
+%\begin{equation}
+%\sigma_{\vec\gamma}=\sigma_{\alp1\oplus{}\vec\gamma}=\sigma_{\alp2\oplus{}\vec\gamma}=\sigma_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
+%\label{eq:19}
+%\end{equation}
+%Thus we find that the $\sigma$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
+%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\sigma_{\alp1}=1$. Further, it follows from the group property
+%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
+%to any other $\vec{\gamma^\prime}$. 
+%
+%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
+%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
+%
+%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
+%in other words, we may double $2N-1$ times.
+%
+%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
+%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
+%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
+%of the $\alp{k}$. 
+%
+%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
+%At this stage, the $\sigma_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
+%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
+%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
+%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
+%
+%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
+%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.
+
+The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
+\begin{equation}
+W=\left\{
+\vec\alpha:\vec\alpha\in V, \sigma_{\vec\alpha}=1
+\right\}
+\label{eq:19}
+\end{equation}
+is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
+a vector $\vec\sigma$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.
+
+By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
+$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
+the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
+the result that all PCE's can be obtained as intersections of maximal PCE's.
+
+****************************************
+
+This should probably be in an Appendix
+
+Finally, we may enumerate straightforwardly the subspaces $W$ of dimension $K$. We do this in 2 steps: first, we evaluate
+$\nnn_{K,N}$, the number of all linearly independent subsets $V$ with $K$ elements. Each of these is the basis of one 
+subspace of dimension $K$, but 
+each subspace has a number $\mmm_K$ of different bases. The crucial point is that $\mmm_K$ is independent 
+of the subspace under consideration: $\mmm_K$ simply describes the number of linear maps of $W$ onto itself. The 
+total number $\sss_{N,K}$ of subspaces of dimension $K$ is therefore $\nnn_{N,K}/\mmm_K$.
+
+To evaluate $\nnn_{N,K}$ we proceed by steps: the first element of the basis can be any non-zero element, of which the number
+is $2^{2N}-1$. For the  basis element $m+1$, we must choose from those which do not belong to the 
+$m$ dimensional space generated by the first $m$ basis elements, so that one chooses from $2^{2N}-2^{m}$. We thus have
+\begin{equation}
+\nnn_{N,K}=\prod_{m=0}^{K-1}\left(
+2^{2N}-2^{m}
+\right).
+\label{eq.20}
+\end{equation}
+On the other hand, any map of a $K$-dimensional vector space $W$ onto itself is uniquely
+defined by a non-singular binary $K\times K$ matrix over the field $\{0,1\}$. To count these, we proceed as 
+above: the first line is an arbitrary non-zero vector, of which there are $2^K-1$. For the row $m+1$  we must 
+choose an arbitrary vector not belonging to those generated by the first $m$ vectors, of which there are $2^K-2^{m}$. 
+This eventually yields
+\begin{equation}
+\mmm_{K}=\prod_{m=0}^{K-1}\left(
+2^{K}-2^{m}
+\right).
+\label{eq.21}
+\end{equation}
+From this follows that
+\begin{equation}
+\sss_{N,K}=\prod_{m=0}^{K-1}
+\frac{2^{2N-m}-1}{2^{K-m}-1}
+.
+\label{eq:22}
+\end{equation}
+%An elementary test is $N=3$ and $K=2,3$: 
+%\begin{eqnarray}
+%\sss_{3,2}&=&\frac{(2^6-1)(2^5-1)}{(2^2-1)(2^1-1)}=\frac{63\cdot31}{3}=651,\\
+%\sss_{3,3}&=&\frac{(2^6-1)(2^5-1)(2^4-1)}{(2^3-1)(2^2-1)(2^1-1)}=\frac{63\cdot31\cdot15}{7\cdot3}=1395,
+%\end{eqnarray}
+%which are indeed the values found numerically. 
+The following symmetry relation
+\begin{equation}
+\sss_{N,K}=\sss_{N,2N-K}
+\end{equation}
+can also be proved straightforwardly from (\ref{eq:22}).
+
+****************************************
+
 \begin{itemize}
@@
 \item Quizá mostrar algunas propiedades de simetrías. 
+\item Notar lo de los generadores y como sale la estructura jerárquica 
 \end{itemize}

### 2021-08-24 documentos/math.tex
See last commit

--- 2021-08-23 documentos/math.tex
@@
 \section{Mathematical derivation} % {{{
+\subsection{Diagonalization of Choi matrix} % {{{
 
-{Vector space, mathematical derivation of properties}
+Prueba de la $\sa$ \todo{Alejo escribe esta parte. Dejelo aca todo y luego si acaso 
+pasamos cosas al apendice. Caso general}
 
-\begin{itemize}
-\item Diagonalización de la matriz de Choi de los canales de Pauli, es decir prueba da la $a$
-\item Prueba de que la a diagonaliza \afnote{Breve descripción de detalles importantes. Cálculos en un Apéndice?}
-\item Canales PCE como espacios vectoriales
-\item Regla de $2^k$
-\item Tamaño de las diferentes clases que borran un numero fijo de componentes
-y tambien nota de qeu son igual entre complementarios: computo del numero de bases dada una dimension de subespacios vectoriales, aqui entra la formula del binomial-q.
-\item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
-\item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
+We have the matrix 
+\begin{equation}
+\sa=\left(
+\begin{array}{cccc}
+1 &1 &1   &1   \\
+ 1 & 1  & -1&-1   \\
+1  & -1  & 1 & -1\\
+1&-1&-1&1  
+\end{array}
+\right)=\frac12\sa^{-1}.
+\label{eq:1}
+\end{equation}
+and further define the matrix
+\begin{equation}
+\san=\left(\sa\right)^{\otimes N}
+\label{eq:1a}
+\end{equation}
+% }}}
+\subsection{A vector space of channels} % {{{
+% \begin{itemize} % {{{ Cosas por escribir aca
+% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
+% \item Regla de $2^k$
+% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
+% y tambien nota de qeu son igual entre complementarios: computo del numero de
+% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
+% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
+% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
+% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
+% Concepts might be complicated, but the tool gives some simple rules to the
+% reader: \textit{tell me what components you want to keep, and the (vector)
+% summation rules will give you the rest of components to make the target
+% operation a CPTP one.}
+% \end{itemize} % }}}
+
+We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
+\begin{equation}
+\san\vec\tau=2^N\vec p
+\label{eq:3}
+\end{equation}
+where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
+and 1's. We number the entries of $\vec\tau$ 
+by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
+The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
+the expression (\ref{eq:3}) satisfies
+\begin{equation}
+\left(
+\san_{\vec\alpha\vec\beta}
+\right)
+\tau_\beta=2^Np_{\vec\alpha}
+\label{eq:4}
+\end{equation}
+where
+\begin{equation}
+\left(
+\san_{\vec\alpha\vec\beta}
+\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+\label{eq:5}
+\end{equation}
+
+From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
+\begin{equation}
+\tau_\alpha=\left(
+\san_{\vec\alpha\vec\beta}
+\right)p_\beta
+\label{eq:6}
+\end{equation}
+which we analyze iteratively. We shall essentially use the fact that
+\begin{equation}
+p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
+\label{eq:7}
+\end{equation}
+
+Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
+of multi-indices $\Phi(\vec\alpha)$ as follows
+\begin{equation}
+\Phi(\vec\alpha):=\left\{
+\vec\beta:\san_{\vec\alpha\vec\beta}=1
+\right\}=\left\{
+\vec\beta:
+\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+=1
+\right\}
+\label{eq:8}
+\end{equation}
+If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting the two combined equations
+\begin{subequations}
+\begin{eqnarray}
+\sum_{\vec\beta}p_{\vec\beta}&=&1
+\label{eq:9a}\\
+\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
+\end{eqnarray}
+\label{eq:9}
+\end{subequations}
+that for all $\vec\beta\notin\Phi(\vec\alpha)$
+\begin{eqnarray}
+p_{\vec\beta}=0.
+\label{eq:10}
+\end{eqnarray}
+Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
+and $\tau_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
+\begin{equation}
+\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
+\label{eq:11}
+\end{equation}
+holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
+to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
+
+% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
+%\begin{subequations}
+%\begin{eqnarray}
+%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
+%\label{eq:10na}
+%\\
+%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
+%\label{eq:10nb}
+%\\
+%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
+%\label{eq:10nc}
+%\\
+%&=&\sum_{\vec\beta}\left(
+%M^{\otimes N}
+%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
+%\label{eq:10nd}
+%\\
+%&=&\tau_{\vec{\gamma^\prime}}
+%\label{eq:10ne}
+%\end{eqnarray}
+%\label{eq:10n}
+%\end{subequations}
+%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
+%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).
+
+Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
+When such a connection exists, $\tau_{\vec\alpha}=1$ implies 
+$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.
+
+Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
+\begin{equation}
+\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+\label{eq:12}
+\end{equation}
+This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
+\begin{equation}
+\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
+\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
+\label{eq:13}
+\end{equation}
+Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
+the above relation must hold individually for every index. Thus we have, 
+that, for all $1\leq k\leq N$, $\gamma_k$
+and $\gamma_k^\prime$ are connected by
+\begin{equation}
+\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
+\label{eq:14}
+\end{equation}
+for all $0\leq\beta\leq3$. This is equivalently expressed as 
+\begin{equation}
+\gamma_k^\prime=\alpha\oplus{}\gamma_k
+\label{eq:15}
+\end{equation}
+where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.
+
+\begin{figure}
+\begin{center}
+\begin{tabular}{| c | c c c c |}
+\hline
+$\oplus{}$ & 0 & 1& 2 & 3\\
+\hline
+0 & 0 & 1 & 2 & 3\\
+1 & 1 & 0 & 3 & 2\\
+2 & 2 & 3 & 0 & 1 \\
+3 &3 & 2 & 1 & 0\\
+\hline
+\end{tabular}
+\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
+is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
+neutral element is $0$. This is the reason for choosing an additive notation for the operation
+defined in (\ref{eq:14}).
+}
+\label{tab:1}
+\end{center}
+\end{figure}
+
+Note further that if we perform the identification
+\begin{subequations}
+\begin{eqnarray}
+0&\to&(0,0)\label{eq:identa}\\
+1&\to&(0,1)\label{eq:identb}\\
+2&\to&(1,0)\label{eq:identc}\\
+3&\to&(1,1)\label{eq:identd}
+\end{eqnarray}
+\label{eq:ident}
+\end{subequations}
+then the $\oplus$ operation reduces to simple vector addition in
+binary arithmetic. If we therefore denote by $\overline{\alpha}$
+the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
+the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
+as
+\begin{equation}
+\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
+\label{eq:17}
+\end{equation}
+where the addition sign here refers to ordinary binary vector addition.
+
+From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
+for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
+to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
+forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
+$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
+\begin{equation}
+\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
+\label{eq:14b}
+\end{equation}
+then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
+and thus equal to one.
+
+So we may now proceed to generate all solutions: we start out from the solution having $\tau_{\vec0}=1$, with
+everything else $0$. We may then successively switch $\tau$'s to $1$ for various values of $\vec\alpha$, 
+taking care immediately to set equal to one the values of $\tau$ that correspond to values of $\vec\beta$
+generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).
+
+A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
+set all $\tau_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
+subspace of the set of all indices, then the vector $\vec\tau$ indeed has an image which is a vector with 
+only positive components.
+
+%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
+%componentwise
+%\begin{equation}
+%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
+%\label{eq:16}
+%\end{equation}
+%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.
+
+%If $\tau_{\vec\alpha}=1$, then it follows from the above that 
+%for all $\gamma$
+%\begin{equation}
+%\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}.
+%\label{eq:17}
+%\end{equation}
+
+%Now take an arbitrary $\vec{\alpha}_1$ and set $\tau_{\vec{\alpha}_1}=1$. This immediately imposes the
+%relationship
+%\begin{equation}
+%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}
+%\label{eq:18}
+%\end{equation}
+%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\tau$
+%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
+%and $\tau_{\vec0}$ is one by convention. 
+%
+%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
+%that is automatically equal to $\tau_{\alp1}$. Set $\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
+%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
+%\begin{equation}
+%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}=\tau_{\alp2\oplus{}\vec\gamma}=\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
+%\label{eq:19}
+%\end{equation}
+%Thus we find that the $\tau$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
+%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$. Further, it follows from the group property
+%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
+%to any other $\vec{\gamma^\prime}$. 
+%
+%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
+%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
+%
+%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
+%in other words, we may double $2N-1$ times.
+%
+%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
+%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
+%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
+%of the $\alp{k}$. 
+%
+%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
+%At this stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
+%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
+%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
+%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
+%
+%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
+%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.
+
+The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
+\begin{equation}
+W=\left\{
+\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
+\right\}
+\label{eq:19}
+\end{equation}
+is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
+a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.
+
+By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
+$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
+the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
+the result that all PCE's can be obtained as intersections of maximal PCE's.
+
+\ddnote{Agrego esto:} A final remarks of the derivation as a tool.
 Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}
-\end{itemize}
 

### 2021-08-26 documentos/kraus.tex
the magic is real
That last commit message about silly mistakes pales in comparision to this one

@@
 \section{Kraus operators and decoherence} % {{{
+\todo{Carlos hace una version}
 
@@
 \item Play with non PCEG PCEs
-\item Dependiendo de si sale algo bonito, podemos poner algun modelo en particular para todos los canales (sistema central + ambiente).
-Seria de buscar dilataciones sencillas y razonables por lo menos a los canales generadores.
+\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
+particular para todos los canales (sistema central + ambiente). Seria de buscar
+dilataciones sencillas y razonables por lo menos a los canales generadores.
+\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
 \end{itemize}
 
+The Kraus operators of PCE channels provide an insight in the physical processes
+that yield such channels. In this section we investigate and construct such 
+operators and explore the corresponding processes.
+
+To study the Kraus operators corresponding to PCE, it is enough to study 
+the ones corresponding to generators, as all PCEs commute and thus to get the 
+Kraus operators of an arbitrary PCE, one can easily combine the Kraus
+operators of its generators.
+
+% The Kraus operators corresponding to one single qubit PCEs are 
+% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
+% % \begin{equation}
+% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
+% % \label{eq:kraus:PCE}
+% % \end{equation}
+% corresponding to the operation that leaves the component $\sigma_i$
+% invariant~\cite{nielsen_chuang_2011}.
+Inspection of the Kraus operators of two qubit PCEG lead to
+the ansatz that the Kraus operators for the generator of 
+$\mcG_{\vec \alpha}$ is 
+\begin{equation}
+\left\{\openone/\sqrt2, \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
+\label{eq:kraus:PCE}
+\end{equation}
+Indeed, the Kraus operators corresponding to one single qubit PCEs are 
+$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
+corresponding to the operation that leaves the component $\sigma_\alpha$
+invariant~\cite{nielsen_chuang_2011}.
+
+We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
+Notice that 
+\begin{equation}
+\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta. 
+\label{}
+\end{equation}
+% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
+Next, consider the action of a channel with Kraus representation 
+\eqref{eq:kraus:PCE} on an $N$ qubit system:
+\begin{align}
+\rho & \to 
+\frac{\openone}{\sqrt{2}} \rho\frac{\openone}{\sqrt{2}} 
+ + 
+\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
+\frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
+&=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
+&=\frac12 \rho
++ \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
+&=
+\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
+\end{align}
+However, $(1+\prod_k a^{i_k}_{j_k})/2$ is 0 or 1, proving the channel is a PCE.
+
+We still have to show that except for $i_1=\cdots=i_n=0$, half of the numbers 
+$(1+\prod_k a^{i_k}_{j_k})/2=1$, or equivalently, half of $\prod_k a^{i_k}_{j_k}=1$. 
+Consider a particular $l$ such that $i_l \ne 0$. This will make half of 
+the $\prod_k a^{i_k}_{j_k}$ 1 and half $-1$ (for fixed $l$). This also implies 
+that half of the correlations of the density matrix are erased and half preserved 
+so the channel is a PCEG.
+
+Notice also that different choices of sets $\{i_k \}$ lead to different channels. This
+can be seen noticing that if two channels were the same, this would imply that
+the matrix representation of the corresponding superoperator of 
+$\bigotimes_k \sigma_{i_k} \cdot \bigotimes_k \sigma_{i_k} $ would have to be
+the same which is clearly false.
+
+Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
+generator. This notation is based on the action on each individual qubit. (ii) Counting the
+number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
+from other arguments.
+
 % }}}

### 2021-08-26 documentos/kraus.tex
removed echo and die statements, lolz.

--- 2021-08-23 documentos/kraus.tex
@@
 \section{Kraus operators and decoherence} % {{{
+% \todo{Carlos hace una version}
+
+The Kraus operators of PCE channels provide an insight in the physical processes
+that yield such channels. In this section we investigate and construct such 
+operators and explore the corresponding processes.
+
+To study the Kraus operators corresponding to PCE, it is enough to study 
+the ones corresponding to generators, as all PCEs commute and thus to get the 
+Kraus operators of an arbitrary PCE, one can easily combine the Kraus
+operators of its generators.
+
+% The Kraus operators corresponding to one single qubit PCEs are 
+% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
+% % \begin{equation}
+% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
+% % \label{eq:kraus:PCE}
+% % \end{equation}
+% corresponding to the operation that leaves the component $\sigma_i$
+% invariant~\cite{nielsen_chuang_2011}.
+Inspection of the Kraus operators of two qubit PCEG lead to
+the ansatz that the Kraus operators for the generator of 
+$\mcG_{\vec \alpha}$ is 
+\begin{equation}
+\left\{\frac{\openone}{\sqrt2}, \frac{\sigma_{\vec \alpha}}{\sqrt2}\right\}. 
+% \left\{\openone/\sqrt2, \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
+\label{eq:kraus:PCE}
+\end{equation}
+Indeed, the Kraus operators corresponding to one single qubit PCEs are 
+$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
+corresponding to the operation that leaves the component $\sigma_\alpha$
+invariant~\cite{nielsen_chuang_2011}.
+
+We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
+Notice that 
+% \begin{equation}
+$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$,
+% \label{}
+% \end{equation}
+which in turn imply that 
+\begin{equation}
+\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
+=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
+\label{}
+\end{equation}
+\cpnote{This is the original $a$, not $H \otimes H$. See how to relate these
+two matrices, or define a new $a$ and $A$}
+% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
+Next, consider the action of a channel with Kraus representation 
+\eqref{eq:kraus:PCE} on an $N$ qubit system:
+\begin{equation}
+% \begin{align}
+\rho & \to 
+ \frac{\rho}{2} 
+ + \sum_{\vec \beta} \frac{\tau_{\vec \beta}}{2}
+\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha}  
+&= 
+  \sum_{\vec \beta} 
+   \tau_{\vec \beta}\frac{1+\san_{\vec \alpha \vec \beta}}{2}\sigma_{\vec \beta}. 
+% 
+% 
+% \frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
+% \frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
+% &=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
+% &=\frac12 \rho
+% + \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
+% &=
+% \sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
+\end{equation}
+However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
+by Kraus operators  \eref{eq:kraus:PCE} is a PCE. Moreover, One can notice that, 
+except for the first row, half of the matrix elements of each row is $+1$ and 
+half $-1$, which implies that the aforementioned channel is a PCEG.
+
+% We still have to show that except for $i_1=\cdots=i_n=0$, half of the numbers 
+% $(1+\prod_k a^{i_k}_{j_k})/2=1$, or equivalently, half of $\prod_k a^{i_k}_{j_k}=1$. 
+% Consider a particular $l$ such that $i_l \ne 0$. This will make half of 
+% the $\prod_k a^{i_k}_{j_k}$ 1 and half $-1$ (for fixed $l$). This also implies 
+% that half of the correlations of the density matrix are erased and half preserved 
+% so the channel is a PCEG.
+
+Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
+lead to different channels. This can be seen noticing that if two channels were
+the same, this would imply that the matrix representation of the corresponding
+superoperator of $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$
+would have to be the same which is clearly false. Since there are $4^n$ different 
+$\vec \alpha$, this implies that all PCEG (plus the identity map) are in one to 
+one correspondence.
+
+\cpnote{We might have spoken about the notation of the generators and here we 
+can add a sentence about it, but I will wait till JA writes his part.}
+% Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
+% generator. This notation is based on the action on each individual qubit. (ii) Counting the
+% number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
+% from other arguments.
 
@@
 \item Play with non PCEG PCEs
-\item Dependiendo de si sale algo bonito, podemos poner algun modelo en particular para todos los canales (sistema central + ambiente).
-Seria de buscar dilataciones sencillas y razonables por lo menos a los canales generadores.
+\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
+particular para todos los canales (sistema central + ambiente). Seria de buscar
+dilataciones sencillas y razonables por lo menos a los canales generadores.
+\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
 \end{itemize} 
-
 % }}}

### 2021-08-28 documentos/pce.tex
v1 de mi parte

@@
 % }}}
+
+The density matrix $\rho$ of a system of $n$ qubits can be written in Pauli matrices basis as 
+\begin{equation}\label{eq:N_qubits_rho}
+	\rho =\frac{1}{2^N} \sum_{j_1,\ldots,j_N=0}^3 \paulicomponents
+	\sigma_{j_1}\otimes \ldots \otimes \sigma_{j_N},
+	%r_{0,\ldots,0}=1,
+\end{equation}
+where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.
+We may and will refer to $\paulicomponents$ as the ``Pauli components'' of the 
+density matrix of a sistem of qubits.
+
+Let us now define a Pauli component erasing (PCE) operation. A linear operation 
+$\mcE$ that acts on a density matrix $\rho$ of a system of qubits is a PCE operation if 
+it transforms the Pauli components of $\rho$ as 
+\begin{equation}
+\begin{split}
+	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
+	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+\end{split}
+\end{equation}
+A PCE operation is a trace-preserving operation that leaves invariant or erases 
+the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
+habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
+todo claro y no hay problema en dejarlo así por el momento.}
+
+In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
+1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
+the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
+$j_1,\ldots,j_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
+\begin{center}
+\includegraphics[width=2cm]{2qubits_pce_example}
+\end{center}
+this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
+components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
+is not completely positive and therefore is not a quantum channel. In contrast, 
+\begin{center}
+\includegraphics[width=2cm]{2qubits_pceChannel_example01}
+\end{center}
+this other example of PCE operation that leaves invariant Pauli components 
+$r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
+is a quantum channel.
+
+\begin{figure} % {{{
+	\centering
+	\hfill \hfill
+	\includegraphics[height=2.5cm]	{tablero_1qubit}
+	\hfill
+	\includegraphics[height=2.5cm]{tablero_2qubits}
+	\hspace{1mm}
+	\includegraphics[height=2.7cm]{rho-3q}
+	\hfill \hfill
+	\caption{From left to right representations of identity map
+	(also PCE operations) of 1, 2 and 3 qubits, respectively.}
+	\label{fig:PCE_figs}
+\end{figure} % }}}
+
+\begin{figure} % {{{
+	\centering
+	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
+	\caption{1 qubit PCE channels. }
+	\label{fig:1qubit_PCEChannles}
+\end{figure} % }}}

### 2021-08-29 documentos/pce.tex
respuesta
bibliografia
avance

@@
 \subsection{Quantum channels}
+Quantum channels comprehend the most general linear operations that a quantum system undergo independently of its past~\cite{zimansbook,cirac}.
+To introduce their construction and properties, first let us define several objects.
+We will denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as $\hilbert_d$.
+The set of bounded operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$, the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset of the so called trace-class operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
+
+Their construction include basically three ingredients: linearity, trace preserving and complete positivity.The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$
 \subsection{Single qubit case} % {{{

### 2021-08-31 documentos/notas/francois.tex

\documentclass[11pt,dvipsnames]{article} % {{{

\usepackage{geometry}
\geometry{total={170mm,240mm}, left=20mm, top=20mm}

\usepackage[utf8]{inputenc}

\usepackage{physics} 
\usepackage{siunitx} 
\usepackage{enumerate} 
\usepackage{pgfplots}
\usepackage{physics}
% To add figures
\usepackage{graphicx}
% Path to figures
\graphicspath{ {../images/} }

\usepackage{pgfplotstable}
\usepackage{tikz,pgfplots}
\usepackage{amsmath} 
\usepackage{xcolor}
\usepackage{float}
\usepackage{amsfonts}
\newcommand{\pce}{PCE}
\usepackage{dsfont}
\usepackage{amssymb}
%\usepackage{bbold}

\newcommand{\fref}[1]{fig.~\ref{#1}}  
\newcommand{\tref}[1]{table~\ref{#1}}
\newcommand{\Fref}[1]{Fig.~\ref{#1}}  
\newcommand{\Tref}[1]{Table~\ref{#1}}
\newcommand\dsone{\mathds{1}}

\newcommand{\R}{\mathcal{R}}
\newcommand{\psii}{\psi_i}
\newcommand{\Pk}[1]{\ket{\psi_{#1} }}
\newcommand{\Pb}[1]{\bra{\psi_{#1} }}
\newcommand{\pk}{\ket{\psi}}
\newcommand{\M}{\mathcal{M}^{(N)}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\Ej}[1]{\E_{j_{#1}}}
\newcommand{\id}[1]{\qty(\1-\E_{j_{#1}})}
\newcommand{\Erho}{\mathcal{E}(\rho)}
\newcommand{\1}{\mathds{1}}
\newcommand{\ten}{\otimes}
\newcommand{\h}[1]{\colorbox{Yellow}{#1}}
\newcommand{\hi}{\mathcal{H}}
\newcommand{\txt}[1]{\text{#1}}
\newcommand{\here}{\h{\hspace{15cm}} }
\newcommand{\rhoi}{\dyad{\psii}{\psii}}
\newcommand{\ind}[2]{ {{}^{#1}_{#2}} }
\newcommand{\rc}[1]{r_{#1}}
\newcommand{\pauli}[2]{\sigma_{#1}\otimes\sigma_{#2}}
\newcommand{\Er}{\E_{\mathcal{R}} }
\newcommand{\PCE}[1]{\mathsf{PCE}_\mathsf{#1}}
\newcommand{\ot}{\otimes}
\usepackage[]{lineno}  \linenumbers
\setlength\linenumbersep{3pt}

\usepackage{fancybox}
\usepackage{colortbl}
\usepackage{amsbsy}
\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{ja}{aja}{\color{RedViolet}JA}
\FXRegisterAuthor{dd}{ddg}{\color{red}DD}
% }}}
\begin{document}
% Titulo y otros {{{
\title{Pauli component erasing operations} 
%Title should be concise and to the point  
\author{J. A. de León, C. Pineda, D. Dávalos, A. Fonseca}
\date{\today}  
\maketitle
\abstract{We study operations that act on the density matrix of $n$-qubits
systems and erase its projections onto tensor products of Pauli matrices. We
call this operations Pauli component erasing (PCE). We seek to characterize 
the subset of PCE operations that are quantum channels. We have solved 
analytically the complete positivity of a more general kind of operations.
Our numerical results suggest that PCE quantum channels have an algebraic structure.}

% }}}
% Intro 
\section*{Introduction} % {{{
The density matrix is an adequate tool to describe the kinematics 
of open quantum systems. An operator $\rho$ represents a quantum state and
is called a density operator if it is (1) of unitary trace, (2) Hermitian, and 
(3) positive. The density matrix of a system of $n$ qubits can be written as 
\begin{align}\label{eq:rho_nQubits_pauliBasis}
\rho =\frac{1}{2^n} \sum_{j_1,\ldots,j_n=0}^3r_{j_1,\ldots,j_n}
\sigma_{j_1}\otimes \ldots \otimes \sigma_{j_n},
\hspace{2cm} r_{0,\ldots,0}=1,
\end{align}
where $\sigma_{j_k}$ are the Pauli matrices (with $\sigma_0$ as $\1$)
and $r_{j_1,\ldots,j_n}$ the projections of $\rho$ onto each element of 
the basis of tensor products of Pauli matrices. We may refer to the 
$r_{j_1,\ldots,j_n}$ as the ``Pauli components'' of the density matrix 
of a system of qubits.  The component $r_{0,\ldots,0}$
must be equal to one in order for $\rho$ to satisfy $\Tr \rho =1$.

Let us now define what a Pauli component erasing (PCE) operation is. 
A linear operation $\mathcal{E}$ is a PCE operations if it 
acts on a density matrix of $n$ qubits and transforms its Pauli components as
\begin{align}\label{eq:PCE-definition}
r_{j_1,\ldots,j_n} \longmapsto \tau_{j_1,\ldots,j_n}r_{j_1,\ldots,j_n}
\hspace{1cm} \tau_{j_1,\ldots,j_n}=0,1,
\hspace{1cm} \tau_{0,\ldots,0}=1.
\end{align}
In simple words, a PCE operation leaves invariant or erases the Pauli 
components of a density matrix of $n$ qubits.
%\begin{align}
%  \rho = \frac{1}{2^n}\1 + \sum _{i=1}^{2^{2n}-1}\tau _i\sigma _i,
%	\label{rho}
%\end{align}
%where the $\sigma _i$s are tensor products of Pauli 
%matrices, which together with the identity, form a orthogonal basis in the space of
%$2^n\times 2^n$ matrices. Thus the $\tau_i$s are the projections of $\rho$ onto
%each element of this basis, using the Hilbert-Schmidt inner product.

In this work, we are interested in studying the subset of PCE operations
that are quantum channels. 
Let us discuss briefly the definition of a quantum channel.
A quantum channel is a linear operation that acts on a density matrix $\rho$
that is completely positive and preserves the trace of $\rho$. The complete
positivity is a condition that captures the non-locality of 
quantum mechanics. One standard definition is the following: an operation
$\mathcal{E}$ is completely positive if and only if $\mathcal{E}\otimes\1_k$
is a positive operator for every possible dimension $k$. In other words, 
$\mathcal{E}\otimes\1_k$ must be an operator that maps positive 
matrices onto positive matrices, including the entangled states between 
the system which $\mathcal{E}$ acts on and an arbitrary system 
which $\1_k$ acts on. In fact, the complete positivity of an operation 
$\mathcal{E}$ may be evaluated by checking that the maximally 
entangled pure state between the system and an identical copy is mapped 
by $\mathcal{E}\otimes\1$ onto a positive matrix, \textit{i.e.}
$\qty(\mathcal{E}\otimes\1)\qty[\dyad{\phi^+}{\phi^+}]\geq 0$, with 
$\dyad{\phi^+}{\phi^+}$ the maximally entangled pure state state.

We're interested in characterizing the quantum PCE channels.
For 1 qubit the picture of our problem is easy to understand given that 
the Pauli components are the components of a vector in the Bloch sphere,
the so-called Bloch vector. 
As an example, let us consider a map that erases any single
component of the Bloch vector. Geometrically, this map collapses 
the Bloch ball into a disk. This operation is not completely positive, and
therefore is not a quantum channel.  However, erasing two components yields 
a quantum channel.

So far, we have analytically solved the diagonalization for 
complete positivity of a more general class of operations than the PCE 
and have numerically found the all the PCE quantum channels up to 
4-qubit systems. We have made several observations from our results, but
we have not been able to prove them analytically and connect them 
all as a consequence of the mathematical characterization we desire
to find of the PCE quantum channels.
%
%So far, we have evaluated complete positivity numerically, we have obtained all 1 and
%2 \pce{} operations. Whereas for $3$ qubits systems we have numerically analyzed
%only maps that leave invariant 1, 2, 3, 4, and 64 Pauli components in $\rho$.
%Nonetheless, we have strong indications that only maps that leave invariant 8
%components are needed to analyze in order to find the complete set of 3-qubit
%PCE channels.
% }}}
\section*{Results} % {{{

\subsection*{Diagonalization of the Choi matrix}
Due to the fact that the Pauli matrices and the identity form a basis of the Hilber-Shmidt space, the state of a qubit may be written as
% 
\begin{equation}
 \hat{\rho}=\frac{1}{2}\sum_{j,k=0}^1r_{jk}\hat{v}_{jk},
\end{equation}
%
where $\hat{v}_{00}=\dsone$, $\hat{v}_{01}=\hat{\sigma}_x$, $\hat{v}_{10}=i\hat{\sigma}_y$ and $\hat{v}_{11}=\hat{\sigma}_z$.
% 
Rewriting $\hat{\rho}$ in ``vector" notation, we have
%
\begin{equation}
 \vec{\rho}=\frac{1}{2}\sum_{jk=0}^1r_{jk}\vec{v}_{jk},
\end{equation}
%
The action of a quantum operation $\hat{M}$ (in its matrix form), capable of modifying each one of the coefficients $r_{jk}$ independently may be written as
%
\begin{equation}
 \hat{M}\vec{\rho}=\frac{1}{2}\sum_{jk=0}^1\tau_{jk}r_{jk}\vec{v}_{jk}.
\end{equation}
%
In our particular case (PCE operations), $\tau_{jk}=\{0,1\}$.

In order to determine whether any specific operation, characterized by the set of coefficients $\{\tau_{jk}\}$ corresponds to a quantum channel, we must ensure that the eigenvalues associated to the Choi matrix are non-negative. For this, let write $\hat{M}$ in the vector Pauli basis
%
\begin{equation}
 \hat{M}=\sum_{jk=0}^1\tau_{jk}~\vec{v}_{jk}\vec{v}_{jk}^\intercal.
 \label{EQA1}
\end{equation}
%
On the other hand, it is easy to show that the elements of the computational and Pauli bases are related by $\vec{u}=\hat{T}\vec{v}$
\begin{equation}
\vec{u}=\begin{pmatrix}
\hat{u}_{00} \\ \hat{u}_{01} \\ \hat{u}_{10} \\ \hat{u}_{11}
\end{pmatrix}=\frac{1}{2}\begin{pmatrix}
1 & 0 & 0 & 1\\
0 & 1 & 1 & 0\\
0 & 1 & -1 & 0\\
1 & 0 & 0 & -1
\end{pmatrix} \begin{pmatrix}
\hat{v}_{00} \\ \hat{v}_{01} \\ \hat{v}_{10} \\ \hat{v}_{11}
\end{pmatrix},
\end{equation}
% 
where $\hat{u}_{jk}=\dyad{j}{k}$. The inverse relation reads $\vec{v}=\hat{S}\vec{u}$
\begin{equation}
\vec{v}=\begin{pmatrix}
\hat{v}_{00} \\ \hat{v}_{01} \\ \hat{v}_{10} \\ \hat{v}_{11}
\end{pmatrix}=\begin{pmatrix}
1 & 0 & 0 & 1\\
0 & 1 & 1 & 0\\
0 & 1 & -1 & 0\\
1 & 0 & 0 & -1
\end{pmatrix} \begin{pmatrix}
\hat{u}_{00} \\ \hat{u}_{01} \\ \hat{u}_{10} \\ \hat{u}_{11}
\end{pmatrix}.
\end{equation}
% 
Thus, for this ``indexing choice" of the elements of the bases, the transformation matrices satisfy $\hat{S}=2\hat{T}$. Then one can relate the bases elements in a compact form as
% 
\begin{equation}
 \vec{v}_{jk}=\sum_{mn=0}^1S_{mn}^{(jk)}\vec{u}_{mn},
\end{equation}
% 
by substituting this in Eq. \ref{EQA1} we get $\hat{M}$ in the computational basis
% 
\begin{align}
 \hat{M}=&\sum_{jk=0}^1\tau_{jk}~\left(\sum_{mn=0}^1S_{mn}^{(jk)}\vec{u}_{mn} \right) \left(\sum_{pq=0}^1S_{jk}^{(pq)}\vec{u}^\intercal_{pq} \right),\\
 =&\sum_{mnpq=0}^1\left(\sum_{jk=0}^1 S_{mn}^{(jk)}S_{jk}^{(pq)}  \tau_{jk} \right) \vec{u}_{mn}\vec{u}^\intercal_{pq}.\\
 &\sum_{mnpq=0}^1 M_{\substack{mn\\pq}} ~\vec{u}_{mn}\vec{u}^\intercal_{pq}.
\end{align}
% 
In order to obtain the Choi matrix $\hat{M}^c$, we must perform the reshuffling operation on $\hat{M}$, i.e. $M_{\substack{mn\\pq}} \to M_{\substack{mp\\nq}}$ \cite{bengtsson_zyczkowski_2017}. In this way, $\hat{M}^c$ holds

\begin{equation}
\hat{M}^c=\sum_{mnpq=0}^1\left(\sum_{jk=0}^1 S_{mp}^{(jk)}S_{jk}^{(nq)}  \tau_{jk} \right) \vec{u}_{mn}\vec{u}^\intercal_{pq}.
\end{equation}
%
Back to the Pauli basis, we have
%
\begin{equation}
 \hat{M}^c=\sum_{\mu\nu\alpha\beta=0}^1\left\{\sum_{jk=0}^1\left[\sum_{mnpq=0}^1S_{mp}^{(jk)}S_{jk}^{(nq)}T_{\mu\nu}^{(mn)}T_{pq}^{(\alpha\beta)}\right]\tau_{jk}\right\}\vec{v}_{\mu\nu}\vec{v}_{\alpha\beta}^\intercal.
\end{equation}
%
By taking into account the relation between the transformation matrices $T_{\mu\nu}^{(mn)}=\frac{1}{2}S_{\mu\nu}^{(mn)}$, $\hat{M}^c$ reads
%
\begin{equation}
 \hat{M}^c=\frac{1}{4}\sum_{\mu\nu\alpha\beta=0}^1\left\{\sum_{jk=0}^1\left[\sum_{mnpq=0}^1S_{mp}^{(jk)}S_{jk}^{(nq)}S_{\mu\nu}^{(mn)}S_{pq}^{(\alpha\beta)}\right]\tau_{jk}\right\}\vec{v}_{\mu\nu}\vec{v}_{\alpha\beta}^\intercal.
\end{equation}
%
By noticing that $S_{mn}^{(jk)}=(-1)^m\delta_{jm}\delta_{kn}+\delta_{j,m\oplus 1}\delta_{k,n\oplus 1}$, and after several steps it is possible to show that 
% 
\begin{equation}
\frac{1}{4}\sum_{jk=0}^1\left[\sum_{mnpq=0}^1S_{mp}^{(jk)}S_{jk}^{(nq)}S_{\mu\nu}^{(mn)}S_{pq}^{(\alpha\beta)}\right]\tau_{jk}=\frac{1}{2}\delta_{\nu\beta}\delta_{\mu\alpha}\sum_{jk=0}^1(-1)^{j\mu\oplus k\nu}\tau_{jk},
\label{EQAL2}
\end{equation}
% 
after substituting, the Choi matrix reduces to
%
\begin{align}
 \hat{M}^c=&\frac{1}{2}\sum_{\mu\nu\alpha\beta=0}^1\left\{\delta_{\nu\beta}\delta_{\mu\alpha}\sum_{jk=0}^1(-1)^{j\mu\oplus k\nu}\tau_{jk}\right\}\vec{v}_{\mu\nu}\vec{v}_{\alpha\beta}^\intercal,\\
 =&\frac{1}{2}\sum_{\mu\nu=0}^1\left\{\sum_{jk=0}^1(-1)^{j\mu\oplus k\nu}\tau_{jk}\right\}\vec{v}_{\mu\nu}\vec{v}_{\mu\nu}^\intercal.
\end{align}
%
As it can be seen, this is the diagonal form of the Choi matrix. Thus, its 4 eigenvalues may be written in a compact form as
%
\begin{equation}
\lambda_{\mu\nu}=\frac{1}{2}\sum_{jk=0}^1(-1)^{j\mu\oplus k\nu}\tau_{jk},
\end{equation}
%
where $\mu,\nu=\{0,1\}$. Note in addition that this is in agreement with results already known in literature.

By following the same steps we can obtain the generalization to the $N$-qubits case. First of all note that $\hat{M}$ may be written as
%
\begin{equation}
 \hat{M}=\sum_{\vec{k}\vec{l}}\tau_{\vec{k}\vec{l}}~\vec{v}_{\vec{k}\vec{l}}\vec{v}_{\vec{k}\vec{l}}^\intercal,
%  \label{EQA1}
\end{equation}
% 
where
% 
\begin{equation}
 \vec{v}_{\vec{k}\vec{l}}=\vec{v}_{k_1l_1}\otimes\dots\vec{v}_{k_Nl_N}=\bigotimes_{j=1}^N\vec{v}_{k_jl_j}.
%  \label{EQA1}
\end{equation}
% 
Let write $\hat{M}$ in the $N$-qubits computational basis
% 
\begin{align}
 \hat{M}=&\sum_{\vec{k}\vec{l}\vec{p}\vec{q}}\left\{\sum_{\vec{m}\vec{n}} \left[ \prod_{i=1}^N S_{k_il_i}^{(m_in_i)}S_{m_in_i}^{(p_iq_i)} \right] \tau_{\vec{m}\vec{n}} \right\} \bigotimes_{j=1}^N\vec{u}_{k_jl_j}\vec{u}_{p_jq_j}^\intercal,\\
 =&\sum_{\vec{k}\vec{l}\vec{p}\vec{q}} M_{\vec{k}\vec{l}\vec{p}\vec{q}} ~\bigotimes_{j=1}^N\vec{u}_{k_jl_j}\vec{u}_{p_jq_j}^\intercal.
\end{align}
% 
After reshuffling ($M_{\vec{k}\vec{l}\vec{p}\vec{q}}\to M_{\vec{k}\vec{p}\vec{l}\vec{q}}$) we can get the associated Choi matrix. Back to the Pauli basis, $\hat{M}^c$ holds
%
\begin{equation}
 \hat{M}^c=\frac{1}{4^N}\sum_{\vec{\mu}\vec{\nu}\vec{\alpha}\vec{\beta}}\left\{\sum_{\vec{m}\vec{n}}\left[\prod_{i=1}^N\left(\sum_{k_il_ip_iq_i=0}^1 S_{k_ip_i}^{(m_in_i)} S_{m_in_i}^{(l_iq_i)}S_{\mu_i\nu_i}^{(k_il_i)}S_{p_iq_i}^{(\alpha_i\beta_i)}\right)\right]\tau_{\vec{m}\vec{n}}\right\} \bigotimes_{j=1}^N\vec{v}_{\mu_j\nu_j}\vec{v}_{\alpha_j\beta_j}^\intercal.
\end{equation}
% 
Using the result in Eq. \ref{EQAL2} and after some steps it can be shown that
%
\begin{equation}
 \hat{M}^c=\sum_{\vec{\mu}\vec{\nu}}\left\{\frac{1}{2^N}\sum_{\vec{\alpha}\vec{\beta}}(-1)^{\vec{\mu}\cdot\vec{\alpha}\oplus \vec{\nu}\cdot\vec{\beta}}\tau_{\vec{\alpha}\vec{\beta}}\right\}\vec{v}_{\vec{\mu}\vec{\nu}}\vec{v}_{\vec{\mu}\vec{\nu}}^\intercal,
\end{equation}
% 
which is also the diagonal form of $\hat{M}^c$. In this way, the $4^N$ eigenvalues may be written compactly as
% 
\begin{equation}
 \lambda_{\vec{\mu}\vec{\nu}}=\frac{1}{2^N}\sum_{\vec{\alpha}\vec{\beta}}(-1)^{\vec{\mu}\cdot\vec{\alpha}\oplus \vec{\nu}\cdot\vec{\beta}}\tau_{\vec{\alpha}\vec{\beta}}.
\end{equation}
% 
From this we can evaluate whether the set of coefficients $\tau_{\vec{\alpha}\vec{\beta}}$ satisfy the condition to the specific operation be considered a quantum channel, i.e. $\lambda_{\vec{\mu}\vec{\nu}}\geq 0$, for all $\vec{\mu},\vec{\nu}$. Note moreover that the expression above may also be written as a tensor product of $4\times 4$ matrices $a$, as illustrated in the next subsection.

\subsection*{Complete positivity: analytical solution}
Let us discuss the role of the complete positivity condition of the 
PCE operations in our problem. We desire to find what are the 
characteristics that make a PCE operation a quantum channel.
In the way we defined a PCE operation in \eqref{eq:PCE-definition} it 
is a trace preserving operation. Therefore, the complete positivity is 
the only condition to be evaluated given a PCE operation.

We found an analytical solution to evaluate the complete positivity.
Recall that an operation $\mathcal{E}$ is completely positive if 
$\qty(\mathcal{E}\otimes\1)\qty[\dyad{\phi^+}{\phi^+}]\geq 0$,
where $\dyad{\phi^+}{\phi^+}$ is the maximally entangled pure 
state between the system and another one that is an identical copy.
We showed that the diagonalization of 
$\qty(\mathcal{E}\otimes\1)\qty[\dyad{\phi^+}{\phi^+}]\geq 0$,
with $\mathcal{E}$ an operation that acts on the Pauli components of
a density matrix of $n$ qubits as
\begin{align} \label{eq:PauliOperation}
r_{j_1,\ldots,j_n}\longmapsto \tau_{j_1,\ldots,j_n}r_{j_1,\ldots,j_n},
\hspace{1.5cm} \tau_{0,\ldots,0}=1,
\end{align}
yields the eigenvalues $\lambda_i$
\begin{align} \label{eq:eigv_Choi_Pauli_operation}
\vec{\lambda}=\frac{1}{2^n}\qty(\bigotimes^na)\vec{\tau},
\end{align}
where 
\begin{align}
a=\mqty(1&1&1&1\\1&1&-1&-1\\1&-1&1&-1\\1&-1&-1&1)
\end{align} 
and the components of $\vec{\tau}$ the same ones in 
\eqref{eq:PauliOperation}. It is very important to realize that 
\eqref{eq:eigv_Choi_Pauli_operation} yields the diagonalization
not exclusively of a PCE operation. The difference between 
the definition of a PCE operation in \eqref{eq:PCE-definition}
and \eqref{eq:PauliOperation} is the relaxation in the value of 
the $\tau_{j_1,\ldots,j_n}$ (exclusively 0 or 1 for a PCE operation).

\subsection*{PCE quantum channels}
In \fref{fig:pictorial-rep-rho} we introduce a pictorial representation 
for the identity map acting on a density matrix for systems 
of 1, 2 and 3 qubits,
respectively. It will be helpful to visualize the maps we are studying 
making use of this tool. We'll consider any little square or cube in blank
as a component erased in $\rho$ by the map. 
Red squares correspond to components of Bloch vectors of one-particle reduced density matrices,
blue squares to correlations between any pair of qubits, and
green squares to correlations between all qubits in the system for
the 3-qubits case.
In the following subsections we present the PCE channels for
1 and 2 qubits, and preliminary results for 3 qubits.
\begin{figure}[H] % {{{
	\centering
	\hfill \hfill
	\includegraphics[height=2.5cm]	{tablero-1q}
	\hfill
	\includegraphics[width=2.5cm]{tablero_2qubits}
	\hfill 
	\includegraphics[width=2.5cm]{rho-3q}
	\hfill \hfill
	\caption{From left to right the identity map acting on
  an arbitrary density matrix of 1, 2 and 3 qubits, respectively. 
	Red squares correspond to components of local Bloch vectors,
	blue squares to correlations between any pair of qubits and
	green squares to correlations between all qubits in the system, for
	the 3-qubits case. }
	\label{fig:pictorial-rep-rho}
\end{figure} % }}}
\subsection*{1 qubit} % {{{
In \fref{fig:1q-ccs} we present the PCE channels for 1 qubit.
The first and last patterns represent identity 
and the total depolarizing channel. 
Patterns in between represent operations that map the Bloch 
sphere to a line on the Cartesian axes, respectively.
These three channels are equivalent via permutation
of the components $r_i$ of the Bloch vector.
\begin{figure}[H]% {{{
	\centering
	\includegraphics[width=5cm]{1q-CCs.png}
	\caption{
1-qubit PCE channels. From left to right patterns represent  
the following channels: identity,
mapping of the Bloch sphere to $x$ axis, $y$ axis, $z$ axis, 
and completely depolarizing (channel that maps every state 
to the maximally mixed).}
	\label{fig:1q-ccs}
\end{figure} % }}}
% }}}
\subsection*{2 qubits} % {{{
2-qubits PCE channels have been classified in equivalence classes 
(as shown from \fref{fig:2q-c1} to \fref{fig:2q-c16}), such
that elements in a class are connected by
\begin{enumerate}
	\item Particle swaps: Qubits in the system can be interchanged. Therefore
	if a map is a PCE channel for a certain arrangement 
	of qubits, then
	there are equivalent PCE channels acting on the system for all possible
	arrangements of qubits. In the pattern-picture this can be
	interpreted as transpositions.
	\item Exchange of axes labels: These operations correspond to permutations of rows and/or columns and are generally are not CPTP maps. For instance the swap of rows (or columns) result in reflections of the Bloch sphere of individual particles. Aside from that, it is clear that the physics of the erasure are the same.
%	The state of an individual
%	qubit may be rotated in such a way that components of its local Bloch
%	vector are swapped via permutations\cpnote{De acuerdo a lo que he pensado, esa frase no es cierta. 
%        Me gustaría discutir.}. PCE channels are equivalent
%	to these permutations.
%	In the pattern-picture this
%	is interpreted as permutations of rows or columns 1, 2 and 3.
\end{enumerate}

\begin{figure}[H] % {{{
	\centering
  \includegraphics[height=1.2cm]{C16.png}
	\caption{C${}^{1}$}
	\label{fig:2q-c1}
\end{figure} % }}}

\begin{figure}[H] % {{{
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C12.png}
		\vspace{1.2cm}
		\caption{C${}_1^2$}
		\label{fig:equivalence_class_c12}
	\end{minipage}\hfill
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C22.png}
		\caption{C${}_2^2$}
		\label{fig:equivalence_class_22}
	\end{minipage}
\end{figure} % }}}

\begin{figure}[H] % {{{
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C14.png}
		\vspace{1.2cm}
		\caption{C${}_1^4$}
		\label{fig:equivalence_class_c14}
	\end{minipage}\hfill
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C24.png}
		\caption{C${}_2^4$}
		\label{fig:equivalence_class_c24}
	\end{minipage}\vfill
\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C34.png}
		\caption{C${}_3^4$}
		\label{fig:equivalence_class_c34}
	\end{minipage}\hfill
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C44.png}
		\vspace{2.5cm}
		\caption{C${}_4^4$}
		\label{fig:equivalence_class_c44}
	\end{minipage}
\end{figure} % }}}

\begin{figure}[H] % {{{
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C18.png}
		\vspace{1.2cm}
		\caption{C${}_1^8$}
		\label{fig:equivalence_class_18}
	\end{minipage}\hfill
	\begin{minipage}[c]{0.5\textwidth}
		\centering
	  \includegraphics[width=.9\textwidth]{C28.png}
		\caption{C${}_2^8$}
		\label{fig:equivalence_class_28}
	\end{minipage}
\end{figure} % }}}

\begin{figure}[H] % {{{
	\centering
  \includegraphics[height=1.2cm]{C0.png}
	\caption{C${}^{16}$}
	\label{fig:2q-c16}
\end{figure} % }}}

In general, our results exhibit the following features:
\begin{itemize}
\item (\textit{Power-of-2 rule})
Only a power-of-2 number of Pauli components in $\rho$ 
may be left invariant by a PCE channel. 
However, not only the number of Pauli components in $\rho$ 
to leave invariant determines complete positivity since
not all maps that leave $2^{k}$ Pauli components invariant in $\rho$
are quantum channels. For example, the pattern below corresponds 
to a map that is a potential element of C${}_2^4$ (\Fref{fig:equivalence_class_c24}).
Nevertheless, complete positivity is not satisfied 
and then the map is not a quantum channel. 
% \begin{figure}[H]
% 	\centering
% 	\includegraphics[height=2cm]{img/not-cc}
% \end{figure}
\begin{center}
	\includegraphics[height=2cm]{not-cc}
\end{center}

\item \textit{(Mirroring)}
The number of PCE quantum channels as a function of the number of Pauli 
components left invariant shows to be symmetric with respect to a
particular value. 
The number of PCE operations and quantum channels,
as a function of the number of Pauli components left invariant, 
for 2 qubits are shown in \tref{tab:qtm_channels}.

%The ratio PCE channels$:$PCE operations according to number of qubits 
%and number of Pauli components invariant are shown in 
%\fref{fig:CCs-by-components}.
%
%\begin{figure}[H]% {{{
%\centering	
%\footnotesize
%\begin{tabular}{c|ccccccccccc|c}
%% \bf{
%\textbf{qubits}  & \multicolumn{11}{c|}{PCE quantum channels${}:{}$PCE operations 
%($2^0,\ldots,2^{2n}$ Pauli components components invariant)} & total PCE \\
%\hline
%1 &&&&&$1:1$&$3:3$&$1:1$&&&&&5\\
%2 &&&&$1:1$&$15:15$&$35:455$&$15:6435$&$1:1$&&&&67\\
%3 &&&$1:1$&$63:63$&$651:39711$&?/$6\times 10^8$&
%$651:1\times 10^{14}$&$63:{9\times 10^{17}}$&$1:1$&&&?
%% }
%\end{tabular}
%\caption{First column shows the number of qubits in the system.  In the second
%column each position correspond to the number of components invariant ($2^0,
%2^1, \ldots, 2^{2n}$) and the numbers shown are the ratios of PCE channels
%and all possible maps according to the number of components invariant.  Finally, third column
%specifies the total number of PCE channels for a $n$-qubit system.}
%\label{fig:CCs-by-components}
%\end{figure} % }}}

\begin{table}[H]
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|cccccccccccccccc}
\cline{2-17}
\multicolumn{1}{l|}{}                               & \multicolumn{16}{c|}{\textbf{Number of Pauli components left invariant}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \\[.5ex]
\multicolumn{1}{l|}{}                               & \multicolumn{1}{c}{\textbf{1}} & \multicolumn{1}{c}{\textbf{2}} & \multicolumn{1}{c}{\textbf{3}} & \multicolumn{1}{c}{\textbf{4}} & \multicolumn{1}{c}{\textbf{5}} & \multicolumn{1}{c}{\textbf{6}} & \multicolumn{1}{c}{\textbf{7}} & \multicolumn{1}{c}{\textbf{8}} & \multicolumn{1}{c}{\textbf{9}} & \multicolumn{1}{c}{\textbf{10}} & \multicolumn{1}{c}{\textbf{11}} & \multicolumn{1}{c}{\textbf{12}} & \multicolumn{1}{c}{\textbf{13}} & \multicolumn{1}{c}{\textbf{14}} & \multicolumn{1}{c}{\textbf{15}} & \multicolumn{1}{c|}{\textbf{16}} \\ \cline{2-17} 
\multicolumn{1}{c|}{\textbf{\# of PCE operations}}   & 1                               & 15                              & 105                             & 455                             & 1365                            & 3003                            & 5005                            & 6435                            & 6435                            & 5005                             & 3003                             & 1365                             & 455                              & 105                              & 15                               & 1                                \\[.4ex]
\multicolumn{1}{c|}{\textbf{\# of PCE qtm channels}} & 1                               & 15                              & 0                               & 35                              & 0                               & 0                               & 0                               & 15                              & 0                               & 0                                & 0                                & 0                                & 0                                & 0                                & 0                                & 1                               
\end{tabular}%
}
\caption{Tabla}
\label{tab:qtm_channels}
\end{table}
Let us focus only on the quantum channels:
\begin{table}[H]
\centering
\resizebox{.42\textwidth}{!}{%
\begin{tabular}{l|ccccc}
\cline{2-6}
\multicolumn{1}{l|}{}                               & \multicolumn{5}{c|}{\textbf{Number of $\boldsymbol{r_{ij}}$ inv.}} \\[.5ex]
\multicolumn{1}{l|}{}                               & \multicolumn{1}{c}{\textbf{1}} & \multicolumn{1}{c}{\textbf{2}} &  \multicolumn{1}{c}{\textbf{4}} & \multicolumn{1}{c}{\textbf{8}} &  \multicolumn{1}{c|}{\textbf{16}} \\ \cline{2-6} 
\multicolumn{1}{c|}{\textbf{\# of PCE qtm channels}} & 1                               & 15                               & 35                          & 15                        & 1                               
\end{tabular}%
}
\end{table}
We denote $f(k)$ the number of PCE quantum channels as a function
of the number $k$ of Pauli components left invariant. The number $k$
must be a power of 2.
In the case of 2 qubits, $f(k)$ is symmetric with respect to $k=4$. 
Our numerical results show that $f(k)$ is symmetric with respect
to $k=2^n$, in general. When 
considering only a power-of-2 Pauli components invariant,  
\tref{tab:qtm_channels} shows that this symmetry 
is not a property of the PCE operations, but only of the quantum channels.

\item \textit{($1:1$ correspondence)} There might be a 
$1:1$ correspondence between PCE quantum channels
that leave $2^k$ and $2^{2n-k}$ Pauli components invariant. 
That is to say in the 2-qubits case, 
PCE channels in Figs. \ref{fig:equivalence_class_c12}
and \ref{fig:equivalence_class_28} correspond to one 
PCE channel in Figs. \ref{fig:equivalence_class_18} and
\ref{fig:equivalence_class_28}. In fact, we've deduced from 
our numerical results the correspondence between PCE channels 
that leave 2 and the half the total Pauli components. For 2 qubits,
given the set $\{j_1,j_2 \}$ of indices of the Pauli component $r_{j_1,j_2}$ left
invariant, other than $r_{0,0}$, of every member in figs.
\ref{fig:equivalence_class_18} and \ref{fig:equivalence_class_18} one 
can one can find a single partner in figs. \ref{fig:equivalence_class_18} and
\ref{fig:equivalence_class_28} via
\begin{align}
\Phi_{j_1,j_2}=\E_{j_1}\ot\E_{j_2}+\qty(\1-\E_{j_1})\ot\qty(\1-\E_{j_2}),
\end{align}
where $\E_{j_l}$ are the first four 1-qubit PCE channels in 
\fref{fig:1q-ccs}, the identity and the 3 PCE operations that 
map the Bloch sphere to a line on every Cartesian axis. In general, 
a PCE quantum channel that leaves invariant $r_{0,\ldots,0}$ and 
$r_{j_1,\ldots,j_n}$ has a single PCE partner that leaves invariant 
half of the total Pauli components of the form 
\begin{align}
\Phi_{j_1,\ldots,j_n}=\sum_{i=0}^{i\leq n/2}\sum_{j\in \mathcal{S}_{2i}^n}
\bigotimes_{j_i=1}^n\Omega_{j_i},
\end{align}
with $\mathcal{S}_{2i}^n$ the set of all subsets with $2i$ elements 
from $\{1,2,\ldots,n\}$ and
\begin{align}
\Omega_{j_i}= \left\{ \begin{array}{rc}
             \E_{j_i}, & j_i \notin j \\
             \1 -\E_{j_i}, & j_i \in j.
             \end{array}
   \right.
\end{align}
We elaborate the 3-qubits and 4-qubits case. For 3 qubits, 
every PCE quantum channel that leaves invariant $r_{0,0,0}$ and 
$r_{j_1,j_2,j_3}$ has a PCE partner that leaves 32 Pauli components 
that can be written in the form
\begin{align}
\Phi_{j_1,j_2,j_3}=& \sum_{i=0}^{i\leq 3/2}
\sum_{j\in \mathcal{S}_{2i}^3}
\bigotimes_{j_i=1}^3\Omega{j_i} \nonumber \\
=&\ \Ej{1}\ot\Ej{2}\ot\Ej{3} + \id{1}\ot\id{2}\ot\Ej{3} \\
&+ \id{1}\ot\Ej{2}\ot\id{3} + \Ej{1}\ot\id{2}\ot\id{3}. \nonumber
\end{align}
For 4 qubits, every PCE quantum channel that leaves invariant $r_{0,0,0,0}$ 
and  $r_{j_1,j_2,j_3,j_4}$ has a PCE partner that leaves 128 Pauli components 
that can be written in the form
\begin{align}
\Phi_{j_1,j_2,j_3,j_4}=& \sum_{i=0}^{i\leq 2}
\sum_{j\in \mathcal{S}_{2i}^4}
\bigotimes_{j_i=1}^4\Omega{j_i} \nonumber \\
=&\ \Ej{1}\ot\Ej{2}\ot\Ej{3}\ot\Ej{4} + 
\qty(\1-\Ej{1})\ot\qty(\1-\Ej{2})\ot\Ej{3}\ot\Ej{4} \nonumber \\
&+ \qty(\1-\Ej{1})\ot\Ej{2}\ot\qty(\1-\Ej{3})\ot\Ej{4}
+ \qty(\1-\Ej{1})\ot\Ej{2}\ot\Ej{3}\ot\qty(\1-\Ej{4}) \\
&+ \Ej{1}\ot\qty(\1-\Ej{2})\ot\qty(\1-\Ej{3})\ot\Ej{4}
+ \Ej{1}\ot\qty(\1-\Ej{2})\ot\Ej{3}\ot\qty(\1-\Ej{4}) \nonumber \\
&+ \Ej{1}\ot\Ej{2}\ot\qty(\1-\Ej{3})\ot\qty(\1-\Ej{4}) \nonumber \\
&+ \id{1}\ot\id{2}\ot\id{3}\ot\id{4}. \nonumber
\end{align}

\item There exists a set of PCE generators and every other PCE 
quantum channel can be written as concatenation of the generators.
The identity plus the PCE channels that leave invariant half the total 
components constitute the set of generators. For example, 
the 2-qubits generators are

\begin{figure}[H]
  \centering
  \includegraphics[width=.75\textwidth]{2Q-fundamentals}
  \caption{Generators of 2 qubits.}
  \label{fig:2qubits-generators}
\end{figure}
and concatenation with the patterns is understood as the intersection
of black squares in the patterns of the generators. For example:

\hfill
\begin{tabular}{m{0.8cm} m{.1cm} m{0.8cm} m{.05cm} m{0.8cm}}
\includegraphics[height=1.1cm]{E2}  
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E5} 
& $=$
& \includegraphics[height=1.1cm]{E2E5} 
\end{tabular} \hspace{1.3cm}

\hfill
\begin{tabular}{m{0.8cm} m{.1cm} m{0.8cm} m{.1cm} m{0.8cm} m{.1cm} m{0.8cm}}
\includegraphics[height=1.1cm]{E4}
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E2}  
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E5} 
& $=$
& \includegraphics[height=1.1cm]{E4E2E5} 
\end{tabular} \hspace{1.3cm}

\hfill
\begin{tabular}{m{0.8cm} m{.1cm} m{0.8cm} m{.1cm} m{0.8cm} m{.1cm} m{0.8cm} m{.1cm} m{0.8cm}}
\includegraphics[height=1.1cm]{E12}
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E4}
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E2}  
& $\bigcirc$ 
& \includegraphics[height=1.1cm]{E5} 
& $=$
& \includegraphics[height=1.1cm]{E12E4E2E5} 
\end{tabular} \hspace{1.3cm}

This shows the idea and that is possible to construct from the generators
in \Fref{fig:2qubits-generators} 
all PCE channels in Figs. from \ref{fig:2q-c1} to \ref{fig:equivalence_class_c44}
\end{itemize}

\section*{Appendix}
\textit{\textbf{Note:}} This section contains
\begin{enumerate}
\item Observations on empirical rules con construct a PCE quantum channel
for 2 and 3 qubits.
\item Comparison with other kind of Pauli operations studied by Ruskai.
\end{enumerate}
The appendix could be skipped without loss of continuity of 
the current observations on our results in the rest of this document.

\begin{itemize}
\item Empirical observations of results for 2 qubits 
led us to some rules that 
patterns showed from \fref{fig:2q-c1} to \fref{fig:2q-c16} obey:
\begin{enumerate}
\item If a component with indices $ij$ is left invariant, then two options are
allowed: \textit{a)} both components with indices $i0$ and $0j$ are left
invariant too, or \textit{b)} both components with indices $i0$ and $0j$ are
erased.
Let us take a look at the next example. 
\begin{center}
\includegraphics[width=2cm]{ex-2q2c-empiricalRule}
\end{center}
% \hfill \hfill
% \newline
The component with indices 21 in the pattern is left invariant,
then the only options allowed are: \textit{a)} components with indices 01 and
20 are erased, as in this pattern above, or \textit{b)} components 
with indices 01 and 20 are left invariant too, 
as in the following pattern 
\begin{center}
% \newline
% \hfill
\includegraphics[width=2cm]{ex-2q4c-empiricalRule},
% \hfill \hfill 
% \newline
\end{center}
which is in fact another PCE channel. This rule can be derived using the complete positive condition over the following pattern:
\begin{equation}
\begin{array}{|c|c|c|c|}
\hline
1 & a_1 & 0 & 0 \\ 
\hline
0 & 0 & 0 & 0 \\ 
\hline
a_2 & b & 0 & 0 \\ 
\hline
0 & 0 & 0 & 0\\
\hline
\end{array}
\end{equation}
% \janote{Fin.}

\item Considering only components in the correlation matrix (blue squares): if a component
with indices $ij$ is left invariant and the previous rule is obeyed, then,
in the correlation matrix, remaining components on row $i$ and column $j$ are
erased, and the rest of the components are left invariant by a PCE channel. 
Let's go back to the last pattern in the previous example. This rule 
ensures that components in the correlation matrix outside of row 2 and 
column 1 may be left invariant by a PCE channel, i.e.
\begin{center}
\includegraphics[width=2cm]{ex-2q8c-empiricalRule},
\end{center}
which is another PCE channel.
\end{enumerate}	
Actually, this two simple rules allow us to relate
different equivalence classes. In the previous example we were able to connect 
an element of C${}_2^2$ to one of C${}_3^4$, to another one of
C${}_2^8$.

\item The action of a PCE channel on every subsystem must be another
PCE channel. 
This can be seen from the patterns in \fref{fig:2q-c1} to \fref{fig:2q-c16}.
Recall that red squares represent components of local Bloch vectors 
and blue squares represent correlations shared between qubits. 
Then, it may be noted in the first column and first row of every
pattern there is a 1-qubit PCE quantum channel of the form of \fref{fig:1q-ccs}.
% \janote{\h{Fin}}
\end{itemize}
% }}}
\subsection*{3 qubits} % {{{

Recall that for 3 qubits system we have numerically analyzed only maps that
leave invariant 1, 2, 3, 4, and 64 components in $\rho$. Therefore, results
presented in this section are preliminary. Maps that are PCE channels follow the same
features of 2-qubits system. Not all 3-qubits PCE channels 
will be shown as in
the previous section, but only one element of every equivalence class found.
Elements in equivalence classes are connected via particle swaps and
permutation of individual components.

\subsubsection*{1-invariant-component maps} % {{{
The only map that leaves invariant 1 component in $\rho$ is the completely
depolarizing channel, and it is trivially a PCE channel.
\begin{figure}[H]
	\includegraphics[height=4cm]{3q-1c}
	\caption{Completely depolarizing channel for 3 qubits.}
	\label{fig:QC-3q-1c}
\end{figure}
% }}}
\subsubsection*{2-invariant-components maps}% {{{
All 63 maps that leave invariant 2 components in $\rho$ are 
PCE channels. It's important to mention that in the 2-qubits case all 
2-invariant-components maps are PCE channels, too. We can distinguish
3 equivalence classes: quantum channels that leave invariant
\begin{enumerate}
	\item any component of a local Bloch vector,
	\item any correlation between any pair of qubits,
	\item any correlation between all qubits in the system.
\end{enumerate}
\begin{figure}[H]
	\centering
	\hfill \hfill
	\includegraphics[height=4cm]{3q-2c-1}
	\hfill
	\includegraphics[height=4cm]{3q-2c-2}
	\hfill
	\includegraphics[height=4cm]{3q-2c-3}
	\hfill \hfill
	\caption{3-qubits 2-components-invariant PCE channels. 
	One element of each of the 3 equivalence classes 
	(from left to right): leaves invariant one component of any local
	Bloch vector, one correlation between any pair or qubits, and 
	one correlation between all qubits in the system.}
	\label{fig:QC-3q-2c}
\end{figure}

% }}}
\subsubsection*{3-invariants-component maps} % {{{
No PCE channels were found in the set of all maps that leave
3 components invariant in $\rho$.
% }}}
\subsubsection*{4-invariant-components maps} % {{{
There are 39,711 maps that leave invariant 4 components in $\rho$, 651
are PCE channels and may be classified in 10 equivalence classes.
One arbitrary element in each class is shown in \fref{fig:QC-3q-4c}. 
We understand how to infer 5 out of the 10 equivalence classes 
from 1 and 2-qubits PCE channels, as it will be discussed.

On top of \fref{fig:QC-3q-4c} the first 4 elements
(from left to right) correspond to PCE channels that are separable
in a 1 or 2 qutbis PCE channel acting on any subsystem 
and a completely depolarzing channel acting on the rest of the system.
The fifth and last element on top of the figure may be understood invoking    
an extension for 3 qubits of one of the empirical rules presented 
for 2 qubits. The extensions of those rules will be discussed at
the end of this section. 
PCE channels belonging to equivalence classes of bottom elements in 
the figure are such that we still cannot infer them with our 
previous results.

\begin{figure}[H]
	\centering
	\hfill \hfill
	\includegraphics[height=3cm]{3q-4c-si-1}
	\hfill
	\includegraphics[height=3cm]{3q-4c-si-2}
	\hfill
	\includegraphics[height=3cm]{3q-4c-si-3}
	\hfill
	\includegraphics[height=3cm]{3q-4c-si-4}
	\hfill
	\includegraphics[height=3cm]{3q-4c-si-5}
	\hfill
	\vfill
	\hfill
	\includegraphics[height=3cm]{3q-4c-no-1}
	\hfill
	\includegraphics[height=3cm]{3q-4c-no-2}
	\hfill
	\includegraphics[height=3cm]{3q-4c-no-3}
	\hfill
	\includegraphics[height=3cm]{3q-4c-no-4}
	\hfill
	\includegraphics[height=3cm]{3q-4c-no-5}
	\hfill \hfill
	\caption{3-qubits 4-components-invariant PCE channels. 
	One element of every of the 10 equivalence classes.}
	\label{fig:QC-3q-4c}
\end{figure}
% }}}
% Rules for 3 qubits {{{
The empirical rules already presented for 2 qubits can be 
formulated for 3 qubits as follows:
\begin{itemize}
	\item A component with indices $ijk$ (all different from zero) is
	left invariant by a PCE channel if and only if 
	one of the cases is followed:
	\begin{enumerate}
		\item Components $ij0$, $0jk$, $i0k$, $i00$, $0j0$, and
		$00k$ are erased.
		\item Components $i00$ and $0jk$ are also left invariant.
		\item Components $0j0$ and $i0k$ are also left invariant.
		\item Components $00k$ and $ij0$ are also left invariant.
		\item Components $ij0$, $0jk$, $i0k$, $i00$, $0j0$, and
		$00k$ are also left invariant.
	\end{enumerate}
	It can be noted that the element in the right upper corner of 
	\fref{fig:QC-3q-4c} is understood as one of the cases 2-4 of this item.
	\item Considering only components that correspond to correlations between
	3 qubits in the system (green cubes): if a little cube 
	with indices $ijk$ (all different from zero) is left invariant 
	and any of the cases of the previous rule is obeyed, 
	then the remaining components on columns $i$, $j$, and $k$ are
	erased and the rest of components in the correlation tensor 
	are left invariant by a PCE channel. 
\end{itemize}
Let us consider an example to make use of both empirical rules. If we 
begin with an element of the same equivalence class as the second
element on top of \fref{fig:QC-3q-4c}, then we make use of one of 
the cases 2-4 of the first empirical rule for 3 qubits and get the PCE channel below.
\begin{center}
	\includegraphics[width=4cm]{3q-8c-je}.
\end{center}
Finally, we make use of the second rule to left invariant only components
corresponding to correlations between all qubits in the system (green cubes)
and get another PCE channel (pattern below).
\begin{center}
	\includegraphics[width=4cm]{3q-8c}
\end{center}
What we have done is start with a PCE channel that leaves 4 invariant
components, make our way trough a 8-invariant-components PCE channel and 
finally arrive at a 16-invariant-components PCE channel.

In principle, the rainbow hypothesis ensures the correspondence between  
the channels we have found and channels that leave invariant 16, 32 and 64
components. The empirical rules for 3 qubits provide one way to \textit{travel}
from a $k$-components-invariant quantum channel to a
$(2n-k)$-components-invariant channel.
It is sufficient to found one element in an 
equivalence class because the rest of the elements are found 
by particle swaps and permutation of individual components.
% }}}
% }}}
% }}}
\section*{Are this channels a subset of Pauli diagonal channels constant on axes?} % {{{
We explored if PCE channels are contained within the set of Pauli diagonal
channels constant on axes \cite{nathanson2007pauli}. Let us call them
$\mathcal{R}$. For 2 qubits, we concluded that Kraus rank $4$ 
PCE channels are the only candidates to
be in $\mathcal{R}$, in fact we are convinced that all of them are in, but are
still working in the proof. 
To see this let us analyze the action of maps in $\R$ 
on arbitrary density matrices
\begin{align}
	\rho \longmapsto \frac{1}{d}\qty[\1 + \sum _{J=1}^{d+1} \lambda_J
	\sum _{j=1}^{d-1}	v_{Jj}W_J^j],
	\label{eq:ruskai-action}
\end{align}
where $\lambda_J$ are the eigenvalues of a given map, and operators $W_J$ are unitaries defined as
\begin{equation}
	W_J = \sum _{k=1}^{d}\omega^k \dyad{\psi_k^J}{\psi_k^J}, 
\end{equation}
where sets of vectors $\qty{\ket{\psi_k^J}}_k$ with $J=1,\dots, 1+d$ are mutually unbiased basis (MUB) over $\mathbb{C}^d$, and $\omega = e^{2\pi i/d}$. There are $d^2-1$ unitaries generated with the powers of the $W_J$s, i.e.
$\qty{W_J^m}_{m=1,\ldots,d,J=1,\ldots,d+1}$. They, together the identity matrix, form a basis in the space of $d\times d$ matrices.
%\fxnote{Por fas
%corrige la argumentacion a partir de la modificacion a la ecuacion}

%\fxnote{JA, ojo
%que los $W_J$ generan un grupo ciclico, mas no generadores de MUBs, uno
%construye los $W_J$ usando MUBs!. Por fas mejor mete la definicion de $W_J$.}

To examine if PCE channels are contained in $\R$ let us consider
the rank of both maps and discuss how only a subset of PCE channels
could be in $\R$. Our results show that PCE channels have 
a power-of-2 rank. On the other hand, from \eqref{eq:ruskai-action} it
can be seen that the rank of a map in $\R$ is 1 plus 
the number of all $\lambda_J$ different from zero. Notice that eigenvalues $\lambda_J$ have multiplicity $d-1$, for each $J$. Consequently, the allowed matrix ranks 
of maps in $\R$ are $1 + k(d-1)$, where $k = 1,2,\ldots,d+1$. It follows
that a \textit{necessary} condition for maps in $\R$ and PCE channels to have the 
same rank is that
\begin{align}
	\hspace{2cm}2^j&=1 + k(2^{2n}-1),	\hspace{1.5cm} j=0,1,\ldots,2n
\end{align}
is always true for some $k\in \mathbb{Z^+}$, and $n$ the number 
of qubits. If we take $n=2$ and $j=3$ 
(2 qubits, $2^3$ components invariant)
\begin{align}
	k&= \frac{2^3-1}{2^{2\qty(2)}-1}=\frac{7}{15}.
\end{align}
Therefore the rank of a PCE channel may not be the same of any map in $\R$.
Then, there are PCE channels that cannot be in $\R$, like
all 8-components-invariant PCE channels, as shown in the previous example.

%% }}}
%\section*{To-do} % {{{
%In order to fully understand our results and generalize this kind of maps 
%for $n$ qubits we propose the following:
%\begin{enumerate}
%\item Investigate the Kraus operator representation of this quantum channels.
%\item Investigate the Schmidt spectrum of the Choi matrix.
%\item Investigate the Jamiolkowski isomorphism to find an equivalence between
%CP and the empirical rules listed previously.
%\item Use our current results to propose an efficient way to do numerical
%analysis to find 3-qubit quantum channels that leave 8 components invariant.
%\end{enumerate}
%% }}}
\bibliographystyle{unsrt}
\bibliography{references}
\vfill

\end{document}

### 2021-08-31 documentos/pce.tex

@@
 
-Their construction include basically three ingredients: linearity, trace preserving and complete positivity.The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$
+The construction of quantum channels includes basically three ingredients: linearity, trace preserving and complete positivity.
+The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$.
+The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ with $\rho \in \mcS(\hilbert)$.
 \subsection{Single qubit case} % {{{

### 2021-09-01 documentos/math.tex
Avance N=1

@@
 pasamos cosas al apendice. Caso general}
+
+This part is devoted to derive the set of conditions a Pauli map need to satisfy to fulfill the CP condition i.e.
+all the eigenvalues of the Choi matrix associated to the channel must be non-negative.
+First we obtain the set of inequalities for a single qubit Pauli channel and then we extend the results for the general case of $N$ qubits.
+
+\subsubsection{Single qubit Pauli channels}
+
+\afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
+
+By writing the elements of the density matrix in vector form $\varrho=\left(\varrho_0,\varrho_1,\varrho_2,\varrho_3\right)^{\intercal}$, the action of a Pauli map on $\varrho$ for a single qubit may be written as $\varrho \to \varrho'=\hat \mcE \varrho$, where $\hat \mcE$ is the matrix representation of the map.
+Moreover it can be shown that in the Pauli basis $(\sigma_0,\sigma_1,i\sigma_2,\sigma_3)$, $\hat \mcE$ reduces simply to $\mathrm{diag}\left(\tau_0,\tau_1,\tau_2,\tau_3\right)$.
+
+Let reorganize the elements of the Pauli basis as $(\sigma_0,\sigma_3,\sigma_1,i\sigma_2)$, in this way it is possible to write the matrix representation of the map as $\hat \mcE = \tau_{03} \oplus \tau_{12}$, where $\tau_{jk}=\mathrm{diag}\left(\tau_j,\tau_k\right)$ and the symbol $``\oplus "$ represents a direct sum of matrices.
+The advantage of this ordering is manifested when the matrix $\hat \mcE$ is transformed to the computational basis $(u_{00},u_{11},u_{01},u_{10})$, $\hat \mcE_c$:
+% 
+\begin{align}
+ \hat \mcE_c =& \left(H\oplus H\right)\hat \mcE \left(H\oplus H\right)^{\intercal}\\
+ =& \left(H\oplus H\right) \left(\tau_{03} \oplus \tau_{12}\right)\left(H\oplus H\right)^{\intercal}\\
+ =& H\tau_{03}H \oplus H\tau_{12}H\\
+ =&\begin{pmatrix}
+        \tau_0+\tau_3 & \tau_0-\tau_3\\
+        \tau_0-\tau_3 & \tau_0+\tau_3\\
+        &&\tau_0+\tau_3 & \tau_0-\tau_3\\
+        &&\tau_0-\tau_3 & \tau_0+\tau_3\\        
+    \end{pmatrix},
+ \label{Eq_E_P_C}
+\end{align}
+% 
+where $H$ is the Haddamard matrix
+% 
+\begin{equation}
+ H=\begin{pmatrix}
+        1 & 1\\
+        1 & -1\\
+    \end{pmatrix}.
+ \label{Hadd_Mat}
+\end{equation}
+% 
+After applying the reshuffling operation on $\hat \mcE_c$, we get the associated Choi matrix (or sometimes called dynamical matrix) of the map $D$, it reads
+% 
+\begin{equation}
+ D=\begin{pmatrix}
+        \tau_0+\tau_3 & \tau_1+\tau_2\\
+        \tau_1+\tau_2 & \tau_0+\tau_3\\
+        &&\tau_0-\tau_3 & \tau_1-\tau_2\\
+        &&\tau_1-\tau_2 & \tau_0-\tau_3\\        
+    \end{pmatrix}.
+ \label{Eq_D_P}
+\end{equation}
+% 
+Back to the Pauli basis, the Choi matrix holds
+\begin{align}
+ D_p =& \left(\frac{1}{2}H\oplus H\right)\hat D \left(\frac{1}{2}H\oplus H\right)^{\intercal}\\
+ =&\frac{1}{4}\left(H\oplus H\right)\hat D \left(H\oplus H\right)^{\intercal}\\
+=&\begin{pmatrix}
+        \lambda_0\\
+        &\lambda_1\\
+        &&\lambda_2\\
+        &&&\lambda_3\\
+    \end{pmatrix}.
+%   =&\begin{pmatrix}
+%         \tau_0+\tau_3+\tau_1+\tau_2\\
+%         &\tau_0-\tau_3+\tau_1-\tau_2\\
+%         &&\tau_0+\tau_3-\tau_1-\tau_2\\
+%         &&&\tau_0-\tau_3-\tau_1+\tau_2\\        
+%     \end{pmatrix}.
+ \label{Eq_D_C_P}
+\end{align}
+% 
+In other words, the Pauli basis diagonalizes the Choi matrix associated to any Pauli map, with eigenvalues related to the map coefficients $\tau$ as
+% 
+\begin{equation}
+\begin{pmatrix}
+        \lambda_0\\
+        \lambda_1\\
+        \lambda_2\\
+        \lambda_3\\   
+    \end{pmatrix}
+ =\frac{1}{2}\begin{pmatrix}
+        1&1&1&1\\
+        1&-1&1&-1\\
+        1&1&-1&-1\\
+        1&-1&-1&1\\
+    \end{pmatrix}
+    \begin{pmatrix}
+        \tau_0\\
+        \tau_3\\
+        \tau_1\\
+        \tau_2\\   
+    \end{pmatrix},
+ \label{Eigen1}
+\end{equation}
+% 
+or in a compact form
+% 
+\begin{equation}
+ \lambda = \frac{1}{2}H\otimes H \tau.
+\end{equation}
+% 
+Now we proceed to generalize this result for the case $N$ qubits case.
+
+\subsubsection{$N$ qubits}
+
+Coming soon...
+
+\subsection{Parte de Francois}
 

### 2021-09-01 documentos/pce.tex
agrego generadores linblad, me falta la derivacion, mas detalels

@@
 The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$.
-The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ with $\rho \in \mcS(\hilbert)$.
+The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$.
+The complete positivity condition is needed to preserve positive semidefiniteness and handle the non-local character of quantum theory.
+This is, with positivity of the map $\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with $\Delta\geq 0$.
+In the other hand, complete positvity of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state between the system and an ancilla with Hilbert space $\hilbert_k$.
+Therefore, complete positivity ensures that every positive semidefinite operator of any extension of the system (where the quantum channel is now a local operation) is mapped into positive semidefinite operators, trace preserving is automatically fulfilled for all extensions if $\mcE$ is.
+Thus, any density matrix of a system where $\mcE$ acts locally, is send to a valid density matrix, this is the substance of complete positivity.
+
+Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
+
+A remarkable consequence of positivity 
 \subsection{Single qubit case} % {{{
-% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
-% mapas proyectivos, hay mapas proyectivos no unitales}
 \todo{David escribe una primera version y luego Carlos itera}
+Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
+\sa g
+\begin{equation}
+\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
+\end{equation}
+then they are defined as follows
+\begin{equation}
+r_i \mapsto \tau_i
+\end{equation}
+
+with
+\begin{equation}
+\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
+\label{eq:1qubit_semigroup}
+\end{equation}
+We will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
+\begin{equation}
+\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
+\label{eq:Nqubit_semigroup}
+\end{equation}
+
+\begin{align}
+U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
+U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
+\label{eq:1qubit_stinespring}
+\end{align}
+similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
+\begin{align}
+U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
+U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
+\label{eq:Nqubit_stinespring}
+\end{align}
+
 \begin{itemize}

### 2021-09-01 documentos/pce.tex
muevo ecuaciones de dilatacion y semigrupo

@@
 Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
-\sa g
 \begin{equation}
@@
 \begin{equation}
-r_i \mapsto \tau_i
+r_i \mapsto \tau_i r_i
 \end{equation}
+where $\tau_k$ is either $1$ or $0$. A direct evaluation of the
 
@@
 \end{equation}
-We will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
-\begin{equation}
-\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
-\label{eq:Nqubit_semigroup}
-\end{equation}
+We will show later that this can be trivially generalized to the $N$ qubit case.
 
@@
 \end{align}
-similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case. \ddnote{[Esto se mueve a la seccion correspondiente:]}
-\begin{align}
-U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
-U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
-\label{eq:Nqubit_stinespring}
-\end{align}
+similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case.
 
@@
 \end{equation}
+\ddnote{hay un typo en esta ecuacion}
 A PCE operation is a trace-preserving operation that leaves invariant or erases 

### 2021-09-01 documentos/pce.tex
los indices son las alpha

@@
 \begin{equation}\label{eq:N_qubits_rho}
-	\rho =\frac{1}{2^N} \sum_{j_1,\ldots,j_N=0}^3 \paulicomponents
-	\sigma_{j_1}\otimes \ldots \otimes \sigma_{j_N},
+	\rho =\frac{1}{2^N} \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
+	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
 	%r_{0,\ldots,0}=1,
@@
 \end{equation}
-\ddnote{hay un typo en esta ecuacion}
+%\ddnote{hay un typo en esta ecuacion}
 A PCE operation is a trace-preserving operation that leaves invariant or erases 
@@
 the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
-$j_1,\ldots,j_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
+$\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
 \begin{center}

### 2021-09-02 documentos/pce.tex
Fixed unnecessary bug.

@@
 \subsection{Single qubit case} % {{{
+\label{sec:single:qubit}
 \todo{David escribe una primera version y luego Carlos itera}
@@
 \begin{itemize}
-\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
-\item Give some two qubit examples to illustrate non-trivial points with examples
-(isualizacion y ejemplos)
-\todo{Jose Alfredo escribe}
 \item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
@@
 \end{itemize}
-% }}}
-% \begin{itemize}
-% \item Son positivas todas las matrices de densidad que resultan de aplicar un
-% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
-% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
-% sucede para $n$ qubits.}
-% \end{itemize}
-% }}}
 
-The density matrix $\rho$ of a system of $n$ qubits can be written in Pauli matrices basis as 
+The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
+matrices basis as 
 \begin{equation}\label{eq:N_qubits_rho}
-	\rho =\frac{1}{2^N} \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
-	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+	\rho =\frac{1}{2^N} 
+            \sum_\valpha r_\valpha \sigma_\valpha,
+% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
+% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
 	%r_{0,\ldots,0}=1,
 \end{equation}
-where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.
-We may and will refer to $\paulicomponents$ as the ``Pauli components'' of the 
-density matrix of a sistem of qubits.
+where $\vec \alpha$ denotes a multi index with $N$ components, 
+$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
+\sigma_{\alpha_N}$ is the tensor product of Pauli matrices and 
+$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
+of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
+\alpha} \}$. In the sum, each of the $N$ components of $\valpha$, i.e.
+$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
+Notice that $\sigma_{\vec 0} = \openone$ and since both $\tr \rho=1$ and 
+$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, $r_{\vec 0}=1$. 
+We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
+matrix of a system of qubits.
 
-Let us now define a Pauli component erasing (PCE) operation. A linear operation 
-$\mcE$ that acts on a density matrix $\rho$ of a system of qubits is a PCE operation if 
-it transforms the Pauli components of $\rho$ as 
+%  $r_{\vec \alpha} =  $
+% where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.
+
+Consider the linear operations that simply attenuate the Pauli components of 
+a multiqubit system:
 \begin{equation}
-\begin{split}
-	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
-	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
-\end{split}
+	\paulicomponents \mapsto \taus \paulicomponents.
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
 \end{equation}
+These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
+rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
+funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
+To preserve the trace of the density matrix, we require that 
+$\tau_{\vec 0}=1$. 
+\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
+A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
+%  A linear operation 
+% $\mcE$ 
+that either preserves or completely erases the Pauli components of a
+density matrix. That is, 
+% it transforms its Pauli components as 
+\begin{equation}
+% \begin{split}
+% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+	\paulicomponents \mapsto \taus \paulicomponents,\quad 
+	\taus = 0,1.
+% \end{split}
+\end{equation}
+It is worth noticing that not all PCE maps are quantum operations. For single 
+qubits, if just one of the $\taus=0$, the complete positivity condition 
+is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
+in this article to determine with $\taus$ lead to a valid quantum map.
+
 %\ddnote{hay un typo en esta ecuacion}
-A PCE operation is a trace-preserving operation that leaves invariant or erases 
-the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
-habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
-todo claro y no hay problema en dejarlo así por el momento.}
+% A PCE operation is a trace-preserving operation that leaves invariant or erases 
+% the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
+% habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
+% todo claro y no hay problema en dejarlo así por el momento.}
+\cpnote{Aca voy}
 
@@
 \end{figure} % }}}
+
+% }}}

### 2021-09-02 documentos/pce.tex
se lee más fácil, creo

@@
             \sum_\valpha r_\valpha \sigma_\valpha,
+            \quad r_{\vec0}=1,
 % 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
@@
 \end{equation}
-where $\vec \alpha$ denotes a multi index with $N$ components, 
+where $\vec \alpha$ denotes a multi index $\qty(\alpha_0,\ldots,\alpha_N)$ and
+each $\alpha_i=0,1,2,3$, 
 $\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
-\sigma_{\alpha_N}$ is the tensor product of Pauli matrices and 
+\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
 $r_{\vec \alpha}$ is the coefficient corresponding to the expansion
 of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
-\alpha} \}$. In the sum, each of the $N$ components of $\valpha$, i.e.
-$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
-Notice that $\sigma_{\vec 0} = \openone$ and since both $\tr \rho=1$ and 
-$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, $r_{\vec 0}=1$. 
+\alpha} \}$. %In the sum each of the $N$ components of $\valpha$, i.e.
+%$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
+Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
+$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
 We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
@@
 funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
-To preserve the trace of the density matrix, we require that 
+For the linear operation to preserve the trace of the density matrix, we require that 
 $\tau_{\vec 0}=1$. 

### 2021-09-02 documentos/pce.tex
unh

@@
-\section{PCE Maps} % {{{
-\subsection{Quantum channels}
-Quantum channels comprehend the most general linear operations that a quantum system undergo independently of its past~\cite{zimansbook,cirac}.
-To introduce their construction and properties, first let us define several objects.
-We will denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as $\hilbert_d$.
-The set of bounded operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$, the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset of the so called trace-class operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
+\section{PCE Maps} 
+\subsection{Quantum channels} % {{{
+Quantum channels comprehend the most general linear operations that a quantum
+system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
+their construction and properties, first let us define several objects. We will
+denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
+$\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will
+be written as $\mcB(\hilbert)$, the subset of density matrices as
+$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
+operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
+here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
 
-The construction of quantum channels includes basically three ingredients: linearity, trace preserving and complete positivity.
-The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$.
-The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$.
-The complete positivity condition is needed to preserve positive semidefiniteness and handle the non-local character of quantum theory.
-This is, with positivity of the map $\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with $\Delta\geq 0$.
-In the other hand, complete positvity of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state between the system and an ancilla with Hilbert space $\hilbert_k$.
-Therefore, complete positivity ensures that every positive semidefinite operator of any extension of the system (where the quantum channel is now a local operation) is mapped into positive semidefinite operators, trace preserving is automatically fulfilled for all extensions if $\mcE$ is.
-Thus, any density matrix of a system where $\mcE$ acts locally, is send to a valid density matrix, this is the substance of complete positivity.
+The construction of quantum channels includes basically three ingredients:
+linearity, trace preserving and complete positivity. The first one is needed to
+send convex combinations of density matrices into the convex combination of the
+evolution of such density matrices, this is, let $\mcE$ such linear operation,
+thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
+trace preserving is required for the process $\mcE$ to be deterministic, this
+is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
+happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
+positivity condition is needed to preserve positive semidefiniteness and handle
+the non-local character of quantum theory. This is, with positivity of the map
+$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
+$\Delta\geq 0$. In the other hand, complete positvity of $\mcE$ reads $\id_k
+\otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state
+between the system and an ancilla with Hilbert space $\hilbert_k$. Therefore,
+complete positivity ensures that every positive semidefinite operator of any
+extension of the system (where the quantum channel is now a local operation) is
+mapped into positive semidefinite operators, trace preserving is automatically
+fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
+where $\mcE$ acts locally, is send to a valid density matrix, this is the
+substance of complete positivity.
 
-Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
+Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring
+dilation]}
 
 A remarkable consequence of positivity
+
+% }}}
 \subsection{Single qubit case} % {{{
@@
             \sum_\valpha r_\valpha \sigma_\valpha,
-            \quad r_{\vec0}=1,
+%             \quad r_{\vec0}=1,
 % 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
@@
 \end{equation}
-where $\vec \alpha$ denotes a multi index $\qty(\alpha_0,\ldots,\alpha_N)$ and
-each $\alpha_i=0,1,2,3$, 
+where $\vec \alpha$ denotes a vector index $\qty(\alpha_0,\ldots,\alpha_N)$,
 $\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
@@
 of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
-\alpha} \}$. %In the sum each of the $N$ components of $\valpha$, i.e.
-%$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
+\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
+$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
+cuando hayamos escrito lo de un qubit}. 
 Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
@@
 funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
-For the linear operation to preserve the trace of the density matrix, we require that 
+For the operation to preserve the trace of the density matrix, we require that 
 $\tau_{\vec 0}=1$. 

### 2021-09-02 documentos/pce.tex
push porque tengo que hacer
Things went wrong...

@@
 \subsection{Pauli component erasing maps} % {{{
+
 \begin{itemize}
+\item Quizá en este punto hablar un poco de decoherencia de $N$ qubits, como 
+solo para motivar los PCEs y decir que se va a ligar al final.
+
 \item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
@@
 \end{equation}
-where $\vec \alpha$ denotes a vector index $\qty(\alpha_0,\ldots,\alpha_N)$,
+where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
 $\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
@@
 	\includegraphics[height=2.5cm]{tablero_2qubits}
-	\hspace{1mm}
-	\includegraphics[height=2.7cm]{rho-3q}
-	\hfill \hfill
+%	\hspace{1mm}
+%	\includegraphics[height=2.7cm]{rho-3q}
+	\hfill \hfill \hfill
 	\caption{From left to right representations of identity map
-	(also PCE operations) of 1, 2 and 3 qubits, respectively.}
+	(also PCE operations) of 1 and 2 qubits, respectively.}
 	\label{fig:PCE_figs}

### 2021-09-03 documentos/pce.tex
microavance

@@
 fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
-where $\mcE$ acts locally, is send to a valid density matrix, this is the
+where $\mcE$ acts locally, is sent to a valid density matrix, this is the
 substance of complete positivity.
 
-Quantum channels \ddnote{[Choi representation, Kraus operators and Stinespring
+Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}.
+Given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.
+
+  \ddnote{[Choi representation, Kraus operators and Stinespring
 dilation]}

### 2021-09-09 documentos/notas/wce.tex

\documentclass[11pt,dvipsnames]{article} % {{{

\usepackage{geometry}
\geometry{total={170mm,240mm}, left=20mm, top=20mm}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{enumerate} 
\usepackage{pgfplots}
\usepackage{float}

% To add graphics
\usepackage{graphicx}
% Path to figures
\graphicspath{ {../images/} }

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\author{José Alfredo de León}
\title{Numerical progress on Weyl component erasing operations}
\begin{document}
\maketitle
\section{3-level system}
The results for Weyl component erasing (WCE) quantum channels claimed by Alejo
have been reproduced by an independent party (me). Since Alejo has been 
using two indices for the components $\tau_{\mu\nu}$ to characterize a WCE
we can represent the 3-level systems WCE quantum channels as in Fig. 
\ref{fig:weylCE_1particle_d3}.
\begin{figure}[h]
	\centering
	\includegraphics[width=10cm]{weylCE_1particle_d3}
	\caption{Representation of a 3-level system WCE quantum channels.}
	\label{fig:weylCE_1particle_d3}
\end{figure}

\section{4-level system}
In Fig. \ref{fig:weylCE_1particle_d4} I show the numerical results for 
4-level system WCE quantum channels. It is worth noting that the 
so-called \textit{rainbow rule} is weirdly followed: 1 3 6 3 1 number of 
quantum channels that leave invariant 1 2 4 8 16 ``Weyl components'' 
of the density matrix.
\begin{figure}[h]
	\centering
	\includegraphics[width=10cm]{weylCE_1particle_d4}
	\caption{Representation of a 4-level system WCE quantum channels.}
	\label{fig:weylCE_1particle_d4}
\end{figure}

\end{document}

### 2021-09-09 documentos/notas/wce.tex
Hacía falta un canal de d=3 y 3 componentes invariantes

@@
 have been reproduced by an independent party (me). Since Alejo has been 
-using two indices for the components $\tau_{\mu\nu}$ to characterize a WCE
-we can represent the 3-level systems WCE quantum channels as in Fig. 
-\ref{fig:weylCE_1particle_d3}.
+using two indices for the components $\tau_{\mu\nu}$ to characterize a WCE operation
+we can represent the 3-level system WCE quantum channels as in Fig. 
+\ref{fig:weylCE_1particle_d3}. Note the existence of the additional quantum 
+channel that leaves invariant $\alpha_{00}$, $\alpha_{1,2}$ and $\alpha_{2,1}$
+(fifth figure from left to right). Therefore, the so-called \textit{rainbow rule}
+follows as 1 4 1 WCE channels that leave invariant 1 3 9 ``Weyl'' components
+of the density matrix. 
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=10cm]{weylCE_1particle_d3}
+	\includegraphics[width=12cm]{weylCE_1particle_d3}
 	\caption{Representation of a 3-level system WCE quantum channels.}
@@
 4-level system WCE quantum channels. It is worth noting that the 
-so-called \textit{rainbow rule} is weirdly followed: 1 3 6 3 1 number of 
+\textit{rainbow rule} is weirdly followed: 1 3 7 3 1 number of 
 quantum channels that leave invariant 1 2 4 8 16 ``Weyl components'' 

### 2021-09-13 documentos/pce.tex
etc

@@
 Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}.
-Given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.
+This is, given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.
 
@@
 
-A remarkable consequence of positivity
+It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=1/2^N\tr\left( \sigma_i \mcE[\sigma_j]
+ \right)$
 

### 2021-09-20 documentos/pce.tex
pequeñez
They came from... Behind

@@
 
+Quantum channels have the well-known \textit{Kraus representation} (or operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho K^\dagger{}_i$ in fact, a linear operation is completely positive if and only if it has a Kraus representation [cite Kraus book]
+
   \ddnote{[Choi representation, Kraus operators and Stinespring
@@
 
-It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=1/2^N\tr\left( \sigma_i \mcE[\sigma_j]
+It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j]
  \right)$
@@
 
+A graphical representation for 1, 2 and 3 qubits may be introduced, being the
+two qubit case what has proved more useful. Consider a $N$ dimensional 
+grid, with $4^N$ places. Each place has $N$ integer coordinates, ranging
+from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill with black 
+the corresponding position \cpnote{No me pone feliz esta redaccion}
+if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
+empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
+for two qubits, we exemplify them in \fref{fig:two:qubit:examples}. Notice
+than in both cases we drop the label $\alpha$ for simplicity, as it will 
+remain unchanged throughout this text.
+
+\begin{figure} % {{{
+\begin{center}
+\begin{tikzpicture}[x=0.5cm, y=0.5cm]
+% Coordenadas  
+\node at (-0.6,0.5) {(a)} ;
+\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
+\begin{scope}[shift={(0,-1)}]
+\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
+\end{scope}
+\begin{scope}[shift={(0,-2)}]
+\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
+\end{scope}
+\begin{scope}[shift={(0,-3)}]
+\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
+\end{scope}
+% Identity
+\begin{scope}[shift={(4,0)}]
+\node at (-0.6,0.5) {(b)} ;
+\fill[black] (0,0) rectangle (1,1);
+\draw (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope}
+% Dephasing
+\begin{scope}[shift={(8,0)}]
+\node at (-0.6,0.5) {(c)} ;
+\fill[black] (0,0) rectangle (1,1);
+\draw (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope}
+% Total depolarization
+\begin{scope}[shift={(12,0)}]
+\node at (-0.6,0.5) {(d)} ;
+\fill[black] (0,0) rectangle (1,1);
+\draw (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope}
+\end{tikzpicture}
+\end{center}
+	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the positions of the single 
+qubit diagrams, so that each square corresponds to a single 
+$\tau_{\alpha}$, $\alpha=0,\cdots,3$. The diagrams in 
+(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
+total depolarization, respectively. In (e) we show a map that erases the two components
+$r_1$ and $r_2$ and thus does not correspond to a quantum operation.}
+	\label{fig:one:qubit:examples}
+\end{figure} % }}}
+
+\begin{figure} % {{{
+	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the
+positions of two qubit diagrams. The diagrams in 
+(b) corresponds to a quantum channel that \cpnote{ver con JA que ejemplo ponemos}, 
+and in (c) a diagram of a map that is not a quantum channel is presented.}
+	\label{fig:two:qubit:examples}
+\end{figure} % }}}
+
 In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 

### 2021-09-20 documentos/pce.tex
WIPTF

@@
 \begin{center}
-\begin{tikzpicture}[x=0.5cm, y=0.5cm]
+
+\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
+\def\unitsep{2cm }
 % Coordenadas  
@@
 % Identity
-\begin{scope}[shift={(4,0)}]
+\begin{scope}[shift={(2*1,0)}]
+% \begin{scope}[shift={(\unitstep*2,0)}]
 \node at (-0.6,0.5) {(b)} ;
@@
 \end{scope}
-\end{tikzpicture}
+\begin{scope}[shift={(16,0)}]
+\node at (-0.6,0.5) {(e)} ;
+\fill[black] (0,0) rectangle (1,1);
+\draw (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope}
+\end{tikzpicture} % }}}
 \end{center}
@@
 qubit diagrams, so that each square corresponds to a single 
-$\tau_{\alpha}$, $\alpha=0,\cdots,3$. The diagrams in 
+$\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
 (b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
-total depolarization, respectively. In (e) we show a map that erases the two components
-$r_1$ and $r_2$ and thus does not correspond to a quantum operation.}
+total depolarization, respectively. In (e) we show a map that only erases the component
+$r_1$ and thus does not correspond to a quantum operation.}
 	\label{fig:one:qubit:examples}
@@
 
-In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
-1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
-the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
-$\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
-\begin{center}
-\includegraphics[width=2cm]{2qubits_pce_example}
-\end{center}
-this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
-components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
-is not completely positive and therefore is not a quantum channel. In contrast, 
-\begin{center}
-\includegraphics[width=2cm]{2qubits_pceChannel_example01}
-\end{center}
-this other example of PCE operation that leaves invariant Pauli components 
-$r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
-is a quantum channel.
-
-\begin{figure} % {{{
-	\centering
-	\hfill \hfill
-	\includegraphics[height=2.5cm]	{tablero_1qubit}
-	\hfill
-	\includegraphics[height=2.5cm]{tablero_2qubits}
-%	\hspace{1mm}
-%	\includegraphics[height=2.7cm]{rho-3q}
-	\hfill \hfill \hfill
-	\caption{From left to right representations of identity map
-	(also PCE operations) of 1 and 2 qubits, respectively.}
-	\label{fig:PCE_figs}
-\end{figure} % }}}
-
-\begin{figure} % {{{
-	\centering
-	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
-	\caption{1 qubit PCE channels. }
-	\label{fig:1qubit_PCEChannles}
-\end{figure} % }}}
+% In \Fref{fig:PCE_figs} we introduce a pictorial representation of PCE operations of 
+% 1, 2 and 3 qubits. Every position in the column, board or cube is associated with 
+% the subindices of $\taus$ of a PCE operation. If a little square or cube  in position
+% $\alpha_1,\ldots,\alpha_N$ is black, then $\taus=1$, if it is white, then $\taus=0$. For example,
+% \begin{center}
+% \includegraphics[width=2cm]{2qubits_pce_example}
+% \end{center}
+% this represents a PCE operation of 2 qubits that leaves invariant the Pauli 
+% components $r_{0,0}$, $r_{0,2}$, $r_{1,0}$, $r_{2,2}$, $r_{3,2}$. This operation
+% is not completely positive and therefore is not a quantum channel. In contrast, 
+% \begin{center}
+% \includegraphics[width=2cm]{2qubits_pceChannel_example01}
+% \end{center}
+% this other example of PCE operation that leaves invariant Pauli components 
+% $r_{0,0}$, $r_{1,2}$, $r_{2,1}$, $r_{3,3}$ satisfies complete positivity and 
+% is a quantum channel. 
+% 
+% \begin{figure} % {{{
+% 	\centering
+% 	\hfill \hfill
+% 	\includegraphics[height=2.5cm]	{tablero_1qubit}
+% 	\hfill
+% 	\includegraphics[height=2.5cm]{tablero_2qubits}
+% %	\hspace{1mm}
+% %	\includegraphics[height=2.7cm]{rho-3q}
+% 	\hfill \hfill \hfill
+% 	\caption{From left to right representations of identity map
+% 	(also PCE operations) of 1 and 2 qubits, respectively.}
+% 	\label{fig:PCE_figs}
+% \end{figure} % }}}
+% 
+% \begin{figure} % {{{
+% 	\centering
+% 	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
+% 	\caption{1 qubit PCE channels. }
+% 	\label{fig:1qubit_PCEChannles}
+% \end{figure} % }}}
 

### 2021-09-20 documentos/pce.tex
pep8 fixer

@@
 \begin{center}
-
 \begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
-\def\unitsep{2cm }
-% Coordenadas  
+\pgfmathsetmacro{\unitstep}{3.5}
+% Coordenadas   {{{
 \node at (-0.6,0.5) {(a)} ;
@@
 \draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
-\end{scope}
-% Identity
-\begin{scope}[shift={(2*1,0)}]
+\end{scope} % }}}
+\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
 % \begin{scope}[shift={(\unitstep*2,0)}]
@@
 \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope}
-% Dephasing
-\begin{scope}[shift={(8,0)}]
+\end{scope} % }}}
+\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
 \node at (-0.6,0.5) {(c)} ;
@@
 \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope}
-% Total depolarization
-\begin{scope}[shift={(12,0)}]
+\end{scope} % }}}
+\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
 \node at (-0.6,0.5) {(d)} ;
@@
 \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope}
-\begin{scope}[shift={(16,0)}]
+\end{scope} % }}}
+\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
 \node at (-0.6,0.5) {(e)} ;
@@
 \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope}
+\end{scope} % }}}
 \end{tikzpicture} % }}}
@@
 \begin{figure} % {{{
+\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
+\pgfmathsetmacro{\unitstep}{5.8}
+\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
+\node at (-0.6,0.5) {(a)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{\y,\x}$}};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\end{scope} % }}}
+\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
+\node at (-0.6,0.5) {(b)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
+\node at (-0.6,0.5) {(c)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\end{tikzpicture} % }}}
 	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the
 positions of two qubit diagrams. The diagrams in 
-(b) corresponds to a quantum channel that \cpnote{ver con JA que ejemplo ponemos}, 
+(b) corresponds to a quantum channel that results from 
+the tensor product of bit flip channels in each qubit,
+\cpnote{ver con JA que ejemplo ponemos}, 
 and in (c) a diagram of a map that is not a quantum channel is presented.}

### 2021-09-20 documentos/pce.tex
it's friday

@@
 % todo claro y no hay problema en dejarlo así por el momento.}
-\cpnote{Aca voy}
+% \cpnote{Aca voy}
 
@@
 \end{center}
-	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the positions of the single 
+	\caption{In (a) we introduce the positions of the single 
 qubit diagrams, so that each square corresponds to a single 
@@
 \end{tikzpicture} % }}}
-	\caption{\cpnote{Aca meter la figura, JA} In (a) we introduce the
+	\caption{In (a) we introduce the
 positions of two qubit diagrams. The diagrams in 
-(b) corresponds to a quantum channel that results from 
-the tensor product of bit flip channels in each qubit,
-\cpnote{ver con JA que ejemplo ponemos}, 
+(b) corresponds to a quantum channel that results from the tensor product of
+bit flip channels in each qubit [see \fref{fig:one:qubit:examples}(c)],
 and in (c) a diagram of a map that is not a quantum channel is presented.}

### 2021-09-20 documentos/pce.tex
Comentarios III.C

@@
 % it transforms its Pauli components as 
-\begin{equation}
+\begin{equation} \label{eq:PCE_definition}
 % \begin{split}
@@
 is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
-in this article to determine with $\taus$ lead to a valid quantum map.
+in this article to determine with $\taus$ lead to a valid quantum map \janote{está 
+incompleto este enunciado, no?}.
 
@@
 
-A graphical representation for 1, 2 and 3 qubits may be introduced, being the
-two qubit case what has proved more useful. Consider a $N$ dimensional 
-grid, with $4^N$ places. Each place has $N$ integer coordinates, ranging
+A graphical representation for 1, 2 and 3 qubits \janote{PCE maps} may be introduced, being the
+two qubits case what has proved \janote{\sout{more}} \janote{to be the most} useful. Consider a $N$ dimensional 
+\janote{cartesian} grid, with $4^N$ places. \janote{We label} Each place has $N$ integer coordinates, ranging
 from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
@@
 than in both cases we drop the label $\alpha$ for simplicity, as it will 
-remain unchanged throughout this text.
+remain unchanged throughout this text \janote{No entiendo qué estás diciendo
+aquí}.
 

### 2021-09-21 documentos/pce.tex
Don’t mess with Voodoo
less french words

--- 2021-09-20 documentos/pce.tex
@@
 \begin{itemize}
-\item Quizá en este punto hablar un poco de decoherencia de $N$ qubits, como 
-solo para motivar los PCEs y decir que se va a ligar al final.
-
 \item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
@@
 is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
-in this article to determine with $\taus$ lead to a valid quantum map.
+in this article to determine which $\taus$ lead to a valid quantum map.
 
@@
 
-A graphical representation for 1, 2 and 3 qubits may be introduced, being the
-two qubit case what has proved more useful. Consider a $N$ dimensional 
-grid, with $4^N$ places. Each place has $N$ integer coordinates, ranging
+A graphical representation for PCE maps may be introduced, being the
+two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
+Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
 from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
@@
 empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
-for two qubits, we exemplify them in \fref{fig:two:qubit:examples}. Notice
-than in both cases we drop the label $\alpha$ for simplicity, as it will 
-remain unchanged throughout this text.
+for two qubits, we exemplify them in \fref{fig:two:qubit:examples}. 
+% Notice
+% than in both cases we drop the label $\alpha$ for simplicity, as it will 
+% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
+% aquí}.
 

### 2021-09-21 documentos/pce.tex
etc

--- 2021-09-20 documentos/pce.tex
@@
 
+ These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.
+They form a tetrahedron in the space of eigenvalues
+
 with
@@
 $r_{\vec \alpha}$ is the coefficient corresponding to the expansion
-of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
-\alpha} \}$. In the sum each of the $N$ components of $\valpha$, i.e.
+of the density matrix in the complete orthonormal basis $\left\{ \frac{1}{2^{N/2}}\sigma_{\vec
+\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
 $\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
@@
 \end{equation}
-These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
+These operations are diagonal in the basis $1/2^{N/2} \left\{\sigma_{\vec \alpha} \right\}_{\vec \alpha}$
+ \cpnote{davalos, dale aca un pequeño 
 rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 

### 2021-09-21 documentos/pce.tex
etc

@@
 $r_{\vec \alpha}$ is the coefficient corresponding to the expansion
-of the density matrix in the complete orthonormal basis $\left\{ \frac{1}{2^{N/2}}\sigma_{\vec
+of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
 \alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
@@
 \end{equation}
-These operations are diagonal in the basis $1/2^{N/2} \left\{\sigma_{\vec \alpha} \right\}_{\vec \alpha}$
+These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$.
+Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
  \cpnote{davalos, dale aca un pequeño 
 rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
-funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
+funciona para eso y quizá también seran relevantes para la parte de decoherencia} \ddnote{De momento no he encontrado alguna reference, para qubits si, pero para los generales no, estoy checando de nuevo el paper de Ruskai para entender que tanto se solapan, a ver si puedo decir algo}.
 For the operation to preserve the trace of the density matrix, we require that 

### 2021-09-23 documentos/math.tex
Choi_2

--- 2021-08-24 documentos/math.tex
@@
 pasamos cosas al apendice. Caso general}
+
+This part is devoted to derive the set of conditions a Pauli map need to satisfy to fulfill the CP condition i.e.
+all the eigenvalues of the Choi matrix associated to the channel must be non-negative.
+First we obtain the set of inequalities for a single qubit Pauli channel and then we extend the results for the general case of $N$ qubits.
+
+\subsubsection{Single qubit Pauli channels}
+
+\afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
+\janote{Qué tal $\vec\rho\quad$?}
+
+We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\mu}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
+By writing the density matrix in vector form $\ket{\rho}=\sum_{\mu=0}^{3} \alpha_{\mu} \ket{\sigma_{\mu}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
+% 
+\begin{equation}
+\hat{\mathcal{E}} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \dyad{\sigma_{\mu}},
+% \label{Map_Pauli}
+\end{equation}
+%
+where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\mu}}}{{\sigma_{\mu'}}} = \tr \left(\sigma_{\mu}^{\dagger} \sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$.
+After some steps it is possible to show that the associated Choi matrix reads
+% 
+\begin{equation}
+ \mathcal{D} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \sigma_{\mu} \otimes \sigma_{\mu}^*.
+%  \label{Choi_1}
+\end{equation}
+% 
+Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\mu}=\sqrt{\frac{\tau_{\mu}}{2}}\sigma_{\mu}$.
+For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
+% 
+\begin{equation}
+ \lambda_{\nu} = \frac{1}{2}\sum_{\mu=0}^3H_{\nu\mu}^{(4)}\tau_{\mu},
+\end{equation}
+%
+or
+% 
+\begin{equation}
+ \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
+\end{equation}
+% 
+where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
+% 
+\begin{equation}
+ H^{(2)}=\begin{pmatrix}
+        1 & 1\\
+        1 & -1\\
+    \end{pmatrix}.
+ \label{Hadd_Mat}
+\end{equation}
+% 
+(Proofs in an appendix using binary indices XD)
+
+% By writing the elements of the density matrix in vector form $\varrho=\left(\varrho_0,\varrho_1,\varrho_2,\varrho_3\right)^{\intercal}$, the action of a Pauli map on $\varrho$ for a single qubit may be written as $\varrho \to \varrho'=\hat \mcE \varrho$, where $\hat \mcE$ is the matrix representation of the map.
+Moreover it can be shown that in the Pauli basis $(\sigma_0,\sigma_1,i\sigma_2,\sigma_3)$, $\hat \mcE$ reduces simply to $\mathrm{diag}\left(\tau_0,\tau_1,\tau_2,\tau_3\right)$.
+% 
+% Let reorganize the elements of the Pauli basis as $(\sigma_0,\sigma_3,\sigma_1,i\sigma_2)$, in this way it is possible to write the matrix representation of the map as $\hat \mcE = \tau_{03} \oplus \tau_{12}$, where $\tau_{jk}=\mathrm{diag}\left(\tau_j,\tau_k\right)$ and the symbol $``\oplus "$ represents a direct sum of matrices.
+The advantage of this ordering is manifested when the matrix $\hat \mcE$ is transformed to the computational basis $(u_{00},u_{11},u_{01},u_{10})$, $\hat \mcE_c$:
+% % 
+% \begin{align}
+%  \hat \mcE_c =& \left(H\oplus H\right)\hat \mcE \left(H\oplus H\right)^{\intercal}\\
+%  =& \left(H\oplus H\right) \left(\tau_{03} \oplus \tau_{12}\right)\left(H\oplus H\right)^{\intercal}\\
+%  =& H\tau_{03}H \oplus H\tau_{12}H\\
+%  =&\begin{pmatrix}
+%         \tau_0+\tau_3 & \tau_0-\tau_3\\
+%         \tau_0-\tau_3 & \tau_0+\tau_3\\
+%         &&\tau_0+\tau_3 & \tau_0-\tau_3\\
+%         &&\tau_0-\tau_3 & \tau_0+\tau_3\\        
+%     \end{pmatrix},
+%  \label{Eq_E_P_C}
+% \end{align}
+% % 
+% where $H$ is the Haddamard matrix
+% % 
+% \begin{equation}
+%  H=\begin{pmatrix}
+%         1 & 1\\
+%         1 & -1\\
+%     \end{pmatrix}.
+%  \label{Hadd_Mat}
+% \end{equation}
+% % 
+% After applying the reshuffling operation on $\hat \mcE_c$, we get the associated Choi matrix (or sometimes called dynamical matrix) of the map $D$, it reads
+% % 
+% \begin{equation}
+%  D=\begin{pmatrix}
+%         \tau_0+\tau_3 & \tau_1+\tau_2\\
+%         \tau_1+\tau_2 & \tau_0+\tau_3\\
+%         &&\tau_0-\tau_3 & \tau_1-\tau_2\\
+%         &&\tau_1-\tau_2 & \tau_0-\tau_3\\        
+%     \end{pmatrix}.
+%  \label{Eq_D_P}
+% \end{equation}
+% % 
+% Back to the Pauli basis, the Choi matrix holds
+% \begin{align}
+%  D_p =& \left(\frac{1}{2}H\oplus H\right)\hat D \left(\frac{1}{2}H\oplus H\right)^{\intercal}\\
+%  =&\frac{1}{4}\left(H\oplus H\right)\hat D \left(H\oplus H\right)^{\intercal}\\
+% =&\begin{pmatrix}
+%         \lambda_0\\
+%         &\lambda_1\\
+%         &&\lambda_2\\
+%         &&&\lambda_3\\
+%     \end{pmatrix}.
+% %   =&\begin{pmatrix}
+% %         \tau_0+\tau_3+\tau_1+\tau_2\\
+% %         &\tau_0-\tau_3+\tau_1-\tau_2\\
+% %         &&\tau_0+\tau_3-\tau_1-\tau_2\\
+% %         &&&\tau_0-\tau_3-\tau_1+\tau_2\\        
+% %     \end{pmatrix}.
+%  \label{Eq_D_C_P}
+% \end{align}
+% % 
+% In other words, the Pauli basis diagonalizes the Choi matrix associated to any Pauli map, with eigenvalues related to the map coefficients $\tau$ as
+% % 
+% \begin{equation}
+% \begin{pmatrix}
+%         \lambda_0\\
+%         \lambda_1\\
+%         \lambda_2\\
+%         \lambda_3\\   
+%     \end{pmatrix}
+%  =\frac{1}{2}\begin{pmatrix}
+%         1&1&1&1\\
+%         1&-1&1&-1\\
+%         1&1&-1&-1\\
+%         1&-1&-1&1\\
+%     \end{pmatrix}
+%     \begin{pmatrix}
+%         \tau_0\\
+%         \tau_3\\
+%         \tau_1\\
+%         \tau_2\\   
+%     \end{pmatrix},
+%  \label{Eigen1}
+% \end{equation}
+% % 
+% or in a compact form
+% % 
+% \begin{equation}
+%  \lambda = \frac{1}{2}H\otimes H \tau.
+% \end{equation}
+% % 
+% Now we proceed to generalize this result for the case $N$ qubits case.
+
+\subsubsection{$N$ qubits}
+
+Coming soon...
+
+\subsection{Parte de Francois}
 

### 2021-09-23 documentos/math.tex
Choi_N_Partial

@@
 
-We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\mu}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
-By writing the density matrix in vector form $\ket{\rho}=\sum_{\mu=0}^{3} \alpha_{\mu} \ket{\sigma_{\mu}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
+We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
+By writing the density matrix in vector form $\ket{\rho}=\sum_{\alpha=0}^{3} \alpha_{\alpha} \ket{\sigma_{\alpha}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
 % 
 \begin{equation}
-\hat{\mathcal{E}} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \dyad{\sigma_{\mu}},
+\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \dyad{\sigma_{\alpha}},
 % \label{Map_Pauli}
@@
 %
-where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\mu}}}{{\sigma_{\mu'}}} = \tr \left(\sigma_{\mu}^{\dagger} \sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$.
+where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
 After some steps it is possible to show that the associated Choi matrix reads
@@
 \begin{equation}
- \mathcal{D} = \frac{1}{2}\sum_{\mu=0}^{3} \tau_{\mu} \sigma_{\mu} \otimes \sigma_{\mu}^*.
+ \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
 %  \label{Choi_1}
@@
 % 
-Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\mu}=\sqrt{\frac{\tau_{\mu}}{2}}\sigma_{\mu}$.
+Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\alpha}=\sqrt{\frac{\tau_{\alpha}}{2}}\sigma_{\alpha}$.
 For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
@@
 \begin{equation}
- \lambda_{\nu} = \frac{1}{2}\sum_{\mu=0}^3H_{\nu\mu}^{(4)}\tau_{\mu},
+ \lambda_{\beta} = \frac{1}{2}\sum_{\alpha=0}^3H_{\beta\alpha}^{(4)}\tau_{\alpha},
 \end{equation}
@@
 \end{equation}
+
+% For the sake of simplicity in the derivation of the relations, let us employ a set of binary indices
 % 
+% \begin{equation}
+% \rho=\sum_{mn=0}^{1} \alpha_{mn} \sigma_{mn},
+% % \label{rho}
+% \end{equation}
+
+\subsubsection{$N$ qubits}
+% 
+For the case of $N$ qubits, the density matrix may be written as
+% 
+\begin{equation}
+\rho=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
+% \label{rho2}
+\end{equation}
+% 
+Analogously to the single qubit case, we can define a $N$-qubits Pauli map
+% 
+\begin{equation}
+\rho \to \rho'=\mathcal{E}[\rho ]=\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
+% \label{Pauli_Map}
+\end{equation}
+% 
+with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
+% 
+In this case the density matrix in vector form holds 
+% 
+\begin{equation}
+ \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+\end{equation}
+% 
+where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
 (Proofs in an appendix using binary indices XD)
@@
 
-\subsubsection{$N$ qubits}
-
-Coming soon...
+% \subsubsection{$N$ qubits}
 

### 2021-09-23 documentos/math.tex
lolwhat?

--- 2021-09-23 documentos/math.tex
@@
 %
-where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\mu}}}{{\sigma_{\mu'}}} = \tr \left(\sigma_{\mu}^{\dagger} \sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$.
-After some steps it is possible to show that the associated Choi matrix reads
+where the kets $\ket{\sigma_{\mu}}$ correspond to the vectorized elements of
+the Pauli basis and satisfy the usual relation $
+\braket{{\sigma_{\mu} }}{{\sigma_{\mu'} }} = \tr \left(\sigma_{\mu}^{\dagger}
+\sigma_{\mu'}\right) = 2 ~\delta_{\mu\mu'}$. After some steps it is possible to
+show that the associated Choi matrix reads
 % 
@@
 % \end{itemize} % }}}
+
+The problem of determining complete positivity of a PCE can be recast as 
+determining which vectors $\vec \tau$ are mapped via
+$\san$
+% \begin{equation}
+% \san\vec\tau=2^N\vec p
+% \label{eq:condition}
+% \end{equation}
+to a positive vector $\vec p$. In compontents, this would read 
+\begin{equation}
+\left(
+\san_{\vec\alpha\vec\beta}
+\right)
+\tau_\beta=2^Np_{\vec\alpha}
+\label{eq:4}
+\end{equation}
+where
+$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
+\sa_{\alpha_N\beta_N}$. From the
+
+It results convenient to express the 
+previous equation in
 

### 2021-09-23 documentos/pce.tex
traza
oops, forgot to add the file
lolwhat?

@@
 \alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
-$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$\cpnote{Quizá se cambia
-cuando hayamos escrito lo de un qubit}. 
+$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
 Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
-$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
+$\tr \sigma_\valpha=2^N\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
 We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
@@
 Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
- \cpnote{davalos, dale aca un pequeño 
-rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
-funciona para eso y quizá también seran relevantes para la parte de decoherencia} \ddnote{De momento no he encontrado alguna reference, para qubits si, pero para los generales no, estoy checando de nuevo el paper de Ruskai para entender que tanto se solapan, a ver si puedo decir algo}.
+ \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
+frases. También debemos tener un nombre pues lo de la diagonazliación funciona
+para eso y quizá también seran relevantes para la parte de decoherencia}
+\ddnote{De momento no he encontrado alguna reference, para qubits si, pero para
+los generales no, estoy checando de nuevo el paper de Ruskai para entender que
+tanto se solapan, a ver si puedo decir algo}.
 For the operation to preserve the trace of the density matrix, we require that 
 $\tau_{\vec 0}=1$. 
-\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
-A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
+A Pauli component erasing (PCE) operation is a Pauli diagonal operation
 %  A linear operation 
@@
 \begin{figure} % {{{
-\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
-\pgfmathsetmacro{\unitstep}{5.8}
+\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
+\pgfmathsetmacro{\unitstep}{5.2}
 \begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
-\node at (-0.6,0.5) {(a)} ;
+\node at (-0.5,0.5) {(a)} ;
     \foreach \x in {0,1,2,3} {
@@
           \draw (0,0) rectangle (1,1); 
-          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{\y,\x}$}};
+          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
          \end{scope}
@@
 \begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
-\node at (-0.6,0.5) {(b)} ;
+\node at (-0.5,0.5) {(b)} ;
     \foreach \x in {0,1,2,3} {
@@
 \begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
-\node at (-0.6,0.5) {(c)} ;
+\node at (-0.5,0.5) {(c)} ;
     \foreach \x in {0,1,2,3} {

### 2021-09-23 documentos/math.tex

--- 2021-09-23 documentos/math.tex
@@
 %
-where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
-After some steps it is possible to show that the associated Choi matrix reads
+where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of
+the Pauli basis and satisfy the usual relation $
+\braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
+~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the
+associated Choi matrix reads
 % 

### 2021-09-23 documentos/math.tex
marks

--- 2021-09-23 documentos/math.tex
@@
 %
-where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
-After some steps it is possible to show that the associated Choi matrix reads
+where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of
+the Pauli basis and satisfy the usual relation $
+\braket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
+~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the
+associated Choi matrix reads
 % 
@@
 \begin{equation}
- \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+ \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha} }},
 \end{equation}
 % 
-where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
+where $\ket{\sigma_{\vec{\alpha} }}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
 (Proofs in an appendix using binary indices XD)
@@
 
-\subsection{Parte de Francois}
+% }}}
 
-We have the matrix 
-\begin{equation}
-\sa=\left(
-\begin{array}{cccc}
-1 &1 &1   &1   \\
- 1 & 1  & -1&-1   \\
-1  & -1  & 1 & -1\\
-1&-1&-1&1  
-\end{array}
-\right)=\frac12\sa^{-1}.
-\label{eq:1}
-\end{equation}
-and further define the matrix
-\begin{equation}
-\san=\left(\sa\right)^{\otimes N}
-\label{eq:1a}
-\end{equation}
-% }}}
-\subsection{A vector space of channels} % {{{
-% \begin{itemize} % {{{ Cosas por escribir aca
-% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
-% \item Regla de $2^k$
-% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
-% y tambien nota de qeu son igual entre complementarios: computo del numero de
-% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
-% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
-% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
-% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
-% Concepts might be complicated, but the tool gives some simple rules to the
-% reader: \textit{tell me what components you want to keep, and the (vector)
-% summation rules will give you the rest of components to make the target
-% operation a CPTP one.}
-% \end{itemize} % }}}
-
-We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
-\begin{equation}
-\san\vec\tau=2^N\vec p
-\label{eq:3}
-\end{equation}
-where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
-and 1's. We number the entries of $\vec\tau$ 
-by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
-The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
-the expression (\ref{eq:3}) satisfies
-\begin{equation}
-\left(
-\san_{\vec\alpha\vec\beta}
-\right)
-\tau_\beta=2^Np_{\vec\alpha}
-\label{eq:4}
-\end{equation}
-where
-\begin{equation}
-\left(
-\san_{\vec\alpha\vec\beta}
-\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
-\label{eq:5}
-\end{equation}
-
-From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
-\begin{equation}
-\tau_\alpha=\left(
-\san_{\vec\alpha\vec\beta}
-\right)p_\beta
-\label{eq:6}
-\end{equation}
-which we analyze iteratively. We shall essentially use the fact that
-\begin{equation}
-p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
-\label{eq:7}
-\end{equation}
-
-Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
-of multi-indices $\Phi(\vec\alpha)$ as follows
-\begin{equation}
-\Phi(\vec\alpha):=\left\{
-\vec\beta:\san_{\vec\alpha\vec\beta}=1
-\right\}=\left\{
-\vec\beta:
-\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
-=1
-\right\}
-\label{eq:8}
-\end{equation}
-If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting the two combined equations
-\begin{subequations}
-\begin{eqnarray}
-\sum_{\vec\beta}p_{\vec\beta}&=&1
-\label{eq:9a}\\
-\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
-\end{eqnarray}
-\label{eq:9}
-\end{subequations}
-that for all $\vec\beta\notin\Phi(\vec\alpha)$
-\begin{eqnarray}
-p_{\vec\beta}=0.
-\label{eq:10}
-\end{eqnarray}
-Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
-and $\tau_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
-\begin{equation}
-\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
-\label{eq:11}
-\end{equation}
-holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
-to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
-
-% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
-%\begin{subequations}
-%\begin{eqnarray}
-%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
-%\label{eq:10na}
-%\\
-%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
-%\label{eq:10nb}
-%\\
-%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
-%\label{eq:10nc}
-%\\
-%&=&\sum_{\vec\beta}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
-%\label{eq:10nd}
-%\\
-%&=&\tau_{\vec{\gamma^\prime}}
-%\label{eq:10ne}
-%\end{eqnarray}
-%\label{eq:10n}
-%\end{subequations}
-%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
-%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).
-
-Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
-When such a connection exists, $\tau_{\vec\alpha}=1$ implies 
-$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.
-
-Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
-\begin{equation}
-\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
-\label{eq:12}
-\end{equation}
-This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
-\begin{equation}
-\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
-\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
-\label{eq:13}
-\end{equation}
-Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
-the above relation must hold individually for every index. Thus we have, 
-that, for all $1\leq k\leq N$, $\gamma_k$
-and $\gamma_k^\prime$ are connected by
-\begin{equation}
-\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
-\label{eq:14}
-\end{equation}
-for all $0\leq\beta\leq3$. This is equivalently expressed as 
-\begin{equation}
-\gamma_k^\prime=\alpha\oplus{}\gamma_k
-\label{eq:15}
-\end{equation}
-where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.
-
-\begin{figure}
-\begin{center}
-\begin{tabular}{| c | c c c c |}
-\hline
-$\oplus{}$ & 0 & 1& 2 & 3\\
-\hline
-0 & 0 & 1 & 2 & 3\\
-1 & 1 & 0 & 3 & 2\\
-2 & 2 & 3 & 0 & 1 \\
-3 &3 & 2 & 1 & 0\\
-\hline
-\end{tabular}
-\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
-is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
-neutral element is $0$. This is the reason for choosing an additive notation for the operation
-defined in (\ref{eq:14}).
-}
-\label{tab:1}
-\end{center}
-\end{figure}
-
-Note further that if we perform the identification
-\begin{subequations}
-\begin{eqnarray}
-0&\to&(0,0)\label{eq:identa}\\
-1&\to&(0,1)\label{eq:identb}\\
-2&\to&(1,0)\label{eq:identc}\\
-3&\to&(1,1)\label{eq:identd}
-\end{eqnarray}
-\label{eq:ident}
-\end{subequations}
-then the $\oplus$ operation reduces to simple vector addition in
-binary arithmetic. If we therefore denote by $\overline{\alpha}$
-the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
-the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
-as
-\begin{equation}
-\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
-\label{eq:17}
-\end{equation}
-where the addition sign here refers to ordinary binary vector addition.
-
-From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
-for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
-to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
-forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
-$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
-\begin{equation}
-\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
-\label{eq:14b}
-\end{equation}
-then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
-and thus equal to one.
-
-So we may now proceed to generate all solutions: we start out from the solution having $\tau_{\vec0}=1$, with
-everything else $0$. We may then successively switch $\tau$'s to $1$ for various values of $\vec\alpha$, 
-taking care immediately to set equal to one the values of $\tau$ that correspond to values of $\vec\beta$
-generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).
-
-A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
-set all $\tau_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
-subspace of the set of all indices, then the vector $\vec\tau$ indeed has an image which is a vector with 
-only positive components.
-
-%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
-%componentwise
-%\begin{equation}
-%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
-%\label{eq:16}
-%\end{equation}
-%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.
-
-%If $\tau_{\vec\alpha}=1$, then it follows from the above that 
-%for all $\gamma$
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}.
-%\label{eq:17}
-%\end{equation}
-
-%Now take an arbitrary $\vec{\alpha}_1$ and set $\tau_{\vec{\alpha}_1}=1$. This immediately imposes the
-%relationship
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}
-%\label{eq:18}
-%\end{equation}
-%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\tau$
-%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
-%and $\tau_{\vec0}$ is one by convention. 
-%
-%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
-%that is automatically equal to $\tau_{\alp1}$. Set $\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
-%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}=\tau_{\alp2\oplus{}\vec\gamma}=\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
-%\label{eq:19}
-%\end{equation}
-%Thus we find that the $\tau$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
-%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$. Further, it follows from the group property
-%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
-%to any other $\vec{\gamma^\prime}$. 
-%
-%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
-%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
-%
-%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
-%in other words, we may double $2N-1$ times.
-%
-%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
-%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
-%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
-%of the $\alp{k}$. 
-%
-%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
-%At this stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
-%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
-%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
-%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
-%
-%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
-%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.
-
-The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
-\begin{equation}
-W=\left\{
-\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
-\right\}
-\label{eq:19}
-\end{equation}
-is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
-a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.
-
-By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
-$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
-the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
-the result that all PCE's can be obtained as intersections of maximal PCE's.
-
-\ddnote{Agrego esto:} A final remarks of the derivation as a tool.
-Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}
-
-% }}}
+\input{vector_space}

### 2021-09-23 documentos/vector_space.tex
marks

\subsection{Parte de Francois} % {{{

We have the matrix 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\end{array}
\right)=\frac12\sa^{-1}.
\label{eq:1}
\end{equation}
and further define the matrix
\begin{equation}
\san=\left(\sa\right)^{\otimes N}
\label{eq:1a}
\end{equation}
% }}}
\subsection{A vector space of channels} % {{{
% \begin{itemize} % {{{ Cosas por escribir aca
% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
% \item Regla de $2^k$
% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
% y tambien nota de qeu son igual entre complementarios: computo del numero de
% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
% Concepts might be complicated, but the tool gives some simple rules to the
% reader: \textit{tell me what components you want to keep, and the (vector)
% summation rules will give you the rest of components to make the target
% operation a CPTP one.}
% \end{itemize} % }}}

The problem of determining complete positivity of a PCE can be recast as 
determining which vectors $\vec \tau$ are mapped via
$\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to a positive vector $\vec p$. In compontents, this would read 
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
\sa_{\alpha_N\beta_N}$. From the

It results convenient to express the 
previous equation in

We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
\begin{equation}
\san\vec\tau=2^N\vec p
\label{eq:3}
\end{equation}
where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
and 1's. We number the entries of $\vec\tau$ 
by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
the expression (\ref{eq:3}) satisfies
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)
\tau_\beta=2^Np_{\vec\alpha}
\label{eq:4}
\end{equation}
where
\begin{equation}
\left(
\san_{\vec\alpha\vec\beta}
\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
\label{eq:5}
\end{equation}

From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
\begin{equation}
\tau_\alpha=\left(
\san_{\vec\alpha\vec\beta}
\right)p_\beta
\label{eq:6}
\end{equation}
which we analyze iteratively. We shall essentially use the fact that
\begin{equation}
p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
\label{eq:7}
\end{equation}

Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}=\left\{
\vec\beta:
\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
=1
\right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting the two combined equations
\begin{subequations}
\begin{eqnarray}
\sum_{\vec\beta}p_{\vec\beta}&=&1
\label{eq:9a}\\
\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
\end{eqnarray}
\label{eq:9}
\end{subequations}
that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
p_{\vec\beta}=0.
\label{eq:10}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
\label{eq:11}
\end{equation}
holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
%\begin{subequations}
%\begin{eqnarray}
%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10na}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
%\label{eq:10nb}
%\\
%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nc}
%\\
%&=&\sum_{\vec\beta}\left(
%M^{\otimes N}
%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
%\label{eq:10nd}
%\\
%&=&\tau_{\vec{\gamma^\prime}}
%\label{eq:10ne}
%\end{eqnarray}
%\label{eq:10n}
%\end{subequations}
%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).

Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies 
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.

Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
\label{eq:12}
\end{equation}
This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. This is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.

\begin{figure}
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
neutral element is $0$. This is the reason for choosing an additive notation for the operation
defined in (\ref{eq:14}).
}
\label{tab:1}
\end{center}
\end{figure}

Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition.

From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
\begin{equation}
\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
\label{eq:14b}
\end{equation}
then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
and thus equal to one.

So we may now proceed to generate all solutions: we start out from the solution having $\tau_{\vec0}=1$, with
everything else $0$. We may then successively switch $\tau$'s to $1$ for various values of $\vec\alpha$, 
taking care immediately to set equal to one the values of $\tau$ that correspond to values of $\vec\beta$
generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).

A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
set all $\tau_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
subspace of the set of all indices, then the vector $\vec\tau$ indeed has an image which is a vector with 
only positive components.

%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
%componentwise
%\begin{equation}
%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
%\label{eq:16}
%\end{equation}
%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.

%If $\tau_{\vec\alpha}=1$, then it follows from the above that 
%for all $\gamma$
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}.
%\label{eq:17}
%\end{equation}

%Now take an arbitrary $\vec{\alpha}_1$ and set $\tau_{\vec{\alpha}_1}=1$. This immediately imposes the
%relationship
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}
%\label{eq:18}
%\end{equation}
%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\tau$
%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
%and $\tau_{\vec0}$ is one by convention. 
%
%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
%that is automatically equal to $\tau_{\alp1}$. Set $\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
%\begin{equation}
%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}=\tau_{\alp2\oplus{}\vec\gamma}=\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
%\label{eq:19}
%\end{equation}
%Thus we find that the $\tau$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$. Further, it follows from the group property
%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
%to any other $\vec{\gamma^\prime}$. 
%
%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
%
%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
%in other words, we may double $2N-1$ times.
%
%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
%of the $\alp{k}$. 
%
%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
%At this stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
%
%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.

The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
\begin{equation}
W=\left\{
\vec\alpha:\vec\alpha\in V, \tau_{\vec\alpha}=1
\right\}
\label{eq:19}
\end{equation}
is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.

By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
the result that all PCE's can be obtained as intersections of maximal PCE's.

\ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}

% }}}

### 2021-09-23 documentos/vector_space.tex
fixed conflicts (LOL merge -s ours; push -f)

@@
 
+% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
 The problem of determining complete positivity of a PCE can be recast as 
@@
 \begin{equation}
-\left(
-\san_{\vec\alpha\vec\beta}
-\right)
+% \left(
+\san_{\vec\alpha\vec\beta} \,
+% \right)
 \tau_\beta=2^Np_{\vec\alpha}
-\label{eq:4}
+\label{eq:A:tau:is:p}
 \end{equation}
@@
 $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
-\sa_{\alpha_N\beta_N}$. From the
+\sa_{\alpha_N\beta_N}$. Using the fact that $a=a^{-1/2}$ (so
+$A = A^{-1}/2^N$) we can directly invert \eref{eq:A:tau:is:p} 
+and obtain 
+\begin{equation}
+\tau_\alpha=
+% \left(
+\san_{\vec\alpha\vec\beta} \,
+% \right)
+p_\beta,
+\label{eq:tau:is:A:p}
+\end{equation}
+which will serve as a starting point for our analysis. Other simple but crucial
+observation that we shall use is that, for valid quantum channels, 
+$p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
+all $p_{\vec\alpha} \ge 0$ due to 
+complete positivity of the underlying channel.
 
-It results convenient to express the 
-previous equation in
+% We shall essentially use the fact that
+% 
+% 
+% 
+% It results convenient to express the 
+% previous equation in  
+%
 
-We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
-\begin{equation}
-\san\vec\tau=2^N\vec p
-\label{eq:3}
-\end{equation}
-where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
-and 1's. We number the entries of $\vec\tau$ 
-by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
-The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
-the expression (\ref{eq:3}) satisfies
-\begin{equation}
-\left(
-\san_{\vec\alpha\vec\beta}
-\right)
-\tau_\beta=2^Np_{\vec\alpha}
-\label{eq:4}
-\end{equation}
-where
-\begin{equation}
-\left(
-\san_{\vec\alpha\vec\beta}
-\right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
-\label{eq:5}
-\end{equation}
-
-From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
-\begin{equation}
-\tau_\alpha=\left(
-\san_{\vec\alpha\vec\beta}
-\right)p_\beta
-\label{eq:6}
-\end{equation}
-which we analyze iteratively. We shall essentially use the fact that
-\begin{equation}
-p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
-\label{eq:7}
-\end{equation}
+% We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
+% \begin{equation}
+% \san\vec\tau=2^N\vec p
+% \label{eq:3}
+% \end{equation}
+% where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
+% and 1's. We number the entries of $\vec\tau$ 
+% by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
+% The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
+% the expression (\ref{eq:3}) satisfies
+% \begin{equation}
+% \left(
+% \san_{\vec\alpha\vec\beta}
+% \right)
+% \tau_\beta=2^Np_{\vec\alpha}
+% \label{eq:4}
+% \end{equation}
+% where
+% \begin{equation}
+% \left(
+% \san_{\vec\alpha\vec\beta}
+% \right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+% \label{eq:5}
+% \end{equation}
+% 
+% From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
+% \begin{equation}
+% \tau_\alpha=\left(
+% \san_{\vec\alpha\vec\beta}
+% \right)p_\beta
+% \label{eq:6}
+% \end{equation}
+% which we analyze iteratively. We shall essentially use the fact that
+% \begin{equation}
+% p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
+% \label{eq:7}
+% \end{equation}
+% }}}
 

### 2021-09-23 documentos/math.tex
Choi_N

@@
 \janote{Qué tal $\vec\rho\quad$?}
+\afnote{Por ahora uso este $\ket{\rho}$}
 
 We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
-By writing the density matrix in vector form $\ket{\rho}=\sum_{\alpha=0}^{3} \alpha_{\alpha} \ket{\sigma_{\alpha}}$, it is easy to show that the matrix form of the map $\mathcal{E}$ may be written as
+By writing the density matrix in vector form $\ket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \ket{\sigma_{\alpha}}$, the matrix form of the map $\mathcal{E}$ may be written as
 % 
@@
 %
-where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of
-the Pauli basis and satisfy the usual relation $
-\braket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
-~\delta_{\alpha\alpha'}$. After some steps it is possible to show that the
-associated Choi matrix reads
+where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
+After some steps it is possible to show that the associated Choi matrix reads
 % 
@@
 % 
-Note that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel whose Kraus operators are given by $K_{\alpha}=\sqrt{\frac{\tau_{\alpha}}{2}}\sigma_{\alpha}$.
-For the latter case, it has been shown that corresponding eigenvalues read \cite{CHRUSCINSKI20131425}
+Moreover, observe that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel, with Kraus operators given by $K_{\alpha}=\sqrt{\tau_{\alpha}/2}\sigma_{\alpha}$ \cite{CHRUSCINSKI20131425}.
+In this way the Choi matrix $\mathcal{D}$ is diagonal in the Pauli basis (see Appendix for details),
 %
 \begin{equation}
- \lambda_{\beta} = \frac{1}{2}\sum_{\alpha=0}^3H_{\beta\alpha}^{(4)}\tau_{\alpha},
+ \mathcal{D} \ket{\sigma_{\alpha}}= \lambda_{\alpha} \ket{\sigma_{\alpha}},
 \end{equation}
 % 
-or
+with eigenvalues given by 
 % 
 \begin{equation}
- \vec{\lambda} = \frac{1}{2}~ H^{(2)}\otimes H^{(2)}\vec{\tau},
+ \lambda_{\alpha} = \sum_{\beta=0}^3\sa_{\alpha\beta}\tau_{\beta},
 \end{equation}
 %
-where $H^{(m)}$ is the Hadamard matrix of order \textit{m}, and for $m=2$ reduces to the usual Hadamard matrix.
+or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix,
 %
 \begin{equation}
- H^{(2)}=\begin{pmatrix}
+ H=\begin{pmatrix}
         1 & 1\\
@@
 \end{equation}
-
-% For the sake of simplicity in the derivation of the relations, let us employ a set of binary indices
 % 
-% \begin{equation}
-% \rho=\sum_{mn=0}^{1} \alpha_{mn} \sigma_{mn},
-% % \label{rho}
-% \end{equation}
+\afnote{Podemos definir la matriz de Hadamard con un factor $2^{-1/2}$, o sea $H'=H/\sqrt{2}$ para evitar cargar factores extra hasta el final, de esta manera tenemos simplemente $\san=H^{\otimes 2N}$.
+Qué opinan?}
 
@@
 % 
-For the case of $N$ qubits, the density matrix may be written as
+Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
 % 
 \begin{equation}
-\rho=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
-% \label{rho2}
-\end{equation}
-% 
-Analogously to the single qubit case, we can define a $N$-qubits Pauli map
-% 
-\begin{equation}
-\rho \to \rho'=\mathcal{E}[\rho ]=\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
+\rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
 % \label{Pauli_Map}
@@
 \begin{equation}
- \ket{\rho}=\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha} }},
+ \ket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
 \end{equation}
 % 
-where $\ket{\sigma_{\vec{\alpha} }}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
+where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
+The matrix representation of this map is given by
+% 
+\begin{equation}
+\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \dyad{\sigma_{\vec{\alpha}}}.
+% \label{Map_Pauli}
+\end{equation}
+%
+As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in terms of tensor products of Pauli matrices
+% 
+\begin{equation}
+ \mathcal{D}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}  \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
+%  \label{Choi_1}
+\end{equation}
+% 
+After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
+%
+\begin{equation}
+ \mathcal{D}_N \ket{\sigma_{\vec{\alpha}}}= \lambda_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+\end{equation}
+% 
+with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
+% 
+\begin{equation}
+ \lambda_{\vec{\alpha}} = \sum_{\vec{\beta}} \san_{\vec{\alpha}\vec{\beta}}\tau_{\vec{\beta}},
+\end{equation}
+%
+where 
+% 
+\begin{equation}
+ \san=\sa^{\otimes N}=\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
+\end{equation}
+%
+
 (Proofs in an appendix using binary indices XD)
 
-% By writing the elements of the density matrix in vector form $\varrho=\left(\varrho_0,\varrho_1,\varrho_2,\varrho_3\right)^{\intercal}$, the action of a Pauli map on $\varrho$ for a single qubit may be written as $\varrho \to \varrho'=\hat \mcE \varrho$, where $\hat \mcE$ is the matrix representation of the map.
-Moreover it can be shown that in the Pauli basis $(\sigma_0,\sigma_1,i\sigma_2,\sigma_3)$, $\hat \mcE$ reduces simply to $\mathrm{diag}\left(\tau_0,\tau_1,\tau_2,\tau_3\right)$.
-% 
-% Let reorganize the elements of the Pauli basis as $(\sigma_0,\sigma_3,\sigma_1,i\sigma_2)$, in this way it is possible to write the matrix representation of the map as $\hat \mcE = \tau_{03} \oplus \tau_{12}$, where $\tau_{jk}=\mathrm{diag}\left(\tau_j,\tau_k\right)$ and the symbol $``\oplus "$ represents a direct sum of matrices.
-The advantage of this ordering is manifested when the matrix $\hat \mcE$ is transformed to the computational basis $(u_{00},u_{11},u_{01},u_{10})$, $\hat \mcE_c$:
-% % 
-% \begin{align}
-%  \hat \mcE_c =& \left(H\oplus H\right)\hat \mcE \left(H\oplus H\right)^{\intercal}\\
-%  =& \left(H\oplus H\right) \left(\tau_{03} \oplus \tau_{12}\right)\left(H\oplus H\right)^{\intercal}\\
-%  =& H\tau_{03}H \oplus H\tau_{12}H\\
-%  =&\begin{pmatrix}
-%         \tau_0+\tau_3 & \tau_0-\tau_3\\
-%         \tau_0-\tau_3 & \tau_0+\tau_3\\
-%         &&\tau_0+\tau_3 & \tau_0-\tau_3\\
-%         &&\tau_0-\tau_3 & \tau_0+\tau_3\\        
-%     \end{pmatrix},
-%  \label{Eq_E_P_C}
-% \end{align}
-% % 
-% where $H$ is the Haddamard matrix
-% % 
-% \begin{equation}
-%  H=\begin{pmatrix}
-%         1 & 1\\
-%         1 & -1\\
-%     \end{pmatrix}.
-%  \label{Hadd_Mat}
-% \end{equation}
-% % 
-% After applying the reshuffling operation on $\hat \mcE_c$, we get the associated Choi matrix (or sometimes called dynamical matrix) of the map $D$, it reads
-% % 
-% \begin{equation}
-%  D=\begin{pmatrix}
-%         \tau_0+\tau_3 & \tau_1+\tau_2\\
-%         \tau_1+\tau_2 & \tau_0+\tau_3\\
-%         &&\tau_0-\tau_3 & \tau_1-\tau_2\\
-%         &&\tau_1-\tau_2 & \tau_0-\tau_3\\        
-%     \end{pmatrix}.
-%  \label{Eq_D_P}
-% \end{equation}
-% % 
-% Back to the Pauli basis, the Choi matrix holds
-% \begin{align}
-%  D_p =& \left(\frac{1}{2}H\oplus H\right)\hat D \left(\frac{1}{2}H\oplus H\right)^{\intercal}\\
-%  =&\frac{1}{4}\left(H\oplus H\right)\hat D \left(H\oplus H\right)^{\intercal}\\
-% =&\begin{pmatrix}
-%         \lambda_0\\
-%         &\lambda_1\\
-%         &&\lambda_2\\
-%         &&&\lambda_3\\
-%     \end{pmatrix}.
-% %   =&\begin{pmatrix}
-% %         \tau_0+\tau_3+\tau_1+\tau_2\\
-% %         &\tau_0-\tau_3+\tau_1-\tau_2\\
-% %         &&\tau_0+\tau_3-\tau_1-\tau_2\\
-% %         &&&\tau_0-\tau_3-\tau_1+\tau_2\\        
-% %     \end{pmatrix}.
-%  \label{Eq_D_C_P}
-% \end{align}
-% % 
-% In other words, the Pauli basis diagonalizes the Choi matrix associated to any Pauli map, with eigenvalues related to the map coefficients $\tau$ as
-% % 
-% \begin{equation}
-% \begin{pmatrix}
-%         \lambda_0\\
-%         \lambda_1\\
-%         \lambda_2\\
-%         \lambda_3\\   
-%     \end{pmatrix}
-%  =\frac{1}{2}\begin{pmatrix}
-%         1&1&1&1\\
-%         1&-1&1&-1\\
-%         1&1&-1&-1\\
-%         1&-1&-1&1\\
-%     \end{pmatrix}
-%     \begin{pmatrix}
-%         \tau_0\\
-%         \tau_3\\
-%         \tau_1\\
-%         \tau_2\\   
-%     \end{pmatrix},
-%  \label{Eigen1}
-% \end{equation}
-% % 
-% or in a compact form
-% % 
-% \begin{equation}
-%  \lambda = \frac{1}{2}H\otimes H \tau.
-% \end{equation}
-% % 
-% Now we proceed to generalize this result for the case $N$ qubits case.
-
-% \subsubsection{$N$ qubits}
+\subsubsection{Appendix - Diagonalization of Choi Matrix $\mathcal{D}_N$}
 

### 2021-09-24 documentos/math.tex
App0
App1

@@
 \janote{Qué tal $\vec\rho\quad$?}
-\afnote{Por ahora uso este $\ket{\rho}$}
+\afnote{Por ahora uso este $\kket{\rho}$}
 
 We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
-By writing the density matrix in vector form $\ket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \ket{\sigma_{\alpha}}$, the matrix form of the map $\mathcal{E}$ may be written as
+By writing the density matrix in vector form $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the matrix form of the map $\mathcal{E}$ may be written as
 % 
 \begin{equation}
-\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \dyad{\sigma_{\alpha}},
+\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \ddyada{\sigma_{\alpha}},
 % \label{Map_Pauli}
@@
 %
-where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
+where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
 After some steps it is possible to show that the associated Choi matrix reads
@@
 \begin{equation}
- \mathcal{D} \ket{\sigma_{\alpha}}= \lambda_{\alpha} \ket{\sigma_{\alpha}},
+ \mathcal{D} \kket{\sigma_{\alpha}}= \lambda_{\alpha} \kket{\sigma_{\alpha}},
 \end{equation}
@@
 % 
+% 
 \afnote{Podemos definir la matriz de Hadamard con un factor $2^{-1/2}$, o sea $H'=H/\sqrt{2}$ para evitar cargar factores extra hasta el final, de esta manera tenemos simplemente $\san=H^{\otimes 2N}$.
@@
 \begin{equation}
- \ket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+ \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha}}},
 \end{equation}
 % 
-where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
+where $\kket{\sigma_{\vec{\alpha}}}=\kket{\sigma_{\alpha_1}}\otimes\dots \otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\bbrakket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
 The matrix representation of this map is given by
@@
 \begin{equation}
-\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \dyad{\sigma_{\vec{\alpha}}}.
+\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha}}}.
 % \label{Map_Pauli}
@@
 \begin{equation}
- \mathcal{D}_N \ket{\sigma_{\vec{\alpha}}}= \lambda_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+ \mathcal{D}_N \kket{\sigma_{\vec{\alpha}}}= \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha}}},
 \end{equation}
@@
 %
+%
 
@@
 
-\subsubsection{Appendix - Diagonalization of Choi Matrix $\mathcal{D}_N$}
+\subsubsection{APPENDIX: Diagonalization of Choi Matrix $\mathcal{D}_N$}
+% 
+In order to simplify the derivation of the relations, let us employ pairs of binary indices instead of a single quaternary, i.e.
+$\alpha\to\mu+2\nu$.
+In this way we can write the elements of the Pauli basis $(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$ in the standard and vectorized forms, compactly as
+% 
+\begin{equation}
+\sigma_{\mu\nu}=\sum_{j=0}^{1} (-1)^{j \mu}\dyad{j}{j\oplus \nu},
+\end{equation}
+% 
+and
+% 
+\begin{equation}
+\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\ket{j,j\oplus \nu}.
+\end{equation}
+% 
+In addition, recall the inverse relation between the computational and Pauli elements
+% 
+\begin{equation}
+\ket{l,l\oplus n}=\frac{1}{2}\sum_{m=0}^{1} (-1)^{ml}\kket{\sigma_{mn}}.
+\label{PauToComp}
+\end{equation}
+% 
+On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may be written as
+% 
+\begin{align}
+\hat{\mathcal{E}} & = \frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}},\\
+& = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \dyad{j,j\oplus\nu}{k,k\oplus\nu}.
+% \label{Map_Pauli}
+\end{align}
+% 
+After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the Choi matrix associated to the map. It reads
+% 
+\begin{equation}
+ \mathcal{D} = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \dyad{j,k}{j\oplus\nu,k\oplus\nu}.
+\label{Choi_a1}
+\end{equation}
+%
+
+Let us appply the index relabeling $k\to j\oplus m$, then the Choi matrix holds
+% 
+\begin{equation}
+ \mathcal{D} = \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu} (-1)^{\mu m} \dyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
+\label{Choi_a1}
+\end{equation}
+%
+By using the relation between computational and Pauli elements (Eq. \ref{PauToComp}), we have
+% 
+\begin{align*}
+ \mathcal{D} & = \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu}(-1)^{\mu m}  \left( \frac{1}{2}\sum_{k=0}^{1} (-1)^{kj}\kket{\sigma_{km}}\right)\left(\frac{1}{2}\sum_{n=0}^{1} (-1)^{n(j\oplus\nu)}\bbra{\sigma_{nm}}\right),\\
+ & = \frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+ & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+ & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} (2\delta_{kn}) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+ & = \frac{1}{4}\sum_{mn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \ddyad{\sigma_{nm}}{\sigma_{nm}},\\
+ & = \frac{1}{2}\sum_{mn} \left(\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu}\right) \ddyad{\sigma_{nm}}{\sigma_{nm}},
+% \label{Choi_a1}
+\end{align*}
+%
+Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
+% 
+\begin{equation}
+\lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
+\end{equation}
+% 
+or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix.
+
+\afnote{Queda faltando pasar a limpio la generalizacion para $N$ qubits.}
 

### 2021-09-29 documentos/math.tex
For the statistics only

--- 2021-09-23 documentos/math.tex
@@
-\section{Mathematical derivation} % {{{
-\subsection{Diagonalization of Choi matrix} % {{{
+\section{Mathematical considerations} 
+\subsection{Diagonalization of Choi matrix}
 
+% Intro {{{
 Prueba de la $\sa$ \todo{Alejo escribe esta parte. Dejelo aca todo y luego si acaso 
@@
 
-This part is devoted to derive the set of conditions a Pauli map need to satisfy to fulfill the CP condition i.e.
-all the eigenvalues of the Choi matrix associated to the channel must be non-negative.
-First we obtain the set of inequalities for a single qubit Pauli channel and then we extend the results for the general case of $N$ qubits.
+This part is devoted to derive the set of conditions a Pauli map need to
+satisfy to fulfill the CP condition i.e. all the eigenvalues of the Choi matrix
+associated to the channel must be non-negative. First we obtain the set of
+inequalities for a single qubit Pauli channel and then we extend the results
+for the general case of $N$ qubits.
 
-\subsubsection{Single qubit Pauli channels}
+% }}}
+\subsubsection{Single qubit Pauli channels} % {{{
 
@@
 %
-where the kets $\ket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \braket{{\sigma_{\alpha}}}{{\sigma_{\alpha'}}} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
+where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha} }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
 After some steps it is possible to show that the associated Choi matrix reads
@@
 %
-or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix,
+or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes
+H$ and $H$ is the Hadamard matrix,
+\cpnote{Decidir si se usa esa $a$ o la otra para ser consistente con lo de los 
+generadores}
 %
@@
 \end{equation}
+
+\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
+dejo por aca por si se nos ofrece}
+\begin{equation}
+\sa=\left(
+\begin{array}{cccc}
+1 &1 &1   &1   \\
+ 1 & 1  & -1&-1   \\
+1  & -1  & 1 & -1\\
+1&-1&-1&1  
+\end{array}
+\right)=\frac12\sa^{-1}.
+\label{eq:1}
+\end{equation}
 % 
-\afnote{Podemos definir la matriz de Hadamard con un factor $2^{-1/2}$, o sea $H'=H/\sqrt{2}$ para evitar cargar factores extra hasta el final, de esta manera tenemos simplemente $\san=H^{\otimes 2N}$.
-Qué opinan?}
-
-\subsubsection{$N$ qubits}
+%  }}}
+\subsubsection{$N$ qubits} % {{{
 % 
@@
 \begin{equation}
- \ket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+ \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
 \end{equation}
 % 
-where $\ket{\sigma_{\vec{\alpha}}}=\ket{\sigma_{\alpha_1}}\otimes\dots \otimes\ket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation $\braket{{\sigma_{\vec{\alpha}}}}{{\sigma_{\vec{\alpha}'}}} = \tr \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N ~\delta_{\vec{\alpha}\vec{\alpha}'}$.
-The matrix representation of this map is given by
+where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
+\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
+$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
+\left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
+~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
+given by
 % 
 \begin{equation}
-\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \dyad{\sigma_{\vec{\alpha}}}.
+\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
 % \label{Map_Pauli}
@@
 \begin{equation}
- \mathcal{D}_N \ket{\sigma_{\vec{\alpha}}}= \lambda_{\vec{\alpha}} \ket{\sigma_{\vec{\alpha}}},
+ \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
+   = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
 \end{equation}
@@
 \begin{equation}
- \san=\sa^{\otimes N}=\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
+ \san=\sa^{\otimes N}
+% =\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
 \end{equation}
-%
-
-(Proofs in an appendix using binary indices XD)
-
-\subsubsection{Appendix - Diagonalization of Choi Matrix $\mathcal{D}_N$}
-
+Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}
+\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
+qubits.}
+% (Proofs in an appendix using binary indices XD)
 % }}}
-
-\input{vector_space}

### 2021-09-29 documentos/proofdiagonalization.tex
For the statistics only

\section{Diagonalization of Choi Matrix $\mathcal{D}_N$} % {{{
\label{sec:appendix:diagonalization}
% 
In order to simplify the derivation of the relations, let us employ pairs of
binary indices instead of a single quaternary, i.e. $\alpha\to\mu+2\nu$. In
this way we can write the elements of the Pauli basis
$(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$ in the standard and vectorized
forms, compactly as
\begin{equation}
\sigma_{\mu\nu}=\sum_{j=0}^{1} (-1)^{j \mu}\dyad{j}{j\oplus \nu},
\end{equation}
and
\begin{equation}
\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\ket{j,j\oplus \nu}.
\end{equation}
In addition, recall the inverse relation between the computational and Pauli elements
\begin{equation}
\ket{l,l\oplus n}=\frac{1}{2}\sum_{m=0}^{1} (-1)^{ml}\kket{\sigma_{mn}}.
\label{PauToComp}
\end{equation}
On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may
be written as
\begin{align}
\hat{\mathcal{E}} & = \frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}},\\
& = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \dyad{j,j\oplus\nu}{k,k\oplus\nu}.
% \label{Map_Pauli}
\end{align}
After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the
Choi matrix associated to the map. It reads
\begin{equation}
 \mathcal{D} = 
  \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} 
      \dyad{j,k}{j\oplus\nu,k\oplus\nu}.
\label{Choi_a1}
\end{equation}

Let us apply the index relabeling $k\to j\oplus m$, then the Choi matrix holds
\begin{equation}
 \mathcal{D} =
    \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu} (-1)^{\mu m} 
        \dyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
\label{Choi_a1}
\end{equation}
By using the relation between computational and Pauli elements (Eq.
\ref{PauToComp}), we have
\begin{align*}
 \mathcal{D} & = \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu}(-1)^{\mu m}  \left( \frac{1}{2}\sum_{k=0}^{1} (-1)^{kj}\kket{\sigma_{km}}\right)\left(\frac{1}{2}\sum_{n=0}^{1} (-1)^{n(j\oplus\nu)}\bbra{\sigma_{nm}}\right),\\
 & = \frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
 & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
 & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} (2\delta_{kn}) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
 & = \frac{1}{4}\sum_{mn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \ddyad{\sigma_{nm}}{\sigma_{nm}},\\
 & = \frac{1}{2}\sum_{mn} \left(\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu}\right) \ddyad{\sigma_{nm}}{\sigma_{nm}},
% \label{Choi_a1}
\end{align*}
Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
\begin{equation}
\lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
\end{equation}
or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes
H$ and $H$ is the Hadamard matrix.

\afnote{Queda faltando pasar a limpio la generalizacion para $N$ qubits.}

% }}}

### 2021-09-29 documentos/vector_space.tex
For the statistics only

@@
-\subsection{Parte de Francois} % {{{
-
-We have the matrix 
-\begin{equation}
-\sa=\left(
-\begin{array}{cccc}
-1 &1 &1   &1   \\
- 1 & 1  & -1&-1   \\
-1  & -1  & 1 & -1\\
-1&-1&-1&1  
-\end{array}
-\right)=\frac12\sa^{-1}.
-\label{eq:1}
-\end{equation}
-and further define the matrix
-\begin{equation}
-\san=\left(\sa\right)^{\otimes N}
-\label{eq:1a}
-\end{equation}
-% }}}
 \subsection{A vector space of channels} % {{{
@@
 $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
-\sa_{\alpha_N\beta_N}$. Using the fact that $a=a^{-1/2}$ (so
+\sa_{\alpha_N\beta_N}$. Using the fact that $a=a^{-1/2}$ \cpnote{ojo cno factores
+globales, depende de la definicion de la $a$ y $A$} (so
 $A = A^{-1}/2^N$) we can directly invert \eref{eq:A:tau:is:p} 
@@
 complete positivity of the underlying channel. 
-
-% We shall essentially use the fact that
-% 
-% 
-% 
-% It results convenient to express the 
-% previous equation in  
-%
-
-% We look for those vectors $\vec\tau$ consisting of 0's and 1's such that 
-% \begin{equation}
-% \san\vec\tau=2^N\vec p
-% \label{eq:3}
-% \end{equation}
-% where $\vec p$ is a vector with positive entries. Here $\vec\tau$ is a $4^N$ dimensional vector of 0's
-% and 1's. We number the entries of $\vec\tau$ 
-% by the multi-indices $\vec\alpha=(\alpha_1,\ldots,\alpha_N)$ where $0\leq\alpha_k\leq3$.
-% The entries of the positive vector are given by $2^Np_{\vec\alpha}$. It then follows that 
-% the expression (\ref{eq:3}) satisfies
-% \begin{equation}
-% \left(
-% \san_{\vec\alpha\vec\beta}
-% \right)
-% \tau_\beta=2^Np_{\vec\alpha}
-% \label{eq:4}
-% \end{equation}
-% where
-% \begin{equation}
-% \left(
-% \san_{\vec\alpha\vec\beta}
-% \right)=\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
-% \label{eq:5}
-% \end{equation}
-% 
-% From (\ref{eq:4}) immediately follows, via (\ref{eq:1})
-% \begin{equation}
-% \tau_\alpha=\left(
-% \san_{\vec\alpha\vec\beta}
-% \right)p_\beta
-% \label{eq:6}
-% \end{equation}
-% which we analyze iteratively. We shall essentially use the fact that
-% \begin{equation}
-% p_{\vec\alpha}+p_{\vec\beta}=0\quad\Leftrightarrow\quad p_{\vec\alpha}=p_{\vec\beta}=0
-% \label{eq:7}
-% \end{equation}
 % }}}
 
-Now we need a definition: to each multi-index $\vec\alpha$ we associate a {\em set\/}
+Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
 of multi-indices $\Phi(\vec\alpha)$ as follows
@@
 \vec\beta:\san_{\vec\alpha\vec\beta}=1
-\right\}=\left\{
-\vec\beta:
-\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
-=1
 \right\}
+% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
+% =1
+% \right\}
 \label{eq:8}

### 2021-10-04 documentos/math.tex
I have no idea what I'm doing here.

@@
 \end{equation}
-% 
 where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
@@
 given by
-% 
 \begin{equation}
@@
 \end{equation}
-%
 As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in terms of tensor products of Pauli matrices
-% 
 \begin{equation}
@@
 \end{equation}
-% 
 After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
-%
 \begin{equation}
@@
 \end{equation}
-% 
 with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
-% 
 \begin{equation}
- \lambda_{\vec{\alpha}} = \sum_{\vec{\beta}} \san_{\vec{\alpha}\vec{\beta}}\tau_{\vec{\beta}},
+ \lambda_{\valpha} = \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
+\label{eq:lambda:is:A:tau}
 \end{equation}
-%
 where 
-% 
 \begin{equation}

### 2021-10-04 documentos/vector_space.tex
I have no idea what I'm doing here.

@@
 The problem of determining complete positivity of a PCE can be recast as 
-determining which vectors $\vec \tau$ are mapped via
+determining which vectors $\vtau$ are mapped via
 $\san$
@@
 % \end{equation}
-to a positive vector $\vec p$. In compontents, this would read 
+to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
+% . In components, this would read 
+% \begin{equation}
+% % \left(
+% \sum_\vbeta
+% \san_{\valpha\vbeta} \,
+% % \right)
+% \tau_{\vec \beta}=2^Np_{\vec\alpha}
+% \label{eq:A:tau:is:p}
+% \end{equation}
+% where
+% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
+% \sa_{\alpha_N\beta_N}$. 
+Using the fact that $a^{-1}=a/4$, so 
+\cpnote{ojo cno factores globales, depende de la definicion de la $a$} 
+% (so $A = A^{-1}/2^N$) 
 \begin{equation}
-% \left(
-\san_{\vec\alpha\vec\beta} \,
-% \right)
-\tau_\beta=2^Np_{\vec\alpha}
-\label{eq:A:tau:is:p}
+A^{-1} = \frac{1}{4^N} A
 \end{equation}
-where
-$\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
-\sa_{\alpha_N\beta_N}$. Using the fact that $a=a^{-1/2}$ \cpnote{ojo cno factores
-globales, depende de la definicion de la $a$ y $A$} (so
-$A = A^{-1}/2^N$) we can directly invert \eref{eq:A:tau:is:p} 
-and obtain 
+we can directly invert \eref{eq:lambda:is:A:tau} to obtain (in matrix form)
 \begin{equation}
-\tau_\alpha=
-% \left(
-\san_{\vec\alpha\vec\beta} \,
-% \right)
-p_\beta,
+% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
+% \tau = 
+\san \lambda
+=4^N \tau
 \label{eq:tau:is:A:p}
 \end{equation}
-which will serve as a starting point for our analysis. Other simple but crucial
-observation that we shall use is that, for valid quantum channels, 
-$p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
-all $p_{\vec\alpha} \ge 0$ due to 
-complete positivity of the underlying channel. 
+\cpnote{me da diferente el factor global que al resto de la banda}
+which will serve as a starting point for our analysis. 
+\cpnote{resaltar aca la importancia de esa ecuacion, y que se aplica
+para cualquier canal diagonal de Pauli}
+Other two simple but crucial
+observation are the following. For valid quantum channels, 
+% \begin{equation}
+% % \sum_{
+% \end{equation}
+$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
+$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
+greater or equal to zero, 
+% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
+% all $p_{\vec\alpha} \ge 0$
+due to complete positivity of the underlying channel. 
+Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
+account the normalization condition that $\tau_{\vec 0}=1$, we obtain
+\begin{equation}
+\sum_\valpha \lambda_\valpha = 4^N,
+\label{eq:sum:alpha:is:4N}
+\end{equation}
+since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. 
 % }}}
@@
 \end{equation}
-If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting the two combined equations
-\begin{subequations}
+If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
+\eref{eq:sum:alpha:is:4N} from 
+% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
+% normalizacion chido y ver el motivo}), and 
+$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=4^N$ 
+(which follows from the aforementioned assumption), 
+% \begin{subequations}
+% \begin{eqnarray}
+% \sum_{\vec\beta}p_{\vec\beta}&=&1
+% \label{eq:9a}\\
+% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
+% \end{eqnarray}
+% \label{eq:9}
+% \end{subequations}
+% that for all $\vec\beta\notin\Phi(\vec\alpha)$
 \begin{eqnarray}
-\sum_{\vec\beta}p_{\vec\beta}&=&1
-\label{eq:9a}\\
-\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
-\end{eqnarray}
-\label{eq:9}
-\end{subequations}
-that for all $\vec\beta\notin\Phi(\vec\alpha)$
-\begin{eqnarray}
-p_{\vec\beta}=0.
+\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
 \label{eq:10}
@@
 Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
-and $\tau_{\vec{\gamma^\prime}}$ are equal if, for all $\vec\beta\in\Phi(\vec\alpha)$.
+and $\tau_{\vec{\gamma^\prime}}$ are equal if
+% , for all $\vec\beta\in\Phi(\vec\alpha)$.
 \begin{equation}
-\san_{\vec\beta\vec\gamma}=\san_{\vec\beta\vec{\gamma^\prime}}
+\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
+\forall \vec\beta\in\Phi(\vec\alpha).
 \label{eq:11}
 \end{equation}
-holds for all $\vec\beta\in\Phi(\vec\alpha)$. This follows from (\ref{eq:6}) as well as the fact that, due 
+% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
+This follows from (\ref{eq:6}) as
+well as the fact that, due 
 to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.

### 2021-10-06 documentos/vector_space.tex
<!DOCTYPE html><html><head><title>Unable to Connect</title><style type="text/css">*{font-family: "Open Sans", sans-serif; color: rgb(101, 102, 106)}body{padding-left: 50px; background-color: #f7f7f7;}h1{font-size: 48px; font-weight: 100; letter-spacing: 0.025em}h2{font-size: 28px; font-weight: 100; letter-spacing: 0.01em}p{font-size: 13px; font-weight: 300; letter-spacing: 0.08em line-height: 1.4;}</style></head><body><h1>Error accessing site</h1><h2>Unable to Connect</h2><p>The requested site&#39;s DNS address could not be found.</p></body></html>
It's 2016; why are we using ColdFusion?!

@@
 Using the fact that $a^{-1}=a/4$, so 
-\cpnote{ojo cno factores globales, depende de la definicion de la $a$} 
 % (so $A = A^{-1}/2^N$) 
@@
 \end{equation}
-we can directly invert \eref{eq:lambda:is:A:tau} to obtain (in matrix form)
+we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
 \begin{equation}
@@
 % \tau = 
-\san \lambda
-=4^N \tau
+% \san \lambda =2^N \tau
+\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
 \label{eq:tau:is:A:p}
 \end{equation}
-\cpnote{me da diferente el factor global que al resto de la banda}
 which will serve as a starting point for our analysis. 
@@
 \begin{equation}
-\sum_\valpha \lambda_\valpha = 4^N,
-\label{eq:sum:alpha:is:4N}
+\sum_\valpha \lambda_\valpha = 2^N,
+\label{eq:sum:alpha:is:2N}
 \end{equation}
@@
 If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
-\eref{eq:sum:alpha:is:4N} from 
+\eref{eq:sum:alpha:is:2N} from 
 % $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
 % normalizacion chido y ver el motivo}), and 
-$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=4^N$ 
+$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
 (which follows from the aforementioned assumption), 
@@
 \lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
-\label{eq:10}
+\label{eq:condition:lambda:zero:Phi}
 \end{eqnarray}
@@
 \forall \vec\beta\in\Phi(\vec\alpha).
-\label{eq:11}
+\label{eq:coneccion:dos:indices:A}
 \end{equation}
 % holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
-This follows from (\ref{eq:6}) as
-well as the fact that, due 
-to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
+This follows from restricting the sum \eref{eq:tau:is:A:p}
+to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}.
 
-% If this condition is fulfilled and $\tau_{\vec\alpha}=1$, then
-%\begin{subequations}
-%\begin{eqnarray}
-%\tau_{\vec\gamma}&=&\sum_{\vec\beta}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
-%\label{eq:10na}
-%\\
-%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec\gamma}p_{\vec\beta}
-%\label{eq:10nb}
-%\\
-%&=&\sum_{\vec\beta\in\Phi(\vec\alpha)}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
-%\label{eq:10nc}
-%\\
-%&=&\sum_{\vec\beta}\left(
-%M^{\otimes N}
-%\right)_{\vec\beta\vec{\gamma^\prime}}p_{\vec\beta}
-%\label{eq:10nd}
-%\\
-%&=&\tau_{\vec{\gamma^\prime}}
-%\label{eq:10ne}
-%\end{eqnarray}
-%\label{eq:10n}
-%\end{subequations}
-%Here the transition from (\ref{eq:10na}) to (\ref{eq:10nb}) follows from (\ref{eq:10}), from (\ref{eq:10nb}) to (\ref{eq:10nc})
-%follows from (\ref{eq:11}), from (\ref{eq:10nc}) to  (\ref{eq:10nd}) follows again from (\ref{eq:10}).
+% 
+% This follows from (\ref{eq:6}) as
+% well as the fact that, due 
+% to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
 
-Condition (\ref{eq:11}) therefore connects three multi-indinces, $\vec\alpha$, $\vec\gamma$ and $\vec{\gamma^\prime}$.
+Condition (\ref{eq:11}) therefore connects three multi-indices, $\vec\alpha$,
+$\vec\gamma$ and $\vec{\gamma^\prime}$.
 When such a connection exists, $\tau_{\vec\alpha}=1$ implies
-$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature of this connection.
+$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
+of this connection. \cpnote{I think that this paragraph can go. }
 
-Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
+Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
+of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
+as
 \begin{equation}
-\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
+= 
+\san_{\valpha\vbeta} 
+, \quad
+\forall \vec\beta\in\Phi(\vec\alpha),
 \label{eq:12}
 \end{equation}
-This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that (\ref{eq:12}) may be rewritten as
+which can be further decomposed in 
 \begin{equation}
-\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
-\sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
+\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
+  \ldots
+%   \cdot\ldots\cdot 
+\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
+\sa_{\alpha_1\beta_1}
+  \ldots
+% \cdot\ldots\cdot
+ \sa_{\alpha_N\beta_N}.
 \label{eq:13}
 \end{equation}
+% Moreover, since 
+% 
+% 
+% 
+% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
+% \begin{equation}
+% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+% \label{eq:12}
+% \end{equation}
+% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
+% (\ref{eq:12}) may be rewritten as
+% \begin{equation}
+% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
+% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
+% \label{eq:13}
+% \end{equation}
 Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
-the above relation must hold individually for every index. Thus we have, 
+the above relation must hold individually for every index\cpnote{francois, recuerdo 
+que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
+proque se tiene que cumplir para los indices individulaes}. Thus we have, 
 that, for all $1\leq k\leq N$, $\gamma_k$
@@
 \end{equation}
-where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure \ref{tab:1} for a detailed description.
+where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure
+\ref{tab:1} for a detailed description. \cpnote{by direct calculation I can verify 
+that its true, but I see it as a coincidence. Is they ere a say to know
+that \eref{eq:14} will lead to a sum?}
 
-\begin{figure}
+\begin{figure} % {{{
 \begin{center}
@@
 \end{tabular}
-\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that the operation
-is an {\em abelian group}, in fact it corresponds to the {\em Klein group}, where the
-neutral element is $0$. This is the reason for choosing an additive notation for the operation
-defined in (\ref{eq:14}).
-}
+\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that
+the operation is an {\em abelian group}, in fact it corresponds to the {\em
+Klein group}, where the neutral element is $0$. This is the reason for choosing
+an additive notation for the operation defined in (\ref{eq:14}).  }
 \label{tab:1}
 \end{center}
-\end{figure}
+\end{figure} % }}}
 
@@
 binary arithmetic. If we therefore denote by $\overline{\alpha}$
-the multi-index $\vec\alpha$ converted to a binary vector by the componentwise application of (\ref{eq:ident}),
+\cpnote{I dont think this is necesary. specially if we will write something
+else}
+the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
+application of (\ref{eq:ident}),
 the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
@@
 
-From this readily follows an amusing property: the set of all multi-indices $\overline\gamma$
-for which $\tau_{\overline\gamma}=1$\cpnote{I guess instead of overline, we want 
-to use arrow, or this denotes something else?}, is closed under binary vector addition, in other words, it
-forms a {\em vector subspace\/} of the set of all multi-indices. Indeed, let
-$\overline\alpha$ and $\overline\gamma$ belong to that set. Then if 
+From this readily follows an amusing property: the set of all multi-indices
+$\overline\gamma$ for which $\tau_{\overline\gamma}=1$, is closed under binary
+vector addition, in other words, it forms a {\em vector subspace\/} of the set
+of all multi-indices. Indeed, let $\overline\alpha$ and $\overline\gamma$
+belong to that set. Then if 
 \begin{equation}

### 2021-10-06 documentos/vector_space.tex
I'm just a grunt. Don't blame me for this awful PoS.

@@
 \end{equation}
-for all $0\leq\beta\leq3$. This is equivalently expressed as 
+for all $0\leq\beta\leq3$. One can verify, by working out the different cases, 
+that \eref{eq:14} equivalently expressed as 
 \begin{equation}
@@
 \end{equation}
-where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure
-\ref{tab:1} for a detailed description. \cpnote{by direct calculation I can verify 
-that its true, but I see it as a coincidence. Is they ere a say to know
-that \eref{eq:14} will lead to a sum?}
+where the $\oplus{}$ denotes the operation of the Kein group; see Figure
+\ref{tab:1} for a detailed description. 
+% \cpnote{by direct calculation I can verify 
+% that its true, but I see it as a coincidence. Is they ere a say to know
+% that \eref{eq:14} will lead to a sum?}
+
+\cpnote{
+It will be useful to think of the multi-index $\valpha$ as an element of 
+a vector space. To do so, we notice that any group with the property that
+$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
+$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
+with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
+\beta_1,\cdots, \alpha_N \oplus \beta_N)$. From this view 
+we can derive several interesting observations that will be presented in 
+the rest of the section. 
+}
 
@@
 
+\cpnote{Propongo quitar desde aca}
 Note further that if we perform the identification
@@
 where the addition sign here refers to ordinary binary vector addition. 
+\cpnote{Hasta aca}
 

### 2021-10-14 documentos/notas/wce.tex
Actualización para presentación reunión mie 13.10

@@
 \usepackage{amssymb}
+\usepackage{physics}
+
+%% commands
+\newcommand{\alphas}{\vec\alpha}
 
@@
 
+\section{Generalization \boldmath{$\oplus$}}
+\subsection{New notation for \boldmath{$\alphas$} and definition of \boldmath{$\oplus$}}
+We will rewrite the multi-indices $\alphas$ using base-$d$ numeral system 
+and will re-define the operation $\oplus$, previously associated by François with the 
+Klein group.
+Every index in the multi-indices $\alphas$ of a WCE quantum channel 
+can be written as a length-2 list with its base-$d$ numeral system digits. 
+Therefore, every index $\alpha_i$ in $\alphas$ can be written as
+\begin{align}
+	\alpha_i=\qty( \alpha_{i_1},\alpha_{i_2} ).
+\end{align}
+The multi-indices $\alphas$ then reads
+\begin{align}\label{eq:alphas_base-d}
+	\alphas=\qty{ \qty( \alpha_{1_1},\alpha_{1_2} ),\ldots,\qty( \alpha_{N_1},\alpha_{N_2} ) }.
+\end{align}
+We define the sum of two multi-indices $\vec\alpha$ and $\vec\beta$ as 
+\begin{align}\label{eq:oplus_generalized}
+	\vec\alpha\oplus\vec\beta=
+	\qty{ \qty( \alpha_{1_1}\oplus\beta_{1_1},\alpha_{1_2}\oplus\beta_{1_2} ),
+	\ldots,
+	\qty( \alpha_{N_1}\oplus\beta_{N_1},\alpha_{N_2}\oplus\beta_{N_2} ) 
+	 },
+\end{align}
+where operation $\oplus$ is the sum modulo $d$.
+
+\subsection{Examples}
+Let us look at some examples. First, let us discuss a familiar example with a PCE 
+quantum channel.
+The set of multi-indices associated with the PCE quantum channel of 
+Fig. \ref{fig:two_qubits_PCEChann_01}
+are, in decimal basis, $\{(0,0),(1,1),(2,1),(3,0) \}$. The same multi-indices
+written in binary basis are 
+$$\qty{ \{(0,0),(0,0)\}, \{(0,1),(0,1)\}, \{(1,0),(0,1)\}, \{(1,1),(0,0)\} }.$$
+Let us sum $(2,1)\oplus(1,1)$ as previously defined by François
+\begin{align}
+	(2,1)\oplus(1,1)=(2\oplus 1,1\oplus 1)=(3,0).
+\end{align}
+Now, let us sum the same two multi-indices, written in binary basis, using
+the definition \eqref{eq:oplus_generalized}
+\begin{align}
+	 \{(1,0),(0,1)\}\oplus\{(0,1),(0,1)\}=\{(1\oplus0,0\oplus1),(0\oplus0,1\oplus1)\}
+	 =\qty{ (1,1),(0,0) },
+\end{align}
+which is equal to $(3,0)$ in decimal basis. This is an example that shows how 
+the operation $\oplus$ defined with the Klein group is equivalent with the new notation 
+and definition \eqref{eq:oplus_generalized}.
+
+\begin{figure}[h] 
+	\centering
+	\includegraphics[width=2cm]{two_qubits_c43}
+	\caption{A random two-qubits PCE quantum channel.}
+	\label{fig:two_qubits_PCEChann_01}
+\end{figure}
+Now, let us look at the set of multi-indices of the 
+fifth 3-level-system WCE channel in Fig. \ref{fig:weylCE_1particle_d3}:
+$\qty{ \qty{(0,0)}, \qty{(1,2)}, \qty{(2,1)} }$.
+The only three different possible sums modulo 3 are
+\begin{subequations}
+\begin{align}
+	(0,0)\oplus(1,2)&=(0\oplus1,0\oplus2)=(1,2)\\
+	(0,0)\oplus(2,1)&=(0\oplus2,0\oplus1)=(2,1)\\
+	(1,2)\oplus(2,1)&=(1\oplus2,2\oplus1)=(0,0)
+\end{align}
+\end{subequations}
+Then, the set of multi-indices $\alphas$ is closed. 
+As the last example, let us check the closure of the set of multi-indices of the 
+tenth 4-level-system WCE channel in Fig \ref{fig:weylCE_1particle_d4}:
+$\qty{ \qty{(0,0)}, \qty{(1,2)}, \qty{(2,0)}, \qty{(3,2)} }$
+The only six different possible sums modulo 4 are
+\begin{subequations}
+\begin{align}
+	(0,0)\oplus(1,2)&=(1,2)\\
+	(0,0)\oplus(2,0)&=(2,0)\\
+	(0,0)\oplus(3,2)&=(3,2)\\
+	(1,2)\oplus(2,0)&=(3,2)\\
+	(1,2)\oplus(3,2)&=(0,0)\\
+	(2,0)\oplus(3,2)&=(1,2),
+\end{align}
+\end{subequations}
+then the set of multi-indices is closed.
+
+\subsection{Hypothesis}
+The set of multi-indices of a $N$-qudits WCE quantum channel, 
+written in base-$d$ numeral system as in \eqref{eq:alphas_base-d},
+is closed under sum modulo $d$ as defined in \eqref{eq:oplus_generalized}.
+There are numerical results that support this hypothesis. The method of brute
+force has been implemented to check if all sets of a
+multi-indices of 3, 4 and partially 5-level system WCE quantum channels 
+are closed under $\oplus$ as defined in \eqref{eq:oplus_generalized}.
+The converse has been numerically analyzed with the method of brute force too.
+All sets of multi-indices that are closed under the operation $\oplus$ are
+associated with a WCE quantum channel. All of this shows clues that a vector 
+structure exists as in the case of PCE quantum channels.
+
 \end{document}

### 2021-10-14 documentos/vector_space.tex
oops

@@
 % \end{itemize} % }}}
-
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
@@
 \end{equation}
-since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. 
+since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
 % }}}
-
+% Conexion de los indices para llegar al grupo de Klein {{{
 Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
@@
 \gamma_k^\prime=\alpha\oplus{}\gamma_k
-\label{eq:15}
+\label{eq:oplus}
 \end{equation}
@@
 \ref{tab:1} for a detailed description. 
+% \cpnote{Quiza poner una relacion como $\tau_{\vgamma}=\tau_{\valpha\oplus{}\vgamma}$}
+
+\par
 % \cpnote{by direct calculation I can verify 
@@
 % that \eref{eq:14} will lead to a sum?}
+% }}}
 
-\cpnote{
 It will be useful to think of the multi-index $\valpha$ as an element of 
@@
 with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
-\beta_1,\cdots, \alpha_N \oplus \beta_N)$. From this view 
+\beta_1,\cdots, \alpha_N \oplus \beta_N)$. 
+We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
+if $\tau_{\vec\alpha}=1$, then
+$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
+From this view 
 we can derive several interesting observations that will be presented in 
 the rest of the section.
-}
 
@@
 
-\cpnote{Propongo quitar desde aca}
-Note further that if we perform the identification
-\begin{subequations}
-\begin{eqnarray}
-0&\to&(0,0)\label{eq:identa}\\
-1&\to&(0,1)\label{eq:identb}\\
-2&\to&(1,0)\label{eq:identc}\\
-3&\to&(1,1)\label{eq:identd}
-\end{eqnarray}
-\label{eq:ident}
-\end{subequations}
-then the $\oplus$ operation reduces to simple vector addition in
-binary arithmetic. If we therefore denote by $\overline{\alpha}$
-\cpnote{I dont think this is necesary. specially if we will write something
-else}
-the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
-application of (\ref{eq:ident}),
-the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
-as
-\begin{equation}
-\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
-\label{eq:17}
-\end{equation}
-where the addition sign here refers to ordinary binary vector addition. 
-\cpnote{Hasta aca}
+% % Lo que quiero quitar {{{
+% \cpnote{Propongo quitar desde aca}
+% Note further that if we perform the identification
+% \begin{subequations}
+% \begin{eqnarray}
+% 0&\to&(0,0)\label{eq:identa}\\
+% 1&\to&(0,1)\label{eq:identb}\\
+% 2&\to&(1,0)\label{eq:identc}\\
+% 3&\to&(1,1)\label{eq:identd}
+% \end{eqnarray}
+% \label{eq:ident}
+% \end{subequations}
+% then the $\oplus$ operation reduces to simple vector addition in
+% binary arithmetic. If we therefore denote by $\overline{\alpha}$
+% \cpnote{I dont think this is necesary. specially if we will write something
+% else}
+% the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
+% application of (\ref{eq:ident}),
+% the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
+% as
+% \begin{equation}
+% \overline\gamma=\overline\alpha+\overline{\gamma^\prime}
+% \label{eq:17}
+% \end{equation}
+% where the addition sign here refers to ordinary binary vector addition. 
+% \cpnote{Hasta aca}
+% % }}}
 
 From this readily follows an amusing property: the set of all multi-indices
-$\overline\gamma$ for which $\tau_{\overline\gamma}=1$, is closed under binary
-vector addition, in other words, it forms a {\em vector subspace\/} of the set
-of all multi-indices. Indeed, let $\overline\alpha$ and $\overline\gamma$
-belong to that set. Then if 
-\begin{equation}
-\overline{\gamma^\prime}=\overline\alpha+\overline\gamma
-\label{eq:14b}
-\end{equation}
-then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
-and thus equal to one.
+$\vec\gamma$ for which $\tau_{\vec\gamma}=1$, is closed under binary
+vector addition, in other words, it forms a vector subspace of the set
+of all multi-indices.
+A moment's consideration will further show that the above reasoning can be
+inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
+whenever the $\vec\gamma$ belong to a given vector subspace of the set of
+all indices, then the vector $\vec\tau$ indeed has an image which is a vector
+with only positive components. 
+In other words, there is a one to one correspondence between 
+a valid quantum channel, and a vector subspace of the aforementioned space. 
+\cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
+figura en la que se tenga algo que es un canal y algo que no es  un canal. 
+Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
+depolarizante y el subespacio mas grande es la identidad}
 
-So we may now proceed to generate all solutions: we start out from the solution having $\tau_{\vec0}=1$, with
-everything else $0$. We may then successively switch $\tau$'s to $1$ for various values of $\vec\alpha$, 
-taking care immediately to set equal to one the values of $\tau$ that correspond to values of $\vec\beta$
-generated by the previously switched values of $\vec\alpha$ via (\ref{eq:11}).
+% Indeed, let $\overline\alpha$ and $\overline\gamma$
+% belong to that set. Then if 
+% \begin{equation}
+% \overline{\gamma^\prime}=\overline\alpha+\overline\gamma
+% \label{eq:14b}
+% \end{equation}
+% then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
+% and thus equal to one.
 
-A moment's consideration will further show that the above reasoning can be inverted, that is, that if we
-set all $\tau_{\overline\gamma}$ equal to one whenever the $\overline\gamma$ belong to a given vector 
-subspace of the set of all indices, then the vector $\vec\tau$ indeed has an image which is a vector with 
-only positive components.
+So we may now proceed to generate all solutions: we start out from the solution
+having $\tau_{\vec0}=1$, with everything else $0$. We may then successively
+switch $\tau$'s to $1$ for various values of $\valpha$, taking care
+immediately to set equal to one the components of $\tau$ that correspond to values
+of $\vbeta$ generated by the previously switched values of $\valpha$ via the
+operation $\oplus$. Doing so, in an ordered way allows one to general 
+all valid quantum channels with given preserved components, without the need
+of exploring the exponentially large space of PCE. 
+% (\ref{eq:11}).
 
-%Now everything follows with delightful simplicity. First extend the $\oplus{}$ operation to vectors 
-%componentwise
+% Procesado pero No lo entiendo/no lo quiero poner {{{
+
+% }}}}
+
+%
+%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$,
+%nor to any site that is automatically equal to $\tau_{\alp1}$. Set
+%$\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
+%since the two are equal because of (\ref{eq:18}). By the same reasoning that
+%led to (\ref{eq:18}), we now find that 
 %\begin{equation}
-%\vec\alpha\oplus{}\vec\beta=(\alpha_1\oplus{}\beta_1,\ldots,\alpha_N\oplus{}\beta_N).
-%\label{eq:16}
-%\end{equation}
-%Remark, as a useful fact, that the inverse under $\oplus$ of any number $\alpha$ is $\alpha$ itself.
-
-%If $\tau_{\vec\alpha}=1$, then it follows from the above that 
-%for all $\gamma$
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}.
-%\label{eq:17}
-%\end{equation}
-
-%Now take an arbitrary $\vec{\alpha}_1$ and set $\tau_{\vec{\alpha}_1}=1$. This immediately imposes the
-%relationship
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}
-%\label{eq:18}
-%\end{equation}
-%which to every $\vec\gamma$ assigns exactly one other multi-index such that the corresponding values of $\tau$
-%must be equal. Note that (\ref{eq:18}) is vacuous when applied to $\gamma=\alp1$: indeed $\alp1\oplus\alp1=\vec0$,
-%and $\tau_{\vec0}$ is one by convention. 
-%
-%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$, nor to any site
-%that is automatically equal to $\tau_{\alp1}$. Set $\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
-%since the two are equal because of (\ref{eq:18}). By the same reasoning that led to (\ref{eq:18}), we now find that 
-%\begin{equation}
-%\tau_{\vec\gamma}=\tau_{\alp1\oplus{}\vec\gamma}=\tau_{\alp2\oplus{}\vec\gamma}=\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
+%\tau_{\vec\gamma} = \tau_{\alp1\oplus{}\vec\gamma}
+%     =\tau_{\alp2\oplus{}\vec\gamma}
+%     =\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
 %\label{eq:19}
 %\end{equation}
-%Thus we find that the $\tau$'s are now constant over domains of $4$, as opposed to $2$ previously, when only one
-%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$. Further, it follows from the group property
-%of $\oplus$ that the different domains are {\em disjoint}. The 3 multi-indices associated to a given $\vec\gamma$ are never associated
-%to any other $\vec{\gamma^\prime}$. 
+%Thus we find that the $\tau$'s are now constant over domains of $4$, as
+%opposed to $2$ previously, when only one
+%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$.
+%Further, it follows from the group property of $\oplus$ that the different
+%domains are {\em disjoint}. The 3 multi-indices associated to a given
+%$\vec\gamma$ are never associated to any other $\vec{\gamma^\prime}$. 
 %
-%After adding $\alp1$, we have at least 2 sites equal to 1, after adding $\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$. 
-%Clearly, at each addition, the total number doubles. This shows the $2^k$ rule. 
+%After adding $\alp1$, we have at least 2 sites equal to 1, after adding
+%$\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$.  Clearly, at
+%each addition, the total number doubles. This shows the $2^k$ rule. 
 %
-%How far can this process go? Well, the total number of multi-indices is $4^N$, so this can go on until $2\cdot4^{N-1}$ sites are occupied,
-%in other words, we may double $2N-1$ times.
+%How far can this process go? Well, the total number of multi-indices is $4^N$,
+%so this can go on until $2\cdot4^{N-1}$ sites are occupied, in other words, we
+%may double $2N-1$ times.
 %
-%Now to show that the maximal solutions are generators, that is, that all solutions can be expressed as intersections of maximal 
-%solutions, that is, solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by the successive adjunction
-%of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to the group property, the final solution generated does not depend on the order
+%Now to show that the maximal solutions are generators, that is, that all
+%solutions can be expressed as intersections of maximal solutions, that is,
+%solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by
+%the successive adjunction of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to
+%the group property, the final solution generated does not depend on the order
 %of the $\alp{k}$. 
 %
-%Now let us consider a solution with half the number of elements of a maximal solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$. 
-%At this stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and there are a total of $4^{N-1}$ 1's. 
-%There are thus 2 inequivalent remaining domains where I could put the final $\alp{2N-1}$. These 2 different choices yield disjoint
-%maximal solutions, the intersection of which yields the solution with half the number of elements of the maximal solution. 
-%Every solution one step away from maximal can thus be expressed (uniquely) as the intersection of 2 maximal solutions. 
+%Now let us consider a solution with half the number of elements of a maximal
+%solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$.  At this
+%stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and
+%there are a total of $4^{N-1}$ 1's.  There are thus 2 inequivalent remaining
+%domains where I could put the final $\alp{2N-1}$. These 2 different choices
+%yield disjoint maximal solutions, the intersection of which yields the
+%solution with half the number of elements of the maximal solution.  Every
+%solution one step away from maximal can thus be expressed (uniquely) as the
+%intersection of 2 maximal solutions. 
 %
-%Arguing inductively backwards, the same result can be shown for arbitrary solutions. We therefore have shown both the $2^k$ 
-%rule and the fact that all solutions are expressible uniquely as intersections of maximal solutions.
+%Arguing inductively backwards, the same result can be shown for arbitrary
+%solutions. We therefore have shown both the $2^k$ rule and the fact that all
+%solutions are expressible uniquely as intersections of maximal solutions.
 
-The dimension of the vector space $V$ of all multi-indices is $2N$, and we have seen earlier that
+The dimension of the vector space $V$ of all multi-indices is $2N$, and we have
+seen earlier that
 \begin{equation}

### 2021-10-14 documentos/generators.tex
See last commit
Well, it's doing something.

--- 2021-08-23 documentos/generators.tex
@@
 \section{Generators} % {{{
+\todo{Francois escribe una primera version del primer punto, y luego quizá Jose
+Alfredo o Carlos la terminan}
+
+By standard theorems of linear algebra, any subspace $W$ can be extended to a
+maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
+additional basis elements. This can clearly be done in different ways. We
+therefore arrive to the set of maximal extensions of $W$. Clearly, the
+intersection of all the elements of this set reduces to $W$ itself, leading to
+the result that all PCE's can be obtained as intersections of maximal PCE's.
+
+Quizá poner las reglas de simetría de los generadores.
+
+Quizá en un apendice poner todos los generadores de dos qubits.
+
+También poner como se pueden calsificar los generadores y por aih poner la clasificacion de los 
+generadores en la figura.  o en el texto
+
 \begin{itemize}

### 2021-10-14 documentos/vector_space.tex
Well, it's doing something.

@@
 \subsection{A vector space of channels} % {{{
-% \begin{itemize} % {{{ Cosas por escribir aca
-% \item Canales PCE como espacios vectoriales \todo{Francois escribe}
-% \item Regla de $2^k$
-% \item Tamaño de las diferentes clases que borran un numero fijo de componentes
-% y tambien nota de qeu son igual entre complementarios: computo del numero de
-% bases dada una dimension de subespacios vectoriales, aqui entra la formula del
-% binomial-q. \todo{Esperemos que evolucione mas el articulo y luego vemos que ponemos}
-% \item Intento de identificar elementos, aka hermanistos PCE \cpnote{Esto dependerá de si sale algo interesante,}: De entrada aqui se tiene que mencionar minimo la identificacion del tamaño de las clases.
-% \item \ddnote{Agrego esto:} A final remarks of the derivation as a tool.
-% Concepts might be complicated, but the tool gives some simple rules to the
-% reader: \textit{tell me what components you want to keep, and the (vector)
-% summation rules will give you the rest of components to make the target
-% operation a CPTP one.}
-% \end{itemize} % }}}
+\cpnote{Quiza falta lo de las clases de equivalencias}\par
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
@@
 which will serve as a starting point for our analysis. 
-\cpnote{resaltar aca la importancia de esa ecuacion, y que se aplica
-para cualquier canal diagonal de Pauli}
+This is a remarkable equation, as it provides a method to diagonalize any diagonal 
+Pauli channel, as in \eref{eq:definition:Pauli}.
+
 Other two simple but crucial
@@
 to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
-
-% 
-% This follows from (\ref{eq:6}) as
-% well as the fact that, due 
-% to (\ref{eq:10}), we only need sum over $\vec\beta\in\Phi(\vec\alpha)$.
-
-Condition (\ref{eq:11}) therefore connects three multi-indices, $\vec\alpha$,
+Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
 $\vec\gamma$ and $\vec{\gamma^\prime}$.
@@
 $\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
-of this connection. \cpnote{I think that this paragraph can go. }
+of this connection.
 
@@
 % \cpnote{Quiza poner una relacion como $\tau_{\vgamma}=\tau_{\valpha\oplus{}\vgamma}$}
-
 \par
@@
 % }}}
+% Espacio vectorial {{{
 
@@
 with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
-\beta_1,\cdots, \alpha_N \oplus \beta_N)$. 
+\beta_1,\cdots, \alpha_N \oplus \beta_N)$
+\footnote{
+We can further \cpnote{desmechar} the vector space, by identifying each index
+$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
+such that to each multindex  $\valpha$ there corresponds a binary string of 
+length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
+each of the $2N$ components. 
+\cpnote{maybe its not necesary}
+}. 
 We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
@@
 $\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
-From this view 
+% \cpnote{Creo que aca podemos referenciar la figura 2c y mostrar como
+% funcionaria que no es cerrada bajo la suma}
+For example, in \fref{fig:two:qubit:examples}(c) the indices that 
+correspond to preserved components are 
+$\valpha^{(0)} = (0,0)$, 
+$\valpha^{(1)} = (0,2)$, 
+$\valpha^{(2)} = (1,0)$, 
+$\valpha^{(3)} = (2,2)$, and
+$\valpha^{(4)} = (3,2)$. However, 
+$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preseverd and thus this 
+diagram does not correspond to a quantum channel.  From this view 
 we can derive several interesting observations that will be presented in 
@@
 Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
-depolarizante y el subespacio mas grande es la identidad}
+depolarizante y el subespacio mas grande es la identidad} \par
 
-% Indeed, let $\overline\alpha$ and $\overline\gamma$
-% belong to that set. Then if 
-% \begin{equation}
-% \overline{\gamma^\prime}=\overline\alpha+\overline\gamma
-% \label{eq:14b}
-% \end{equation}
-% then by the preceding considerations, $\tau_{\overline\gamma^\prime}$ is equal to $\tau_{\overline\gamma}$
-% and thus equal to one.
-
+% }}}
+% Generacion de soluciones {{{
 So we may now proceed to generate all solutions: we start out from the solution
@@
 of $\vbeta$ generated by the previously switched values of $\valpha$ via the
-operation $\oplus$. Doing so, in an ordered way allows one to general 
-all valid quantum channels with given preserved components, without the need
-of exploring the exponentially large space of PCE. 
-% (\ref{eq:11}).
-
-% Procesado pero No lo entiendo/no lo quiero poner {{{
-
+operation $\oplus$. Doing so, in an ordered way, allows one to general 
+all valid quantum channels with a given set of preserved components, without the need
+of exploring the exponentially large space of PCE.  \par 
 % }}}}
-
-%
-%Now choose another multi-index, say $\alp2$, which is not equal to $\alp1$,
-%nor to any site that is automatically equal to $\tau_{\alp1}$. Set
-%$\tau_{\alp2}=1$. We obviously must also set $\tau_{\alp2\oplus\alp1}=1$,
-%since the two are equal because of (\ref{eq:18}). By the same reasoning that
-%led to (\ref{eq:18}), we now find that 
-%\begin{equation}
-%\tau_{\vec\gamma} = \tau_{\alp1\oplus{}\vec\gamma}
-%     =\tau_{\alp2\oplus{}\vec\gamma}
-%     =\tau_{\alp1\oplus\alp2\alp2\oplus{}\vec\gamma}
-%\label{eq:19}
-%\end{equation}
-%Thus we find that the $\tau$'s are now constant over domains of $4$, as
-%opposed to $2$ previously, when only one
-%single $\vec\alpha$, namely $\alp1$, had been fixed to have $\tau_{\alp1}=1$.
-%Further, it follows from the group property of $\oplus$ that the different
-%domains are {\em disjoint}. The 3 multi-indices associated to a given
-%$\vec\gamma$ are never associated to any other $\vec{\gamma^\prime}$. 
-%
-%After adding $\alp1$, we have at least 2 sites equal to 1, after adding
-%$\alp2$, we have 4: $\vec0$, $\alp1$, $\alp2$, and $\alp1+\alp2$.  Clearly, at
-%each addition, the total number doubles. This shows the $2^k$ rule. 
-%
-%How far can this process go? Well, the total number of multi-indices is $4^N$,
-%so this can go on until $2\cdot4^{N-1}$ sites are occupied, in other words, we
-%may double $2N-1$ times.
-%
-%Now to show that the maximal solutions are generators, that is, that all
-%solutions can be expressed as intersections of maximal solutions, that is,
-%solutions with $2\cdot4^{N-1}$ 1's. Any maximal solution can be obtained by
-%the successive adjunction of $\alp1, \alp2,\ldots,\alp{2N-1}$. Again, due to
-%the group property, the final solution generated does not depend on the order
-%of the $\alp{k}$. 
-%
-%Now let us consider a solution with half the number of elements of a maximal
-%solution, that is, one generated by $\alp1, \alp2,\ldots,\alp{2N-2}$.  At this
-%stage, the $\tau_{\vec\alpha}$ are constant over domains of size $4^{N-1}$ and
-%there are a total of $4^{N-1}$ 1's.  There are thus 2 inequivalent remaining
-%domains where I could put the final $\alp{2N-1}$. These 2 different choices
-%yield disjoint maximal solutions, the intersection of which yields the
-%solution with half the number of elements of the maximal solution.  Every
-%solution one step away from maximal can thus be expressed (uniquely) as the
-%intersection of 2 maximal solutions. 
-%
-%Arguing inductively backwards, the same result can be shown for arbitrary
-%solutions. We therefore have shown both the $2^k$ rule and the fact that all
-%solutions are expressible uniquely as intersections of maximal solutions.
+\begin{figure} % {{{
+\begin{center}
+% Del dcumento francois.pdf pg 8 agarramos:
+% e11, e4 y E7
+\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
+\pgfmathsetmacro{\unitstep}{5.2}
+\begin{scope}[shift={(1*\unitstep,0)}] % Depolirizng channel {{{
+\node at (-0.5,0.5) {(a)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(2*\unitstep,0)}] % Interseccion {{{
+\node at (-0.5,0.5) {(b)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(3*\unitstep,0)}] % E4 {{{
+\node at (-0.5,0.5) {(c)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(1*\unitstep,-\unitstep)}] % E7 {{{
+\node at (-0.5,0.5) {(d)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(2*\unitstep,-\unitstep)}] % E11 {{{
+\node at (-0.5,0.5) {(e)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(3*\unitstep,-\unitstep)}] % Identity channel {{{
+\node at (-0.5,0.5) {(f)} ;
+    \foreach \x in {0,1,2,3} {
+      \foreach \y in {0,1,2,3} {
+        \begin{scope}[shift={(\x,-\y)}] 
+          \draw (0,0) rectangle (1,1); 
+%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+         \end{scope}
+%         \node at (0,-\y) (input\y) {$i_\y$};
+%         \node[block] at (2,-\y) (block\y) {$f_\y$};
+%         \draw[->] (input\y) -- (block\y);
+%         \draw[->] (block\y.east) -- +(0.5,0);
+    }
+    }
+\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\end{tikzpicture} % }}}
+\end{center}
+\caption{\cpnote{Mejorar el caption cuando me ponga de acuerdo con la gente}
+Aca poner 6 PCEs. (f) Identidad, (a) totally depolarizing, (c, d y e) tres
+generadores, (b) un canal que resulte del generador. Sobra un espacio para
+ilustrar alguna otra cosa. Quiza poner otro generador para que se vea que no
+hay una manera unica de generar esos bichos.}
+\label{fig:examplesPCE}
+\end{figure} % }}}
+% Los canales tiene 2^K componente {{{
+We can then see that all PCEs preserve $2^K$ components. In fact, with the above 
+picture, it is clearly revealed that the vector space has dimension $2N$. Moreover, 
+consider any subspace and chose the maximum number of linearly independent
+elements (say $K$).  Any of the  $2^K$ subsets of those elements will yield a
+unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
+elements of the vector space. This means that any PCE will preserve $2^K$ 
+components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
+\par
 
@@
 seen earlier that
+\cpnote{Why is the dimension $2N$? I can work it out, but just after adding one 
+by one elements}
 \begin{equation}
@@
 \end{equation}
-is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that $W$ has $2^K$ elements. In other words,
-a vector $\vec\tau$ with the property discussed above can only have $2^K$ elements equal to 1, for a given integer $K$.
+is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that
+$W$ has $2^K$ elements. In other words, a vector $\vec\tau$ with the property
+discussed above can only have $2^K$ elements equal to 1, for a given integer
+$K$.
 
-By standard theorems of linear algebra, any subspace $W$ can be extended to a maximal (non-trivial) subspace of dimension
-$2N-1$ by adjoining appropriate additional basis elements. This can clearly be done in different ways. We therefore arrive to
-the set of maximal extensions of $W$. Clearly, the intersection of all the elements of this set reduces to $W$ itself, leading to
-the result that all PCE's can be obtained as intersections of maximal PCE's.
-
-\ddnote{Agrego esto:} A final remarks of the derivation as a tool.
-Concepts might be complicated, but the tool gives some simple rules to the reader: \textit{tell me what components you want to keep, and the (vector) summation rules will give you the rest of components to make the target operation a CPTP one.}
+\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}
+ % }}}
+% Cuantos canales conservan $2^K$ componentes? {{{
+It is natural to ask how many PCEs exist that conserve $2^K$ components. One
+can calculate such number, $\sss_{N,K}$, by examining the number of different
+independent subsets of vectors that spawn a given vector subspace. In appendix 
+\ref{app:contar} we show that 
+\begin{equation}
+\sss_{N,K}=\prod_{m=0}^{K-1} \frac{2^{2N-m}-1}{2^{K-m}-1}.
+\label{eq:conteo:main}
+\end{equation}
+%An elementary test is $N=3$ and $K=2,3$: 
+%\begin{eqnarray}
+%\sss_{3,2}&=&\frac{(2^6-1)(2^5-1)}{(2^2-1)(2^1-1)}=\frac{63\cdot31}{3}=651,\\
+%\sss_{3,3}&=&\frac{(2^6-1)(2^5-1)(2^4-1)}{(2^3-1)(2^2-1)(2^1-1)}=\frac{63\cdot31\cdot15}{7\cdot3}=1395,
+%\end{eqnarray}
+%which are indeed the values found numerically. 
+From the above expression, it is easy to see the symmetry relation
+\begin{equation}
+\sss_{N,K}=\sss_{N,2N-K}
+\end{equation}
+which suggest an relation  between individual channels that for the time being
+has escaped our efforts to identify. 
+\par % }}}
+% Frase de David {{{
+\ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts
+might be complicated, but the tool gives some simple rules to the reader:
+\textit{tell me what components you want to keep, and the (vector) summation
+rules will give you the rest of components to make the target operation a CPTP
+one.}
+\par % }}}
 

### 2021-10-14 documentos/vector_space.tex
I'll explain when you're older!

@@
 \eref{eq:sum:alpha:is:2N} from 
-% $\sum_{\vec\beta}p_{\vec\beta}=1$ (which follows from \cpnote{ver constante de 
-% normalizacion chido y ver el motivo}), and 
 $\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
@@
 \ref{tab:1} for a detailed description. 
-% \cpnote{Quiza poner una relacion como $\tau_{\vgamma}=\tau_{\valpha\oplus{}\vgamma}$}
 \par
-% \cpnote{by direct calculation I can verify 
-% that its true, but I see it as a coincidence. Is they ere a say to know
-% that \eref{eq:14} will lead to a sum?}
 % }}}
@@
 each of the $2N$ components. 
-\cpnote{maybe its not necesary}
 }. 
@@
 $\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
-% \cpnote{Creo que aca podemos referenciar la figura 2c y mostrar como
-% funcionaria que no es cerrada bajo la suma}
 For example, in \fref{fig:two:qubit:examples}(c) the indices that 
@@
 a valid quantum channel, and a vector subspace of the aforementioned space. 
-\cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
-figura en la que se tenga algo que es un canal y algo que no es  un canal. 
-Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
-depolarizante y el subespacio mas grande es la identidad} \par
+% \cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
+% figura en la que se tenga algo que es un canal y algo que no es  un canal. 
+% Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
+% depolarizante y el subespacio mas grande es la identidad} 
+\par
 
@@
 seen earlier that
-\cpnote{Why is the dimension $2N$? I can work it out, but just after adding one 
-by one elements}
 \begin{equation}
@@
 discussed above can only have $2^K$ elements equal to 1, for a given integer
-$K$.
+$K$. \par
 
-\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}
+\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores} \par
+
  % }}}

### 2021-10-18 documentos/prueba.tex
.

\section{Proof of a non-obvious consequence}
\label{app:proof}
Here we show that (\ref{eq:13}) implies (\ref{eq:14}). Since (\ref{eq:13}) holds for 
all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
$\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
such that
\begin{equation}
\sa_{\alpha_k\beta}=1.
\end{equation}
This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so that (\ref{eq:13})
indeed holds for this $\vec\beta$. On the other hand, it is then readily verified that, for this
$\vec\beta$, (\ref{eq:13}) reduces to (\ref{eq:14}), whcih therefore follows.

### 2021-10-18 documentos/vector_space.tex
.

@@
 = 
-\san_{\valpha\vbeta} 
+1
 , \quad
@@
 %   \cdot\ldots\cdot 
-\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
-\sa_{\alpha_1\beta_1}
-  \ldots
-% \cdot\ldots\cdot
- \sa_{\alpha_N\beta_N}.
+\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
 \label{eq:13}
@@
 % \end{equation}
-Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
-the above relation must hold individually for every index\cpnote{francois, recuerdo 
+\flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del texto siguiente. } \cpnote{francois, recuerdo 
 que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
-proque se tiene que cumplir para los indices individulaes}. Thus we have, 
-that, for all $1\leq k\leq N$, $\gamma_k$
+proque se tiene que cumplir para los indices individulaes}. 
+We now show in Appendix
+\ref{app:proof} that from this follows that
+for all $1\leq k\leq N$, $\gamma_k$
 and $\gamma_k^\prime$ are connected by
 \begin{equation}
-\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
+\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
 \label{eq:14}
 \end{equation}
-for all $0\leq\beta\leq3$. One can verify, by working out the different cases, 
-that \eref{eq:14} equivalently expressed as 
+for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$ . One can verify, by working out the different cases, 
+that \eref{eq:14} is equivalently expressed as 
 \begin{equation}
-\gamma_k^\prime=\alpha\oplus{}\gamma_k
+\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
 \label{eq:oplus}
 \end{equation}
-where the $\oplus{}$ denotes the operation of the Kein group; see Figure
+where the $\oplus{}$ denotes the operation of the Klein group; see Figure
 \ref{tab:1} for a detailed description. 
@@
 $\valpha^{(4)} = (3,2)$. However, 
-$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preseverd and thus this 
+$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
 diagram does not correspond to a quantum channel.  From this view 

### 2021-10-18 documentos/vector_space.tex
forgot to save that file

@@
 % \end{equation}
-\flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del texto siguiente. } \cpnote{francois, recuerdo 
-que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
-proque se tiene que cumplir para los indices individulaes}. 
-We now show in Appendix
-\ref{app:proof} that from this follows that
-for all $1\leq k\leq N$, $\gamma_k$
-and $\gamma_k^\prime$ are connected by
+% Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
+Since \eref{eq:13} holds for 
+all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
+$\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
+such that
+$\sa_{\alpha_k\beta}=1$. 
+% \begin{equation}
+% \sa_{\alpha_k\beta}=1.
+% \end{equation}
+This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so that \eref{eq:13}
+indeed holds for this $\vec\beta$. On the other hand, it is then readily verified that, for this
+$\vec\beta$, \eref{eq:13} reduces to 
+% (\ref{eq:14}), whcih therefore follows. 
+% \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
+% texto siguiente. } \cpnote{francois, recuerdo 
+% que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
+% proque se tiene que cumplir para los indices individulaes}. 
+% We now show in Appendix
+% \ref{app:proof} that from this follows that
+% for all $1\leq k\leq N$, $\gamma_k$
+% and $\gamma_k^\prime$ are connected by
 \begin{equation}

### 2021-10-18 documentos/generators.tex
Ideas

@@
 Alfredo o Carlos la terminan}
+
+\janote{Mis suferencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
+explicar a punta de las figuras PCE cómo generar todos los canales PCE 
+de 2 qubits. Sólo es necesario mostrar cómo se generan elementos representativos
+de cada clase de equivalencia. [Ya se habló de las clases de equivalencia a
+esta altura del artículo?] Esto es algo que se puede poner en un apéndice.\newline\indent
+(2) Para el caso de 1 qubit, nuestra noción de generadores es compatible 
+con los resultados de Siudzinska \cite{siudzinska2019geometry} sobre 
+el espacio en el tetraedro de los canales cuánticos que son accesibles 
+mediante generadores locales de tiempo. Quizás una referencia es 
+apropiada.\newline\indent
+(3) Hablar sobre la relación entre los generadores y filas o columnas de la $A$.
+Esto lo podemos discutir con más detalles, Carlos. 
+}
 

### 2021-10-18 documentos/vector_space.tex
Primeros comentarios

@@
 \subsection{A vector space of channels} % {{{
-\cpnote{Quiza falta lo de las clases de equivalencias}\par
+\cpnote{Quiza falta lo de las clases de equivalencias}\janote{Pienso que sí porque
+puede y debería ser útil para la sección siguiente de generadores.}\par
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
@@
 to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
+\janote{Siento que hace falta un enunciado por aquí, al inicio de la sección, que haga
+que el lector se pueda colgar de la idea de los espacios vectoriales. Quizás algo 
+como}\janote{We will show how to associate unequivocally PCE quantum
+channels with vector spaces.}
 % . In components, this would read 
@@
 This is a remarkable equation, as it provides a method to diagonalize any diagonal 
-Pauli channel, as in \eref{eq:definition:Pauli}.
+Pauli channel, as in \eref{eq:definition:Pauli}. \janote{por qué diagonalizar al 
+canal de Pauli? Creo que sería más bien a la matriz de Choi, pero igual estoy 
+un poco pérdido con el sentido del enunciado. }
 
@@
 $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
-$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
+$\lambda_\valpha=0$ for all $\valpha\in \Omega$\janote{Qué es $\Omega$?}, as each member of the sum \janote{is}
 greater or equal to zero, 
@@
 \eref{eq:sum:alpha:is:2N} from 
-$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$ 
+$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$\janote{la resta no es al revés?}
 (which follows from the aforementioned assumption), 

### 2021-10-19 documentos/vector_space.tex
Estoy atorado en el paso al oplus

@@
 to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
+\janote{Para entender esto tuve que revisar de nuevo 
+el manuscrito de Francois. No veía cómo llegar a la implicación establecida
+en \eqref{eq:coneccion:dos:indices:A}. Creo que algunos pasos intermedios son
+importantes.}
 Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,

### 2021-10-19 documentos/proofdiagonalization.tex
Proof_Eigen_N

@@
 % 
+\subsection{Single qubit}
 In order to simplify the derivation of the relations, let us employ pairs of
@@
 \begin{equation}
-\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\ket{j,j\oplus \nu}.
+\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\kket{j,j\oplus \nu}.
 \end{equation}
@@
 \begin{equation}
-\ket{l,l\oplus n}=\frac{1}{2}\sum_{m=0}^{1} (-1)^{ml}\kket{\sigma_{mn}}.
+\kket{l,l\oplus n}=\frac{1}{2}\sum_{m=0}^{1} (-1)^{ml}\kket{\sigma_{mn}}.
 \label{PauToComp}
@@
 \hat{\mathcal{E}} & = \frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}},\\
-& = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \dyad{j,j\oplus\nu}{k,k\oplus\nu}.
+& = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \ddyad{j,j\oplus\nu}{k,k\oplus\nu}.
 % \label{Map_Pauli}
@@
   \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} 
-      \dyad{j,k}{j\oplus\nu,k\oplus\nu}.
+      \ddyad{j,k}{j\oplus\nu,k\oplus\nu}.
 \label{Choi_a1}
@@
     \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu} (-1)^{\mu m} 
-        \dyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
+        \ddyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
 \label{Choi_a1}
@@
 \begin{align*}
- \mathcal{D} & = \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu}(-1)^{\mu m}  \left( \frac{1}{2}\sum_{k=0}^{1} (-1)^{kj}\kket{\sigma_{km}}\right)\left(\frac{1}{2}\sum_{n=0}^{1} (-1)^{n(j\oplus\nu)}\bbra{\sigma_{nm}}\right),\\
- & = \frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+ \mathcal{D} & = 
+%  \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu}(-1)^{\mu m}  \left( \frac{1}{2}\sum_{k=0}^{1} (-1)^{kj}\kket{\sigma_{km}}\right)\left(\frac{1}{2}\sum_{n=0}^{1} (-1)^{n(j\oplus\nu)}\bbra{\sigma_{nm}}\right),\\
+\frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
  & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
@@
 
-\afnote{Queda faltando pasar a limpio la generalizacion para $N$ qubits.}
+\subsection{$N$ qubits}
 
+Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
+\begin{equation}
+\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu}}}, 
+\end{equation}
+where
+\begin{align}
+\kket{\sigma_{\vec{\mu}\vec{\nu}}} & = \kket{\sigma_{\mu_1\nu_1}}\otimes \cdots \kket{\sigma_{\mu_N\nu_N}},\\
+& = \left(\sum_{j_1=0}^{1} (-1)^{j_1 \mu_1}\kket{j_1,j_1\oplus \nu_1}\right)\otimes\cdots \otimes \left(\sum_{j_N=0}^{1} (-1)^{j_N \mu_N}\kket{j_N,j_N\oplus \nu_N}\right),\\
+& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{j_1,j_1\oplus \nu_1}\otimes\cdots \otimes \kket{j_N,j_N\oplus \nu_N},\\
+& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}}
+\end{align}
+and
+\begin{equation}
+\bbrakket{\sigma_{\vec{\mu}\vec{\nu}}}{\sigma_{\vec{\mu}'\vec{\nu}'}} = 2^N \delta_{\vec{\mu}\vec{\mu}'}\delta_{\vec{\nu}\vec{\nu}'}.
+\end{equation}
+
+Recall the relation between the computational and Pauli basis elements (Eq. \ref{PauToComp}), in this way for the $N$-qubits case we have
+% 
+\begin{align}
+ \kket{\vec{l},\vec{l}\oplus \vec{n}} & = \kket{l_1,l_1\oplus n_1} \otimes\cdots \otimes \kket{l_N,l_N\oplus n_N} \\
+  & = \left( \frac{1}{2}\sum_{m_1=0}^{1} (-1)^{m_1l_1}\kket{\sigma_{m_1n_1}}\right)\otimes\cdots \otimes\left(\frac{1}{2}\sum_{m_N=0}^{1} (-1)^{m_Nl_N}\kket{\sigma_{m_Nn_N}}\right),\\
+ & = \frac{1}{2^N}\left(\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{m_1n_1}}\otimes\cdots \otimes\kket{\sigma_{m_Nn_N}}\right),\\
+ & = \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n}}}.
+\label{PauToCompN}
+ \end{align}
+By employing the previous relations, we can write the matrix representation of the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
+\begin{align}
+\hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu}}},\\
+= & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.\\
+\end{align}
+In this way it is straightforward to apply the reshuffling operation on $\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix $\mathcal{D}_N$,
+\begin{equation}
+\mathcal{D}_N =\frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{k}}{\vec{j}\oplus \vec{\nu},\vec{k}\oplus \vec{\nu}}.
+\end{equation}
+After the change of vector indices $\vec{k}=\vec{j}\oplus\vec{l}$, the Choi matrix holds
+\begin{equation}
+\mathcal{D}_N =\frac{1}{2^N}\sum_{\vec{j}\vec{l}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{j}\oplus\vec{l})} \ddyad{\vec{j},\vec{j}\oplus\vec{l}}{\vec{j}\oplus \vec{\nu},\vec{j}\oplus \vec{\nu}\oplus \vec{l}}.
+\end{equation}
+Back to the vectorized Pauli basis (Eq. \ref{PauToCompN}), we have
+\begin{equation}
+\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\vec{j}\vec{l}\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l}}}{\sigma_{\vec{n}\vec{l}}}.
+\end{equation}
+Due to the fact that we are dealing with binary indices, then we can safely write the modular sum in the exponent as standard sum.
+On the other hand, recall the relation $\sum_{\vec{j}}(-1)^{\vec{j}\cdot(\vec{m}+\vec{n})}=2^N\delta_{\vec{m}\vec{n}}$.
+Thus $\mathcal{D}_N$ reduces to
+\begin{align}
+\mathcal{D}_N & = \frac{1}{2^{2N}}\sum_{\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \ddyad{\sigma_{\vec{m}\vec{n}}}{\sigma_{\vec{m}\vec{n}}},\\
+& = \frac{1}{2^{N}}\sum_{\vec{m}\vec{n}} \left( \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \right)\ddyad{\sigma_{\vec{m}\vec{n}}}{\sigma_{\vec{m}\vec{n}}}.
+\end{align}
+Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
+\begin{equation}
+\lambda_{\vec{m}\vec{n}}= \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}}
+\end{equation}
+or more compactly $\vec{\lambda} = \san~\vec{\tau}$, where $\san=a^{\otimes N}$, $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix.
 % }}}

### 2021-10-20 documentos/vector_space.tex
No time to commit.. My people need me!

--- 2021-10-18 documentos/vector_space.tex
@@
 \subsection{A vector space of channels} % {{{
-\cpnote{Quiza falta lo de las clases de equivalencias}\par
+\cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
+espacio. Quizá cuando haga falta se puede poner}
+% \janote{Pienso que sí porque puede y debería ser útil para la sección siguiente
+% de generadores.}
+\par
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
-The problem of determining complete positivity of a PCE can be recast as 
-determining which vectors $\vtau$ are mapped via
+
+In this subsection we will provide a one-to-one relation between PCE quantum channels 
+and the subspaces of a discrete vector subspace associated with the indices $\valpha$
+labeling the components of a state; see \eref{eq:N_qubits_rho}.
+
+Let us start by recalling that the problem of determining complete positivity
+of a PCE can be recast as determining which vectors $\vtau$ are mapped via
 $\san$
@@
 to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
+% \janote{Siento que hace falta un enunciado por aquí, al inicio de la sección, que haga
+% que el lector se pueda colgar de la idea de los espacios vectoriales. Quizás algo 
+% como}\janote{We will show how to associate unequivocally PCE quantum
+% channels with vector spaces.}
 % . In components, this would read 
@@
 \begin{equation}
-A^{-1} = \frac{1}{4^N} A
+A^{-1} = \frac{1}{4^N} A,
 \end{equation}
@@
 which will serve as a starting point for our analysis. 
-This is a remarkable equation, as it provides a method to diagonalize any diagonal 
+This is a remarkable equation, as it provides a method to diagonalize the
+Choi matrix of any diagonal 
 Pauli channel, as in \eref{eq:definition:Pauli}. 
+% \janote{por qué diagonalizar al 
+% canal de Pauli? Creo que sería más bien a la matriz de Choi, pero igual estoy 
+% un poco pérdido con el sentido del enunciado. }
 
@@
 $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
-$\lambda_\valpha=0$ for all $\valpha\in \Omega$, as each member of the sum 
+$\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
+multi-indices $\Omega$, as each member of the sum is
 greater or equal to zero, 
@@
 \end{equation}
-If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
-\eref{eq:sum:alpha:is:2N} from 
+% If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
+If we now assume that $\tau_{\vec\alpha}=1$, and calculate the difference between
+\eref{eq:sum:alpha:is:2N} and
 $\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
-(which follows from the aforementioned assumption), 
+% \janote{la resta no es al revés?} 
+(which follows from the aforementioned assumption), one obtains
 % \begin{subequations}
@@
 to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
-Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
+% \janote{Para entender esto tuve que revisar de nuevo 
+% el manuscrito de Francois. No veía cómo llegar a la implicación establecida
+% en \eqref{eq:coneccion:dos:indices:A}. Creo que algunos pasos intermedios son
+% importantes.}
+Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
+multi-indices, $\valpha$,
 $\vec\gamma$ and $\vec{\gamma^\prime}$.

### 2021-10-21 documentos/vector_space.tex
done. going to bed now.

@@
 
-Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
-of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
-as
+Let the components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for
+a particular particle index $k$, with 
+$\beta$ such that $\sa_{\alpha_k\beta}=1$.
+Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular election of $\vbeta$
+belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
+indeed holds. However, for such election of $\vbeta$ the above relation reduces
+to 
 \begin{equation}
-\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
-= 
-1
-, \quad
-\forall \vec\beta\in\Phi(\vec\alpha),
-\label{eq:12}
-\end{equation}
-which can be further decomposed in 
-\begin{equation}
-\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
-  \ldots
-%   \cdot\ldots\cdot 
-\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
-\label{eq:13}
-\end{equation}
-% Moreover, since 
-% 
-% 
-% 
-% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
-% \begin{equation}
-% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
-% \label{eq:12}
-% \end{equation}
-% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
-% (\ref{eq:12}) may be rewritten as
-% \begin{equation}
-% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
-% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
-% \label{eq:13}
-% \end{equation}
-% Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
-Since \eref{eq:13} holds for 
-all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
-$\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
-such that
-$\sa_{\alpha_k\beta}=1$. 
-% \begin{equation}
-% \sa_{\alpha_k\beta}=1.
-% \end{equation}
-This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so that \eref{eq:13}
-indeed holds for this $\vec\beta$. On the other hand, it is then readily verified that, for this
-$\vec\beta$, \eref{eq:13} reduces to 
-% (\ref{eq:14}), whcih therefore follows. 
-% \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
-% texto siguiente. } \cpnote{francois, recuerdo 
-% que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
-% proque se tiene que cumplir para los indices individulaes}. 
-% We now show in Appendix
-% \ref{app:proof} that from this follows that
-% for all $1\leq k\leq N$, $\gamma_k$
-% and $\gamma_k^\prime$ are connected by
-\begin{equation}
-\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
+\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
 \label{eq:14}
 \end{equation}
-for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$ . One can verify, by working out the different cases, 
+for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
+One can verify, by working out the different cases, 
 that \eref{eq:14} is equivalently expressed as 
@@
 \par
+% 
+% 
+% % Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
+% % of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
+% % as
+% % \begin{equation}
+% % \san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
+% % = 
+% % 1
+% % , \quad
+% % \forall \vec\beta\in\Phi(\vec\alpha),
+% % \label{eq:12}
+% % \end{equation}
+% % which can be further decomposed in 
+% % \begin{equation}
+% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
+% %   \ldots
+% % %   \cdot\ldots\cdot 
+% % \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+% % \label{eq:13}
+% % \end{equation}
+% % Moreover, since 
+% % 
+% % 
+% % 
+% % Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
+% % \begin{equation}
+% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
+% % \label{eq:12}
+% % \end{equation}
+% % This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
+% % (\ref{eq:12}) may be rewritten as
+% % \begin{equation}
+% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
+% % \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
+% % \label{eq:13}
+% % \end{equation}
+% % Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
+% Since \eref{eq:13} holds for 
+% all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
+% $\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
+% such that
+% $\sa_{\alpha_k\beta}=1$. 
+% % \begin{equation}
+% % \sa_{\alpha_k\beta}=1.
+% % \end{equation}
+% This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so
+% that \eref{eq:13} indeed holds for this $\vec\beta$. On the other hand, it is
+% then readily verified that, for this $\vec\beta$, \eref{eq:13} reduces to 
+% % (\ref{eq:14}), whcih therefore follows. 
+% % \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
+% % texto siguiente. } \cpnote{francois, recuerdo 
+% % que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
+% % proque se tiene que cumplir para los indices individulaes}. 
+% % We now show in Appendix
+% % \ref{app:proof} that from this follows that
+% % for all $1\leq k\leq N$, $\gamma_k$
+% % and $\gamma_k^\prime$ are connected by
+% \begin{equation}
+% \sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
+% \label{eq:14}
+% \end{equation}
+% for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
+% One can verify, by working out the different cases, 
+% that \eref{eq:14} is equivalently expressed as 
+% \begin{equation}
+% \gamma_k^\prime=\alpha_k\oplus{}\gamma_k
+% \label{eq:oplus}
+% \end{equation}
+% where the $\oplus{}$ denotes the operation of the Klein group; see Figure
+% \ref{tab:1} for a detailed description. 
+% \par
 % }}}

### 2021-10-21 documentos/vector_space.tex
Últimos comentarios al draft

@@
 }. 
-We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
+We can indeed restate \eref{eq:oplus}, an\janote{and?} say that for valid quantum channels, 
 if $\tau_{\vec\alpha}=1$, then
@@
 whenever the $\vec\gamma$ belong to a given vector subspace of the set of
-all indices, then the vector $\vec\tau$ indeed has an image which is a vector
-with only positive components. 
+all indices, then the vector $\vec\tau$\janote{Se me hace bien un recordatorio aquí de qué es $\vec\tau$, por ejemplo:}\janote{, whose components are the diagonal elements of a PCE superoperator in Pauli basis,} indeed has an image which is a vector
+with only positive components\janote{Siento que hace falta en algún lado de este párrafo un enunciado recordando para qué necesitamos que $\vec\tau$ tenga una imagen positiva}\janote{Recall that complete positivity of a PCE map is equivalent to the condition of $\vec\tau$ having a positive image under \san}.
 In other words, there is a one to one correspondence between 
@@
 of $\vbeta$ generated by the previously switched values of $\valpha$ via the
-operation $\oplus$. Doing so, in an ordered way, allows one to general 
+operation $\oplus$. Doing so, in an ordered way, allows one to general\janote{generate*?} 
 all valid quantum channels with a given set of preserved components, without the need
@@
 % Los canales tiene 2^K componente {{{
-We can then see that all PCEs preserve $2^K$ components. In fact, with the above 
+We can then see that all PCEs \janote{PCE quantum channels, PCEs me parece que refiere más a todos los PCE maps} preserve $2^K$ components. In fact, with the above 
 picture, it is clearly revealed that the vector space has dimension $2N$. Moreover, 
@@
 unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
-elements of the vector space. This means that any PCE will preserve $2^K$ 
+elements of the vector space. This means that any PCE\janote{quantum channel} will preserve $2^K$ 
 components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
@@
 
-\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores} \par
+\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El primero (simón, cambié de opinión)} \par
 
@@
 From the above expression, it is easy to see the symmetry relation
-\begin{equation}
+\begin{equation}\label{eq:conteo:simmetry}
 \sss_{N,K}=\sss_{N,2N-K}
 \end{equation}
-which suggest an relation  between individual channels that for the time being
+which suggest an\janote{a*} relation  between individual channels\janote{that
+preserve $K$ and $2N-K$ Pauli components} that for the time being
 has escaped our efforts to identify. 
@@
 rules will give you the rest of components to make the target operation a CPTP
-one.}
+one.} \janote{Me gusta esto que puso David, pero lo movería a las conclusiones.}
 \par % }}}

### 2021-10-21 documentos/vector_space.tex
Typo en mis últimos comentarios

@@
 }. 
-We can indeed restate \eref{eq:oplus}, an\janote{and?} say that for valid quantum channels, 
+We can indeed restate \eref{eq:oplus}, an\janote{and*?} say that for valid quantum channels, 
 if $\tau_{\vec\alpha}=1$, then

### 2021-10-22 documentos/pce.tex
Well, it's doing something.
Fixed everything.

@@
 % 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+\label{eq:definition:Pauli}
 \end{equation}
@@
 \node at (-0.6,0.5) {(a)} ;
-\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
+\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
 \begin{scope}[shift={(0,-1)}]
-\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
+\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
 \end{scope}
 \begin{scope}[shift={(0,-2)}]
-\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
+\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
 \end{scope}
 \begin{scope}[shift={(0,-3)}]
-\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
-\end{scope} % }}}
+\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
+\end{scope} 
+\draw (0,-3) rectangle (1,1); 
+% }}}
 \begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
@@
 \fill[black] (0,0) rectangle (1,1);
-\draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
 \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
 \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
 \end{scope} % }}}
@@
 \fill[black] (0,0) rectangle (1,1);
-\draw (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
 % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
 \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
 \end{scope} % }}}
@@
 \fill[black] (0,0) rectangle (1,1);
-\draw (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
 % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
 \end{scope} % }}}
@@
 \fill[black] (0,0) rectangle (1,1);
-\draw (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
 \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
 \end{scope} % }}}
@@
 \node at (-0.5,0.5) {(a)} ;
+% \cuadritotikz{}
     \foreach \x in {0,1,2,3} {
@@
         \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
+          \draw[black!10] (0,0) rectangle (1,1); 
+%           \draw (0,0) rectangle (1,1); 
           \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
@@
     }
+ \draw (0,-3) rectangle (4,1);
 \end{scope} % }}}
@@
 \node at (-0.5,0.5) {(b)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
+%     \foreach \x in {0,1,2,3} {
+%       \foreach \y in {0,1,2,3} {
+%         \begin{scope}[shift={(\x,-\y)}] 
+%           \draw (0,0) rectangle (1,1); 
+% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+%          \end{scope}
+% %         \node at (0,-\y) (input\y) {$i_\y$};
+% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
+% %         \draw[->] (input\y) -- (block\y);
+% %         \draw[->] (block\y.east) -- +(0.5,0);
+%     }
+%     }
 \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \node at (-0.5,0.5) {(c)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
+%     \foreach \x in {0,1,2,3} {
+%       \foreach \y in {0,1,2,3} {
+%         \begin{scope}[shift={(\x,-\y)}] 
+%           \draw (0,0) rectangle (1,1); 
+% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
+%          \end{scope}
+% %         \node at (0,-\y) (input\y) {$i_\y$};
+% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
+% %         \draw[->] (input\y) -- (block\y);
+% %         \draw[->] (block\y.east) -- +(0.5,0);
+%     }
+%     }
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}

### 2021-10-22 documentos/vector_space.tex
Fixed everything.

--- 2021-10-21 documentos/vector_space.tex
@@
 espacio. Quizá cuando haga falta se puede poner}
-% \janote{Pienso que sí porque puede y debería ser útil para la sección siguiente
-% de generadores.}
 \par
@@
 to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
-% \janote{Siento que hace falta un enunciado por aquí, al inicio de la sección, que haga
-% que el lector se pueda colgar de la idea de los espacios vectoriales. Quizás algo 
-% como}\janote{We will show how to associate unequivocally PCE quantum
-% channels with vector spaces.}
 % . In components, this would read 
@@
 Pauli channel, as in \eref{eq:definition:Pauli}.
-% \janote{por qué diagonalizar al 
-% canal de Pauli? Creo que sería más bien a la matriz de Choi, pero igual estoy 
-% un poco pérdido con el sentido del enunciado. }
 
@@
 $\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
-% \janote{la resta no es al revés?} 
 (which follows from the aforementioned assumption), one obtains
@@
 to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
-% \janote{Para entender esto tuve que revisar de nuevo 
-% el manuscrito de Francois. No veía cómo llegar a la implicación establecida
-% en \eqref{eq:coneccion:dos:indices:A}. Creo que algunos pasos intermedios son
-% importantes.}
 Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
@@
 }. 
-We can indeed restate \eref{eq:oplus}, an say that for valid quantum channels, 
+We can indeed restate \eref{eq:oplus}, and say that for valid quantum channels, 
 if $\tau_{\vec\alpha}=1$, then
@@
 whenever the $\vec\gamma$ belong to a given vector subspace of the set of
-all indices, then the vector $\vec\tau$ indeed has an image which is a vector
+all indices, then the vector $\vec\tau$ indeed has an image
+which is a vector
 with only positive components. 
@@
 of $\vbeta$ generated by the previously switched values of $\valpha$ via the
-operation $\oplus$. Doing so, in an ordered way, allows one to general 
+operation $\oplus$. Doing so, in an ordered way, allows one to generate
 all valid quantum channels with a given set of preserved components, without the need
@@
 % }}}}
+
 \begin{figure} % {{{
@@
 \node at (-0.5,0.5) {(a)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 \end{scope} % }}}
@@
 \node at (-0.5,0.5) {(b)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \node at (-0.5,0.5) {(c)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \node at (-0.5,0.5) {(d)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \node at (-0.5,0.5) {(e)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \node at (-0.5,0.5) {(f)} ;
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw (0,0) rectangle (1,1); 
-%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
+\cuadritotikz{}
 \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 % Los canales tiene 2^K componente {{{
-We can then see that all PCEs preserve $2^K$ components. In fact, with the above 
-picture, it is clearly revealed that the vector space has dimension $2N$. Moreover, 
+We can then see that all PCE quantum channels preserve $2^K$ components. In
+fact, with the above picture, it is clearly revealed that the vector space has
+dimension $2N$. Moreover, 
 consider any subspace and chose the maximum number of linearly independent
@@
 unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
-elements of the vector space. This means that any PCE will preserve $2^K$ 
+elements of the vector space. This means that any PCE quantum channel will preserve $2^K$ 
 components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
@@
 
-\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores} \par
+\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
+primero (simón, cambié de opinión)} \par
 
@@
 From the above expression, it is easy to see the symmetry relation
-\begin{equation}
+\begin{equation}\label{eq:conteo:simmetry}
 \sss_{N,K}=\sss_{N,2N-K}
 \end{equation}
-which suggest an relation  between individual channels that for the time being
+which suggest a relation  between individual channels that
+preserve $K$ and $2N-K$ Pauli components that for the time being
 has escaped our efforts to identify. 

### 2021-10-22 documentos/vector_space.tex
Derp

@@
 % \end{equation}
-$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
-$\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
-multi-indices $\Omega$, as each member of the sum is
+% $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
+% $\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
+% multi-indices $\Omega$, 
+\begin{equation}
+\sum_{\valpha \in \Omega} \lambda_\valpha=0 
+\quad \implies 
+\quad 
+\lambda_\valpha=0, \, \forall \valpha \in \Omega
+\label{eq:lambda:is:zero}
+\end{equation}
+for an arbitrary subset of multi-indices $\Omega$, 
+as each member of the sum is
 greater or equal to zero, 
-% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
-% all $p_{\vec\alpha} \ge 0$
 due to complete positivity of the underlying channel. 
@@
 $\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
-(which follows from the aforementioned assumption), one obtains
+(which follows from \eref{eq:tau:is:A:p} and $\tau_{\vec\alpha}=1$), one obtains
 % \begin{subequations}
@@
 \end{equation}
-% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
 This follows from restricting the sum \eref{eq:tau:is:A:p}
@@
 $\beta$ such that $\sa_{\alpha_k\beta}=1$.
-Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular election of $\vbeta$
+Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
 belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
@@
 $\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
-$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
+$\{0,1\}$\cite{alguna:referencia}. 
+We notice that the Klein group described in \fref{tab:1} is actually isomorphic
+to the two dimensional vector space over the field of two elements $\{0,1\}$.
+Then, we build the complete vector space,
 with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus

### 2021-10-22 documentos/proofdiagonalization.tex
Appendix_Proof

@@
 \subsection{Single qubit}
-In order to simplify the derivation of the relations, let us employ pairs of
-binary indices instead of a single quaternary, i.e. $\alpha\to\mu+2\nu$. In
-this way we can write the elements of the Pauli basis
-$(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$ in the standard and vectorized
-forms, compactly as
+In order to simplify the derivation of the relations, let us employ pairs of binary indices instead of a single quaternary, i.e. $\alpha\to\mu+2\nu$. Hence we can write the elements of the Pauli basis
+$(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$, compactly as
+$\sigma_{\mu\nu}=\sum_{j=0}^{1} (-1)^{j \mu}\dyad{j}{j\oplus \nu}$. In vectorized form
 \begin{equation}
-\sigma_{\mu\nu}=\sum_{j=0}^{1} (-1)^{j \mu}\dyad{j}{j\oplus \nu},
+\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\kket{j,j\oplus \nu},
 \end{equation}
-and
-\begin{equation}
-\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\kket{j,j\oplus \nu}.
-\end{equation}
-In addition, recall the inverse relation between the computational and Pauli elements
+in the same way,
 \begin{equation}
@@
 \end{equation}
-On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may
-be written as
+On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may be written as
 \begin{align}
@@
 \end{align}
-After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the
-Choi matrix associated to the map. It reads
+After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the Choi matrix associated to the map. It reads
 \begin{equation}
@@
 \end{equation}
-By using the relation between computational and Pauli elements (Eq.
-\ref{PauToComp}), we have
+Due to the fact that we are dealing with binary indices, thus we can safely write the modular sums in the exponents as standard sums.
+By employing the relation between computational and Pauli elements (Eq.
+\ref{PauToComp}), by noticing that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$, and after some steps we have
 \begin{align*}
@@
 \frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
- & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
- & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} (2\delta_{kn}) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+%  & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
+%  & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} (2\delta_{kn}) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
  & = \frac{1}{4}\sum_{mn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \ddyad{\sigma_{nm}}{\sigma_{nm}},\\
@@
 where
+\begin{widetext}
 \begin{align}
@@
 & = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{j_1,j_1\oplus \nu_1}\otimes\cdots \otimes \kket{j_N,j_N\oplus \nu_N},\\
-& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}}
+& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},
 \end{align}
+\end{widetext}
 and
@@
 
-Recall the relation between the computational and Pauli basis elements (Eq. \ref{PauToComp}), in this way for the $N$-qubits case we have
+Recall the relation between the computational and Pauli basis elements (Eq. \ref{PauToComp}), hence for the $N$-qubits case we have
 % 
+\begin{widetext}
 \begin{align}
@@
 \end{align}
+\end{widetext}
 By employing the previous relations, we can write the matrix representation of the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
@@
 \hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu}}},\\
-= & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.\\
+= & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.
 \end{align}
-In this way it is straightforward to apply the reshuffling operation on $\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix $\mathcal{D}_N$,
+In this way it is straightforward to apply the reshuffling operation on $\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix,
 \begin{equation}
@@
 \end{equation}
-Back to the vectorized Pauli basis (Eq. \ref{PauToCompN}), we have
+Back to the vectorized Pauli basis (Eq. \ref{PauToCompN}) we have
 \begin{equation}
-\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\vec{j}\vec{l}\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l}}}{\sigma_{\vec{n}\vec{l}}}.
+\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\substack{\vec{j}\vec{l}\vec{m} \\ \vec{n}\vec{\mu}\vec{\nu}}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l}}}{\sigma_{\vec{n}\vec{l}}}.
 \end{equation}
-Due to the fact that we are dealing with binary indices, then we can safely write the modular sum in the exponent as standard sum.
-On the other hand, recall the relation $\sum_{\vec{j}}(-1)^{\vec{j}\cdot(\vec{m}+\vec{n})}=2^N\delta_{\vec{m}\vec{n}}$.
-Thus $\mathcal{D}_N$ reduces to
+On the other hand, recall the relation $\sum_{\vec{j}}(-1)^{\vec{j}\cdot(\vec{m}+\vec{n})}=2^N\delta_{\vec{m}\vec{n}}$. After some steps $\mathcal{D}_N$ reduces to 
 \begin{align}

### 2021-10-27 documentos/math.tex
<!DOCTYPE html><html><head><title>Unable to Connect</title><style type="text/css">*{font-family: "Open Sans", sans-serif; color: rgb(101, 102, 106)}body{padding-left: 50px; background-color: #f7f7f7;}h1{font-size: 48px; font-weight: 100; letter-spacing: 0.025em}h2{font-size: 28px; font-weight: 100; letter-spacing: 0.01em}p{font-size: 13px; font-weight: 300; letter-spacing: 0.08em line-height: 1.4;}</style></head><body><h1>Error accessing site</h1><h2>Unable to Connect</h2><p>The requested site&#39;s DNS address could not be found.</p></body></html>
Updated build targets.

@@
 \section{Mathematical considerations} 
+This section is devoted to derive the conditions a Pauli map need to
+satisfy to fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
+associated to the channel must be non-negative. 
+To do so, we first calculate and diagonalize the matrix associated with the map, 
+first for a single qubit and then for $N$ qubits. We then associate a vector space
+to the set of coefficients $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from 
+which we are able to derive several important conclusions.
+
+% First we obtain the set of
+% inequalities for a single qubit Pauli channel and then we extend the results
+% for the general case of $N$ qubits. 
 \subsection{Diagonalization of Choi matrix}
 
-% Intro {{{
-Prueba de la $\sa$ \todo{Alejo escribe esta parte. Dejelo aca todo y luego si acaso 
-pasamos cosas al apendice. Caso general}
-
-This part is devoted to derive the set of conditions a Pauli map need to
-satisfy to fulfill the CP condition i.e. all the eigenvalues of the Choi matrix
-associated to the channel must be non-negative. First we obtain the set of
-inequalities for a single qubit Pauli channel and then we extend the results
-for the general case of $N$ qubits.
-
-% }}}
 \subsubsection{Single qubit Pauli channels} % {{{
 
-\afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
-\janote{Qué tal $\vec\rho\quad$?}
-\afnote{Por ahora uso este $\kket{\rho}$}
+% \afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
+% \janote{Qué tal $\vec\rho\quad$?}
+% \afnote{Por ahora uso este $\kket{\rho}$}
 
-We now turn to find the matrix form of the map $\mathcal{E}$ in order to construct the Choi matrix and the conditions the set of parameters $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a quantum channel.
-By writing the density matrix in vector form $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the matrix form of the map $\mathcal{E}$ may be written as
+We now study the matrix form of the single qubit map $\mathcal{E}$ in
+order to construct the associated Choi matrix. 
+% and the conditions the set of parameters
+% $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a
+% quantum channel. 
+To do so, we shall denote operators in the superoperator space with the symbol
+$\kket{\cdot}$. For example, $\kket{\sigma_{\alpha}}$ correspond to the
+vectorized elements of the Pauli basis and satisfy the usual relation 
+$\bbrakket{{\sigma_{\alpha}}}{{\sigma_{\alpha'} }} = \tr
+\left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
+\delta_{\alpha\alpha'}$.
+In this language, 
+the state reads
+$\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$
+and the 
+% By writing the density matrix in vector form
+% $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the
+matrix form of the map $\mathcal{E}$ is
 % 
 \begin{equation}
-\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \ddyada{\sigma_{\alpha}},
+\hat{\mathcal{E}} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha}
+\ddyada{\sigma_{\alpha}}.
 % \label{Map_Pauli}
@@
 %
-where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha} }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$.
+% where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements
+% of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha}
+% }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger}
+% \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. 
 After some steps it is possible to show that the associated Choi matrix reads
@@
 with eigenvalues given by 
-% 
 \begin{equation}
- \lambda_{\alpha} = \sum_{\beta=0}^3\sa_{\alpha\beta}\tau_{\beta},
+ \lambda_{\alpha} = \frac12 \sum_{\beta=0}^3\sa_{\alpha\beta}\tau_{\beta},
 \end{equation}
-%
-or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes
-H$ and $H$ is the Hadamard matrix,
-\cpnote{Decidir si se usa esa $a$ o la otra para ser consistente con lo de los 
-generadores}
-%
-\begin{equation}
- H=\begin{pmatrix}
-        1 & 1\\
-        1 & -1\\
-    \end{pmatrix}.
- \label{Hadd_Mat}
-\end{equation}
-
-\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
-dejo por aca por si se nos ofrece}
+or more compactly $\vec{\lambda} = \sa \vec{\tau}$, where 
 \begin{equation}
@@
 \end{array}
-\right)=\frac12\sa^{-1}.
+\right)
+% =\frac12\sa^{-1}.
 \label{eq:1}
 \end{equation}
+
+% $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix,
+% \cpnote{Decidir si se usa esa $a$ o la otra para ser consistente con lo de los 
+% generadores}
+% %
+% \begin{equation}
+%  H=\begin{pmatrix}
+%         1 & 1\\
+%         1 & -1\\
+%     \end{pmatrix}.
+%  \label{Hadd_Mat}
+% \end{equation}
+
+\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
+dejo por aca por si se nos ofrece}
 % 
@@
 \begin{equation}
- \lambda_{\valpha} = \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
+ \lambda_{\valpha} = \frac{1}{2^N} \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
 \label{eq:lambda:is:A:tau}

### 2021-10-27 documentos/proofdiagonalization.tex
Choi_Paulis

@@
 \end{equation}
-
-Let us apply the index relabeling $k\to j\oplus m$, then the Choi matrix holds
+Note furthermore that the expression above may also be written as a combination of tensor products of Pauli matrices
+% 
+\begin{equation}
+ \mathcal{D} = \frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} \sigma_{\mu\nu} \otimes \sigma_{\mu\nu}^*.
+ \label{Choi_Pauli_1q}
+\end{equation}
+% 
+Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus m$, then the Choi matrix holds
 \begin{equation}
@@
         \ddyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
-\label{Choi_a1}
+% \label{Choi_a1}
 \end{equation}

### 2021-10-27 documentos/math.tex
bump to 0.0.3-dev:wq

@@
 \begin{equation}
- \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha} \otimes \sigma_{\alpha}^*.
+ \mathcal{D} = \frac{1}{2}\sum_{\alpha=0}^{3} \tau_{\alpha} \sigma_{\alpha}
+\otimes \sigma_{\alpha}^*.
 %  \label{Choi_1}
 \end{equation}
+\cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}
 % 
-Moreover, observe that $\mathcal{D}$ has the same form as the matrix representation of a random unitary channel, with Kraus operators given by $K_{\alpha}=\sqrt{\tau_{\alpha}/2}\sigma_{\alpha}$ \cite{CHRUSCINSKI20131425}.
-In this way the Choi matrix $\mathcal{D}$ is diagonal in the Pauli basis (see Appendix for details),
+% Moreover, observe that $\mathcal{D}$ has the same form as the matrix
+% representation of a random unitary channel, with Kraus operators given by
+% $K_{\alpha}=\sqrt{\tau_{\alpha}/2}\sigma_{\alpha}$ \cite{CHRUSCINSKI20131425}.
+Surprisingly, one can in fact show that $\mathcal{D}$ is diagonal in the Pauli
+basis (see Appendix \ref{sec:appendix:diagonalization}  for details).
+% In this way the Choi matrix $\mathcal{D}$ is diagonal in the Pauli basis (see
+% Appendix for details),
 %
-\begin{equation}
- \mathcal{D} \kket{\sigma_{\alpha}}= \lambda_{\alpha} \kket{\sigma_{\alpha}},
-\end{equation}
+% \begin{equation}
+%  \mathcal{D} \kket{\sigma_{\alpha}}= \lambda_{\alpha} \kket{\sigma_{\alpha}},
+% \end{equation}
 % 
-with eigenvalues given by 
+The eigenvalues are
 \begin{equation}
@@
 \end{equation}
-or more compactly $\vec{\lambda} = \sa \vec{\tau}$, where 
+% or more compactly $\vec{\lambda} = \sa \vec{\tau}$, 
+where 
 \begin{equation}
@@
 \end{equation}
+We wish to add that one can replace $a$ with $H \otimes H$, with $H$ the
+Hadamard matrix, and still diagonalize the same Choi matrix. This is due to the
+fact that $a$ corresponds to a permutation of rows of  $H \otimes H$. However
+we chose $a$ as some later considerations [see  \eref{eq:sigma_property}]
+cannot be written easily in terms of $H \otimes H$.
 
@@
 
-\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
-dejo por aca por si se nos ofrece}
+% \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar y la
+% dejo por aca por si se nos ofrece}
 % 

### 2021-10-27 documentos/math.tex
I should have had a V8 this morning.

@@
 \section{Mathematical considerations} 
+% Intro {{{
 This section is devoted to derive the conditions a Pauli map need to
@@
 associated to the channel must be non-negative. 
-To do so, we first calculate and diagonalize the matrix associated with the map, 
-first for a single qubit and then for $N$ qubits. We then associate a vector space
+To do so, we first calculate and diagonalize the matrix associated with general 
+Pauli maps, 
+first for a single qubit and then for $N$ qubits. We then restrict to
+PCEs and, for quantum channels, associate a vector space
 to the set of coefficients $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from 
@@
 
-% First we obtain the set of
-% inequalities for a single qubit Pauli channel and then we extend the results
-% for the general case of $N$ qubits. 
+% }}}
 \subsection{Diagonalization of Choi matrix} 
-
-\subsubsection{Single qubit Pauli channels} % {{{
+% \subsubsection{Single qubit Pauli channels} % {{{
 
@@
 vectorized elements of the Pauli basis and satisfy the usual relation 
-$\bbrakket{{\sigma_{\alpha}}}{{\sigma_{\alpha'} }} = \tr
+$\bbrakket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr
 \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
@@
 % \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. 
-After some steps it is possible to show that the associated Choi matrix reads
-% 
+After some steps, detailed from \eref{eq:inicio:canal:pauli} to 
+\eref{Choi_Pauli_1q}, it is possible to show that the associated Choi matrix
+reads
 \begin{equation}
@@
 \end{equation}
-\cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}
+Notice that, despite the similarity, $\ddyada{\sigma_{\alpha}}$ 
+and $\sigma_{\alpha} \otimes \sigma_{\alpha}^*$ are different operators.
+% \cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}
 % 
@@
 %  }}}
-\subsubsection{$N$ qubits} % {{{
+% \subsubsection{$N$ qubits} % {{{
 %
-Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
-% 
-\begin{equation}
-\rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
-% \label{Pauli_Map}
-\end{equation}
-% 
-with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
-% 
-In this case the density matrix in vector form holds 
-% 
-\begin{equation}
- \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
-\end{equation}
-where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
-\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
-$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
-\left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
-~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
-given by
+
+The same program can be carried out for $N$ qubits. In this case, 
+the vectorized Pauli operators are 
+ $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
+\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the orthogonality relation
+$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
+\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
+map corresponding to \eref{eq:definition:Pauli} is 
+% Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
+% % 
+% \begin{equation}
+% \rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
+% % \label{Pauli_Map}
+% \end{equation}
+% % 
+% with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
+% % 
+% In this case the density matrix in vector form holds 
+% % 
+% \begin{equation}
+%  \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
+% \end{equation}
+% where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
+% \otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
+% $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
+% \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
+% ~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
+% given by
 \begin{equation}
@@
 \end{equation}
-As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in terms of tensor products of Pauli matrices
+As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in
+terms of tensor products of Pauli matrices
 \begin{equation}
- \mathcal{D}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}  \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
+ \mathcal{D}_N 
+  = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}
+       \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
 %  \label{Choi_1}
 \end{equation}
-After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
-\begin{equation}
- \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
-   = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
-\end{equation}
-with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
+This superoperator is again diagonal in the (multi-qubit) Pauli basis, with the 
+eigenvalue corresponding to 
+$ \kket{\sigma_{\vec{\alpha} }}$ given by 
+% 
+% After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
+% \begin{equation}
+%  \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
+%    = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
+% \end{equation}
+% with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
 \begin{equation}
@@
 \end{equation}
-Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}
-\cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
-qubits.}
+Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}. We wish 
+to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
+$a^N$, which might be more convenient for other applications.
+% \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
+% qubits.}
 % (Proofs in an appendix using binary indices XD)

### 2021-10-27 documentos/math.tex
a \neq HxH

@@
 which we are able to derive several important conclusions. 
-
+\afnote{This section is devoted to derive the conditions a Pauli map need to
+satisfy to fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
+associated to the channel must be non-negative. 
+To do so, we first calculate and diagonalize the matrix associated with general 
+Pauli maps, both for a single qubit and for $N$ qubits. We then restrict to
+PCEs and, for quantum channels, associate a vector space
+to the set of coefficients $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from 
+which we are able to derive several important conclusions.}
 % }}}

### 2021-10-27 documentos/proofdiagonalization.tex
I should have had a V8 this morning.
a \neq HxH

@@
 \end{equation}
-On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may be written as
+On the other hand, the matrix form of an arbitrary Pauli map $\mathcal{E}$ may
+be written as
 \begin{align}
-\hat{\mathcal{E}} & = \frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}},\\
+\hat{\mathcal{E}} & = 
+\frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}} 
+\label{eq:inicio:canal:pauli}\\
 & = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \ddyad{j,j\oplus\nu}{k,k\oplus\nu}.
@@
 \end{equation}
-or more compactly $\vec{\lambda} = \sa~\vec{\tau}$, where $\sa=2^{-1}H\otimes
+or more compactly $\vec{\lambda} = \sa~\vec{\tau}/2$, where $\sa=H\otimes
 H$ and $H$ is the Hadamard matrix.
 
+For the sake of convenience in the demonstration of several useful properties of the PCE channels, throughout the main text we use the matrix 
+\begin{equation}
+\sa=\left(
+\begin{array}{cccc}
+1 &1 &1   &1   \\
+ 1 & 1  & -1&-1   \\
+1  & -1  & 1 & -1\\
+1&-1&-1&1  
+\label{a_appendix}
+\end{array}
+\right),
+\end{equation}
+instead of $H\otimes H$.
+Moreover notice that this can be done due to the fact that both matrices are equivalent up to a permutation of rows.
+In other words this operation corresponds to a relabeling in the eigenvalues $\lambda_{mn}$.
 \subsection{$N$ qubits}
@@
 \begin{equation}
-\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu}}}, 
+\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }}, 
 \end{equation}
@@
 \begin{align}
-\kket{\sigma_{\vec{\mu}\vec{\nu}}} & = \kket{\sigma_{\mu_1\nu_1}}\otimes \cdots \kket{\sigma_{\mu_N\nu_N}},\\
+\kket{\sigma_{\vec{\mu}\vec{\nu} }} & = \kket{\sigma_{\mu_1\nu_1}}\otimes \cdots \kket{\sigma_{\mu_N\nu_N}},\\
 & = \left(\sum_{j_1=0}^{1} (-1)^{j_1 \mu_1}\kket{j_1,j_1\oplus \nu_1}\right)\otimes\cdots \otimes \left(\sum_{j_N=0}^{1} (-1)^{j_N \mu_N}\kket{j_N,j_N\oplus \nu_N}\right),\\
@@
 \begin{equation}
-\bbrakket{\sigma_{\vec{\mu}\vec{\nu}}}{\sigma_{\vec{\mu}'\vec{\nu}'}} = 2^N \delta_{\vec{\mu}\vec{\mu}'}\delta_{\vec{\nu}\vec{\nu}'}.
+\bbrakket{\sigma_{\vec{\mu}\vec{\nu} }}{\sigma_{\vec{\mu}'\vec{\nu}'}} = 2^N \delta_{\vec{\mu}\vec{\mu}'}\delta_{\vec{\nu}\vec{\nu}'}.
 \end{equation}
@@
  & = \frac{1}{2^N}\left(\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{m_1n_1}}\otimes\cdots \otimes\kket{\sigma_{m_Nn_N}}\right),\\
- & = \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n}}}.
+ & = \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
 \label{PauToCompN}
@@
 \begin{align}
-\hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu}}},\\
+\hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }},\\
 = & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.
@@
 \begin{equation}
-\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\substack{\vec{j}\vec{l}\vec{m} \\ \vec{n}\vec{\mu}\vec{\nu}}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l}}}{\sigma_{\vec{n}\vec{l}}}.
+\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\substack{\vec{j}\vec{l}\vec{m} \\ \vec{n}\vec{\mu}\vec{\nu} }} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l} }}{\sigma_{\vec{n}\vec{l} }}.
 \end{equation}
@@
 \begin{align}
-\mathcal{D}_N & = \frac{1}{2^{2N}}\sum_{\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \ddyad{\sigma_{\vec{m}\vec{n}}}{\sigma_{\vec{m}\vec{n}}},\\
-& = \frac{1}{2^{N}}\sum_{\vec{m}\vec{n}} \left( \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \right)\ddyad{\sigma_{\vec{m}\vec{n}}}{\sigma_{\vec{m}\vec{n}}}.
+\mathcal{D}_N & = \frac{1}{2^{2N}}\sum_{\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \ddyad{\sigma_{\vec{m}\vec{n} }}{\sigma_{\vec{m}\vec{n} }},\\
+& = \frac{1}{2^{N}}\sum_{\vec{m}\vec{n}} \left( \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \right)\ddyad{\sigma_{\vec{m}\vec{n} }}{\sigma_{\vec{m}\vec{n} }}.
 \end{align}
@@
 \end{equation}
-or more compactly $\vec{\lambda} = \san~\vec{\tau}$, where $\san=a^{\otimes N}$, $\sa=2^{-1}H\otimes H$ and $H$ is the Hadamard matrix.
+or more compactly $\vec{\lambda} = \san~\vec{\tau}/2^N$, where $\san=a^{\otimes N}$, $\sa=H\otimes H$ and $H$ is the Hadamard matrix.
+
+As in the case of a single qubit, the analyses in the main text employ the matrix $\sa$ defined in Eq. \ref{a_appendix}, to define the $\san=a^{\otimes N}$, instead of $\sa=H\otimes H$.
+
 % }}}

### 2021-10-27 documentos/proofdiagonalization.tex
Fixed the fuck out of #594!

@@
 \subsection{Single qubit}
-In order to simplify the derivation of the relations, let us employ pairs of binary indices instead of a single quaternary, i.e. $\alpha\to\mu+2\nu$. Hence we can write the elements of the Pauli basis
-$(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$, compactly as
-$\sigma_{\mu\nu}=\sum_{j=0}^{1} (-1)^{j \mu}\dyad{j}{j\oplus \nu}$. In vectorized form
+In order to simplify the derivation of the relations, let us employ pairs of
+binary indices instead of a single quaternary, i.e. $\alpha\to j +2 k$. For
+the sake of clarity, we will use Latin symbols for binary indices, and
+reserve the Greek ones for quaternary ones. 
+We can write the elements of the Pauli basis
+$(\sigma_{0},\sigma_{1},i\sigma_{2},\sigma_{3})$, 
+compactly as
+$\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j\oplus l }$. In vectorized form
 \begin{equation}
-\kket{\sigma_{\mu\nu}}=\sum_{j=0}^{1} (-1)^{j \mu}\kket{j,j\oplus \nu},
+\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },
 \end{equation}
-in the same way,
+and its inverse relation,
 \begin{equation}
-\kket{l,l\oplus n}=\frac{1}{2}\sum_{m=0}^{1} (-1)^{ml}\kket{\sigma_{mn}}.
+\kket{k,k\oplus l}=\frac{1}{2}\sum_{j=0}^{1} (-1)^{jk}\kket{\sigma_{jl}}.
 \label{PauToComp}
@@
 \hat{\mathcal{E}} & = 
-\frac{1}{2}\sum_{\mu\nu=0}^{1} \tau_{\mu\nu} \ddyada{\sigma_{\mu\nu}} 
+\frac{1}{2}\sum_{l m=0}^{1} \tau_{l m} \ddyada{\sigma_{l m}} 
 \label{eq:inicio:canal:pauli}\\
-& = \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} \ddyad{j,j\oplus\nu}{k,k\oplus\nu}.
+& = \frac{1}{2}\sum_{jkl m} \tau_{l m} (-1)^{l (j+k)} 
+     \ddyad{j,j\oplus m}{k,k\oplus m}.
 % \label{Map_Pauli}
 \end{align}
-After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the Choi matrix associated to the map. It reads
+After applying the reshuffling operation on $\hat{\mathcal{E}}$, we obtain the
+Choi matrix associated to the map. It reads
 \begin{equation}
  \mathcal{D} = 
-  \frac{1}{2}\sum_{jk\mu\nu} \tau_{\mu\nu} (-1)^{\mu(j+k)} 
-      \ddyad{j,k}{j\oplus\nu,k\oplus\nu}.
+  \frac{1}{2}\sum_{jklm} \tau_{lm} (-1)^{l(j+k)} 
+      \ddyad{j,k}{j\oplus m,k\oplus m}.
 \label{Choi_a1}
 \end{equation}
-Note furthermore that the expression above may also be written as a combination of tensor products of Pauli matrices
-% 
+Note furthermore that the expression above may also be written as a combination
+of tensor products of Pauli matrices
 \begin{equation}
- \mathcal{D} = \frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} \sigma_{\mu\nu} \otimes \sigma_{\mu\nu}^*.
+ \mathcal{D} = 
+   \frac{1}{2}\sum_{l m } \tau_{l m } \sigma_{l m } \otimes \sigma_{l m }^*.
  \label{Choi_Pauli_1q}

### 2021-10-27 documentos/proofdiagonalization.tex
WTF is this.

@@
 \end{equation}
-% 
-Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus m$, then the Choi matrix holds
+Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus
+k$, then the Choi matrix holds
 \begin{equation}
  \mathcal{D} =
-    \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu} (-1)^{\mu m} 
-        \ddyad{j,j\oplus m}{j\oplus\nu,j\oplus\nu\oplus m}.
+    \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} 
+        \ddyad{j,j\oplus k}{j\oplus m,j\oplus m\oplus k}.
+\nonumber
 % \label{Choi_a1}
 \end{equation}
-Due to the fact that we are dealing with binary indices, thus we can safely write the modular sums in the exponents as standard sums.
-By employing the relation between computational and Pauli elements (Eq.
-\ref{PauToComp}), by noticing that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$, and after some steps we have
+\cpnote{Alejo, porfa revise la ecuacion anterior con mucho cuidado}
+Due to the fact that we are dealing with binary indices, thus we can safely
+write the modular sums in the exponents as standard sums. Employing the
+relation between computational and Pauli elements [\eref{PauToComp}],
+noticing that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$, and after some steps we
+have
 \begin{align*}
  \mathcal{D} & = 
-%  \frac{1}{2}\sum_{jm\mu\nu} \tau_{\mu\nu}(-1)^{\mu m}  \left( \frac{1}{2}\sum_{k=0}^{1} (-1)^{kj}\kket{\sigma_{km}}\right)\left(\frac{1}{2}\sum_{n=0}^{1} (-1)^{n(j\oplus\nu)}\bbra{\sigma_{nm}}\right),\\
-\frac{1}{8}\sum_{jkmn\mu\nu} \tau_{\mu\nu}(-1)^{\mu m+kj+n(j\oplus\nu)}  \ddyad{\sigma_{km}}{\sigma_{nm}},\\
-%  & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \left(\sum_{j} (-1)^{j(k+n)} \right) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
-%  & = \frac{1}{8}\sum_{kmn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} (2\delta_{kn}) \ddyad{\sigma_{km}}{\sigma_{nm}},\\
- & = \frac{1}{4}\sum_{mn\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu} \ddyad{\sigma_{nm}}{\sigma_{nm}},\\
- & = \frac{1}{2}\sum_{mn} \left(\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu}\right) \ddyad{\sigma_{nm}}{\sigma_{nm}},
-% \label{Choi_a1}
+\frac{1}{8}\sum_{jkMnl m} \tau_{l m}(-1)^{l  M+kj+n(j\oplus m)} 
+           \ddyad{\sigma_{kM}}{\sigma_{nM}},\\
+ & = \frac{1}{4}\sum_{Mnl  m } \tau_{l  m } (-1)^{l  M+n m } 
+           \ddyad{\sigma_{nM}}{\sigma_{nM}},\\
+ & = \frac{1}{2}\sum_{Mn} 
+      \left(\frac{1}{2}\sum_{l  m } \tau_{l  m } (-1)^{l  M+n m }\right) 
+     \ddyad{\sigma_{nM}}{\sigma_{nM}},
 \end{align*}

### 2021-11-01 documentos/proofdiagonalization.tex
various changes

@@
 % 
-\subsection{Single qubit}
+\subsection{Single qubit} % {{{
 In order to simplify the derivation of the relations, let us employ pairs of
@@
 \kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },
+\label{CompToPau}
 \end{equation}
@@
 Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus
-k$, then the Choi matrix holds
+k$, then the Choi matrix reads
 \begin{equation}
@@
     \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} 
-        \ddyad{j,j\oplus k}{j\oplus m,j\oplus m\oplus k}.
+        \ddyad{j,j\oplus k}{j\oplus m,j\oplus m\oplus k},
 \nonumber
@@
 \end{equation}
-\cpnote{Alejo, porfa revise la ecuacion anterior con mucho cuidado}
-Due to the fact that we are dealing with binary indices, thus we can safely
-write the modular sums in the exponents as standard sums. Employing the
-relation between computational and Pauli elements [\eref{PauToComp}],
-noticing that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$, and after some steps we
-have
+% thanks to a simplification in the argument of the power of $-1$. To continue, 
+since $ (-1)^{j+j\oplus k} = (-1)^k $. To continue, we 
+use the relation between computational and Pauli elements [\eref{PauToComp}],
+and notice that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$. We arrive to the
+simple expression 
 \begin{align*}
  \mathcal{D} & = 
-\frac{1}{8}\sum_{jkMnl m} \tau_{l m}(-1)^{l  M+kj+n(j\oplus m)} 
-           \ddyad{\sigma_{kM}}{\sigma_{nM}},\\
- & = \frac{1}{4}\sum_{Mnl  m } \tau_{l  m } (-1)^{l  M+n m } 
-           \ddyad{\sigma_{nM}}{\sigma_{nM}},\\
- & = \frac{1}{2}\sum_{Mn} 
-      \left(\frac{1}{2}\sum_{l  m } \tau_{l  m } (-1)^{l  M+n m }\right) 
-     \ddyad{\sigma_{nM}}{\sigma_{nM}},
+  \frac{1}{2}\sum_{jk} 
+      \left(\frac{1}{2}\sum_{l  m } 
+(-1)^{l  k+j m }\right) 
+\tau_{l  m } 
+     \ddyad{\sigma_{jk}}{\sigma_{jk}}.
 \end{align*}
-Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
+Notice that  $\mathcal{D}$ is already written in its diagonal form, and one can 
+identify by inspection the eigenvalues. 
+% Due to the fact that we are dealing with binary indices, thus we can safely
+% write the modular sums in the exponents as standard sums. Employing the
+% relation between computational and Pauli elements [\eref{PauToComp}],
+% noticing that $\sum_j(-1)^{j(m\pm n)}=2\delta_{mn}$, and after some steps we
+% have
+% \begin{align*}
+%  \mathcal{D} & = 
+% \frac{1}{8}\sum_{jkMnl m} \tau_{l m}(-1)^{l  M+kj+n(j\oplus m)} 
+%            \ddyad{\sigma_{kM}}{\sigma_{nM}},\\
+%  & = \frac{1}{4}\sum_{Mnl  m } \tau_{l  m } (-1)^{l  M+n m } 
+%            \ddyad{\sigma_{nM}}{\sigma_{nM}},\\
+%  & = \frac{1}{2}\sum_{Mn} 
+%       \left(\frac{1}{2}\sum_{l  m } \tau_{l  m } (-1)^{l  M+n m }\right) 
+%      \ddyad{\sigma_{nM}}{\sigma_{nM}},
+% \end{align*}
+% Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
+The eigenvalues read
 \begin{equation}
-\lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
+\lambda_{jk}=\frac{1}{2}\sum_{l m } 
+(-1)^{jl +k m },
+\tau_{l m } 
+% \lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
+% m -> j 
+% n -> k
+% mu -> l
+% nu -> m
+\label{eq:lambda:is:tau:appendix}
 \end{equation}
-or more compactly $\vec{\lambda} = \sa~\vec{\tau}/2$, where $\sa=H\otimes
-H$ and $H$ is the Hadamard matrix.
+or more compactly $\vec{\lambda} =(1/2) H \otimes H \vec{\tau}$, where 
+$H$ is the Hadamard matrix.
 
-For the sake of convenience in the demonstration of several useful properties of the PCE channels, throughout the main text we use the matrix 
+For the sake of convenience in the demonstration of several useful properties
+of the PCE channels, 
+we shall reorder the eigenvalues, to write 
+\begin{equation}
+\lambda =  \frac12 \sa \tau
+\end{equation}
+with 
 \begin{equation}
@@
 \end{equation}
-instead of $H\otimes H$.
-Moreover notice that this can be done due to the fact that both matrices are equivalent up to a permutation of rows.
-In other words this operation corresponds to a relabeling in the eigenvalues $\lambda_{mn}$.
+instead of $H\otimes H$. This can be done due to the fact
+that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. In other words
+this operation corresponds to a relabeling in the eigenvalues $\lambda_{mn}$.
+% }}}
 \subsection{$N$ qubits}
+To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
+$N$ dimensional vector $\valpha$ with a pair of $N$ dimensional vector binary
+indices $\vec j$ and $\vec k$ so that 
+each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
+single qubit case of the previous subsection. Then, all the steps leading to 
+\eref{eq:lambda:is:tau:appendix} can be redone, but with vector indices instead of binary scalars.
 
-Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
+The tensor product of Pauli matrices, in vector form,  will be denoted by 
+$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
+and fulfill the orthogonality relation 
+$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
+2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$. 
+% \begin{equation}
+% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
+% \end{equation}
+With this in mind, a $N$-qubit Pauli map can be written as 
+% 
+% 
+% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
 \begin{equation}
-\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }}, 
+\hat{\mathcal{E}}_N = 
+  \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }}. 
 \end{equation}
-where
-\begin{widetext}
+The generalization of \eref{CompToPau} and \eref{PauToComp} read
 \begin{align}
-\kket{\sigma_{\vec{\mu}\vec{\nu} }} & = \kket{\sigma_{\mu_1\nu_1}}\otimes \cdots \kket{\sigma_{\mu_N\nu_N}},\\
-& = \left(\sum_{j_1=0}^{1} (-1)^{j_1 \mu_1}\kket{j_1,j_1\oplus \nu_1}\right)\otimes\cdots \otimes \left(\sum_{j_N=0}^{1} (-1)^{j_N \mu_N}\kket{j_N,j_N\oplus \nu_N}\right),\\
-& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{j_1,j_1\oplus \nu_1}\otimes\cdots \otimes \kket{j_N,j_N\oplus \nu_N},\\
-& = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},
+\kket{\sigma_{\vec{\mu}\vec{\nu} }}  & = 
+   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},\\
+%
+ \kket{\vec{l},\vec{l}\oplus \vec{n}} & = 
+   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
 \end{align}
-\end{widetext}
-and
-\begin{equation}
-\bbrakket{\sigma_{\vec{\mu}\vec{\nu} }}{\sigma_{\vec{\mu}'\vec{\nu}'}} = 2^N \delta_{\vec{\mu}\vec{\mu}'}\delta_{\vec{\nu}\vec{\nu}'}.
-\end{equation}
 
-Recall the relation between the computational and Pauli basis elements (Eq. \ref{PauToComp}), hence for the $N$-qubits case we have
+% where
+% \begin{widetext}
+% \begin{align}
+% \kket{\sigma_{\vec{\mu}\vec{\nu} }} & = \kket{\sigma_{\mu_1\nu_1}}\otimes \cdots \kket{\sigma_{\mu_N\nu_N}},\\
+% & = \left(\sum_{j_1=0}^{1} (-1)^{j_1 \mu_1}\kket{j_1,j_1\oplus \nu_1}\right)\otimes\cdots \otimes \left(\sum_{j_N=0}^{1} (-1)^{j_N \mu_N}\kket{j_N,j_N\oplus \nu_N}\right),\\
+% & = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{j_1,j_1\oplus \nu_1}\otimes\cdots \otimes \kket{j_N,j_N\oplus \nu_N},\\
+% & = \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},
+% \end{align}
+% \end{widetext}
+% and
+% \begin{equation}
+% \bbrakket{\sigma_{\vec{\mu}\vec{\nu} }}{\sigma_{\vec{\mu}'\vec{\nu}'}} = 2^N \delta_{\vec{\mu}\vec{\mu}'}\delta_{\vec{\nu}\vec{\nu}'}.
+% \end{equation}
 % 
+% Recall the relation between the computational and Pauli basis elements (Eq. \ref{PauToComp}), hence for the $N$-qubits case we have
+% % 
 \begin{widetext}

### 2021-11-01 documentos/proofdiagonalization.tex
Fix hard-coded [object Object] string (thanks!)

@@
 simple expression 
-\begin{align*}
+\begin{align}
  \mathcal{D} & = 
@@
      \ddyad{\sigma_{jk}}{\sigma_{jk}}.
-\end{align*}
+\label{eq:D:diagonalize}
+\end{align}
 Notice that  $\mathcal{D}$ is already written in its diagonal form, and one can 
@@
 \lambda_{jk}=\frac{1}{2}\sum_{l m } 
-(-1)^{jl +k m },
-\tau_{l m } 
+(-1)^{jl +k m }
+\tau_{l m },
 % \lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
@@
 % }}}
-\subsection{$N$ qubits}
+\subsection{$N$ qubits} % {{{
 To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
@@
 \hat{\mathcal{E}}_N = 
-  \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }}. 
+  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
 \end{equation}
@@
 % % 
-\begin{widetext}
+% \begin{widetext}
+% \begin{align}
+%  \kket{\vec{l},\vec{l}\oplus \vec{n}} & = \kket{l_1,l_1\oplus n_1} \otimes\cdots \otimes \kket{l_N,l_N\oplus n_N} \\
+%   & = \left( \frac{1}{2}\sum_{m_1=0}^{1} (-1)^{m_1l_1}\kket{\sigma_{m_1n_1}}\right)\otimes\cdots \otimes\left(\frac{1}{2}\sum_{m_N=0}^{1} (-1)^{m_Nl_N}\kket{\sigma_{m_Nn_N}}\right),\\
+%  & = \frac{1}{2^N}\left(\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{m_1n_1}}\otimes\cdots \otimes\kket{\sigma_{m_Nn_N}}\right),\\
+%  & = \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
+% \label{PauToCompN}
+% \end{align}
+% \end{widetext}
+By employing the previous relations, we can write the matrix representation of
+the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
 \begin{align}
- \kket{\vec{l},\vec{l}\oplus \vec{n}} & = \kket{l_1,l_1\oplus n_1} \otimes\cdots \otimes \kket{l_N,l_N\oplus n_N} \\
-  & = \left( \frac{1}{2}\sum_{m_1=0}^{1} (-1)^{m_1l_1}\kket{\sigma_{m_1n_1}}\right)\otimes\cdots \otimes\left(\frac{1}{2}\sum_{m_N=0}^{1} (-1)^{m_Nl_N}\kket{\sigma_{m_Nn_N}}\right),\\
- & = \frac{1}{2^N}\left(\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{m_1n_1}}\otimes\cdots \otimes\kket{\sigma_{m_Nn_N}}\right),\\
- & = \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
-\label{PauToCompN}
+\hat{\mathcal{E}} 
+% & = \frac{1}{2}\sum_{l m=0}^{1} \tau_{l m} \ddyada{\sigma_{l m}} 
+& = \frac{1}{2}\sum_{\vec j\vec k\vec l \vec m} 
+     \tau_{\vec l \vec m} (-1)^{\vec l (\vec j+\vec k)} 
+     \ddyad{\vec j,\vec j\oplus \vec m}{\vec k,\vec k\oplus \vec m}.
+% \label{eq:inicio:canal:pauli:N}
+% \label{Map_Pauli}
 \end{align}
-\end{widetext}
-By employing the previous relations, we can write the matrix representation of the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
+% 
+% 
+% \begin{align}
+% \hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }},\\
+% = & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.
+% \end{align}
+In this way it is straightforward to apply the reshuffling operation on
+$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix 
+then transform back to the Pauli basis  and simplify to obtain 
 \begin{align}
-\hat{\mathcal{E}}_N = & \frac{1}{2^N}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} \ddyada{\sigma_{\vec{\mu}\vec{\nu} }},\\
-= & \frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{j}\oplus \vec{\nu}}{\vec{k},\vec{k}\oplus \vec{\nu}}.
+\mathcal{D}_N & = 
+   \frac{1}{2^{N}}\sum_{\vec{m}\vec{n}} \left( 
+        \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} (-1)^{\vec{l}\cdot\vec{n}+\vec{m}\cdot\vec{m}} \right)\ddyad{\sigma_{\vec{m}\vec{n} }}{\sigma_{\vec{m}\vec{n} }}.
 \end{align}
-In this way it is straightforward to apply the reshuffling operation on $\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix,
-\begin{equation}
-\mathcal{D}_N =\frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{k}}{\vec{j}\oplus \vec{\nu},\vec{k}\oplus \vec{\nu}}.
-\end{equation}
-After the change of vector indices $\vec{k}=\vec{j}\oplus\vec{l}$, the Choi matrix holds
-\begin{equation}
-\mathcal{D}_N =\frac{1}{2^N}\sum_{\vec{j}\vec{l}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{j}\oplus\vec{l})} \ddyad{\vec{j},\vec{j}\oplus\vec{l}}{\vec{j}\oplus \vec{\nu},\vec{j}\oplus \vec{\nu}\oplus \vec{l}}.
-\end{equation}
-Back to the vectorized Pauli basis (Eq. \ref{PauToCompN}) we have
-\begin{equation}
-\mathcal{D}_N = \frac{1}{2^{3N}}\sum_{\substack{\vec{j}\vec{l}\vec{m} \\ \vec{n}\vec{\mu}\vec{\nu} }} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{l}+\vec{j}\vec{m}+(\vec{j}\oplus\vec{\nu})\cdot\vec{n}} \ddyad{\sigma_{\vec{m}\vec{l} }}{\sigma_{\vec{n}\vec{l} }}.
-\end{equation}
-On the other hand, recall the relation $\sum_{\vec{j}}(-1)^{\vec{j}\cdot(\vec{m}+\vec{n})}=2^N\delta_{\vec{m}\vec{n}}$. After some steps $\mathcal{D}_N$ reduces to 
-\begin{align}
-\mathcal{D}_N & = \frac{1}{2^{2N}}\sum_{\vec{m}\vec{n}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \ddyad{\sigma_{\vec{m}\vec{n} }}{\sigma_{\vec{m}\vec{n} }},\\
-& = \frac{1}{2^{N}}\sum_{\vec{m}\vec{n}} \left( \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}} \right)\ddyad{\sigma_{\vec{m}\vec{n} }}{\sigma_{\vec{m}\vec{n} }}.
-\end{align}
+All intermediate steps, from \eref{eq:inicio:canal:pauli} to 
+\eref{eq:D:diagonalize} are similar, but with a vectorized version of the 
+indices, and appropriate normalization constants. 
+Again, we are left with an expression that displays explicitly the eigenvalues of 
+the Choi matrix, so we can write 
+% \begin{equation}
+% \mathcal{D}_N =\frac{1}{2^N}\sum_{\vec{j}\vec{k}\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot(\vec{j}+\vec{k})} \ddyad{\vec{j},\vec{k}}{\vec{j}\oplus \vec{\nu},\vec{k}\oplus \vec{\nu}}.
+% \end{equation}
 Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
 \begin{equation}
-\lambda_{\vec{m}\vec{n}}= \frac{1}{2^{N}}\sum_{\vec{\mu}\vec{\nu}} \tau_{\vec{\mu}\vec{\nu}} (-1)^{\vec{\mu}\cdot\vec{n}+\vec{\nu}\cdot\vec{m}}
+\lambda_{\vec{j}\vec{n}}= \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} 
+    (-1)^{\vec{j}\cdot\vec{l}+\vec{k}\cdot\vec{m}}
+    \tau_{\vec{l}\vec{m}} 
 \end{equation}
-or more compactly $\vec{\lambda} = \san~\vec{\tau}/2^N$, where $\san=a^{\otimes N}$, $\sa=H\otimes H$ and $H$ is the Hadamard matrix.
-
-As in the case of a single qubit, the analyses in the main text employ the matrix $\sa$ defined in Eq. \ref{a_appendix}, to define the $\san=a^{\otimes N}$, instead of $\sa=H\otimes H$.
+or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 
+Again, we prefer to reorganize the indices to be able to write
+\begin{equation}
+\lambda = \frac{1}{2^N} A \tau, 
+\end{equation}
+where 
+\begin{equation}
+\san=a^{\otimes N}. 
+\end{equation}
+% As in the case of a single qubit, the analyses in the main text employ the
+% matrix $\sa$ defined in Eq. \ref{a_appendix}, to define the $\san=a^{\otimes
+% N}$, instead of $\sa=H\otimes H$.
 
 % }}}
+% }}}

### 2021-11-03 documentos/generators.tex
Esqueleto v1

@@
 }
+
+\colorbox{yellow}{\textcolor{blue}{Esqueleto}}
+\textcolor{jacolor}{
+\begin{itemize}
+\item Siguiendo la discusión de los espacios vectoriales de la sección anterior, 
+introducir de forma consecuente los generadores como subespacios maximales. 
+Es decir, darle una retocada a lo que ya escribió Francois, pero que armonice 
+con lo que viene de la sección anterior.
+\item Ilustrar el algoritmo para construir todos los PCEs como 
+concatenaciones de los generadores. Comentar al final del párrafo que, para 
+1 qubit, nuestro descubrimiento de los PCEGs es compatible con los resultados 
+de Siudzinska~\cite{siudzinska2019geometry} sobre el espacio en el tetrahedro 
+en el que ella encontró que viven los canales cuánticos que son accesibles 
+mediante generadores. **en algún lado aquí se puede decir que en el apéndice 
+se muestra con los tableros como generar todo el caso de 2 qubits
+\item Ya que expusimos en el párrafo anterior la utilidad de los generadores, 
+hablar de la relación de los generadores con la $A$, como una forma de 
+obtenerlos. El enunciado principal podría ser algo como "The matrix $A$ 
+contains all the information of PCE quantum channels". Es una frase fuerte, 
+pero creo que con un poco de meditación es cierto; de la $A$ puedes sacar 
+los generadores, y con ellos todos los PCEs, se acabó. 
+\item Hablar de las simetrías de los generadores. (No sé a qué se refiere quien 
+escribió eso. Toca hablarlo con Carlos.)
+\end{itemize}}
 

### 2021-11-03 documentos/proofdiagonalization.tex
diaaaaaazeeeeeeeeeepam
Appendix_D

@@
 the sake of clarity, we will use Latin symbols for binary indices, and
-reserve the Greek ones for quaternary ones. 
+reserve the Greek ones for quaternary ones \afnote{(and
+reserve Greek letters for quaternary ones)}. 
 We can write the elements of the Pauli basis
@@
 \end{align}
+\afnote{Creo que es mejor dejar el tau dentro del parentesis para dejar implícito que está sumando también.}
 Notice that  $\mathcal{D}$ is already written in its diagonal form, and one can 
@@
 % Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
-The eigenvalues read
+The eigenvalues read \
 \begin{equation}
@@
 \end{equation}
-The generalization of \eref{CompToPau} and \eref{PauToComp} read
+The generalization of \eref{CompToPau} and \eref{PauToComp} read \afnote{eq. $\to$ Eq.}
 \begin{align}
@@
 \end{align}
+\afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}
 
@@
 In this way it is straightforward to apply the reshuffling operation on
-$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix 
+$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix, 
 then transform back to the Pauli basis and simplify to obtain 
@@
 Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
+\afnote{Creo que esta ultima linea se puede borrar.}
 \begin{equation}
@@
 \end{equation}
+\afnote{Aqui los vectores $l$ y $m$ en el exponente estan cambiados}
 or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 
@@
 where 
-\begin{equation}
-\san=a^{\otimes N}. 
-\end{equation}
+$\san=a^{\otimes N}$. 
+% \begin{equation}
+% \san=a^{\otimes N}. 
+% \end{equation}
 % As in the case of a single qubit, the analyses in the main text employ the

### 2021-11-04 documentos/proofdiagonalization.tex
Whee, good night.

--- 2021-11-01 documentos/proofdiagonalization.tex
@@
 the sake of clarity, we will use Latin symbols for binary indices, and
-reserve the Greek ones for quaternary ones. 
+reserve Greek letters for quaternary ones. 
 We can write the elements of the Pauli basis
@@
       \left(\frac{1}{2}\sum_{l  m } 
-(-1)^{l  k+j m }\right) 
+(-1)^{l  k+j m }
 \tau_{l  m } 
+\right) 
      \ddyad{\sigma_{jk}}{\sigma_{jk}}.
@@
 \begin{equation}
-\lambda_{jk}=\frac{1}{2}\sum_{l m } 
-(-1)^{jl +k m }
-\tau_{l m },
+\lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{jl +k m } \tau_{l m },
 % \lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
@@
 \end{equation}
-The generalization of \eref{CompToPau} and \eref{PauToComp} read
+The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
 \begin{align}
-\kket{\sigma_{\vec{\mu}\vec{\nu} }}  & = 
-   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},\\
+\kket{\sigma_{\vec{k}\vec{l} }}  & = 
+   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \kket{\vec{j},\vec{j}\oplus \vec{l}},\\
 %
@@
 \end{align}
+% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}
 
@@
 % \end{equation}
-Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
+% Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
+% \afnote{Creo que esta ultima linea se puede borrar.}
 \begin{equation}
@@
     \tau_{\vec{l}\vec{m}} 
+% \lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{jl +k m } \tau_{l m },
 \end{equation}
+\afnote{Aqui los vectores $l$ y $m$ en el exponente estan cambiados}
 or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 

### 2021-11-08 documentos/math.tex
really ignore ignored worsd
Comentarios sobre draft sección III.intro y III.A

--- 2021-10-27 documentos/math.tex
@@
 % Intro {{{
-This section is devoted to derive the conditions a Pauli map need to
-satisfy to fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
-associated to the channel must be non-negative. 
-To do so, we first calculate and diagonalize the matrix associated with general 
-Pauli maps, 
-first for a single qubit and then for $N$ qubits. We then restrict to
-PCEs and, for quantum channels, associate a vector space
-to the set of coefficients $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from 
-which we are able to derive several important conclusions.
-
+This section is devoted to derive the conditions a Pauli map needs to satisfy to
+fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
+associated to the channel \sout{must be}\janote{are} non-negative.  To do so, we calculate
+and diagonalize the \janote{Choi} matrix associated with general Pauli maps, first for a
+single qubit and then for $N$ qubits. We then restrict to PCEs and, for quantum
+channels, associate a vector space to the set of coefficients
+$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from which we are able to
+derive several important conclusions. 
 % }}}
@@
 \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
-\delta_{\alpha\alpha'}$.
+\delta_{\alpha\alpha'}$~\janote{cita?}.
 In this language, 
@@
 \end{array}
-\right)
+\right).
 % =\frac12\sa^{-1}.
@@
 Hadamard matrix, and still diagonalize the same Choi matrix. This is due to the
-fact that $a$ corresponds to a permutation of rows of  $H \otimes H$. However
-we chose $a$ as some later considerations [see  \eref{eq:sigma_property}]
+fact that $a$ corresponds to a permutation of rows of  $H \otimes H$. However,
+we chose \janote{to keep} $a$ \janote{as in \eqref{eq:1},} as some later considerations [see  \eref{eq:sigma_property}]
 cannot be written easily in terms of $H \otimes H$.
@@
  $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}}$, and satisfy the orthogonality relation
+\otimes\kket{\sigma_{\alpha_N}}$\janote{aquí hay algo extraño, pues los operadores 
+que utilizamos son la vectorización del producto tensorial de las paulis, no los
+productos tensoriales de las paulis vectorizadas, que es lo que entiendo con la 
+expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
+\otimes\kket{\sigma_{\alpha_N}}$}, and satisfy the orthogonality relation
 $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
-\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
+\delta_{\vec{\alpha}\vec{\alpha}'}$\janote{cita?}. The matrix representation of the
 map corresponding to \eref{eq:definition:Pauli} is 
@@
 to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
-$a^N$, which might be more convenient for other applications.
+$a^N$, which might be more convenient for other applications.\janote{en una 
+iteración posterior del artículo completo quizás es buena idea enmarcar más esto
+último de la otra a, ya que puede ser de interés en alguna aplicación}
 % \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 

### 2021-11-10 documentos/pce.tex
Comentario para Carlos
starting the service is always better

@@
 \section{PCE Maps} 
-\subsection{Quantum channels} % {{{
-Quantum channels comprehend the most general linear operations that a quantum
-system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
-their construction and properties, first let us define several objects. We will
-denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
-$\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will
-be written as $\mcB(\hilbert)$, the subset of density matrices as
-$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
-operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
-here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
+\subsection{Quantum channels} % {{{ Quantum channels comprehend the most
+general linear operations that a quantum system undergo independently of its
+past~\cite{zimansbook,cirac}. To introduce their construction and properties,
+first let us define several objects. We will denote Hilbert spaces as \hilbert
+and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded
+operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$,
+the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset
+of the so called trace-class operators $\mcT(\hilbert)$, for the finite
+dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$
+coincide~\cite{zimansbook}.
 
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preserving and complete positivity. The first one is needed to
+linearity, trace preserving and complete positivity. The trace preserving
+property is needed to
 send convex combinations of density matrices into the convex combination of the
@@
 thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
-trace preserving is required for the process $\mcE$ to be deterministic, this
+trace preserving property is required for the process $\mcE$ to be deterministic, this
 is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
@@
 $\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
-$\Delta\geq 0$. In the other hand, complete positvity of $\mcE$ reads $\id_k
-\otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where $\omega$ is the Bell state
-between the system and an ancilla with Hilbert space $\hilbert_k$. Therefore,
+$\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
+decimos que es una matriz de densidad}. In the other hand, complete positivity
+of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where
+$\omega$ is the Bell state
+between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
+E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }. Therefore,
 complete positivity ensures that every positive semidefinite operator of any
@@
 
-Quantum channels can be characterized by means of the Choi-\jami{} isomorphism~\cite{choi,jamil}.
-This is, given a linear operation $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it, $C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the Bell state between to copies of \hilbert, is positive semi-definite if and only if $\mcE$ is completely positive.
+Quantum channels can be characterized by means of the Choi-\jami{}
+isomorphism~\cite{choi,jamil}. This is, given a linear operation
+$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it,
+$C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
+$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
+Bell state between two copies of \hilbert, is positive semi-definite if and only
+if $\mcE$ is completely positive.
 
-Quantum channels have the well-known \textit{Kraus representation} (or operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho K^\dagger{}_i$ in fact, a linear operation is completely positive if and only if it has a Kraus representation [cite Kraus book]
+Quantum channels have the well-known \textit{Kraus representation} (or
+operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho
+K^\dagger{}_i$ in fact, a linear operation is completely positive if and only
+if it has a Kraus representation [cite Kraus book] 
+\flnote{
+probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
+$\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
+Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
+}
 
-  \ddnote{[Choi representation, Kraus operators and Stinespring
-dilation]}
+  \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
 
-It can be seen from Kraus decomposition that quantum channels preserve hermiticity, this has a practical consequence when using hermitian bases. $\hat \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j]
- \right)$
+It can be seen from Kraus decomposition that quantum channels preserve
+hermiticity, this has a practical consequence when using hermitian bases. $\hat
+\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$
 
@@
 
-\begin{itemize}
-\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
-y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
-que mover si es que necesitamos herramientas que discutiremos mas adelante para
-hacer notar la diferencia}
-\end{itemize}
-
 The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
@@
 
-%  $r_{\vec \alpha} =  $
-% where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.
-
 Consider the linear operations that simply attenuate the Pauli components of 
@@
 \end{equation}
-These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$.
-Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
- \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-frases. También debemos tener un nombre pues lo de la diagonazliación funciona
-para eso y quizá también seran relevantes para la parte de decoherencia}
-\ddnote{De momento no he encontrado alguna reference, para qubits si, pero para
-los generales no, estoy checando de nuevo el paper de Ruskai para entender que
-tanto se solapan, a ver si puedo decir algo}.
 For the operation to preserve the trace of the density matrix, we require that
 $\tau_{\vec 0}=1$.  
+% These operations are diagonal in the basis $\left\{
+% 2^{-N/2}\sigma_{\vec \alpha} \right\}$, which follows from
+% \eref{eq:sigma_property}. 
+% The diagonal components are $\taus$, i.e. $\hat
+% \mcE=\diag(\taus)$. Additionally, they belong to the subset of unital channels
+% that can be written as convex combinations of unitary channels. \cpnote{Alguien 
+% puso aca que lo probarian, pero no lo hemos discutido y quizá no le veo 
+% el caso en este articulo}
+\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
+Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
+si se mencionan a los canales  \cite{Siudzinska2020}}
+
+\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
+frases de la importancia de esta familia.} \ddnote{De momento no he encontrado
+alguna reference, para qubits si, pero para los generales no}.
+
 A Pauli component erasing (PCE) operation is a Pauli diagonal operation
@@
 from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill with black 
-the corresponding position \cpnote{No me pone feliz esta redaccion}
-if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
+the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
 empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
@@
 % \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
 \end{scope} % }}}
@@
 $\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
-(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
+(b), (c) and (d) correspond to the identity map, dephasing channel, and 
 total depolarization, respectively. In (e) we show a map that only erases the component

### 2021-11-10 documentos/pce.tex
microavance

--- 2021-10-22 documentos/pce.tex
@@
 denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
-$\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will
-be written as $\mcB(\hilbert)$, the subset of density matrices as
-$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
-operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
-here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
+$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
+be written as $\mcB(\hilbert)$.
+%, the subset of density matrices as
+%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
+%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
+%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
 
@@
 linearity, trace preserving and complete positivity. The first one is needed to
-send convex combinations of density matrices into the convex combination of the
+send convex combinations of density matrices into the convex combinations of the
 evolution of such density matrices, this is, let $\mcE$ such linear operation,
@@
 trace preserving is required for the process $\mcE$ to be deterministic, this
-is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
-happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
+is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
+happen with probability equal to one. The complete
 positivity condition is needed to preserve positive semidefiniteness and handle
@@
 \end{center}
+\janote{Faltó el contorno negro en (e)??}
 	\caption{In (a) we introduce the positions of the single 

### 2021-11-10 documentos/math.tex
Arreglo de notación del vector prod tensorial de matrices de Pauli

@@
 fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
-associated to the channel \sout{must be}\janote{are} non-negative.  To do so, we calculate
-and diagonalize the \janote{Choi} matrix associated with general Pauli maps, first for a
+associated to the channel are non-negative.  To do so, we calculate
+and diagonalize the Choi matrix associated with general Pauli maps, first for a
 single qubit and then for $N$ qubits. We then restrict to PCEs and, for quantum
@@
 % }}}
-\subsection{Diagonalization of Choi matrix} 
-% \subsubsection{Single qubit Pauli channels} % {{{
-
-% \afnote{Notación para matrices densidad vectorizadas? $\varrho$ ?}
-% \janote{Qué tal $\vec\rho\quad$?}
-% \afnote{Por ahora uso este $\kket{\rho}$}
-
+\subsection{Diagonalization of Choi matrix} % {{{
+\cpnote{Aca Francois escribio algo que puede sustituir 
+el inicio del parrafo, pero estoy esperando la fuente }
 We now study the matrix form of the single qubit map $\mathcal{E}$ in
 order to construct the associated Choi matrix. 
-% and the conditions the set of parameters
-% $\{\tau_{\alpha}\}$ need to satisfy in order to $\mathcal{E}$ be considered a
-% quantum channel. 
 To do so, we shall denote operators in the superoperator space with the symbol
@@
 \left(\sigma_{\alpha}^{\dagger} \sigma_{\alpha'}\right) = 2
-\delta_{\alpha\alpha'}$~\janote{cita?}.
-In this language, 
-the state reads
+\delta_{\alpha\alpha'}$.
+In this language, the state reads
 $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$
-and the 
-% By writing the density matrix in vector form
-% $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$, the
-matrix form of the map $\mathcal{E}$ is
+and the matrix form of the map $\mathcal{E}$ is
 % 
@@
 \ddyada{\sigma_{\alpha}}.
-% \label{Map_Pauli}
 \end{equation}
-%
-% where the kets $\kket{\sigma_{\alpha}}$ correspond to the vectorized elements
-% of the Pauli basis and satisfy the usual relation $ \bbrakket{{\sigma_{\alpha}
-% }}{{\sigma_{\alpha'} }} = \tr \left(\sigma_{\alpha}^{\dagger}
-% \sigma_{\alpha'}\right) = 2 ~\delta_{\alpha\alpha'}$. 
 After some steps, detailed from \eref{eq:inicio:canal:pauli} to
@@
 \end{equation}
-Notice that, despite the similarity, $\ddyada{\sigma_{\alpha}}$ 
+Notice that $\ddyada{\sigma_{\alpha}}$ 
 and $\sigma_{\alpha} \otimes \sigma_{\alpha}^*$ are different operators.
+\cpnote{Aca tambien metio un rollo Francois que resulta muy util.}
 % \cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}
@@
 expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}}$}, and satisfy the orthogonality relation
+\otimes\kket{\sigma_{\alpha_N}}$}\janote{mi sugerencia es nada más reescribir
+$\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}\otimes\cdots
+\otimes\sigma_{\alpha_N}}$}, and satisfy the orthogonality relation
 $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
@@
 \hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
-% \label{Map_Pauli}
 \end{equation}

### 2021-11-10 documentos/math.tex
Who has two thumbs and remembers the rudiments of his linear algebra courses?  Apparently, this guy.

@@
 \subsection{Diagonalization of Choi matrix} % {{{
-\cpnote{Aca Francois escribio algo que puede sustituir 
-el inicio del parrafo, pero estoy esperando la fuente }
-We now study the matrix form of the single qubit map $\mathcal{E}$ in
-order to construct the associated Choi matrix. 
-To do so, we shall denote operators in the superoperator space with the symbol
-$\kket{\cdot}$. For example, $\kket{\sigma_{\alpha}}$ correspond to the
-vectorized elements of the Pauli basis and satisfy the usual relation 
+
+\flnote{
+We now construct the Choi matrix associated to the single qubit map
+$\mathcal{E}$. As described above, $\mathcal{E}$ is a linear map from
+$\mcB(\hilbert)$ to itself. We shall denote elements of
+$\mcB(\hilbert)$ by the notation $\kket{\cdot}$. Thus, for instance,
+$\kket{\sigma_\alpha}$ represents the Pauli matrix $\sigma_\alpha$ understood
+as a vector belonging to $\mcB(\hilbert)$, for the present case, in which
+$\hilbert={\mathbb{C}^2}$. Since the scalar product on $\mcB(\hilbert)$ is
+given by  $\bbrakket{A_1}{A_2}=\tr A_1^\star A_2$,
+} 
+% We now study the matrix form of the single qubit map $\mathcal{E}$ in
+% order to construct the associated Choi matrix. 
+% To do so, we shall denote operators in the superoperator space with the symbol
+% $\kket{\cdot}$. For example, $\kket{\sigma_{\alpha}}$ correspond to the
+% vectorized 
+elements of the Pauli basis and satisfy the relation 
 $\bbrakket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr
@@
 and $\sigma_{\alpha} \otimes \sigma_{\alpha}^*$ are different operators.
-\cpnote{Aca tambien metio un rollo Francois que resulta muy util.}
+\flnote{
+Indeed, the former acts as a linear map upon the vector space $\mcB(\hilbert)$,
+whereas the latter acts on the tensor product $\hilbert\otimes\hilbert$. Of
+course, there is a basis dependent identification between these two
+spaces, which is used 
+in the construction of the Choi matrix~\cite{}. 
+}
 % \cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}

### 2021-11-10 documentos/pce.tex

--- 2021-11-10 documentos/pce.tex
@@
 \section{PCE Maps} 
+\subsection{Quantum channels} % {{{
+Quantum channels comprehend the most general linear operations that a quantum
+system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
+their construction and properties, first let us define several objects. We will
+denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
+$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
+be written as $\mcB(\hilbert)$.
+%, the subset of density matrices as
+%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
+%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
+%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.
+
+The construction of quantum channels includes basically three ingredients:
+linearity, trace preserving and complete positivity. The first one is needed to
+send convex combinations of density matrices into the convex combinations of the
+evolution of such density matrices, this is, let $\mcE$ such linear operation,
+thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
+trace preserving is required for the process $\mcE$ to be deterministic, this
+is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
+happen with probability equal to one. The complete
 \subsection{Quantum channels} % {{{ Quantum channels comprehend the most
@@
 happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
+>>>>>>> 50430f9b3813da4a6f9b09d9b473cf9477afefd3
 positivity condition is needed to preserve positive semidefiniteness and handle

### 2021-11-10 documentos/math.tex
This is why git rebase is a horrible horrible thing.

@@
 and $\sigma_{\alpha} \otimes \sigma_{\alpha}^*$ are different operators.
-\flnote{
 Indeed, the former acts as a linear map upon the vector space $\mcB(\hilbert)$,
@@
 in the construction of the Choi matrix~\cite{}. 
-}
 % \cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}

### 2021-11-11 documentos/vector_space.tex
Comentarios sobre draft sección III.intro y III.A
Transpiled mainframe.

@@
 espacio. Quizá cuando haga falta se puede poner}
+\janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
+se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
+parece una buena idea podría elaborar más cómo meterlo ahí}
 \par
@@
 % Los canales tiene 2^K componente {{{
-We can then see that all PCE quantum channels preserve $2^K$ components. In
-fact, with the above picture, it is clearly revealed that the vector space has
-dimension $2N$. Moreover, 
-consider any subspace and chose the maximum number of linearly independent
-elements (say $K$).  Any of the  $2^K$ subsets of those elements will yield a
-unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
-elements of the vector space. This means that any PCE quantum channel will preserve $2^K$ 
-components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
-\par
 
-The dimension of the vector space $V$ of all multi-indices is $2N$, and we have
+% **********************************
+% 
+% We can show that all PCE quantum channels preserve $2^K$ components. 
+% In
+% fact, with the above picture, it is clearly revealed that the vector space has
+% dimension $2N$. Moreover, 
+% consider any subspace and chose the maximum number of linearly independent
+% elements (say $K$).  Any of the  $2^K$ subsets of those elements will yield a
+% unique element. Moreover, since $\valpha + \valpha = \vec 0$, these are all
+% elements of the vector space. This means that any PCE quantum channel will preserve $2^K$ 
+% components, for $K$ an integer. See \fref{fig:examplesPCE} for some examples. 
+% \par 
+% 
+% **********************************
+% **********************************
+
+We can show that all PCE quantum channels preserve $2^K$ components. 
+First recall that a vector space of dimension $d$ over a field of $q$ elements
+has $q^d$ elements~\cite{CitaAlgebraLineal}.
+Now $V$ is a vector space on a field of two elements having dimension $2N$. 
+% The dimension of the vector space $V$ of all multi-indices is $2N$, and 
+We have
 seen earlier that
@@
 \end{equation}
-is a subspace of $V$. As such, $W$ has a given dimension $K$, which means that
+is a subspace of $V$. 
+As such, $W$ has a given dimension $K$, which means that
 $W$ has $2^K$ elements. In other words, a vector $\vec\tau$ with the property
@@
 
-\cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
-primero (simón, cambié de opinión)} \par
+% **********************************
+% **********************************
+% 
+% \cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
+% primero (simón, cambié de opinión)} \par
 

### 2021-11-13 documentos/generators.tex
Pequeño avance en el esqueleto

@@
 
-\janote{Mis suferencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
+\janote{Mis sugerencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
 explicar a punta de las figuras PCE cómo generar todos los canales PCE 
@@
 }
+
+%\esqueletoja{By standard theorems of linear algebra, any subspace $W$ 
+%in \eqref{eq:19}, associated with a unique PCE quantum channel, can be 
+%extended to a maximal subspace of dimension $2N-1$ by adjoining appropiate
+%additional basis elements.}
 
@@
 
+\esqueletoja{There exists a subset of PCE quantum channels that generate 
+all of the PCE's and the existence of these generators may be explained with 
+the vector space point of view.}
+
+\esqueletoja{The matrix $\san$ [see \eref{eq:san}] encodes all the information
+of PCE generators and, therefore, of PCE quantum channels.}
+
+\esqueletoja{Given the existence of PCE generators one can cons}
+
 By standard theorems of linear algebra, any subspace $W$ can be extended to a

### 2021-11-16 documentos/generators.tex
Esqueleto v2

--- 2021-10-18 documentos/generators.tex
@@
 
-\janote{Mis suferencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
-explicar a punta de las figuras PCE cómo generar todos los canales PCE 
-de 2 qubits. Sólo es necesario mostrar cómo se generan elementos representativos
-de cada clase de equivalencia. [Ya se habló de las clases de equivalencia a
-esta altura del artículo?] Esto es algo que se puede poner en un apéndice.\newline\indent
-(2) Para el caso de 1 qubit, nuestra noción de generadores es compatible 
-con los resultados de Siudzinska \cite{siudzinska2019geometry} sobre 
-el espacio en el tetraedro de los canales cuánticos que son accesibles 
-mediante generadores locales de tiempo. Quizás una referencia es 
-apropiada.\newline\indent
-(3) Hablar sobre la relación entre los generadores y filas o columnas de la $A$.
-Esto lo podemos discutir con más detalles, Carlos. 
-}
+%\janote{Mis sugerencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
+%explicar a punta de las figuras PCE cómo generar todos los canales PCE 
+%de 2 qubits. Sólo es necesario mostrar cómo se generan elementos representativos
+%de cada clase de equivalencia. [Ya se habló de las clases de equivalencia a
+%esta altura del artículo?] Esto es algo que se puede poner en un apéndice.\newline\indent
+%(2) Para el caso de 1 qubit, nuestra noción de generadores es compatible 
+%con los resultados de Siudzinska \cite{siudzinska2019geometry} sobre 
+%el espacio en el tetraedro de los canales cuánticos que son accesibles 
+%mediante generadores locales de tiempo. Quizás una referencia es 
+%apropiada.\newline\indent
+%(3) Hablar sobre la relación entre los generadores y filas o columnas de la $A$.
+%Esto lo podemos discutir con más detalles, Carlos. 
+%}
 
+%\esqueletoja{By standard theorems of linear algebra, any subspace $W$ 
+%in \eqref{eq:19}, associated with a unique PCE quantum channel, can be 
+%extended to a maximal subspace of dimension $2N-1$ by adjoining appropiate
+%additional basis elements.}
+
+%\colorbox{yellow}{\textcolor{blue}{Esqueleto}}
+%\textcolor{jacolor}{
+%\begin{itemize}
+%\item Siguiendo la discusión de los espacios vectoriales de la sección anterior, 
+%introducir de forma consecuente los generadores como subespacios maximales. 
+%Es decir, darle una retocada a lo que ya escribió Francois, pero que armonice 
+%con lo que viene de la sección anterior.
+%\item Ilustrar el algoritmo para construir todos los PCEs como 
+%concatenaciones de los generadores. Comentar al final del párrafo que, para 
+%1 qubit, nuestro descubrimiento de los PCEGs es compatible con los resultados 
+%de Siudzinska~\cite{siudzinska2019geometry} sobre el espacio en el tetrahedro 
+%en el que ella encontró que viven los canales cuánticos que son accesibles 
+%mediante generadores. **en algún lado aquí se puede decir que en el apéndice 
+%se muestra con los tableros como generar todo el caso de 2 qubits
+%\item Ya que expusimos en el párrafo anterior la utilidad de los generadores, 
+%hablar de la relación de los generadores con la $A$, como una forma de 
+%obtenerlos. El enunciado principal podría ser algo como "The matrix $A$ 
+%contains all the information of PCE quantum channels". Es una frase fuerte, 
+%pero creo que con un poco de meditación es cierto; de la $A$ puedes sacar 
+%los generadores, y con ellos todos los PCEs, se acabó. 
+%\item Hablar de las simetrías de los generadores. (No sé a qué se refiere quien 
+%escribió eso. Toca hablarlo con Carlos.)
+%\end{itemize}}
+
+\esqueletoja{There exists a subset of PCE quantum channels that generate 
+all PCE's, and the existence of these PCE generators may be explained with 
+the vector space point of view.}
+
+\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
+del nuebo párrafo.}
 By standard theorems of linear algebra, any subspace $W$ can be extended to a
@@
 the result that all PCE's can be obtained as intersections of maximal PCE's.
+
+\esqueletoja{For the case of 1 qubit the existence of PCE generators is  
+verified by Siudzińska~\cite{siudzinska2019geometry}.} \janote{Esto puede
+ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
+
+\esqueletoja{The matrix $\san$ [see \eref{eq:san}] encodes all the information
+of PCE generators and, therefore, of the PCE quantum channels.} \janote{Aquí
+tendrá que ir una prueba que aún se está cocinando}
+
+\janote{Aquí croe que podría hablar de las `simetrías de los PCEGs', pero necesito
+estar seguro a qué te refieres con eso, Carlos. Te refieres a aquella regla que 
+tú encontraste con la que se pueden encontrar todos los generadores? Que 
+para los tableritos es como ir desdoblando en mitades?}
+
+\esqueletoja{The set of all PCE quantum channels may be sorted in subsets, 
+which we will call equivalence classes, whose
+elements are equivalent via particle swaps and local-basis element
+permutations. Then, the algorithm to generate all PCEs reduces to finding
+only representative elements of every equivalence class.} \janote{aquí planeo 
+hacer una referencia al apéndice que para ver la construccón en figuritas 
+del caso de 2 qubits}
 

### 2021-11-16 documentos/pce.tex
quito colision

@@
 happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
->>>>>>> 50430f9b3813da4a6f9b09d9b473cf9477afefd3
 positivity condition is needed to preserve positive semidefiniteness and handle

### 2021-11-17 documentos/generators.tex
Esqueleto v2.1

@@
 \section{Generators} % {{{
-\todo{Francois escribe una primera version del primer punto, y luego quizá Jose
-Alfredo o Carlos la terminan}
+%\todo{Francois escribe una primera version del primer punto, y luego quizá Jose
+%Alfredo o Carlos la terminan}
 
@@
 
-\esqueletoja{There exists a subset of PCE quantum channels that generate 
+\janote{\colorbox{yellow}{¡¡¡Léeme Carlos!!!:} Las frases nuevas que hacen
+parte del esqueleto y que no estaban ayer, miércoles, son las que aparecen 
+en las líneas 412, 422 y 425.}
+
+There exists a subset of PCE quantum channels that generate 
 all PCE's, and the existence of these PCE generators may be explained with 
-the vector space point of view.}
-
+the vector space point of view.
 \janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
-del nuebo párrafo.}
+del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
 By standard theorems of linear algebra, any subspace $W$ can be extended to a
@@
 the result that all PCE's can be obtained as intersections of maximal PCE's. 
+\janote{Referenciar \Fref{fig:examplesPCE} y apéndice con una ilustración 
+del caso de 2 qubits usando los $\mcG$. Mostrar en ese apéndice todos
+los generadores de 2 qubits}
 
-\esqueletoja{For the case of 1 qubit the existence of PCE generators is  
-verified by Siudzińska~\cite{siudzinska2019geometry}.} \janote{Esto puede
+PCE generators may be characterized with a unique vector index
+$\vec\alpha$, and therefore, denoted as $\pceg$.
+
+For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
+verified by Siudzińska~\cite{siudzinska2019geometry}.
+\janote{Esto puede
 ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
 
-\esqueletoja{The matrix $\san$ [see \eref{eq:san}] encodes all the information
-of PCE generators and, therefore, of the PCE quantum channels.} \janote{Aquí
+The matrix $\san$ [see \eref{eq:san}] encodes all the information
+of PCE generators $\pceg$ and, therefore, of the PCE quantum channels. \janote{Aquí
 tendrá que ir una prueba que aún se está cocinando}
 
-\janote{Aquí croe que podría hablar de las `simetrías de los PCEGs', pero necesito
-estar seguro a qué te refieres con eso, Carlos. Te refieres a aquella regla que 
-tú encontraste con la que se pueden encontrar todos los generadores? Que 
-para los tableritos es como ir desdoblando en mitades?}
+PCE generators $\pceg$ (and so $\san$'s rows and columns) obey a symmetry rule
+that defines uniquely every PCE generator.
 
-\esqueletoja{The set of all PCE quantum channels may be sorted in subsets, 
+PCE generators $\pceg$ may be classified by its local action on 
+all individual qubits in the system.
+
+-------------------------------------------------------------------
+The set of all PCE quantum channels may be sorted in subsets, 
 which we will call equivalence classes, whose
 elements are equivalent via particle swaps and local-basis element
-permutations. Then, the algorithm to generate all PCEs reduces to finding
-only representative elements of every equivalence class.} \janote{aquí planeo 
-hacer una referencia al apéndice que para ver la construccón en figuritas 
-del caso de 2 qubits}
+permutations. 
+\janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
+Aún hay que decidirlo con los demás.}
 
-Quizá poner las reglas de simetría de los generadores.
-
-Quizá en un apendice poner todos los generadores de dos qubits.
-
-También poner como se pueden calsificar los generadores y por aih poner la clasificacion de los 
-generadores en la figura.  o en el texto
-
-\begin{itemize}
-\item Clasificacion de los generadores, es decir que para dos qubits, lo podemos indicar con la acción sobre cada qubit individual
-\item Quizá mostrar algunas propiedades de simetrías. 
-\item Notar lo de los generadores y como sale la estructura jerárquica 
-\end{itemize}
+%Quizá en un apendice poner todos los generadores de dos qubits. 
+%\janote{Poner el comentario en algún lado de que hay que hacer una
+%referencia a un apéndice.}
+%
+%\janote{falta escribir un párrafo sobre la clasificación: (la clasificación 
+%es de que cada generador está caracterizado por un $\alpha$)}
+%También poner como se pueden calsificar los generadores y por aih poner la clasificacion de los 
+%generadores en la figura.  o en el texto
+%
+%\begin{itemize}
+%\item Clasificacion de los generadores, es decir que para dos qubits, lo podemos indicar con la acción sobre cada qubit individual
+%\item Quizá mostrar algunas propiedades de simetrías. 
+%\item Notar lo de los generadores y como sale la estructura jerárquica 
+%\end{itemize}
 % }}}

### 2021-11-17 documentos/generators.tex
Puta yo ya vivo en el futuro..

@@
 \janote{\colorbox{yellow}{¡¡¡Léeme Carlos!!!:} Las frases nuevas que hacen
-parte del esqueleto y que no estaban ayer, miércoles, son las que aparecen 
+parte del esqueleto y que no estaban ayer, martes, son las que aparecen 
 en las líneas 412, 422 y 425.}

### 2021-11-17 documentos/generators.tex
permanent hack, do not revert

@@
 parte del esqueleto y que no estaban ayer, martes, son las que aparecen 
-en las líneas 412, 422 y 425.}
+en las líneas 412, 422 y 425.  a todonote at line \lineref{lne:label1}}
 
@@
 PCE generators may be characterized with a unique vector index
-$\vec\alpha$, and therefore, denoted as $\pceg$.
+$\vec\alpha$, and therefore, denoted as $\pceg$. \linelabel{lne:label1}
 

### 2021-11-17 documentos/generators.tex
Committing fixes in the dark, seriously, who killed my power!?

--- 2021-11-17 documentos/generators.tex
@@
 
-\janote{\colorbox{yellow}{¡¡¡Léeme Carlos!!!:} Las frases nuevas que hacen
-parte del esqueleto y que no estaban ayer, martes, son las que aparecen 
-en las líneas 412, 422 y 425.}
-
 There exists a subset of PCE quantum channels that generate 
@@
 los generadores de 2 qubits}
-
-PCE generators may be characterized with a unique vector index
-$\vec\alpha$, and therefore, denoted as $\pceg$.
-
 For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
@@
 ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
+
+PCE generators may be characterized with a unique vector index
+$\vec\alpha$, and therefore, denoted as $\pceg$. El numero de generadores 
+concide con esa vaina. 
+PCE generators $\pceg$ may be classified by its local action on 
+all individual qubits in the system.
+\cpnote{Acuerdate de la referencia a la figura 4}
 
@@
 that defines uniquely every PCE generator.
-
-PCE generators $\pceg$ may be classified by its local action on 
-all individual qubits in the system.
+\cpnote{Acuerdate de otra referencia a la figura 4}
 

### 2021-11-18 documentos/pce.tex
para revisar linea

@@
 happen with probability equal to one. The complete
-\subsection{Quantum channels} % {{{ Quantum channels comprehend the most
-general linear operations that a quantum system undergo independently of its
-past~\cite{zimansbook,cirac}. To introduce their construction and properties,
-first let us define several objects. We will denote Hilbert spaces as \hilbert
-and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded
-operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$,
-the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset
-of the so called trace-class operators $\mcT(\hilbert)$, for the finite
-dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$
-coincide~\cite{zimansbook}.
 

### 2021-11-18 documentos/pce.tex
totally more readable
dandole

@@
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preserving and complete positivity. The first one is needed to
-send convex combinations of density matrices into the convex combinations of the
-evolution of such density matrices, this is, let $\mcE$ such linear operation,
-thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
-trace preserving is required for the process $\mcE$ to be deterministic, this
-is $\tr\mcE[\rho]=\tr \rho =1$ for any density matrix $\rho$, \ie{} the process $\mcE$ will
-happen with probability equal to one. The complete
-
-The construction of quantum channels includes basically three ingredients:
 linearity, trace preserving and complete positivity. The trace preserving
@@
 positivity condition is needed to preserve positive semidefiniteness and handle
-the non-local character of quantum theory. This is, with positivity of the map
-$\mcE$ one has $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ with
-$\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
-decimos que es una matriz de densidad}. In the other hand, complete positivity
-of $\mcE$ reads $\id_k \otimes \mcE[\omega]\geq 0$ for $k=1,2,\dots$, where
-$\omega$ is the Bell state
+the non-local feature of quantum theory.
+A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues
+decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto.
+Sin embargo esos casos no son relevantes en este contexto por supuesto}.
+In the other hand, a map is completely positive if
+ $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
 between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
-E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }. Therefore,
+E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}. Therefore,
 complete positivity ensures that every positive semidefinite operator of any
@@
 Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
-}
+}\ddnote{trabajando en ello, hacia falta edicion aqui}
 

### 2021-11-19 documentos/pce.tex
avanzando

@@
 thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
-trace preserving property is required for the process $\mcE$ to be deterministic, this
-is, $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
-happen to the state $\rho$, with $\rho \in \mcS(\hilbert)$. The complete
+trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
+happen to the state $\rho\in \mcS(\hilbert)$. The complete
 positivity condition is needed to preserve positive semidefiniteness and handle
@@
  $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
-between the system and an ancilla with Hilbert space $\hilbert_k$\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
-E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}. Therefore,
-complete positivity ensures that every positive semidefinite operator of any
+between the system and an ancilla with Hilbert space $\hilbert_k$. This ensures that every positive semidefinite operator of any
 extension of the system (where the quantum channel is now a local operation) is
-mapped into positive semidefinite operators, trace preserving is automatically
-fulfilled for all extensions if $\mcE$ is. Thus, any density matrix of a system
+mapped into positive semidefinite operators. The trace preserving is automatically
+fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
 where $\mcE$ acts locally, is sent to a valid density matrix, this is the
 substance of complete positivity.
+\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
+E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}
 
@@
 isomorphism~\cite{choi,jamil}. This is, given a linear operation
-$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it,
-$C_\mcE=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
+$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
+$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called dynamical matrix), where
 $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
-Bell state between two copies of \hilbert, is positive semi-definite if and only
-if $\mcE$ is completely positive.
+Bell state between two copies of \hilbert. The map \mcE is completely positive if and only
+\choi is positive-semidefinite.
 
-Quantum channels have the well-known \textit{Kraus representation} (or
-operator-sum representation) which reads $\mcE[\rho]=\sum_i K_i \rho
-K^\dagger{}_i$ in fact, a linear operation is completely positive if and only
+Furthermore, quantum channels have the well-known \textit{Kraus representation} (or
+operator-sum representation) which reads 
+\begin{equation}
+\mcE[\rho]=\sum_i K_i \rho
+K_i^\dagger{}
+\end{equation}
+ in fact, a linear operation is completely positive if and only
 if it has a Kraus representation [cite Kraus book] 
@@
 % 
-% \begin{figure} % {{{
-% 	\centering
-% 	\hfill \hfill
-% 	\includegraphics[height=2.5cm]	{tablero_1qubit}
-% 	\hfill
-% 	\includegraphics[height=2.5cm]{tablero_2qubits}
-% %	\hspace{1mm}
-% %	\includegraphics[height=2.7cm]{rho-3q}
-% 	\hfill \hfill \hfill
-% 	\caption{From left to right representations of identity map
-% 	(also PCE operations) of 1 and 2 qubits, respectively.}
-% 	\label{fig:PCE_figs}
-% \end{figure} % }}}
 %
-% \begin{figure} % {{{
-% 	\centering
-% 	\includegraphics[height=2.5cm]	{1qubit_PCEChannels}
-% 	\caption{1 qubit PCE channels. }
-% 	\label{fig:1qubit_PCEChannles}
-% \end{figure} % }}}
 

### 2021-11-22 documentos/pce.tex
avanzando

@@
 
-Furthermore, quantum channels have the well-known \textit{Kraus representation} (or
+Furthermore, quantum channels enjoy the well-known \textit{Kraus representation} (or
 operator-sum representation) which reads 
@@
 \end{equation}
- in fact, a linear operation is completely positive if and only
-if it has a Kraus representation [cite Kraus book] 
+with $\sum_i K_i^\dagger{}K_i=\one$ (the trace preserving condition). In fact, a linear operation is completely positive if and only
+if it has a Kraus representation~\cite{Kraus1983}. The minimum number of Kraus operators $K_i$ needed to represent the channel is called \textit{Kraus rank}. 
+%
+It can be seen from Kraus decomposition that quantum channels preserve
+hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
+\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases consisting in the so-called \textit{Pauli strings}, defined as 
+\begin{equation}
+\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
+\label{eq:pauli_strings}
+\end{equation}
+where $N$ is the number of two-level particles (\aka{} qubits), with $alpha_i$. Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal
+
 \flnote{
@@
 Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
-}\ddnote{trabajando en ello, hacia falta edicion aqui}
+}\ddnote{ejecutado, hacia falta edicion, sin embargo lo de hermiticity preserving es para hacer incapie en por que podemos trabajar en una representacion totalmente real de los canales.}
 
   \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
-
-It can be seen from Kraus decomposition that quantum channels preserve
-hermiticity, this has a practical consequence when using hermitian bases. $\hat
-\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$
 
@@
 \todo{David escribe una primera version y luego Carlos itera}
+\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, which in the case of one particle, it consist on maps nullifying averages $\langle \sigma_i \rangle$ with $i=1,2,3$.
 Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that

### 2021-11-23 documentos/generators.tex
Iteración 1 de la redacción

@@
 the vector space point of view.
-\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
-del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
-By standard theorems of linear algebra, any subspace $W$ can be extended to a
+%\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
+%del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
+By standard theorems of linear algebra, any subspace $W$ [see. \Eref{eq:19}] can be extended to a
 maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
-additional basis elements. This can clearly be done in different ways. We
-therefore arrive to the set of maximal extensions of $W$. Clearly, the
-intersection of all the elements of this set reduces to $W$ itself, leading to
-the result that all PCE's can be obtained as intersections of maximal PCE's. 
-\janote{Referenciar \Fref{fig:examplesPCE} y apéndice con una ilustración 
-del caso de 2 qubits usando los $\mcG$. Mostrar en ese apéndice todos
-los generadores de 2 qubits}
-For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
-verified by Siudzińska~\cite{siudzinska2019geometry}.
-\janote{Esto puede
-ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
+additional basis elements. This can clearly be done in different ways. 
+We therefore arrive to the set of maximal extensions of $W$,
+where every maximal subspace corresponds to a PCE quantum channel that 
+preserves $2^{2N-1}$ (half the) Pauli components $\paulicomponents$ 
+of density matrix $\rho$. The
+intersection of all the elements of this set reduces to $W$ itself, meaning 
+that all PCE's can be obtained as intersections of maximal PCE's, the
+PCE generators $\mcG$. Intersections of the maximal subspaces translates into 
+compositions of the generators $\mcG$ to obtain any PCE.
+Compositions of generators $\mcG$ can be understood intuitively from PCE diagrams
+in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE generators 
+in (c), (d), or (e) is represented by taking the intersection between them both
+and the three different possible compositions result in PCE channel in (b).
+The existence of the PCE generators $\mcG$ provide the program of 
+constructing all PCE channels a tool that avoids the usage of a 
+high-computational-cost method. In a moment, we will discuss how to find the 
+generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
+$\mcG$ and matrix $A$ in \Eref{eq:san}.
+%For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
+%verified by Siudzińska~\cite{siudzinska2019geometry}.
+%\janote{Esto puede
+%ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
 
-PCE generators may be characterized with a unique vector index
-$\vec\alpha$, and therefore, denoted as $\pceg$. El numero de generadores 
-concide con esa vaina. 
-PCE generators $\pceg$ may be classified by its local action on 
-all individual qubits in the system.
-\cpnote{Acuerdate de la referencia a la figura 4}
+PCE generators may be identified with a unique vector index
+$\vec\alpha$, and thus be denoted as $\pceg$.
+% El numero de generadores concide con esa vaina. 
+%Let us introduce a convention for the following discussion for 
+%the indices in $\vec\alpha$; the number 0 to 3 identifies
+Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
+the identity map and the 3 1-qubit PCE quantum channels that project the 
+Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
+Therefore we will correspond every PCE generator to a collection of numbers 
+that tells what its local-action is on every individual qubit in the system.
+All of this collections of numbers happen to be all vector indices $\{\valpha\}$.
+For example, the PCE generator represented in \Fref{fig:examplesPCE}(c),
+whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
+to the $x$ axis and on the second qubit (first row) to map the corresponding
+local Bloch sphere to itself, may be characterized with the vector index (1,0). 
+Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
+every PCE generator and so denote them as $\pceg$.
+
+PCE generators $\pceg$ obey a symmetry
+that defines uniquely every PCE generator. The coefficients  $\{\taus\}$ of every 
+generator $\pceg$ arranged in a hypercubic $N$-dimensional array 
+%of dimensions $\underbrace{4\times 4\times\ldots\times 4}_{N}$ 
+obey a symmetry with respect to the $N$ hyperplanes of dimension $N-1$
+\janote{según wikipedia, por definición, los hiperplanos son de dimensión 
+$N-1$. Así que podría quitarse la aclaración de la dimensión. Lo dejo así y 
+espero retroalimentación} 
+that separate the array into two half arrays \janote{No estoy tan satisfecho con la redacción de este enunciado}.
+See, in \Fref{fig:examplesPCE}, that generators $\mcG_{(1,3)}$, $\mcG_{(3,2)}$
+and $\mcG_{(2,2)}$ represented in (c), (d) and (e), respectively,
+are either symmetric or anti-symmetric with respect to the lines that cut vertically 
+and horizontally in half the diagrams. In fact, this symmetry may be used to
+construct all generators $\pceg$ as follows. Start out with $\tau_{0,\ldots,0}=1$
+and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
+whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
+respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
+\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
+$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
+for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
+the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
+anti-symmetric to the previous subset. For example, let us illustrate the 
+procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
+One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
+$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
+$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
+to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
+the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
+eight.
 
 The matrix $\san$ [see \eref{eq:san}] encodes all the information
-of PCE generators $\pceg$ and, therefore, of the PCE quantum channels. \janote{Aquí
-tendrá que ir una prueba que aún se está cocinando}
+of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
+The rows and columns of matrix $A$ also obey the symmetry previously discussed 
+for PCE generators $\pceg$. It suffices to check that rows and columns of matrix $a$
+in \Eref{eq:1} obey the aforementioned symmetry when they are arranged in a hypercubic 
+$N$-dimensional array of order $4$.
+As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
+rows and columns of $A$. 
+Therefore, this establishes a deep connection between the matrix $A$ and 
+PCE quantum channels. It allows one to infer the PCE generators $\pceg$
+by taking its corresponding coefficients $\{\taus\}$ as the rows or columns of $A$ 
+after taking $-1\mapsto0$. In \appref{sec:2_qubits} we illustrate this program 
+for 2-qubits PCE channels.
+In short, it is sufficient to have the matrix $A$ to construct 
+all PCE quantum channels.
+%\janote{Aquí
+%tendrá que ir una prueba que aún se está cocinando}
 
-PCE generators $\pceg$ (and so $\san$'s rows and columns) obey a symmetry rule
-that defines uniquely every PCE generator.
-\cpnote{Acuerdate de otra referencia a la figura 4}
+- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
 
--------------------------------------------------------------------
 The set of all PCE quantum channels may be sorted in subsets, 

### 2021-11-23 documentos/pce.tex
avanzando

@@
 \end{equation}
-where $N$ is the number of two-level particles (\aka{} qubits), with $alpha_i$. Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal
+where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ and $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
+Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$.
 
@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, which in the case of one particle, it consist on maps nullifying averages $\langle \sigma_i \rangle$ with $i=1,2,3$.
+\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, thus, the case of one particle consists of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$.
 Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that

### 2021-11-23 documentos/pce.tex
qubit examples

@@
 Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$.
+Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
 
@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, thus, the case of one particle consists of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$.
-Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
+\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, in the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$.
+The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
 \begin{equation}
-\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
+\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
 \end{equation}
-then they are defined as follows
+Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
 \begin{equation}
-r_i \mapsto \tau_i r_i
+r_\alpha \mapsto \tau_\alpha r_\alpha
 \end{equation}
-where $\tau_k$ is either $1$ or $0$. A direct evaluation of the
-
+where $\tau_k$ is either $1$ or $0$.
+It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel.
+A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
+\begin{align}
+1+\tau_1+\tau_2+\tau_3 &\geq 0 \nonumber \\
+1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
+\end{align}
+show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and bit-phase flip channels~\cite{chuangbook}.
+These channels can be pictured with one column tables, see~\fref{fig:one:qubit:examples}.
+Finally notice that the condition $\tau_0=1$ is needed to have trace-preserving maps.
 These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.

### 2021-11-23 documentos/pce.tex
quito cosas de decoherencia de un qubit

@@
 They form a tetrahedron in the space of eigenvalues
-
-with
-\begin{equation}
-\mcL_\alpha[\Delta]:= \frac{\gamma}{2}\left( \sigma_\alpha \Delta \sigma_\alpha -\Delta \right).
-\label{eq:1qubit_semigroup}
-\end{equation}
-We will show later that this can be trivially generalized to the $N$ qubit case.
-
-\begin{align}
-U_\alpha\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_\alpha \ket{\psi}\ket{1} \right)\\
-U_\alpha\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_\alpha \ket{\psi}\ket{1} \right)
-\label{eq:1qubit_stinespring}
-\end{align}
-similar to the semigroup generator, we will show later that this can be trivially generalized to the $N$ qubit case.
-
-\begin{itemize}
-\item The single qubit case, describe some of the features.
-\item Single qubit Kraus operators.
-\item Single qubit relation with decoherence. 
-\end{itemize}
 % }}}
@@
 total depolarization, respectively. In (e) we show a map that only erases the component
-$r_1$ and thus does not correspond to a quantum operation.}
+$r_1$, collapsing the Block sphere into a disk, and thus does not correspond to a quantum operation.}
 	\label{fig:one:qubit:examples}

### 2021-11-23 documentos/generators.tex
TODO: Tell someone to implement this

@@
 
-There exists a subset of PCE quantum channels that generate 
-all PCE's, and the existence of these PCE generators may be explained with 
-the vector space point of view.
+There exists a subset of PCE channels that generate 
+all PCEs; the nature of these generators may be studied, as we
+shall see, with the properties of the aforementioned vector space.
 %\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
 %del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
-By standard theorems of linear algebra, any subspace $W$ [see. \Eref{eq:19}] can be extended to a
-maximal (non-trivial) subspace of dimension $2N-1$ by adjoining appropriate
-additional basis elements. This can clearly be done in different ways. 
-We therefore arrive to the set of maximal extensions of $W$,
+By standard theorems of linear algebra, any subspace $W$, see \Eref{eq:19}, 
+can be extended to a maximal non-trivial subspace of dimension $2N-1$ by
+adjoining appropriate additional basis elements. This can be done in
+different ways. We therefore arrive to the set of maximal extensions of $W$,
 where every maximal subspace corresponds to a PCE quantum channel that
-preserves $2^{2N-1}$ (half the) Pauli components $\paulicomponents$ 
-of density matrix $\rho$. The
-intersection of all the elements of this set reduces to $W$ itself, meaning 
-that all PCE's can be obtained as intersections of maximal PCE's, the
-PCE generators $\mcG$. Intersections of the maximal subspaces translates into 
-compositions of the generators $\mcG$ to obtain any PCE.
-Compositions of generators $\mcG$ can be understood intuitively from PCE diagrams
-in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE generators 
+preserves half of the Pauli components. The intersection of all the elements of
+this set reduces to $W$ itself,
+and since intersection of subspaces translates to composition of PCEs,
+this implies that all PCEs \cpnote{damm la identidad} can be obtained as
+compositions the PCEs corresponding to maximally non-trivial subspaces, 
+which we call generators. 
+Compositions of generators can be understood intuitively from PCE
+diagrams in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE
+generators 
 in (c), (d), or (e) is represented by taking the intersection between them both

### 2021-11-23 documentos/generators.tex
bifurcation

@@
 which we call generators. 
-Compositions of generators can be understood intuitively from PCE
-diagrams in \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE
+\cpnote{Aca voy}
+Consider \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE
 generators 

### 2021-11-24 documentos/pce.tex
avance
Typo

@@
 \end{equation}
-with $\sum_i K_i^\dagger{}K_i=\one$ (the trace preserving condition). In fact, a linear operation is completely positive if and only
+with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition). In fact, a linear operation is completely positive if and only
 if it has a Kraus representation~\cite{Kraus1983}. The minimum number of Kraus operators $K_i$ needed to represent the channel is called \textit{Kraus rank}. 
@@
 \begin{align}
-1+\tau_1+\tau_2+\tau_3 &\geq 0 \nonumber \\
+1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
 1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
@@
 show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and bit-phase flip channels~\cite{chuangbook}.
-These channels can be pictured with one column tables, see~\fref{fig:one:qubit:examples}.
+These channels can be pictured with one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
 Finally notice that the condition $\tau_0=1$ is needed to have trace-preserving maps.

### 2021-11-25 documentos/pce.tex

@@
 Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
+%
+$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$
+%
 
@@
 \end{align}
-show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and bit-phase flip channels~\cite{chuangbook}.
+where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
 These channels can be pictured with one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
-Finally notice that the condition $\tau_0=1$ is needed to have trace-preserving maps.
-These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.
+These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.
 They form a tetrahedron in the space of eigenvalues

### 2021-11-25 documentos/generators.tex
Agregada potencial figura para ver la simetría en la a y PCEGs de 1 qubit
Please no changes this time.

@@
 %del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
-By standard theorems of linear algebra, any subspace $W$, see \Eref{eq:19}, 
+By standard theorems of linear algebra, any proper subspace $W$, see \Eref{eq:19}, 
 can be extended to a maximal non-trivial subspace of dimension $2N-1$ by
@@
 and since intersection of subspaces translates to composition of PCEs,
-this implies that all PCEs \cpnote{damm la identidad} can be obtained as
-compositions the PCEs corresponding to maximally non-trivial subspaces, 
-which we call generators. 
-\cpnote{Aca voy}
-Consider \Fref{fig:examplesPCE}; the composition of any two 2-qubits PCE
-generators 
-in (c), (d), or (e) is represented by taking the intersection between them both
-and the three different possible compositions result in PCE channel in (b).
+this implies that all PCEs can be obtained as
+compositions the PCEs corresponding to maximally non-trivial subspaces, plus
+the identity map. In other words, the set of PCEs that preserve half 
+of the components plus the identity map, are a generator set for 
+all PCE channels.
+% and the complete vector space (corresponding to the identity channel),
+% which we call generators. 
+% \cpnote{Aca tenemos un semigrupo y no se si incluir a la identidad como 
+% generador. De alguna manera es excepcional. Es problematico incluirla y es 
+% problematico no incluirla.}
+Consider \Fref{fig:examplesPCE}; subfigures (c), (d) and (e) represent nontrivial 
+generators and the composition of any two of them yield the PCE channel
+corresponding to (b). 
+% 
+% 
+% the composition of any two 2-qubits PCE
+% generators 
+% in (c), (d), or (e) is equivalent to taking the intersection between them both
+% and the three different possible compositions result in PCE channel in (b).
+\cpnote{Aca se me hace que hay un cambio brusco de tema. Ver que onda
+con Jose Alfredo}
 The existence of the PCE generators $\mcG$ provide the program of 
@@
 generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
-$\mcG$ and matrix $A$ in \Eref{eq:san}.
+$\mcG$ and matrix $A$ in \Eref{eq:san}\cpnote{Como que para que ahora se
+menciona entonces?}.
 %For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
@@
 
+\cpnote{Arreglar}
 PCE generators may be identified with a unique vector index
@@
 
+\cpnote{Mucha lora y no se prueba nada}
 PCE generators $\pceg$ obey a symmetry
@@
 
+\begin{figure} % {{{
+\centering
+\includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
+\caption{\janote{Propuesta de figura para mostrar que generadores 
+y la a obedecen las mismas simetrías.}}
+\end{figure} % }}}
+
+\cpnote{Mucha lora y no se prueba nada, again}
 The matrix $\san$ [see \eref{eq:san}] encodes all the information
@@
 %tendrá que ir una prueba que aún se está cocinando}
+
+\cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
+del primer parrafo}
 

### 2021-11-30 documentos/generators.tex
Comments on corrections added

@@
 and horizontally in half the diagrams. In fact, this symmetry may be used to
-construct all generators $\pceg$ as follows. Start out with $\tau_{0,\ldots,0}=1$
+construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$
 and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
@@
 \cpnote{Mucha lora y no se prueba nada, again}
-The matrix $\san$ [see \eref{eq:san}] encodes all the information
+The matrix $\san$ (and thus $a$) [see \eref{eq:san}] encodes all the information
 of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
@@
 As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
-rows and columns of $A$. 
+rows and columns of $A$. \janote{falta prueba}
 Therefore, this establishes a deep connection between the matrix $A$ and 

### 2021-11-30 documentos/images/twoQ_PCEGs_4by4_v2.tex
Another option for 2-qubit PCEGs fig

\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{tikz}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\newcommand{\mcG}{\mathcal{G}}

\begin{document}
\pagestyle{empty}
\begin{center}
\includegraphics[width=.5\textwidth]{twoQ_PCEGs_v2}
\begin{tikzpicture}[x=1mm,y=1mm,overlay,remember picture]
\node[inner sep=0pt] (usac) at (-88.5,77.5) {\Huge \textcolor{Red}{$\cdot$}};
\node[inner sep=0pt] (usac) at (-69.8,87.5)  {\Huge \textcolor{Red}{$\cdot$}};
\node[inner sep=0pt] (usac) at (-66,87.5) {\Huge \textcolor{Red}{$\cdot$}};
%\node[inner sep=0pt] (usac) at (-88.5,97) {\Huge .};
\node[inner sep=0pt] (usac) at (-79.15,76) {\large $\mcG_{(0,0)}$};
\node[inner sep=0pt] (usac) at (-56.65,76) {\large $\mcG_{(0,1)}$};
\node[inner sep=0pt] (usac) at (-34.15,76) {\large \textcolor{Red}{$\mcG_{(0,2)}$}};
\node[inner sep=0pt] (usac) at (-11.65,76) {\large \textcolor{Red}{$\mcG_{(0,3)}$}};
\node[inner sep=0pt] (usac) at (-75,61) {\large \textcolor{Red}{$\mcG_{(1,0)}$}};
\node[inner sep=0pt] (usac) at (-52,61) {\large \textcolor{Red}{$\mcG_{(1,1)}$}};
\node[inner sep=0pt] (usac) at (-29,61) {\large \textcolor{Red}{$\mcG_{(1,2)}$}};
\node[inner sep=0pt] (usac) at (-7,61) {\large \textcolor{Red}{$\mcG_{(1,3)}$}};
\node[inner sep=0pt] (usac) at (-75,39.5) {\large \textcolor{Red}{$\mcG_{(2,0)}$}};
\node[inner sep=0pt] (usac) at (-52,39.5) {\large \textcolor{Red}{$\mcG_{(2,1)}$}};
\node[inner sep=0pt] (usac) at (-29,39.5) {\large \textcolor{Red}{$\mcG_{(2,2)}$}};
\node[inner sep=0pt] (usac) at (-7,39.5) {\large \textcolor{Red}{$\mcG_{(2,3)}$}};
\node[inner sep=0pt] (usac) at (-75,17) {\large \textcolor{Red}{$\mcG_{(3,0)}$}};
\node[inner sep=0pt] (usac) at (-52,17) {\large \textcolor{Red}{$\mcG_{(3,1)}$}};
\node[inner sep=0pt] (usac) at (-29,17) {\large \textcolor{Red}{$\mcG_{(3,2)}$}};
\node[inner sep=0pt] (usac) at (-7,17) {\large \textcolor{Red}{$\mcG_{(3,3)}$}};
\end{tikzpicture}
\end{center}
\end{document}

### 2021-12-03 documentos/intro.tex
the magic is real
Arrrrgggg
etc

@@
 Several PRA articles go straight into matter. I guess we will write what we have to write
+
+Creo que puede quedar bonito, honesto y util si comenzamos motivando el
+problema desde un punto de vista matemático, y luego seguimos platicando de las
+consecuencias físicas, es decir mostrando que el problema como lo planteamos
+tiene aplicaciones practicas.
+
+Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
+\begin{equation}
+\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
+\end{equation}
+and \textit{completely depolarizing},
+\begin{equation}
+\rho \mapsto \frac{\one}{2} \tr \rho,
+\end{equation}
+These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
 % }}}

### 2021-12-06 documentos/intro.tex
dandole

@@
 
+Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
 Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,

### 2021-12-09 documentos/generators.tex
Medio corregido el párrafo de la caracterización. Falta explicación rigurosa

@@
 
+Un párrafo de intro a las tres ideas 
+\begin{itemize}
+\item Existen los generadores 
+\item Clasificación de los generadores 
+\item Simetrías
+\end{itemize}
+
+In this section we will discuss the existence of a generator set for all PCE
+quantum channels, how to label each element of this set according to its local-action to 
+every qubit in the system, and, finally, we  	will discuss a symmetry of
+both PCE quantum channel generators and $A$, the matrix that diagonalizes
+the Choi matrix $\mcD_N$ of a PCE map.
+
 There exists a subset of PCE channels that generate 
@@
 shall see, with the properties of the aforementioned vector space.
-%\janote{Este párrafo lo voy a retocar. El enunciado de arriba es el primer enunciado
-%del nuevo párrafo. Ojo que hay que introducir la notación $\mcG$.}
 By standard theorems of linear algebra, any proper subspace $W$, see \Eref{eq:19}, 
@@
 this implies that all PCEs can be obtained as
-compositions the PCEs corresponding to maximally non-trivial subspaces, plus
+compositions of PCEs corresponding to maximally non-trivial subspaces, plus
 the identity map. In other words, the set of PCEs that preserve half 
@@
 Consider \Fref{fig:examplesPCE}; subfigures (c), (d) and (e) represent nontrivial 
-generators and the composition of any two of them yield the PCE channel
+PCE generators and the composition of any two of them yield the PCE channel
 corresponding to (b). 
@@
 % and the three different possible compositions result in PCE channel in (b).
-\cpnote{Aca se me hace que hay un cambio brusco de tema. Ver que onda
-con Jose Alfredo}
-The existence of the PCE generators $\mcG$ provide the program of 
-constructing all PCE channels a tool that avoids the usage of a 
-high-computational-cost method. In a moment, we will discuss how to find the 
-generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
-$\mcG$ and matrix $A$ in \Eref{eq:san}\cpnote{Como que para que ahora se
-menciona entonces?}.
+%\cpnote{Aca se me hace que hay un cambio brusco de tema. Ver que onda
+%con Jose Alfredo}
+%The existence of the PCE generators $\mcG$ provide the program of 
+%constructing all PCE channels a tool that avoids the usage of a 
+%high-computational-cost method. In a moment, we will discuss how to find the 
+%generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
+%$\mcG$ and matrix $A$ in \Eref{eq:san}\cpnote{Como que para que ahora se
+%menciona entonces?}.
 %For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
@@
 \cpnote{Arreglar}
-PCE generators may be identified with a unique vector index
-$\vec\alpha$, and thus be denoted as $\pceg$.
+PCE generators may be characterized by its local-action on every qubit 
+in the system, and thus be denoted as $\mcG_{\vec\alpha}$. First, let us denote
+the four 1-qubit PCE generators as $\mcG_{\alpha}$, with $\alpha=0,1,2,3$.
+The first being the trivial generator and the remaining the channels that 
+map the Bloch sphere to each of the Cartesian axes.
+%PCE generator may be identified with a unique vector index
+%$\vec\alpha$, and thus be denoted as $\pceg$.
 % El numero de generadores concide con esa vaina. 
@@
 %the indices in $\vec\alpha$; the number 0 to 3 identifies
-Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
-the identity map and the 3 1-qubit PCE quantum channels that project the 
-Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
-Therefore we will correspond every PCE generator to a collection of numbers 
-that tells what its local-action is on every individual qubit in the system.
-All of this collections of numbers happen to be all vector indices $\{\valpha\}$.
-For example, the PCE generator represented in \Fref{fig:examplesPCE}(c),
-whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
-to the $x$ axis and on the second qubit (first row) to map the corresponding
-local Bloch sphere to itself, may be characterized with the vector index (1,0). 
-Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
-every PCE generator and so denote them as $\pceg$.
+%Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
+%the identity map and the 3 1-qubit PCE quantum channels that project the 
+%Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
+%If one sets all indices in $\vec\alpha$ to zero except for the $k$-th index.
+\janote{A rigorous explanation of why every $\vec\alpha$ is corresponded
+to every generator.}
+Therefore we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
+of the PCE generator on the $k$-th qubit. In consequence, we will denote 
+PCE generators as $\mcG_{\vec\alpha}$. 
+See in \Fref{fig:appex:twoQ_PCEGs} the notation of  two-qubit PCE generators.
+%See, for example, non-trivial generators in subfigures (c), (d) and (e) of
+%\Fref{fig:examplesPCE} are denoted $\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and
+%$\mcG_{(2,2)}$, respectively.
+%whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
+%to the $x$ axis and on the second qubit (first row) to map the corresponding
+%local Bloch sphere to itself, may be characterized with the vector index (1,0). 
+%Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
+%every PCE generator and so denote them as $\pceg$.
 
 \cpnote{Mucha lora y no se prueba nada}
-PCE generators $\pceg$ obey a symmetry
-that defines uniquely every PCE generator. The coefficients  $\{\taus\}$ of every 
+The same symmetry can be identified for both the PCE generators $\pceg$ and
+matrix $A$ the diagonalizes PCE map's Choi matrix $\mcD_N$.
+%PCE generators $\pceg$ obey a symmetry
+%that defines uniquely every PCE generator. 
+For a PCE generator the symmetry is encoded in the array of $\taus$, and 
+for $A$ in its rows and columns.\janote{aquí voy}
+The coefficients  $\{\taus\}$ of every 
 generator $\pceg$ arranged in a hypercubic $N$-dimensional array 

### 2021-12-10 documentos/pce.tex
dandole

@@
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preserving and complete positivity. The trace preserving
-property is needed to
-send convex combinations of density matrices into the convex combination of the
+linearity, trace preserving and complete positivity. Linearity is needed to
+map every convex combination of density matrices into a convex combination of the
 evolution of such density matrices, this is, let $\mcE$ such linear operation,
@@
 hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
-\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases consisting in the so-called \textit{Pauli strings}, defined as 
+\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases containing the so-called \textit{Pauli strings}, defined as 
 \begin{equation}
@@
 \end{equation}
-where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ and $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
+where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
 Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$.
 Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
+In particular, for one qubit systems, the
 %

### 2021-12-12 documentos/pce.tex
dandole

--- 2021-11-25 documentos/pce.tex
@@
 \section{PCE Maps} 
+In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed for.
 \subsection{Quantum channels} % {{{
@@
 $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
-be written as $\mcB(\hilbert)$.
+be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
 %, the subset of density matrices as
@@
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preserving and complete positivity. The trace preserving
-property is needed to
-send convex combinations of density matrices into the convex combination of the
+linearity, trace preserving (TP) and complete positivity (CP). Linearity is needed to
+map every convex combination of density matrices into a convex combination of the
 evolution of such density matrices, this is, let $\mcE$ such linear operation,
-thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The
+thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$ with $0 \leq p\leq 1$. The
 trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
-happen to the state $\rho\in \mcS(\hilbert)$. The complete
+take place to any state $\rho\in \mcS(\hilbert)$. The complete
 positivity condition is needed to preserve positive semidefiniteness and handle
 the non-local feature of quantum theory.
-A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert), \ \ \Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues
-decimos que es una matriz de densidad} \ddnote{$\Delta$ no es hermítico, sin embargo la definición de positividad-semidefinida se extiende a la parte hermítica por convención, revisé y en ningún libro mencionan la hermiticidad en este punto.
-Sin embargo esos casos no son relevantes en este contexto por supuesto}.
+A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ hermitian with $\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues
+decimos que es una matriz de densidad} \ddnote{Aqui hablamos de matrices positivas definidas en general, estuve revisando en varios libros, y parece que lo mas estandar es suponer que si se dice que es positiva (o negativa) definida o semi-definida, automaticamente se dice que es hermítica.
+Sin embargo hay definiciones mas generales que involucran matrices no hermiticas, esas eran las que yo tenía en mente (pero parece que no son tan conocidas).
+Opto por mencionar que $\Delta$ es hermítico.}.
 In the other hand, a map is completely positive if
- $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where 
-between the system and an ancilla with Hilbert space $\hilbert_k$. This ensures that every positive semidefinite operator of any
+ $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where $\id_k$ is the identity channel over $\mcB(\hilbert_k)$. This ensures that every positive semidefinite operator of any
 extension of the system (where the quantum channel is now a local operation) is
-mapped into positive semidefinite operators. The trace preserving is automatically
+mapped to a positive semidefinite operator. The trace preserving is automatically
 fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
@@
 \flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
-E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation. }\ddnote{ejecutado}
+E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation.
+}\ddnote{ejecutado} Concluding, quantum channels are defined to be linear completely positive trace preserving maps (\cptp{}).
 
@@
 \choi is positive-semidefinite.
-
+%
+%
 Furthermore, quantum channels enjoy the well-known \textit{Kraus representation} (or
@@
 \mcE[\rho]=\sum_i K_i \rho
-K_i^\dagger{}
+K_i^\dagger{},
 \end{equation}
@@
 %
+
 It can be seen from Kraus decomposition that quantum channels preserve
-hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
-\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular in this work we use bases consisting in the so-called \textit{Pauli strings}, defined as 
+hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
+\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real.
+In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings}, defined as
 \begin{equation}
@@
 \end{equation}
-where $N$ is the number of two-level particles (\aka{} qubits), $\alpha_i=0,1,2,3$ and $\sigma_0:=\one$, $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
-Thus, the bases $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ are orthonormal in $\mcB(\hilbert)$.
-Also notice that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
+where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
+Thus, given $N$ and the fact that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in $\mcB(\hilbert_{2^N})$.
+The case with $N=1$ corresponds to the well-known \textit{Pauli basis},
 %
-$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$
+$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
 %

### 2021-12-12 documentos/pce.tex
dandole

@@
 \section{PCE Maps} 
-In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed for.
+In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed to discuss them.
 \subsection{Quantum channels} % {{{
@@
 \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real.
-In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings}, defined as
+In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, defined as
 \begin{equation}
@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, in the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$.
+\pce{} maps are defined as those quantum channels that \textit{nullify} Pauli strings.
+In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$.
 The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
@@
 where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
-These channels can be pictured with one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
+These operations can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
 These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.

### 2021-12-13 documentos/pce.tex
dandole

@@
 where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
-These operations can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
-These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$.
-They form a tetrahedron in the space of eigenvalues
-% }}}
-\subsection{Pauli component erasing maps} % {{{
-
-The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
-matrices basis as 
-\begin{equation}\label{eq:N_qubits_rho}
-	\rho =\frac{1}{2^N} 
-            \sum_\valpha r_\valpha \sigma_\valpha,
-%             \quad r_{\vec0}=1,
-% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
-%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
-% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
-	%r_{0,\ldots,0}=1,
-\end{equation}
-where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
-$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
-\sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
-$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
-of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
-\alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
-$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
-Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
-$\tr \sigma_\valpha=2^N\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
-We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
-matrix of a system of qubits.
-
-Consider the linear operations that simply attenuate the Pauli components of 
-a multiqubit system:
-\begin{equation}
-	\paulicomponents \mapsto \taus \paulicomponents.
-% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
-\label{eq:definition:Pauli}
-\end{equation}
-For the operation to preserve the trace of the density matrix, we require that
-$\tau_{\vec 0}=1$.  
-% These operations are diagonal in the basis $\left\{
-% 2^{-N/2}\sigma_{\vec \alpha} \right\}$, which follows from
-% \eref{eq:sigma_property}. 
-% The diagonal components are $\taus$, i.e. $\hat
-% \mcE=\diag(\taus)$. Additionally, they belong to the subset of unital channels
-% that can be written as convex combinations of unitary channels. \cpnote{Alguien 
-% puso aca que lo probarian, pero no lo hemos discutido y quizá no le veo 
-% el caso en este articulo}
-\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
-Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
-si se mencionan a los canales  \cite{Siudzinska2020}}
-
-\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-frases de la importancia de esta familia.} \ddnote{De momento no he encontrado
-alguna reference, para qubits si, pero para los generales no}.
-
-A Pauli component erasing (PCE) operation is a Pauli diagonal operation
-%  A linear operation 
-% $\mcE$ 
-that either preserves or completely erases the Pauli components of a
-density matrix. That is, 
-% it transforms its Pauli components as 
-\begin{equation} \label{eq:PCE_definition}
-% \begin{split}
-% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
-% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
-	\paulicomponents \mapsto \taus \paulicomponents,\quad 
-	\taus = 0,1.
-% \end{split}
-\end{equation}
-It is worth noticing that not all PCE maps are quantum operations. For single 
-qubits, if just one of the $\taus=0$, the complete positivity condition 
-is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
-in this article to determine which $\taus$ lead to a valid quantum map.
-
-%\ddnote{hay un typo en esta ecuacion}
-% A PCE operation is a trace-preserving operation that leaves invariant or erases 
-% the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
-% habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
-% todo claro y no hay problema en dejarlo así por el momento.}
-% \cpnote{Aca voy}
-
-A graphical representation for PCE maps may be introduced, being the
-two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
-Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
-from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
-the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
-empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
-for two qubits, we exemplify them in \fref{fig:two:qubit:examples}. 
-% Notice
-% than in both cases we drop the label $\alpha$ for simplicity, as it will 
-% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
-% aquí}.
-
+These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
 \begin{figure} % {{{
@@
 \end{figure} % }}}
+% }}}
+\subsection{Pauli component erasing maps} % {{{
+
+Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$ qubits can be written using Pauli strings in the following way, 
+\begin{equation}\label{eq:N_qubits_rho}
+	\rho =\frac{1}{2^N} 
+            \sum_\valpha r_\valpha \sigma_\valpha,
+%             \quad r_{\vec0}=1,
+% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
+% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+	%r_{0,\ldots,0}=1,
+\end{equation}
+where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$ such that $r_{\vec \alpha}:=\langle \sigma_{\vec \alpha} \rangle=\tr \left(\rho \sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
+of the density matrix in the basis $\left\{ 2^{-N/2}\sigma_{\vec
+\alpha} \right\}$. The components of $\valpha$ range from $0$ to $3$. 
+Notice that given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that $r_{\vec 0}=1$. 
+{\red We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
+matrix of a system of qubits. } \ddnote{esto se quita, ya lo definí arriba como Pauli strings.}
+
+As mentioned above, \pce{} maps nullify Pauli strings, thus Consider the linear operations that simply attenuate the Pauli components of 
+a multiqubit system:
+\begin{equation}
+	\paulicomponents \mapsto \taus \paulicomponents.
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+\label{eq:definition:Pauli}
+\end{equation}
+For the operation to preserve the trace of the density matrix, we require that
+$\tau_{\vec 0}=1$.  
+% These operations are diagonal in the basis $\left\{
+% 2^{-N/2}\sigma_{\vec \alpha} \right\}$, which follows from
+% \eref{eq:sigma_property}. 
+% The diagonal components are $\taus$, i.e. $\hat
+% \mcE=\diag(\taus)$. Additionally, they belong to the subset of unital channels
+% that can be written as convex combinations of unitary channels. \cpnote{Alguien 
+% puso aca que lo probarian, pero no lo hemos discutido y quizá no le veo 
+% el caso en este articulo}
+
+A Pauli component erasing (PCE) operation is a Pauli diagonal operation
+%  A linear operation 
+% $\mcE$ 
+that either preserves or completely erases the Pauli components of a
+density matrix. That is, 
+% it transforms its Pauli components as 
+\begin{equation} \label{eq:PCE_definition}
+% \begin{split}
+% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+	\paulicomponents \mapsto \taus \paulicomponents,\quad 
+	\taus = 0,1.
+% \end{split}
+\end{equation}
+It is worth noticing that not all PCE maps are quantum operations. For single 
+qubits, if just one of the $\taus=0$, the complete positivity condition 
+is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
+in this article to determine which $\taus$ lead to a valid quantum map.
+
+%\ddnote{hay un typo en esta ecuacion}
+% A PCE operation is a trace-preserving operation that leaves invariant or erases 
+% the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
+% habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
+% todo claro y no hay problema en dejarlo así por el momento.}
+% \cpnote{Aca voy}
+
+A graphical representation for PCE maps may be introduced, being the
+two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
+Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
+from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
+the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
+empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
+for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
+
+\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
+Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
+si se mencionan a los canales  \cite{Siudzinska2020}}\ddnote{Eh estado trabajando en esto, pero el material que he encontrado va mejor en la introduccion, y en todo caso, creo que es muy pronto para mencionar detalles tecnicos sobre los canales que coinciden con los de Ruskai, pues ni siquiera hemos dicho que operaciones de las que definimos aqui, son válidas}
+
+\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
+frases de la importancia de esta familia.} \ddnote{De momento no he encontrado
+alguna reference, para qubits si, pero para los generales no} \ddnote{Como comento arriba, no le veo sentido que eso esté aqui}.
+% Notice
+% than in both cases we drop the label $\alpha$ for simplicity, as it will 
+% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
+% aquí}.
 

### 2021-12-13 documentos/pce.tex
Contradicción

@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those quantum channels that \textit{nullify} Pauli strings.
+\pce{} maps are defined as those quantum channels\R{A1} that \textit{nullify} Pauli strings.
 In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$.
@@
 \end{equation}
-It is worth noticing that not all PCE maps are quantum operations. For single 
+It is worth noticing that not all PCE maps are quantum operations\janote{aquí hay una contradicción
+con lo que se dice en la \lr{A1}}. For single 
 qubits, if just one of the $\taus=0$, the complete positivity condition 

### 2021-12-13 documentos/generators.tex
Algunas frases sobre simetría de PCEGs

@@
 %\end{itemize}}
-
-Un párrafo de intro a las tres ideas 
-\begin{itemize}
-\item Existen los generadores 
-\item Clasificación de los generadores 
-\item Simetrías
-\end{itemize}
+%
+%Un párrafo de intro a las tres ideas 
+%\begin{itemize}
+%\item Existen los generadores 
+%\item Clasificación de los generadores 
+%\item Simetrías
+%\end{itemize}
 
@@
 
-\cpnote{Arreglar}
+%\cpnote{Arreglar}
+\janote{Discutir con Carlos}
 PCE generators may be characterized by its local-action on every qubit 
@@
 
-\cpnote{Mucha lora y no se prueba nada}
-The same symmetry can be identified for both the PCE generators $\pceg$ and
-matrix $A$ the diagonalizes PCE map's Choi matrix $\mcD_N$.
+%\cpnote{Mucha lora y no se prueba nada}
+A symmetry is identified for both PCE generators $\pceg$ and
+the matrix $A$ the diagonalizes a PCE map's Choi matrix $\mcD_N$.
 %PCE generators $\pceg$ obey a symmetry
 %that defines uniquely every PCE generator. 
-For a PCE generator the symmetry is encoded in the array of $\taus$, and 
-for $A$ in its rows and columns.\janote{aquí voy}
-The coefficients  $\{\taus\}$ of every 
-generator $\pceg$ arranged in a hypercubic $N$-dimensional array 
-%of dimensions $\underbrace{4\times 4\times\ldots\times 4}_{N}$ 
-obey a symmetry with respect to the $N$ hyperplanes of dimension $N-1$
-\janote{según wikipedia, por definición, los hiperplanos son de dimensión 
-$N-1$. Así que podría quitarse la aclaración de la dimensión. Lo dejo así y 
-espero retroalimentación} 
-that separate the array into two half arrays \janote{No estoy tan satisfecho con la redacción de este enunciado}.
-See, in \Fref{fig:examplesPCE}, that generators $\mcG_{(1,3)}$, $\mcG_{(3,2)}$
-and $\mcG_{(2,2)}$ represented in (c), (d) and (e), respectively,
-are either symmetric or anti-symmetric with respect to the lines that cut vertically 
-and horizontally in half the diagrams. In fact, this symmetry may be used to
+For a PCE generator the symmetry is encoded in the parameters $\{\taus\}$, and 
+for $A$ in its rows and columns.
+The $N$-dimensional Cartesian grid associated with $\{\tau_{\vec\alpha}\}$
+is either symmetric or anti-symmetric with respect to
+the $N$ hyperplanes of dimension $N-1$ that divide the grid in half.
+For instance, see that the diagrams representing the generators 
+$\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$ in subfigures 
+(c), (d) and (e) of \Fref{fig:two:qubit:examples}, respectively,
+are either symmetric or anti-symmetric with respect to the lines that divide vertically 
+and horizontally the diagrams in half. In fact, this symmetry may be used to
 construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$

### 2021-12-15 documentos/pce.tex
dandole

@@
 % }}}
-\subsection{Single qubit case} % {{{
+\subsection{One qubit \pce{} maps} % {{{
 \label{sec:single:qubit}
@@
 % }}}
-\subsection{Pauli component erasing maps} % {{{
+\subsection{$\mathbf{N}$ qubits Pauli component erasing maps} % {{{
 
@@
 Notice that given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that $r_{\vec 0}=1$.
-{\red We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
-matrix of a system of qubits. } \ddnote{esto se quita, ya lo definí arriba como Pauli strings.}
+Additionally, observe that $\vec r_{\vec \alpha}$ can be understood as a generalization of the Bloch vector for $N$ qubits.
 
-As mentioned above, \pce{} maps nullify Pauli strings, thus Consider the linear operations that simply attenuate the Pauli components of 
-a multiqubit system:
+As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
 \begin{equation}
@@
 \end{equation}
-For the operation to preserve the trace of the density matrix, we require that
-$\tau_{\vec 0}=1$.  
-% These operations are diagonal in the basis $\left\{
-% 2^{-N/2}\sigma_{\vec \alpha} \right\}$, which follows from
-% \eref{eq:sigma_property}. 
-% The diagonal components are $\taus$, i.e. $\hat
-% \mcE=\diag(\taus)$. Additionally, they belong to the subset of unital channels
-% that can be written as convex combinations of unitary channels. \cpnote{Alguien 
-% puso aca que lo probarian, pero no lo hemos discutido y quizá no le veo 
-% el caso en este articulo}
+Similar to the qubit case, not every operation with this form is a \cptp{} map.
+For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$.
+In the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.
 
@@
 \end{equation}
-It is worth noticing that not all PCE maps are quantum operations\janote{aquí hay una contradicción
-con lo que se dice en la \lr{A1}}. For single 
-qubits, if just one of the $\taus=0$, the complete positivity condition 
-is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
-in this article to determine which $\taus$ lead to a valid quantum map.
+ determine which $\taus$ lead to a valid quantum map.
 
@@
 \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-frases de la importancia de esta familia.} \ddnote{De momento no he encontrado
-alguna reference, para qubits si, pero para los generales no} \ddnote{Como comento arriba, no le veo sentido que eso esté aqui}.
+frases de la importancia de esta familia.} \ddnote{hecho}.
 % Notice

### 2021-12-15 documentos/pce.tex
dandole

@@
 	\paulicomponents \mapsto \taus \paulicomponents.
-% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
 \label{eq:definition:Pauli}
 \end{equation}
+with $\tau_{\vec k}$ either $1$ or $0$.
 Similar to the qubit case, not every operation with this form is a \cptp{} map.
 For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$.
-In the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.
+On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.
+Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
+\alpha} \right\}$ basis.
 
-A Pauli component erasing (PCE) operation is a Pauli diagonal operation
-%  A linear operation 
-% $\mcE$ 
-that either preserves or completely erases the Pauli components of a
-density matrix. That is, 
-% it transforms its Pauli components as 
-\begin{equation} \label{eq:PCE_definition}
-% \begin{split}
-% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
-% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
-	\paulicomponents \mapsto \taus \paulicomponents,\quad 
-	\taus = 0,1.
-% \end{split}
-\end{equation}
- determine which $\taus$ lead to a valid quantum map.
+\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
+Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
+si se mencionan a los canales  \cite{Siudzinska2020}}\ddnote{Eh estado trabajando en esto, pero el material que he encontrado va mejor en la introduccion, y en todo caso, creo que es muy pronto para mencionar detalles tecnicos sobre los canales que coinciden con los de Ruskai, pues ni siquiera hemos dicho que operaciones de las que definimos aqui, son válidas}
+
+It is worth noticing that the set of \pce{} maps overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels.
+In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.
+
+\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
+frases de la importancia de esta familia.} \ddnote{hecho, pero de pronto quedo espeso.
+Me estan gustando las cosas que he estado encontrando, voy a investigar en esa direccion por mi cuenta, si sale algo interesante, los invito, como no}
 
@@
 
-A graphical representation for PCE maps may be introduced, being the
-two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
-Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
-from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
-the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
-empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
-for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
+For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}.
+This way of representing \pce{} maps turned out to be very useful for their analysis throughout this work.
 
-\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
-Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
-si se mencionan a los canales  \cite{Siudzinska2020}}\ddnote{Eh estado trabajando en esto, pero el material que he encontrado va mejor en la introduccion, y en todo caso, creo que es muy pronto para mencionar detalles tecnicos sobre los canales que coinciden con los de Ruskai, pues ni siquiera hemos dicho que operaciones de las que definimos aqui, son válidas}
-
-\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-frases de la importancia de esta familia.} \ddnote{hecho}.
 % Notice

### 2021-12-15 documentos/pce.tex
dandole

@@
 \end{equation}
-where $\tau_k$ is either $1$ or $0$.
+where $\tau_\alpha$ is either $1$ or $0$.
 It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel.
@@
 \end{align}
-where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
+where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
 These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
@@
 \end{equation}
-with $\tau_{\vec k}$ either $1$ or $0$.
+with $\tau_{\vec \alpha}$ either $1$ or $0$.
 Similar to the qubit case, not every operation with this form is a \cptp{} map.

### 2021-12-15 documentos/math.tex
first blush
Añadida label a eq de la A
comentario
Added some NullPointerExceptions - Happy easter, you bastards! :D

@@
 % Intro {{{
-This section is devoted to derive the conditions a Pauli map needs to satisfy to
-fulfill the CP condition i.e. that all the eigenvalues of the Choi matrix
+This section is devoted to derive the conditions a Pauli map needs to satisfy 
+the complete positivity condition i.e. that all the eigenvalues of the Choi matrix
 associated to the channel are non-negative.  To do so, we calculate
@@
 the vectorized Pauli operators are 
- $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}}$\janote{aquí hay algo extraño, pues los operadores 
-que utilizamos son la vectorización del producto tensorial de las paulis, no los
-productos tensoriales de las paulis vectorizadas, que es lo que entiendo con la 
-expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}}$}\janote{mi sugerencia es nada más reescribir
-$\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}\otimes\cdots
-\otimes\sigma_{\alpha_N}}$}, and satisfy the orthogonality relation
+\begin{align}
+\kket{\sigma_{\vec{\alpha} }}&=\kket{\sigma_{\alpha_1}}\otimes\cdots
+\otimes\kket{\sigma_{\alpha_N}} \nonumber \\
+&=\kket{\sigma_{\alpha_1}\otimes\cdots
+\otimes\sigma_{\alpha_N}},
+\end{align}
+\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la vectorizacion de la Pauli string, con eso.}
+% 
+% $\janote{aquí hay algo extraño, pues los operadores 
+% que utilizamos son la vectorización del producto tensorial de las paulis, no los
+% productos tensoriales de las paulis vectorizadas, que es lo que entiendo con la 
+% expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
+% \otimes\kket{\sigma_{\alpha_N}}$}\janote{mi sugerencia es nada más reescribir
+% $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}\otimes\cdots
+% \otimes\sigma_{\alpha_N}}$}
+% kkkj
+and satisfy the orthogonality relation
 $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
-\delta_{\vec{\alpha}\vec{\alpha}'}$\janote{cita?}. The matrix representation of the
+\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
 map corresponding to \eref{eq:definition:Pauli} is 
@@
 where 
-\begin{equation}
+\begin{equation}\label{eq:san}
  \san=\sa^{\otimes N}

### 2021-12-15 documentos/pce.tex
Added some NullPointerExceptions - Happy easter, you bastards! :D

--- 2021-12-15 documentos/pce.tex
@@
 \section{PCE Maps} 
-In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed to discuss them.
+To introduce the family of Pauli component erasing maps we start with 
+review basic concepts of quantum channels that will allow us to introduce some 
+notation. 
+% In this section we introduce the definition of Pauli component erasing maps,
+% but first we go through several standard definitions needed to discuss them.
 \subsection{Quantum channels} % {{{
-Quantum channels comprehend the most general linear operations that a quantum
-system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
-their construction and properties, first let us define several objects. We will
-denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
-$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
-be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
+
+Quantum channels are the most general linear operations that a quantum
+system undergo independently of its past~\cite{zimansbook,cirac}.
+The physical system under study will be associated with a Hilbert space
+denoted by \hilbert, and the set of linear operators over such space will 
+be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
+ is an element of $\mcB(\hilbert)$.
+
+% Quantum channels comprehend the most general linear operations that a quantum
+% system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
+% their construction and properties, first let us define several objects. We will
+% denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
+% $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
+% be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
 %, the subset of density matrices as
@@
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preserving (TP) and complete positivity (CP). Linearity is needed to
+linearity, trace preservation and complete positivity. Linearity is needed to
 map every convex combination of density matrices into a convex combination of the
-evolution of such density matrices, this is, let $\mcE$ such linear operation,
-thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$ with $0 \leq p\leq 1$. The
-trace preserving property is required for the process $\mcE$ to be deterministic, \ie{} $\tr\mcE[\rho]=\tr \rho =1$ is the probability that the process $\mcE$ will
-take place to any state $\rho\in \mcS(\hilbert)$. The complete
+evolution of such density matrices. The
+trace preserving property is required for the process $\mcE$ to be
+deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
+The
+complete
 positivity condition is needed to preserve positive semidefiniteness and handle

### 2021-12-15 documentos/pce.tex
GIT :/

@@
 the non-local feature of quantum theory. 
-A map $\mcE$ is positive if $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ hermitian with $\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues
-decimos que es una matriz de densidad} \ddnote{Aqui hablamos de matrices positivas definidas en general, estuve revisando en varios libros, y parece que lo mas estandar es suponer que si se dice que es positiva (o negativa) definida o semi-definida, automaticamente se dice que es hermítica.
-Sin embargo hay definiciones mas generales que involucran matrices no hermiticas, esas eran las que yo tenía en mente (pero parece que no son tan conocidas).
-Opto por mencionar que $\Delta$ es hermítico.}.
-In the other hand, a map is completely positive if
- $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where $\id_k$ is the identity channel over $\mcB(\hilbert_k)$. This ensures that every positive semidefinite operator of any
-extension of the system (where the quantum channel is now a local operation) is
-mapped to a positive semidefinite operator. The trace preserving is automatically
-fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
-where $\mcE$ acts locally, is sent to a valid density matrix, this is the
-substance of complete positivity.
-\flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: 
-E is totally positive if trivially extending E to the tensor product of H with an arbitrary dimensional ancilla space yields a positive operation.
-}\ddnote{ejecutado} Concluding, quantum channels are defined to be linear completely positive trace preserving maps (\cptp{}).
+A linear map $\mcE$ is positive if it maps density operators to density operators, \ie
+if $\mcE[\rho]\geq 0$ for all density matrices $\rho$. 
+% 
+% $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ hermitian with $\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
+% decimos que es una matriz de densidad} \ddnote{Aqui hablamos de matrices
+% positivas definidas en general, estuve revisando en varios libros, y parece que
+% lo mas estandar es suponer que si se dice que es positiva (o negativa) definida
+% o semi-definida, automaticamente se dice que es hermítica. Sin embargo hay
+% definiciones mas generales que involucran matrices no hermiticas, esas eran las
+% que yo tenía en mente (pero parece que no son tan conocidas). Opto por
+% mencionar que $\Delta$ es hermítico.}. 
+%
+On the other hand, if one extends a positive map to include an ancilla, the resulting
+map is not always positive. If, for all dimensions of the ancilla, such extension
+results in a positive map, we say that the original map is completely
+positive~\cite{}.  Quantum channels are required to be completely positive
+so as to allow the proper evolution of potentially entangled states with an 
+ancilla. 
+% In the other hand, a map is completely positive if extending the 
+%  $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where $\id_k$ is the identity channel over $\mcB(\hilbert_k)$. This ensures that every positive semidefinite operator of any
+% extension of the system (where the quantum channel is now a local operation) is
+% mapped to a positive semidefinite operator. The trace preserving is automatically
+% fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
+% where $\mcE$ acts locally, is sent to a valid density matrix, this is the
+% substance of complete positivity.
+% \flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: E
+% is totally positive if trivially extending E to the tensor product of H with an
+% arbitrary dimensional ancilla space yields a positive operation.
+% }\ddnote{ejecutado} 
+Concluding, quantum channels are linear completely positive trace preserving
+maps.
 

### 2021-12-16 documentos/pce.tex
Mapas PCE no son canales cuánticos
Sobre el uso de "PCE maps"

@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those quantum channels\R{A1} that \textit{nullify} Pauli strings.
+\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamentecanales cuánticos. Por esto, 
+estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
+Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los 
+mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings. 
+\janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
+\janote{
+\pce{} maps are defined as positive trace-preserving (PTP) maps that 
+\textit{nullify} Pauli strings.}
 In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$.
@@
 
-As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
+As mentioned above, \pce{} maps\R{A1} nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
 \begin{equation}
@@
 
-It is worth noticing that the set of \pce{} maps overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels.
+It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels.
 In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.
@@
 For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}.
-This way of representing \pce{} maps turned out to be very useful for their analysis throughout this work.
+This way of representing \pce{} maps\R{A3} turned out to be very useful for their analysis throughout this work.
 

### 2021-12-16 documentos/pce.tex
Typo
Otro comentario sobre "PCE maps"

@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamentecanales cuánticos. Por esto, 
+\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamente canales cuánticos. Por esto, 
 estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
@@
 \end{align}
-where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
+where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce:
+\janote{Derivado de mi comentario sobre el uso de ``PCE maps''
+también propongo que en vez de ``show that only five operations are \pce{}''
+se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
+channels''} 
+the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
 These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.

### 2021-12-16 documentos/generators.tex
Párrafo de caracterización de PCEgs. Falta prueba para N qubits

@@
 In this section we will discuss the existence of a generator set for all PCE
-quantum channels, how to label each element of this set according to its local-action to 
-every qubit in the system, and, finally, we  	will discuss a symmetry of
+quantum channels, how to label each of them uniquely according to its local-action 
+on every qubit in the system, and, finally, we  	will discuss a symmetry of
 both PCE quantum channel generators and $A$, the matrix that diagonalizes
@@
 %\cpnote{Arreglar}
-\janote{Discutir con Carlos}
 PCE generators may be characterized by its local-action on every qubit 
-in the system, and thus be denoted as $\mcG_{\vec\alpha}$. First, let us denote
-the four 1-qubit PCE generators as $\mcG_{\alpha}$, with $\alpha=0,1,2,3$.
-The first being the trivial generator and the remaining the channels that 
-map the Bloch sphere to each of the Cartesian axes.
-%PCE generator may be identified with a unique vector index
-%$\vec\alpha$, and thus be denoted as $\pceg$.
-% El numero de generadores concide con esa vaina. 
-%Let us introduce a convention for the following discussion for 
-%the indices in $\vec\alpha$; the number 0 to 3 identifies
-%Recall that indices $0,1,2,3$ in $\vec\alpha$ correspond to, respectively,
-%the identity map and the 3 1-qubit PCE quantum channels that project the 
-%Bloch sphere to the rectangular axes $x$, $y$ and $z$. 
-%If one sets all indices in $\vec\alpha$ to zero except for the $k$-th index.
-\janote{A rigorous explanation of why every $\vec\alpha$ is corresponded
-to every generator.}
+in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
+with $\vec\alpha$ each of the $4^{n}$ different vector indices. For 1-qubit
+the PCE generators are the identity map plus the channels that map the Bloch 
+sphere to each Cartesian axis, as their associated vector subspaces are trivial
+to prove and their dimension 1 is met. 
+\janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
+\pce{} generators}
 Therefore we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
@@
 PCE generators as $\mcG_{\vec\alpha}$. 
-See in \Fref{fig:appex:twoQ_PCEGs} the notation of  two-qubit PCE generators.
-%See, for example, non-trivial generators in subfigures (c), (d) and (e) of
-%\Fref{fig:examplesPCE} are denoted $\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and
-%$\mcG_{(2,2)}$, respectively.
-%whose local-action on the first qubit (first column) is to project the corresponding local Bloch sphere 
-%to the $x$ axis and on the second qubit (first row) to map the corresponding
-%local Bloch sphere to itself, may be characterized with the vector index (1,0). 
-%Then, it is clear that in general one can associate a unique $\vec\alpha$ to 
-%every PCE generator and so denote them as $\pceg$.
+See, for example, that the 2-qubits PCE generator represented in subfigure (c)
+in \Fref{fig:two:qubit:examples} acts on the first qubit (first column) as mapping its
+Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
+hence it is labeled $\mcG_{(1,0)}$.
+See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.
 
@@
 eight.
+
+\begin{align}
+\tau_{(\vec\alpha)}
+\end{align}
 

### 2021-12-16 documentos/generators.tex
Redacción y referencia a fig, párrafo caracterización PCEGs

@@
 \pce{} generators}
-Therefore we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
+Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
 of the PCE generator on the $k$-th qubit. In consequence, we will denote 
@@
 See, for example, that the 2-qubits PCE generator represented in subfigure (c)
-in \Fref{fig:two:qubit:examples} acts on the first qubit (first column) as mapping its
+of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
 Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,

### 2021-12-16 documentos/generators.tex
A medias con el párrafo sobre simetrías PCEGs

@@
 In this section we will discuss the existence of a generator set for all PCE
-quantum channels, how to label each of them uniquely according to its local-action 
+quantum channels, how to label each of them uniquely according to its local action 
 on every qubit in the system, and, finally, we  	will discuss a symmetry of
@@
 %\cpnote{Arreglar}
-PCE generators may be characterized by its local-action on every qubit 
+PCE generators may be characterized by its local action on every qubit 
 in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
@@
 \pce{} generators}
-Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
-of the PCE generator on the $k$-th qubit. In consequence, we will denote 
-PCE generators as $\mcG_{\vec\alpha}$. 
+Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ by the local action
+of the PCE generator on the $k$-th qubit. 
 See, for example, that the 2-qubits PCE generator represented in subfigure (c)
@@
 %\cpnote{Mucha lora y no se prueba nada}
-A symmetry is identified for both PCE generators $\pceg$ and
-the matrix $A$ the diagonalizes a PCE map's Choi matrix $\mcD_N$.
+A reflection symmetry is identified for both PCE generators $\pceg$ and
+the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
 %PCE generators $\pceg$ obey a symmetry
 %that defines uniquely every PCE generator. 
-For a PCE generator the symmetry is encoded in the parameters $\{\taus\}$, and 
-for $A$ in its rows and columns.
-The $N$-dimensional Cartesian grid associated with $\{\tau_{\vec\alpha}\}$
-is either symmetric or anti-symmetric with respect to
+The symmetry for a PCE generator $\pceg$ is encoded in the 
+parameters $\{\taus\}$, the $N$-dimensional Cartesian grid associated with it 
+(the set) is either symmetric or anti-symmetric under reflection of the 
+indices in the $k$-th position in $\vec\alpha$ as
+\begin{align}
+\alpha_{0}\mapsto\alpha_3,\quad\alpha_{3}\mapsto\alpha_0,
+\quad\alpha_1\mapsto\alpha_2, \quad\alpha_2\mapsto\alpha_1.
+\end{align}
 the $N$ hyperplanes of dimension $N-1$ that divide the grid in half.

### 2021-12-16 documentos/kraus.tex
quitando typos?
lots of changes after a lot of time
muevo ecuaciones de dilatacion y semigrupo
etc
Pig

@@
 \section{Kraus operators and decoherence} % {{{
+\cpnote{HAcer esta seccion despues de que david ponga lo de decoherencia, 
+para servirla bien}
 % \todo{Carlos hace una version}
+
+Furthermore, quantum channels enjoy the well-known \textit{Kraus
+representation} (or operator-sum representation) which reads 
+\begin{equation}
+\mcE[\rho]=\sum_i K_i \rho
+K_i^\dagger{},
+\end{equation}
+with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
 
@@
 =\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
-\label{}
+\label{eq:sigma_property}
 \end{equation}
@@
 Next, consider the action of a channel with Kraus representation 
-\eqref{eq:kraus:PCE} on an $N$ qubit system:
+\eqref{eq:kraus:PCE} on an $N$ qubit system:\janote{acá abajo tenías un $\&$ dentro 
+del entorno \texttt{equation} y no compilaba}\janote{había otro en algún lado que quité 
+también.}
 \begin{equation}
 % \begin{align}
-\rho & \to 
+\rho 
+%& 
+\to 
  \frac{\rho}{2} 
@@
 \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha}  
-&= 
+= 
   \sum_{\vec \beta} 
@@
 \begin{itemize}
-\item Construct the Kraus operators, and relate to decoherence, for PCEG
+\item Relate to decoherence, for PCEG
 \item Play with non PCEG PCEs
@@
 \end{itemize}
+
+\begin{equation}
+\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
+\label{eq:Nqubit_semigroup}
+\end{equation}
+
+\begin{align}
+U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
+U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
+\label{eq:Nqubit_stinespring}
+\end{align}
 % }}}

### 2021-12-16 documentos/pce.tex
Pig

--- 2021-12-15 documentos/pce.tex
@@
 \subsection{Quantum channels} % {{{
+\cpnote{Cambios importantes, qeu David revise}
 
@@
 deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
+Often, this condition is easy to test.
 The
@@
 % }\ddnote{ejecutado} 
-Concluding, quantum channels are linear completely positive trace preserving
-maps.
+% Concluding, quantum channels are linear completely positive trace preserving
+% maps.
 
-Quantum channels can be characterized by means of the Choi-\jami{}
-isomorphism~\cite{choi,jamil}. This is, given a linear operation
-$\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
-$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called dynamical matrix), where
-$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
-Bell state between two copies of \hilbert. The map \mcE is completely positive if and only
-\choi is positive-semidefinite.
+A simple algorithm to test the complete positivity of a quantum channel 
+was developed by 
+\jami{}~\cite{jamil} and Choi~\cite{choi}.
+One first exploits an isomorphism that maps a channel $\mcE$ to the state
+$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
+$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is a 
+maximally entangled state between the original system and an ancilla.
+Remarkably, the map \mcE is completely positive
+if and only \choi (also called dynamical matrix) is positive-semidefinite.
+
+%  the
+% Bell state between two copies of \hilbert.
+
+% Quantum channels can be characterized by means of the Choi-\jami{}
+% isomorphism~\cite{choi,jamil}. This is, given a linear operation
+% $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
+% $\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called
+% dynamical matrix), where
+% $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
+% Bell state between two copies of \hilbert. The map \mcE is completely positive
+% if and only \choi is positive-semidefinite.
 %
 %
-Furthermore, quantum channels enjoy the well-known \textit{Kraus representation} (or
-operator-sum representation) which reads 
-\begin{equation}
-\mcE[\rho]=\sum_i K_i \rho
-K_i^\dagger{},
-\end{equation}
-with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition). In fact, a linear operation is completely positive if and only
-if it has a Kraus representation~\cite{Kraus1983}. The minimum number of Kraus operators $K_i$ needed to represent the channel is called \textit{Kraus rank}. 
+
+% In fact,
+% a linear operation is completely positive if and only if it has a Kraus
+% representation~\cite{Kraus1983}.
+% The minimum number of Kraus operators $K_i$
+% needed to represent the channel is called \textit{Kraus rank}. 
 %
@@
 It can be seen from Kraus decomposition that quantum channels preserve
-hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
-\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real.
-In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, defined as
+hermiticity, this has a practical consequence when using hermitian bases, \ie{}
+let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then
+the entries of the matrix representation of the quantum channel $\mcE$, $\hat
+\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular,
+in this work we are interested in systems of $N$ qubits, and we use hermitian
+bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui
+introduzco el nombre estandar}, defined as 
 \begin{equation}
@@
 \end{equation}
-where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and $\sigma_{1,2,3}:=\sigma_{x,y,z}$.
-Thus, given $N$ and the fact that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in $\mcB(\hilbert_{2^N})$.
-The case with $N=1$ corresponds to the well-known \textit{Pauli basis},
+where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and
+$\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr
+\sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
+basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
+$\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
+\textit{Pauli basis},
 %
@@
 
-\flnote{
-probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
-$\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
-Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
-}\ddnote{ejecutado, hacia falta edicion, sin embargo lo de hermiticity preserving es para hacer incapie en por que podemos trabajar en una representacion totalmente real de los canales.}
-
-  \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
+% \flnote{
+% probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
+% $\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
+% Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
+% }\ddnote{ejecutado, hacia falta edicion, sin embargo lo de hermiticity preserving es para hacer incapie en por que podemos trabajar en una representacion totalmente real de los canales.}
+% 
+%   \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
 
 % }}}
-\subsection{One qubit \pce{} maps} % {{{
+\subsection{Pauli component erasing maps} % {{{
 \label{sec:single:qubit}
@@
 % }}}
-\subsection{$\mathbf{N}$ qubits Pauli component erasing maps} % {{{
+% \subsection{$\mathbf{N}$ qubits Pauli component erasing maps} % {{{
 
@@
 with $\tau_{\vec \alpha}$ either $1$ or $0$.
-Similar to the qubit case, not every operation with this form is a \cptp{} map.
-For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$.
-On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper.
-Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
+\cpnote{Revisar aca lo que sigue}
+Similar to the qubit case, not every operation with this form is a completely
+positive trace perserving map. For the operation to be trace preserving, it is
+easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and
+evaluating the conditions for complete positivity is involved and is the main
+problem addressed in this paper. Moreover, these operations are by definition
+diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
 \alpha} \right\}$ basis.

### 2021-12-16 documentos/pce.tex

@@
 \todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those quantum channels\R{A1} that \textit{nullify} Pauli strings.
+\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamente canales cuánticos. Por esto, 
+estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
+Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los 
+mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings. 
+\janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
+\janote{
+\pce{} maps are defined as positive trace-preserving (PTP) maps that 
+\textit{nullify} Pauli strings.}
 In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$.

### 2021-12-16 documentos/pce.tex
Cita del GofQS para completa positividad

@@
 results in a positive map, we say that the original map is completely
-positive~\cite{}.  Quantum channels are required to be completely positive
+positive~\cite{bengtsson_zyczkowski_2017}\janote{El comando de cita aparecía vacío. 
+Yo agregué la del GofQS}.  Quantum channels are required to be completely positive
 so as to allow the proper evolution of potentially entangled states with an 

### 2021-12-16 documentos/pce.tex
Comentario sobre dynamical or Choi matrix

@@
 Remarkably, the map \mcE is completely positive
-if and only \choi (also called dynamical matrix) is positive-semidefinite.
+if and only \choi (also called \janote{Choi or} dynamical matrix \janote{of $\mcE$}) 
+\janote{en el resto del manuscrito siempre usamos Choi matrix}
+is positive-semidefinite.
 

### 2021-12-16 documentos/pce.tex
I was told to leave it alone, but I have this thing called OCD, you see

--- 2021-12-16 documentos/pce.tex
@@
 Remarkably, the map \mcE is completely positive
-if and only \choi (also called dynamical matrix) is positive-semidefinite.
+if and only \choi (also called dynamical matrix) is
+positive-semidefinite~\cite{jamil,choi}.
 
@@
 
-It can be seen from Kraus decomposition that quantum channels preserve
-hermiticity, this has a practical consequence when using hermitian bases, \ie{}
-let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then
-the entries of the matrix representation of the quantum channel $\mcE$, $\hat
-\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular,
-in this work we are interested in systems of $N$ qubits, and we use hermitian
-bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui
-introduzco el nombre estandar}, defined as 
-\begin{equation}
-\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
-\label{eq:pauli_strings}
-\end{equation}
-where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and
-$\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr
-\sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
-basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
-$\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
-\textit{Pauli basis},
-%
-$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
+% It can be seen from Kraus decomposition that quantum channels preserve
+% hermiticity, this has a practical consequence when using hermitian bases, \ie{}
+% let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then
+% the entries of the matrix representation of the quantum channel $\mcE$, $\hat
+% \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular,
+% in this work we are interested in systems of $N$ qubits, and we use hermitian
+% bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui
+% introduzco el nombre estandar}, defined as 
+% \begin{equation}
+% \sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
+% \label{eq:pauli_strings}
+% \end{equation}
+% where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and
+% $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr
+% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
+% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
+% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
+% \textit{Pauli basis},
+% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
+
 %
@@
 \label{sec:single:qubit}
-\todo{David escribe una primera version y luego Carlos itera}
-\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamente canales cuánticos. Por esto, 
-estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
-Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los 
-mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings. 
-\janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
-\janote{
-\pce{} maps are defined as positive trace-preserving (PTP) maps that 
-\textit{nullify} Pauli strings.}
-In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$.
-The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
+% \todo{David escribe una primera version y luego Carlos itera}
+
+We shall start exploring a single qubit scenario, where the most general 
+density matrix can be written as
 \begin{equation}
-\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
+% \rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
+\rho=\frac12 {\sum_{\alpha=0}^3 r_\alpha \sigma_\alpha},
 \end{equation}
-Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
+with $\sigma_0= \one$, and $\sigma_{1,2,3}$ the usual Pauli matrices. 
+Normalization requires that $r_0=1$ and the remaining $r_{1,2,3}$ 
+form the Bloch vector. Consider the map that projects
+each component 
+in the following way,
 \begin{equation}
@@
 \end{equation}
-where $\tau_\alpha$ is either $1$ or $0$.
+where $\tau_\alpha$ is either $1$ or $0$. Not every
+operation like this is a quantum map; for example collapsing the entire Bloch
+ball to the $xy$ plane (setting $\tau_3=0$ and the rest to 1) is not a quantum
+channel. A direct evaluation of the complete positivity
+conditions~\cite{zimansbook,davalosdivisibility}, 
+\begin{align}
+1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
+1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall \alpha\neq \beta \neq \gamma,
+\end{align}
+where trace-preserving is already imposed ($\tau_0=1$), show that five out of
+the eight 1-qubit PCE maps are quantum channels.
+% 
+% show that only five
+% operations are \pce:
+% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
+% también propongo que en vez de ``show that only five operations are \pce{}''
+% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
+% channels''} 
+These operations are the identity map, the completely depolarizing channel
+($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip
+channels~\cite{chuangbook}, 
+% These operations are by definition diagonal in the
+% Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat
+% \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$
+and can be pictured using one column tables showing the positions of $0$s and
+$1$s, see~\fref{fig:one:qubit:examples}.
+
+% \pce{} maps are defined as those quantum channels\janote{David, los mapas PCE
+% no son necesariamente canales cuánticos. Por esto, estás siendo incosistente en
+% el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF.
+% Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los
+% mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings.
+% \janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
+% \janote{
+% \pce{} maps are defined as positive trace-preserving (PTP) maps that 
+% \textit{nullify} Pauli strings.}
+% In the case of one qubit, they consist of maps nullifying the averages
+% $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$
+% with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known
+% \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
+% \begin{equation}
+% \rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
+% \end{equation}
+% Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
+% \begin{equation}
+% r_\alpha \mapsto \tau_\alpha r_\alpha
+% \end{equation}
+% where $\tau_\alpha$ is either $1$ or $0$.
 It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel.
 A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
-\begin{align}
-1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
-1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
-\end{align}
-where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce:
-\janote{Derivado de mi comentario sobre el uso de ``PCE maps''
-también propongo que en vez de ``show that only five operations are \pce{}''
-se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
-channels''} 
-the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
+% \begin{align}
+% 1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
+% 1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
+% \end{align}
+% where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce:
+% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
+% también propongo que en vez de ``show that only five operations are \pce{}''
+% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
+% channels''} 
+% the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
 These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
@@
 
-Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$ qubits can be written using Pauli strings in the following way, 
+In order to present and work the $N$ qubit case, it is useful 
+to introduce 
+the so-called \textit{Pauli strings}, defined as 
+\begin{equation}
+\sigma_{\vec \alpha}=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
+\label{eq:pauli_strings}
+\end{equation}
+where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$
+and $\alpha_i=0,1,2,3$. These hermitian operators form an orthogonal 
+basis in the space of operators acting on $N$ qubits. In fact, 
+$\tr \sigma_{\vec \alpha} \sigma_{\vec \alpha'}=2^N\delta_{\alpha \alpha'}$
+and 
+$\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
+% 
+% Thus, given $N$ and the fact that $\tr
+% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
+% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
+% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
+% \textit{Pauli basis},
+% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
+
+Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$
+qubits can be written using Pauli strings in the following way, 
 \begin{equation}\label{eq:N_qubits_rho}
@@
 \end{equation}
-where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$ such that $r_{\vec \alpha}:=\langle \sigma_{\vec \alpha} \rangle=\tr \left(\rho \sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
-of the density matrix in the basis $\left\{ 2^{-N/2}\sigma_{\vec
-\alpha} \right\}$. The components of $\valpha$ range from $0$ to $3$. 
-Notice that given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that $r_{\vec 0}=1$.
-Additionally, observe that $\vec r_{\vec \alpha}$ can be understood as a generalization of the Bloch vector for $N$ qubits.
+so $r_{\vec \alpha}=\langle \sigma_{\vec \alpha} \rangle=\tr \left(\rho
+\sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
+of the density matrix in the normalized basis of Pauli strings. Again,
+normalization of the state requires that $r_{\vec 0}=1$.
+We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
+matrix of a system of qubits.
+
+% The components of $\valpha$ range from $0$ to $3$.  Notice that
+% given that $\tr \rho=1$ and $\sigma_{\vec 0} = \openone$, it is clear that
+% $r_{\vec 0}=1$. Additionally, observe that $\vec r_{\vec \alpha}$ can be
+% understood as a generalization of the Bloch vector for $N$ qubits.
+%
+
+% The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
+% matrices basis as 
+% \begin{equation}\label{eq:N_qubits_rho}
+% 	\rho =\frac{1}{2^N} 
+%             \sum_\valpha r_\valpha \sigma_\valpha,
+% %             \quad r_{\vec0}=1,
+% % 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+% %             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
+% % 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
+% 	%r_{0,\ldots,0}=1,
+% \end{equation}
+% where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$,
+% $\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
+% \sigma_{\alpha_N}$ is the tensor product of Pauli matrices, and 
+% $r_{\vec \alpha}$ is the coefficient corresponding to the expansion
+% of the density matrix in the complete orthonormal basis $\left\{ 2^{-N/2}\sigma_{\vec
+% \alpha} \right\}$. In the sum each of the $N$ components of $\valpha$, i.e.
+% $\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
+% Notice that $\sigma_{\vec 0} = \openone$, and since both $\tr \rho=1$ and 
+% $\tr \sigma_\valpha=2^N\delta_{\valpha,\vec 0}$, then $r_{\vec 0}=1$. 
+% We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
+% matrix of a system of qubits.
+
+A Pauli component erasing (PCE) operation is a Pauli diagonal operation
+that either preserves or completely erases the Pauli components of a
+density matrix. That is, 
+% it transforms its Pauli components as 
+\begin{equation} \label{eq:PCE_definition}
+% \begin{split}
+% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
+% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
+	\paulicomponents \mapsto \taus \paulicomponents,\quad 
+	\taus = 0,1.
+% \end{split}
+\end{equation}
+It is worth noticing that not all PCE maps are quantum operations. For single 
+qubits, if just one of the $\taus=0$, the complete positivity condition 
+is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
+in this article to determine which $\taus$ lead to a valid quantum map.
 
@@
 
-For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}.
-This way of representing \pce{} maps\R{A3} turned out to be very useful for their analysis throughout this work.
+For the two qubits case, the operations illustrated
+in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing
+the positions of the $0$s and $1$s of the diagonal using the Pauli string
+basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{}
+maps\R{A3} turned out to be very useful for their analysis throughout this
+work.
+
+A graphical representation for PCE maps may be introduced, being the
+two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
+Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
+from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
+the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
+empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
+for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
 

### 2021-12-16 documentos/generators.tex
Otra iteración de sección Generators lista

@@
 
-In this section we will discuss the existence of a generator set for all PCE
-quantum channels, how to label each of them uniquely according to its local action 
+We now discuss the existence of a generator set for all PCE quantum channels, 
+how to label each of them uniquely as $\pceg$ according to its local action 
 on every qubit in the system, and, finally, we will discuss a symmetry of
@@
 corresponding to (b).
-% 
-% 
-% the composition of any two 2-qubits PCE
-% generators 
-% in (c), (d), or (e) is equivalent to taking the intersection between them both
-% and the three different possible compositions result in PCE channel in (b).
-%\cpnote{Aca se me hace que hay un cambio brusco de tema. Ver que onda
-%con Jose Alfredo}
-%The existence of the PCE generators $\mcG$ provide the program of 
-%constructing all PCE channels a tool that avoids the usage of a 
-%high-computational-cost method. In a moment, we will discuss how to find the 
-%generators $\mcG$ from matrix $A$, given a symmetry that is obeyed both by the generators 
-%$\mcG$ and matrix $A$ in \Eref{eq:san}\cpnote{Como que para que ahora se
-%menciona entonces?}.
-%For the case of 1 qubit, the existence of PCE generators $\pceg$ is  
-%verified by Siudzińska~\cite{siudzinska2019geometry}.
-%\janote{Esto puede
-%ser un párrafo, o puede ser un comentario final dentro del párrafo antrerior.}
 
@@
 sphere to each Cartesian axis, as their associated vector subspaces are trivial
-to prove and their dimension 1 is met. 
+to prove and their dimension $2(1)-1=1$ is met. 
 \janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
@@
 The symmetry for a PCE generator $\pceg$ is encoded in the 
-parameters $\{\taus\}$, the $N$-dimensional Cartesian grid associated with it 
-(the set) is either symmetric or anti-symmetric under reflection of the 
+$N$-dimensional array of all $\taus$, the Cartesian grid associated with it 
+is either symmetric or anti-symmetric under reflection of the 
 indices in the $k$-th position in $\vec\alpha$ as
@@
 \end{align}
-the $N$ hyperplanes of dimension $N-1$ that divide the grid in half.
-For instance, see that the diagrams representing the generators 
-$\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$ in subfigures 
-(c), (d) and (e) of \Fref{fig:two:qubit:examples}, respectively,
-are either symmetric or anti-symmetric with respect to the lines that divide vertically 
-and horizontally the diagrams in half. In fact, this symmetry may be used to
-construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$
-and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
-whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
-respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
-\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
-$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
-for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
-the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
-anti-symmetric to the previous subset. For example, let us illustrate the 
-procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
-One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
-$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
-$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
-to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
-the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
-eight.
-
-\begin{align}
-\tau_{(\vec\alpha)}
-\end{align}
+\janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
+For instance, see that the 2-qubit PCE generators 
+$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
+represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
+respectively, are either symmetric or anti-symmetric under reflection with 
+respect to lines that divide the diagram in half vertically and horizontally. 
+The same symmetry is identified for the rows and columns of $A$ if one 
+labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$,
+where $\vec\alpha$ is the same vector index used throughout in this manuscript.
+\janote{Aquí habría que agregar la prueva de simetría para la $A$.}
 
@@
 \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
-\caption{\janote{Propuesta de figura para mostrar que generadores 
-y la a obedecen las mismas simetrías.}}
+\caption{
+\janote{Propuesta de figura para mostrar que generadores 
+y la a obedecen las mismas simetrías.}
+}
+\label{fig:A_and_PCEGs_connection}
 \end{figure} % }}}
 
-\cpnote{Mucha lora y no se prueba nada, again}
-The matrix $\san$ (and thus $a$) [see \eref{eq:san}] encodes all the information
-of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
-The rows and columns of matrix $A$ also obey the symmetry previously discussed 
-for PCE generators $\pceg$. It suffices to check that rows and columns of matrix $a$
-in \Eref{eq:1} obey the aforementioned symmetry when they are arranged in a hypercubic 
-$N$-dimensional array of order $4$.
-As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
-rows and columns of $A$. \janote{falta prueba}
-Therefore, this establishes a deep connection between the matrix $A$ and 
-PCE quantum channels. It allows one to infer the PCE generators $\pceg$
-by taking its corresponding coefficients $\{\taus\}$ as the rows or columns of $A$ 
-after taking $-1\mapsto0$. In \appref{sec:2_qubits} we illustrate this program 
-for 2-qubits PCE channels.
-In short, it is sufficient to have the matrix $A$ to construct 
-all PCE quantum channels.
-%\janote{Aquí
-%tendrá que ir una prueba que aún se está cocinando}
+%\cpnote{Mucha lora y no se prueba nada, again}
+Given that both matrix $\san$ and PCE generators $\pceg$ have the same 
+symmetries, it is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
+encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
+From the tensor power of matrix $a$ one can infer the $\{\taus\}$ of a PCE
+generator $\pceg$ by taking any row or column $A^{(i)}$ and mapping 
+all entries with $-1$ to $0$. In \Fref{fig:A_and_PCEGs_connection} we illustrate
+this connection between $a$ and 1-qubit PCE generators.
+In \appref{sec:2_qubits} we illustrate this program for 2-qubits PCE channels.
 

### 2021-12-16 documentos/kraus.tex
dandole

@@
 Next, consider the action of a channel with Kraus representation 
-\eqref{eq:kraus:PCE} on an $N$ qubit system:\janote{acá abajo tenías un $\&$ dentro 
-del entorno \texttt{equation} y no compilaba}\janote{había otro en algún lado que quité 
-también.}
-\begin{equation}
-% \begin{align}
-\rho 
-%& 
-\to 
- \frac{\rho}{2} 
- + \sum_{\vec \beta} \frac{\tau_{\vec \beta}}{2}
-\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha}  
-= 
-  \sum_{\vec \beta} 
-   \tau_{\vec \beta}\frac{1+\san_{\vec \alpha \vec \beta}}{2}\sigma_{\vec \beta}. 
-% 
-% 
-% \frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \rho
-% \frac{\otimes_k \sigma_{i_k}}{\sqrt{2}} \\
-% &=\frac12 \left(\rho + \bigotimes_k \sigma_{i_k} \rho \bigotimes_k \sigma_{i_k} \right)\\
-% &=\frac12 \rho
-% + \frac12\sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \bigotimes_k  \sigma_{i_k} \sigma_{j_k}  \sigma_{i_k} \\
-% &=
-% \sum_{j_1, \ldots,j_n} r_{j_1 \ldots j_n} \frac{1+\prod_k a^{i_k}_{j_k}}{2} \bigotimes_k  \sigma_{j_k} . 
-\end{equation}
+\eqref{eq:kraus:PCE} on an $N$ qubit system:
+\begin{align}
+\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
+=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}
+\end{align}
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
@@
 Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
-lead to different channels. This can be seen noticing that if two channels were
+leads to different channels. This can be seen noticing that if two channels were
 the same, this would imply that the matrix representation of the corresponding
-superoperator of $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$
+superoperator of $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$ \ddnote{en este punto me confundio bastante esta notacion, contrapropongo $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$, que es una notación que hemos venido usando.}
 would have to be the same which is clearly false. Since there are $4^n$ different 

### 2021-12-16 documentos/generators.tex
Caption fig de conexion a y PCEGs de 1 qubit

@@
 in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
-with $\vec\alpha$ each of the $4^{n}$ different vector indices. For 1-qubit
+with $\vec\alpha$ each of the $4^{N}$ different vector indices. For 1-qubit
 the PCE generators are the identity map plus the channels that map the Bloch 
@@
 \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
-\caption{
+\caption{Connection between rows and columns of $a$ and 1-qubit PCE generators.
+The rows or columns of $a$ and the diagrams of the generators are either 
+symmetric or anti-symmetric under reflection.
 \janote{Propuesta de figura para mostrar que generadores 

### 2021-12-16 documentos/pce.tex
really ignore ignored worsd

@@
 results in a positive map, we say that the original map is completely
-positive~\cite{}.  Quantum channels are required to be completely positive
+positive~\cite{bengtsson_zyczkowski_2017}.
+Quantum channels are required to be completely positive
 so as to allow the proper evolution of potentially entangled states with an 
@@
 Remarkably, the map \mcE is completely positive
-if and only \choi (also called dynamical matrix) is
-positive-semidefinite~\cite{jamil,choi}.
+if and only \choi (also called Choi or dynamical matrix of $\mcE$) 
+is positive-semidefinite~\cite{jamil,choi}.
 
@@
 basis in the space of operators acting on $N$ qubits. In fact, 
-$\tr \sigma_{\vec \alpha} \sigma_{\vec \alpha'}=2^N\delta_{\alpha \alpha'}$
+$\tr \sigma_{\vec \alpha} \sigma_{\vec \alpha'}=2^N\delta_{\valpha \valpha'}$
 and 
-$\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$.
+$\tr \sigma_{\vec \alpha}= 2^{N}\delta_{\vec\alpha \vec 0}$.
 % 
@@
 
-A Pauli component erasing (PCE) operation is a Pauli diagonal operation
+A Pauli component erasing (PCE) map is a map
+%  Pauli diagonal operation
 that either preserves or completely erases the Pauli components of a
@@
 \end{equation}
-It is worth noticing that not all PCE maps are quantum operations. For single 
-qubits, if just one of the $\taus=0$, the complete positivity condition 
-is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
-in this article to determine which $\taus$ lead to a valid quantum map.
+For the operation to be trace preserving, it is required that $\tau_{\vec
+0}=1$. 
+It is worth noticing that, as for the single qubit case, not all PCE maps are
+quantum operations. 
+On the other hand, constructing and
+evaluating the conditions for complete positivity is involved and is the main
+problem addressed in this paper. 
+If we refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
+with arbitrary values of 
+% but allow the 
+$\taus$ (only restricted by complete positivity) as Pauli diagonal operations.
 
-As mentioned above, \pce{} maps\R{A1} nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
-\begin{equation}
-	\paulicomponents \mapsto \taus \paulicomponents.
-% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
-\label{eq:definition:Pauli}
-\end{equation}
-with $\tau_{\vec \alpha}$ either $1$ or $0$.
-\cpnote{Revisar aca lo que sigue}
-Similar to the qubit case, not every operation with this form is a completely
-positive trace perserving map. For the operation to be trace preserving, it is
-easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and
-evaluating the conditions for complete positivity is involved and is the main
-problem addressed in this paper. Moreover, these operations are by definition
-diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
-\alpha} \right\}$ basis.
+% For single 
+% qubits, if just one of the $\taus=0$, the complete positivity condition 
+% is not met, as discussed in \sref{sec:single:qubit}. 
+% It will be of central interest
+% in this article to determine which $\taus$ lead to a valid quantum map.
 
-\cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai. 
-Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien discutir
-si se mencionan a los canales  \cite{Siudzinska2020}}\ddnote{Eh estado trabajando en esto, pero el material que he encontrado va mejor en la introduccion, y en todo caso, creo que es muy pronto para mencionar detalles tecnicos sobre los canales que coinciden con los de Ruskai, pues ni siquiera hemos dicho que operaciones de las que definimos aqui, son válidas}
+% On the other hand, constructing and
+% evaluating the conditions for complete positivity is involved and is the main
+% problem addressed in this paper. 
+% Moreover, these operations are by definition
+% diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
+% \alpha} \right\}$ basis.
 
-It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels.
-In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.
+% As mentioned above, \pce{} maps\R{A1} nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
+% \begin{equation}
+% 	\paulicomponents \mapsto \taus \paulicomponents.
+% % 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
+% \label{eq:definition:Pauli}
+% \end{equation}
+% % with $\tau_{\vec \alpha}$ either $1$ or $0$.
+% % \cpnote{Revisar aca lo que sigue}
+% % Similar to the qubit case, not every operation with this form is a completely
+% % positive trace perserving map. 
+% For the operation to be trace preserving, it is
+% easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and
+% evaluating the conditions for complete positivity is involved and is the main
+% problem addressed in this paper. Moreover, these operations are by definition
+% diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
+% \alpha} \right\}$ basis.
 
-\cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-frases de la importancia de esta familia.} \ddnote{hecho, pero de pronto quedo espeso.
-Me estan gustando las cosas que he estado encontrando, voy a investigar en esa direccion por mi cuenta, si sale algo interesante, los invito, como no}
+% \cpnote{Creo qeu vale la pena mencionar la relacion con los canales de Ruskai.
+% Lo discutimos en pleno, o por lo menos cuando esten JA y FL. quizá tambien
+% discutir si se mencionan a los canales  \cite{Siudzinska2020}}\ddnote{Eh estado
+% trabajando en esto, pero el material que he encontrado va mejor en la
+% introduccion, y en todo caso, creo que es muy pronto para mencionar detalles
+% tecnicos sobre los canales que coinciden con los de Ruskai, pues ni siquiera
+% hemos dicho que operaciones de las que definimos aqui, son válidas}
 
+It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set
+of ``Pauli diagonal channels constant on axes'' defined in
+Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of
+\textit{quantum-classical} channels. In particular, it can be shown that
+quantum-classical channels defined with the eigenbasis of some set of $2^N-1$
+commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
+2^N $ components equal to $1$s in its diagonal.
+
+% \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
+% frases de la importancia de esta familia.} \ddnote{hecho, pero de pronto
+% quedo espeso. Me estan gustando las cosas que he estado encontrando, voy a
+% investigar en esa direccion por mi cuenta, si sale algo interesante, los
+% invito, como no}
+% 
 %\ddnote{hay un typo en esta ecuacion}
@@
 
-For the two qubits case, the operations illustrated
-in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing
-the positions of the $0$s and $1$s of the diagonal using the Pauli string
-basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{}
-maps\R{A3} turned out to be very useful for their analysis throughout this
-work.
+% For the two qubits case, the operations illustrated
+% in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing
+% the positions of the $0$s and $1$s of the diagonal using the Pauli string
+% basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{}
+% maps\R{A3} turned out to be very useful for their analysis throughout this
+% work.
+%
 

### 2021-12-16 documentos/vector_space.tex
etc
Referencia a ecuación rota

@@
-\subsection{A vector space of channels} % {{{
+\subsection{A vector space of channels } % {{{
+\ddnote{propongo channels as vector spaces como titulo de seccion, pues lo actual se entiende mas en el sentido estandar: canales como miembros de un espacio vectorial, que tambien es cierto, pero no es el punto aqui}
 \cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
@@
 Choi matrix of any diagonal 
-Pauli channel, as in \eref{eq:definition:Pauli}.
+Pauli channel, as in \eref{eq:definition:Pauli}\janote{referencia rota}.
 

### 2021-12-16 documentos/generators.tex
En vez de PCE a secas, PCE map, PCE channel o PCE quantum channel

@@
 
-There exists a subset of PCE channels that generate 
-all PCEs; the nature of these generators may be studied, as we
+There exists a subset of PCE quantum channels that generates the entire set; 
+the nature of these generators may be studied, as we
 shall see, with the properties of the aforementioned vector space.
@@
 this set reduces to $W$ itself,
-and since intersection of subspaces translates to composition of PCEs,
-this implies that all PCEs can be obtained as
-compositions of PCEs corresponding to maximally non-trivial subspaces, plus
-the identity map. In other words, the set of PCEs that preserve half 
+and since intersection of subspaces translates to composition of PCE channels,
+this implies that all PCE quantum channels can be obtained as
+compositions of PCE channels corresponding to maximally non-trivial subspaces, plus
+the identity map. In other words, the set of PCE quantum channels that preserve half 
 of the components plus the identity map, are a generator set for 
@@
 The same symmetry is identified for the rows and columns of $A$ if one 
-labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$,
-where $\vec\alpha$ is the same vector index used throughout in this manuscript.
+labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
 \janote{Aquí habría que agregar la prueva de simetría para la $A$.}

### 2021-12-16 documentos/generators.tex
Cambio 1-qubit por single qubit, para que armonice con todo el artículo

@@
 %Alfredo o Carlos la terminan}
-
-%\janote{Mis sugerencias para esta sección son:\newline\indent (1) Es ilustrativo y bonito
-%explicar a punta de las figuras PCE cómo generar todos los canales PCE 
-%de 2 qubits. Sólo es necesario mostrar cómo se generan elementos representativos
-%de cada clase de equivalencia. [Ya se habló de las clases de equivalencia a
-%esta altura del artículo?] Esto es algo que se puede poner en un apéndice.\newline\indent
-%(2) Para el caso de 1 qubit, nuestra noción de generadores es compatible 
-%con los resultados de Siudzinska \cite{siudzinska2019geometry} sobre 
-%el espacio en el tetraedro de los canales cuánticos que son accesibles 
-%mediante generadores locales de tiempo. Quizás una referencia es 
-%apropiada.\newline\indent
-%(3) Hablar sobre la relación entre los generadores y filas o columnas de la $A$.
-%Esto lo podemos discutir con más detalles, Carlos. 
-%}
-
-%\esqueletoja{By standard theorems of linear algebra, any subspace $W$ 
-%in \eqref{eq:19}, associated with a unique PCE quantum channel, can be 
-%extended to a maximal subspace of dimension $2N-1$ by adjoining appropiate
-%additional basis elements.}
-
-%\colorbox{yellow}{\textcolor{blue}{Esqueleto}}
-%\textcolor{jacolor}{
-%\begin{itemize}
-%\item Siguiendo la discusión de los espacios vectoriales de la sección anterior, 
-%introducir de forma consecuente los generadores como subespacios maximales. 
-%Es decir, darle una retocada a lo que ya escribió Francois, pero que armonice 
-%con lo que viene de la sección anterior.
-%\item Ilustrar el algoritmo para construir todos los PCEs como 
-%concatenaciones de los generadores. Comentar al final del párrafo que, para 
-%1 qubit, nuestro descubrimiento de los PCEGs es compatible con los resultados 
-%de Siudzinska~\cite{siudzinska2019geometry} sobre el espacio en el tetrahedro 
-%en el que ella encontró que viven los canales cuánticos que son accesibles 
-%mediante generadores. **en algún lado aquí se puede decir que en el apéndice 
-%se muestra con los tableros como generar todo el caso de 2 qubits
-%\item Ya que expusimos en el párrafo anterior la utilidad de los generadores, 
-%hablar de la relación de los generadores con la $A$, como una forma de 
-%obtenerlos. El enunciado principal podría ser algo como "The matrix $A$ 
-%contains all the information of PCE quantum channels". Es una frase fuerte, 
-%pero creo que con un poco de meditación es cierto; de la $A$ puedes sacar 
-%los generadores, y con ellos todos los PCEs, se acabó. 
-%\item Hablar de las simetrías de los generadores. (No sé a qué se refiere quien 
-%escribió eso. Toca hablarlo con Carlos.)
-%\end{itemize}}
-%
-%Un párrafo de intro a las tres ideas 
-%\begin{itemize}
-%\item Existen los generadores 
-%\item Clasificación de los generadores 
-%\item Simetrías
-%\end{itemize}
 
@@
 all PCE channels.
-% and the complete vector space (corresponding to the identity channel),
-% which we call generators. 
-% \cpnote{Aca tenemos un semigrupo y no se si incluir a la identidad como 
-% generador. De alguna manera es excepcional. Es problematico incluirla y es 
-% problematico no incluirla.}
 Consider \Fref{fig:examplesPCE}; subfigures (c), (d) and (e) represent nontrivial 
@@
 
-%\cpnote{Arreglar}
 PCE generators may be characterized by its local action on every qubit 
 in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
-with $\vec\alpha$ each of the $4^{N}$ different vector indices. For 1-qubit
+with $\vec\alpha$ each of the $4^{N}$ different vector indices. For a single qubit
 the PCE generators are the identity map plus the channels that map the Bloch 
@@
 
-%\cpnote{Mucha lora y no se prueba nada}
 A reflection symmetry is identified for both PCE generators $\pceg$ and
 the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
-%PCE generators $\pceg$ obey a symmetry
-%that defines uniquely every PCE generator. 
 The symmetry for a PCE generator $\pceg$ is encoded in the 
@@
 \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
-\caption{Connection between rows and columns of $a$ and 1-qubit PCE generators.
+\caption{Connection between rows and columns of $a$ and single qubit PCE generators.
 The rows or columns of $a$ and the diagrams of the generators are either 
@@
 
-%\cpnote{Mucha lora y no se prueba nada, again}
 Given that both matrix $\san$ and PCE generators $\pceg$ have the same 
@@
 all entries with $-1$ to $0$. In \Fref{fig:A_and_PCEGs_connection} we illustrate
-this connection between $a$ and 1-qubit PCE generators.
+this connection between $a$ and single qubit PCE generators.
 In \appref{sec:2_qubits} we illustrate this program for 2-qubits PCE channels.
@@
 
-%Quizá en un apendice poner todos los generadores de dos qubits. 
-%\janote{Poner el comentario en algún lado de que hay que hacer una
-%referencia a un apéndice.}
-%
-%\janote{falta escribir un párrafo sobre la clasificación: (la clasificación 
-%es de que cada generador está caracterizado por un $\alpha$)}
-%También poner como se pueden calsificar los generadores y por aih poner la clasificacion de los 
-%generadores en la figura.  o en el texto
-%
-%\begin{itemize}
-%\item Clasificacion de los generadores, es decir que para dos qubits, lo podemos indicar con la acción sobre cada qubit individual
-%\item Quizá mostrar algunas propiedades de simetrías. 
-%\item Notar lo de los generadores y como sale la estructura jerárquica 
-%\end{itemize}
 % }}}

### 2021-12-18 documentos/kraus.tex
dandole

@@
 \cpnote{This is the original $a$, not $H \otimes H$. See how to relate these
-two matrices, or define a new $a$ and $A$}
+two matrices, or define a new $a$ and $A$} \ddnote{tengo entendido que nunca se define o redefine $a$ como $H \otimes H$, ni en el apendice, solo se dice que se intercambian para ciertos calculos.
+Creo que la notacion es segura.}
 % with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
@@
 \rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
-=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}
+=&\frac{1}{2^N}\sum_{\vec \beta}  \frac{1+A_{\vec \alpha \vec \beta}}{ 2} r_{\vec \beta} \sigma_{\vec \beta}
 \end{align}
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
-by Kraus operators  \eref{eq:kraus:PCE} is a PCE. Moreover, One can notice that, 
+by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel\ddnote{agrego 'channel', aqui el PCE map si es por construccion un canal}. Moreover, One can notice that, 
 except for the first row, half of the matrix elements of each row is $+1$ and 
@@
 
+PCE channels can be seen as the fixed points of some decoherence process.
+We will show this first for PCEGs.
+Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
+\begin{align}
+\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
+&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}.
+\end{align}
+It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative Markovian process
 \begin{itemize}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 \end{align}
-It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative Markovian process
+It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process.
+The Lindblad generator~\cite{lindblad}, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
+\begin{equation}
+\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
+\end{equation}
+where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.
+
+Since PCEGs commute, we can construct easily decoherence processes for any other PCE channel, in these cases the Lindblad generator 
 \begin{itemize}

### 2021-12-19 documentos/kraus.tex
Updated framework to the lattest version
dandole

@@
 \rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
-=&\frac{1}{2^N}\sum_{\vec \beta}  \frac{1+A_{\vec \alpha \vec \beta}}{ 2} r_{\vec \beta} \sigma_{\vec \beta}
+=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}
 \end{align}
@@
 \mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
-&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}.
+&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
 \end{align}
+where $\gamma>0$.
 It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process.
@@
 
-Since PCEGs commute, we can construct easily decoherence processes for any other PCE channel, in these cases the Lindblad generator 
+Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process.
+For them, the Lindblad generator is simply the sum of the generators of the corresponding generators, thus, the Lindblad operators are simply [...] The channel depicted in [...] is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$
+\begin{equation}
+\mcL=\frac{\gamma_{(0,3)}\left(\one\otimes\sigma_z\rho\one\otimes\sigma_z -\rho \right)}{2}+\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2}
+\end{equation}
+
+In addition to decoherence processes, PCE channels can also be described with collision models, 
 \begin{itemize}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process.
-For them, the Lindblad generator is simply the sum of the generators of the corresponding generators, thus, the Lindblad operators are simply [...] The channel depicted in [...] is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$
+For them, the Lindblad generators are simply the sum of the Lindbladians of the corresponding generators.
+As an example, consider the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation process described with the following Lindbladian,
 \begin{equation}
-\mcL=\frac{\gamma_{(0,3)}\left(\one\otimes\sigma_z\rho\one\otimes\sigma_z -\rho \right)}{2}+\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2}
+\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}+\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho \right)}{2},
 \end{equation}
+where $\gamma_{(0,3)}$ and $\gamma_{(3,3)}$ are positive and correspond to the Lindblad operators $\sigma_{(0,3)}$ and $\sigma_{(3,3)}$.
+Notice that such election of Lindblad operators is not unique, as the PCE channel described here is also equal to $\mcG_{(0,3)}\mcG_{(3,0)}$.
 
-In addition to decoherence processes, PCE channels can also be described with collision models, 
+In addition to the implementation via decoherence processes, PCE channels can also be described with collision models [cita].
+To see this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla [Stinespring citation].
+For any PCEG, a qubit can always be chosen as the ancilla, concretely,
+\begin{equation}
+\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \rho\otimes \projj{0} U^\dagger{}_{\vec \alpha} \right),
+\end{equation}
+where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
+\begin{align}
+U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
+U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
+\label{eq:Nqubit_stinespring}
+\end{align}
+Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed.
+In fact, generators are described with one collision.
+For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
+For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit environment with the additional assumption that its state is erased and transformed again $\ket{0}$ after each collision).
+The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$
+\begin{equation}
+\mcE[\rho]=\tr_{\text{E}} \left( U \left( \rho \projj{0}^{\otimes M}\right) \right)
+\end{equation}
+Described as the system \textit{colliding} with qubit particles
 \begin{itemize}
@@
 
-\begin{align}
-U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)\\
-U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right)
-\label{eq:Nqubit_stinespring}
-\end{align}
 % }}}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 
-PCE channels can be seen as the fixed points of some decoherence process.
+Any PCE channel can be seen as the fixed point of some decoherence process.
 We will show this first for PCEGs.
@@
 For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit environment with the additional assumption that its state is erased and transformed again $\ket{0}$ after each collision).
-The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$
+The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle.
+Therefore $\mcE$ can be written as follows,
 \begin{equation}
-\mcE[\rho]=\tr_{\text{E}} \left( U \left( \rho \projj{0}^{\otimes M}\right) \right)
+\mcE[\rho]=\tr_{\text{E}} \left( (U_{\vec\alpha_1}) \left( \rho \projj{0}^{\otimes M}\right) \right)
 \end{equation}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 where $\gamma>0$.
-It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process.
-The Lindblad generator~\cite{lindblad}, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
+It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}.
+The Lindblad generator of $\mcG_{\vec \alpha, t}$, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
 \begin{equation}
@@
 \begin{equation}
-\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \rho\otimes \projj{0} U^\dagger{}_{\vec \alpha} \right),
+\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
 \end{equation}
@@
 \begin{equation}
-\mcE[\rho]=\tr_{\text{E}} \left( (U_{\vec\alpha_1}) \left( \rho \projj{0}^{\otimes M}\right) \right)
+\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
 \end{equation}
+where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits.
+Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
+$U_{\vec\alpha_M}U_{\vec\alpha_{M-1}}\dots U_{\vec\alpha_1}$
 Described as the system \textit{colliding} with qubit particles

### 2021-12-19 documentos/kraus.tex
dandole

@@
 It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}.
-The Lindblad generator of $\mcG_{\vec \alpha, t}$, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
+The Lindblad generator of $\mcG_{\vec \alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
 \begin{equation}
@@
 Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process.
-For them, the Lindblad generators are simply the sum of the Lindbladians of the corresponding generators.
+For them, the Lindblad generators are the sum of the Lindbladians of the corresponding generators.
 As an example, consider the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation process described with the following Lindbladian,
@@
 
-In addition to the implementation via decoherence processes, PCE channels can also be described with collision models [cita].
-To see this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla [Stinespring citation].
-For any PCEG, a qubit can always be chosen as the ancilla, concretely,
+PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}.
+To prove this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla~\cite{Stinespring2006}.
+Since PCEG always have Kraus rank $2$, one can always choose a qubit as the ancillary system, concretely,
 \begin{equation}
@@
 \end{equation}
-where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
+where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as,
 \begin{align}
@@
 For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
-For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit environment with the additional assumption that its state is erased and transformed again $\ket{0}$ after each collision).
+For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision).
 The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle.
@@
 Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
-$U_{\vec\alpha_M}U_{\vec\alpha_{M-1}}\dots U_{\vec\alpha_1}$
-Described as the system \textit{colliding} with qubit particles
 \begin{itemize}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 \begin{itemize}
-\item Relate to decoherence, for PCEG
-\item Play with non PCEG PCEs
+\item Relate to decoherence, for PCEG\ddnote{hecho}
+\item Play with non PCEG PCEs\ddnote{hecho}
 \item Dependiendo de si sale algo bonito, podemos poner algun modelo en
 particular para todos los canales (sistema central + ambiente). Seria de buscar
-dilataciones sencillas y razonables por lo menos a los canales generadores.
+dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
 \todo{Davalos lidera la discusión de ese punto, pero no escribe nada}

### 2021-12-19 documentos/kraus.tex
dandole

@@
 For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
-For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision).
+For this, we can define an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision).
 The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle.

### 2021-12-24 other/ht-01.tex
Temporal

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{makeidx}
\usepackage{graphicx}

\usepackage{physics}
\usepackage{dsfont}

\renewcommand{\theenumi}{\alph{enumi}}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\definecolor{jacolor}{RGB}{200,40,0} \FXRegisterAuthor{ja}{aja}{\color{jacolor}JA}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{José Alfredo de León}
\title{Hoja de trabajo 1}
\begin{document}
\maketitle

\textbf{Instrucciones:} Resuelva de forma clara y ordenada (a papel y lapiz o 
utilizando \LaTeX) los ejercicios y suba su solución a más tardar para la fecha
XXX a la plataforma de Google Classroom. La calificación de esta hoja de trabajo
será por cantidad de ejercicios \textbf{resueltos completamente}.

\subsubsection*{Ejercicio 1. Notación de Dirac.}
Si consideramos únicamente los grados de libertad de espín, el fotón es un 
sistema cuántico de 3 niveles. Es decir, el espacio de Hilbert de un fotón es 
$\mathcal{H}=\mathbb{C}^3$. Consideremos ahora una base ortonormal 
de este espacio $\qty{\ket{\phi_i}}$ y también dos estados del 
fotón $\ket{\psi_1}=i\ket{\phi_1}+3i\ket{\phi_2}-\ket{\phi_3}$
y $\ket{\psi_2}=\ket{\phi_1}-i\ket{\phi_2}+5i\ket{\phi_3}$, donde $\qty{\phi_i}$.
\begin{enumerate}
\item El producto interior, llamado ``bracket'' en la notación de Dirac, 
cuántifica la proyección de un estado (vector) sobre otro estado
(vector). Calcule los brackets
$\braket{\phi_i}{\phi_j}$, cuando $i=j$ y cuando $i\ne j$.
\item Calcule $\braket{\psi_i}{\psi_j}$ para $i,j=1,2$ y, a partir de estos
resultados, calcule 
$\Big(\bra{\psi_1}+\bra{\psi_2}\Big)\Big(\ket{(\psi_1}+\ket{\psi_2}\Big)$.
\item En general, para cualesquiera dos estados $\ket{\psi_1}$ y
$\ket{\psi_2}$, ¿los brackets $\braket{\psi_1}{\psi_2}$ y
$\braket{\psi_2}{\psi_1}$ son iguales? ¿Por qué?
\end{enumerate}
\textit{Checkpoint: (medí cuánta física has aprendido)} Cualquier estado $\ket{\psi}$
del fotón puede escribirse como
\begin{align}
\ket{\psi}=\sum_{i=1}^3c_i\ket{\varphi_i}
\end{align}
Matemáticamente (y en notación de Dirac), ¿qué es lo que debés calcular si
te preguntan por la proyección del estado $\ket{\psi}$ sobre cada uno de los 
elementos de la base $\qty{\ket{\varphi_i}}$?
\begin{enumerate}
\item[d.]
Los operadores que actúan sobre $\mathcal{H}$ también se pueden 
escribir en la notación de Dirac como productos externos de ket's con bra's.
Calcule $\dyad{\psi_1}{\psi_2}$ y $\dyad{\psi_2}{\psi_1}$.
\item[e.] Dada una base ortonormal $\qty{\ket{\phi_i}}$
y un operador $\Lambda$, la traza de $\Lambda$ se calcula como
\begin{align}
\Tr (\Lambda)&=\sum_i \matrixel{\phi_i}{\Lambda}{\phi_i}
\end{align}
Calcule la traza de los operadores en (d).
\item 
Repita los cálculos de los incisos (b), (c), (d) y (e) usando la representación 
matricial. \textit{Ayuda para repetir (d):} calcule $\dyad{\phi_1}{\phi_1}$, 
$\dyad{\phi_2}{\phi_1}$ y $\dyad{\phi_3}{\phi_2}$ y note la relación entre 
los índices $i$ y $j$ del producto $\dyad{\phi_i}{\phi_j}$ y las posiciones del
elemento no nulo en la matriz de $3\times 3$.
\item[f.] Escriba los conjugados Hermíticos de $\ket{\psi_1}$, $\ket{\psi_2}$,
$\dyad{\psi_1}{\psi_2}$ y $\dyad{\psi_2}{\psi_1}$ en notación de Dirac
y en su representación matricial asumiendo que $\qty{\ket{\phi_i}}$ es la base
canónica.
\end{enumerate}

\subsection*{Ejercicio 2. De la notación de Dirac a la representación
matricial.}
Repita los incisos d, e y f del ejercicio 1 calculando la representación matricial 
de $\dyad{\psi_1}{\psi_2}$ y $\dyad{\psi_2}{\psi_1}$.\newline

\textit{Ayuda:} Los indices $i,j$ del operador $\lambda \dyad{\phi_i}{\phi_j}$ se 
corresponden con la posición del escalar $\lambda$ en la matriz de $3\times 3$.
Por ejemplo, 
\begin{align}
3\dyad{\phi_1}{\phi_3}=\mqty(0&0&3\\0&0&0\\0&0&0).
\end{align}

\subsection*{Ejercicio 3. Operadores I.}
Considere un sistema de dos niveles, como una partícula de espín $1/2$ (un 
electrón, por ejemplo). Considere la matriz de Pauli $\hat \sigma_z$ que se define 
como $\hat \sigma_z\ket{0}=\ket{0}$ y $\hat \sigma_z\ket{1}=-\ket{1}$; $\ket{0}$ 
y $\ket{1}$ son ortonormales,
\begin{enumerate}
\item ¿Los estados $\ket{0}$ y $\ket{1}$ forman una base del espacio
de estados? ¿Por qué?
%\item[(b)] Considere el operador $\hat \Lambda=\dyad{0}{1}$. ¿Es $\hat \Lambda$ hermítico?
\item Muestre que $\hat \Lambda^2=0$.
\item Un operador $\hat P$ que es un proyector satisface la condición
$\hat P^2=\hat P$. Muestre que $\hat \Lambda \hat \Lambda^{\dagger}$ y 
$\hat \Lambda^{\dagger} \hat \Lambda$ son proyectores.
\item Los operadores unitarios son importantes en física porque describen 
la evolución de los sistemas cuánticos cerrados. Por otro lado, el conmutador 
de dos operadores en mecánica cuántica nos proporciona información sobre 
la implicación que podría tener alterar el orden de dos mediciones sucesivas.

Un operador $\hat U$ se dice que es unitario si satisface la condición
$\hat U\hat U^{\dagger}=\hat U^{\dagger}\hat U=\mathds{1}$ ($\mathds{1}$ el operador identidad).
El conmutador de dos operadores $\hat \Lambda$ y $\hat B$ se define como
$\comm{\hat \Lambda}{\hat B}=\hat \Lambda\hat B-\hat B\hat \Lambda$. 
Muestre que el operador 
$\hat \Lambda\hat \Lambda^{\dagger}-\hat \Lambda^{\dagger}\hat \Lambda$ es unitario.
\end{enumerate}

\subsection*{Ejercicio 4. Operadores II.}
Considere el estado $\ket{\psi}$ del fotón, que está dado en términos de la 
base ortonormal $\qty{\ket{\phi_k}}$, de la forma
\begin{align}
\ket{\psi}=a\bigg(\frac{i}{\sqrt{15}}\ket{\phi_1}+
\frac{1}{\sqrt{3}}\ket{\phi_2}-
\frac{i}{\sqrt{5}}\ket{\phi_3}\bigg),
\end{align}
donde $a\in \mathbb{R}$ y $\ket{\phi_k}$ son eigenestados del 
operador $\hat B$, tal que satisface la ecuación de eigenvalores siguiente,
\begin{align}
\hat B\ket{\phi_k}=k\ket{\phi_k}.
\end{align}
\begin{enumerate}
\item Encuentre la constante de normalización $a$ del estado $\ket{\psi}$. 
\item Encuentre el valor de expectación de $\hat B$ para el estado $\ket{\psi}$.
\item Encuentre el valor de expectación de $\hat B^2$ para el estado 
$\ket{\psi}$. 
\end{enumerate}

\subsection*{Ejercicio 5. Operadores III.}
Considere el operador
\begin{align}
\hat A=\dyad{\phi_1}{\phi_1}+\dyad{\phi_2}{\phi_2}+\dyad{\phi_3}{\phi_3}
-i\dyad{\phi_1}{\phi_2}-\dyad{\phi_1}{\phi_3}+i\dyad{\phi_2}{\phi_1}
-\dyad{\phi_3}{\phi_1},
\end{align}
donde $\qty{\ket{\phi_i}}$ forma una base ortonormal y completa.
\begin{enumerate}
\item ¿Es $\hat A$ hermítico?
\item ¿Es $\hat A$ un proyector?
\item Encuentre la representación matricial de $\hat A$ en la base $\qty{\ket{\phi}}$.
\item Encuentre los eigenvalores y eigenvectores de la matriz. 
\end{enumerate}

\subsection*{Ejercicio 6. Representación en bases discretas.}
\janote{Hacer este ejercicio para $\Tr (AB)=\Tr (BA)$ en el taller.}
Supongamos tres operadores $\hat \Lambda$, $\hat B$ y $\hat C$ que actúan sobre 
el espacio de Hilbert de un sistema cuántico de dimensión finita. Utilizando
notación de Dirac, muestre que
\begin{align}
\Tr \big(\hat \Lambda\hat B\hat C \big)=\Tr \big(\hat C\hat \Lambda\hat B \big)
=\Tr \big(\hat B\hat C\hat \Lambda \big).
\end{align}
Esta se conoce como la ``propiedad cíclica'' de la traza y es generalizable
para cualquier cantidad de operadores. La traza de la multiplicación de $n$
operadores es invariante ante permutaciones de cíclicas del producto de los
operadores.

\subsection*{Ejercicio 7. Representación en bases continuas.}
\janote{Dar pistas en el taller. Quizás hacer el caso inverso?}
Utilizando la notación de Dirac muestre que la función de onda $\psi(x)$ es 
la transformada de Fourier de la función de onda $\Psi (p)$. Utilice el hecho 
de que el cambio de base del espacio de los momenta al de posiciones está 
dado por
\begin{align}
\braket{x}{p}=\frac{1}{\qty(2\pi\hbar)^{3/2}}e^{ipx/\hbar}.
\end{align}

\subsection*{Ejercicio 8. Mecánica matricial.}
El Hamiltoniano de un sistema de dos niveles está dado por 
\begin{align}
\hat H=E\qty(\dyad{\phi_1}{\phi_1}-\dyad{\phi_2}{\phi_2}-i\dyad{\phi_1}{\phi_2}
+i\dyad{\phi_2}{\phi_1}),
\end{align}
donde $\ket{\phi_1}$ y $\ket{\phi_2}$ forman una base ortonormal y completa, y
$E$ es una constante real que tiene dimensionales de energía.
\begin{enumerate}
\item ¿Es $\hat H$ Hermítico? Utilizando la notación de Dirac, 
calcule la traza de $\hat H$.
\item Encuentra la representación matricial de $\hat H$ en la base 
$\ket{\phi_1}$ y $\ket{\phi_2}$ y calcule los eigenvalores y eigenvectores
de la matriz. Ahora que tiene la matriz que representa a $\hat H$ calcule de nuevo
la traza (sumando los elementos de la diagonal) y comparelo con el resultado
del inciso (a).
\item Calcule $\comm{\hat H}{\dyad{\phi_1}{\phi_1}}$, $\comm{\hat H}
{\dyad{\phi_2}{\phi_2}}$ y $\comm{\hat H}{\dyad{\phi_1}{\phi_2}}$.
\end{enumerate}

\subsection*{Respuestas}
\begin{enumerate}
\item[2.a.] $a=\sqrt{5/3}$
\item[2.b.] $\matrixel{\psi}{\hat B}{\psi}=20/9$
\item[2.c.] $\matrixel{\psi}{\hat B^2}{\psi}=16/3$
\end{enumerate}
\end{document}

### 2021-12-24 other/ht-02.tex
Temporal

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{makeidx}
\usepackage{graphicx}

\usepackage{physics}
\usepackage{dsfont}

\renewcommand{\theenumi}{\alph{enumi}}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\definecolor{jacolor}{RGB}{200,40,0} 
\FXRegisterAuthor{ja}{aja}{\color{jacolor}JA}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{José Alfredo de León}
\title{Hoja de trabajo 2}
\begin{document}
\maketitle

\textbf{Instrucciones:} Resuelva de forma clara y ordenada (a papel y lapiz o 
utilizando \LaTeX) los ejercicios y suba su solución a más tardar para la fecha
XXX a la plataforma de Google Classroom. La calificación de esta hoja de trabajo
será por cantidad de ejercicios \textbf{resueltos completamente}.

\textbf{Se recomienda fuertemente utilizar algún software, como Python
o Mathematica, para resolver operaciones entre matrices, calcular eigenvalores 
y eigenvectores o cualquier otro procedimiento algebraico repetitivo y largo.}

\subsubsection*{Ejercicio 1. Estados estacionarios y evolución temporal.}
Se denota como $\psi(n)$ a los estados estacionarios 
ortonormales de un sistema cuya energ\'ia correspondiente es $E_n$. 
Supongamos que la funci\'on de onda normalizada
del sistema en el tiempo $t=0$ es $\Psi(x,0)$ y supongamos que una medici\'on
de la energ\'ia da como resultado el valor $E_1$ con probabilidad $1/2$, $E_2$
con probabilidad $3/8$ y $E_3$ con probabilidad $1/8$. 
\begin{enumerate}
\item ¿Qu\'e significa que un estado sea estacionario?
\item ¿Escriba la expansi\'on m\'as general para $\Psi(x,0)$ consistente con 
esta informaci\'on.
\item ¿Cu\'al es la expansi\'on para la funci\'on de onda del sistema para un tiempo 
$t>0$, $\Psi(x,t)$?
\item ¿Muestre que el valor esperado del Hamiltoniano no cambia en el tiempo.
\end{enumerate}

\subsubsection*{Ejercicio 2. Medición de la energía.}
Un sistema compuesto por dos átomos de dos niveles (estado fundamental + 
estado excitado) es un sistema cuántico de 4 niveles, por consiguiente, su 
espacio de estados es $\mathcal{H}=\mathbb{C}^4$. Supongamos un estado
inicial, en $t=0$, de la forma
\begin{align}
\ket{\psi(0)}&=\frac{1}{\sqrt{3}}\ket{\phi_1}+\frac{1}{2}\ket{\phi_2}
+\frac{1}{\sqrt{6}}\ket{\phi_3}+\frac{1}{2}\ket{\phi_4},
\end{align}
donde $\{ \ket{\phi_i}\}$ son los eigenestados ortonormales del Hamiltoniano
$\hat H$ del sistema. 
\begin{enumerate}
\item Si los eigenestados $\ket{\phi_i}$ del Hamiltoniano tienen
energías $E_i$, respectivamente, escriba el estado
$\ket{\psi(t)}$, para $t>0$.
\item ¿Cuáles son los posibles resultados de medir la energía de este sistema
en el estado $\ket{\psi(t)}$ y con qué probabilidad ocurrirán?
\item Encuentre el valor esperado del Hamiltoniano del sistema en $t=0$
y $t=10$ s. ¿De qué forma tendría que ser el estado $\ket{\psi(0)}$ para que 
el valor esperado del Hamiltoniano $\hat H$ sea constante en el tiempo?
\end{enumerate}

\subsubsection*{Ejercicio 3. Conjunto completo de operadores 
que conmutan I.}
El fotón (partícula de espín 1), cuando sólo consideramos sus grados de 
libertad de espín,
es un sistema cuántico de 3 niveles, \textit{i.e.} $\mathcal{H}=\mathbb{C}^3$.
\begin{enumerate}
\item ¿Cuál es la dimensión de las matrices que representan a los observables que 
actúan sobre el espacio de estados del fotón? Convánzase de que la dimensión 
debe ser $3\times 3$.
\end{enumerate}
Considere que el Hamiltoniano $\hat H$ y un operador $\hat A$ que actúan 
sobre el espacio 
de estados del fotón están dados por 
\begin{align}
\hat H&=\epsilon_0\mqty(-2&0&0\\ 0&1&0\\ 0&0&1),
&
\hat A&=a_0\mqty(5&0&0\\ 0&0&2\\ 0&2&0),
\end{align}
donde $\epsilon_0$ tiene dimensionales de energ\'ia.
\begin{enumerate}
\item ¿Los operadores $\hat H$ y $\hat A$ conmutan? Si es as\'i
encuentre la base de eigenvectores en com\'un.
\item ¿Cu\'al de los siguientes conjuntos de operadores forman un conjunto 
completo de operadores que conmutan: $\{ \hat H\}$, $\{ \hat A\}$, 
$\{ \hat H, \hat A\}$, $\{ \hat H^2, \hat A \}$?
\end{enumerate}

\subsubsection*{Ejercicio 4. Medición de la energía. CSCO y 
mediciones consecutivas.}
Consideremos de nuevo a un sistema cuántico compuesto por un fotón
cuyo Hamiltoniano $\hat H$ y estado inicial $\ket{\psi(0)}$ son
\begin{align}
\hat H&=\epsilon_0\mqty(1&-1&0\\-1&1&0\\0&0&-1),
&
\ket{\psi(0)}=\frac{1}{\sqrt{6}}\mqty(1\\1\\2),
\end{align}
donde $\epsilon_0$ tiene dimensionales de energía. 
\begin{enumerate}
\item ¿Cuáles valores se obtendrían al medir la energía del estado 
$\ket{\psi(0)}$ y con qué probabilidades?
\item Calcule el valor esperado del Hamiltoniano $\hat H$ en el estado 
$\ket{\psi(0)}$.
\end{enumerate}

\subsubsection*{Ejercicio 5}
De nuevo, consideremos a nuestro buen fotón como sistema cuántico,
cuyo estado $\ket{\psi}$ y dos observables $A$ y $B$ están dados por 
\begin{align}
\ket{\psi}&=\frac{1}{3}\mqty(-i\\2\\0),&
A&=\frac{1}{\sqrt{2}}\mqty(1&i&1\\-i&0&0\\1&0&0),&
B&=\mqty(3&0&0\\0&1&i\\0&-i&1).
\end{align}
\begin{enumerate}
\item ¿Los operadores $A$ y $B$ son compatibles? ¿Cuáles de los conjuntos 
$\{ \hat A\}$, $\{ \hat B\}$,$\{ \hat A,\hat B\}$ forman un conjunto completo 
de operadores que conmutan?
\item Se mide $\hat A$ primero e inmediatamente después $\hat B$. Encuentre
la probabilidad de obtener el valor $-1$ para $\hat A$ y el valor $3$ para $B$.
\item Ahora se mide en el orden inverso que en el inciso anterior. Encuentre
la probabilidad de obtener el valor $3$ para $B$ y el valor $-1$ para $\hat A$.
\item Compare y explique los resultados de los incisos b y c.
\end{enumerate}

\subsubsection*{Ejercicio 6}
De nuevo, consideremos a nuestro buen fotón como sistema cuántico,
cuyo estado $\ket{\psi}$ y dos observables $A$ y $B$ están dados por 
\begin{align}
\ket{\psi}&=\mqty(5\\1\\3),&
A&=\frac{1}{\sqrt{2}}\mqty(2&0&0\\0&1&1\\0&1&1),&
B&=\mqty(1&0&0\\0&0&1\\0&1&0).
\end{align}
\begin{enumerate}
\item ¿Los operadores $A$ y $B$ son compatibles? 
\item ¿Cuáles de los conjuntos $\{ \hat A\}$, $\{ \hat B\}$,$\{ \hat A,\hat B\}$ 
forman un conjunto completo de operadores que conmutan?
\end{enumerate}
\textbf{Advertencia:} la respuesta de los inciso a. y b. son suficientes
para contestar a los insisos siguientes sin tener que hacer un sólo 
cálculo. Tómese unos minutos para meditar la respuesta y discútalo con
sus compañeros. Si decide hacer los cálculos y no los hará con ayuda del algún 
software, ni siquiera intente hacerlos a mano, sólo perderá su tiempo y se frustrará.
\begin{enumerate}
\item[c.] Se realiza una medición donde $A$ se mide primero y luego $B$ 
inmediatamente 
después. Encuentre la probabilidad de obtener el valor de $\sqrt{2}$ para $A$
y el valor de $-1$ para $B$.
\item[d.] Ahora se mide $B$ primero e inmediatamente después $A$. Encuentre 
la probabilidad de obtener el valor $-1$ para $B$ y el valor $\sqrt{2}$ para $A$.
\item[e.] Compare los resultados de los incisos a y b. Explique.
\end{enumerate}

\subsubsection*{Ejercicio 7}
Considere un sistema cuántico de 3 niveles que tiene tres observables
que se representan por las siguientes matrices:
\begin{align}
A&=\mqty(1&0&0\\0&0&1\\0&1&0),&
B&=\mqty(0&0&-1\\0&0&i\\-1&-i&4),&
C&=\mqty(2&0&0\\0&1&3\\0&3&1).
\end{align}
\begin{enumerate}
\item Encuentre los posibles resultados de medir cada uno de los observables 
$A$, $B$ y $C$.
\item De los 3 observables, ¿cuáles de ellos son compatibles?
Encuentre la base de eigenvectores en común a ese/esos conjunto/os 
xde observables. 
\item ¿Cuáles de los conjuntos de operadores $\{ \hat A\}$, $\{ \hat B\}$, 
$\{ \hat C\}$
$\{ \hat A, \hat B\}$, $\{ \hat B, \hat C\}$, $\{ \hat A, \hat C\}$ y
$\{ \hat A, \hat B, \hat C\}$ forman un conjunto completo de observables que 
conmutan? 
\end{enumerate}

\end{document}

### 2022-01-18 documentos/math.tex
Fix the fixes

@@
 single qubit and then for $N$ qubits. We then restrict to PCEs and, for quantum
-channels, associate a vector space to the set of coefficients
-$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}, from which we are able to
+channels, associate a vector subspace to the set of coefficients
+$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}. This allows us  to
 derive several important conclusions. 
@@
 
-\flnote{
 We now construct the Choi matrix associated to the single qubit map
@@
 given by  $\bbrakket{A_1}{A_2}=\tr A_1^\star A_2$,
-} 
 % We now study the matrix form of the single qubit map $\mathcal{E}$ in

### 2022-01-18 documentos/pce.tex
Fix the fixes

@@
 \end{equation}
-where $\tau_\alpha$ is either $1$ or $0$. Not every
-operation like this is a quantum map; for example collapsing the entire Bloch
-ball to the $xy$ plane (setting $\tau_3=0$ and the rest to 1) is not a quantum
+where $\tau_\alpha$ is either $1$ or $0$ (trace preserving requires
+that $\tau_0=1$). Not every
+such operation  is a quantum map; for example collapsing the entire Bloch
+ball to the $xy$ plane (setting $\tau_{1,2}=1$ and  $\tau_3=0$) is not a quantum
 channel. A direct evaluation of the complete positivity
@@
 \end{align}
-where trace-preserving is already imposed ($\tau_0=1$), show that five out of
+where trace-preserving is already imposed, show that five out of
 the eight 1-qubit PCE maps are quantum channels.
@@
 
-In order to present and work the $N$ qubit case, it is useful 
+In order to present and develop the $N$ qubit case, it is useful 
 to introduce 
@@
 normalization of the state requires that $r_{\vec 0}=1$.
-We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
+We shall refer to $\paulicomponents$ as the {\it Pauli components} of the density
 matrix of a system of qubits.
@@
 problem addressed in this paper. 
-If we refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
+We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
 with arbitrary values of 
 % but allow the 
-$\taus$ (only restricted by complete positivity) as Pauli diagonal operations.
+$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.
 
@@
 
+A graphical representation for PCE maps may be introduced, being the
+two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
+Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
+from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
+the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
+empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
+for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
+
 It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set
@@
 %
-
-A graphical representation for PCE maps may be introduced, being the
-two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
-Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
-from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
-the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
-empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
-for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
 

### 2022-01-18 documentos/math.tex
just checking if git is working properly...
refuckulated the carbonator

@@
 spaces, which is used 
-in the construction of the Choi matrix~\cite{}. 
+in the construction of the Choi matrix.
 % \cpnote{Aca poner algo de que no es trivial y que se detalla en el apendice.}
@@
 \delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
-map corresponding to \eref{eq:definition:Pauli} is 
+map corresponding to a Pauli diagonal operation is 
 % Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$

### 2022-01-18 documentos/vector_space.tex
cita de libro algebra lineal
refuckulated the carbonator

@@
 This is a remarkable equation, as it provides a method to diagonalize the
-Choi matrix of any diagonal 
-Pauli channel, as in \eref{eq:definition:Pauli}\janote{referencia rota}.
+Choi matrix of any 
+Pauli diagonal operation.
 
@@
 First recall that a vector space of dimension $d$ over a field of $q$ elements
-has $q^d$ elements~\cite{CitaAlgebraLineal}.
+has $q^d$ elements~\cite{Roman2008}.
 Now $V$ is a vector space on a field of two elements having dimension $2N$. 

### 2022-01-18 documentos/vector_space.tex
Derp. Fix missing constant post rename

@@
 $\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
-$\{0,1\}$\cite{alguna:referencia}. 
+$\{0,1\}$.
 We notice that the Klein group described in \fref{tab:1} is actually isomorphic

### 2022-01-18 documentos/pce.tex
Who Let the Bugs Out??

@@
 
-It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set
+It is worth noticing that the set of \pce{} maps overlaps with the set
 of ``Pauli diagonal channels constant on axes'' defined in

### 2022-01-18 documentos/math.tex
I dont know what I am doing

@@
 fact that $a$ corresponds to a permutation of rows of  $H \otimes H$. However,
-we chose \janote{to keep} $a$ \janote{as in \eqref{eq:1},} as some later considerations [see  \eref{eq:sigma_property}]
-cannot be written easily in terms of $H \otimes H$.
+we chose the aforementioned definition as some later considerations [see
+\eref{eq:sigma_property}] cannot be written easily in terms of $H \otimes H$.
 

### 2022-01-18 documentos/math.tex
This should work until december 2013.

@@
 \kket{\sigma_{\vec{\alpha} }}&=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}} \nonumber \\
+\otimes\kket{\sigma_{\alpha_N}} 
+\nonumber \\
 &=\kket{\sigma_{\alpha_1}\otimes\cdots
@@
 \end{align}
-\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la vectorizacion de la Pauli string, con eso.}
+\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la
+vectorizacion de la Pauli string, con eso.}
 % 
@@
 to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
-$a^N$, which might be more convenient for other applications.\janote{en una 
-iteración posterior del artículo completo quizás es buena idea enmarcar más esto
-último de la otra a, ya que puede ser de interés en alguna aplicación}
+$a^N$, which might be more convenient for other applications.
+% \janote{en una 
+% iteración posterior del artículo completo quizás es buena idea enmarcar más esto
+% último de la otra a, ya que puede ser de interés en alguna aplicación}
 % \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 

### 2022-01-19 documentos/math.tex
vectorization issue

@@
 
-The same program can be carried out for $N$ qubits. In this case, 
+{\red The same program can be carried out for $N$ qubits. In this case, 
 the vectorized Pauli operators are 
@@
 \otimes\sigma_{\alpha_N}},
-\end{align}
-\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la
-vectorizacion de la Pauli string, con eso.}
+\end{align}}
+\ddnote{Mi edit: The same program can be carried out for $N$ qubits. In this case, 
+the vectorized Pauli operators are defined as follows, 
+\begin{equation}
+\kket{\sigma_{\vec{\alpha} }}:=\kket{\sigma_{\alpha_1}}\otimes\cdots
+\otimes\kket{\sigma_{\alpha_N}}.
+\end{equation}
+This vectorization must not be confused with the direct vectorization of $\sigma_{\vec \alpha}$, since the tensor product and the vectorization process generally do not commute~\cite{Gilchrist2009}.
+}
 % 

### 2022-01-19 documentos/pce.tex
quito espacios de las definiciones q meten problemas

@@
 The physical system under study will be associated with a Hilbert space
-denoted by \hilbert, and the set of linear operators over such space will 
+denoted by \hilbert{}, and the set of linear operators over such space will 
 be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system

### 2022-01-19 documentos/pce.tex
seccion 2 revisada

@@
 the non-local feature of quantum theory. 
-A linear map $\mcE$ is positive if it maps density operators to density operators, \ie
+A linear map $\mcE$ is positive if it maps density operators to density operators, \ie{}
 if $\mcE[\rho]\geq 0$ for all density matrices $\rho$. 
@@
 maximally entangled state between the original system and an ancilla.
-Remarkably, the map \mcE is completely positive
-if and only \choi (also called Choi or dynamical matrix of $\mcE$) 
+Remarkably, the map \mcE{} is completely positive
+if and only \choi{} (also called Choi or dynamical matrix of $\mcE$) 
 is positive-semidefinite~\cite{jamil,choi}.

### 2022-01-19 documentos/pce.tex
quito comentario de carlos

@@
 \subsection{Quantum channels} % {{{
-\cpnote{Cambios importantes, qeu David revise}
-
 Quantum channels are the most general linear operations that a quantum

### 2022-01-19 documentos/math.tex
lo de vectorizacion implementado en rojo

--- 2022-01-18 documentos/math.tex
@@
 
-The same program can be carried out for $N$ qubits. In this case, 
-the vectorized Pauli operators are 
-\begin{align}
-\kket{\sigma_{\vec{\alpha} }}&=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}} 
-\nonumber \\
-&=\kket{\sigma_{\alpha_1}\otimes\cdots
-\otimes\sigma_{\alpha_N}},
-\end{align}
-\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la
-vectorizacion de la Pauli string, con eso.}
+{\red The same program can be carried out for $N$ qubits. In this case, 
+the vectorized Pauli operators are defined as follows, 
+\begin{equation}
+\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
+\otimes\kket{\sigma_{\alpha_N}}.
+\end{equation}
+This vectorization must not be confused with the direct vectorization of $\sigma_{\vec \alpha}$, since the tensor product and the vectorization process generally do not commute~\cite{Gilchrist2009}.
+}
 % 

### 2022-01-19 documentos/vector_space.tex
stuff

@@
-\subsection{A vector space of channels } % {{{
-\ddnote{propongo channels as vector spaces como titulo de seccion, pues lo actual se entiende mas en el sentido estandar: canales como miembros de un espacio vectorial, que tambien es cierto, pero no es el punto aqui}
-\cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
-espacio. Quizá cuando haga falta se puede poner}
-\janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
-se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
-parece una buena idea podría elaborar más cómo meterlo ahí}
-\par
+\subsection{PCE channels as vector spaces} % {{{
+\cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
+% \ddnote{propongo channels as vector spaces como titulo de seccion, pues lo
+% actual se entiende mas en el sentido estandar: canales como miembros de un
+% espacio vectorial, que tambien es cierto, pero no es el punto aqui}
+% \cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
+% espacio. Quizá cuando haga falta se puede poner}
+% \janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
+% se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
+% parece una buena idea podría elaborar más cómo meterlo ahí}
+% \par
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
 
-In this subsection we will provide a one-to-one relation between PCE quantum channels 
-and the subspaces of a discrete vector subspace associated with the indices $\valpha$
-labeling the components of a state; see \eref{eq:N_qubits_rho}.
+In this subsection we will provide a one-to-one relation between PCE quantum
+channels and the subspaces of a discrete vector subspace associated with the
+indices $\valpha$ labeling the components of a state; see
+\eref{eq:N_qubits_rho}. \cpnote{Some established facts about vector spaces will allow
+us to draw conclusions for PCE quantum channels.}
 
@@
 due to complete positivity of the underlying channel. 
-Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
+Finally, setting $\valpha =0$ in \eref{eq:tau:is:A:p}, and taking into 
 account the normalization condition that $\tau_{\vec 0}=1$, we obtain
@@
 \begin{equation}
-\Phi(\vec\alpha):=\left\{
+\Phi(\vec\alpha)=\left\{
 \vec\beta:\san_{\vec\alpha\vec\beta}=1
@@
 When such a connection exists, $\tau_{\vec\alpha}=1$ implies
-$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
-of this connection.
+$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$.
 
-Let the components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for
-a particular particle index $k$, with 
-$\beta$ such that $\sa_{\alpha_k\beta}=1$.
+Let us now work out the nature of the aforementioned connection.  Let the
+components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
+particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
 Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
@@
 \end{equation}
-for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
-One can verify, by working out the different cases, 
-that \eref{eq:14} is equivalently expressed as 
+for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$.  One can verify, by
+working out the different cases, that \eref{eq:14} is equivalently expressed as 
 \begin{equation}
@@
 \caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that
-the operation is an {\em abelian group}, in fact it corresponds to the {\em
-Klein group}, where the neutral element is $0$. This is the reason for choosing
+the operation is an abelian group, in fact it corresponds to the 
+Klein group, where the neutral element is $0$. This is the reason for choosing
 an additive notation for the operation defined in (\ref{eq:14}). }
@@
 % Generacion de soluciones {{{
-So we may now proceed to generate all solutions: we start out from the solution
-having $\tau_{\vec0}=1$, with everything else $0$. We may then successively
-switch $\tau$'s to $1$ for various values of $\valpha$, taking care
-immediately to set equal to one the components of $\tau$ that correspond to values
-of $\vbeta$ generated by the previously switched values of $\valpha$ via the
-operation $\oplus$. Doing so, in an ordered way, allows one to generate
+With this information, we present a procedure to generate all solutions: we start out
+from the solution having $\tau_{\vec0}=1$, with everything else $0$. We may
+then successively switch $\tau$'s to $1$ for various values of $\valpha$,
+taking care immediately to set equal to one the components of $\tau$ that
+correspond to values of $\vbeta$ generated by the previously switched values of
+$\valpha$ via the operation $\oplus$. Doing so, in an ordered way, allows one
+to generate
 all valid quantum channels with a given set of preserved components, without the need
@@
 \end{center}
-\caption{\cpnote{Mejorar el caption cuando me ponga de acuerdo con la gente}
-Aca poner 6 PCEs. (f) Identidad, (a) totally depolarizing, (c, d y e) tres
-generadores, (b) un canal que resulte del generador. Sobra un espacio para
-ilustrar alguna otra cosa. Quiza poner otro generador para que se vea que no
-hay una manera unica de generar esos bichos.}
+\caption{
+\cpnote{Revisar, solo tiene una iteracion por parte mia}
+Examples of diagrams for several PCE quantum channels. In
+ (a) the totally depolarizing channel is represented whereas
+in (b) a PCE channel that preserves four components.  (c), (d)
+and (e) show three generators; the combination of any two of them
+yields the channel in (b). (f) represents the identity map. 
+% 
+% \cpnote{Mejorar el caption cuando me ponga de acuerdo con la gente}
+% Aca poner 6 PCEs. (f) Identidad, (a) totally depolarizing, (c, d y e) tres
+% generadores, (b) un canal que resulte del generador. Sobra un espacio para
+% ilustrar alguna otra cosa. Quiza poner otro generador para que se vea que no
+% hay una manera unica de generar esos bichos.
+}
 \label{fig:examplesPCE}
@@
 \par % }}}
-% Frase de David {{{
-\ddnote{Agrego esto:} A final remarks of the derivation as a tool. Concepts
-might be complicated, but the tool gives some simple rules to the reader:
-\textit{tell me what components you want to keep, and the (vector) summation
-rules will give you the rest of components to make the target operation a CPTP
-one.} \janote{Me gusta esto que puso David, pero lo movería a las conclusiones.}
-\par % }}}
 

### 2022-01-20 documentos/pce.tex
agrego archivos del apendice

@@
 commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
-2^N $ components equal to $1$s in its diagonal.
+2^N $ components equal to $1$s in its diagonal, see appendix~\sref{quantum_classical}.
 

### 2022-01-20 documentos/quantum_classical.tex
agrego archivos del apendice

\section{Quantum-Classical channels}
\label{quantum_classical}
A Quantum-classical channels is defined using orthonormal basis in the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ an orthonormal basis in $\hilbert_{2^N}$

### 2022-01-25 documentos/kraus.tex
dandole
quito texto rojo
secc V

--- 2021-12-19 documentos/kraus.tex
@@
-\section{Kraus operators and decoherence} % {{{
+\section{Kraus operators and decoherence  propuesta: Physical implementations of PCE maps} % {{{
 \cpnote{HAcer esta seccion despues de que david ponga lo de decoherencia, 
@@
 
-Furthermore, quantum channels enjoy the well-known \textit{Kraus
+{\red [texto viejo introductorio de la seccion] Furthermore, quantum channels enjoy the well-known \textit{Kraus
 representation} (or operator-sum representation) which reads 
@@
 that yield such channels. In this section we investigate and construct such 
-operators and explore the corresponding processes.
-
-To study the Kraus operators corresponding to PCE, it is enough to study 
+operators and explore the corresponding processes. To study the Kraus operators corresponding to PCE, it is enough to study 
 the ones corresponding to generators, as all PCEs commute and thus to get the 
 Kraus operators of an arbitrary PCE, one can easily combine the Kraus
-operators of its generators.
+operators of its generators. }
+
+{\blue [texto nuevo introductorio de la seccion]
+Given that \pce{} channels are projections, we might ask whether they are fixed points of some memory-less (Markovian) process or not.
+In this section we prove that they are, and give two examples of Markovian implementations.
+The first one consist in identifying each \pce{} channel as a fixed point of some pure dissipative process.
+The second, in identifying each \pce{} channel as fixed points of some memory-less collision model.
+
+\subsection{Kraus representation}
+To derive the aforementioned implementations, we exploit the existence of the PCEGs and their \textit{Kraus representation} (or operator-sum representation), which reads 
+\begin{equation}
+\mcE[\rho]=\sum_i K_i \rho
+K_i^\dagger{},
+\end{equation}
+with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
+}
 
@@
 % from other arguments. 
-
+\subsection{Pure dissipative implementation}
 Any PCE channel can be seen as the fixed point of some decoherence process.
@@
 where $\gamma>0$.
-It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}.
+It is easy to show that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}.
 The Lindblad generator of $\mcG_{\vec \alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
@@
 where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.
+Notice that $\sigma_{\vec \alpha}$ is trace-less, therefore the process is pure dissipative~\cite{cirac}.
 
@@
 
+\subsection{Collision model implementation}
 PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}.
@@
 \end{equation}
-where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as,
+where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as follows,
 \begin{align}
@@
 In fact, generators are described with one collision.
-For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
-For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision).
+For the general case consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
+For this we can define an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$, or equivalently one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision (memory-less collisions).
 The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle.
@@
 \begin{equation}
-\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
+\mcE[\rho]=\tr_{\text{E}} \left[ \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right) \rho \otimes \left(\projj{0}\right)^{\otimes M} \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right],
 \end{equation}
-where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits.
-Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
+where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be any.
 \begin{itemize}

### 2022-01-25 documentos/quantum_classical.tex
secc V

@@
 \label{quantum_classical}
-A Quantum-classical channels is defined using orthonormal basis in the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ an orthonormal basis in $\hilbert_{2^N}$
+A Quantum-classical (CQ) channel is defined  is defined using orthonormal basis in the Hilbert space.
+Let $B=\left\{ \ket{\psi_i} \right\}$ a orthonormal basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC associated to $B$ is
+\begin{equation}
+\mcE^{\text{QC}}_B[\rho]=\sum_{i=1}^{2^N} \bra{\psi_i}\rho \ket{\psi_i} \projj{\psi_i}.
+\end{equation}

### 2022-01-25 documentos/quantum_classical.tex
etc

--- 2022-01-20 documentos/quantum_classical.tex
@@
 \label{quantum_classical}
-A Quantum-classical channels is defined using orthonormal basis in the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ an orthonormal basis in $\hilbert_{2^N}$
+A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space.
+Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC associated to $B$ is
+\begin{equation}
+\mcE^{\text{QC}}_B[\rho]=\sum_{i=1}^{2^N} \bra{\psi_i}\rho \ket{\psi_i} \projj{\psi_i},
+\end{equation}
+this is, QC channels project density matrices onto the corresponding diagonal matrix in this basis~\cite{nathanson2007pauli}.
+
+Consider now that the basis $B$ is the common eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity in each set), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
+We will prove that the QCs defined in this way are \pce{} channels with $2^N$ on their diagonal.
+
+First we compute the components of $\mcE^{\text{QC}}_B$ in the basis $1/2^{N/1}\left\{\sigma_{\vec \alpha}\right\}$,
+\begin{equation}
+\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=\frac{1}{2^N}\sum_{i=1}^{2^N} \bra{\psi_i}\sigma_{\vec k} \ket{\psi_i}\bra{\psi_i}\sigma_{\vec l} \ket{\psi_i}.
+\end{equation}
+To evaluate it observe that $\bra{\psi_i}\sigma_{\vec k} \ket{\psi_i}^2=1 \ \ \forall \sigma_{\vec k}\in \text{set}(B)$, and from the formula for the purity of $\ket{\psi_i}$,
+\begin{equation}
+1=\frac{1}{2^N}\sum_{\vec k} \bra{\psi_i} \sigma_{\vec k} \ket{\psi_i}^2,
+\end{equation}
+it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there only positive terms in the sum, and $2^N$ of them are already equal to $1$.
+Therefore,
+\begin{align}
+\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}&=1,\nonumber\\ \left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l'}&=\left(\mcE^{\text{QC}}_B\right)_{\vec l' \vec l'}=0 \ \ \forall \sigma_{\vec k} \in \text{set}(B) \ \ \forall \sigma_{\vec l'} \not\in \text{set}(B).
+\end{align}
+To compute $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}$ for $\sigma_{\vec k}, \sigma_{\vec l} \in \text{set}(B)$ with $\vec k \neq \vec l$, observe that $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=\left(\mcE^{\text{QC}}_B\right)_{\vec l \vec k}$, \ie{} the matrix corresponding to $\mcE^{\text{QC}}$ is an orthogonal projector.
+Thus, consider the blocks,
+\begin{equation}
+\left[ \begin{array}{cc}
+\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k} & \left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l} \\ 
+\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l} & \left(\mcE^{\text{QC}}_B\right)_{\vec l \vec l}
+\end{array}  \right]=\left[ \begin{array}{cc}
+1 & \left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l} \\ 
+\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l} & 1
+\end{array}  \right],
+\end{equation}
+it is easy to check that the latter is a projector only if $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=0$. Since there are exactly $2^N$ elements

### 2022-01-25 documentos/kraus.tex
fixes

@@
 \section{Kraus operators and decoherence  propuesta: Physical implementations of PCE maps} % {{{
-\cpnote{HAcer esta seccion despues de que david ponga lo de decoherencia, 
-para servirla bien}
+% Intro {{{
+\cpnote{Crep qe hay que hacer una mini introduccion en donde se explique el porqué de
+esta seccion. Básicamente la idea es conectar estos bichos con procesos fisicos.
+Siento que la introduccion propuesta est´a un poco debil}
+
+% \cpnote{HAcer esta seccion despues de que david ponga lo de decoherencia, 
+% para servirla bien}
 % \todo{Carlos hace una version}
 
-{\red [texto viejo introductorio de la seccion] Furthermore, quantum channels enjoy the well-known \textit{Kraus
-representation} (or operator-sum representation) which reads 
+% {\red [texto viejo introductorio de la seccion] Furthermore, quantum channels enjoy the well-known \textit{Kraus
+% representation} (or operator-sum representation) which reads 
+% \begin{equation}
+% \mcE[\rho]=\sum_i K_i \rho
+% K_i^\dagger{},
+% \end{equation}
+% with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
+% 
+% The Kraus operators of PCE channels provide an insight in the physical processes
+% that yield such channels. In this section we investigate and construct such 
+% operators and explore the corresponding processes. To study the Kraus operators corresponding to PCE, it is enough to study 
+% the ones corresponding to generators, as all PCEs commute and thus to get the 
+% Kraus operators of an arbitrary PCE, one can easily combine the Kraus
+% operators of its generators. }
+
+Given that \pce{} channels are projections, we might ask whether they are fixed
+points of some memory-less (Markovian) process or not. In this section we prove
+that they are, and give two examples of Markovian implementations. The first
+one consist in identifying each \pce{} channel as a fixed point of some pure
+dissipative process. The second, in identifying each \pce{} channel as fixed
+points of some memory-less collision model.
+% }}}
+\subsection{Kraus representation} % {{{
+To derive the aforementioned implementations, we exploit the existence of the
+PCEGs and their \textit{Kraus representation} (or operator-sum representation)
+which, for an arbitrary channel $\mcE$,  reads 
 \begin{equation}
@@
 with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
-
-The Kraus operators of PCE channels provide an insight in the physical processes
-that yield such channels. In this section we investigate and construct such 
-operators and explore the corresponding processes. To study the Kraus operators corresponding to PCE, it is enough to study 
-the ones corresponding to generators, as all PCEs commute and thus to get the 
-Kraus operators of an arbitrary PCE, one can easily combine the Kraus
-operators of its generators. }
-
-{\blue [texto nuevo introductorio de la seccion]
-Given that \pce{} channels are projections, we might ask whether they are fixed points of some memory-less (Markovian) process or not.
-In this section we prove that they are, and give two examples of Markovian implementations.
-The first one consist in identifying each \pce{} channel as a fixed point of some pure dissipative process.
-The second, in identifying each \pce{} channel as fixed points of some memory-less collision model.
-
-\subsection{Kraus representation}
-To derive the aforementioned implementations, we exploit the existence of the PCEGs and their \textit{Kraus representation} (or operator-sum representation), which reads 
-\begin{equation}
-\mcE[\rho]=\sum_i K_i \rho
-K_i^\dagger{},
-\end{equation}
-with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
-}
-
 % The Kraus operators corresponding to one single qubit PCEs are 
@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators of two qubit PCEG lead to
+Inspection of the Kraus operators of two qubit PCEG leads to
 the ansatz that the Kraus operators for the generator of 
-$\mcG_{\vec \alpha}$ is 
+$\mcG_{\vec \alpha}$ are 
 \begin{equation}
-\left\{\frac{\openone}{\sqrt2}, \frac{\sigma_{\vec \alpha}}{\sqrt2}\right\}. 
-% \left\{\openone/\sqrt2, \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
+K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
+% \left\{\openone/\sqrt2, 
+% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
 \label{eq:kraus:PCE}
 \end{equation}
-Indeed, the Kraus operators corresponding to one single qubit PCEs are 
+since the Kraus operators corresponding to one single qubit PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
@@
 
-We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
+We shall first show that the aforementioned Kraus operators produce a PCE. 
 Notice that 
@@
 \end{equation}
-\cpnote{This is the original $a$, not $H \otimes H$. See how to relate these
-two matrices, or define a new $a$ and $A$} \ddnote{tengo entendido que nunca se define o redefine $a$ como $H \otimes H$, ni en el apendice, solo se dice que se intercambian para ciertos calculos.
-Creo que la notacion es segura.}
 % with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
@@
 \rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
-=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}
+=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}.
 \end{align}
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
-by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel\ddnote{agrego 'channel', aqui el PCE map si es por construccion un canal}. Moreover, One can notice that, 
+by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
 except for the first row, half of the matrix elements of each row is $+1$ and 
-half $-1$, which implies that the aforementioned channel is a PCEG.
+half $-1$, which implies that the channel is a PCEG.
 
@@
 Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
-leads to different channels. This can be seen noticing that if two channels were
+leads to different channels. This follows from the fact that if two channels were
 the same, this would imply that the matrix representation of the corresponding
-superoperator of $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$ \ddnote{en este punto me confundio bastante esta notacion, contrapropongo $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$, que es una notación que hemos venido usando.}
+superoperator of $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$
+% $\sigma_{\vec \alpha} \cdot \sigma_{\vec \alpha}$ 
+% \ddnote{en este punto me confundio bastante esta notacion, contrapropongo $\rho
+% \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$, que es una notación que
+% hemos venido usando.}
 would have to be the same which is clearly false. Since there are $4^n$ different 
@@
 
-\cpnote{We might have spoken about the notation of the generators and here we 
-can add a sentence about it, but I will wait till JA writes his part.}
+% \cpnote{We might have spoken about the notation of the generators and here we 
+% can add a sentence about it, but I will wait till JA writes his part.}
 % Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
@@
 % from other arguments. 
-\subsection{Pure dissipative implementation}
+% }}}
+\subsection{Pure dissipative implementation} % {{{
 Any PCE channel can be seen as the fixed point of some decoherence process.
@@
 
-\subsection{Collision model implementation}
+% }}}
+\subsection{Collision model implementation} % {{{
 PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}.
@@
 % }}}
+% }}}

### 2022-01-25 documentos/kraus.tex
Chuck Norris Emailed Me This Patch... I'm Not Going To Question It

@@
 \subsection{Pure dissipative implementation} % {{{
-Any PCE channel can be seen as the fixed point of some decoherence process.
-We will show this first for PCEGs.
-Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
+Any PCE channel can be seen as the fixed point of some decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos los canales son resultado de
+lindblad. Me gustaria modificar esta frase para que pueda ser apreciada mejor}. We
+will show this first for PCEGs. Consider the following dynamical process that
+\textit{implements} \cpnote{porque en italicas? Me cae gordo} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
 \begin{align}
@@
 \end{align}
-where $\gamma>0$.
-It is easy to show that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process, those are always characterized by some Lindblad generator~\cite{lindblad}.
-The Lindblad generator of $\mcG_{\vec \alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,
+where $\gamma>0$. It is easy to show that the family of channels $\mcG_{\vec
+\alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup,
+\ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha,
+t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
+time-homogeneous Markovian process, those are always characterized by some
+Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec
+\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard
+procedure,  
 \begin{equation}
@@
 \end{equation}
-where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.
-Notice that $\sigma_{\vec \alpha}$ is trace-less, therefore the process is pure dissipative~\cite{cirac}.
+where the unique Lindblad operator associated with the relaxation ratio
+$\gamma/2$ is simply $\sigma_{\vec \alpha}$. Notice that $\sigma_{\vec \alpha}$
+is trace-less, therefore the process is pure dissipative~\cite{cirac}.
 
-Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process.
-For them, the Lindblad generators are the sum of the Lindbladians of the corresponding generators.
-As an example, consider the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation process described with the following Lindbladian,
+Since PCEGs commute, we can describe easily any other PCE channel as a fixed
+point of a decoherence process. For them, the Lindblad generators are the sum
+of the Lindbladians of the corresponding generators. As an example, consider
+the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to
+$\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation
+process described with the following Lindbladian,
 \begin{equation}
-\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}+\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho \right)}{2},
+\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}
+   +\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho
+\right)}{2},
 \end{equation}
+\cpnote{Aca cambio la notacion, no se deberia poner L[rho] ?}
 where $\gamma_{(0,3)}$ and $\gamma_{(3,3)}$ are positive and correspond to the Lindblad operators $\sigma_{(0,3)}$ and $\sigma_{(3,3)}$.
@@
 \subsection{Collision model implementation} % {{{
-PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}.
-To prove this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla~\cite{Stinespring2006}.
-Since PCEG always have Kraus rank $2$, one can always choose a qubit as the ancillary system, concretely,
+We now show that PCE channels can also be described with \textit{simple
+collision models}~\cite{Ziman2010} \cpnote{can also be implemented can result 
+from collision models o ago asi. No cre oqeu uno describa un PCE con un modelo
+de colision}. First, observe that PCEGs can
+be implemented using an unitary over the system and an
+ancilla~\cite{Stinespring2006}\cpnote{No creo qeu la cita vaya acá}. Since PCEG
+always have Kraus rank $2$, one can
+always choose a qubit as the ancillary system. Concretely,
 \begin{equation}
-\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
+\mcG_{\vec \alpha}[\rho]=
+    \tr_{\text{qubit}} \left( 
+         U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} 
+     \right),
 \end{equation}
-where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as follows,
+where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
+the unitary defined as follows,
 \begin{align}
-U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
-U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
+U_{\vec\alpha}\ket{\psi} \ket{0}= \frac{1}{\sqrt{2}} 
+   \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
+U_{\vec\alpha}\ket{\psi} \ket{1}=\frac{1}{\sqrt{2}} 
+   \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
 \label{eq:Nqubit_stinespring}
 \end{align}
-Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed.
-In fact, generators are described with one collision.
-For the general case consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$.
-For this we can define an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$, or equivalently one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision (memory-less collisions).
-The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle.
-Therefore $\mcE$ can be written as follows,
+Therefore, any concatenation of PCEGs can be described as a collision model
+with as many collisions as generators needed. In fact, generators are described
+with one collision. For the general case consider some PCE channel $\mcE$
+generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots,
+\mcG_{\vec \alpha_M} \right\}$. For this we can define an environment
+consisting of $M$ qubits initially in the state $\left( \projj{0}
+\right)^{\otimes M}$, or equivalently one qubit with the additional assumption
+that its state is reset to $\ket{0}$ after each collision (memory-less
+collisions). The collision with the $k\text{th}$ particle is described by
+$U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$
+particle. Therefore $\mcE$ can be written as follows,
 \begin{equation}
@@
 where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be any.
-\begin{itemize}
-\item Relate to decoherence, for PCEG\ddnote{hecho}
-\item Play with non PCEG PCEs\ddnote{hecho}
-\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
-particular para todos los canales (sistema central + ambiente). Seria de buscar
-dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
-\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
-\end{itemize}
-
-\begin{equation}
-\mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
-\label{eq:Nqubit_semigroup}
-\end{equation}
+% \begin{itemize}
+% \item Relate to decoherence, for PCEG\ddnote{hecho}
+% \item Play with non PCEG PCEs\ddnote{hecho}
+% \item Dependiendo de si sale algo bonito, podemos poner algun modelo en
+% particular para todos los canales (sistema central + ambiente). Seria de buscar
+% dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
+% \todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
+% \end{itemize} 
+% 
+% \begin{equation}
+% \mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
+% \label{eq:Nqubit_semigroup}
+% \end{equation}
 

### 2022-01-26 documentos/generators.tex
etc

@@
 
+\ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya esta probado en la secc V}
 Given that both matrix $\san$ and PCE generators $\pceg$ have the same 

### 2022-01-26 documentos/kraus.tex
etc

@@
 will show this first for PCEGs. Consider the following dynamical process that
-\textit{implements} \cpnote{porque en italicas? Me cae gordo} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
+implements \cpnote{porque en italicas? Me cae gordo} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
 \begin{align}
@@
 \begin{equation}
-\mcL=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}
+\mcL[\rho]=\frac{\gamma_{(0,3)}\left(\sigma_{(0,3)}\rho\sigma_{(0,3)}-\rho \right)}{2}
    +\frac{\gamma_{(3,3)}\left(\sigma_{(3,3)}\rho\sigma_{(3,3)}-\rho
@@
 \subsection{Collision model implementation} % {{{
-We now show that PCE channels can also be described with \textit{simple
+We now show that PCE channels can also be implemented with \textit{simple
 collision models}~\cite{Ziman2010} \cpnote{can also be implemented can result 

### 2022-01-26 documentos/quantum_classical.tex
etc

@@
 \label{quantum_classical}
+\ddnote{Alguien revise este apendice, tiene solo una iterada}
 A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space.
@@
 \end{equation}
-this is, QC channels project density matrices onto the corresponding diagonal matrix in this basis~\cite{nathanson2007pauli}.
+this is, QC channels project density matrices onto the corresponding diagonal matrix in the basis $B$~\cite{nathanson2007pauli}.
 
-Consider now that the basis $B$ is the common eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity in each set), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
+Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
 We will prove that the QCs defined in this way are \pce{} channels with $2^N$ on their diagonal.
 
-First we compute the components of $\mcE^{\text{QC}}_B$ in the basis $1/2^{N/1}\left\{\sigma_{\vec \alpha}\right\}$,
+First we compute the components of $\mcE^{\text{QC}}_B$ in the basis $2^{-N/2}\left\{\sigma_{\vec \alpha}\right\}$,
 \begin{equation}
@@
 \end{equation}
-To evaluate it observe that $\bra{\psi_i}\sigma_{\vec k} \ket{\psi_i}^2=1 \ \ \forall \sigma_{\vec k}\in \text{set}(B)$, and from the formula for the purity of $\ket{\psi_i}$,
+To evaluate the components, observe that $\bra{\psi_i}\sigma_{\vec k} \ket{\psi_i}^2=1 \ \ \forall \sigma_{\vec k}\in \text{set}(B)$, and from the formula for the purity of $\ket{\psi_i}$,
 \begin{equation}
@@
 To compute $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}$ for $\sigma_{\vec k}, \sigma_{\vec l} \in \text{set}(B)$ with $\vec k \neq \vec l$, observe that $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=\left(\mcE^{\text{QC}}_B\right)_{\vec l \vec k}$, \ie{} the matrix corresponding to $\mcE^{\text{QC}}$ is an orthogonal projector.
-Thus, consider the blocks,
+Thus, consider the block,
 \begin{equation}
@@
 \end{equation}
-it is easy to check that the latter is a projector only if $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=0$. Since there are exactly $2^N$ elements
+it is easy to check that the latter is a projector only if $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=0$.
+Since there are exactly $2^N$ elements of the form $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}$ with $\sigma_{\vec k} \in \text{set}(B)$, the channel $\mcE^{\text{QC}}_B$ is \pce{} with $2^N$ $1$s on its diagonal.

### 2022-01-26 documentos/kraus.tex
etc

@@
 from collision models o ago asi. No cre oqeu uno describa un PCE con un modelo
-de colision}. First, observe that PCEGs can
+de colision}. To do this, observe that using the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
 be implemented using an unitary over the system and an

### 2022-01-26 documentos/math.tex
quito texto rojo
etc

@@
 
-{\red The same program can be carried out for $N$ qubits. In this case, 
+The same program can be carried out for $N$ qubits. In this case, 
 the vectorized Pauli operators are defined as follows, 
@@
 This vectorization must not be confused with the direct vectorization of $\sigma_{\vec \alpha}$, since the tensor product and the vectorization process generally do not commute~\cite{Gilchrist2009}.
-}
 % 
@@
 % kkkj
-and satisfy the orthogonality relation
+The vectors satisfy the orthogonality relation
 $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
@@
 to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
-$a^N$, which might be more convenient for other applications.
+$a^{\otimes N}$, which might be more convenient for other applications.
 % \janote{en una 

### 2022-01-26 documentos/kraus.tex
etc

--- 2022-01-26 documentos/kraus.tex
@@
 \subsection{Collision model implementation} % {{{
-We now show that PCE channels can also be implemented with \textit{simple
+We show now that PCE channels can also be implemented with \textit{simple
 collision models}~\cite{Ziman2010} \cpnote{can also be implemented can result 
 from collision models o ago asi. No cre oqeu uno describa un PCE con un modelo
-de colision}. First, observe that PCEGs can
+de colision}. To do this, observe that using the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
 be implemented using an unitary over the system and an
-ancilla~\cite{Stinespring2006}\cpnote{No creo qeu la cita vaya acá}. Since PCEG
+ancilla\cpnote{No creo qeu la cita vaya acá}. Since PCEG
 always have Kraus rank $2$, one can

### 2022-01-26 documentos/kraus.tex
etc

--- 2022-01-26 documentos/kraus.tex
@@
 will show this first for PCEGs. Consider the following dynamical process that
-implements \cpnote{porque en italicas? Me cae gordo} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
+implements the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
 \begin{align}
@@
 \end{equation}
-\cpnote{Aca cambio la notacion, no se deberia poner L[rho] ?}
 where $\gamma_{(0,3)}$ and $\gamma_{(3,3)}$ are positive and correspond to the Lindblad operators $\sigma_{(0,3)}$ and $\sigma_{(3,3)}$.
@@
 \subsection{Collision model implementation} % {{{
-We now show that PCE channels can also be implemented with \textit{simple
-collision models}~\cite{Ziman2010} \cpnote{can also be implemented can result 
-from collision models o ago asi. No cre oqeu uno describa un PCE con un modelo
-de colision}. First, observe that PCEGs can
+We show now that PCE channels can also be implemented with \textit{simple
+collision models}~\cite{Ziman2010}. To do this, observe that using the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
 be implemented using an unitary over the system and an
-ancilla~\cite{Stinespring2006}\cpnote{No creo qeu la cita vaya acá}. Since PCEG
+ancilla. Since PCEG
 always have Kraus rank $2$, one can

### 2022-01-27 documentos/pce.tex
Revisión de JA a la sec II

@@
 \section{PCE Maps} 
-To introduce the family of Pauli component erasing maps we start with 
-review basic concepts of quantum channels that will allow us to introduce some 
+To introduce the family of Pauli component erasing maps we start \sout{with 
+review}\janote{reviewing} basic concepts of quantum channels that will allow us to introduce some 
 notation. 
@@
 deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
-Often, this condition is easy to test.
+Often, this condition is easy to test.\janote{El comentario anterior se me hace de más}
 The
@@
 % \todo{David escribe una primera version y luego Carlos itera}
-
-We shall start exploring a single qubit scenario, where the most general 
+\janote{Siento que la subsección comienza de golpe con 'hablemos de los PCE 
+de 1 qubit' y hace falta una transición de lo de arriba a los PCE. Propongo lo siguiente:}
+\janote{Now that we have discussed the main features of quantum channels
+we are going to introduce the Pauli component erasing maps.}
+We shall start exploring \sout{a}\janote{the} single qubit scenario, where the most general 
 density matrix can be written as
@@
 that $\tau_0=1$). Not every
-such operation  is a quantum map; for example collapsing the entire Bloch
+such operation  is a quantum map; for example, collapsing the entire Bloch
 ball to the $xy$ plane (setting $\tau_{1,2}=1$ and  $\tau_3=0$) is not a quantum
@@
 total depolarization, respectively. In (e) we show a map that only erases the component
-$r_1$, collapsing the Block sphere into a disk, and thus does not correspond to a quantum operation.}
+$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.}
 	\label{fig:one:qubit:examples}
@@
 
-Similarly to the one qubit case, the density matrix $\rho$ of a system of $N$
+Similarly to the single qubit case, the density matrix $\rho$ of a system of $N$
 qubits can be written using Pauli strings in the following way, 

### 2022-01-27 documentos/pce.tex
Comentario a la caption de la Fig 1

@@
 \janote{Siento que la subsección comienza de golpe con 'hablemos de los PCE 
-de 1 qubit' y hace falta una transición de lo de arriba a los PCE. Propongo lo siguiente:}
+de 1 qubit' y hace falta una transición de lo de arriba a los PCE, además 
+de una frase que resuma de qué hablamos en II.B. Propongo 
+la siguiente reformulación:}
+
 \janote{Now that we have discussed the main features of quantum channels
 we are going to introduce the Pauli component erasing maps.}
-We shall start exploring \sout{a}\janote{the} single qubit scenario, where the most general 
-density matrix can be written as
+We shall start exploring \sout{a}\janote{the} single qubit scenario 
+\janote{to finish developing the $N$-qubit case}\sout{, where the most general 
+density matrix can be written as}\janote{The most general 
+single qubit density matrix can be written as}
 \begin{equation}
@@
 \end{center}
-	\caption{In (a) we introduce the positions of the single 
-qubit diagrams, so that each square corresponds to a single 
+	\caption{In (a) we introduce the positions of 
+\janote{\textbf{in}(?) the diagrams that picture the single qubit \pce{} maps}
+\sout{the single qubit diagrams}\janote{para que sea autocontenida la caption}, so that each square corresponds to a single 
 $\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 

### 2022-01-27 documentos/pce.tex
Comentarios de JA al II resueltos con CP

--- 2022-01-27 documentos/pce.tex
@@
 \section{PCE Maps} 
-To introduce the family of Pauli component erasing maps we start \sout{with 
-review}\janote{reviewing} basic concepts of quantum channels that will allow us to introduce some 
+To introduce the family of Pauli component erasing maps we start  
+reviewing basic concepts of quantum channels that will allow us to introduce some 
 notation. 
@@
 deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
-Often, this condition is easy to test.\janote{El comentario anterior se me hace de más}
+Often, this condition is easy to test.
 The
@@
 % \todo{David escribe una primera version y luego Carlos itera}
-\janote{Siento que la subsección comienza de golpe con 'hablemos de los PCE 
-de 1 qubit' y hace falta una transición de lo de arriba a los PCE. Propongo lo siguiente:}
-\janote{Now that we have discussed the main features of quantum channels
-we are going to introduce the Pauli component erasing maps.}
-We shall start exploring \sout{a}\janote{the} single qubit scenario, where the most general 
-density matrix can be written as
+\janote{Se añadió un primer párrafo para hacer una transición suave del A
+al B y decir qué discutimos aquí.}
+Now that we have discussed the main features of quantum channels
+we are going to introduce the Pauli component erasing maps.
+We shall start exploring the single qubit scenario 
+and continue with the $N$-qubit case.
+
+The most general single qubit density matrix can be written as
 \begin{equation}
@@
 \end{center}
-	\caption{In (a) we introduce the positions of the single 
-qubit diagrams, so that each square corresponds to a single 
+	\caption{\janote{Le modificamos la primera frase a esta caption para que la Fig sea
+	autocontenida}
+In (a) we introduce the notation
+in the diagrams that represent the single qubit \pce{} maps,
+so that each square corresponds to a single 
 $\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 

### 2022-01-27 documentos/generators.tex
It's 2016; why are we using ColdFusion?!
Insert Commit Message Here
remove certain things and added stuff

@@
 in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
-with $\vec\alpha$ each of the $4^{N}$ different vector indices. For a single qubit
-the PCE generators are the identity map plus the channels that map the Bloch 
-sphere to each Cartesian axis, as their associated vector subspaces are trivial
-to prove and their dimension $2(1)-1=1$ is met. 
-\janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
-\pce{} generators}
-Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ by the local action
-of the PCE generator on the $k$-th qubit. 
+with $\vec\alpha$ each of the $4^{N}$ different vector indices.
+\cpnote{
+The proof is simplified if one uses the Kraus representation developed in 
+\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
+For single qubits, the identity corresponds to $\mcG_0$, shown in 
+\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
+\fref{fig:one:qubit:examples}(c).
+}
 See, for example, that the 2-qubits PCE generator represented in subfigure (c)

### 2022-01-27 documentos/generators.tex
This commit is a lie

@@
 with $\vec\alpha$ each of the $4^{N}$ different vector indices.
-\cpnote{
+% \cpnote{
 The proof is simplified if one uses the Kraus representation developed in 
@@
 \fref{fig:one:qubit:examples}(c).
-}
-See, for example, that the 2-qubits PCE generator represented in subfigure (c)
+% }
+The 2-qubits PCE generator represented in subfigure (c)
 of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its

### 2022-01-27 documentos/generators.tex
Frase agregada al párrafo de relación alphas-PCEGs
Primera frase de párrafo relación alphas-PCEGs corregida de nuevo

@@
 PCE generators may be characterized by its local action on every qubit 
-in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
-with $\vec\alpha$ each of the $4^{N}$ different vector indices.
+in the system. This action can be encoded in the same vector index $\vec\alpha$
+introduced in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
+vector indices may be related uniquely to each of the PCE generators
+and thus denoted as $\mcG_{\vec\alpha}$.
 % \cpnote{

### 2022-01-27 documentos/generators.tex
Please no changes this time.

@@
 PCE generators may be characterized by its local action on every qubit 
-in the system. This action can be encoded in the same vector index $\vec\alpha$
-introduced in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
-vector indices may be related uniquely to each of the PCE generators
+in the system. This action can be encoded using a vector index $\vec\alpha$, 
+as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
+vector indices may be uniquely related to each of the PCE generators
 and thus denoted as $\mcG_{\vec\alpha}$.

### 2022-01-27 documentos/pce.tex
Títulos y referencias a secciones

@@
 \section{PCE Maps}
-To introduce the family of Pauli component erasing maps we start  
-reviewing basic concepts of quantum channels that will allow us to introduce some 
-notation. 
+\janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
+\janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
+To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
+maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
+channels that will allow us to introduce some notation. 
 % In this section we introduce the definition of Pauli component erasing maps,
 % but first we go through several standard definitions needed to discuss them.
-\subsection{Quantum channels} % {{{
+\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
 Quantum channels are the most general linear operations that a quantum

### 2022-02-01 documentos/intro.tex
etc
notas intro y mas etc

@@
 \section{Introduction} % {{{
+\ddnote{Generalization of the notion that squeezing the Bloch sphere into a disk is not a channel.
+Quantum channels have a astonishing number of parameters as the dimension grows, so studies like ours is important to understand less parametric families of quantum channels.
+}
 Several PRA articles go straight into matter. I guess we will write what we have to write
@@
 
+\ddnote{Yo agregare un parrafo delineando la literatura alrededor de Ruskai}
 Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}

### 2022-02-01 documentos/proofdiagonalization.tex
ALL SORTS OF THINGS
Saint Pipeline, please give me the green light
notas intro y mas etc

--- 2021-11-03 documentos/proofdiagonalization.tex
@@
 the sake of clarity, we will use Latin symbols for binary indices, and
-reserve the Greek ones for quaternary ones \afnote{(and
-reserve Greek letters for quaternary ones)}. 
+reserve Greek letters for quaternary ones. 
 We can write the elements of the Pauli basis
@@
 \end{equation}
-and its inverse relation,
+and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$},
 \begin{equation}
@@
       \left(\frac{1}{2}\sum_{l  m } 
-(-1)^{l  k+j m }\right) 
+(-1)^{j m + k l}
 \tau_{l  m } 
+\right) 
      \ddyad{\sigma_{jk}}{\sigma_{jk}}.
@@
 \end{align}
-\afnote{Creo que es mejor dejar el tau dentro del parentesis para dejar implícito que está sumando también.}
 Notice that  $\mathcal{D}$ is already written in its diagonal form, and one can 
@@
 % Then $\mathcal{D}$ is diagonal in the Pauli basis, with eigenvalues given by
-The eigenvalues read \
+The eigenvalues read 
 \begin{equation}
-\lambda_{jk}=\frac{1}{2}\sum_{l m } 
-(-1)^{jl +k m }
-\tau_{l m },
+\lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{j m + k l} \tau_{l m },
+% \lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{jl +k m } \tau_{l m },
 % \lambda_{mn}=\frac{1}{2}\sum_{\mu\nu} \tau_{\mu\nu} (-1)^{\mu m+n\nu},
@@
 instead of $H\otimes H$. This can be done due to the fact
-that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. In other words
-this operation corresponds to a relabeling in the eigenvalues $\lambda_{mn}$.
+that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. 
+In other words this operation corresponds to a reordering of the eigenvalues.
+
 % }}}
@@
 \end{equation}
-The generalization of \eref{CompToPau} and \eref{PauToComp} read \afnote{eq. $\to$ Eq.}
+The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
 \begin{align}
-\kket{\sigma_{\vec{\mu}\vec{\nu} }}  & = 
-   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{\mu}} \kket{\vec{j},\vec{j}\oplus \vec{\nu}},\\
+\kket{\sigma_{\vec{k}\vec{l} }}  & = 
+   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \kket{\vec{j},\vec{j}\oplus \vec{l}},\\
 %
@@
 \end{align}
-\afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}
+% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}
 
@@
 % \end{equation}
-Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
-\afnote{Creo que esta ultima linea se puede borrar.}
+% Thus the eigenvalues of the Choi matrix $\mathcal{D}_N$ may be written as
+% \afnote{Creo que esta ultima linea se puede borrar.}
 \begin{equation}
-\lambda_{\vec{j}\vec{n}}= \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} 
-    (-1)^{\vec{j}\cdot\vec{l}+\vec{k}\cdot\vec{m}}
+\lambda_{\vec{j}\vec{k}}= \frac{1}{2^{N}}\sum_{\vec{l}\vec{m}} 
+    (-1)^{\vec{j}\cdot\vec{m}+\vec{k}\cdot\vec{l}}
     \tau_{\vec{l}\vec{m}} 
+% \lambda_{jk}=\frac{1}{2}\sum_{l m } (-1)^{jl +k m } \tau_{l m },
 \end{equation}
-\afnote{Aqui los vectores $l$ y $m$ en el exponente estan cambiados}
 or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 

### 2022-02-08 documentos/math.tex
etc
cambios

@@
 % Intro {{{
-This section is devoted to derive the conditions a Pauli map needs to satisfy 
+This section is devoted to derive the conditions a Pauli diagonal map needs to satisfy 
 the complete positivity condition i.e. that all the eigenvalues of the Choi matrix
 associated to the channel are non-negative.  To do so, we calculate
-and diagonalize the Choi matrix associated with general Pauli maps, first for a
+and diagonalize the Choi matrix associated with general Pauli diagonal maps, first for a
 single qubit and then for $N$ qubits. We then restrict to PCEs and, for quantum
@@
 $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}. This allows us to
-derive several important conclusions. 
+derive several important \janote{properties of this particular family of channels.}
+\sout{conclusions. }
 % }}}
@@
 % vectorized 
-elements of the Pauli basis and satisfy the relation 
+elements of the Pauli basis satisfy the relation 
 $\bbrakket{{\sigma_{\alpha}} }{{\sigma_{\alpha'} }} = \tr

### 2022-02-08 documentos/kraus.tex
It's 2016; why are we using ColdFusion?!

@@
 \section{Kraus operators and decoherence  propuesta: Physical implementations of PCE maps} % {{{
+\label{sec:kraus}
 % Intro {{{
+
+\cpnote{Contrapropuesta: PCE channels and decoherence}
+
 \cpnote{Crep qe hay que hacer una mini introduccion en donde se explique el porqué de
@@
 
-Given that \pce{} channels are projections, we might ask whether they are fixed
+{\red [anterior]Given that \pce{} channels are projections, we might ask whether they are fixed
 points of some memory-less (Markovian) process or not. In this section we prove
@@
 dissipative process. The second, in identifying each \pce{} channel as fixed
+points of some memory-less collision model.}
+{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation,
+\begin{multline}
+\dot \rho(t)=-i [H(t),\rho(t)]+\\
+\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right)
+\end{multline}
+ \pce{} channels erase information
+The first
+one consist in identifying each \pce{} channel as a fixed point of some pure
+dissipative process. The second, in identifying each \pce{} channel as fixed
 points of some memory-less collision model.
+}
 % }}}

### 2022-02-09 documentos/math.tex
Vectorized Pauli strings!

@@
 $\hilbert={\mathbb{C}^2}$. Since the scalar product on $\mcB(\hilbert)$ is
-given by  $\bbrakket{A_1}{A_2}=\tr A_1^\star A_2$,
+given by  $\bbrakket{A_1}{A_2}=\tr A_1^\dagger{} A_2$,
 % We now study the matrix form of the single qubit map $\mathcal{E}$ in
@@
 the vectorized Pauli operators are defined as follows, 
-\begin{equation}
-\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
-\otimes\kket{\sigma_{\alpha_N}}.
+\begin{equation}\label{eq:vectorized_pauli_strings}
+\kket{\sigma_{\vec{\alpha} }}=
+\kket{\sigma_{\alpha_1}\otimes\cdots\otimes \sigma_{\alpha_N}}.
+%\kket{\sigma_{\alpha_1}}\otimes\cdots\otimes\kket{\sigma_{\alpha_N}}.
 \end{equation}
+\janote{Ojo que cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
+modifica el comentario de la frase que le sigue a este comentario. Luego lo cambio yo}
 This vectorization must not be confused with the direct vectorization of $\sigma_{\vec \alpha}$, since the tensor product and the vectorization process generally do not commute~\cite{Gilchrist2009}.

### 2022-02-10 documentos/math.tex
Hechos mis comentarios a III

@@
 associated to the channel are non-negative.  To do so, we calculate
-and diagonalize the Choi matrix associated with general Pauli diagonal maps, first for a
-single qubit and then for $N$ qubits. We then restrict to PCEs and, for quantum
+and diagonalize the Choi matrix of a general Pauli diagonal map, first for a
+single qubit and then for $N$ qubits. 
+\janote{Finally, we restrict Pauli diagonal maps to PCE maps, and provide a connection
+between a vector subspace to the set of coefficients $\{\tau_\valpha\}$ 
+in \eref{eq:PCE_definition} of a PCE quantum channel.}
+{\red [anterior]
+We then restrict to PCEs and, for quantum
 channels, associate a vector subspace to the set of coefficients
-$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}. This allows us to
-derive several important \janote{properties of this particular family of channels.}
-\sout{conclusions. }
+$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}.} 
+This allows us to
+derive several important properties of this particular family of channels.
+%\sout{conclusions. }
 % }}}
 \subsection{Diagonalization of Choi matrix} % {{{
-
-We now construct the Choi matrix associated to the single qubit map
+We now construct the Choi matrix of a single qubit Pauli diagonal map
+%We now construct the Choi matrix associated to the single qubit map
 $\mathcal{E}$. As described above, $\mathcal{E}$ is a linear map from
@@
 as a vector belonging to $\mcB(\hilbert)$, for the present case, in which
-$\hilbert={\mathbb{C}^2}$. Since the scalar product on $\mcB(\hilbert)$ is
+$\hilbert={\mathbb{C}^2}$. Since the scalar product in $\mcB(\hilbert)$ is
 given by  $\bbrakket{A_1}{A_2}=\tr A_1^\dagger{} A_2$,
@@
 \delta_{\alpha\alpha'}$.
-In this language, the state reads
+In this language, the state of a single qubit reads
 $\kket{\rho}=2^{-1}\sum_{\alpha=0}^{3} r_{\alpha} \kket{\sigma_{\alpha}}$
@@
 After some steps, detailed from \eref{eq:inicio:canal:pauli} to
-\eref{Choi_Pauli_1q}, it is possible to show that the associated Choi matrix
+\eref{Choi_Pauli_1q}, it is possible to show that the Choi matrix of $\mathcal{E}$
 reads
@@
 We wish to add that one can replace $a$ with $H \otimes H$, with $H$ the
-Hadamard matrix, and still diagonalize the same Choi matrix. This is due to the
+Hadamard matrix, and still diagonalize the same Choi matrix $\mathcal{D}$. This is due to the
 fact that $a$ corresponds to a permutation of rows of  $H \otimes H$. However,
 we chose the aforementioned definition as some later considerations [see
-\eref{eq:sigma_property}] cannot be written easily in terms of $H \otimes H$.
+\eref{eq:sigma_property}] cannot be easily written in terms of $H \otimes H$.
 
@@
 The same program can be carried out for $N$ qubits. In this case, 
-the vectorized Pauli operators are defined as follows, 
+%the vectorized Pauli operators are defined as follows, 
+one uses the vectorized Pauli strings, 
 \begin{equation}\label{eq:vectorized_pauli_strings}
@@
 \end{equation}
-\janote{Ojo que cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
-modifica el comentario de la frase que le sigue a este comentario. Luego lo cambio yo}
-This vectorization must not be confused with the direct vectorization of $\sigma_{\vec \alpha}$, since the tensor product and the vectorization process generally do not commute~\cite{Gilchrist2009}.
+\janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
+modificó la frase que le sigue a este comentario.}
+This vectorization must not be confused with the 
+%direct vectorization of $\sigma_{\vec \alpha}$
+tensor product of  all $\kket{\sigma_{\alpha_i}}$, 
+since the tensor product and the vectorization 
+process generally do not commute~\cite{Gilchrist2009}.
 % 

### 2022-02-10 documentos/vector_space.tex
This commit is a lie
Hechos mis comentarios a III

@@
-\subsection{PCE channels as vector spaces} % {{{
+\subsection{PCE quantum channels as vector spaces} % {{{
 \cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
@@
 us to draw conclusions for PCE quantum channels.}
+\janote{Prefiero esta frase:}
+\janote{Some established facts about vector spaces will allow
+us to derive the main features of PCE quantum channels.}
 
 Let us start by recalling that the problem of determining complete positivity
-of a PCE can be recast as determining which vectors $\vtau$ are mapped via
+of a PCE map can be recast as determining which vectors $\vtau$ are mapped via
 $\san$
@@
 This is a remarkable equation, as it provides a method to diagonalize the
-Choi matrix of any 
-Pauli diagonal operation.
+Choi matrix of any Pauli diagonal map.
 
-Other two simple but crucial
-observation are the following. For valid quantum channels, 
+Other two simple but crucial observations are the following. 
+For valid quantum channels it holds 
 % \begin{equation}
@@
 for an arbitrary subset of multi-indices $\Omega$, 
-as each member of the sum is
-greater or equal to zero, 
+as each member of the sum is greater than or equal to zero, 
 due to complete positivity of the underlying channel. 
@@
 }. 
-We can indeed restate \eref{eq:oplus}, and say that for valid quantum channels, 
+We can indeed restate \eref{eq:oplus}, and say that for quantum channels, 
 if $\tau_{\vec\alpha}=1$, then
@@
 $\valpha^{(4)} = (3,2)$. However, 
-$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved and thus this 
+$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved, and thus this 
 diagram does not correspond to a quantum channel.  From this view 
@@
 inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
-whenever the $\vec\gamma$ belong to a given vector subspace of the set of
+whenever the $\vec\gamma$ belongs to a given vector subspace of the set of
 all indices, then the vector $\vec\tau$ indeed has an image
@@
 with only positive components. 
-In other words, there is a one to one correspondence between 
-a valid quantum channel, and a vector subspace of the aforementioned space. 
+In other words, there is a one-to-one correspondence between 
+a quantum channel, and a vector subspace of the aforementioned space. 
 % \cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
@@
 from the solution having $\tau_{\vec0}=1$, with everything else $0$. We may
-then successively switch $\tau$'s to $1$ for various values of $\valpha$,
-taking care immediately to set equal to one the components of $\tau$ that
+then successively switch $\tau_{\vec\alpha}$'s
+\janote{agregué el subíndice $\vec\alpha$} 
+to $1$ for various values of $\valpha$,
+taking care immediately to set equal to one the components of $\vec\tau$
+\janote{puse la $\tau$ como vector}
+that
 correspond to values of $\vbeta$ generated by the previously switched values of
@@
 to generate
-all valid quantum channels with a given set of preserved components, without the need
-of exploring the exponentially large space of PCE.  \par 
+all PCE quantum channels with a given set of preserved components, without the need
+of exploring the exponentially large space of all PCE maps.  \par 
 % }}}}
@@
 in (b) a PCE channel that preserves four components.  (c), (d)
-and (e) show three generators; the combination of any two of them
+and (e) show three generators \cpnote{Quizá poner los nombres de los generadores acá}; the combination of any two of them
 yields the channel in (b). (f) represents the identity map. 
@@
 % Cuantos canales conservan $2^K$ componentes? {{{
-It is natural to ask how many PCEs exist that conserve $2^K$ components. One
+It is natural to ask how many PCE quantum channels exist that preserve $2^K$ components. One
 can calculate such number, $\sss_{N,K}$, by examining the number of different

### 2022-02-10 documentos/proofdiagonalization.tex
Comentarios apéndice Alejo y otra cosa chiquita

@@
 $\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j\oplus l }$. In vectorized form
-\begin{equation}
-\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },
+\begin{align}
+\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },\\
+\janote{
+\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\ket{j,j+l} \text{ (mod 2)},
+}
 \label{CompToPau}
-\end{equation}
-and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$},
+\end{align}
+and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$}
+\janote{yo creo que es mejor dejar el $\oplus$ para la suma de Francois y usar otro símbolo para suma módulo 2. Además, creo que es mejor escribir $\ket{j,j+l´} \text{ (mod 2)}$ 
+para que sea claro que esos son vectores canónicos (son los canónicos, verdad?)},
 \begin{equation}

### 2022-02-14 documentos/generators.tex
anotaciones
Fix all errors, all errors on the WORLD!!!!

@@
 \sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
-For single qubits, the identity corresponds to $\mcG_0$, shown in 
+\janote{referir a fig 5} For single qubits, the identity corresponds to $\mcG_0$, shown in 
 \fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
@@
 \begin{align}
-\alpha_{0}\mapsto\alpha_3,\quad\alpha_{3}\mapsto\alpha_0,
-\quad\alpha_1\mapsto\alpha_2, \quad\alpha_2\mapsto\alpha_1.
+\Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
 \end{align}
+Indeed, any generator is a subspace containing half the elements of the full vector space.  
+The map $\Sigma$ has the following properties
+\begin{enumerate}
+\item $\Sigma(\vec\alpha)+\Sigma(\vec\beta)=\vec\alpha+\vec\beta$.
+\item $\Sigma(\vec\alpha)\neq\vec\alpha$
+\end{enumerate}
+From the first property, we now obtain
+\begin{equation}
+\vec\alpha=\Sigma(\vec\alpha)+\Sigma(\vec0)
+\end{equation}
+We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
+$\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.
+
 \janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}

### 2022-02-14 documentos/kraus.tex
I just evaluated random code in my console
avanzando a Kraus y typos en mi apendice

@@
 Siento que la introduccion propuesta est´a un poco debil}
+\ddnote{hecha miniintroduccion, es basicamente la misma idea, pero con detalles y justificaciones matematicas}
 
@@
 points of some memory-less collision model.}
-{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation,
+{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation~\cite{lindblad,kossa,kossa2,Gorini1976},
 \begin{multline}
 \dot \rho(t)=-i [H(t),\rho(t)]+\\
-\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right)
+\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right),
 \end{multline}
+where the first part is the so-called Hamiltonian term, the second the dissipative term with $\gamma_k(t)\geq 0$ the relaxation ratios associated with the Lindblad operators $V_k(t)$.
+%
+In the particular case where the Hamiltonian, relaxation rations and Lindblad operators are independent of time, we recover the well-known Lindblad master equations~\cite{lindblad}.
+Such equations model time-homogeneous processes, implying one-parameter semigroup structures that will be exploited later.
+%
+Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$.
+Furthermore, channels belonging to one-parameter semigroup families usually have non-negative eigenvalues~\cite{davalosdivisibility}
+%
+Thus we might ask whether 
  \pce{} channels erase information

### 2022-02-14 documentos/quantum_classical.tex
avanzando a Kraus y typos en mi apendice

@@
 A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space.
-Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC associated to $B$ is
+Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC channel associated to $B$ is
 \begin{equation}
@@
 Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
-We will prove that the QCs defined in this way are \pce{} channels with $2^N$ on their diagonal.
+We will prove that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
 

### 2022-02-14 documentos/generators.tex

@@
 
+\cpnote{Notas, no entiendo que es 3+3. Ceo qe no es suma de Klein tampoco 
+por un aparente contraejemeplo: 
+$3=\Sigma(0) = \Sigma(0+0) = \Sigma(0)+\Sigma(0) = 3+3 = ??$}
+\cpnote{Este es un mapeo que depende de $k$, por lo que propondria ponerle
+o un subindice o un superindice $(k)$. }
+\cpnote{La simetría clasifica también al generador!! Quizá podemos quitar el miniapendice
+que había escrito}
 A reflection symmetry is identified for both PCE generators $\pceg$ and
@@
 The symmetry for a PCE generator $\pceg$ is encoded in the 
-$N$-dimensional array of all $\taus$, the Cartesian grid associated with it 
+$N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
 is either symmetric or anti-symmetric under reflection of the 
 indices in the $k$-th position in $\vec\alpha$ as
-\begin{align}
+\begin{equation}
 \Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
-\end{align}
+\end{equation}
 Indeed, any generator is a subspace containing half the elements of the full vector space.  

### 2022-02-14 documentos/generators.tex
Moved something to somewhere... goodnight...

@@
 
-\cpnote{Notas, no entiendo que es 3+3. Ceo qe no es suma de Klein tampoco 
-por un aparente contraejemeplo: 
-$3=\Sigma(0) = \Sigma(0+0) = \Sigma(0)+\Sigma(0) = 3+3 = ??$}
 \cpnote{Este es un mapeo que depende de $k$, por lo que propondria ponerle
@@
 is either symmetric or anti-symmetric under reflection of the 
-indices in the $k$-th position in $\vec\alpha$ as
+indices in the $k$-th position in $\vec\alpha$. Consider the map
 \begin{equation}
-\Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
+% \Sigma: 
+0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
+\label{eq:Sigma}
 \end{equation}
 Indeed, any generator is a subspace containing half the elements of the full vector space.  
-The map $\Sigma$ has the following properties
+Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
 \begin{enumerate}
-\item $\Sigma(\vec\alpha)+\Sigma(\vec\beta)=\vec\alpha+\vec\beta$.
+\item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
 \item $\Sigma(\vec\alpha)\neq\vec\alpha$
@@
 \begin{equation}
-\vec\alpha=\Sigma(\vec\alpha)+\Sigma(\vec0)
+\vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
 \end{equation}

### 2022-02-15 documentos/kraus.tex
intro a secction de implementaciones y etc

@@
 %
-Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$.
-Furthermore, channels belonging to one-parameter semigroup families usually have non-negative eigenvalues~\cite{davalosdivisibility}
+Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
+Therefore, we might ask whether \pce{} channels can be seen as limit points of some Markovian processes.
+In this section we prove what in fact they are, and give two examples of Markovian implementations.
 %
-Thus we might ask whether 
- \pce{} channels erase information
 The first
@@
 \subsection{Pure dissipative implementation} % {{{
-Any PCE channel can be seen as the fixed point of some decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos los canales son resultado de
-lindblad. Me gustaria modificar esta frase para que pueda ser apreciada mejor}. We
+{\red [viejo] Any PCE channel can be seen as the fixed point of some decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos los canales son resultado de
+lindblad.}
+{\blue [nuevo] In this section we show that any PCE channel can be seen as the fixed point of some decoherence process, this is a property that is not accomplished by any channel, as mentioned above.} Me gustaria modificar esta frase para que pueda ser apreciada mejor} \ddnote{la modificacion fue leve debido a que la mayor parte del contenido esta en la introduccion de la seccion}.
+We
 will show this first for PCEGs. Consider the following dynamical process that
@@
     \tr_{\text{qubit}} \left( 
-         U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} 
+         U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U_{\vec \alpha}^\dagger{} 
      \right),

### 2022-02-15 documentos/pce.tex

@@
 channels that will allow us to introduce some notation.
+
+\afnote{Propongo que cambiemos el inicio de esta sección por: This section is devoted to introduce the family of Pauli component erasing maps.
+Let us start our discussion with a brief review of several basic concepts of quantum channels that will allow us to introduce some notation.}
 % In this section we introduce the definition of Pauli component erasing maps,
@@
 \subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
-Quantum channels are the most general linear operations that a quantum
-system undergo independently of its past~\cite{zimansbook,cirac}.
-The physical system under study will be associated with a Hilbert space
-denoted by \hilbert{}, and the set of linear operators over such space will 
-be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
- is an element of $\mcB(\hilbert)$.
-
+\afnote{Creo que podríamos empezar la sección introduciendo el espacio de Hilbert y esas cosas y después si dedicarse solamente a Quantum channels.
+Si están de acuerdo, entonces sólo tendriamos que cambiar el orden de las dos primeras frases en el primer párrafo.}
+Quantum channels are the most general linear operations that a quantum system undergo independently of its past~\cite{zimansbook,cirac}.
+The physical system under study will be associated with a Hilbert space denoted by \hilbert{}, and the set of linear operators over such space will be denoted by $\mcB(\hilbert)$.
+That way, a density matrix $\rho$ of such system is an element of $\mcB(\hilbert)$.
+\afnote{En esta última parte podriamos cambiar asi:}
+\afnote{The state of the physical system under study is associated to a Hilbert space \hilbert{}, and the set of linear operators over such space is denoted by $\mcB(\hilbert)$.
+In this way, a density matrix $\rho$ of such system is an element of $\mcB(\hilbert)$.}
 % Quantum channels comprehend the most general linear operations that a quantum
@@
 deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
-Often, this condition is easy to test.
+Often, this condition is easy to test \afnote{Podríamos decir que tanto linealidad como preservación de la traza son faciles de checar.}.
 The
@@
 positivity condition is needed to preserve positive semidefiniteness and handle
-the non-local feature of quantum theory. 
+the non-local feature of quantum theory \afnote{(... the non-local nature of QT.)}. 
 A linear map $\mcE$ is positive if it maps density operators to density operators, \ie{}
@@
 On the other hand, if one extends a positive map to include an ancilla, the resulting
-map is not always positive. If, for all dimensions of the ancilla, such extension
+map is not always positive. If, for all dimensions of the ancilla \afnote{(for any ancillary system of arbitrary dimension)}, such extension
 results in a positive map, we say that the original map is completely
@@
 Quantum channels are required to be completely positive
-so as to allow the proper evolution of potentially entangled states with an 
-ancilla. 
+so as to allow the proper evolution of potentially entangled states with an ancilla.
+\afnote{Sería bueno mencionar también que la tarea de determinar la CP de un mapa es no trivial, lo que sirviría también como conector o preambulo del siguiente párrafo.}
 % In the other hand, a map is completely positive if extending the 
@@
 is positive-semidefinite~\cite{jamil,choi}. 
-
+\afnote{No sé si es algo obvio, pero creo que seria bueno comentar que es el objeto $\id$.}
 %  the
@@
 %   \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
+\afnote{Creo que el párrafo conector que ha introducido JA queda mejor antes del título de la siguiente subsección, es decir:}
 
+\afnote{We have discussed the main features associated to quantum channels, now we turn our attention to introduce the Pauli component erasing maps.
+We start by exploring the single qubit scenario and then we treat the $N$-qubit case.}
 % }}}
@@
 \end{equation}
+\afnote{Creo que este párrafo queda mejor así: where $\{\sigma_{0},\sigma_{1},\sigma_{2},\sigma_{3}\}=\{\one,\sigma_{x},\sigma_{y},\sigma_{z}\}$, with $\one$ the $2\times 2$ identity matrix and $\sigma_{j}$ the usual Pauli matrices.
+Note that normalization requires that $r_0=1$.
+On the other hand, the remaining $r_{j}$ coefficients constitute the so called Bloch vector $\vec{r}=(r_{x},r_{y},r_{z})$.
+Consider the map that projects each component in the following way:}
+% 
 with $\sigma_0= \one$, and $\sigma_{1,2,3}$ the usual Pauli matrices.  
 Normalization requires that $r_0=1$ and the remaining $r_{1,2,3}$ 
-form the Bloch vector. Consider the map that projects
+form the Bloch vector. 
+Consider the map that projects
 each component 
 in the following way,
+% 
 \begin{equation}
 r_\alpha \mapsto \tau_\alpha r_\alpha
+\label{EqPCE}
 \end{equation}
-where $\tau_\alpha$ is either $1$ or $0$ (trace preserving requires
-that $\tau_0=1$). Not every
-such operation  is a quantum map; for example, collapsing the entire Bloch
-ball to the $xy$ plane (setting $\tau_{1,2}=1$ and  $\tau_3=0$) is not a quantum
-channel. A direct evaluation of the complete positivity
-conditions~\cite{zimansbook,davalosdivisibility}, 
+where $\tau_\alpha$ is either $0$ or $1$ (trace preserving requires
+that $\tau_0=1$ \afnote{Esto ya fue dicho y creo que sobra aquí.}).
+\afnote{From now on we refer to any operation like that described in Eq.
+\ref{EqPCE}, as single qubit \textit{Pauli Component Erasing} (\pce{}) maps}.
+\afnote{It is worth to mention that not all PCE operations correspond to a quantum channel; for example...} Not every
+such operation  is a quantum map; for example, collapsing the entire Bloch ball to \afnote{a disk on} the $xy$ plane ($\tau_{1}=\tau_{2}=1$ and  $\tau_3=0$) is not a quantum channel \afnote{(Aquí podemos colocar en vez de ``is not a quantum channel'', ``leads to a violation of the CP conditions, indeed a direct evaluation \cite{zimansbook,davalosdivisibility}'')}.
+A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
 \begin{align}
 1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
-1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall \alpha\neq \beta \neq \gamma,
+1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall ~\alpha\neq \beta \neq \gamma,
 \end{align}
@@
 total depolarization, respectively. In (e) we show a map that only erases the component
-$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.}
+$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.\afnote{Propongo el siguiente caption: (a) Pictorial representation of a single qubit \pce{} map.
+The color of each square indicates the value attained by the corresponding $\tau_{\alpha}$, either 0 (white) or 1 (black).
+The diagrams in (b), (c) and (d) correspond to the identity map, dephasing channel, and total depolarization, respectively.
+In (e) we show a map that only erases the component $r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.}}
 	\label{fig:one:qubit:examples}
@@
 \sigma_{\vec \alpha} \right)$ is the coefficient corresponding to the expansion
-of the density matrix in the normalized basis of Pauli strings. Again,
-normalization of the state requires that $r_{\vec 0}=1$.
+of the density matrix in the normalized basis of Pauli strings \afnote{Me parece que no hay necesidad de colocar el ``normalized''}.  Again, normalization of the state requires that $r_{\vec 0}=1$.
 We shall refer to $\paulicomponents$ as the {\it Pauli components} of the density
@@
 
-A Pauli component erasing (PCE) map is a map
+\afnote{Thus in general,} a Pauli component erasing (PCE) map is a map
 %  Pauli diagonal operation
@@
 \end{equation}
-For the operation to be trace preserving, it is required that $\tau_{\vec
+\afnote{In addition,} for the operation to be trace preserving, it is required that $\tau_{\vec
 0}=1$. 
@@
 evaluating the conditions for complete positivity is involved and is the main
-problem addressed in this paper. 
+problem addressed in this paper \afnote{Propongo cambiar el ``involved'' por un sinónimo}. 
 We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
@@
 % but allow the 
-$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.
+$\taus$ (only restricted by complete positivity \afnote{También dejamos libre la condicion de preservación de la traza?}) as {\it Pauli diagonal operations}.
 
@@
 for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
+\afnote{Propongo cambiar esta ultima parte asi: Examples for $N=1$ and $N=2$ are provided in \fref{fig:one:qubit:examples} and \fref{fig:two:qubit:examples}, respectively.}
 
@@
 commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
-2^N $ components equal to $1$s in its diagonal, see appendix~\sref{quantum_classical}.
+2^N $ components equal to $1$s in its diagonal \afnote{Aquí me parece que falta información.
+Creo que hay que decir que es lo que es diagonal y en que base}.
+\afnote{For details, we refer the reader to} appendix~\sref{quantum_classical}.
 

### 2022-02-15 documentos/kraus.tex
etc

@@
 points of some memory-less collision model.}
-{\blue [nuevo, sigo trabajando] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation~\cite{lindblad,kossa,kossa2,Gorini1976},
+{\blue [nuevo] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation~\cite{lindblad,kossa,kossa2,Gorini1976},
 \begin{multline}

### 2022-02-15 documentos/intro.tex
salvaguardando intro

@@
 These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
+\newline
+{\blue [Aqui arranco con la introduccion]\\}
+Similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
+For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real numbers which are not fully independent (the complete positivity condition imposes which regions have physical meaning, see Ref.~\cite{zimansbook}).
+Therefore, even the qubit case is difficult to explore, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
+Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
+For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters~\cite{Rybar2012,ruskai,davalosdivisibility}
 % }}}

### 2022-02-16 documentos/intro.tex
salvaguardando

@@
 Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters~\cite{Rybar2012,ruskai,davalosdivisibility}
+For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters~\cite{Rybar2012,ruskai,davalosdivisibility}.
+For general finite-dimensional channels families of channels based on [...]~\cite{nathanson2007pauli} based on MUBs...
+Based on mutually unbiased measurements~\cite{Siudzinska2020}
 % }}}

### 2022-02-17 documentos/generators.tex
You should have trusted me.

--- 2022-02-14 documentos/generators.tex
@@
 A reflection symmetry is identified for both PCE generators $\pceg$ and
-the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
-The symmetry for a PCE generator $\pceg$ is encoded in the 
-$N$-dimensional array of all $\taus$, the Cartesian grid associated with it 
-is either symmetric or anti-symmetric under reflection of the 
-indices in the $k$-th position in $\vec\alpha$ as
-\begin{align}
-\Sigma: 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
-\end{align}
-Indeed, any generator is a subspace containing half the elements of the full vector space.  
-The map $\Sigma$ has the following properties
+the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map\cpnote{Creo que aun 
+no tenemos el link entre el generador y la matriz A}.
+Consider the map $\Sigma^{(k)}$ that reflects an index $\valpha$ with 
+respect to the $k$-th axis. This map leaves all components of $\valpha$
+invariant, except the $k$-th component, which is transformed according to 
+\begin{equation}
+% \Sigma: 
+0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1. 
+\label{eq:Sigma}
+\end{equation}
+% and the associated 
+All $N$ maps have the following properties:
 \begin{enumerate}
-\item $\Sigma(\vec\alpha)+\Sigma(\vec\beta)=\vec\alpha+\vec\beta$.
-\item $\Sigma(\vec\alpha)\neq\vec\alpha$
+\item $\Sigma^{(k)}(\vec\alpha)\oplus \Sigma^{(k)}(\vec\beta)=\vec\alpha\oplus \vec\beta$.
+\item $\Sigma^{(k)}(\vec\alpha)\neq\vec\alpha$.
 \end{enumerate}
@@
 \begin{equation}
-\vec\alpha=\Sigma(\vec\alpha)+\Sigma(\vec0)
+\valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0), 
+\label{eq:Sigma}
 \end{equation}
-We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
-$\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.
+which means that if $\Sigma^{(k)}(\vec0)$ belongs
+to a channel then 
+$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}$, where we used 
+the fact that for channels, the non-zero elements are closed
+under $\oplus$. In other words, the components of a PCE channel
+are symmetric under reflection over the $k$-th axis. \cpnote{Quizá 
+referencia a algunas figuras}. Now consider the case in which 
+ $\Sigma^{(k)}(\vec0)$ does not belong to generator. Then 
+$\tau_\valpha \ne \tau_{\Sigma^{(k)}(\vec\alpha)}$, since
+the case $\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=1$
+is forbidden due to \eref{eq:Sigma} and the case 
+$\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=0$ is also forbidden 
+because for generators, the codimension of the associated vector space 
+is 1.
+
+% 
+% 
+% The symmetry for a PCE generator $\pceg$ is encoded in the 
+% $N$-dimensional array of all $\taus$. The Cartesian grid associated with it 
+% is either symmetric or anti-symmetric under reflection of the 
+% indices in the $k$-th position in $\vec\alpha$. 
+% Consider the map
+% \begin{equation}
+% % \Sigma: 
+% 0\mapsto3,\quad3\mapsto0,\quad1\mapsto2,\quad2\mapsto1
+% \label{eq:Sigma}
+% \end{equation}
+% Indeed, any generator is a subspace containing half the elements of the full vector space.  
+% Map \eref{eq:Sigma} applied to the $k$-th qubit has the following properties
+% \begin{enumerate}
+% \item $\Sigma(\vec\alpha)\oplus \Sigma(\vec\beta)=\vec\alpha\oplus \vec\beta$.
+% \item $\Sigma(\vec\alpha)\neq\vec\alpha$
+% \end{enumerate}
+% From the first property, we now obtain
+% \begin{equation}
+% \vec\alpha=\Sigma(\vec\alpha) \oplus \Sigma(\vec0)
+% \end{equation}
+% We now see that, depending on whether $\Sigma(\vec0)$ belongs (respectively does not belong) to the generator,
+% $\vec\alpha$ belongs to the generator if and only if $\Sigma(\vec\alpha)$ belongs (respectively does not belong) to the generator.  
+%
 

### 2022-02-17 documentos/generators.tex
WHO THE FUCK CAME UP WITH MAKE?

@@
 A reflection symmetry is identified for both PCE generators $\pceg$ and
-the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map\cpnote{Creo que aun 
+matrix $A$ \cpnote{Creo que aun 
 no tenemos el link entre el generador y la matriz A}.
@@
 % and the associated 
-All $N$ maps have the following properties:
+The maps have the following properties:
 \begin{enumerate}
-\item $\Sigma^{(k)}(\vec\alpha)\oplus \Sigma^{(k)}(\vec\beta)=\vec\alpha\oplus \vec\beta$.
+\item $\Sigma^{(k)}(\vec\alpha)\oplus \Sigma^{(k)}(\vec\beta)=\vec\alpha\oplus \vec\beta$, and
 \item $\Sigma^{(k)}(\vec\alpha)\neq\vec\alpha$.
@@
 \begin{equation}
-\valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0), 
+\valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0). 
 \label{eq:Sigma}
 \end{equation}
-which means that if $\Sigma^{(k)}(\vec0)$ belongs
+This implies that if $\Sigma^{(k)}(\vec0)$ belongs
 to a channel then 
@@
 under $\oplus$. In other words, the components of a PCE channel
-are symmetric under reflection over the $k$-th axis. \cpnote{Quizá 
-referencia a algunas figuras}. Now consider the case in which 
+are symmetric under reflection over the $k$-th axis. Now consider the case in which 
  $\Sigma^{(k)}(\vec0)$ does not belong to generator. Then 
@@
 because for generators, the codimension of the associated vector space 
-is 1.
+is 1. This means that the components of a PCE channel are antisymmetric
+with respect to reflection over the $k$-th axis. 
+Indeed, the 2-qubit PCE generators 
+$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
+represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
+respectively, are either symmetric or anti-symmetric under reflection with 
+respect to lines that divide the diagram in half vertically and horizontally.
 
+\cpnote{De aca al resto de la seccion o establecemos la conexion con A o lo quitamos}
 % 
@@
 
-\janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
-For instance, see that the 2-qubit PCE generators 
-$\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
-represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
-respectively, are either symmetric or anti-symmetric under reflection with 
-respect to lines that divide the diagram in half vertically and horizontally. 
+% \janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
+% For instance, see that the 2-qubit PCE generators 
+% $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
+% represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
+% respectively, are either symmetric or anti-symmetric under reflection with 
+% respect to lines that divide the diagram in half vertically and horizontally. 
 The same symmetry is identified for the rows and columns of $A$ if one 
@@
 
-\cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
-del primer parrafo}
+% \cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
+% del primer parrafo}
 
-- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
-
-The set of all PCE quantum channels may be sorted in subsets, 
-which we will call equivalence classes, whose
-elements are equivalent via particle swaps and local-basis element
-permutations. 
-\janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
-Aún hay que decidirlo con los demás.}
+% - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
+% 
+% The set of all PCE quantum channels may be sorted in subsets, 
+% which we will call equivalence classes, whose
+% elements are equivalent via particle swaps and local-basis element
+% permutations. 
+% \janote{El párrafo que pretendía ser este tendrá que ir en otra parte. 
+% Aún hay que decidirlo con los demás.}
 

### 2022-02-18 documentos/proofdiagonalization.tex
anotaciones
Comm_Proof_Diag

@@
 and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$}
-\janote{yo creo que es mejor dejar el $\oplus$ para la suma de Francois y usar otro símbolo para suma módulo 2. Además, creo que es mejor escribir $\ket{j,j+l´} \text{ (mod 2)}$ 
+\janote{yo creo que es mejor dejar el $\oplus$ para la suma de Francois y usar otro símbolo para suma módulo 2. Además, creo que es mejor escribir $\ket{j,j+l'} \text{ (mod 2)}$ 
 para que sea claro que esos son vectores canónicos (son los canónicos, verdad?)},
+\afnote{La base usada es la computacional, pero en esta parte no sabria como nombrarla.
+Tal vez ``Vectorized computational basis"?
+En relación al símbolo $\oplus$, creo que es mejor especificar dentro del texto que esta es una suma modulo 2, y en la parte de François que es suma módulo 4, esto con el fin de no sobrecargar la notación dentro de las ecuaciones.}
 \begin{equation}
@@
 \begin{equation}
-\lambda = \frac{1}{2^N} A \tau, 
+\lambda = \frac{1}{2^N} A \vec\tau, 
 \end{equation}

### 2022-02-18 documentos/pce.tex
deterministic

@@
 evolution of such density matrices. The
-trace preserving property is required for the process $\mcE$ to be
-deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
+trace preserving property is required for the process $\mcE$ {\red [viejo]to be
+deterministic}{\blue [nuevo] to happen with probability $1$}, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
 Often, this condition is easy to test \afnote{Podríamos decir que tanto linealidad como preservación de la traza son faciles de checar.}.

### 2022-02-18 documentos/intro.tex
intro

--- 2022-02-15 documentos/intro.tex
@@
 Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters~\cite{Rybar2012,ruskai,davalosdivisibility}
+For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
+For general finite-dimensional channels, families of channels defined as convex combinations of quantum-classical channels, in turn defined with bases that belong to a mutually unbiased basis (MUB), are studied in Ref.~\cite{nathanson2007pauli}.
+These channels have properties in common with unital qubit channels [...].
+Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020}
+\par
+[Role of completely positivity]
+%
+\par
+The paper is organized as follows, in section~\ref{sec:pce_maps}
 % }}}

### 2022-02-22 documentos/intro.tex
salvaguardando

@@
 For general finite-dimensional channels, families of channels defined as convex combinations of quantum-classical channels, in turn defined with bases that belong to a mutually unbiased basis (MUB), are studied in Ref.~\cite{nathanson2007pauli}.
-These channels have properties in common with unital qubit channels [...].
-Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020}
+These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs.
+Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020} as another attempt to generalize unital qubit channels.
+%
+[Other references]
+
 \par
+In the present work, we give a generalization of the qubit flip operations (bit, phase and bit-phase) to the 
 [Role of completely positivity]

### 2022-02-22 documentos/math.tex
Now it's all microservices, I hope the fad persists.

@@
 single qubit and then for $N$ qubits. 
-\janote{Finally, we restrict Pauli diagonal maps to PCE maps, and provide a connection
-between a vector subspace to the set of coefficients $\{\tau_\valpha\}$ 
-in \eref{eq:PCE_definition} of a PCE quantum channel.}
-{\red [anterior]
-We then restrict to PCEs and, for quantum
-channels, associate a vector subspace to the set of coefficients
-$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}.} 
+Finally, we restrict from Pauli diagonal maps to PCE maps, and provide a connection
+between a vector subspace and the set of coefficients $\{\tau_\valpha\}$ 
+in \eref{eq:PCE_definition} of a PCE quantum channel.
+% {\red [anterior]
+% We then restrict to PCEs and, for quantum
+% channels, associate a vector subspace to the set of coefficients
+% $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}.} 
 This allows us to
@@
 \end{equation}
-\janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
-modificó la frase que le sigue a este comentario.}
+% \janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
+% modificó la frase que le sigue a este comentario.}
 This vectorization must not be confused with the 

### 2022-02-22 documentos/pce.tex
intro
Now it's all microservices, I hope the fad persists.

--- 2022-01-27 documentos/pce.tex
@@
-\section{PCE Maps}
-\janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
-\janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
-To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
-maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
-channels that will allow us to introduce some notation. 
+\section{Pauli component erasing maps}
+\label{sec:pce_maps}
+% \janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
+% \janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
+% To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
+% maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
+% channels that will allow us to introduce some notation.
+
+% \afnote{Propongo que cambiemos el inicio de esta sección por: 
+In this section we introduce the family of Pauli component erasing (PCE)
+\cpnote{Revisar despues de escribir la intro que no se ha introducido la sigla}
+maps. Let us start our discussion with a brief review of several basic concepts
+of quantum channels that will allow us to introduce some notation, 
+and finish with the definition of PCE maps, some generalities. We further 
+introduce a useful graphical representation  for them.
+% of the aforementioned maps. 
+% and finish with the definition of PCE maps, some generalities and a graphical representation. 
+% }
 % In this section we introduce the definition of Pauli component erasing maps,
@@
 \subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
-Quantum channels are the most general linear operations that a quantum
-system undergo independently of its past~\cite{zimansbook,cirac}.
-The physical system under study will be associated with a Hilbert space
-denoted by \hilbert{}, and the set of linear operators over such space will 
-be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
- is an element of $\mcB(\hilbert)$.
-
+% \afnote{Creo que podríamos empezar la sección introduciendo el espacio de
+% Hilbert y esas cosas y después si dedicarse solamente a Quantum channels. Si
+% están de acuerdo, entonces sólo tendriamos que cambiar el orden de las dos
+% primeras frases en el primer párrafo.}
+Quantum channels are the most general linear operations that a quantum system
+undergo independently of its past~\cite{zimansbook,cirac}.  The physical system
+under study will be associated with a Hilbert space denoted by \hilbert{}, and
+the set of linear operators over such space will be denoted by
+$\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system is an
+element of $\mcB(\hilbert)$.
+% \afnote{En esta última parte podriamos cambiar asi:}
+% \afnote{The state of the physical system under study is associated to a
+% Hilbert space \hilbert{}, and the set of linear operators over such space is
+% denoted by $\mcB(\hilbert)$. In this way, a density matrix $\rho$ of such
+% system is an element of $\mcB(\hilbert)$.}
 % Quantum channels comprehend the most general linear operations that a quantum
@@
 evolution of such density matrices. The
-trace preserving property is required for the process $\mcE$ to be
-deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
+trace preserving property is required for the process $\mcE$ 
+ to happen with probability $1$, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
 Often, this condition is easy to test.
@@
 positivity condition is needed to preserve positive semidefiniteness and handle
-the non-local feature of quantum theory. 
+the non-local nature of quantum theory.
 A linear map $\mcE$ is positive if it maps density operators to density operators, \ie{}
@@
 On the other hand, if one extends a positive map to include an ancilla, the resulting
-map is not always positive. If, for all dimensions of the ancilla, such extension
+map is not always positive. If, for an ancillary system of arbitrary dimension, such extension
 results in a positive map, we say that the original map is completely
@@
 so as to allow the proper evolution of potentially entangled states with an
-ancilla. 
+ancilla; to test this condition we require some additional steps. 
+% \afnote{Sería bueno mencionar también que la tarea de determinar la CP
+% de un mapa es no trivial, lo que sirviría también como conector o preambulo del
+% siguiente párrafo.}
 % In the other hand, a map is completely positive if extending the 
@@
 $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is a 
-maximally entangled state between the original system and an ancilla.
+maximally entangled state between the original system and an ancilla and
+``$\id$'' is the identity channel.
 Remarkably, the map \mcE{} is completely positive
@@
 is positive-semidefinite~\cite{jamil,choi}. 
-
+% \afnote{No sé si es algo obvio, pero creo que seria bueno comentar que es el objeto $\id$.}
 %  the
@@
 
-% Quantum channels can be characterized by means of the Choi-\jami{}
-% isomorphism~\cite{choi,jamil}. This is, given a linear operation
-% $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
-% $\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called
-% dynamical matrix), where
-% $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
-% Bell state between two copies of \hilbert. The map \mcE is completely positive
-% if and only \choi is positive-semidefinite.
-%
-%
-
-% In fact,
-% a linear operation is completely positive if and only if it has a Kraus
-% representation~\cite{Kraus1983}.
-% The minimum number of Kraus operators $K_i$
-% needed to represent the channel is called \textit{Kraus rank}. 
-%
-
-% It can be seen from Kraus decomposition that quantum channels preserve
-% hermiticity, this has a practical consequence when using hermitian bases, \ie{}
-% let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then
-% the entries of the matrix representation of the quantum channel $\mcE$, $\hat
-% \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular,
-% in this work we are interested in systems of $N$ qubits, and we use hermitian
-% bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui
-% introduzco el nombre estandar}, defined as 
-% \begin{equation}
-% \sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
-% \label{eq:pauli_strings}
-% \end{equation}
-% where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and
-% $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr
-% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
-% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
-% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
-% \textit{Pauli basis},
-% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
-
-%
-
-% \flnote{
-% probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
-% $\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
-% Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
-% }\ddnote{ejecutado, hacia falta edicion, sin embargo lo de hermiticity preserving es para hacer incapie en por que podemos trabajar en una representacion totalmente real de los canales.}
-% 
-%   \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}
-
 % }}}
-\subsection{Pauli component erasing maps} % {{{
+\subsection{Structure of PCE maps} % {{{
 \label{sec:single:qubit}
 % \todo{David escribe una primera version y luego Carlos itera}
-\janote{Se añadió un primer párrafo para hacer una transición suave del A
-al B y decir qué discutimos aquí.}
-Now that we have discussed the main features of quantum channels
-we are going to introduce the Pauli component erasing maps.
-We shall start exploring the single qubit scenario 
-and continue with the $N$-qubit case.
+% Now that we have discussed the main features of quantum channels
+% we are going to introduce the Pauli component erasing maps.
+% We shall start exploring the single qubit scenario 
+% and continue with the $N$-qubit case. 
+% 
+% \afnote{
+We have discussed the main features of quantum channels, now
+we turn our attention to introduce the Pauli component erasing maps. We start
+by exploring the single qubit scenario and then we treat the $N$-qubit case.
+% }
 
@@
 \end{equation}
+% \afnote{Creo que este párrafo queda mejor así: where
+% $\{\sigma_{0},\sigma_{1},\sigma_{2},\sigma_{3}\}=\{\one,\sigma_{x},\sigma_{y},\sigma_{z}\}$,
+% with $\one$ the $2\times 2$ identity matrix and $\sigma_{j}$ the usual Pauli
+% matrices. Note that normalization requires that $r_0=1$. On the other hand, the
+% remaining $r_{j}$ coefficients constitute the so called Bloch vector
+% $\vec{r}=(r_{x},r_{y},r_{z})$. Consider the map that projects each component in
+% the following way:}
+% 
 with $\sigma_0= \one$, and $\sigma_{1,2,3}$ the usual Pauli matrices.  
 Normalization requires that $r_0=1$ and the remaining $r_{1,2,3}$ 
-form the Bloch vector. Consider the map that projects
+form the Bloch vector. 
+Consider the map that projects
 each component 
 in the following way,
+% 
 \begin{equation}
 r_\alpha \mapsto \tau_\alpha r_\alpha
+\label{EqPCE}
 \end{equation}
-where $\tau_\alpha$ is either $1$ or $0$ (trace preserving requires
-that $\tau_0=1$). Not every
-such operation  is a quantum map; for example, collapsing the entire Bloch
-ball to the $xy$ plane (setting $\tau_{1,2}=1$ and  $\tau_3=0$) is not a quantum
-channel. A direct evaluation of the complete positivity
-conditions~\cite{zimansbook,davalosdivisibility}, 
+where $\tau_\alpha$ is either $0$ or $1$ (trace preserving requires
+that $\tau_0=1$). 
+From now on we refer to any operation like that described in
+\eref{EqPCE}, as single qubit \textit{Pauli component erasing} (\pce{}) maps.
+Not every such operation  is a quantum channel;
+for example, collapsing the entire Bloch ball to a disk on the $xy$
+plane ($\tau_{1}=\tau_{2}=1$ and  $\tau_3=0$) 
+leads
+to a violation of the CP conditions. Indeed a direct evaluation
+of such conditions yield~\cite{zimansbook,davalosdivisibility}, 
+% 
+% 
+% is not a quantum channel
+% \afnote{(Aquí podemos colocar en vez de ``is not a quantum channel'', ``leads
+% to a violation of the CP conditions, indeed a direct evaluation
+% \cite{zimansbook,davalosdivisibility}'')}. A direct evaluation of the complete
+% positivity conditions~\cite{zimansbook,davalosdivisibility}, 
 \begin{align}
 1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
-1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall \alpha\neq \beta \neq \gamma,
+1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall ~\alpha\neq \beta \neq \gamma,
 \end{align}
@@
 \end{center}
-	\caption{\janote{Le modificamos la primera frase a esta caption para que la Fig sea
-	autocontenida}
+	\caption{
+% \janote{Le modificamos la primera frase a esta caption para que la Fig sea
+% 	autocontenida}
 In (a) we introduce the notation
@@
 (b), (c) and (d) correspond to the identity map, dephasing channel, and 
-total depolarization, respectively. In (e) we show a map that only erases the component
-$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.}
+total depolarization, respectively, 
+as the color of each square indicates the value attained by the corresponding
+$\tau_{\alpha}$, either 0 (white) or 1 (black). 
+In (e) we show a map that only erases the component
+$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to
+a quantum operation.
+% \afnote{Propongo el siguiente caption: (a) Pictorial
+% representation of a single qubit \pce{} map.
+% The color of each square indicates the value attained by the corresponding
+% $\tau_{\alpha}$, either 0 (white) or 1 (black). The diagrams in (b), (c) and
+% (d) correspond to the identity map, dephasing channel, and total
+% depolarization, respectively. In (e) we show a map that only erases the
+% component $r_1$, collapsing the Bloch sphere into a disk, and thus does not
+% correspond to a quantum operation.}
+}
 	\label{fig:one:qubit:examples}
@@
 
-A Pauli component erasing (PCE) map is a map
+% Thus, i
+In general, a Pauli component erasing (PCE) map is a map
 %  Pauli diagonal operation
@@
 \end{equation}
-For the operation to be trace preserving, it is required that $\tau_{\vec
+In addition, for the operation to be trace preserving, it is required that $\tau_{\vec
 0}=1$. 
@@
 On the other hand, constructing and
-evaluating the conditions for complete positivity is involved and is the main
+evaluating the conditions for complete positivity is non-trivial and is the main
 problem addressed in this paper.
@@
 from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill  \janote{Jose Alfredo quizá itera}
 the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
-empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
-for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.
+empty. 
+Examples for $N=1$ and $N=2$ are provided in \fref{fig:one:qubit:examples} and
+\fref{fig:two:qubit:examples}, respectively.
 
@@
 commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
-2^N $ components equal to $1$s in its diagonal, see appendix~\sref{quantum_classical}.
+2^N $ components equal to $1$s in its diagonal.
+% \afnote{Aquí me parece que falta información. Creo que hay que decir que es lo
+% que es diagonal y en que base.} 
+For details, we refer the reader to appendix~\ref{quantum_classical}.
 

### 2022-02-22 documentos/vector_space.tex
Comentarios apéndice Alejo y otra cosa chiquita
I transformed a bug into a feature. Once you learn how, you'll never forget it
Now it's all microservices, I hope the fad persists.

@@
 \subsection{PCE quantum channels as vector spaces} % {{{
-\cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
+% \cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
 % \ddnote{propongo channels as vector spaces como titulo de seccion, pues lo
@@
 indices $\valpha$ labeling the components of a state; see
-\eref{eq:N_qubits_rho}. \cpnote{Some established facts about vector spaces will allow
-us to draw conclusions for PCE quantum channels.}
-\janote{Prefiero esta frase:}
-\janote{Some established facts about vector spaces will allow
-us to derive the main features of PCE quantum channels.}
+\eref{eq:N_qubits_rho}. 
+Some established facts about vector spaces will allow
+us to derive the main features of PCE quantum channels.
 
 Let us start by recalling that the problem of determining complete positivity
-of a PCE map can be recast as determining which vectors $\vtau$ are mapped via
-$\san$
+of a PCE map can be recast as determining which vectors $\vtau$ 
+are mapped via $\san$
 % \begin{equation}
@@
 \caption{
-\cpnote{Revisar, solo tiene una iteracion por parte mia}
-Examples of diagrams for several PCE quantum channels. In
- (a) the totally depolarizing channel is represented whereas
-in (b) a PCE channel that preserves four components.  (c), (d)
-and (e) show three generators \cpnote{Quizá poner los nombres de los generadores acá}; the combination of any two of them
-yields the channel in (b). (f) represents the identity map. 
+% \cpnote{Revisar, solo tiene una iteracion por parte mia}
+% Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
+% depolarizing channel, (b) a PCE channel that preserves four components.
+% (c), (d) and (e) show three generators \cpnote{Quizá poner los nombres de los
+% generadores acá}; the combination of any two of them yields the channel in (b).
+% (f) represents the identity map. 
 % 
@@
 % hay una manera unica de generar esos bichos.
+Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
+depolarizing channel, (b) a PCE channel that preserves four components, the
+normalization component, one local component of qubit 2 and two correlations between the 
+two qubits.
+(c), (d) and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and
+$\mcG_{(2,2)}$, respectively; the combination (overlap of diagrams) of any two
+of them yields the channel in (b).
+(f) represents the identity map. 
 }

### 2022-02-22 documentos/vector_space.tex
Blaming regex.

@@
 then successively switch $\tau_{\vec\alpha}$'s
-\janote{agregué el subíndice $\vec\alpha$} 
+% \janote{agregué el subíndice $\vec\alpha$} 
 to $1$ for various values of $\valpha$,
 taking care immediately to set equal to one the components of $\vec\tau$
-\janote{puse la $\tau$ como vector}
+\janote{puse la $\tau$ como vector y hay otro antes}
 that

### 2022-02-23 documentos/vector_space.tex
We should get someone from Purdue to do this. They are the boilerplaters.

@@
 Let us start by recalling that the problem of determining complete positivity
-of a PCE map can be recast as determining which vectors $\vtau$ 
+of a PCE map can be recast as determining which coefficients $\tau_\valpha$ 
 are mapped via $\san$
@@
 % \end{equation}
-to a vector with positive entries $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
+to positive eigenvalues $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
 % . In components, this would read 
@@
 whenever the $\vec\gamma$ belongs to a given vector subspace of the set of
-all indices, then the vector $\vec\tau$ indeed has an image
-which is a vector
-with only positive components. 
+all indices, then $\tau$ indeed has an image
+which has
+only positive components. 
 In other words, there is a one-to-one correspondence between 
@@
 to $1$ for various values of $\valpha$,
-taking care immediately to set equal to one the components of $\vec\tau$
-\janote{puse la $\tau$ como vector y hay otro antes}
+taking care immediately to set equal to one the components of $\tau$
+% \janote{puse la $\tau$ como vector y hay otro antes}
 that
@@
 As such, $W$ has a given dimension $K$, which means that
-$W$ has $2^K$ elements. In other words, a vector $\vec\tau$ with the property
+$W$ has $2^K$ elements. In other words, a set of indices $\tau_\valpha$ with the property
 discussed above can only have $2^K$ elements equal to 1, for a given integer

### 2022-02-23 documentos/proofdiagonalization.tex
Now it's all microservices, I hope the fad persists.
We should get someone from Purdue to do this. They are the boilerplaters.
mod2 y comentarios

--- 2022-02-01 documentos/proofdiagonalization.tex
@@
 \subsection{Single qubit} % {{{
+\ddnote{Alejo, por fa revise q no se me fue un typo con el asunto de mod 2, ya corregí toda la notación y removi los otros comentarios, que ya fueron aclarados en la reunion y trataban de lo mismo}
 In order to simplify the derivation of the relations, let us employ pairs of
@@
 compactly as
-$\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j\oplus l }$. In vectorized form
+$\sigma_{k l }=\sum_{j=0}^{1} (-1)^{j k }\dyad{j}{j + l ( \text{mod}2) }$. In vectorized form
 \begin{equation}
-\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\kket{j,j\oplus l },
+\kket{\sigma_{k l }}=\sum_{j=0}^{1} (-1)^{j k }\ket{j} \ket{j+l(\text{mod } 2) },
 \label{CompToPau}
 \end{equation}
-and its inverse relation \ddnote{falta definir que es el $\oplus$ en este contexto, y no solo eso, sino quienes son los vectores del lado derecho, \ie{} $\kket{k,l}$},
+and its inverse relation
 \begin{equation}
-\kket{k,k\oplus l}=\frac{1}{2}\sum_{j=0}^{1} (-1)^{jk}\kket{\sigma_{jl}}.
+\ket{k}\ket{k+l (\text{mod } 2)}=\frac{1}{2}\sum_{j=0}^{1} (-1)^{jk}\kket{\sigma_{jl}}.
 \label{PauToComp}
@@
 \label{eq:inicio:canal:pauli}\\
-& = \frac{1}{2}\sum_{jkl m} \tau_{l m} (-1)^{l (j+k)} 
-     \ddyad{j,j\oplus m}{k,k\oplus m}.
-% \label{Map_Pauli}
+& = \frac{1}{2}\sum_{jkl m} \tau_{l m} (-1)^{l (j+k)} \nonumber\\
+     & \hspace{1cm} \times \ket{j}\ket{j +m  (\text{mod } 2)}\bra{k}\bra{k +m (\text{mod } 2)}.
 \end{align}
@@
 Choi matrix associated to the map. It reads
-\begin{equation}
+\begin{multline}
  \mathcal{D} = 
-  \frac{1}{2}\sum_{jklm} \tau_{lm} (-1)^{l(j+k)} 
-      \ddyad{j,k}{j\oplus m,k\oplus m}.
+  \frac{1}{2}\sum_{jklm} \tau_{lm} (-1)^{l(j+k)} \\
+     \times \ket{j}\ket{k}\bra{j+ m(\text{mod}2)}\bra{k+m(\text{mod}2)}.
 \label{Choi_a1}
-\end{equation}
+\end{multline}
 Note furthermore that the expression above may also be written as a combination
@@
 \end{equation}
-Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j\oplus
-k$, then the Choi matrix reads
-\begin{equation}
+Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
+k (\text{mod} 2)$, then the Choi matrix reads
+\begin{multline}
  \mathcal{D} =
-    \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} 
-        \ddyad{j,j\oplus k}{j\oplus m,j\oplus m\oplus k},
+    \frac{1}{2}\sum_{jk lm} \tau_{ lm} (-1)^{ l k} \\
+       \times \ket{j}\ket{j +k(\text{mod } 2)}\bra{j+ m(\text{mod } 2)}\bra{j+ m+ k(\text{mod } 2)},
 \nonumber
 % \label{Choi_a1}
-\end{equation}
+\end{multline}
 % thanks to a simplification in the argument of the power of $-1$. To continue, 
-since $ (-1)^{j+j\oplus k} = (-1)^k $. To continue, we 
+since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $ \ddnote{Alejo, por fas checa esto, se me hace curioso que el modulo 2 solo este solo en la segunda suma del exponente}. To continue, we 
 use the relation between computational and Pauli elements [\eref{PauToComp}],
@@
 
-The tensor product of Pauli matrices, in vector form,  will be denoted by 
+\ddnote{Poner atencion a lo siguiente}
+{\red[viejo y mal]The tensor product of Pauli matrices, in vector form,  will be denoted by 
 $\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
@@
 $\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
-2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$. 
+2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$.}
+{\blue [nuevo y correcto y breve, la condicion de ortogonalidad no se usa explicitamente y es trivial]
+The tensor product of Pauli matrices, in vector form,  will be denoted by 
+$\kket{\sigma_{\vec{k}\vec{l} }}$.
+}
 % \begin{equation}
@@
 The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
+\ddnote{corregir el angulo doble y tambien el oplus}
 \begin{align}
 \kket{\sigma_{\vec{k}\vec{l} }}  & = 
-   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \kket{\vec{j},\vec{j}\oplus \vec{l}},\\
+   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \ket{\vec{j}}\ket{\vec{j}+ \vec{l}(\text{mod}2)},\\
 %
- \kket{\vec{l},\vec{l}\oplus \vec{n}} & = 
+ \ket{\vec{l}}\ket{\vec{l}+ \vec{n}(\text{mod}2)} & = 
    \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
@@
 the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
-\begin{align}
+\begin{multline}
 \hat{\mathcal{E}} 
 % & = \frac{1}{2}\sum_{l m=0}^{1} \tau_{l m} \ddyada{\sigma_{l m}} 
-& = \frac{1}{2}\sum_{\vec j\vec k\vec l \vec m} 
-     \tau_{\vec l \vec m} (-1)^{\vec l (\vec j+\vec k)} 
-     \ddyad{\vec j,\vec j\oplus \vec m}{\vec k,\vec k\oplus \vec m}.
+= \frac{1}{2}\sum_{\vec j\vec k\vec l \vec m} 
+     \tau_{\vec l \vec m} (-1)^{\vec l (\vec j+\vec k)} \\
+     \times\ket{\vec j}\ket{\vec j+\vec m (\text{mod}2)}\bra{\vec k}\bra{\vec k+\vec m(\text{mod}2)}.
 % \label{eq:inicio:canal:pauli:N}
 % \label{Map_Pauli}
-\end{align}
+\end{multline}
 % 
@@
 \end{equation}
-or more compactly $\vec{\lambda} = (H\otimes H/2)^{\otimes N} \vec{\tau}$. 
+or more compactly $\lambda = (H\otimes H/2)^{\otimes N} \tau$. 
 Again, we prefer to reorganize the indices to be able to write

### 2022-03-08 documentos/kraus.tex
Added missing file in previous commit

@@
-\section{Kraus operators and decoherence  propuesta: Physical implementations of PCE maps} % {{{
+\section{PCE channels and decoherence o Physical implementations of PCE maps} % {{{
 \label{sec:kraus}
 % Intro {{{
-
-\cpnote{Contrapropuesta: PCE channels and decoherence}
-
-\cpnote{Crep qe hay que hacer una mini introduccion en donde se explique el porqué de
-esta seccion. Básicamente la idea es conectar estos bichos con procesos fisicos.
-Siento que la introduccion propuesta est´a un poco debil}
-\ddnote{hecha miniintroduccion, es basicamente la misma idea, pero con detalles y justificaciones matematicas}
 

### 2022-03-08 documentos/kraus.tex
stuff

@@
 
-{\red [anterior]Given that \pce{} channels are projections, we might ask whether they are fixed
-points of some memory-less (Markovian) process or not. In this section we prove
-that they are, and give two examples of Markovian implementations. The first
-one consist in identifying each \pce{} channel as a fixed point of some pure
-dissipative process. The second, in identifying each \pce{} channel as fixed
-points of some memory-less collision model.}
-{\blue [nuevo] It is known that not every quantum channel can be seen as a snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility}, \ie{} a process described with a Markovian master equation~\cite{lindblad,kossa,kossa2,Gorini1976},
+% {\red [anterior]
+% Given that \pce{} channels are projections, we might ask whether they are fixed
+% points of some memory-less (Markovian) process or not. In this section we prove
+% that they are, and give two examples of Markovian implementations. The first
+% one consist in identifying each \pce{} channel as a fixed point of some pure
+% dissipative process. The second, in identifying each \pce{} channel as fixed
+% points of some memory-less collision model.}
+
+{\blue [anterior] It is known that not every quantum channel can be seen as a
+snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility},
+\ie{} a process described with a Markovian master
+equation~\cite{lindblad,kossa,kossa2,Gorini1976},
 \begin{multline}
@@
 }
+
+{\red [nuevo]
+Lindblad processes arise naturally in many theoretical~\cite{} and
+experimental~\cite{} settings and are archetypical in decoherence dynamics. 
+It is known that not every quantum channel can be seen as a snapshot of a
+process
+arising from a traditional Lindblad equation or even a time-dependent Lindblad
+equation~\cite{cirac,davalosdivisibility}. 
+Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
+some Markovian processes. In this section we prove what in fact they are, and
+give two examples of Markovian implementations.
+%
+The first
+one consist in identifying each \pce{} channel as a fixed point of some pure
+dissipative process. The second, in identifying each \pce{} channel as fixed
+points of some memory-less collision model.
+
+% the most 
+% common decoherence 
+% 
+% with a Markovian master
+% equation~\cite{lindblad,kossa,kossa2,Gorini1976},
+% \begin{multline}
+% \dot \rho(t)=-i [H(t),\rho(t)]+\\
+% \sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right),
+% \end{multline}
+% where the first part is the so-called Hamiltonian term, the second the dissipative term with $\gamma_k(t)\geq 0$ the relaxation ratios associated with the Lindblad operators $V_k(t)$.
+% %
+% In the particular case where the Hamiltonian, relaxation rations and Lindblad
+% operators are independent of time, we recover the well-known Lindblad master
+% equations~\cite{lindblad}. Such equations model time-homogeneous processes,
+% implying one-parameter semigroup structures that will be exploited later.
+% %
+% Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
+Therefore, we might ask whether \pce{} channels can be seen as limit points of some Markovian processes.
+In this section we prove what in fact they are, and give two examples of Markovian implementations.
+% %
+% The first
+% one consist in identifying each \pce{} channel as a fixed point of some pure
+% dissipative process. The second, in identifying each \pce{} channel as fixed
+% points of some memory-less collision model.
+}
+
 % }}}

### 2022-03-08 documentos/kraus.tex
That's just how I roll

@@
 
-We shall first show that the aforementioned Kraus operators produce a PCE. 
+We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce a PCE. 
 Notice that 
@@
 \subsection{Pure dissipative implementation} % {{{
-{\red [viejo] Any PCE channel can be seen as the fixed point of some decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos los canales son resultado de
-lindblad.}
-{\blue [nuevo] In this section we show that any PCE channel can be seen as the fixed point of some decoherence process, this is a property that is not accomplished by any channel, as mentioned above.} Me gustaria modificar esta frase para que pueda ser apreciada mejor} \ddnote{la modificacion fue leve debido a que la mayor parte del contenido esta en la introduccion de la seccion}.
-We
-will show this first for PCEGs. Consider the following dynamical process that
-implements the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
+% {\red [viejo] Any PCE channel can be seen as the fixed point of some
+% decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos
+% los canales son resultado de lindblad.}
+In this section we show that any PCE channel can be seen as the
+fixed point of some decoherence process, starting with PCEGs and 
+then generalizing to more general channels. 
+% Me gustaria modificar esta
+% frase para que pueda ser apreciada mejor} \ddnote{la modificacion fue leve
+% debido a que la mayor parte del contenido esta en la introduccion de la
+% seccion}. 
+% We start with PCEGs. 
+Consider the following dynamical process that
+implements $\mcG_{\vec \alpha}$ when $t\to \infty$,
 \begin{align}

### 2022-03-09 documentos/a_and_generators.tex
Sobre simetrías de A y los generadores

\documentclass[11pt,dvipsnames]{article} % {{{

\usepackage{geometry}
\geometry{total={170mm,240mm}, left=20mm, top=20mm}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{enumerate} 
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{physics}

\usepackage{bbold}

% To add graphics
\usepackage{graphicx}
% Path to figures
\graphicspath{ {../images/} }

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\definecolor{jacolor}{RGB}{200,40,0} \FXRegisterAuthor{ja}{aja}{\color{jacolor}JA}

%% commands
\newcommand{\valpha}{\vec\alpha}
\newcommand{\pceg}{\mathcal{G}_{\valpha}}
\newcommand{\1}{\mathbb{1}}

\author{José Alfredo de León}
\title{a and generators}
\begin{document}
\maketitle

One can express $\vec \tau(\pceg)$, the vector $\vec\tau$
of a PCE generator $\pceg$, in terms of $a(\alpha_{j_k})$, the rows or columns
of matrix 
\begin{align}
a=
\left(
\begin{array}{cccc}
 1 & 1 & 1 & 1 \\
 1 & 1 & -1 & -1 \\
 1 & -1 & 1 & -1 \\
 1 & -1 & -1 & 1 \\
\end{array}
\right).
\end{align}
The aforementioned expression is 
\begin{align}
\vec \tau(\pceg)=\frac{a(\alpha_{j_1})\otimes\ldots\otimes a(\alpha_{j_N})+\1_{4^N}}{2},
\end{align}
where $\1_{4^N}$ is a $4^N$-length vector with all its components equal to 1.

Note that the rows or columns $a(\alpha_{j_k})$ of matrix $a$ 
are eigenvectors of the reflection matrix
\begin{align}
R=
\left(
\begin{array}{cccc}
 0 & 0 & 0 & 1 \\
 0 & 0 & 1 & 0 \\
 0 & 1 & 0 & 0 \\
 1 & 0 & 0 & 0 \\
\end{array}
\right)
\end{align}
with eigenvalues $r_{0,1,2,3}=1,-1,-1,1$. In other words, we can identify
the `symmetric' (`anti-symmetric') eigenvectors as those with eigenvalues
1 (-1).

\janote{probar que (2) si es la tau de un generador}
We shall start proving that $\vec \tau(\pceg)$ has $4^{N-1}$ components 
equal to 1 and the rest 0.

The vector $a(\alpha_{j_1})\otimes\ldots\otimes a(\alpha_{j_N})$ has 
$n_-$  and $n_+$ number of components with minus and plus sign, respectively.
\begin{align}
n_{\pm}&=\sum_k\mathbb{n}_{\pm}\big[a(\alpha_{j_k})\big],
\end{align}
with $\mathbb{n}_{\pm}\big[a(\alpha_{j_k})\big]$ the number of components
with sign $\pm$ in vector $a(\alpha_{j_k})$.\janote{asumiendo que ya 
se probó que el número de +1 es $4^{N-1}$ o $4^{N}$ y de -1 $4^{N-1}$ o 0:}

Now we shall prove the symmetry.
\begin{align}
\Sigma^{(k)}\big[\vec \tau(\pceg)\big]=
\frac{a(\alpha_{j_1})\otimes\ldots\otimes R\big[ a(\alpha_{j_k})\big]\ldots\otimes a(\alpha_{j_N})+\1_{4^N}}{2}
\end{align}

\end{document}

### 2022-03-14 documentos/generators.tex
I should get a raise for this.

@@
 
-A reflection symmetry is identified for both PCE generators $\pceg$ and
-matrix $A$ \cpnote{Creo que aun 
-no tenemos el link entre el generador y la matriz A}.
+A reflection symmetry is identified for PCE generators.
 Consider the map $\Sigma^{(k)}$ that reflects an index $\valpha$ with 
@@
 
-\cpnote{De aca al resto de la seccion o establecemos la conexion con A o lo quitamos}
+\cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
 % 
@@
 % respect to lines that divide the diagram in half vertically and horizontally. 
-The same symmetry is identified for the rows and columns of $A$ if one 
-labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
-\janote{Aquí habría que agregar la prueva de simetría para la $A$.}
+% The same symmetry is identified for the rows and columns of $A$ if one 
+% labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
+% \janote{Aquí habría que agregar la prueva de simetría para la $A$.}
 
@@
 
-\ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya esta probado en la secc V}
-Given that both matrix $\san$ and PCE generators $\pceg$ have the same 
-symmetries, it is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
+% \ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya
+% esta probado en la secc V}
+It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
 encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
-From the tensor power of matrix $a$ one can infer the $\{\taus\}$ of a PCE
-generator $\pceg$ by taking any row or column $A^{(i)}$ and mapping 
-all entries with $-1$ to $0$. In \Fref{fig:A_and_PCEGs_connection} we illustrate
-this connection between $a$ and single qubit PCE generators.
-In \appref{sec:2_qubits} we illustrate this program for 2-qubits PCE channels.
+From the tensor power of matrix $a$ one can infer the components $\{\taus\}$ of a PCE
+generator $\pceg$ by taking row (or column) $\alpha$ of $A$ and replacing
+$-1$ with $0$. 
+The proof is given in \appref{sec:2_qubits} and in \fref{fig:A_and_PCEGs_connection} we illustrate
+this connection for the single qubit case.
 

### 2022-03-17 documentos/kraus.tex
parrafo lindblad etc

@@
 
-{\blue [anterior] It is known that not every quantum channel can be seen as a
-snapshot of a Markovian decoherence process~\cite{cirac,davalosdivisibility},
-\ie{} a process described with a Markovian master
-equation~\cite{lindblad,kossa,kossa2,Gorini1976},
-\begin{multline}
-\dot \rho(t)=-i [H(t),\rho(t)]+\\
-\sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right),
-\end{multline}
-where the first part is the so-called Hamiltonian term, the second the dissipative term with $\gamma_k(t)\geq 0$ the relaxation ratios associated with the Lindblad operators $V_k(t)$.
-%
-In the particular case where the Hamiltonian, relaxation rations and Lindblad operators are independent of time, we recover the well-known Lindblad master equations~\cite{lindblad}.
-Such equations model time-homogeneous processes, implying one-parameter semigroup structures that will be exploited later.
-%
-Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
-Therefore, we might ask whether \pce{} channels can be seen as limit points of some Markovian processes.
-In this section we prove what in fact they are, and give two examples of Markovian implementations.
-%
-The first
-one consist in identifying each \pce{} channel as a fixed point of some pure
-dissipative process. The second, in identifying each \pce{} channel as fixed
-points of some memory-less collision model.
-}
-
-{\red [nuevo]
-Lindblad processes arise naturally in many theoretical~\cite{} and
-experimental~\cite{} settings and are archetypical in decoherence dynamics. 
+Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
+experimental~\cite{PhysRevA.67.042322} \ddnote{aqui hace falta buscar mas citas, estoy buscando algo relacionado con la optical master equation, el pedo es que creo que esas ondas son time-dependent} settings and are archetypical in decoherence dynamics.
+\ddnote{añado esto a ver si gusta, motiva el hecho de que los PCEs sean puntos limite y no "puntos intermedios"} {\blue Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).}
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 % points of some memory-less collision model.
-}
 

### 2022-03-26 documentos/intro.tex
etc

@@
 {\blue [Aqui arranco con la introduccion]\\}
-Similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
+The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics, and recently, even coarse graining~\cite{Duarte2017,pinedacg}.
+One of the main difficulties is that, similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
 For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real numbers which are not fully independent (the complete positivity condition imposes which regions have physical meaning, see Ref.~\cite{zimansbook}).
-Therefore, even the qubit case is difficult to explore, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
+Therefore, even the qubit case is difficult to analyze, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
 Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.

### 2022-03-31 documentos/kraus.tex
quito comments ya hablados con Carlos

@@
 Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
-experimental~\cite{PhysRevA.67.042322} \ddnote{aqui hace falta buscar mas citas, estoy buscando algo relacionado con la optical master equation, el pedo es que creo que esas ondas son time-dependent} settings and are archetypical in decoherence dynamics.
-\ddnote{añado esto a ver si gusta, motiva el hecho de que los PCEs sean puntos limite y no "puntos intermedios"} {\blue Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).}
+experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
+Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a

### 2022-03-31 documentos/intro.tex
intro mas label a seccion

@@
 \section{Introduction} % {{{
-\ddnote{Generalization of the notion that squeezing the Bloch sphere into a disk is not a channel.
-Quantum channels have a astonishing number of parameters as the dimension grows, so studies like ours is important to understand less parametric families of quantum channels.
-}
-Several PRA articles go straight into matter. I guess we will write what we have to write
-
-Creo que puede quedar bonito, honesto y util si comenzamos motivando el
-problema desde un punto de vista matemático, y luego seguimos platicando de las
-consecuencias físicas, es decir mostrando que el problema como lo planteamos
-tiene aplicaciones practicas.
-
-\ddnote{Yo agregare un parrafo delineando la literatura alrededor de Ruskai}
-Nathanson, Ruskai~\cite{nathanson2007pauli} based on MUBs... Based on mutually unbiased measurements~\cite{Siudzinska2020}
-Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
-\begin{equation}
-\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
-\end{equation}
-and \textit{completely depolarizing},
-\begin{equation}
-\rho \mapsto \frac{\one}{2} \tr \rho,
-\end{equation}
-These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
-\newline
-{\blue [Aqui arranco con la introduccion]\\}
-The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics, and recently, even coarse graining~\cite{Duarte2017,pinedacg}.
+%
+The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space, is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics, and recently, even coarse graining~\cite{Duarte2017,pinedacg}.
 One of the main difficulties is that, similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
-For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real numbers which are not fully independent (the complete positivity condition imposes which regions have physical meaning, see Ref.~\cite{zimansbook}).
-Therefore, even the qubit case is difficult to analyze, having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
+For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real parameters which are not fully independent (the complete positivity condition imposes the regions that physical meaning, see Ref.~\cite{zimansbook}).
+Therefore, even the qubit case is difficult to analyze having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
 Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning only unital channels, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
-For general finite-dimensional channels, families of channels defined as convex combinations of quantum-classical channels, in turn defined with bases that belong to a mutually unbiased basis (MUB), are studied in Ref.~\cite{nathanson2007pauli}.
+For the qubit case there are several studies concerning the unital case, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
+For general finite-dimensional channels, several families of channels have been defined in order to explore the huge parametric space of channels.
+In~Ref.~\cite{nathanson2007pauli} channels defined as convex combinations of quantum-classical channels, in turn defined with mutually unbiased basis (MUB), are introduced.
 These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs.
-Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020} as another attempt to generalize unital qubit channels.
+Similar studies a re Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020} as another attempt to generalize unital qubit channels.
 %
@@
 \par
-In the present work, we give a generalization of the qubit flip operations (bit, phase and bit-phase) to the 
+In this work we present a generalization of Pauli channels that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel.
+It is known that not every linear operation mapping density matrices into density matrices is a valid quantum operation
 [Role of completely positivity]
@@
 \par
-The paper is organized as follows, in section~\ref{sec:pce_maps}
+The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \textit{Pauli component erasing maps} (\pce{}), being the generalization of idempotent Pauli channels aforementioned.
+In section~\ref{sec:math} we derive the
 % }}}

### 2022-03-31 documentos/intro.tex
intro outline almost finished

@@
 The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \textit{Pauli component erasing maps} (\pce{}), being the generalization of idempotent Pauli channels aforementioned.
-In section~\ref{sec:math} we derive the
+In section~\ref{sec:math} we diagonalize analytically the Choi matrix for arbitrary \pce{} maps and characterize completely positive maps by interpreting \pce{} maps as discrete vector spaces.
+In section~\ref{sec:generators} we study generators of the semigroup structure of the set of \pce{} channels
+
+To finish, we conclude in section~\ref{sec:conclusions}.
 % }}}

### 2022-03-31 documentos/intro.tex
empujon abstract e intro

@@
 %
-The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space, is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics, and recently, even coarse graining~\cite{Duarte2017,pinedacg}.
+The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space, is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse graining~\cite{Duarte2017,pinedacg}.
 One of the main difficulties is that, similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
@@
 Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning the unital case, which non-trivial properties can be described using only $3$ parameters, which in turn form the tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
-For general finite-dimensional channels, several families of channels have been defined in order to explore the huge parametric space of channels.
-In~Ref.~\cite{nathanson2007pauli} channels defined as convex combinations of quantum-classical channels, in turn defined with mutually unbiased basis (MUB), are introduced.
+For the qubit case there are several studies concerning the unital case, which non-trivial properties can be described using only $3$ parameters, which in turn form the well known tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
+For general finite-dimensional channels, several families of channels have been defined.
+In~Ref.~\cite{nathanson2007pauli} authors define families of unital channels as convex combinations of quantum-classical channels, in turn defined with mutually unbiased basis (MUB), are introduced.
 These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs.
@@
 In section~\ref{sec:math} we diagonalize analytically the Choi matrix for arbitrary \pce{} maps and characterize completely positive maps by interpreting \pce{} maps as discrete vector spaces.
-In section~\ref{sec:generators} we study generators of the semigroup structure of the set of \pce{} channels
-
+In section~\ref{sec:generators} we study generators of the semigroup structure of the set of \pce{} channels, and we use them to derive meaningful physical interpretations of \pce{} channels in section~\ref{sec:kraus}, as well Kraus operators of the generators.
+%
 To finish, we conclude in section~\ref{sec:conclusions}.

### 2022-04-01 documentos/intro.tex

@@
 These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs.
-Similar studies a re Similarly, channels based on mutually unbiased measurements are studied in Ref.~\cite{Siudzinska2020} as another attempt to generalize unital qubit channels.
-%
-[Other references]
+Similarly, a generalization of Pauli channels based on mutually unbiased measurements is introduced and studied in Ref.~\cite{Siudzinska2020}.
+Other studies of channels beyond the qubit can be found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
 
 \par
-In this work we present a generalization of Pauli channels that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel.
-It is known that not every linear operation mapping density matrices into density matrices is a valid quantum operation
-[Role of completely positivity]
+In this work we present a generalization of Pauli channels (convex combinations of Pauli unitaries) that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel, to the case of $N$ qubits.
+The generalization is done by extending Pauli observables to \textit{Pauli strings} (tensor products of Pauli matrices), the resulting maps are unital and diagonal in the Pauli strings' basis.
+We call such maps \textit{Pauli component erasing maps} (\pce{}).
+We derive necessary and sufficient conditions for such mappings to be completely positive trace preserving, thus, showing which idempotent operations are valid quantum channels (\pce{} channels).
+Additionally, we characterize the algebraic properties of the set of \pce{} channels, showing that is equipped with a semigroup structure, which is later used to derive physical implementations.
 %
 \par
-The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \textit{Pauli component erasing maps} (\pce{}), being the generalization of idempotent Pauli channels aforementioned.
+The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \pce{} maps, being the generalization of idempotent Pauli channels aforementioned.
 In section~\ref{sec:math} we diagonalize analytically the Choi matrix for arbitrary \pce{} maps and characterize completely positive maps by interpreting \pce{} maps as discrete vector spaces.

### 2022-04-13 documentos/kraus.tex
Pequeñas anotaciones

@@
 To derive the aforementioned implementations, we exploit the existence of the
-PCEGs and their \textit{Kraus representation} (or operator-sum representation)
+PCEGs \janote{introducimos esta notación antes?} and their \textit{Kraus representation} (or operator-sum representation)
 which, for an arbitrary channel $\mcE$,  reads 
@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators of two qubit PCEG leads to
+Inspection of the Kraus operators of two qubit PCEGs leads to
 the ansatz that the Kraus operators for the generator of 
@@
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
-corresponding to the operation that leaves the component $\sigma_\alpha$
+corresponding to the operation that leaves the component $\sigma_\alpha$ \janote{$r_0$ and $r_\alpha$}
 invariant~\cite{nielsen_chuang_2011}.
 
-We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce a PCE. 
+We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce \janote{are indeed} a PCE. 
 Notice that 
 % \begin{equation}
-$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$,
+$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$ \janote{[see \Eref{eq:1}]},
 % \label{}
@@
 Next, consider the action of a channel with Kraus representation 
-\eqref{eq:kraus:PCE} on an $N$ qubit system:
+\eqref{eq:kraus:PCE} on a $N$-qubit system:
 \begin{align}
@@
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
-by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
+by Kraus operators  \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
 except for the first row, half of the matrix elements of each row is $+1$ and 
@@
 % hemos venido usando.}
-would have to be the same which is clearly false. Since there are $4^n$ different 
+would have to be the same, which is clearly false. Since there are $4^n$ different 
 $\vec \alpha$, this implies that all PCEG (plus the identity map) are in one to 

### 2022-04-18 documentos/intro.tex
Feed. You. Stuff. No time.

@@
 \section{Introduction} % {{{
+
+Quantum correlations \cite{}, including entanglement~\cite{}, are an important
+resource for a wide variate of tasks that include teleportation~\cite{},
+quantum computation~\cite{}, and others~\cite{}.
+However, this resource is also extremely delicate~\cite{}, specially 
+for multi-particle systems~ \cite{},  and important part
+of the efforts of the community implementing quantum technologies is 
+devoted to tackle this issue from an experimental \cite{} and
+theoretical \cite{} point of view. 
+The process by which quantum correlations are unintentionally dissipated
+is called decoherence~\cite{}
+One of the main tools to study the effects of decoherence are 
+quantum channels. \cpnote{Ver como pegar con el siguiente bicho. Quizá 
+modificar la primera frase del siguiente parrafo o pasar a este.}\par
 %
-The identification of families of quantum channels among the whole convex set of quantum channels associated to a Hilbert space, is crucial to understand quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse graining~\cite{Duarte2017,pinedacg}.
-One of the main difficulties is that, similar to quantum states, the parameters needed to describe quantum channels increases overwhelmingly rapid respect to the dimension of the Hilbert space.
-For a Hilbert space of dimension $d$, the space of quantum channels is parametrized with $d^4-d^2$ real parameters which are not fully independent (the complete positivity condition imposes the regions that physical meaning, see Ref.~\cite{zimansbook}).
-Therefore, even the qubit case is difficult to analyze having $12$ parameters corresponding to $6$ angles, $3$ components of the displacement vector and $3$ describing the compression of the Bloch sphere~\cite{ruskai}.
-Thus, understanding families of channels sharing a common property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning the unital case, which non-trivial properties can be described using only $3$ parameters, which in turn form the well known tetrahedron of Pauli channels~\cite{Rybar2012,ruskai,davalosdivisibility}.
-For general finite-dimensional channels, several families of channels have been defined.
-In~Ref.~\cite{nathanson2007pauli} authors define families of unital channels as convex combinations of quantum-classical channels, in turn defined with mutually unbiased basis (MUB), are introduced.
-These channels have properties in common with unital qubit channels with positive eigenvalues, and give a generalization of the Bloch sphere in terms of the generators of the MUBs.
-Similarly, a generalization of Pauli channels based on mutually unbiased measurements is introduced and studied in Ref.~\cite{Siudzinska2020}.
-Other studies of channels beyond the qubit can be found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
+The identification of families of quantum channels among the whole convex set
+of quantum channels associated to a Hilbert space, is crucial to understand
+quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
+dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
+graining~\cite{Duarte2017,pinedacg}. One of the main difficulties is that,
+similar to quantum states, the parameters needed to describe quantum channels
+increases overwhelmingly rapid respect to the dimension of the Hilbert space.
+For a Hilbert space of dimension $d$, the space of quantum channels is
+parametrized with $d^4-d^2$ real parameters which are not fully independent
+(the complete positivity condition imposes the regions that physical meaning,
+see Ref.~\cite{zimansbook})\cpnote{quiza quitar (QQ), o modificiar 
+a decir que el numero de parametros crece exponencialmente con el numero 
+de particulas.}. Therefore, even the
+qubit case is difficult to
+analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
+the displacement vector and $3$ describing the compression of the Bloch
+sphere~\cite{ruskai}\cpnote{QQ}. Thus, understanding families of channels sharing a common
+property usually gives a good insight about the jungle of quantum operations.
+For the qubit case there are several studies concerning the unital case, which
+non-trivial properties can be described using only $3$ parameters, which in
+turn form the well known tetrahedron of Pauli
+channels~\cite{Rybar2012,ruskai,davalosdivisibility}\cpnote{QQ}. For general
+finite-dimensional channels, several families of channels have been defined.
+In~Ref.~\cite{nathanson2007pauli} authors define families of unital channels as
+convex combinations of quantum-classical channels, in turn defined with
+mutually unbiased basis (MUB), are introduced. These channels have properties
+in common with unital qubit channels with positive eigenvalues, and give a
+generalization of the Bloch sphere in terms of the generators of the MUBs.
+Similarly, a generalization of Pauli channels based on mutually unbiased
+measurements is introduced and studied in Ref.~\cite{Siudzinska2020}. Other
+studies of channels beyond the qubit can be
+found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
+\cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
+mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
+discutir que familias mencionamos acá}
 
 \par
-In this work we present a generalization of Pauli channels (convex combinations of Pauli unitaries) that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel, to the case of $N$ qubits.
-The generalization is done by extending Pauli observables to \textit{Pauli strings} (tensor products of Pauli matrices), the resulting maps are unital and diagonal in the Pauli strings' basis.
-We call such maps \textit{Pauli component erasing maps} (\pce{}).
-We derive necessary and sufficient conditions for such mappings to be completely positive trace preserving, thus, showing which idempotent operations are valid quantum channels (\pce{} channels).
-Additionally, we characterize the algebraic properties of the set of \pce{} channels, showing that is equipped with a semigroup structure, which is later used to derive physical implementations.
+In this work we present a generalization of Pauli channels (convex combinations
+of Pauli unitaries) that are also idempotent, \ie{} the qubit flip operations
+(bit, phase and bit-phase), total depolarizing qubit channel and the identity
+channel, to the case of $N$ qubits. The generalization is done by extending
+Pauli observables to \textit{Pauli strings} (tensor products of Pauli
+matrices), the resulting maps are unital and diagonal in the Pauli strings'
+basis. We call such maps \textit{Pauli component erasing maps} (\pce{}). We
+derive necessary and sufficient conditions for such mappings to be completely
+positive trace preserving, thus, showing which idempotent operations are valid
+quantum channels (\pce{} channels). Additionally, we characterize the algebraic
+properties of the set of \pce{} channels, showing that is equipped with a
+semigroup structure, which is later used to derive physical implementations.
 %
 \par
-The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \pce{} maps, being the generalization of idempotent Pauli channels aforementioned.
-In section~\ref{sec:math} we diagonalize analytically the Choi matrix for arbitrary \pce{} maps and characterize completely positive maps by interpreting \pce{} maps as discrete vector spaces.
-In section~\ref{sec:generators} we study generators of the semigroup structure of the set of \pce{} channels, and we use them to derive meaningful physical interpretations of \pce{} channels in section~\ref{sec:kraus}, as well Kraus operators of the generators.
+The paper is organized as follows, in section~\ref{sec:pce_maps} we give a
+refreshing of quantum channels theory and the definition of \pce{} maps, being
+the generalization of idempotent Pauli channels aforementioned. In
+section~\ref{sec:math} we diagonalize analytically the Choi matrix for
+arbitrary \pce{} maps and characterize completely positive maps by interpreting
+\pce{} maps as discrete vector spaces. In section~\ref{sec:generators} we study
+generators of the semigroup structure of the set of \pce{} channels, and we use
+them to derive meaningful physical interpretations of \pce{} channels in
+section~\ref{sec:kraus}, as well Kraus operators of the generators.
 %

### 2022-04-19 documentos/intro.tex
implemento comentarios de Francois y dejo comentarios a Carlos

@@
 similar to quantum states, the parameters needed to describe quantum channels
-increases overwhelmingly rapid respect to the dimension of the Hilbert space.
+increases overwhelmingly rapidly with the dimension of the Hilbert space.
 For a Hilbert space of dimension $d$, the space of quantum channels is
 parametrized with $d^4-d^2$ real parameters which are not fully independent
-(the complete positivity condition imposes the regions that physical meaning,
+(the complete positivity condition imposes the regions that have physical meaning,
 see Ref.~\cite{zimansbook})\cpnote{quiza quitar (QQ), o modificiar 
 a decir que el numero de parametros crece exponencialmente con el numero 
-de particulas.}. Therefore, even the
+de particulas.}\ddnote{no crece exponencialmente.
+La expresión no me parece complicada como para dejarla, sospecho que hay lectores que aprenderan algo interesante de aqui, y espero eso los atrape.
+Ojo tambien con que la observacion de que son muchos parametros que no son completamente libres, es lo que hace no-trivial el problema matematico que resolvemos aqui.}.
+Therefore, even the
 qubit case is difficult to
@@
 the displacement vector and $3$ describing the compression of the Bloch
-sphere~\cite{ruskai}\cpnote{QQ}. Thus, understanding families of channels sharing a common
-property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning the unital case, which
+sphere~\cite{ruskai}\cpnote{QQ}. Thus, describing in detail small families of channels having a given property may provide insight into the jungle of quantum operations.
+For the qubit case there are several studies concerning the unital case, for which
 non-trivial properties can be described using only $3$ parameters, which in
@@
 finite-dimensional channels, several families of channels have been defined.
-In~Ref.~\cite{nathanson2007pauli} authors define families of unital channels as
+In~Ref.~\cite{nathanson2007pauli} the authors define families of unital channels as
 convex combinations of quantum-classical channels, in turn defined with
@@
 mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
-discutir que familias mencionamos acá}
+discutir que familias mencionamos acá}\ddnote{las siglas si están de mas, puede que simplemente compactemos los trabajos con MUBs y MUMs con todas las citas genericas donde se estudian generlizacones, sin embargo, ese trabajo de MUBs fue importante para nosotros y al final si identificamos un overlap.
+Ademas las MUBs son conocidas, y siento que si la gente ve cosas familiaires se va a interesar.}
 

### 2022-04-19 documentos/intro.tex
comentarios a la intro y algunas referencias

--- 2022-04-18 documentos/intro.tex
@@
 
-Quantum correlations \cite{}, including entanglement~\cite{}, are an important
-resource for a wide variate of tasks that include teleportation~\cite{},
+Quantum correlations \cite{}, including entanglement~\cite{Horodecki}, are an important
+resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
 quantum computation~\cite{}, and others~\cite{}.
@@
 The process by which quantum correlations are unintentionally dissipated
-is called decoherence~\cite{}
+is called decoherence~\cite{}.
 One of the main tools to study the effects of decoherence are 
@@
 modificar la primera frase del siguiente parrafo o pasar a este.}\par
+\ddnote{Para pegar los dos parrafos, propongo la siguiente modificacion a la primera frase}.
+{\blue In fact, more generally, quantum channels model quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
+dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
+graining~\cite{Duarte2017,pinedacg}. [...] Luego continuar con el resto}
 %
@@
 similar to quantum states, the parameters needed to describe quantum channels
-increases overwhelmingly rapid respect to the dimension of the Hilbert space.
-For a Hilbert space of dimension $d$, the space of quantum channels is
-parametrized with $d^4-d^2$ real parameters which are not fully independent
-(the complete positivity condition imposes the regions that physical meaning,
-see Ref.~\cite{zimansbook})\cpnote{quiza quitar (QQ), o modificiar 
+increases overwhelmingly rapidly with the dimension of the Hilbert space.
+Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.\cpnote{quiza quitar (QQ), o modificiar 
 a decir que el numero de parametros crece exponencialmente con el numero 
-de particulas.}. Therefore, even the
+de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
 qubit case is difficult to
@@
 the displacement vector and $3$ describing the compression of the Bloch
-sphere~\cite{ruskai}\cpnote{QQ}. Thus, understanding families of channels sharing a common
-property usually gives a good insight about the jungle of quantum operations.
-For the qubit case there are several studies concerning the unital case, which
+sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. Thus, describing in detail small families of channels having a given property may provide insight into the jungle of quantum operations.
+For the qubit case there are several studies concerning the unital case, for which
 non-trivial properties can be described using only $3$ parameters, which in
 turn form the well known tetrahedron of Pauli
-channels~\cite{Rybar2012,ruskai,davalosdivisibility}\cpnote{QQ}. For general
+channels~\cite{Rybar2012,ruskai,davalosdivisibility}\cpnote{QQ}\ddnote{quitemoslo}. For general
 finite-dimensional channels, several families of channels have been defined.
-In~Ref.~\cite{nathanson2007pauli} authors define families of unital channels as
-convex combinations of quantum-classical channels, in turn defined with
-mutually unbiased basis (MUB), are introduced. These channels have properties
+In~Ref.~\cite{nathanson2007pauli} the authors define families of unital channels as
+convex combinations of quantum-classical channels, having properties
 in common with unital qubit channels with positive eigenvalues, and give a
-generalization of the Bloch sphere in terms of the generators of the MUBs.
+generalization of the Bloch sphere.
+{\blue We will show later that some of the channels studied here are also quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada mejor en tanto a la escritura.
+Propongo omitirla, despues se volvera a mencionar esto pero en donde corresponde.}
 Similarly, a generalization of Pauli channels based on mutually unbiased
@@
 mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
-discutir que familias mencionamos acá}
+discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}
 

### 2022-04-19 documentos/intro.tex
frase

@@
 \ddnote{Para pegar los dos parrafos, propongo la siguiente modificacion a la primera frase}.
-{\blue In fact, more generally, quantum channels model quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
+{\blue More generally, quantum channels model quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
 dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse

### 2022-04-20 documentos/intro.tex
referencias

@@
 
-Quantum correlations \cite{}, including entanglement~\cite{Horodecki}, are an important
+Quantum correlations~\cite{Ollivier2001}, including entanglement~\cite{Horodecki}, are an important
 resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
-quantum computation~\cite{}, and others~\cite{}.
-However, this resource is also extremely delicate~\cite{}, specially 
+quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{}.
+However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
 for multi-particle systems~ \cite{},  and important part
@@
 The process by which quantum correlations are unintentionally dissipated
-is called decoherence~\cite{}.
+is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
 One of the main tools to study the effects of decoherence are 

### 2022-04-20 documentos/intro.tex
things occurred

@@
 
-Quantum correlations~\cite{Ollivier2001}, including entanglement~\cite{Horodecki}, are an important
+Quantum correlations~\cite{Ollivier2001}, including
+entanglement~\cite{Horodecki}, are an important
 resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
@@
 One of the main tools to study the effects of decoherence are 
-quantum channels. \cpnote{Ver como pegar con el siguiente bicho. Quizá 
-modificar la primera frase del siguiente parrafo o pasar a este.}\par
-\ddnote{Para pegar los dos parrafos, propongo la siguiente modificacion a la primera frase}.
-{\blue More generally, quantum channels model quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
+quantum channels. Quantum channels can describe quantum
+noise~\cite{davalosdivisibility,ruskai}, open quantum systems
 dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
-graining~\cite{Duarte2017,pinedacg}. [...] Luego continuar con el resto}
+graining~\cite{Duarte2017,pinedacg}. 
 %
-The identification of families of quantum channels among the whole convex set
-of quantum channels associated to a Hilbert space, is crucial to understand
-quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
-dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
-graining~\cite{Duarte2017,pinedacg}. One of the main difficulties is that,
-similar to quantum states, the parameters needed to describe quantum channels
+% The identification of families of quantum channels among the whole convex set
+% of quantum channels associated to a Hilbert space, is crucial to understand
+% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
+% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
+% graining~\cite{Duarte2017,pinedacg}. 
+One of the main difficulties to characterize quantum channels is that,
+similar to quantum states, the parameters needed to describe them
 increases overwhelmingly rapidly with the dimension of the Hilbert space.
-Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.\cpnote{quiza quitar (QQ), o modificiar 
-a decir que el numero de parametros crece exponencialmente con el numero 
-de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
-qubit case is difficult to
-analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
-the displacement vector and $3$ describing the compression of the Bloch
-sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. Thus, describing in detail small families of channels having a given property may provide insight into the jungle of quantum operations.
+%
+Moreover, such parameters are constrained in a complicated way by 
+physical conditions, such as complete positivity ~\cite{zimansbook}.
+% Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.
+% 
+% \cpnote{quiza quitar (QQ), o modificiar 
+% a decir que el numero de parametros crece exponencialmente con el numero 
+% de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
+% qubit case is difficult to
+% analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
+% the displacement vector and $3$ describing the compression of the Bloch
+% sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. 
+Describing in detail families of channels having a given property provides
+insight into the jungle of quantum operations.
 For the qubit case there are several studies concerning the unital case, for which
@@
 turn form the well known tetrahedron of Pauli
-channels~\cite{Rybar2012,ruskai,davalosdivisibility}\cpnote{QQ}\ddnote{quitemoslo}. For general
-finite-dimensional channels, several families of channels have been defined.
-In~Ref.~\cite{nathanson2007pauli} the authors define families of unital channels as
-convex combinations of quantum-classical channels, having properties
-in common with unital qubit channels with positive eigenvalues, and give a
+channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
+% For general
+% finite-dimensional channels, several families of channels have been defined.
+More generally, in~Ref.~\cite{nathanson2007pauli} the authors study families of 
+convex combinations of quantum-classical channels that relate to
+% have a close relation with 
+unital qubit channels with positive eigenvalues, and give a
 generalization of the Bloch sphere. 
-{\blue We will show later that some of the channels studied here are also quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada mejor en tanto a la escritura.
-Propongo omitirla, despues se volvera a mencionar esto pero en donde corresponde.}
+% {\blue We will show later that some of the channels studied here are also
+% quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada
+% mejor en tanto a la escritura. Propongo omitirla, despues se volvera a
+% mencionar esto pero en donde corresponde.}
 Similarly, a generalization of Pauli channels based on mutually unbiased
@@
 found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
-\cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
-mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
-discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}
+% \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
+% mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
+% discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}
 
 \par
-In this work we present a generalization of Pauli channels (convex combinations
-of Pauli unitaries) that are also idempotent, \ie{} the qubit flip operations
-(bit, phase and bit-phase), total depolarizing qubit channel and the identity
-channel, to the case of $N$ qubits. The generalization is done by extending
+In this work we present a generalization of idempotent Pauli channels, \ie{}
+the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit
+channel and the identity channel, to the case of $N$ qubits. 
+% \cpnote{Mencionar decoherencia} 
+The generalization is done by extending
 Pauli observables to \textit{Pauli strings} (tensor products of Pauli
 matrices), the resulting maps are unital and diagonal in the Pauli strings'
-basis. We call such maps \textit{Pauli component erasing maps} (\pce{}). We
+basis.
+Moreover, these channels describe decoherence in a similar way as the aforementioned
+single-qubit channels describe decoherence. \cpnote{Si alguien mejora esta
+frase, de lujo}
+We call such maps \textit{Pauli component erasing} (\pce{}) maps . We
 derive necessary and sufficient conditions for such mappings to be completely
@@
 \par
-The paper is organized as follows, in section~\ref{sec:pce_maps} we give a
-refreshing of quantum channels theory and the definition of \pce{} maps, being
-the generalization of idempotent Pauli channels aforementioned. In
+The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
+the properties of quantum channels needed to proceed with the definition 
+of 
+% the tools to unders
+% refreshing of quantum channels theory and the definition of 
+\pce{} maps. In
 section~\ref{sec:math} we diagonalize analytically the Choi matrix for

### 2022-04-20 documentos/intro.tex
referencias todas intro

@@
 
-Quantum correlations~\cite{Ollivier2001}, including
+Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195, PhysRevLett.126.170404,Ollivier2001}, including
 entanglement~\cite{Horodecki}, are an important
 resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
-quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{}.
+quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
-for multi-particle systems~ \cite{},  and important part
+for multi-particle systems~\cite{Horodecki},  and important part
 of the efforts of the community implementing quantum technologies is 
-devoted to tackle this issue from an experimental \cite{} and
-theoretical \cite{} point of view. 
+devoted to tackle this issue from an experimental \cite{Mooney_2021,Briegel1998} and
+theoretical \cite{Bennett1996,Georgescu2020,RevModPhys.87.307} point of view. 
 The process by which quantum correlations are unintentionally dissipated

### 2022-04-20 documentos/pce.tex
Comentario de potencial incosistencia de nombre de \valpha
needs more cow bell

@@
 In this section we introduce the family of Pauli component erasing (PCE)
-\cpnote{Revisar despues de escribir la intro que no se ha introducido la sigla}
 maps. Let us start our discussion with a brief review of several basic concepts
@@
 where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$
+\janote{revisar si en el resto del artículo siempre le llamamos a $\valpha$
+`vector index'. A veces le poníamos `multi-index'}
 and $\alpha_i=0,1,2,3$. These hermitian operators form an orthogonal 
@@
 from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
-\eref{eq:N_qubits_rho}. For a given PCE, we shall fill  \janote{Jose Alfredo quizá itera}
+\eref{eq:N_qubits_rho}. For a given PCE, we shall fill  
 the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 

### 2022-04-21 documentos/intro.tex
flips

@@
 In this work we present a generalization of idempotent Pauli channels, \ie{}
-the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit
+the qubit flip operations (bit, phase and bit-phase {\blue when the flip probability is $1/2$}), total depolarizing qubit
 channel and the identity channel, to the case of $N$ qubits. 

### 2022-04-21 documentos/pce.tex
flips

@@
 These operations are the identity map, the completely depolarizing channel
-($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip
+($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip {\blue (with flip probability of $1/2$)}
 channels~\cite{chuangbook}, 

### 2022-04-21 documentos/kraus.tex
bullet points y pequeñas correcciones y adiciones

@@
 invariant~\cite{nielsen_chuang_2011}.
+\ddnote{agrego lo de los flips aqui}{\blue Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$.
+In fact, tracing out all particles except particle $k$ gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}).
+And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel.}
 
@@
 % \begin{equation}
-$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$ \janote{[see \Eref{eq:1}]},
+$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$, see~\Eref{eq:1},
 % \label{}
@@
 
-Notice also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
+Observe	 also that a different choice of $\vec \alpha$ in \eref{eq:kraus:PCE}
 leads to different channels. This follows from the fact that if two channels were

### 2022-04-21 documentos/intro.tex
bullet points y pequeñas correcciones y adiciones
hoo boy

--- 2022-04-20 documentos/intro.tex
@@
 In this work we present a generalization of idempotent Pauli channels, \ie{}
-the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit
+the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
 channel and the identity channel, to the case of $N$ qubits. 
@@
 arbitrary \pce{} maps and characterize completely positive maps by interpreting
-\pce{} maps as discrete vector spaces. In section~\ref{sec:generators} we study
+\pce{} maps as finite vector spaces. In section~\ref{sec:generators} we study
 generators of the semigroup structure of the set of \pce{} channels, and we use

### 2022-04-21 documentos/pce.tex
hoo boy

--- 2022-04-20 documentos/pce.tex
@@
 These operations are the identity map, the completely depolarizing channel
-($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip
+($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip (with flip probability of $1/2$)
 channels~\cite{chuangbook}, 

### 2022-04-23 documentos/intro.tex
Rev_App

@@
 entanglement~\cite{Horodecki}, are an important
-resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
+resource for a wide variate \afnote{(variety)} of tasks that include teleportation~\cite{PhysRevLett.70.1895},
 quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
@@
 unital qubit channels with positive eigenvalues, and give a
-generalization of the Bloch sphere. 
+generalization of the Bloch sphere \afnote{seria bueno mencionar en que sentido es dicha generalización.}. 
 % {\blue We will show later that some of the channels studied here are also
@@
 frase, de lujo}
-We call such maps \textit{Pauli component erasing} (\pce{}) maps . We
+\afnote{In addition, these channels describe the decoherence process in a similar way as the aforementioned
+ones for the single-qubit case.}
+We call such maps \textit{Pauli component erasing} (\pce{}) maps \afnote{From now on we refer to them as \textit{Pauli component erasing} (\pce{}) maps}. We
 derive necessary and sufficient conditions for such mappings to be completely
-positive trace preserving, thus, showing which idempotent operations are valid
+positive trace preserving \afnote{(CPTP)}, thus, showing which idempotent operations are valid
 quantum channels (\pce{} channels). Additionally, we characterize the algebraic
-properties of the set of \pce{} channels, showing that is equipped with a
+properties of the set of \pce{} channels, showing that \afnote{it} is equipped with a
 semigroup structure, which is later used to derive physical implementations.
@@
 arbitrary \pce{} maps and characterize completely positive maps by interpreting
-\pce{} maps as finite vector spaces. In section~\ref{sec:generators} we study
-generators of the semigroup structure of the set of \pce{} channels, and we use
+\pce{} maps as finite vector spaces \afnote{The section~\ref{sec:math} is devoted to present an analytical diagonalization of the the Choi matrix for
+arbitrary \pce{} maps, and to provide a characterization of completely positive maps by interpreting
+\pce{} maps as finite vector spaces}. In section~\ref{sec:generators} we study
+generators of the semigroup structure of the set of \pce{} channels, and use
 them to derive meaningful physical interpretations of \pce{} channels in
@@
 %
-To finish, we conclude in section~\ref{sec:conclusions}.
+\afnote{We study the
+generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
+them to derive meaningful physical interpretations of \pce{} channels in
+section~\ref{sec:kraus}, as well Kraus operators of the generators.}
+% 
+\afnote{No entendí que se quiere decir con ``as well Kraus operators of the generators"} To finish, we conclude in section~\ref{sec:conclusions}.
 % }}}

### 2022-04-23 documentos/kraus.tex
Rev_App

@@
 experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
-Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
+Moreover, these processes lead to a monotonically \afnote{monotonic (continuous)} lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically \afnote{(continuous)} decreasing of the determinant, see Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
-some Markovian processes. In this section we prove what in fact they are, and
+some Markovian processes. In this section we prove what \afnote{that} in fact they are, and
 give two examples of Markovian implementations.
@@
 dissipative process. The second, in identifying each \pce{} channel as fixed
-points of some memory-less collision model.
+points of some memory-less collision model \afnote{The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
+points of some memory-less collision model }.
 
@@
 To derive the aforementioned implementations, we exploit the existence of the
-PCEGs \janote{introducimos esta notación antes?} and their \textit{Kraus representation} (or operator-sum representation)
+PCEGs \janote{introducimos esta notación antes?} \afnote{(acabo de colocarla en el 3er parrafo de la sección de generadores)} and their \textit{Kraus representation} (or operator-sum representation)
 which, for an arbitrary channel $\mcE$,  reads 
@@
 $\mcG_{\vec \alpha}$ are 
+\afnote{By inspection, it is easy to prove that two qubit PCEGs leads to
+the ansatz that the Kraus operators for the generator of 
+$\mcG_{\vec \alpha}$ are}
 \begin{equation}
@@
 \end{equation}
-since the Kraus operators corresponding to one single qubit PCEs are 
+since the Kraus operators corresponding to one \afnote{a} single qubit PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
@@
 \ddnote{agrego lo de los flips aqui}{\blue Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$.
-In fact, tracing out all particles except particle $k$ gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}).
-And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel.}
+In fact, tracing out all particles except particle $k$ \afnote{...except the $k-$th one} gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}).
+And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel \afnote{with weight $1/2$}.}
 
@@
 % \end{equation}
-which in turn imply that 
+which in turn imply \afnote{implies} that 
 \begin{equation}
@@
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
-by Kraus operators  \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
+by \afnote{the} Kraus operators \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
 except for the first row, half of the matrix elements of each row is $+1$ and 
@@
 fixed point of some decoherence process, starting with PCEGs and 
-then generalizing to more general channels. 
+then generalizing \afnote{extending} to more general channels. 
 % Me gustaria modificar esta
@@
 time-homogeneous Markovian process, those are always characterized by some
-Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec
-\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard
+Lindblad generator~\cite{lindblad} \afnote{Me parece que se podría conectar mejor esta última frase (pero no pude XD)}. The Lindblad generator of $\mcG_{\vec
+\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with \afnote{by} the standard
 procedure,  
@@
 We show now that PCE channels can also be implemented with \textit{simple
-collision models}~\cite{Ziman2010}. To do this, observe that using the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
+collision models}~\cite{Ziman2010}. To do this, observe that using \afnote{by employing} the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
 be implemented using an unitary over the system and an
@@
 \mcG_{\vec \alpha_M} \right\}$. For this we can define an environment
-consisting of $M$ qubits initially in the state $\left( \projj{0}
+consisting of \afnote{on} $M$ qubits initially in the state $\left( \projj{0}
 \right)^{\otimes M}$, or equivalently one qubit with the additional assumption
 that its state is reset to $\ket{0}$ after each collision (memory-less
-collisions). The collision with the $k\text{th}$ particle is described by
+collisions). The collision with the $k\text{th}$ \afnote{$k\text{-th}$} particle is described by
 $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$
@@
 \end{equation}
-where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be any.
+where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits \afnote{over the whole ancillary qubits}.
+Notice that as PCEGs commute, the order of the collisions can be any \afnote{the order of the collisions is irrelevant}.
 % \begin{itemize}

### 2022-04-23 documentos/proofdiagonalization.tex
Comentario sobre duplicidad de a
Rev_App

@@
 \subsection{Single qubit} % {{{
-\ddnote{Alejo, por fa revise q no se me fue un typo con el asunto de mod 2, ya corregí toda la notación y removi los otros comentarios, que ya fueron aclarados en la reunion y trataban de lo mismo}
+\ddnote{Alejo, por fa revise q no se me fue un typo con el asunto de mod 2, ya corregí toda la notación y removi los otros comentarios, que ya fueron aclarados en la reunion y trataban de lo mismo} \afnote{Listo, todo en orden.}
 In order to simplify the derivation of the relations, let us employ pairs of
 binary indices instead of a single quaternary, i.e. $\alpha\to j +2 k$. For
-the sake of clarity, we will use Latin symbols for binary indices, and
+the sake of clarity, we will use \afnote{we use} Latin symbols for binary indices, and
 reserve Greek letters for quaternary ones. 
@@
 % thanks to a simplification in the argument of the power of $-1$. To continue, 
-since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $ \ddnote{Alejo, por fas checa esto, se me hace curioso que el modulo 2 solo este solo en la segunda suma del exponente}. To continue, we 
+since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $ \ddnote{Alejo, por fas checa esto, se me hace curioso que el modulo 2 solo este solo en la segunda suma del exponente} \afnote{Efectivamente solo tiene el mod2 en la segunda, sin embargo da exactamente lo mismo incluso si no existiera el mod2, pues la base es la misma (-1).
+En el caso de Weyl si hay que tener extremo cuidado con eso.}.
+To continue, we
 use the relation between computational and Pauli elements [\eref{PauToComp}],
@@
 \right),
-\end{equation}
+\end{equation}\janote{esta matriz ya está en el cuerpo principal del artículo. Sugiero quitar de acá.}
 instead of $H\otimes H$. This can be done due to the fact
@@
 $\kket{\sigma_{\vec{k}\vec{l} }}$.
-}
+} \afnote{perfecto}
 % \begin{equation}

### 2022-04-23 documentos/quantum_classical.tex
Rev_App

@@
 \ddnote{Alguien revise este apendice, tiene solo una iterada}
-A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space.
+A Quantum-classical (QC) channel is defined \afnote{by} using an orthonormal basis in the Hilbert space.
 Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC channel associated to $B$ is
@@
 Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
-We will prove that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
+\afnote{Now we proceed to demonstrate that...} We will prove that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
 
@@
 \end{equation}
-it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there only positive terms in the sum, and $2^N$ of them are already equal to $1$.
+it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there \afnote{are} only positive terms in the sum, and $2^N$ of them are already equal to $1$.
 Therefore,
@@
 it is easy to check that the latter is a projector only if $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=0$.
-Since there are exactly $2^N$ elements of the form $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}$ with $\sigma_{\vec k} \in \text{set}(B)$, the channel $\mcE^{\text{QC}}_B$ is \pce{} with $2^N$ $1$s on its diagonal.
+Since there are exactly $2^N$ elements of the form $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}$ with $\sigma_{\vec k} \in \text{set}(B)$, \afnote{then} the channel $\mcE^{\text{QC}}_B$ is \pce{} with $2^N$ $1$s on its diagonal.

### 2022-05-03 documentos/intro.tex
Give me a break, it's 2am.  But it works now.

--- 2022-04-21 documentos/intro.tex
@@
 
-Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195, PhysRevLett.126.170404,Ollivier2001}, including
-entanglement~\cite{Horodecki}, are an important
-resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
-quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
+Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195,
+PhysRevLett.126.170404,Ollivier2001}, including entanglement~\cite{Horodecki},
+are an important resource for a wide variety of tasks that
+include teleportation~\cite{PhysRevLett.70.1895}, quantum
+computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
@@
 % 
-% \cpnote{quiza quitar (QQ), o modificiar 
-% a decir que el numero de parametros crece exponencialmente con el numero 
-% de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
-% qubit case is difficult to
-% analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
-% the displacement vector and $3$ describing the compression of the Bloch
-% sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. 
 Describing in detail families of channels having a given property provides
@@
 Pauli observables to \textit{Pauli strings} (tensor products of Pauli
-matrices), the resulting maps are unital and diagonal in the Pauli strings'
+matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and diagonal in the Pauli strings'
 basis.

### 2022-05-03 documentos/intro.tex
Is there an award for this?

@@
 Pauli observables to \textit{Pauli strings} (tensor products of Pauli
-matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and diagonal in the Pauli strings'
-basis.
-Moreover, these channels describe decoherence in a similar way as the aforementioned
-single-qubit channels describe decoherence. \cpnote{Si alguien mejora esta
-frase, de lujo}
-\afnote{In addition, these channels describe the decoherence process in a similar way as the aforementioned
-ones for the single-qubit case.}
-We call such maps \textit{Pauli component erasing} (\pce{}) maps \afnote{From now on we refer to them as \textit{Pauli component erasing} (\pce{}) maps}. We
+matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and
+diagonal in the Pauli strings' basis.
+In addition, these channels describe the decoherence process in a similar way
+as the aforementioned
+ones for the single-qubit case.
+From now on we refer to these maps as \textit{Pauli component erasing} (\pce{})
+maps. We
 derive necessary and sufficient conditions for such mappings to be completely
-positive trace preserving \afnote{(CPTP)}, thus, showing which idempotent operations are valid
+positive trace preserving, thus, showing which idempotent operations are valid
 quantum channels (\pce{} channels). Additionally, we characterize the algebraic
-properties of the set of \pce{} channels, showing that \afnote{it} is equipped with a
-semigroup structure, which is later used to derive physical implementations.
+properties of the set of \pce{} channels, showing that it is equipped
+with a semigroup structure, which is later used to derive physical
+implementations.
 %
@@
 arbitrary \pce{} maps and characterize completely positive maps by interpreting
-\pce{} maps as finite vector spaces \afnote{The section~\ref{sec:math} is devoted to present an analytical diagonalization of the the Choi matrix for
-arbitrary \pce{} maps, and to provide a characterization of completely positive maps by interpreting
-\pce{} maps as finite vector spaces}. In section~\ref{sec:generators} we study
-generators of the semigroup structure of the set of \pce{} channels, and use
+\pce{} maps as finite vector spaces. 
+We study the
+generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
 them to derive meaningful physical interpretations of \pce{} channels in
@@
 % 
-\afnote{We study the
-generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
-them to derive meaningful physical interpretations of \pce{} channels in
-section~\ref{sec:kraus}, as well Kraus operators of the generators.}
-% 
-\afnote{No entendí que se quiere decir con ``as well Kraus operators of the generators"} To finish, we conclude in section~\ref{sec:conclusions}.
+To finish, we conclude in section~\ref{sec:conclusions}.
 % }}}

### 2022-05-03 documentos/generators.tex
section labels
Rev_App
gave up and used tables.
multiindex

@@
 \section{Generators} % {{{
+\label{sec:generators}
 %\todo{Francois escribe una primera version del primer punto, y luego quizá Jose
@@
 
-PCE generators may be characterized by its local action on every qubit 
-in the system. This action can be encoded using a vector index $\vec\alpha$, 
+PCE generators \afnote{(hereafter PCEGs)} may be characterized by its local action on every qubit 
+in the system. This action can be encoded using a multi-index $\vec\alpha$, 
 as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
@@
 A reflection symmetry is identified for PCE generators.
-Consider the map $\Sigma^{(k)}$ that reflects an index $\valpha$ with 
+Consider the map $\Sigma^{(k)}$ that reflects an multi-index $\valpha$ with 
 respect to the $k$-th axis. This map leaves all components of $\valpha$
@@
 \valpha=\Sigma^{(k)}(\valpha) \oplus \Sigma^{(k)}(\vec0). 
-\label{eq:Sigma}
+\label{eq:Sigma:oplus}
 \end{equation}

### 2022-05-03 documentos/generators.tex
comentarios

@@
 as in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
-vector indices may be uniquely related to each of the PCE generators
+multi-indices may be uniquely related to each of the PCE generators
 and thus denoted as $\mcG_{\vec\alpha}$.

### 2022-05-03 documentos/generators.tex
Merging the merge

@@
 
-PCE generators \afnote{(hereafter PCEGs)} may be characterized by its local action on every qubit 
+PCE generators (hereafter PCEGs) may be characterized by its local
+action on every qubit 
 in the system. This action can be encoded using a multi-index $\vec\alpha$, 
@@
 multi-indices may be uniquely related to each of the PCE generators
-and thus denoted as $\mcG_{\vec\alpha}$.
+and thus denoted as $\mcG_{\vec\alpha}$, see figures \ref{fig:A_and_PCEGs_connection} and \ref{fig:appex:twoQ_PCEGs}.
 % \cpnote{
@@
 \sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
-\janote{referir a fig 5} For single qubits, the identity corresponds to $\mcG_0$, shown in 
+For single qubits, the identity corresponds to $\mcG_0$, shown in 
 \fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
@@
 symmetric or anti-symmetric under reflection.
-\janote{Propuesta de figura para mostrar que generadores 
-y la a obedecen las mismas simetrías.}
+\cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
 }

### 2022-05-03 documentos/generators.tex
<<<<<<<<<<<<<<< HEAD

@@
 and thus denoted as $\mcG_{\vec\alpha}$, see figures \ref{fig:A_and_PCEGs_connection} and \ref{fig:appex:twoQ_PCEGs}.
-% \cpnote{
 The proof is simplified if one uses the Kraus representation developed in 
@@
 \fref{fig:one:qubit:examples}(c).
-% }
 The 2-qubits PCE generator represented in subfigure (c)
@@
 
-\cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
+% \cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
 % 
@@
 \centering
+\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
+\pgfmathsetmacro{\unitstep}{1.5}
+% % Coordenadas   {{{
+% \node at (-0.6,0.5) {(a)} ;
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
+% \begin{scope}[shift={(0,-1)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
+% \end{scope}
+% \begin{scope}[shift={(0,-2)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
+% \end{scope}
+% \begin{scope}[shift={(0,-3)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
+% \end{scope} 
+% \draw (0,-3) rectangle (1,1); 
+% % }}}
+\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
+% \begin{scope}[shift={(\unitstep*2,0)}]
+\node at (-0.6,0.5) {(b)} ;
+\fill[black] (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
+\node at (-0.6,0.5) {(c)} ;
+\fill[black] (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
+\node at (-0.6,0.5) {(d)} ;
+\fill[black] (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\end{scope} % }}}
+\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
+\node at (-0.6,0.5) {(e)} ;
+\fill[black] (0,0) rectangle (1,1);
+% \draw (0,0) rectangle (1,1);
+\draw[black!10] (0,0) rectangle (1,1);
+\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+\draw (0,-3) rectangle (1,1); 
+\end{scope} % }}}
+\end{tikzpicture} % }}}
 \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
@@
 From the tensor power of matrix $a$ one can infer the components $\{\taus\}$ of a PCE
-generator $\pceg$ by taking row (or column) $\alpha$ of $A$ and replacing
+generator $\pceg$ by taking row (or column) $\valpha$ of $A$ and replacing
 $-1$ with $0$. 
@@
 this connection for the single qubit case.
-
-% \cpnote{Sienot que no tiene flujo. Quizá se le pueda dar flujo usando el final 
-% del primer parrafo}
 

### 2022-05-03 documentos/generators.tex
Too tired to write descriptive message
arrrggghhhhh fixed!

@@
 \begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
-\pgfmathsetmacro{\unitstep}{1.5}
+\node at (-2.5,-0.9) {
+$
+\begin{pmatrix}
+1 & 1 & 1 & 1\\
+1 & 1 & -1 & -1\\
+1 & -1 & 1 & -1\\
+1 & -1 & -1 & 1
+\end{pmatrix}
+\longleftrightarrow
+% \mcG_1
+$
+} ;
+\pgfmathsetmacro{\unitstep}{1.2}
 % % Coordenadas   {{{
@@
 % \begin{scope}[shift={(\unitstep*2,0)}]
-\node at (-0.6,0.5) {(b)} ;
+\node at (0.5,-3.5) {$\mcG_0$} ;
+% \node at (-0.6,0.5) {(b)} ;
 \fill[black] (0,0) rectangle (1,1);
@@
 \begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
-\node at (-0.6,0.5) {(c)} ;
+\node at (0.5,-3.5) {$\mcG_1$} ;
 \fill[black] (0,0) rectangle (1,1);
@@
 % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
@@
 \begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
-\node at (-0.6,0.5) {(d)} ;
+\node at (0.5,-3.5) {$\mcG_2$} ;
+% \node at (-0.6,0.5) {(d)} ;
 \fill[black] (0,0) rectangle (1,1);
@@
 % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
@@
 \begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
-\node at (-0.6,0.5) {(e)} ;
+\node at (0.5,-3.5) {$\mcG_3$} ;
+% \node at (-0.6,0.5) {(e)} ;
 \fill[black] (0,0) rectangle (1,1);
@@
 % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
@@
 \end{tikzpicture} % }}}
-\includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
-\caption{Connection between rows and columns of $a$ and single qubit PCE generators.
-The rows or columns of $a$ and the diagrams of the generators are either 
-symmetric or anti-symmetric under reflection.
-\cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
+% \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
+\caption{Connection between rows and columns of $a$ and single qubit PCE
+generators. We also include the corresponding 
+labels $\mcG_\alpha$ of the generators.
+% The rows or columns of $a$ and the diagrams of the generators are either 
+% symmetric or anti-symmetric under reflection.
+% \cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
 }

### 2022-05-03 documentos/kraus.tex

@@
 experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
-Moreover, these processes lead to a monotonically \afnote{monotonic (continuous)} lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically \afnote{(continuous)} decreasing of the determinant, see Ref.~\cite{cirac}).
+Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
-some Markovian processes. In this section we prove what \afnote{that} in fact they are, and
+some Markovian processes. In this section we prove that in fact they are, and
 give two examples of Markovian implementations.
 %
-The first
-one consist in identifying each \pce{} channel as a fixed point of some pure
-dissipative process. The second, in identifying each \pce{} channel as fixed
-points of some memory-less collision model \afnote{The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
-points of some memory-less collision model }.
+The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
+points of some memory-less collision model.
 

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 To derive the aforementioned implementations, we exploit the existence of the
-PCEGs \janote{introducimos esta notación antes?} \afnote{(acabo de colocarla en el 3er parrafo de la sección de generadores)} and their \textit{Kraus representation} (or operator-sum representation)
+PCEGs and their \textit{Kraus representation} (or operator-sum representation)
 which, for an arbitrary channel $\mcE$,  reads 

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators of two qubit PCEGs leads to
+Inspection of the Kraus operators for one qubit PCEGs leads to
 the ansatz that the Kraus operators for the generator of 
 $\mcG_{\vec \alpha}$ are 
-\afnote{By inspection, it is easy to prove that two qubit PCEGs leads to
-the ansatz that the Kraus operators for the generator of 
-$\mcG_{\vec \alpha}$ are}
 \begin{equation}

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators for one qubit PCEGs leads to
+Inspection of the Kraus operators for two qubit PCEGs leads to
 the ansatz that the Kraus operators for the generator of 
@@
 \end{equation}
-since the Kraus operators corresponding to one \afnote{a} single qubit PCEs are 
+since the Kraus operators corresponding to a single qubit PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
-corresponding to the operation that leaves the component $\sigma_\alpha$ \janote{$r_0$ and $r_\alpha$}
+corresponding to the operation that leaves the component $\sigma_\alpha$
 invariant~\cite{nielsen_chuang_2011}.

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 invariant~\cite{nielsen_chuang_2011}.
-\ddnote{agrego lo de los flips aqui}{\blue Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$.
-In fact, tracing out all particles except particle $k$ \afnote{...except the $k-$th one} gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}).
-And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel \afnote{with weight $1/2$}.}
+Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$.
+In fact, tracing out all particles except the $k$-th one gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$, see~ \eref{eq:generator:individual:qubit}.
+And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel  (completely dephasing).
 

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 
-We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce \janote{are indeed} a PCE. 
+We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce a PCE. 
 Notice that 
@@
 % \end{equation}
-which in turn imply \afnote{implies} that 
+which in turn implies that 
 \begin{equation}
@@
 However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
-by \afnote{the} Kraus operators \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
+by the Kraus operators in \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
 except for the first row, half of the matrix elements of each row is $+1$ and 
@@
 fixed point of some decoherence process, starting with PCEGs and 
-then generalizing \afnote{extending} to more general channels. 
+then extending to more general channels. 
 % Me gustaria modificar esta
@@
 \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha,
-t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
-time-homogeneous Markovian process, those are always characterized by some
+t_1+t_2}$. Therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
+time-homogeneous Markovian process, which are always characterized by some
 Lindblad generator~\cite{lindblad} \afnote{Me parece que se podría conectar mejor esta última frase (pero no pude XD)}. The Lindblad generator of $\mcG_{\vec

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 time-homogeneous Markovian process, which are always characterized by some
-Lindblad generator~\cite{lindblad} \afnote{Me parece que se podría conectar mejor esta última frase (pero no pude XD)}. The Lindblad generator of $\mcG_{\vec
-\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with \afnote{by} the standard
+Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec
+\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained using the standard
 procedure,  

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 We show now that PCE channels can also be implemented with \textit{simple
-collision models}~\cite{Ziman2010}. To do this, observe that using \afnote{by employing} the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
+collision models}~\cite{Ziman2010}. To do this, observe that employing the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
 be implemented using an unitary over the system and an

### 2022-05-03 documentos/kraus.tex
comentarios

@@
 \mcG_{\vec \alpha_M} \right\}$. For this we can define an environment
-consisting of \afnote{on} $M$ qubits initially in the state $\left( \projj{0}
+consisting of $M$ qubits initially in the state $\left( \projj{0}
 \right)^{\otimes M}$, or equivalently one qubit with the additional assumption
 that its state is reset to $\ket{0}$ after each collision (memory-less
-collisions). The collision with the $k\text{th}$ \afnote{$k\text{-th}$} particle is described by
+collisions). The collision with the $k$-\text{th} particle is described by
 $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$
@@
 \end{equation}
-where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits \afnote{over the whole ancillary qubits}.
-Notice that as PCEGs commute, the order of the collisions can be any \afnote{the order of the collisions is irrelevant}.
+where $\tr_{\text{E}}$ is the partial trace over the whole ancillary qubits. Notice that as PCEGs commute, the order of the collisions is irrelevant.
 % \begin{itemize}

### 2022-05-03 documentos/pce.tex
multiindex
comentarios
Errare humanum est.

@@
 $\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
-(b), (c) and (d) correspond to the identity map, dephasing channel, and 
-total depolarization, respectively, 
+(b), (c) and (d) correspond to the identity map, completely dephasing channel,
+and 
+complete depolarization, respectively, 
 as the color of each square indicates the value attained by the corresponding
@@
 \end{equation}
-where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$
-\janote{revisar si en el resto del artículo siempre le llamamos a $\valpha$
-`vector index'. A veces le poníamos `multi-index'}
+where $\vec \alpha$ denotes a multi-index $\qty(\alpha_1,\ldots,\alpha_N)$
 and $\alpha_i=0,1,2,3$. These hermitian operators form an orthogonal 

### 2022-05-03 documentos/proofdiagonalization.tex
comentarios

@@
 % 
-\subsection{Single qubit} % {{{
-\ddnote{Alejo, por fa revise q no se me fue un typo con el asunto de mod 2, ya corregí toda la notación y removi los otros comentarios, que ya fueron aclarados en la reunion y trataban de lo mismo} \afnote{Listo, todo en orden.}
 In order to simplify the derivation of the relations, let us employ pairs of
 binary indices instead of a single quaternary, i.e. $\alpha\to j +2 k$. For
-the sake of clarity, we will use \afnote{we use} Latin symbols for binary indices, and
+the sake of clarity, we use Latin symbols for binary indices, and
 reserve Greek letters for quaternary ones. 
@@
 single qubit case of the previous subsection. Then, all the steps leading to 
-\eref{eq:lambda:is:tau:appendix} can be redone, but with vector indices instead of binary scalars.
+\eref{eq:lambda:is:tau:appendix} can be redone.
 
-\ddnote{Poner atencion a lo siguiente}
-{\red[viejo y mal]The tensor product of Pauli matrices, in vector form,  will be denoted by 
-$\kket{\sigma_{\vec{k}\vec{l} }} = \kket{\sigma_{k_1l_1}}\otimes \cdots \otimes \kket{\sigma_{k_Nl_N}}$
-and fulfill the orthogonality relation 
-$\bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 
-2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}$.}
-{\blue [nuevo y correcto y breve, la condicion de ortogonalidad no se usa explicitamente y es trivial]
 The tensor product of Pauli matrices, in vector form,  will be denoted by 
 $\kket{\sigma_{\vec{k}\vec{l} }}$.
-} \afnote{perfecto}
 % \begin{equation}
@@
 The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
-\ddnote{corregir el angulo doble y tambien el oplus}
 \begin{align}

### 2022-05-03 documentos/quantum_classical.tex
comentarios

--- 2022-02-14 documentos/quantum_classical.tex
@@
 \label{quantum_classical}
-\ddnote{Alguien revise este apendice, tiene solo una iterada}
-A Quantum-classical (QC) channel is defined using an orthonormal basis in the Hilbert space.
+A Quantum-classical (QC) channel is defined by using an orthonormal basis in the Hilbert space.
 Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC channel associated to $B$ is
@@
 Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
-We will prove that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
+Now we proceed to demonstrate that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
 
@@
 \end{equation}
-it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there only positive terms in the sum, and $2^N$ of them are already equal to $1$.
+it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there are only positive terms in the sum, and $2^N$ of them are already equal to $1$.
 Therefore,
@@
 it is easy to check that the latter is a projector only if $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=0$.
-Since there are exactly $2^N$ elements of the form $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}$ with $\sigma_{\vec k} \in \text{set}(B)$, the channel $\mcE^{\text{QC}}_B$ is \pce{} with $2^N$ $1$s on its diagonal.
+Since there are exactly $2^N$ elements of the form $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec k}$ with $\sigma_{\vec k} \in \text{set}(B)$, then the channel $\mcE^{\text{QC}}_B$ is \pce{} with $2^N$ $1$s on its diagonal.

### 2022-05-03 documentos/proofdiagonalization.tex
comentarios

@@
 % thanks to a simplification in the argument of the power of $-1$. To continue, 
-since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $ \ddnote{Alejo, por fas checa esto, se me hace curioso que el modulo 2 solo este solo en la segunda suma del exponente} \afnote{Efectivamente solo tiene el mod2 en la segunda, sin embargo da exactamente lo mismo incluso si no existiera el mod2, pues la base es la misma (-1).
-En el caso de Weyl si hay que tener extremo cuidado con eso.}.
-To continue, we
+since $ (-1)^{j+(j+ k (\text{mod} 2))} = (-1)^k $. To continue, we 
 use the relation between computational and Pauli elements [\eref{PauToComp}],

### 2022-05-05 documentos/generators.tex
It only compiles every 3 tries... good luck.
Comentarios hechos

@@
 generators. We also include the corresponding 
-labels $\mcG_\alpha$ of the generators.
+labels $\mcG_\alpha$ of the generators. \cpnote{Nadie ha revisado el nuevo caption y la nueva figura con cuidado}
 % The rows or columns of $a$ and the diagrams of the generators are either 
@@
 % \cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
+\janote{Acá dejo mi propuesta para la caption:}
+\janote{A profound connection exists between the rows or columns of matrix $a$ 
+(in turn, $A$) [refer to \eref{eq:lambda:is:A:tau}] that diagonalizes 
+Choi's matrix of a PCE map and PCE generators $\mcG_\valpha$.
+For instance, if one takes the columns of $a$ and replace all -1's with 0's one
+is left with the sets of $\{\tau_\valpha\}$ of all single-qubit PCE generators.
+The converse procedure is also valid, one goes from the PCE generators 
+to the matrix $a$.}
 }

### 2022-05-06 documentos/generators.tex
This is a basic implementation that works.
Comentarios resueltos

@@
 
-% \cpnote{Revisar este párrfo. Solo ha pasado una persona por ahi}
 % 
@@
 to the matrix $a$.}
+\cpnote{The connection between rows or columns of $a$ and single-qubit PCE
+generators is shown, with the 1s identified with preserved components and
+the $-1$s with deleted ones. For any number of particles, such simple relation 
+still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
+\janote{The connection between rows or columns of $a$ and single-qubit PCE
+generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
+left with the sets $\{\tau_\alpha\}$ of preserved and erased components
+by each $\mathcal G_\alpha$.
+For any number of particles, such simple relation 
+holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
 }

### 2022-05-06 documentos/generators.tex
ajax-loader hotness, oh yeah

--- 2022-05-03 documentos/generators.tex
@@
 % \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
-\caption{Connection between rows and columns of $a$ and single qubit PCE
-generators. We also include the corresponding 
-labels $\mcG_\alpha$ of the generators.
-% The rows or columns of $a$ and the diagrams of the generators are either 
-% symmetric or anti-symmetric under reflection.
-% \cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
+\caption{
+% Connection between rows and columns of $a$ and single qubit PCE
+% generators. We also include the corresponding 
+% labels $\mcG_\alpha$ of the generators. \cpnote{Nadie ha revisado el nuevo caption y la nueva figura con cuidado}
+% \janote{Acá dejo mi propuesta para la caption:}
+% \janote{A profound connection exists between the rows or columns of matrix $a$ 
+% (in turn, $A$) [refer to \eref{eq:lambda:is:A:tau}] that diagonalizes 
+% Choi's matrix of a PCE map and PCE generators $\mcG_\valpha$.
+% For instance, if one takes the columns of $a$ and replace all -1's with 0's one
+% is left with the sets of $\{\tau_\valpha\}$ of all single-qubit PCE generators.
+% The converse procedure is also valid, one goes from the PCE generators 
+% to the matrix $a$.}
+% \cpnote{The connection between rows or columns of $a$ and single-qubit PCE
+% generators is shown, with the 1s identified with preserved components and
+% the $-1$s with deleted ones. For any number of particles, such simple relation 
+% still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
+\janote{The connection between rows or columns of $a$ and single-qubit PCE
+generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
+left with the sets $\{\tau_\alpha\}$ of preserved and erased components
+by each $\mathcal G_\alpha$.
+For any number of particles, such simple relation 
+holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
+\cpnote{The connection between rows or columns of $a$ and single-qubit PCE
+generators $\mathcal G_\alpha$ is shown. One can identify the -1s of $a$ with
+0s in the sets $\{\tau_\alpha\}$ of preserved and erased components
+of each $\mathcal G_\alpha$.
+For any number of particles, such simple relation 
+holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
 }

### 2022-05-06 documentos/generators.tex
No nos fuimos a duelo a muerte con cuchillos con CP

@@
 % still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
-\janote{The connection between rows or columns of $a$ and single-qubit PCE
-generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
-left with the sets $\{\tau_\alpha\}$ of preserved and erased components
-by each $\mathcal G_\alpha$.
-For any number of particles, such simple relation 
-holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
-\cpnote{The connection between rows or columns of $a$ and single-qubit PCE
+%\janote{The connection between rows or columns of $a$ and single-qubit PCE
+%generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
+%left with the sets $\{\tau_\alpha\}$ of preserved and erased components
+%by each $\mathcal G_\alpha$.
+%For any number of particles, such simple relation 
+%holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
+%\cpnote{
+The connection between rows or columns of $a$ and single-qubit PCE
 generators $\mathcal G_\alpha$ is shown. One can identify the -1s of $a$ with
@@
 For any number of particles, such simple relation 
-holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
+holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.
+\janote{Propuesta de CP y JA. Le toca a la gente resolver que también 
+están de acuerdo, o no}
 } 
+%}
 \label{fig:A_and_PCEGs_connection}

### 2022-05-10 documentos/intro.tex
Rev_Alejo

@@
 studies of channels beyond the qubit can be
-found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
+found~\cite{pub.1117408526,pub.1060516327,pub.1014660854,Fonseca2019}. \afnote{adicioné un paper mío donde trabajé con los flip-channels sobre qudits.}
 % \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 

### 2022-05-10 documentos/pce.tex
Rev_Alejo

@@
 of quantum channels that will allow us to introduce some notation, 
-and finish with the definition of PCE maps, some generalities. We further 
+and finish with the definition of PCE maps, some generalities \afnote{...and some generalities. (?)}. We further 
 introduce a useful graphical representation  for them.

### 2022-05-10 documentos/intro.tex
Comentarios Francois

@@
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
-for multi-particle systems~\cite{Horodecki},  and important part
+for multi-particle systems~\cite{Horodecki}, \flnote{an} \sout{and} important part
 of the efforts of the community implementing quantum technologies is 
@@
 % graining~\cite{Duarte2017,pinedacg}. 
-One of the main difficulties to characterize quantum channels is that,
+One of the main difficulties 
+\flnote{in characterizing quantum channels is that, like for quatum states, 
+the number of parameters required for their description increases quite 
+rapidly with Hilbert space dimension.}
+\sout{to characterize quantum channels is that,
 similar to quantum states, the parameters needed to describe them
-increases overwhelmingly rapidly with the dimension of the Hilbert space.
+increases overwhelmingly rapidly with the dimension of the Hilbert space.}
 %

### 2022-05-10 documentos/pce.tex
Comentarios Francois

@@
  to happen with probability $1$, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
-Often, this condition is easy to test.
+\flnote{\sout{Often, this condition is easy to test.}}
 The

### 2022-05-10 documentos/vector_space.tex
asdfasdfasdfasdfasdfasdfadsf
nueva propuesta de conclusiones
One little whitespace gets its very own commit! Oh, life is so erratic!
ajax-loader hotness, oh yeah
Comentarios Francois

@@
 \subsection{PCE quantum channels as vector spaces} % {{{
-% \cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
-% \ddnote{propongo channels as vector spaces como titulo de seccion, pues lo
-% actual se entiende mas en el sentido estandar: canales como miembros de un
-% espacio vectorial, que tambien es cierto, pero no es el punto aqui}
-% \cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
-% espacio. Quizá cuando haga falta se puede poner}
-% \janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
-% se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
-% parece una buena idea podría elaborar más cómo meterlo ahí}
-% \par
+\label{sec:vector_spaces}
 % Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{
@@
 belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
-indeed holds. However, for such election of $\vbeta$ the above relation reduces
+indeed holds. However, for such \flnote{a choice} \sout{election}
+of $\vbeta$ the above relation reduces
 to 
@@
 \par
-% 
-% 
-% % Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
-% % of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
-% % as
-% % \begin{equation}
-% % \san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
-% % = 
-% % 1
-% % , \quad
-% % \forall \vec\beta\in\Phi(\vec\alpha),
-% % \label{eq:12}
-% % \end{equation}
-% % which can be further decomposed in 
-% % \begin{equation}
-% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
-% %   \ldots
-% % %   \cdot\ldots\cdot 
-% % \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
-% % \label{eq:13}
-% % \end{equation}
-% % Moreover, since 
-% % 
-% % 
-% % 
-% % Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
-% % \begin{equation}
-% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
-% % \label{eq:12}
-% % \end{equation}
-% % This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
-% % (\ref{eq:12}) may be rewritten as
-% % \begin{equation}
-% % \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
-% % \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
-% % \label{eq:13}
-% % \end{equation}
-% % Here we show that (\ref{eq:13}) implies (\ref{eq:14}). 
-% Since \eref{eq:13} holds for 
-% all $\vec\beta\in\Phi(\vec\alpha)$, we may choose a specific such $\vec\beta$, namely
-% $\beta_l=0$ for all $l\neq k$ and $\beta_k=\beta$, where $\beta$ is an arbitrary number
-% such that
-% $\sa_{\alpha_k\beta}=1$. 
-% % \begin{equation}
-% % \sa_{\alpha_k\beta}=1.
-% % \end{equation}
-% This $\vec\beta$, as is readily verified, belongs to $\Phi(\vec\alpha)$, so
-% that \eref{eq:13} indeed holds for this $\vec\beta$. On the other hand, it is
-% then readily verified that, for this $\vec\beta$, \eref{eq:13} reduces to 
-% % (\ref{eq:14}), whcih therefore follows. 
-% % \flnote{Leve modificaci\'on de las ecuaciones anteriores, y adecuaci\'on del
-% % texto siguiente. } \cpnote{francois, recuerdo 
-% % que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
-% % proque se tiene que cumplir para los indices individulaes}. 
-% % We now show in Appendix
-% % \ref{app:proof} that from this follows that
-% % for all $1\leq k\leq N$, $\gamma_k$
-% % and $\gamma_k^\prime$ are connected by
-% \begin{equation}
-% \sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=1
-% \label{eq:14}
-% \end{equation}
-% for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$. 
-% One can verify, by working out the different cases, 
-% that \eref{eq:14} is equivalently expressed as 
-% \begin{equation}
-% \gamma_k^\prime=\alpha_k\oplus{}\gamma_k
-% \label{eq:oplus}
-% \end{equation}
-% where the $\oplus{}$ denotes the operation of the Klein group; see Figure
-% \ref{tab:1} for a detailed description. 
-% \par
 % }}}
@@
 \footnote{
-We can further \cpnote{desmechar} the vector space, by identifying each index
+We can further unravel the vector space, by identifying each index
 $\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
@@
 
-% % Lo que quiero quitar {{{
-% \cpnote{Propongo quitar desde aca}
-% Note further that if we perform the identification
-% \begin{subequations}
-% \begin{eqnarray}
-% 0&\to&(0,0)\label{eq:identa}\\
-% 1&\to&(0,1)\label{eq:identb}\\
-% 2&\to&(1,0)\label{eq:identc}\\
-% 3&\to&(1,1)\label{eq:identd}
-% \end{eqnarray}
-% \label{eq:ident}
-% \end{subequations}
-% then the $\oplus$ operation reduces to simple vector addition in
-% binary arithmetic. If we therefore denote by $\overline{\alpha}$
-% \cpnote{I dont think this is necesary. specially if we will write something
-% else}
-% the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
-% application of (\ref{eq:ident}),
-% the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
-% as
-% \begin{equation}
-% \overline\gamma=\overline\alpha+\overline{\gamma^\prime}
-% \label{eq:17}
-% \end{equation}
-% where the addition sign here refers to ordinary binary vector addition. 
-% \cpnote{Hasta aca}
-% % }}}
-
 From this readily follows an amusing property: the set of all multi-indices
@@
 a quantum channel, and a vector subspace of the aforementioned space. 
-% \cpnote{Aca quizá que Jose Alfredo ponga un ejemplo de una 
-% figura en la que se tenga algo que es un canal y algo que no es  un canal. 
-% Quizá también se puede mencionar qeu el subespacio mas chico es el canal totalmente 
-% depolarizante y el subespacio mas grande es la identidad} 
 \par
@@
 \caption{
-% \cpnote{Revisar, solo tiene una iteracion por parte mia}
-% Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
-% depolarizing channel, (b) a PCE channel that preserves four components.
-% (c), (d) and (e) show three generators \cpnote{Quizá poner los nombres de los
-% generadores acá}; the combination of any two of them yields the channel in (b).
-% (f) represents the identity map. 
-% 
-% \cpnote{Mejorar el caption cuando me ponga de acuerdo con la gente}
-% Aca poner 6 PCEs. (f) Identidad, (a) totally depolarizing, (c, d y e) tres
-% generadores, (b) un canal que resulte del generador. Sobra un espacio para
-% ilustrar alguna otra cosa. Quiza poner otro generador para que se vea que no
-% hay una manera unica de generar esos bichos.
 Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
@@
 
-% **********************************
-% **********************************
-% 
-% \cpnote{Dejar que la raza elija uno de los dos parrafos anteriores}\janote{El
-% primero (simón, cambié de opinión)} \par
-
  % }}}

### 2022-05-10 documentos/pce.tex
Comentario

@@
 \jami{}~\cite{jamil} and Choi~\cite{choi}.
-One first exploits an isomorphism that maps a channel $\mcE$ to the state
+One first exploits \janote{the} \sout{an} isomorphism that maps a channel $\mcE$ to the state
 $\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where

### 2022-05-10 documentos/pce.tex
typo
comentario

@@
 From now on we refer to any operation like that described in
-\eref{EqPCE}, as single qubit \textit{Pauli component erasing} (\pce{}) maps.
+\eref{EqPCE}, as single-aco aqubit \textit{Pauli component erasing} (\pce{}) maps.
 Not every such operation  is a quantum channel;
@@
 \end{align}
-where trace-preserving is already imposed, show that five out of
+where trace-preserving is already imposed, \janote{and} show that five out of
 the eight 1-qubit PCE maps are quantum channels.

### 2022-05-10 documentos/pce.tex
linea
otro

@@
 
-In order to present and develop the $N$ qubit case, it is useful 
+In order to present and develop the $N$-qubit case, it is useful 
 to introduce 
@@
 0}=1$. 
-It is worth noticing that, as for the single qubit case, not all PCE maps are
+It is worth noticing that, as for the single-qubit case, not all PCE maps are
 quantum operations. 

### 2022-05-10 documentos/pce.tex
single-qubit
single-qubit en todos

@@
 we turn our attention to introduce the Pauli component erasing maps. We start
-by exploring the single qubit scenario and then we treat the $N$-qubit case.
+by exploring the single-qubit scenario and then we treat the $N$-qubit case.
 % }
 
-The most general single qubit density matrix can be written as
+The most general single-qubit density matrix can be written as
 \begin{equation}
@@
 In (a) we introduce the notation
-in the diagrams that represent the single qubit \pce{} maps,
+in the diagrams that represent the single-qubit \pce{} maps,
 so that each square corresponds to a single 
@@
 % \afnote{Propongo el siguiente caption: (a) Pictorial
-% representation of a single qubit \pce{} map.
+% representation of a single-qubit \pce{} map.
 % The color of each square indicates the value attained by the corresponding
@@
 
-Similarly to the single qubit case, the density matrix $\rho$ of a system of $N$
+Similarly to the single-qubit case, the density matrix $\rho$ of a system of $N$
 qubits can be written using Pauli strings in the following way, 

### 2022-05-10 documentos/generators.tex
Rev_Alejo
an por a
Está mal escrito o yo soy pendejo?

@@
 A reflection symmetry is identified for PCE generators.
-Consider the map $\Sigma^{(k)}$ that reflects an multi-index $\valpha$ with 
+Consider the map $\Sigma^{(k)}$ that reflects a multi-index $\valpha$ with 
 respect to the $k$-th axis. This map leaves all components of $\valpha$
@@
 % and the associated 
-The maps have the following properties:
+\janote{This map} \sout{The maps} have the following properties:
 \begin{enumerate}
@@
 \janote{Propuesta de CP y JA. Le toca a la gente resolver que también 
-están de acuerdo, o no}
+están de acuerdo, o no} \afnote{para mi queda bien como está}
 } 

### 2022-05-10 documentos/generators.tex
Ya entendí, no es maps sino map
Comentarios medio mayor

@@
 We now discuss the existence of a generator set for all PCE quantum channels, 
-how to label each of them uniquely as $\pceg$ according to its local action 
-on every qubit in the system, and, finally, we will discuss a symmetry of
-both PCE quantum channel generators and $A$, the matrix that diagonalizes
-the Choi matrix $\mcD_N$ of a PCE map.
+how to label each of them uniquely as $\pceg$, according to its local action 
+on every qubit in the system, and finally, we will discuss a symmetry of
+\janote{PCE quantum channel generators and a connection between
+them and and $A$, the matrix that diagonalizes the Choi matrix $\mcD_N$ 
+of a PCE map.}
+\sout{both PCE quantum channel generators and $A$, the matrix that diagonalizes
+the Choi matrix $\mcD_N$ of a PCE map.}
+\janote{Al final de la sección no discutimos la simetría para $a$, sólo
+comentamos que están conectados los PCEGs y la $a$}
 
@@
 % and the associated 
-\janote{This map} \sout{The maps} have the following properties:
+The map have the following properties:
 \begin{enumerate}
@@
 $-1$ with $0$. 
-The proof is given in \appref{sec:2_qubits} and in \fref{fig:A_and_PCEGs_connection} we illustrate
-this connection for the single qubit case.
+The proof is given in \appref{sec:2_qubits}, and in \fref{fig:A_and_PCEGs_connection} we illustrate
+this connection for the single-qubit case.
 

### 2022-05-10 documentos/generators.tex
single-qubit de nuevo

@@
 % esta probado en la secc V}
-It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
+Finally, it is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
 encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
@@
 generator $\pceg$ by taking row (or column) $\valpha$ of $A$ and replacing
-$-1$ with $0$. 
-The proof is given in \appref{sec:2_qubits}, and in \fref{fig:A_and_PCEGs_connection} we illustrate
+$-1$s with $0$s. 
+The proof \janote{of this connection between PCEGs and $A$} is given in \appref{sec:2_qubits}, and in \fref{fig:A_and_PCEGs_connection} we illustrate
 this connection for the single-qubit case.

### 2022-05-10 documentos/kraus.tex
single-qubit de nuevo

@@
 experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
-Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
+Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non-invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 \end{equation}
-since the Kraus operators corresponding to a single qubit PCEs are 
+since the Kraus operators corresponding to a PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,

### 2022-05-10 documentos/kraus.tex
Más cambios

@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators for two qubit PCEGs leads to
+Inspection of the Kraus operators for two-qubit PCEGs leads to
 the ansatz that the Kraus operators for the generator of 
@@
 \end{equation}
-since the Kraus operators corresponding to a PCEs are 
+since the Kraus operators corresponding to a single-qubit PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,

### 2022-05-10 documentos/generators.tex
Cambios marcados

--- 2022-05-10 documentos/generators.tex
@@
 A reflection symmetry is identified for PCE generators.
-Consider the map $\Sigma^{(k)}$ that reflects a multi-index $\valpha$ with 
+Consider the map $\Sigma^{(k)}$ that reflects \janote{a} \sout{an} multi-index $\valpha$ with 
 respect to the $k$-th axis. This map leaves all components of $\valpha$
@@
 % and the associated 
-The map have the following properties:
+The maps have the following properties:
+\janote{lo dejé como antes}
 \begin{enumerate}
@@
 % esta probado en la secc V}
-It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
+\janote{Finally,} it is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
 encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
@@
 generator $\pceg$ by taking row (or column) $\valpha$ of $A$ and replacing
-$-1$ with $0$. 
-The proof is given in \appref{sec:2_qubits}, and in \fref{fig:A_and_PCEGs_connection} we illustrate
-this connection for the single-qubit case.
+$-1$\janote{s} with $0$\janote{s}. 
+The proof \janote{of this connection between PCEGs and $A$} is given in \appref{sec:2_qubits}\janote{,} and in \fref{fig:A_and_PCEGs_connection} we illustrate
+this connection for the single\janote{-}qubit case.
 

### 2022-05-10 documentos/kraus.tex
Cambios marcados

--- 2022-05-10 documentos/kraus.tex
@@
 experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
-Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non-invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
+Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non\janote{-}invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 % invariant~\cite{nielsen_chuang_2011}.
-Inspection of the Kraus operators for two qubit PCEGs leads to
+Inspection of the Kraus operators for two\janote{-}qubit PCEGs leads to
 the ansatz that the Kraus operators for the generator of 
@@
 \end{equation}
-since the Kraus operators corresponding to a PCEs are 
+since the Kraus operators corresponding to \janote{\sout{a}} single-qubit PCEs are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,

### 2022-05-10 documentos/pce.tex
Cambios marcados

@@
 we turn our attention to introduce the Pauli component erasing maps. We start
-by exploring the single-qubit scenario and then we treat the $N$-qubit case.
+by exploring the single-qubit scenario and then we treat the $N$\janote{-}qubit case.
 % }
 
-The most general single-qubit density matrix can be written as
+The most general single\janote{-}qubit density matrix can be written as
 \begin{equation}
@@
 From now on we refer to any operation like that described in
-\eref{EqPCE}, as single-aco aqubit \textit{Pauli component erasing} (\pce{}) maps.
+\eref{EqPCE}, as \janote{single-qubit} \textit{Pauli component erasing} (\pce{}) maps.
 Not every such operation  is a quantum channel;
@@
 In (a) we introduce the notation
-in the diagrams that represent the single-qubit \pce{} maps,
+in the diagrams that represent the single\janote{-}qubit \pce{} maps,
 so that each square corresponds to a single 
@@
 
-In order to present and develop the $N$-qubit case, it is useful 
+In order to present and develop the $N$\janote{-}qubit case, it is useful 
 to introduce 
@@
 
-Similarly to the single-qubit case, the density matrix $\rho$ of a system of $N$
+Similarly to the single\janote{-}qubit case, the density matrix $\rho$ of a system of $N$
 qubits can be written using Pauli strings in the following way, 
@@
 0}=1$. 
-It is worth noticing that, as for the single-qubit case, not all PCE maps are
+It is worth noticing that, as for the single\janote{-}qubit case, not all PCE maps are
 quantum operations. 

### 2022-05-11 documentos/intro.tex
fixed errors in the previous commit

--- 2022-05-10 documentos/intro.tex
@@
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
-for multi-particle systems~\cite{Horodecki},  and important part
+for multi-particle systems~\cite{Horodecki}, an important part
 of the efforts of the community implementing quantum technologies is 
@@
 % graining~\cite{Duarte2017,pinedacg}. 
-One of the main difficulties to characterize quantum channels is that,
-similar to quantum states, the parameters needed to describe them
-increases overwhelmingly rapidly with the dimension of the Hilbert space.
+One of the main difficulties 
+in characterizing quantum channels is that, like for quatum states, 
+the number of parameters required for their description increases quite 
+rapidly with Hilbert space dimension.
+% \sout{to characterize quantum channels is that,
+% similar to quantum states, the parameters needed to describe them
+% increases overwhelmingly rapidly with the dimension of the Hilbert space.}
 %
@@
 studies of channels beyond the qubit can be
-found~\cite{pub.1117408526,pub.1060516327,pub.1014660854,Fonseca2019}. \afnote{adicioné un paper mío donde trabajé con los flip-channels sobre qudits.}
+found~\cite{pub.1117408526,pub.1060516327,pub.1014660854,Fonseca2019}. 
 % \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 

### 2022-05-11 documentos/pce.tex
fixed errors in the previous commit

@@
 of quantum channels that will allow us to introduce some notation, 
-and finish with the definition of PCE maps, some generalities \afnote{...and some generalities. (?)}. We further 
+and finish with the definition of PCE maps and some generalities. We further 
 introduce a useful graphical representation  for them.

### 2022-05-11 documentos/pce.tex
pam anderson is going to love me.

@@
 \label{sec:pce_maps}
-% \janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
-% \janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
-% To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
-% maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
-% channels that will allow us to introduce some notation.
 
@@
  to happen with probability $1$, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
-\flnote{\sout{Often, this condition is easy to test.}}
+% \flnote{\sout{Often, this condition is easy to test.}}
 The
@@
 \jami{}~\cite{jamil} and Choi~\cite{choi}.
-One first exploits \janote{the} \sout{an} isomorphism that maps a channel $\mcE$ to the state
+One first exploits the isomorphism that maps a channel $\mcE$ to the state
 $\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
@@
 we turn our attention to introduce the Pauli component erasing maps. We start
-by exploring the single-qubit scenario and then we treat the $N$\janote{-}qubit case.
+by exploring the single-qubit scenario and then we treat the $N$-qubit case.
 % }
 
-The most general single\janote{-}qubit density matrix can be written as
+The most general single-qubit density matrix can be written as
 \begin{equation}
@@
 From now on we refer to any operation like that described in
-\eref{EqPCE}, as \janote{single-qubit} \textit{Pauli component erasing} (\pce{}) maps.
+\eref{EqPCE}, as single-qubit \textit{Pauli component erasing} (\pce{}) maps.
 Not every such operation  is a quantum channel;
@@
 \end{align}
-where trace-preserving is already imposed, \janote{and} show that five out of
+where trace-preserving is already imposed, and show that five out of
 the eight 1-qubit PCE maps are quantum channels.
@@
 % operations are \pce:
-% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
-% también propongo que en vez de ``show that only five operations are \pce{}''
-% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
-% channels''} 
 These operations are the identity map, the completely depolarizing channel
@@
 
-% \pce{} maps are defined as those quantum channels\janote{David, los mapas PCE
-% no son necesariamente canales cuánticos. Por esto, estás siendo incosistente en
-% el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF.
-% Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los
-% mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings.
-% \janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
-% \janote{
-% \pce{} maps are defined as positive trace-preserving (PTP) maps that 
-% \textit{nullify} Pauli strings.}
-% In the case of one qubit, they consist of maps nullifying the averages
-% $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$
-% with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known
-% \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
-% \begin{equation}
-% \rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
-% \end{equation}
-% Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
-% \begin{equation}
-% r_\alpha \mapsto \tau_\alpha r_\alpha
-% \end{equation}
-% where $\tau_\alpha$ is either $1$ or $0$.
-It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel.
-A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
-% \begin{align}
-% 1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
-% 1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
-% \end{align}
-% where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce:
-% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
-% también propongo que en vez de ``show that only five operations are \pce{}''
-% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
-% channels''} 
-% the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}.
-These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
 \begin{figure} % {{{
@@
 	\caption{
-% \janote{Le modificamos la primera frase a esta caption para que la Fig sea
-% 	autocontenida}
 In (a) we introduce the notation
-in the diagrams that represent the single\janote{-}qubit \pce{} maps,
+in the diagrams that represent the single-qubit \pce{} maps,
 so that each square corresponds to a single 
@@
 
-In order to present and develop the $N$\janote{-}qubit case, it is useful 
+In order to present and develop the $N$-qubit case, it is useful 
 to introduce 

### 2022-05-11 documentos/generators.tex
yet another quality commit

--- 2022-05-10 documentos/generators.tex
@@
+\clearpage
 \section{Generators} % {{{
@@
 
-We now discuss the existence of a generator set for all PCE quantum channels, 
-how to label each of them uniquely as $\pceg$, according to its local action 
-on every qubit in the system, and finally, we will discuss a symmetry of
-\janote{PCE quantum channel generators and a connection between
-them and and $A$, the matrix that diagonalizes the Choi matrix $\mcD_N$ 
-of a PCE map.}
-\sout{both PCE quantum channel generators and $A$, the matrix that diagonalizes
-the Choi matrix $\mcD_N$ of a PCE map.}
-\janote{Al final de la sección no discutimos la simetría para $a$, sólo
-comentamos que están conectados los PCEGs y la $a$}
+We now discuss the existence of a generator set for all PCE quantum channels and 
+how to label each of them uniquely as $\pceg$ (according to its local action 
+on every qubit in the system). Finally we will discuss a symmetry of
+PCE quantum channel generators and a connection between
+them and $A$, see \eref{eq:san}.
+% , the matrix that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
+% \sout{both PCE quantum channel generators and $A$, the matrix that diagonalizes
+% the Choi matrix $\mcD_N$ of a PCE map.}
 
@@
 % and the associated 
-The map have the following properties:
+The maps have the following properties:
 \begin{enumerate}
@@
 %
-
-% \janote{Aquí iría la prueva de la simetría de reflexión que está en el horno aún.}
-% For instance, see that the 2-qubit PCE generators 
-% $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
-% represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
-% respectively, are either symmetric or anti-symmetric under reflection with 
-% respect to lines that divide the diagram in half vertically and horizontally. 
-% The same symmetry is identified for the rows and columns of $A$ if one 
-% labels each position in a row or column $A^{(i)}$ as $A^{(i)}_{\vec\alpha}$.
-% \janote{Aquí habría que agregar la prueva de simetría para la $A$.}
 
@@
 % labels $\mcG_\alpha$ of the generators. \cpnote{Nadie ha revisado el nuevo caption y la nueva figura con cuidado}
-% \janote{Acá dejo mi propuesta para la caption:}
-% \janote{A profound connection exists between the rows or columns of matrix $a$ 
-% (in turn, $A$) [refer to \eref{eq:lambda:is:A:tau}] that diagonalizes 
-% Choi's matrix of a PCE map and PCE generators $\mcG_\valpha$.
-% For instance, if one takes the columns of $a$ and replace all -1's with 0's one
-% is left with the sets of $\{\tau_\valpha\}$ of all single-qubit PCE generators.
-% The converse procedure is also valid, one goes from the PCE generators 
-% to the matrix $a$.}
-% \cpnote{The connection between rows or columns of $a$ and single-qubit PCE
-% generators is shown, with the 1s identified with preserved components and
-% the $-1$s with deleted ones. For any number of particles, such simple relation 
-% still holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}. }
-%\janote{The connection between rows or columns of $a$ and single-qubit PCE
-%generators $\mathcal G_\alpha$ is shown; identifying -1s with 0s one is 
-%left with the sets $\{\tau_\alpha\}$ of preserved and erased components
-%by each $\mathcal G_\alpha$.
-%For any number of particles, such simple relation 
-%holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.} 
-%\cpnote{
 The connection between rows or columns of $a$ and single-qubit PCE
@@
 holds, see \sref{sec:generators} and appendix \ref{sec:2_qubits}.
-\janote{Propuesta de CP y JA. Le toca a la gente resolver que también 
-están de acuerdo, o no} \afnote{para mi queda bien como está}
 } 
@@
 
-% \ddnote{Tengo entendido que esto se queria probar usando las simetrias, esto ya
-% esta probado en la secc V}
-It is worth pointing out that $\san$ (and thus $a$) [see \eref{eq:san}] 
-encodes all the information of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
-From the tensor power of matrix $a$ one can infer the components $\{\taus\}$ of a PCE
-generator $\pceg$ by taking row (or column) $\valpha$ of $A$ and replacing
-$-1$ with $0$. 
-The proof is given in \appref{sec:2_qubits}, and in \fref{fig:A_and_PCEGs_connection} we illustrate
-this connection for the single-qubit case.
+Finally, it is worth pointing out that $\san$ (and thus $a$) [see
+\eref{eq:san}] encodes all the information of PCE generators $\pceg$ and,
+therefore, of all PCE quantum channels.  
+% 
+% 
+% 
+% From the tensor power of matrix $a$
+% one can infer the components $\{\taus\}$ of a PCE generator $\pceg$ by taking
+% row (or column) $\valpha$ of $A$ and replacing $-1$\janote{s} with
+% $0$\janote{s}.  
+% 
+From $A$, the tensor power of matrix $a$, one can infer the components
+$\{\taus\}$ of a PCE generator $\pceg$ by taking
+row (or column) $\valpha$ of $A$ and replacing $-1$ with
+$0$.
+The proof of the connection between PCEGs and $A$ is
+given in \appref{sec:2_qubits}, and in
+\fref{fig:A_and_PCEGs_connection} we illustrate this connection for the
+single-qubit case.
 

### 2022-05-11 documentos/kraus.tex
yet another quality commit

--- 2022-05-10 documentos/kraus.tex
@@
 
-% \cpnote{HAcer esta seccion despues de que david ponga lo de decoherencia, 
-% para servirla bien}
-% \todo{Carlos hace una version}
-
-% {\red [texto viejo introductorio de la seccion] Furthermore, quantum channels enjoy the well-known \textit{Kraus
-% representation} (or operator-sum representation) which reads 
-% \begin{equation}
-% \mcE[\rho]=\sum_i K_i \rho
-% K_i^\dagger{},
-% \end{equation}
-% with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
-% 
-% The Kraus operators of PCE channels provide an insight in the physical processes
-% that yield such channels. In this section we investigate and construct such 
-% operators and explore the corresponding processes. To study the Kraus operators corresponding to PCE, it is enough to study 
-% the ones corresponding to generators, as all PCEs commute and thus to get the 
-% Kraus operators of an arbitrary PCE, one can easily combine the Kraus
-% operators of its generators. }
-
-% {\red [anterior]
-% Given that \pce{} channels are projections, we might ask whether they are fixed
-% points of some memory-less (Markovian) process or not. In this section we prove
-% that they are, and give two examples of Markovian implementations. The first
-% one consist in identifying each \pce{} channel as a fixed point of some pure
-% dissipative process. The second, in identifying each \pce{} channel as fixed
-% points of some memory-less collision model.}
-
-Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
-experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics.
-Moreover, these processes lead to a monotonic (continuous) lose of information~\cite{breuerreview} and describe non-invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically (continuous) decreasing of the determinant, see Ref.~\cite{cirac}).
+Lindblad processes arise naturally in many
+theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility}
+and experimental~\cite{PhysRevA.67.042322} settings and are archetypical in
+decoherence dynamics. Moreover, these processes lead to a monotonic
+(continuous) lose of information~\cite{breuerreview} and describe
+non-invertible channels in the asymptotic limit $t\to \infty$ (this can be seen
+from the monotonically (continuous) decreasing of the determinant, see
+Ref.~\cite{cirac}).
 It is known that not every quantum channel can be seen as a snapshot of a
@@
 give two examples of Markovian implementations.
-%
-The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
+The first of them consists in identifying each \pce{} channel as a fixed point
+of some pure dissipative process, and in the second implementation we relate
+each \pce{} channel to fixed
 points of some memory-less collision model.
-
-% the most 
-% common decoherence 
-% 
-% with a Markovian master
-% equation~\cite{lindblad,kossa,kossa2,Gorini1976},
-% \begin{multline}
-% \dot \rho(t)=-i [H(t),\rho(t)]+\\
-% \sum_k \gamma_k(t)\left( V_k(t)\rho(t)V_k^{\dagger{}}-\frac{1}{2} \left\{V_k^\dagger{} V_k(t),\rho(t) \right\}\right),
-% \end{multline}
-% where the first part is the so-called Hamiltonian term, the second the dissipative term with $\gamma_k(t)\geq 0$ the relaxation ratios associated with the Lindblad operators $V_k(t)$.
-% %
-% In the particular case where the Hamiltonian, relaxation rations and Lindblad
-% operators are independent of time, we recover the well-known Lindblad master
-% equations~\cite{lindblad}. Such equations model time-homogeneous processes,
-% implying one-parameter semigroup structures that will be exploited later.
-% %
-% Besides, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
-Therefore, we might ask whether \pce{} channels can be seen as limit points of some Markovian processes.
-In this section we prove what in fact they are, and give two examples of Markovian implementations.
-% %
-% The first
-% one consist in identifying each \pce{} channel as a fixed point of some pure
-% dissipative process. The second, in identifying each \pce{} channel as fixed
-% points of some memory-less collision model.
-
 % }}}
@@
 \end{equation}
-since the Kraus operators corresponding to a single-qubit PCEs are 
+since the Kraus operators corresponding to a single-qubit PCE are 
 $\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,

### 2022-05-11 documentos/pce.tex
yet another quality commit

@@
 
-Similarly to the single\janote{-}qubit case, the density matrix $\rho$ of a system of $N$
+Similarly to the single-qubit case, the density matrix $\rho$ of a system of $N$
 qubits can be written using Pauli strings in the following way, 
@@
 0}=1$. 
-It is worth noticing that, as for the single\janote{-}qubit case, not all PCE maps are
+It is worth noticing that, as for the single-qubit case, not all PCE maps are
 quantum operations. 
@@
 For details, we refer the reader to appendix~\ref{quantum_classical}.
-
-% \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
-% frases de la importancia de esta familia.} \ddnote{hecho, pero de pronto
-% quedo espeso. Me estan gustando las cosas que he estado encontrando, voy a
-% investigar en esa direccion por mi cuenta, si sale algo interesante, los
-% invito, como no}
-% 
-%\ddnote{hay un typo en esta ecuacion}
-% A PCE operation is a trace-preserving operation that leaves invariant or erases 
-% the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
-% habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
-% todo claro y no hay problema en dejarlo así por el momento.}
-% \cpnote{Aca voy}
-
-% For the two qubits case, the operations illustrated
-% in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing
-% the positions of the $0$s and $1$s of the diagonal using the Pauli string
-% basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{}
-% maps\R{A3} turned out to be very useful for their analysis throughout this
-% work.
-%
-
-% Notice
-% than in both cases we drop the label $\alpha$ for simplicity, as it will 
-% remain unchanged throughout this text \janote{No entiendo qué estás diciendo
-% aquí}.
 

### 2022-05-13 documentos/intro.tex
Arreglos de forma  a la intro

@@
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
-for multi-particle systems~\cite{Horodecki}, an important part
+for multi-particle systems~\cite{Horodecki}, \janote{that is why} an important part
 of the efforts of the community implementing quantum technologies is 
@@
 Pauli observables to \textit{Pauli strings} (tensor products of Pauli
-matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and
+matrices)~\cite{KIMURA2003339,Lawrence2002}, \janote{hence} the resulting maps are unital and
 diagonal in the Pauli strings' basis.
@@
 derive necessary and sufficient conditions for such mappings to be completely
-positive trace preserving, thus, showing which idempotent operations are valid
+positive \janote{and} trace\janote{-}preserving \janote{(CPTP)}, thus, showing which idempotent operations are valid
 quantum channels (\pce{} channels). Additionally, we characterize the algebraic
@@
 section~\ref{sec:math} we diagonalize analytically the Choi matrix for
-arbitrary \pce{} maps and characterize completely positive maps by interpreting
-\pce{} maps as finite vector spaces. 
+arbitrary \pce{} maps and characterize \janote{the} completely positive maps by interpreting
+\pce{} maps \janote{quantum channels?} as finite vector spaces. 
 We study the
@@
 them to derive meaningful physical interpretations of \pce{} channels in
-section~\ref{sec:kraus}, as well Kraus operators of the generators.
+section~\ref{sec:kraus}, as well \janote{as} Kraus operators of the generators.
 % 
-To finish, we conclude in section~\ref{sec:conclusions}.
+To finish, we conclude \janote{and discuss future perspectives} in section~\ref{sec:conclusions}.
 % }}}

### 2022-05-16 documentos/intro.tex
Next time someone asks you how to fix an infinite loop, remember this commit

--- 2022-05-11 documentos/intro.tex
@@
 However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
-for multi-particle systems~\cite{Horodecki}, an important part
+for multi-particle systems~\cite{Horodecki}; that is why an important part
 of the efforts of the community implementing quantum technologies is 
@@
 Pauli observables to \textit{Pauli strings} (tensor products of Pauli
-matrices)~\cite{KIMURA2003339,Lawrence2002}, the resulting maps are unital and
+matrices)~\cite{KIMURA2003339,Lawrence2002}. The resulting maps are unital and
 diagonal in the Pauli strings' basis.
@@
 derive necessary and sufficient conditions for such mappings to be completely
-positive trace preserving, thus, showing which idempotent operations are valid
+positive and trace-preserving, thus, showing which idempotent operations are valid
 quantum channels (\pce{} channels). Additionally, we characterize the algebraic
@@
 % refreshing of quantum channels theory and the definition of 
-\pce{} maps. In
-section~\ref{sec:math} we diagonalize analytically the Choi matrix for
-arbitrary \pce{} maps and characterize completely positive maps by interpreting
-\pce{} maps as finite vector spaces. 
+\pce{} maps. 
+In section~\ref{sec:math} we diagonalize analytically the Choi matrix for
+arbitrary \pce{} maps and characterize their complete positivity by
+interpreting \pce{} quantum channels as finite vector subspaces.
+% In
+% section~\ref{sec:math} we diagonalize analytically the Choi matrix for
+% arbitrary \pce{} maps and characterize \janote{the} completely positive maps by interpreting
+% \pce{} maps \janote{quantum channels?} as finite vector spaces. 
 We study the
@@
 them to derive meaningful physical interpretations of \pce{} channels in
-section~\ref{sec:kraus}, as well Kraus operators of the generators.
+section~\ref{sec:kraus}, as well as Kraus operators of the generators.
 % 
-To finish, we conclude in section~\ref{sec:conclusions}.
+To finish, we conclude and discuss future perspectives in
+section~\ref{sec:conclusions}.
 % }}}

### 2022-07-25 documentos/answer_referees_PRA.txt
<<<<<<<<<<<<<<< HEAD

Dear Editor,

We are happy to receive positive feedback from the referees. The points
raised by the referees are answer in what follows.

Answer to the First Referee  {{{

*********************************************************************
1, Is there any difference or they are interchangeable between Pauli
diagonal operation and Pauli diagonal map? Please define them clearly
in the text when they first appear.

Answer:
There is no difference. We have replaced all occurrences
of "PCE operation" with "PCE map" (or similar), see list of changes.

*********************************************************************
2, It is clear that the channel Eq. (12) defines a super operator
acting on any B(H), but for the Choi matrix in Eq. (13), why it is a
super-operator?

Answer:
We have changed the wording. We now call D_N a "matrix"
(as it is a Choi matrix) instead of a superoperator.

*********************************************************************
3, I find this sentence “Let the components of \beta be such that
\beta_l =\beta\delta_lk for a particular particle index k, with \beta
such that a_\alpha_k\beta  = 1” rather confusing.

Answer:
We agree, the statement was confusing. We are now providing a 
new (and hopefully better) explanation.

*********************************************************************
4, Although two mathematical decoherence models are given, the
physical motivation of studying this general many qubit PCE channel is
not quite clear? It also would be better to motivate it in the
beginning.

Answer:
This paper grew from the sheer curiosity of why, for a single qubit, some
projections are allowed and others not. After some time, the beautiful 
mathematical structure presented in this paper appeared. Indeed some 
motivations might be presented, however the main one is simply to gain a 
deeper understanding of quantum channels in a multiparticle setting.
We have tried to put together an introduction that reflects that point 
of view, and we wish to keep it that way. However if further insistence 
on this point is made by the referee we can add some sentences in the
introduction.

*********************************************************************
I feel like there is a simple example of the PCE channel: it might be
called the stabilizer state PCE, e.g., N qubit stabilizer state,
erasing one stabilizer generator could give another stabilizer state,
and the remaining Pauli component is obviously 2^{N-1}, satisfying the
2^K components preserving statement. Moreover, in this case erasing
any one stabilizer generator will preserve exactly half the Pauli
components, as generator for all PCE channel?

Since stabilizer states are very useful in quantum computation,
perhaps it is a good practical motivation to study this PCE channel,
as long as they have a solid connection?

Answer:
The connection with stabilizer states might be interesting, given 
that for both stabilizer states and PCEs, Pauli strings play 
a prominent roll in there definitions. We have added a paragraph 
at the end of section III pointing out this possible relation.

*********************************************************************
}}}

Answer to of the Second Referee {{{
----------------------------------------------------------------------

*********************************************************************
Could you shed more light on the physical motivation for this study?

Answer:
The other referee has brought up the same question. We kindly refer the referee
to the paragraph in question in which we prefer to leave the motivation as it
stands. 
*********************************************************************
How do you think the scheme would work for qudits in dimensions of
Hilbert spaces which are not 2^n? Of course, I understand that your
results are pertinent to basis of Pauli tensors, but I am curious to
know your thoughts on the same.

For dimensions $d$ that allow $d+1$ maximally unbiased bases, one can
construct generalized Pauli channels. In those cases, do you think
your results could be extended in some way?

Answer:
This is clearly an interesting question. The generalization is not totally 
direct, and requires some mathematical work.  This is why we did not
present results in this paper, however we will hopefully present a generalization 
for arbitrary dimension. Some care must be taken as some results depend on the
field structure of the set {0,1}, which will not be available for arbitrary 
$d$.

*********************************************************************

}}}

List of changes {{{
* Between eq. (2) and eq. (3) we replaced 
    Not every such operation  is a quantum channel;
with 
    Not every such map  is a quantum channel;

* In the caption of figure 1, we replaced 
    ... and thus does not correspond to a quantum operation.
with 
    ... and thus does not correspond to a quantum channel.

* After eq. (6), we replaced 
    In addition, for the operation to be trace preserving...
with 
    In addition, for the map to be trace preserving...

* In that same paragraph, we replaced 
    We shall refer to the map  $xx$, with arbitrary values of $\taus$ (only
    restricted by complete positivity) as {\it Pauli diagonal operations}.  
with 
    We shall refer to the map  $xx$, with arbitrary values of $\taus$ (only
    restricted by complete positivity) as {\it Pauli diagonal maps}.

* Before eq. (13) we replaced 
    The matrix representation of the map corresponding to a Pauli diagonal operation is...
with 
    The matrix representation of the map corresponding to a Pauli diagonal map is...

* After eq. (13) we replaced 
    This superoperator is again diagonal in the (multi-qubit) Pauli basis...
with 
    This matrix is again diagonal in the (multi-qubit) Pauli basis...

* We changed the paragraph leading to eq. (23) from
    Let us now work out the nature of the aforementioned connection.  Let the
    components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
    particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
    Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
    belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
    indeed holds. However, for such a choice
    of $\vbeta$ the above relation reduces to 
to
    Let us now work out the nature of the aforementioned connection.  For
    arbitrary $k$ we define a vector $\vbeta_k$ such that
    $\vbeta_k\in\Phi(\vec\alpha)$ as follows: $\vbeta_k$ is zero everywhere except
    for the $k$'th coordinate, which takes a value $\beta$ such that
    $\sa_{\alpha_k\beta}=1$. Since $\sa_{\alpha 0}=1$ for any $\alpha$, this
    particular choice of $\vbeta$ indeed belongs to  $\Phi(\vec\alpha)$, so
    that if \eref{eq:coneccion:dos:indices:A} holds for all
    $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$,
    which leads to:

* At the end of section III we added the following paragraph:
    Finally, let us point out the following: if we wish to specify a PCE
    channel explicitly, the naive way to proceed would be simply to list all the
    Pauli components which are not erased. This requires in general, however, an
    exponential amount of information: that is, if the system has $N$ qubits, we
    generally require of the order of $2^N$ bits to do this. If, on the other hand,
    we take advantage of the vector space structure of a PCE channel, we only need
    to specify a basis. Since a basis consists of $N$ vectors of length $N$, the
    information required is only of $N^2$ bits, so that we have obtained a very
    substantial improvement by exploiting the total positivity. This is reminiscent
    of a rather similar effect in {\em stabilizer states\/} which can also be
    specified by $N^2$ bits, as opposed to an exponentially large number of basis
    coefficients for arbitrary states.  A stabilizer state is one which is the
    common eigenvector to the eigenvalue 1 of a set of $N$ commuting 
    Pauli strings.  The similarity is highly intriguing, and
    potentially of interest, since stabilizer states are of central importance in
    quantum error correction \cite{Gottesman1997}. 
}}}

Email, all {{{
Re: AS12227
    Pauli component erasing quantum channels
    by Jos\'e Alfredo de Leon, Alejandro Fonseca, Fran\c{c}ois Leyvraz, et
    al.

Dear Dr. Pineda,

The above manuscript has been reviewed by two of our referees. Comments
from the reports appear below.

These comments suggest that specific revisions of your manuscript are
in order. When you resubmit your manuscript, please include a summary
of the changes made and a succinct response to all recommendations or
criticisms contained in the reports.

Yours sincerely,

Mrs. Terre Arena (she/her/hers)
Senior Editorial Assistant
Physical Review A

----------------------------------------------------------------------
Report of the First Referee -- AS12227/de Leon
----------------------------------------------------------------------

This paper generalizes the single qubit channel as a concept of Pauli
component erasure channel, and extends it to the multi-qubit case.
Since the erasure map doesn’t always gives a valid quantum channel,
the authors try identifying the condition for the map to be CPTP,
which turns out to be related to the vector subspace of the Pauli
string set indices. Two simple mathematical decoherence model are also
introduced. This study is overall interesting. I give my comments and
questions in the following and would give my recommendation for
publication upon appropriately addressing them:

1, Is there any difference or they are interchangeable between Pauli
diagonal operation and Pauli diagonal map? Please define them clearly
in the text when they first appear.

2, It is clear that the channel Eq. (12) defines a super operator
acting on any B(H), but for the Choi matrix in Eq. (13), why it is a
super-operator?

3, I find this sentence “Let the components of \beta be such that
\beta_l =\beta\delta_lk for a particular particle index k, with \beta
such that a_\alpha_k\beta  = 1” rather confusing.

4, Although two mathematical decoherence models are given, the
physical motivation of studying this general many qubit PCE channel is
not quite clear? It also would be better to motivate it in the
beginning.

I feel like there is a simple example of the PCE channel: it might be
called the stabilizer state PCE, e.g., N qubit stabilizer state,
erasing one stabilizer generator could give another stabilizer state,
and the remaining Pauli component is obviously 2^{N-1}, satisfying the
2^K components preserving statement. Moreover, in this case erasing
any one stabilizer generator will preserve exactly half the Pauli
components, as generator for all PCE channel?

Since stabilizer states are very useful in quantum computation,
perhaps it is a good practical motivation to study this PCE channel,
as long as they have a solid connection?

----------------------------------------------------------------------
Report of the Second Referee -- AS12227/de Leon
----------------------------------------------------------------------

This is an interesting paper which is well articulated. However,
before I accept the same for publication, I have a few questions to
the authors.

Could you shed more light on the physical motivation for this study?

How do you think the scheme would work for qudits in dimensions of
Hilbert spaces which are not 2^n? Of course, I understand that your
results are pertinent to basis of Pauli tensors, but I am curious to
know your thoughts on the same.

For dimensions $d$ that allow $d+1$ maximally unbiased bases, one can
construct generalized Pauli channels. In those cases, do you think
your results could be extended in some way?
}}}

### 2022-07-25 documentos/math.tex
intro mas label a seccion
otra vez single-qubit
Cambios marcados
yet another quality commit
<<<<<<<<<<<<<<< HEAD

@@
 \section{Mathematical considerations} 
+\label{sec:math}
 % Intro {{{
@@
 \subsection{Diagonalization of Choi matrix} % {{{
-We now construct the Choi matrix of a single qubit Pauli diagonal map
+We now construct the Choi matrix of a single-qubit Pauli diagonal map
 %We now construct the Choi matrix associated to the single qubit map
@@
 \end{equation}
-% \janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
-% modificó la frase que le sigue a este comentario.}
 This vectorization must not be confused with the 
-%direct vectorization of $\sigma_{\vec \alpha}$
 tensor product of  all $\kket{\sigma_{\alpha_i}}$, 
@@
 \delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
-map corresponding to a Pauli diagonal operation is 
+map corresponding to a Pauli diagonal map is 
 % Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
@@
 \end{equation}
-This superoperator is again diagonal in the (multi-qubit) Pauli basis, with the 
+This matrix is again diagonal in the (multi-qubit) Pauli basis, with the 
 eigenvalue corresponding to 
@@
 % 
-% After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
+% After several steps, it is possible to prove that analogously to the  case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
 % \begin{equation}

### 2022-07-25 documentos/pce.tex
<<<<<<<<<<<<<<< HEAD

@@
 $r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to
-a quantum operation.
+a quantum channel.
 % \afnote{Propongo el siguiente caption: (a) Pictorial
@@
 In general, a Pauli component erasing (PCE) map is a map
-%  Pauli diagonal operation
 that either preserves or completely erases the Pauli components of a
@@
 with arbitrary values of 
-% but allow the 
-$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.
+$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal maps}.
 

### 2022-07-25 documentos/vector_space.tex
yet another quality commit
<<<<<<<<<<<<<<< HEAD

@@
 
-Let us now work out the nature of the aforementioned connection.  Let the
-components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
-particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
-Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
-belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
-indeed holds. However, for such \flnote{a choice} \sout{election}
-of $\vbeta$ the above relation reduces
-to 
+Let us now work out the nature of the aforementioned connection.  For arbitrary
+$k$ we define a vector $\vbeta_k$ such that $\vbeta_k\in\Phi(\vec\alpha)$ as
+follows: $\vbeta_k$ is zero everywhere except
+for the $k$'th coordinate, which takes a value $\beta$ such that  $\sa_{\alpha_k\beta}=1$. Since 
+$\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
+indeed belongs to  $\Phi(\vec\alpha)$, so that if \eref{eq:coneccion:dos:indices:A} holds for 
+all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to:
+% 
+% Let us now work out the nature of the aforementioned connection.  Let the
+% components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
+% particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
+% Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
+% belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
+% indeed holds. However, for such a choice
+% of $\vbeta$ the above relation reduces
+% to 
 \begin{equation}
@@
 
+% Stabilizer codes {{{
+Finally, let us point out the following: if we wish to specify a PCE
+channel explicitly, the naive way to proceed would be simply to list all the
+Pauli components which are not erased. This requires in general, however, an
+exponential amount of information: that is, if the system has $N$ qubits, we
+generally require of the order of $2^N$ bits to do this. If, on the other hand,
+we take advantage of the vector space structure of a PCE channel, we only need
+to specify a basis. Since a basis consists of $N$ vectors of length $N$, the
+information required is only of $N^2$ bits, so that we have obtained a very
+substantial improvement by exploiting the total positivity. This is reminiscent
+of a rather similar effect in {\em stabilizer states\/} which can also be
+specified by $N^2$ bits, as opposed to an exponentially large number of basis
+coefficients for arbitrary states.  A stabilizer state is one which is the
+common eigenvector to the eigenvalue 1 of a set of $N$ commuting 
+Pauli strings.  The similarity is highly intriguing, and
+potentially of interest, since stabilizer states are of central importance in
+quantum error correction \cite{Gottesman1997}.
+
 % }}}
+% }}}

### 2022-08-01 documentos/answer_referees_PRA.txt
I was wrong...

@@
 deeper understanding of quantum channels in a multiparticle setting.
-We have tried to put together an introduction that reflects that point 
-of view, and we wish to keep it that way. However if further insistence 
-on this point is made by the referee we can add some sentences in the
-introduction.
+We have put together a modified introduction that reflects that point 
+of view, but also addresses the referee's concern, see list of changes.
 
@@
 Answer:
-The other referee has brought up the same question. We kindly refer the referee
-to the paragraph in question in which we prefer to leave the motivation as it
-stands. 
+This paper grew from the sheer curiosity of why, for a single qubit, some
+projections are allowed and others not. After some time, the beautiful 
+mathematical structure presented in this paper appeared. Indeed some 
+motivations might be presented, however the main one is simply to gain a 
+deeper understanding of quantum channels in a multiparticle setting.
+We have put together a modified introduction that reflects that point 
+of view, but also addresses the referee's concern, see list of changes.
+
 *********************************************************************
@@
 List of changes {{{
+* Added to the second paragraph of the intro the following text:
+    The main task which we perform in this paper is the identification of the
+    conditions which an arbitrary PCE map must satisfy in order to be completely
+    positive. The answer turns out to involve a strikingly simple and unexpected
+    mathematical structure that is exploited to gain deeper understanding
+    on aforementioned channels, as we show in section \ref{sec:vector_spaces}. This
+    structure allows for example to describe such channels with a much reduced
+    set of parameters (as compared to specifying a list of all erased Pauli
+    components) or to define an
+    interesting semigroup structure on the set of all PCE channels. 
+    Additionally, these channels, are in a sense the simplest possible channels,
+    and as such can be used as building bocks of more general channels, for
+    instance through convex combination or composition.
+    To summarize succinctly the final result, we show that it is possible
+    to assign to every Pauli string a simple PCE channel, obtained by extending
+    the system with an ancilla of a single qubit, acting on the combined system by
+    a unitary involving the Pauli string and tracing over the ancilla. It then
+    follows from our results that all PCE channels arise from such
+    channels by composition.
 * Between eq. (2) and eq. (3) we replaced 

### 2022-08-01 documentos/intro.tex
I was wrong...

@@
 
-\par
 In this work we present a generalization of idempotent Pauli channels, \ie{}
@@
 diagonal in the Pauli strings' basis. 
-In addition, these channels describe the decoherence process in a similar way
-as the aforementioned
-ones for the single-qubit case.
-From now on we refer to these maps as \textit{Pauli component erasing} (\pce{})
-maps. We
-derive necessary and sufficient conditions for such mappings to be completely
-positive and trace-preserving, thus, showing which idempotent operations are valid
-quantum channels (\pce{} channels). Additionally, we characterize the algebraic
-properties of the set of \pce{} channels, showing that it is equipped
-with a semigroup structure, which is later used to derive physical
-implementations.
+We shall in the following refer to 
+such maps as {\em Pauli component erasing maps} (\pce{} maps)
+The main task which we perform in this paper is the identification of the
+conditions which an arbitrary \pce{} map must satisfy in order to be completely
+positive. The answer turns out to involve a strikingly simple and unexpected
+mathematical structure that is exploited to gain deeper understanding
+on aforementioned channels, as we show in section \ref{sec:vector_spaces}. This
+structure allows for example to describe such channels with a much reduced
+set of parameters (as compared to specifying a list of all erased Pauli
+components) or to define an
+interesting semigroup structure on the set of all \pce{} channels. 
+Additionally, these channels, are in a sense the simplest possible channels,
+and as such can be used as building bocks of more general channels, for
+instance through convex combination or composition.
+To summarize succinctly the final result, we show that it is possible
+to assign to every Pauli string a simple \pce{} channel, obtained by extending
+the system with an ancilla of a single qubit, acting on the combined system by
+a unitary involving the Pauli string and tracing over the ancilla. It then
+follows from our results that {\em all\/} \pce{} channels arise from such
+channels by composition.
+
+%In addition, these channels describe the decoherence process in a similar way
+%as the aforementioned
+%ones for the single-qubit case.
+%Additionally, we characterize the algebraic
+%properties of the set of \pce{} channels, showing that it is equipped
+%with a semigroup structure, which is later used to derive physical
+%implementations.
+
 %
@@
 % 
-To finish, we conclude and discuss future perspectives in
+To finish, we conclude and discuss future perspectives \flnote{and possible generalizations} in
 section~\ref{sec:conclusions}.

### 2022-08-02 documentos/answer_referees_PRA.txt
oops

@@
 that for both stabilizer states and PCEs, Pauli strings play 
-a prominent roll in there definitions. We have added a paragraph 
+a prominent roll in their definitions. We have added a paragraph 
 at the end of section III pointing out this possible relation.

### 2022-08-03 documentos/answer_referees_PRA.txt
grrrr

@@
 We are happy to receive positive feedback from the referees. The points
-raised by the referees are answer in what follows.
+raised by the referees are answered in what follows.
 
@@
 that for both stabilizer states and PCEs, Pauli strings play 
-a prominent roll in their definitions. We have added a paragraph 
+a prominent role in their definitions. We have added a paragraph 
 at the end of section III pointing out this possible relation.

### 2022-08-04 documentos/answer_referees_PRA.txt
Argh! About to give up :(

@@
     and as such can be used as building bocks of more general channels, for
-    instance through convex combination or composition.
+    instance through convex combination or composition with unitary transformations.
     To summarize succinctly the final result, we show that it is possible
@@
     information required is only of $N^2$ bits, so that we have obtained a very
-    substantial improvement by exploiting the total positivity. This is reminiscent
+    substantial improvement by exploiting complete positivity. This is reminiscent
     of a rather similar effect in {\em stabilizer states\/} which can also be

### 2022-08-04 documentos/intro.tex
Argh! About to give up :(

@@
 and as such can be used as building bocks of more general channels, for
-instance through convex combination or composition.
+instance through convex combination or composition with unitary transformations.
 To summarize succinctly the final result, we show that it is possible

### 2022-08-04 documentos/vector_space.tex
Argh! About to give up :(

@@
 information required is only of $N^2$ bits, so that we have obtained a very
-substantial improvement by exploiting the total positivity. This is reminiscent
+substantial improvement by exploiting complete positivity. This is reminiscent
 of a rather similar effect in {\em stabilizer states\/} which can also be

### 2022-08-05 documentos/intro.tex
Code was clean until manager requested to fuck it up

--- 2022-08-01 documentos/intro.tex
@@
 We shall in the following refer to 
-such maps as {\em Pauli component erasing maps} (\pce{} maps)
+such maps as {\em Pauli component erasing maps} (\pce{} maps).
+
 The main task which we perform in this paper is the identification of the
@@
 interesting semigroup structure on the set of all \pce{} channels. 
-Additionally, these channels, are in a sense the simplest possible channels,
-and as such can be used as building bocks of more general channels, for
-instance through convex combination or composition.
+Additionally, these channels are, in a sense, the simplest possible channels,
+and as such can be used as building blocks of more general channels. For 
+instance one can combine them (through convex superposition) or compose them
+with unitary transformations.
 To summarize succinctly the final result, we show that it is possible

### 2022-08-05 documentos/answer_referees_PRA.txt
My bad

@@
 We are happy to receive positive feedback from the referees. The points
-raised by the referees are answered in what follows.
+raised by them are answered in what follows.
 
@@
 List of changes {{{
-* Added to the second paragraph of the intro the following text:
+* Added to the introduction the following text:
     The main task which we perform in this paper is the identification of the
@@
 }}}
-
-Email, all {{{
-Re: AS12227
-    Pauli component erasing quantum channels
-    by Jos\'e Alfredo de Leon, Alejandro Fonseca, Fran\c{c}ois Leyvraz, et
-    al.
-
-Dear Dr. Pineda,
-
-The above manuscript has been reviewed by two of our referees. Comments
-from the reports appear below.
-
-These comments suggest that specific revisions of your manuscript are
-in order. When you resubmit your manuscript, please include a summary
-of the changes made and a succinct response to all recommendations or
-criticisms contained in the reports.
-
-Yours sincerely,
-
-Mrs. Terre Arena (she/her/hers)
-Senior Editorial Assistant
-Physical Review A
-
-----------------------------------------------------------------------
-Report of the First Referee -- AS12227/de Leon
-----------------------------------------------------------------------
-
-This paper generalizes the single qubit channel as a concept of Pauli
-component erasure channel, and extends it to the multi-qubit case.
-Since the erasure map doesn’t always gives a valid quantum channel,
-the authors try identifying the condition for the map to be CPTP,
-which turns out to be related to the vector subspace of the Pauli
-string set indices. Two simple mathematical decoherence model are also
-introduced. This study is overall interesting. I give my comments and
-questions in the following and would give my recommendation for
-publication upon appropriately addressing them:
-
-1, Is there any difference or they are interchangeable between Pauli
-diagonal operation and Pauli diagonal map? Please define them clearly
-in the text when they first appear.
-
-2, It is clear that the channel Eq. (12) defines a super operator
-acting on any B(H), but for the Choi matrix in Eq. (13), why it is a
-super-operator?
-
-3, I find this sentence “Let the components of \beta be such that
-\beta_l =\beta\delta_lk for a particular particle index k, with \beta
-such that a_\alpha_k\beta  = 1” rather confusing.
-
-4, Although two mathematical decoherence models are given, the
-physical motivation of studying this general many qubit PCE channel is
-not quite clear? It also would be better to motivate it in the
-beginning.
-
-I feel like there is a simple example of the PCE channel: it might be
-called the stabilizer state PCE, e.g., N qubit stabilizer state,
-erasing one stabilizer generator could give another stabilizer state,
-and the remaining Pauli component is obviously 2^{N-1}, satisfying the
-2^K components preserving statement. Moreover, in this case erasing
-any one stabilizer generator will preserve exactly half the Pauli
-components, as generator for all PCE channel?
-
-Since stabilizer states are very useful in quantum computation,
-perhaps it is a good practical motivation to study this PCE channel,
-as long as they have a solid connection?
-
-----------------------------------------------------------------------
-Report of the Second Referee -- AS12227/de Leon
-----------------------------------------------------------------------
-
-This is an interesting paper which is well articulated. However,
-before I accept the same for publication, I have a few questions to
-the authors.
-
-Could you shed more light on the physical motivation for this study?
-
-How do you think the scheme would work for qudits in dimensions of
-Hilbert spaces which are not 2^n? Of course, I understand that your
-results are pertinent to basis of Pauli tensors, but I am curious to
-know your thoughts on the same.
-
-For dimensions $d$ that allow $d+1$ maximally unbiased bases, one can
-construct generalized Pauli channels. In those cases, do you think
-your results could be extended in some way?
-}}}

### 2022-09-06 documentos/generators.tex
Committing in accordance with the prophecy.
pep8 - cause I fell like doing a barrel roll

@@
-\clearpage
 \section{Generators} % {{{
@@
 \centering
-\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
-\node at (-2.5,-0.9) {
-$
-\begin{pmatrix}
-1 & 1 & 1 & 1\\
-1 & 1 & -1 & -1\\
-1 & -1 & 1 & -1\\
-1 & -1 & -1 & 1
-\end{pmatrix}
-\longleftrightarrow
-% \mcG_1
-$
-} ;
-\pgfmathsetmacro{\unitstep}{1.2}
-% % Coordenadas   {{{
-% \node at (-0.6,0.5) {(a)} ;
-% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
-% \begin{scope}[shift={(0,-1)}]
-% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
-% \end{scope}
-% \begin{scope}[shift={(0,-2)}]
-% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
-% \end{scope}
-% \begin{scope}[shift={(0,-3)}]
-% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
-% \end{scope} 
-% \draw (0,-3) rectangle (1,1); 
-% % }}}
-\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
-% \begin{scope}[shift={(\unitstep*2,0)}]
-\node at (0.5,-3.5) {$\mcG_0$} ;
-% \node at (-0.6,0.5) {(b)} ;
-\fill[black] (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
-\node at (0.5,-3.5) {$\mcG_1$} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
-\node at (0.5,-3.5) {$\mcG_2$} ;
-% \node at (-0.6,0.5) {(d)} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
-\node at (0.5,-3.5) {$\mcG_3$} ;
-% \node at (-0.6,0.5) {(e)} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-\end{scope} % }}}
-\end{tikzpicture} % }}}
-% \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
+\includegraphics{connection_a_generators.pdf}
 \caption{

### 2022-09-06 documentos/vector_space.tex
pep8 - cause I fell like doing a barrel roll

@@
 \end{equation}
-where the $\oplus{}$ denotes the operation of the Klein group; see Figure
+where the $\oplus{}$ denotes the operation of the Klein group; see Table
 \ref{tab:1} for a detailed description. 
@@
 $\{0,1\}$.
-We notice that the Klein group described in \fref{tab:1} is actually isomorphic
+We notice that the Klein group described in Table \ref{tab:1} is actually isomorphic
 to the two dimensional vector space over the field of two elements $\{0,1\}$.
@@
 
-\begin{figure} % {{{
+\begin{table} % {{{
 \begin{center}
@@
 \end{tabular}
-\caption{Table for the $\oplus{}$ operation defined in (\ref{eq:14}). Note that
+\caption{Definition of the $\oplus{}$ operation, see \eref{eq:14}. Note that
 the operation is an abelian group, in fact it corresponds to the 
@@
 \end{center}
-\end{figure} % }}}
+\end{table} % }}}
 
@@
 \begin{center}
+\includegraphics{two_qubit_channels.pdf}
 % Del dcumento francois.pdf pg 8 agarramos:
 % e11, e4 y E7
-\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
-\pgfmathsetmacro{\unitstep}{5.2}
-\begin{scope}[shift={(1*\unitstep,0)}] % Depolirizng channel {{{
-\node at (-0.5,0.5) {(a)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(2*\unitstep,0)}] % Interseccion {{{
-\node at (-0.5,0.5) {(b)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
+% \pgfmathsetmacro{\unitstep}{5.2}
+% \begin{scope}[shift={(1*\unitstep,0)}] % Depolirizng channel {{{
+% \node at (-0.5,0.5) {(a)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(2*\unitstep,0)}] % Interseccion {{{
+% \node at (-0.5,0.5) {(b)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(3*\unitstep,0)}] % E4 {{{
+% \node at (-0.5,0.5) {(c)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(1*\unitstep,-\unitstep)}] % E7 {{{
+% \node at (-0.5,0.5) {(d)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(3*\unitstep,0)}] % E4 {{{
-\node at (-0.5,0.5) {(c)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(2*\unitstep,-\unitstep)}] % E11 {{{
+% \node at (-0.5,0.5) {(e)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(3*\unitstep,-\unitstep)}] % Identity channel {{{
+% \node at (-0.5,0.5) {(f)} ;
+% \cuadritotikz{}
+% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(1*\unitstep,-\unitstep)}] % E7 {{{
-\node at (-0.5,0.5) {(d)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(2*\unitstep,-\unitstep)}] % E11 {{{
-\node at (-0.5,0.5) {(e)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(3*\unitstep,-\unitstep)}] % Identity channel {{{
-\node at (-0.5,0.5) {(f)} ;
-\cuadritotikz{}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(1,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\end{tikzpicture} % }}}
+% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \end{tikzpicture} % }}}
 \end{center}

### 2022-09-06 documentos/notas/prueba_alternativa_grupo.tex
Terminadp

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{placeins}

\usepackage[mathlines]{lineno}  \linenumbers
\setlength\linenumbersep{3pt}
\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\definecolor{jacolor}{RGB}{200,40,0} \FXRegisterAuthor{ja}{aja}{\color{jacolor}JA}

\usepackage{physics}
\usepackage{graphicx}
% \usepackage{mathrsfs}
\usepackage{dutchcal}
\usepackage{multirow}
%

%% Notas
\usepackage[dvipsnames]{xcolor}
\newcommand\todo[1]{\textcolor{Green}{#1}}

\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{imakeidx}
\makeindex[columns=3, title=Alphabetical Index, intoc]

\def\bbra#1{\mathinner{\langle \! \langle{#1}|}}
\def\kket#1{\mathinner{|{#1}\rangle \! \rangle}}
\def\ddyada#1{\mathinner{|{#1}\rangle\!\rangle\!\langle\!\langle{#1}|}}
\def\ddyad#1#2{\mathinner{|{#1}\rangle\!\rangle\!\langle\!\langle{#2}|}}
\def\bbrakket#1#2{\mathinner{\langle\!\langle {#1}|{#2}\rangle\!\rangle}}
\newcommand{\sa}{\ensuremath{\textit{a}}}
\newcommand{\san}{\ensuremath{\textit{A}}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
% 
\title{Group structure of PCEs}
\author{José Alfredo de León}
\date{}
% 
\begin{document}
\maketitle
%\tableofcontents

For a PCE quantum channel If $\tau_{pq}=\tau_{p'q'}=1$, with $p,q\ne p',q'$, 
then $\tau_{p+p',q+q'}=1$. Our proof goes as follows. With the expressions
for $\tau_{pq}$ in terms of $\lambda_{\mu\nu}$ and the sum of all 
$\lambda_{\mu\nu}$ we derive another expression that must hold for a 
particular set of indices $\mu,\nu$. With this, the algebraic property
is computed straightforwardly. This very important 
property reveals the semigroup structure of 
PCE quantum channels.

We will begin from the expression for the Choi's eigenvalues $\lambda_{\mu \nu}$
with binary indices, that is $\mu,\nu\in\qty{0,1}$. This form of the 
eigenvalues read 
\begin{align}
\lambda_{\mu\nu}=\frac{1}{2}\sum_{m,n=0}^1\qty(-1)^{\mu m+\nu n}\tau_{mn}
\Mod{2},
\end{align}
where sums are modulo $2$. From here on we will use implicitly the
modulo 2 arithmetic and drop the $\Mod{2}$ notation.
To invert this expression let us multiply each side by $\qty(-1)^{-\mu p-\nu q}$
and sum over $\mu$ and $\nu$,
\begin{align}\label{eq:inverting}
\sum_{\mu,\nu=0}^1\qty(-1)^{-\mu p-\nu q}\lambda_{\mu\nu}=
\frac{1}{2}\sum_{m,n,\mu,\nu=0}^1\qty(-1)^{\mu(m-p) m+\nu (n-q)}\tau_{mn}.
\end{align}
We notice that 
\begin{align}
\sum_{j=0}^1(-1)^{j(k-l)}=1+(-1)^{k-l}=2\delta_{kl}
\end{align}
because $k-l=0$ when $k=l$ and $k-l=1$ when $k\ne l$. There is no other possible
value because we are using modulo 2 arithmetic. Using this property, we resume
to eq. \eqref{eq:inverting},
\begin{subequations}
\begin{align}
\sum_{\mu,\nu=0}^1\qty(-1)^{-\mu p-\nu q}\lambda_{\mu\nu}&=
\frac{1}{2}\sum_{m,n,\mu,\nu=0}^1(2\delta_{mp})(2\delta_{nq})\tau_{mn} \\
\tau_{pq}&=\frac{1}{2}\sum_{\mu,\nu=0}^1\qty(-1)^{-\mu p-\nu q}\lambda_{\mu\nu}.
\label{eq:tau:lambdas}
\end{align}
\end{subequations}
Now, we subtract $\sum_{\mu,\nu}\lambda_{\mu\nu}=2$
from $2=\sum_{\mu,\nu}\qty(-1)^{-\mu p-\nu q}\lambda_{\mu\nu}$ (setting
$\tau_{pq}=1$ in \eqref{eq:tau:lambdas}),
\begin{align}\label{eq:paso}
\sum_{\mu,\nu=0}^1\lambda_{\mu\nu}\qty[(-1)^{-\mu p-\nu q}-1]=0.
\end{align}
Recall that $\lambda_{\mu \nu}\geq 0$ for the corresponding map to be 
completely positive, and $(-1)^{-\mu p-\nu q}-1\leq 0$ because we are
summing modulo 2, thus $-\mu p-\nu q=0,1$. These being said, now it must
be evident that every term in left side of \eqref{eq:paso} has to be
zero for the expression to hold. Therefore, if $\lambda_{\mu\nu}\ne 0$,
then
\begin{align}\label{eq:property}
(-1)^{-\mu p}=(-1)^{\nu q},\qquad \forall\,\mu,\nu \vert \lambda_{\mu\nu}\ne 0.
\end{align}
The same expression holds for indices $p',q'$. Now we use this expression to
evaluate 
\begin{subequations}
\begin{align}
\tau_{m+m',n+n'}&=\frac{1}{2}\sum_{\mu,\nu=0}^1
(-1)^{-\mu(p+p')-\nu(q+q')}\lambda_{\mu\nu} \\
&=\frac{1}{2}\sum_{\mu,\nu|\lambda_{\mu\nu}\ne 0}
(-1)^{\nu(q+q')-\nu(q+q')}\lambda_{\mu\nu}\label{eq:paso:7b}\\
&=\frac{1}{2}\sum_{\mu,\nu|\lambda_{\mu\nu}\ne 0}\lambda_{\mu\nu}\label{eq:paso:7c}\\
&=1,
\end{align}
\end{subequations}
where \eqref{eq:property} has been used in \eqref{eq:paso:7b} and the fact
that Choi's eigenvalues sum $2$ in \eqref{eq:paso:7c}. $\square$
% 
\bibliography{References}{}
\bibliographystyle{unsrt}
% 
\end{document}

### 2022-09-15 documentos/generators.tex
Make Sure You Are Square With Your God Before Trying To Merge This

@@
 the identity map. In other words, the set of PCE quantum channels that preserve half 
-of the components plus the identity map, are a generator set for 
+of the components plus the identity map, is a generator set for 
 all PCE channels.
 Consider \Fref{fig:examplesPCE}; subfigures (c), (d) and (e) represent nontrivial 
-PCE generators and the composition of any two of them yield the PCE channel
+PCE generators (PCEGs) and the composition of any two of them yields the PCE channel
 corresponding to (b).
 
-PCE generators (hereafter PCEGs) may be characterized by its local
+A PCEGs may be characterized by its local
 action on every qubit 
@@
 For single qubits, the identity corresponds to $\mcG_0$, shown in 
-\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
+\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in 
 \fref{fig:one:qubit:examples}(c).
-The 2-qubits PCE generator represented in subfigure (c)
-of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
-Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
+The two-qubit PCE generator represented in subfigure (c)
+of \Fref{fig:examplesPCE} acts on the first qubit (first column) as a map of its
+Bloch sphere to the $x$ axis, and on the second qubit (first row) as an identity,
 hence it is labeled $\mcG_{(1,0)}$.
-See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.
+See \Fref{fig:appex:twoQ_PCEGs} for the notation of all two-qubit PCE generators.
 
@@
 $\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}$, where we used 
-the fact that for channels, the non-zero elements are closed
+the fact that for channels the non-zero elements are closed
 under $\oplus$. In other words, the components of a PCE channel
-are symmetric under reflection over the $k$-th axis. Now consider the case in which 
+are symmetric under reflection over the $k$th axis. Now consider the case in which 
  $\Sigma^{(k)}(\vec0)$ does not belong to generator. Then 
@@
 $\tau_\valpha = \tau_{\Sigma^{(k)}(\vec\alpha)}=0$ is also forbidden 
-because for generators, the codimension of the associated vector space 
+because for generators the codimension of the associated vector space 
 is 1. This means that the components of a PCE channel are antisymmetric
-with respect to reflection over the $k$-th axis. 
-Indeed, the 2-qubit PCE generators 
+with respect to reflection over the $k$th axis. 
+Indeed, the two-qubit PCE generators 
 $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$
-represented in subfigures (c), (d) and (e) of \Fref{fig:two:qubit:examples}, 
+represented in Figs.~\ref{fig:two:qubit:examples}(c),
+\ref{fig:two:qubit:examples}(d), and \ref{fig:two:qubit:examples}(e),
 respectively, are either symmetric or anti-symmetric under reflection with 

### 2022-09-15 documentos/math.tex
Make Sure You Are Square With Your God Before Trying To Merge This

@@
 % Intro {{{
-This section is devoted to derive the conditions a Pauli diagonal map needs to satisfy 
-the complete positivity condition i.e. that all the eigenvalues of the Choi matrix
+This section is devoted to deriving the conditions a Pauli diagonal map needs to satisfy 
+the complete positivity condition, i.e., that all the eigenvalues of the Choi matrix
 associated to the channel are non-negative.  To do so, we calculate
@@
 % }}}
-\subsection{Diagonalization of Choi matrix} % {{{
+\subsection{Diagonalization of the Choi matrix} % {{{
 We now construct the Choi matrix of a single-qubit Pauli diagonal map
@@
 %the vectorized Pauli operators are defined as follows, 
-one uses the vectorized Pauli strings, 
+one uses the vectorized Pauli strings:
 \begin{equation}\label{eq:vectorized_pauli_strings}
@@
 As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in
-terms of tensor products of Pauli matrices
+terms of tensor products of Pauli matrices:
 \begin{equation}

### 2022-09-15 documentos/pce.tex
arrgghh... damn this thing for not working.
Make Sure You Are Square With Your God Before Trying To Merge This

@@
 % \afnote{Propongo que cambiemos el inicio de esta sección por: 
-In this section we introduce the family of Pauli component erasing (PCE)
+In this section we introduce the family of PCE
 maps. Let us start our discussion with a brief review of several basic concepts
@@
 Quantum channels are the most general linear operations that a quantum system
-undergo independently of its past~\cite{zimansbook,cirac}.  The physical system
+undergoes independently of its past~\cite{zimansbook,cirac}.  The physical system
 under study will be associated with a Hilbert space denoted by \hilbert{}, and
@@
 The construction of quantum channels includes basically three ingredients:
-linearity, trace preservation and complete positivity. Linearity is needed to
+linearity, trace preservation, and complete positivity. Linearity is needed to
 map every convex combination of density matrices into a convex combination of the
@@
 Remarkably, the map \mcE{} is completely positive
-if and only \choi{} (also called Choi or dynamical matrix of $\mcE$) 
-is positive-semidefinite~\cite{jamil,choi}. 
+if and only if \choi{} (also called the Choi or dynamical matrix of $\mcE$) 
+is positive semidefinite~\cite{jamil,choi}. 
 % \afnote{No sé si es algo obvio, pero creo que seria bueno comentar que es el objeto $\id$.}
@@
 % \afnote{
-We have discussed the main features of quantum channels, now
+We have discussed the main features of quantum channels, and now
 we turn our attention to introduce the Pauli component erasing maps. We start
@@
 each component 
-in the following way,
+in the following way:
 % 
@@
 From now on we refer to any operation like that described in
-\eref{EqPCE}, as single-qubit \textit{Pauli component erasing} (\pce{}) maps.
+\eref{EqPCE}, as a single-qubit \pce{} map.
 Not every such operation  is a quantum channel;
@@
 leads
-to a violation of the CP conditions. Indeed a direct evaluation
-of such conditions yield~\cite{zimansbook,davalosdivisibility}, 
+to a violation of the complete positivity condition. Indeed, a direct evaluation
+of such conditions yields~\cite{zimansbook,davalosdivisibility}
 % 
@@
 \end{align}
-where trace-preserving is already imposed, and show that five out of
-the eight 1-qubit PCE maps are quantum channels.
+where trace preserving is already imposed, and shows that five out of
+the eight single-qubit PCE maps are quantum channels.
 % 
@@
 \begin{center}
-\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
-\pgfmathsetmacro{\unitstep}{3.5}
-% Coordenadas   {{{
-\node at (-0.6,0.5) {(a)} ;
-\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
-\begin{scope}[shift={(0,-1)}]
-\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
-\end{scope}
-\begin{scope}[shift={(0,-2)}]
-\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
-\end{scope}
-\begin{scope}[shift={(0,-3)}]
-\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
-\end{scope} 
-\draw (0,-3) rectangle (1,1); 
-% }}}
-\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
-% \begin{scope}[shift={(\unitstep*2,0)}]
-\node at (-0.6,0.5) {(b)} ;
-\fill[black] (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
-\node at (-0.6,0.5) {(c)} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
+\includegraphics{one_qubit_PCE.pdf}
+% \begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
+% \pgfmathsetmacro{\unitstep}{3.5}
+% % Coordenadas   {{{
+% \node at (-0.6,0.5) {(a)} ;
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
+% \begin{scope}[shift={(0,-1)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
+% \end{scope}
+% \begin{scope}[shift={(0,-2)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
+% \end{scope}
+% \begin{scope}[shift={(0,-3)}]
+% \draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
+% \end{scope} 
+% \draw (0,-3) rectangle (1,1); 
+% % }}}
+% \begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
+% % \begin{scope}[shift={(\unitstep*2,0)}]
+% \node at (-0.6,0.5) {(b)} ;
+% \fill[black] (0,0) rectangle (1,1);
+% \draw[black!10] (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \draw (0,-3) rectangle (1,1); 
 % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
-\node at (-0.6,0.5) {(d)} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
+% \node at (-0.6,0.5) {(c)} ;
+% \fill[black] (0,0) rectangle (1,1);
+% % \draw (0,0) rectangle (1,1);
+% \draw[black!10] (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \draw (0,-3) rectangle (1,1); 
+% % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
+% \node at (-0.6,0.5) {(d)} ;
+% \fill[black] (0,0) rectangle (1,1);
+% % \draw (0,0) rectangle (1,1);
+% \draw[black!10] (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \draw (0,-3) rectangle (1,1); 
+% % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \end{scope} % }}}
+% \begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
+% \node at (-0.6,0.5) {(e)} ;
+% \fill[black] (0,0) rectangle (1,1);
+% % \draw (0,0) rectangle (1,1);
+% \draw[black!10] (0,0) rectangle (1,1);
+% \begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% \begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
+% % \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
 % \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
-\node at (-0.6,0.5) {(e)} ;
-\fill[black] (0,0) rectangle (1,1);
-% \draw (0,0) rectangle (1,1);
-\draw[black!10] (0,0) rectangle (1,1);
-\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
-\draw (0,-3) rectangle (1,1); 
-\end{scope} % }}}
-\end{tikzpicture} % }}}
+% % \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
+% \draw (0,-3) rectangle (1,1); 
+% \end{scope} % }}}
+% \end{tikzpicture} % }}}
 \end{center}
@@
 % Thus, i
-In general, a Pauli component erasing (PCE) map is a map
+In general, a PCE map is a map
 that either preserves or completely erases the Pauli components of a
@@
 with arbitrary values of 
-$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal maps}.
+$\taus$ (only restricted by complete positivity), as {\it Pauli diagonal maps}.
 
@@
 A graphical representation for PCE maps may be introduced, being the
-two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
+two-qubit case that has proved to be the most useful. Consider a $N$-dimensional 
 Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
@@
 empty. 
-Examples for $N=1$ and $N=2$ are provided in \fref{fig:one:qubit:examples} and
+Examples for $N=1$ and $2$ are provided in \fref{fig:one:qubit:examples} and
 \fref{fig:two:qubit:examples}, respectively.
@@
 quantum-classical channels defined with the eigenbasis of some set of $2^N-1$
-commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
+commuting Pauli observables~\cite{Lawrence2002} comprise a \pce{} map with exactly $
 2^N $ components equal to $1$s in its diagonal.
@@
 \begin{figure} % {{{
-\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
-\pgfmathsetmacro{\unitstep}{5.2}
-\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
-\node at (-0.5,0.5) {(a)} ;
-% \cuadritotikz{}
-    \foreach \x in {0,1,2,3} {
-      \foreach \y in {0,1,2,3} {
-        \begin{scope}[shift={(\x,-\y)}] 
-          \draw[black!10] (0,0) rectangle (1,1); 
-%           \draw (0,0) rectangle (1,1); 
-          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
-         \end{scope}
-%         \node at (0,-\y) (input\y) {$i_\y$};
-%         \node[block] at (2,-\y) (block\y) {$f_\y$};
-%         \draw[->] (input\y) -- (block\y);
-%         \draw[->] (block\y.east) -- +(0.5,0);
-    }
-    }
- \draw (0,-3) rectangle (4,1);
-\end{scope} % }}}
-\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
-\node at (-0.5,0.5) {(b)} ;
-\cuadritotikz{}
-%     \foreach \x in {0,1,2,3} {
-%       \foreach \y in {0,1,2,3} {
-%         \begin{scope}[shift={(\x,-\y)}] 
-%           \draw (0,0) rectangle (1,1); 
-% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-%          \end{scope}
-% %         \node at (0,-\y) (input\y) {$i_\y$};
-% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
-% %         \draw[->] (input\y) -- (block\y);
-% %         \draw[->] (block\y.east) -- +(0.5,0);
-%     }
-%     }
-\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
-\node at (-0.5,0.5) {(c)} ;
-\cuadritotikz{}
-%     \foreach \x in {0,1,2,3} {
-%       \foreach \y in {0,1,2,3} {
-%         \begin{scope}[shift={(\x,-\y)}] 
-%           \draw (0,0) rectangle (1,1); 
-% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
-%          \end{scope}
-% %         \node at (0,-\y) (input\y) {$i_\y$};
-% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
-% %         \draw[->] (input\y) -- (block\y);
-% %         \draw[->] (block\y.east) -- +(0.5,0);
-%     }
-%     }
-\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
-\end{scope} % }}}
-\end{tikzpicture} % }}}
+\includegraphics{two_qubit_PCE.pdf}
 	\caption{In (a) we introduce the
-positions of two qubit diagrams. The diagrams in 
+positions of two qubit diagrams. The diagram in 
 (b) corresponds to a quantum channel that results from the tensor product of

### 2022-09-15 documentos/proofdiagonalization.tex
comentarios
Make Sure You Are Square With Your God Before Trying To Merge This

@@
 In order to simplify the derivation of the relations, let us employ pairs of
-binary indices instead of a single quaternary, i.e. $\alpha\to j +2 k$. For
+binary indices instead of a single quaternary, i.e., $\alpha\to j +2 k$. For
 the sake of clarity, we use Latin symbols for binary indices, and
@@
 \end{equation}
-Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
-k (\text{mod} 2)$, then the Choi matrix reads
+Returning to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
+k (\text{mod} 2)$; then the Choi matrix reads
 \begin{multline}
@@
 \end{equation}
-with 
-\begin{equation}
-\sa=\left(
-\begin{array}{cccc}
-1 &1 &1   &1   \\
- 1 & 1  & -1&-1   \\
-1  & -1  & 1 & -1\\
-1&-1&-1&1  
-\label{a_appendix}
-\end{array}
-\right),
-\end{equation}\janote{esta matriz ya está en el cuerpo principal del artículo. Sugiero quitar de acá.}
+with $a$ the matrix shown in~\eref{eq:1} 
 instead of $H\otimes H$. This can be done due to the fact
@@
 \subsection{$N$ qubits} % {{{
-To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
-$N$ dimensional vector $\valpha$ with a pair of $N$ dimensional vector binary
+To work out the $N$-qubit case, we again rely on binary indices. In this case, we replace 
+$N$-dimensional vector $\valpha$ with a pair of $N$-dimensional vector binary
 indices $\vec j$ and $\vec k$ so that 
 each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
-single qubit case of the previous subsection. Then, all the steps leading to 
+single-qubit case of the previous subsection. Then, all the steps leading to 
 \eref{eq:lambda:is:tau:appendix} can be redone.
@@
 \end{equation}
-The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
+The generalizations of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
 \begin{align}
@@
 By employing the previous relations, we can write the matrix representation of
-the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as
+the map, $\hat{\mathcal{E}}_N $ in the $N$-qubit computational basis as
 \begin{multline}
@@
 In this way it is straightforward to apply the reshuffling operation on
-$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix, 
+$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix, and
 then transform back to the Pauli basis and simplify to obtain 

### 2022-09-15 documentos/vector_space.tex
Make Sure You Are Square With Your God Before Trying To Merge This

@@
 % \sa_{\alpha_N\beta_N}$. 
-Using the fact that $a^{-1}=a/4$, so 
+Using the fact that $a^{-1}=a/4$, and so 
 % (so $A = A^{-1}/2^N$) 
@@
 
-Other two simple but crucial observations are the following. 
-For valid quantum channels it holds 
+Two other simple but crucial observations are the following. 
+For valid quantum channels it holds that 
 % \begin{equation}
@@
 This follows from restricting the sum \eref{eq:tau:is:A:p}
-to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
+to $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
 Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
@@
 indeed belongs to  $\Phi(\vec\alpha)$, so that if \eref{eq:coneccion:dos:indices:A} holds for 
-all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to:
+all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to
 % 
@@
 \end{equation}
-where the $\oplus{}$ denotes the operation of the Klein group; see Table
+where $\oplus{}$ denotes the operation of the Klein group; see Table
 \ref{tab:1} for a detailed description. 
@@
 We notice that the Klein group described in Table \ref{tab:1} is actually isomorphic
-to the two dimensional vector space over the field of two elements $\{0,1\}$.
+to the two-dimensional vector space over the field of two elements $\{0,1\}$.
 Then, we build the complete vector space,
@@
 }. 
-We can indeed restate \eref{eq:oplus}, and say that for quantum channels, 
+We can indeed restate \eref{eq:oplus} and say that, for quantum channels, 
 if $\tau_{\vec\alpha}=1$, then
@@
 \caption{Definition of the $\oplus{}$ operation, see \eref{eq:14}. Note that
-the operation is an abelian group, in fact it corresponds to the 
-Klein group, where the neutral element is $0$. This is the reason for choosing
+the operation is an Abelian group; in fact it corresponds to the 
+Klein group, where the neutral element is zero. This is the reason for choosing
 an additive notation for the operation defined in (\ref{eq:14}). }
@@
 From this readily follows an amusing property: the set of all multi-indices
-$\vec\gamma$ for which $\tau_{\vec\gamma}=1$, is closed under binary
-vector addition, in other words, it forms a vector subspace of the set
+$\vec\gamma$ for which $\tau_{\vec\gamma}=1$ is closed under binary
+vector addition; in other words, it forms a vector subspace of the set
 of all multi-indices.
 A moment's consideration will further show that the above reasoning can be
-inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
-whenever the $\vec\gamma$ belongs to a given vector subspace of the set of
+inverted; that is, if we set all $\tau_{\vec\gamma}$ equal to $1$
+whenever $\vec\gamma$ belongs to a given vector subspace of the set of
 all indices, then $\tau$ indeed has an image
@@
 With this information, we present a procedure to generate all solutions: we start out
-from the solution having $\tau_{\vec0}=1$, with everything else $0$. We may
+from the solution having $\tau_{\vec0}=1$, with everything else zero. We may
 then successively switch $\tau_{\vec\alpha}$'s
 % \janote{agregué el subíndice $\vec\alpha$} 
-to $1$ for various values of $\valpha$,
+to one for various values of $\valpha$,
 taking care immediately to set equal to one the components of $\tau$
@@
 \caption{
-Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
-depolarizing channel, (b) a PCE channel that preserves four components, the
-normalization component, one local component of qubit 2 and two correlations between the 
+Examples of diagrams for several two-qubit PCE quantum channels: (a) the totally
+depolarizing channel and (b) a PCE channel that preserves four components---the
+normalization component, one local component of qubit 2, and two correlations between the 
 two qubits.
-(c), (d) and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and
+(c), (d), and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$, and
 $\mcG_{(2,2)}$, respectively; the combination (overlap of diagrams) of any two
@@
 \end{equation}
-which suggest a relation  between individual channels that
+which suggests a relation  between individual channels that
 preserve $K$ and $2N-K$ Pauli components that for the time being

### 2022-09-21 documentos/posters/cnf_2022.tex

%==============================================================================
%== template for LATEX poster =================================================
%==============================================================================
%
%--A0 beamer slide-------------------------------------------------------------
\documentclass[final,svgnames]{beamer}
\usepackage{tikz}
\usepackage[orientation=portrait,size=a0,
            scale=1.25         % font scale factor
           ]{beamerposter}

\geometry{
  hmargin=2.5cm, % little modification of margins
}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\definecolor{jacolor}{RGB}{200,40,0} \FXRegisterAuthor{ja}{aja}{\color{jacolor}JA}
% \usepackage[mathlines]{lineno}  \linenumbers \setlength\linenumbersep{3pt}

\newcommand{\cuadritotikz}{
% \pgfmathsetmacro{\unitstep}{5.2}
% \node at (-0.5,0.5) {(a)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw[black!10] (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
 \draw (0,-3) rectangle (4,1);
}

\renewcommand{\indent}{\hspace*{15pt}}
\newcommand{\mcG}{\mathcal{G}}
\newcommand\todo[1]{\textcolor{red}{#1}}

\usepackage[spanish,activeacute]{babel}
\usepackage{physics}

\newcommand{\Mod}[1]{\ (\mathrm{•}mathrm{mod}\ #1)}

%
\usepackage[utf8]{inputenc}
\usepackage{dsfont}

\newcommand{\one}{\mathds{1}}

\newcommand{\valpha}{\vec\alpha}

\linespread{1.15}
%
%==The poster style============================================================
\usetheme{sharelatex}

%==Title, date and authors of the poster=======================================
\title
% [LXV Congreso Nacional de Física - Zacatecas] % Conference
{ % Poster title
Pauli component erasing (PCE) quantum channels
}

\author{ % Authors
Jose Alfredo de Leon\inst{1,2}, Alejandro Fonseca\inst{3,2}, Francois Leyvraz\inst{4},
David Davalos\inst{5}, Carlos Pineda\inst{2}
}
\institute
[Very Large University] % General University
{
\inst{1} Instituto de Investigación en Ciencias Físicas, ECFM, Universidad de San Carlos de Guatemala, Guatemala\\[-0.3ex]
\inst{2} Instituto de Física, Universidad Nacional Autónoma de México, México\\[-0.3ex]
\inst{3} Departamento de Física, CCEN, Universidade Federal de Pernambuco, Brasil\\[-0.3ex]
\inst{4} Instituto de Ciencias Físicas, Universidad Nacional Autónoma de México, México\\[-0.3ex]
\inst{5} Institute of Physics, Slovak Academy of Sciences, Slovakia
}
\date{\today}

\begin{document}
\vspace*{-2cm}
\begin{frame}[t]
\begin{tikzpicture}[x=1mm,y=1mm,overlay,remember picture]
\pgftransformshift{\pgfpointanchor{current page}{center}}
\node[inner sep=0pt] (usac) at (-370,445) %
{\includegraphics[height=5cm]{logos/ecfmByN.png}};
\node[inner sep=0pt] (usac) at (-305,445) %
{\includegraphics[height=4cm]{logos/ifunam.png}};
\node[inner sep=0pt] (usac) at (265,445) %
{\includegraphics[height=5cm]{logos/pernambuco_logo.png}};
\node[inner sep=0pt] (usac) at (315,445) %
{\includegraphics[height=5.2cm]{logos/icf.png}};
\node[inner sep=0pt] (usac) at (370,445) %
{\includegraphics[height=5.2cm]{logos/Slovak-Academy-of-Sciences.png}};
\end{tikzpicture}
%==============================================================================
\begin{multicols}{3}
%==============================================================================
%==The poster content==========================================================
%==============================================================================

\section{Resumen}
\indent Procesos de disipación, como la decoherencia de los sistemas cuánticos, pueden describirse con la teoría de los canales cuánticos. No obstante, sigue siendo una tarea difícil entender el conjunto de todos los canales cuánticos, especialmente para sistemas de muchas partículas. En ese contexto, proponemos los mapeos \textit{Pauli component erasing} (PCE), que preservan o borran por completo las componentes de la matriz de densidad de un sistema de muchos qubits. Para aquellos que son canales cuánticos mostramos su correspondencia con subespacios vectoriales y así hacemos su caracterización. A partir de su estructura de semigrupo derivamos sus generadores y, con esto, determinamos implementaciones físicas para conectar a los canales PCE con procesos Markovianos.

% \section{Introducción}
\section{El problema}
\indent Los estados de una partícula de dos niveles, un qubit, pueden visualizarse geométricamente en la esfera de Bloch. Los procesos de disipación y decoherencia se describen como proyecciones de la esfera de Bloch. Sin embargo, como mostramos en la Fig. \ref{fig:projections} no todas las proyecciones describen evoluciones físicas.
\begin{figure}
    \centering
    \includegraphics[width=0.6\columnwidth]{img/bloch.png}
    \caption{Sólo algunas de las proyecciones de la esfera de Bloch son permitidas.}
    \label{fig:projections}
\end{figure}
\section{Canales cuánticos}
\indent Los canales cuánticos son un marco teórico dentro del cual se pueden estudiar la dinámica de sistemas cuánticos, como las transformaciones de la esfera de Bloch en la Fig. \ref{fig:projections}.

\indent Un canal cuántico es un mapeo de matrices de densidad a matrices de densidad. Es decir, $\rho\mapsto\mathcal{E}(\rho)$, donde $\mathcal{E}$ es un mapeo completamente positivo que preserva la traza de $\rho$.
Un mapeo $\mathcal{E}$ está unívocamente caracterizado por su matriz de Choi $\mathcal{D}\propto \qty(\one\otimes\mathcal{E})\qty[\sum_{j,k}\ket{j}\ket{j}\bra{k}\bra{k}]$. $\mathcal{D}$ es una matriz positiva semidefinida si y sólo si $\mathcal{E}$ es completamente positivo.

\section{Mapeos PCE}
% La forma más general de escribir a la matriz de densidad de un qubit es 
% \begin{align}\label{eq:one:qubit:matrix}
%     \rho=\frac{1}{2}\sum_{\alpha=0}^3r_\alpha\sigma_\alpha,
% \end{align}
% con $\sigma_0=\one$ y $\sigma_{1,2,3}=\sigma_{x,y,z}$ las matrices de Pauli. La condición 
% de normalización requiere que $r_0=1$. Las componentes $r_{1,2,3}$ forman el vector de Bloch.

% \hspace*{6pt}Introducimos a un mapeo \textit{Pauli component erasing} (PCE) como un mapeo que actúa sobre las componentes de la matriz de densidad \eqref{eq:one:qubit:matrix} según
% \begin{align}
%     r_\alpha\mapsto \tau_\alpha r_\alpha,\quad \tau_\alpha=0,1.
% \end{align}
% En la Fig. \ref{fig:1:qubit:diagrams} introducimos una representación de los mapeos PCE. 
% \vskip1ex
% \begin{figure}
% \centering
% \includegraphics[width=.8\columnwidth]{img/one_qubit_PCE.pdf}
% \caption{Ejemplos de diagramas para mapeos PCE de 1 qubit. En (a) introducimos la correspondencia entre las $\tau_{i}$ de $\mathcal{E}$ y las posiciones de los cuadros en el diagrama. Un cuadro negro (blanco) se corresponde con $\tau_i=1$ ($\tau_i=0$). En (b) se muestra la identidad, en (c) y (e) los canales de abajo y arriba en la Fig. \ref{fig:projections}, respectivamente, y en (d) el completamente depolarizante.}    
% \label{fig:1:qubit:diagrams}
% \end{figure}

% Como vimos en la Fig. \ref{fig:projections} no todos los mapeos PCE son canales cuánticos. Para 
% esto debemos evaluar las condiciones que las $\tau_\alpha$ deben de satisfacer,
% \begin{align}
%     1+\tau_1+\tau_2+\tau_3&\geq 0\\
%     1+\tau_\alpha+\tau_\beta+\tau_\gamma &\geq 0,\quad \forall \alpha\ne \beta\ne \gamma.
% \end{align}
% %============================================
% Estas desigualdades aseguran que el mapeo PCE sea completamente positivo y, por lo tanto,
% un canal cuántico.
\indent La forma más general de escribir a la matriz de densidad de $N$ qubits es 
\begin{align}
    \rho=\frac{1}{2^N}\sum_{\valpha}r_{\valpha}\sigma_{\valpha},
\end{align}
donde $\valpha$ denota un multi índice $(\alpha_1,\ldots,\alpha_N)$, $\alpha_j=0,1,2,4$, y 
$\sigma_{\valpha}=\sigma_{\alpha_1}\otimes\sigma_{\alpha_2}\otimes\ldots\otimes\sigma_{\alpha_N}$. La condición de normalización de $\rho$ restringe que $r_{\vec 0}=1$.

\indent Definimos a un mapeo \textit{Pauli component erasing} (PCE) como un mapeo que actúa sobre $\rho$ como
\begin{align}\label{eq:pce:N:qubits}
    r_{\valpha}\mapsto\tau_{\valpha} r_{\valpha},\quad \tau_{\valpha}=0,1.
\end{align}
Para que, por definición, un mapeo PCE preserve la traza imponemos que $\tau_{\vec 0}=1$. Nos vamos a referir a un mapeo de la forma \eqref{eq:pce:N:qubits}, pero sin la restricción sobre los valores de $\tau_{\valpha{}}$, como un mapeo diagonal de Pauli. En la Fig. \ref{fig:2:qubits:diagrams} introducimos diagramas para representar a los mapeos 
PCE de 1 y 2 qubits. 
%============================================
\vskip2ex
\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{img/one_and_two_qubit_PCE.pdf}
\vspace*{2ex}
\caption{En (a) y (f) introducimos la correspondencia entre las $\tau_{\valpha{}}$ de un mapeo PCE [vea Eq. \eqref{eq:pce:N:qubits}] y las posiciones de los cuadros en los diagramas. Un cuadro negro (blanco) se corresponde con $\tau_{\valpha{}}=1$ ($\tau_{\valpha{}}=0$). En (b) se muestra la identidad de 1 qubit, en (c) y (e) los canales ilustrados en la Fig. \ref{fig:projections}, en (d) el completamente depolarizante, (g) corresponde a un canal cuántico que es el producto tensorial del canal (c) en cada qubit y en (h) mostramos un mapeo PCE de 2 qubits que no es un canal cuántico.}
\label{fig:2:qubits:diagrams}
\end{figure}
\indent Los mapeos PCE no son trivialmente canales cuánticos. En general, un mapeo PCE [vea Eq. \eqref{eq:pce:N:qubits}] no es completamente positivo. 
Para determinar si un mapeo PCE es completamente positivo y, por consiguiente, un canal cuántico investigamos la diagonalización de la matriz de Choi de un mapeo diagonal de Pauli.

% \section{Consideraciones matemáticas} 
\section{Diagonalización de la matriz de Choi}
\indent Diagonalizamos exactamente la matriz de Choi $\mathcal{D}$ de un mapeo diagonal de Pauli de $N$ qubits y mostramos que los eigenvalores de $\mathcal{D}$ se pueden escribir como
\begin{align}\label{eq:eigvalues}
    \lambda_{\valpha}=\frac{1}{2^N}\sum_{\vec\beta}A_{\valpha{}\vec\beta}\tau_{\vec\beta},
\end{align}
donde 
\begin{align}\label{eq:a}
    A=a^{\otimes N},\qquad 
    a = \mqty( 1&1&1&1\\
    1&1&-1&-1\\
    1&-1&1&-1\\
    1&-1&-1&1).
\end{align}
Para que un mapeo PCE sea completamente positivo y, por consiguiente, un canal cuántico los eigenvalores \eqref{eq:eigvalues} deben satisfacer  $\lambda_{\valpha}\geq 0$.

\section{Canales cuánticos PCE\\como espacios vectoriales}
\indent Los canales cuánticos PCE tienen una estructura algebraica bella y simple a partir de la cual se pueden derivar sus propiedades.

\indent Si reescribimos $\valpha{}$ con dos índices binarios como $\valpha{}=\qty{(\mu_1,\ldots,\mu_N),(\nu_1,\ldots,\nu_N)}$ y  $\mu_j,\nu_j=0,1$, es fácil de mostrar la propiedad algebraica
\begin{align}
    \tau_{\valpha{}}\tau_{\vec\beta}=\tau_{\valpha{}\oplus\vec\beta},\quad \forall\,\valpha{},\vec\beta :\alpha\ne \beta \wedge \tau_{\valpha{}}=\tau_{\vec\beta}=1.
\end{align}
Es decir, el conjunto $\{\valpha{}:\tau_{\valpha{}}=1\}$ junto con la operación $\oplus$ forman un grupo. Si además, uno equipa a este grupo con el campo $\{0,1\}$ se deduce que cada canal cuántico PCE está asociado con un subespacio vectorial, y viceversa.
% Vea la Fig. \ref{fig:vector:spaces:examples}.
% \vskip2ex
% \begin{figure}
% \begin{center}
% \begin{tikzpicture}[x=1.4cm, y=1.4cm] % {{{
% \pgfmathsetmacro{\unitstep}{5.2}
% \begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
% \cuadritotikz{}
% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(1,-1)}] \fill[black!25!white] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,-1)}] \node at (0.5,0.5) 
%      {\textcolor{white}{$\valpha^{(1)}$}}; \end{scope}
% \begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(2,0)}] \node at (0.5,0.5) 
%      {\textcolor{white}{$\valpha^{(2)}$}}; \end{scope}
% \begin{scope}[shift={(-1,0)}] \node at (0.5,0.5) 
%      {\textcolor{black}{(a)}}; \end{scope}     
% \end{scope} % }}}
% \end{tikzpicture} % }}}
% \begin{tikzpicture}[x=1.4cm, y=1.4cm] % {{{
% \pgfmathsetmacro{\unitstep}{5.2}
% \begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
% \cuadritotikz{}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(3,0)}] \node at (0.5,0.5) 
%      {\textcolor{white}{$\vec\beta^{(1)}$}}; \end{scope}
% \begin{scope}[shift={(0,-3)}] \node at (0.5,0.5) 
%      {\textcolor{white}{$\vec\beta^{(2)}$}}; \end{scope}
% \begin{scope}[shift={(3,-3)}] \node at (0.5,0.5) 
%      {\textcolor{white}{$\vec\beta^{(3)}$}}; \end{scope}
% \begin{scope}[shift={(-1,0)}] \node at (0.5,0.5) 
%      {\textcolor{black}{(b)}}; \end{scope}     
% \end{scope} % }}}
% \end{tikzpicture} % }}}
% \end{center}
% \caption{El mapeo PCE en (a) no es un canal cuántico porque $\valpha^{(1)}\oplus\valpha^{(2)}=\{(0,0),(1,0)\}\oplus\{(0,1),(1,1)\}=\{(0,1),(0,1)\}$ son los índices de un cuadro no negro (cuadro gris). Por otro lado, los vectores $\vec\beta^{(j)}$ en (b) son cerrados bajo $\oplus$, por lo tanto, sí es un canal cuántico.}
% \label{fig:vector:spaces:examples}
% \end{figure}

\section{Generadores}
\indent A partir de la estructura de grupo de los canales cuánticos PCE se deduce la existencia de un conjunto generador. Los diagramas (c)-(e) de la Fig. \ref{fig:examplesPCE} son ejemplos de generadores PCE de 2 qubits, cualquier intersección entre dos de ellos (concatenación de canales) da como resultado el canal en (b).
\vskip2ex
\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{img/two_qubit_channels.pdf}
\vspace*{2ex}
\caption{Ejemplos de diagramas para varios canales cuánticos PCE de 2 qubits: (a) el canal completamente depolarizante, (b) un canal PCE que preserva cuatro componentes, la componente de normalización, una componente local del qubit 1 y
dos correlaciones entre los dos qubits. En (c), (d) y (e) mostramos los tres generadores $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ y $\mcG_{(2,2)}$, respectivamente; y en (f) mostramos el mapeo de la identidad.}
\label{fig:examplesPCE}
\end{figure} % }}}

\indent Más aún, como mostramos en la Fig. \ref{fig:connection:a:generators}, existe una relación entre los generadores PCE y la matriz $a$ en \eqref{eq:a} que establece la simetría de reflexión respecto a una partícula.
\vskip2ex
\begin{figure}
\centering
\includegraphics[width=0.65\columnwidth]{img/connection_a_generators.pdf}
\caption{Conexión entre las filas y columnas de la matriz $a$ en \eqref{eq:a} y de los generadores PCE $\mathcal{G}_{\alpha}$ de 1 qubit.}
\label{fig:connection:a:generators}
\end{figure}\vskip2ex

\section{Canales PCE y decoherencia}
\indent Los canales PCE pueden identificarse como procesos de disipación en el límite $t\to\infty$ y como puntos particulares de un modelo de colisiones sin memoria. Ambas implementaciones antes mencionadas se derivan a partir de la forma de Kraus de los generadores PCE, que tienen la forma simple siguiente,
\begin{align}
% \mathcal{L}_{\valpha{}}[\rho]=\frac{\gamma\qty(\sigma_{\valpha{}}\rho\sigma_{\valpha{}}-\rho)}{2}.
K_0=\frac{\one}{\sqrt{2}},\quad K_1=\frac{\sigma_{\valpha{}}}{\sqrt{2}}.
\end{align}
% \todo{iterar aquí}

\section{Conclusiones}
\begin{itemize}
\item Introducimos los mapeos PCE. 
\item Diagonalizamos exactamente a la matriz de Choi de un mapeo diagonal de Pauli de $N$ qubits.
\item Caracterizamos a los canales cuánticos PCE mediante su estructura de espacio vectorial.
\item Estudiamos que los canales cuánticos PCE pueden implementarse como puntos límite de procesos Markovianos. 
\end{itemize}

%==============================================================================
%==End of content==============================================================
%==============================================================================

%--References------------------------------------------------------------------

\subsection{Referencia}
% \todo{Escribir referencia PRA?}
\begin{thebibliography}{99}

% \bibitem{ref1} J.~Doe, Article name, \textit{Phys. Rev. Lett.}
\bibitem{}\href{https://arxiv.org/abs/2205.05808}{Pauli component erasing quantum channels. Jose Alfredo de Leon, Alejandro Fonseca, Francois Leyvraz, David Davalos, Carlos Pineda. arXiv:2205.05808.  [\textit{Aceptado para publicarse en Physical Review A}]}

\end{thebibliography}

\subsection{Contacto}
\href{mailto:josedleon@estudiantes.fisica.unam.mx}{josedleon@estudiantes.fisica.unam.mx}
%--End of references-----------------------------------------------------------

\end{multicols}

%==============================================================================
\end{frame}
\end{document}

### 2022-09-26 documentos/posters/cnf_2022.tex
Updated CNF poster

@@
 }
+
+\usepackage{amssymb}% http://ctan.org/pkg/amssymb
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 
@@
 
-\renewcommand{\indent}{\hspace*{15pt}}
+\renewcommand{\indent}{\hspace*{25pt}}
 \newcommand{\mcG}{\mathcal{G}}
@@
 \indent Procesos de disipación, como la decoherencia de los sistemas cuánticos, pueden describirse con la teoría de los canales cuánticos. 
-No obstante, sigue siendo una tarea difícil entender el conjunto de todos los canales cuánticos, especialmente para sistemas de muchas partículas.
+%No obstante, sigue siendo una tarea difícil entender el conjunto de todos los canales cuánticos, especialmente para sistemas de muchas partículas. 
 En ese contexto, proponemos los mapeos \textit{Pauli component erasing} (PCE), que preservan o borran por completo las componentes de la matriz de densidad de un sistema de muchos qubits. 
-Para aquellos que son canales cuánticos mostramos su correspondencia con subespacios vectoriales y así hacemos su caracterización.
-A partir de su estructura de semigrupo derivamos sus generadores y, con esto, determinamos implementaciones físicas para conectar a los canales PCE con procesos Markovianos.
+Mostramos que el subconjunto de mapeos PCE que describen evoluciones físicas, es decir, los \textit{canales cuánticos PCE}, se corresponden con subespacios vectoriales.
+%Para aquellos que son canales cuánticos mostramos su correspondencia con subespacios vectoriales y así hacemos su caracterización. 
+Finalmente, derivamos los generadores de este subconjunto a partir de su estructura de semigrupo y, con esto, determinamos implementaciones físicas para conectar a los canales cuánticos PCE con procesos Markovianos.
 
 % \section{Introducción}
-\section{El problema}
-\indent Los estados de una partícula de dos niveles, un qubit, pueden visualizarse geométricamente en la esfera de Bloch.
-Los procesos de disipación y decoherencia se describen como proyecciones de la esfera de Bloch.
-Sin embargo, como mostramos en la Fig.
-\ref{fig:projections} no todas las proyecciones describen evoluciones físicas.
+\section{Motivación}
+\indent 
+%Los estados de una partícula de dos niveles, un qubit, pueden visualizarse geométricamente en la esfera de Bloch. 
+Algunos procesos de decoherencia de 1 partícula de 2 niveles se describen como proyecciones de la esfera de Bloch.
+Sin embargo, no todas las proyecciones describen evoluciones físicas [vea la Fig.
+\ref{fig:projections}].
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.6\columnwidth]{img/bloch.png}
+%    \caption{Sólo algunas de las proyecciones de la esfera de Bloch son permitidas.}
+%    \label{fig:projections}
+%\end{figure}
 \begin{figure}
-    \centering
-    \includegraphics[width=0.6\columnwidth]{img/bloch.png}
-    \caption{Sólo algunas de las proyecciones de la esfera de Bloch son permitidas.}
+\begin{center}
+\begin{tikzpicture}
+ %nodes
+% \draw[draw=white] (-2.7,-4.5) rectangle ++(5.5,5);
+\draw[draw=white] (-1.2,-4.1) rectangle ++(6.5,5.5);
+%  \node[punkt] (market) {Market (b)};
+% \filldraw [fill=Peach, draw=black] (11.1,5) rectangle (0.3,0.3);
+ % We make a dummy figure to make everything look nice.
+%  \node at (0, 0)  {\includegraphics[width=.99\textwidth]{spectraAll}};
+\node at (-6, 0)  {%
+%\includegraphics[width=.2\columnwidth,page=1]{../images/blochs-crop}%
+\includegraphics[width=7cm,page=2]{../images/blochs-crop}%
+};
+\draw [-stealth,line width=8pt] (-1,0) -- (1,0);
+%\draw [-{stealth[length=3mm, width=3mm]},line width=3pt] (1.4,0) -- (2.7,0); 
+\node at (0.,1.5) {\color{green} \Huge\cmark};
+\node at (0.,-8.5) {\color{red} \Huge\xmark};
+%\draw [-{stealth[length=3mm, width=3mm]},line width=3pt] (1.4,-2.8) -- (2.7,-2.8); 
+\draw [-stealth,line width=8pt] (-1.2,-10) -- (1.2,-10); 
+\node at (6,  0)  {%
+\includegraphics[width=7cm,page=3]{../images/blochs-crop}%
+% \only<2->{\includegraphics[width=.2\textwidth,page=2]{../images/blochs-crop}}%
+};
+\node at (6,  -8)  {%
+\includegraphics[width=7cm,page=4]{../images/blochs-crop}%
+};
+\node at (-6,  -8)  {%
+\includegraphics[width=7cm,page=5]{../images/blochs-crop}%
+};
+\end{tikzpicture}
+% Sistemas naturales, estables\\[.2cm]
+% Acá un dibujo en dos partes, con la esfera de Bloch en la primera indicando 
+% algun punto que ava a viajar al disco central, luego una segunda con solo el 
+% disco. Luego una segunda serie con eso, pero proyectado al eje z. 
+\end{center}
+\caption{No todas las proyecciones de la esfera de Bloch describen evoluciones físicas.}
 \label{fig:projections}
@@
 \ref{fig:projections}.
-
-\indent Un canal cuántico es un mapeo de matrices de densidad a matrices de densidad.
+Un canal cuántico es un mapeo de matrices de densidad a matrices de densidad.
 Es decir, $\rho\mapsto\mathcal{E}(\rho)$, donde $\mathcal{E}$ es un mapeo completamente positivo que preserva la traza de $\rho$.
@@
 
-\section{Mapeos PCE}
+\section{Planteamiento del problema:\\mapeos PCE}
 % La forma más general de escribir a la matriz de densidad de un qubit es 
@@
 \indent La forma más general de escribir a la matriz de densidad de $N$ qubits es 
-\begin{align}
+\begin{align}\label{eq:rho}
     \rho=\frac{1}{2^N}\sum_{\valpha}r_{\valpha}\sigma_{\valpha},
@@
 
-\indent Definimos a un mapeo \textit{Pauli component erasing} (PCE) como un mapeo que actúa sobre $\rho$ como
+\indent Definimos a un mapeo \textit{Pauli component erasing} (PCE) como un mapeo que actúa sobre $\rho$, de la forma \eqref{eq:rho}, como
 \begin{align}\label{eq:pce:N:qubits}
@@
 \end{align}
-Para que, por definición, un mapeo PCE preserve la traza imponemos que $\tau_{\vec 0}=1$.
+Para que un mapeo PCE preserve la traza de $\rho$ por definición imponemos $\tau_{\vec 0}=1$.
 Nos vamos a referir a un mapeo de la forma \eqref{eq:pce:N:qubits}, pero sin la restricción sobre los valores de $\tau_{\valpha{}}$, como un mapeo diagonal de Pauli.
@@
 \centering
-\includegraphics[width=.8\columnwidth]{img/one_and_two_qubit_PCE.pdf}
-\vspace*{2ex}
+\includegraphics[height=12cm]{../images/one_and_two_qubit_PCE.pdf}
+\vspace*{1ex}
 \caption{En (a) y (f) introducimos la correspondencia entre las $\tau_{\valpha{}}$ de un mapeo PCE [vea Eq.
@@
 \end{figure}
-\indent Los mapeos PCE no son trivialmente canales cuánticos. En general, un mapeo PCE [vea Eq. \eqref{eq:pce:N:qubits}] no es completamente positivo. 
-Para determinar si un mapeo PCE es completamente positivo y, por consiguiente, un canal cuántico investigamos la diagonalización de la matriz de Choi de un mapeo diagonal de Pauli.
+\indent En general, un mapeo PCE [vea Eq. \eqref{eq:pce:N:qubits}] no es completamente positivo y, por consiguiente, no todos los mapeos PCE son canales cuánticos. 
+Para determinar si un mapeo PCE es completamente positivo investigamos la diagonalización de la matriz de Choi de un mapeo diagonal de Pauli.
 
-% \section{Consideraciones matemáticas} 
-\section{Diagonalización de la matriz de Choi}
+% \section{Consideraciones matemáticas} d
+\section{Diagonalización de la matriz de Choi $\pmb{\mathcal{D}}$}
 \indent Diagonalizamos exactamente la matriz de Choi $\mathcal{D}$ de un mapeo diagonal de Pauli de $N$ qubits y mostramos que los eigenvalores de $\mathcal{D}$ se pueden escribir como
@@
 \end{align}
-Para que un mapeo PCE sea completamente positivo y, por consiguiente, un canal cuántico los eigenvalores \eqref{eq:eigvalues} deben satisfacer  $\lambda_{\valpha}\geq 0$.
+Para que un mapeo PCE sea completamente positivo y, por consiguiente un canal cuántico, los eigenvalores \eqref{eq:eigvalues} deben satisfacer  $\lambda_{\valpha}\geq 0$.
 
@@
 \section{Generadores}
-\indent A partir de la estructura de grupo de los canales cuánticos PCE se deduce la existencia de un conjunto generador.
+\indent Si los canales cuánticos PCE forman un grupo, entonces existe un subconjunto de canales PCE generadores $\mathcal{G}_{\valpha{}}$.
 Los diagramas (c)-(e) de la Fig.
@@
 \centering
-\includegraphics[width=0.65\columnwidth]{img/connection_a_generators.pdf}
+\includegraphics[height=6.5cm]{img/connection_a_generators.pdf}
 \caption{Conexión entre las filas y columnas de la matriz $a$ en \eqref{eq:a} y de los generadores PCE $\mathcal{G}_{\alpha}$ de 1 qubit.}
 \label{fig:connection:a:generators}
-\end{figure}\vskip2ex
+\end{figure}
+\vspace*{-2cm}
 
@@
 %==============================================================================
+
 \end{frame}

### 2022-11-01 documentos/posters/cnf_2022.tex
algo cambie

@@
 \usepackage[orientation=portrait,size=a0,
-            scale=1.25         % font scale factor
+            scale=1.26         % font scale factor
            ]{beamerposter}
@@
 \section{Generadores}
-\indent Si los canales cuánticos PCE forman un grupo, entonces existe un subconjunto de canales PCE generadores $\mathcal{G}_{\valpha{}}$.
+\indent A partir de la estructura de semigrupo del subconjunto de canales PCE derivamos sus generadores $\mathcal{G}_{\valpha{}}$.
 Los diagramas (c)-(e) de la Fig.

### 2022-11-09 documentos/arxiv/intro.tex
luego ordeno

--- 2022-08-05 documentos/intro.tex
@@
 computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
-However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
+However, this resource is also extremely
+delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, especially 
 for multi-particle systems~\cite{Horodecki}; that is why an important part
@@
 The process by which quantum correlations are unintentionally dissipated
-is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
+is called {\it decoherence}~\cite{Schlosshauer2004,sep-qm-decoherence}.
 One of the main tools to study the effects of decoherence are 
@@
 %
-% The identification of families of quantum channels among the whole convex set
-% of quantum channels associated to a Hilbert space, is crucial to understand
-% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
-% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
-% graining~\cite{Duarte2017,pinedacg}. 
 One of the main difficulties 
-in characterizing quantum channels is that, like for quatum states, 
+in characterizing quantum channels is that, like for quantum states, 
 the number of parameters required for their description increases quite 
-rapidly with Hilbert space dimension.
+rapidly with Hilbert-space dimension.
 % \sout{to characterize quantum channels is that,
@@
 For the qubit case there are several studies concerning the unital case, for which
-non-trivial properties can be described using only $3$ parameters, which in
-turn form the well known tetrahedron of Pauli
+non-trivial properties can be described using only three parameters, which in
+turn form the well-known tetrahedron of Pauli
 channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
@@
 
-In this work we present a generalization of idempotent Pauli channels, \ie{}
-the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
-channel and the identity channel, to the case of $N$ qubits. 
+In this paper we present a generalization of idempotent Pauli channels---\ie{},
+the qubit flip operations (bit, phase, and bit-phase when the flip probability is $1/2$), total depolarizing qubit
+channel and the identity channel---to the case of $N$ qubits. 
 % \cpnote{Mencionar decoherencia} 
@@
 We shall in the following refer to 
-such maps as {\em Pauli component erasing maps} (\pce{} maps).
+such maps as {\em Pauli component erasing} (\pce{}) {\it maps}.
 
@@
 on aforementioned channels, as we show in section \ref{sec:vector_spaces}. This
-structure allows for example to describe such channels with a much reduced
+structure allows us, for example, to describe such channels with a much reduced
 set of parameters (as compared to specifying a list of all erased Pauli
@@
 and as such can be used as building blocks of more general channels. For 
-instance one can combine them (through convex superposition) or compose them
+instance, one can combine them (through convex superposition) or compose them
 with unitary transformations.
@@
 \par
-The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
+The paper is organized as follows. In section~\ref{sec:pce_maps} we recall
 the properties of quantum channels needed to proceed with the definition 
@@
 % 
-To finish, we conclude and discuss future perspectives \flnote{and possible generalizations} in
+To finish, we conclude and discuss future perspectives and possible generalizations in
 section~\ref{sec:conclusions}.

### 2022-11-09 documentos/arxiv/kraus.tex
luego ordeno

--- 2022-05-11 documentos/kraus.tex
@@
-\section{PCE channels and decoherence o Physical implementations of PCE maps} % {{{
+\section{PCE channels and decoherence} % {{{
 \label{sec:kraus}
@@
 decoherence dynamics. Moreover, these processes lead to a monotonic
-(continuous) lose of information~\cite{breuerreview} and describe
+(continuous) loss of information~\cite{breuerreview} and describe
 non-invertible channels in the asymptotic limit $t\to \infty$ (this can be seen
-from the monotonically (continuous) decreasing of the determinant, see
+from the monotonic (continuous) decrease of the determinant, see
 Ref.~\cite{cirac}).
@@
 corresponding to the operation that leaves the component $\sigma_\alpha$
-invariant~\cite{nielsen_chuang_2011}.
-Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$.
-In fact, tracing out all particles except the $k$-th one gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$, see~ \eref{eq:generator:individual:qubit}.
-And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel  (completely dephasing).
+invariant~\cite{nielsen_chuang_2011}. Notice that according to Kraus operators
+the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip
+probability $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec
+\alpha} \rho \sigma_{\vec \alpha}$. In fact, tracing out all particles except
+the $k$th one gives the well-known qubit flip channels, \ie{}, $\tr_{\not k}
+\mcG_\valpha=\mcG_{\alpha_k}$, see~ \eref{eq:generator:individual:qubit}. 
+More generally, tracing out $m$ particles leaves a $N-m$ particles flip channel
+(completely dephasing).
 
@@
 by the Kraus operators in \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
-except for the first row, half of the matrix elements of each row is $+1$ and 
-half $-1$, which implies that the channel is a PCEG.
+except for the first row, half of the matrix elements of each row are $+1$ and 
+half are $-1$, which implies that the channel is a PCEG.
 
@@
 leads to different channels. This follows from the fact that if two channels were
-the same, this would imply that the matrix representation of the corresponding
+the same this would imply that the matrix representation of the corresponding
 superoperator of $\rho \mapsto \sigma_{\vec \alpha}\rho \sigma_{\vec \alpha}$
@@
 would have to be the same, which is clearly false. Since there are $4^n$ different 
-$\vec \alpha$, this implies that all PCEG (plus the identity map) are in one to 
-one correspondence.
+$\vec \alpha$ values, this implies that all PCEGs (plus the identity map) are in 
+one-to-one correspondence.
 
@@
 t_1+t_2}$. Therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
-time-homogeneous Markovian process, which are always characterized by some
+time-homogeneous Markovian process, which is always characterized by some
 Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec
 \alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained using the standard
-procedure,  
+procedure:
 \begin{equation}
-\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
+\mcL_{\vec \alpha}[\rho]
+   =\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}
+   =\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
 \end{equation}
@@
 $\gamma/2$ is simply $\sigma_{\vec \alpha}$. Notice that $\sigma_{\vec \alpha}$
-is trace-less, therefore the process is pure dissipative~\cite{cirac}.
+is trace-less, therefore the process is purely dissipative~\cite{cirac}.
 
@@
 of the Lindbladians of the corresponding generators. As an example, consider
-the channel depicted in \fref{fig:two:qubit:examples} b), it is equal to
+the channel depicted in \fref{fig:two:qubit:examples}(b); it is equal to
 $\mcG_{(0,3)}\mcG_{(3,3)}$, therefore it is the fixed point of the dissipation
-process described with the following Lindbladian,
+process described with the following Lindbladian:
 \begin{equation}
@@
 We show now that PCE channels can also be implemented with \textit{simple
-collision models}~\cite{Ziman2010}. To do this, observe that employing the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
-be implemented using an unitary over the system and an
-ancilla. Since PCEG
+collision models}~\cite{Ziman2010}. To do this, observe that employing the
+Stinespring dilation theorem~\cite{Stinespring2006} PCEGs can
+be implemented using a unitary over the system and an
+ancilla. Since PCEGs
 always have Kraus rank $2$, one can
@@
 \end{equation}
-where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
-the unitary defined as follows,
+where $\tr_{\text{qubit}}$ denotes the partial trace over the ancillary qubit, with
+the unitary defined as follows:
 \begin{align}
@@
 \end{equation}
-where $\tr_{\text{E}}$ is the partial trace over the whole ancillary qubits. Notice that as PCEGs commute, the order of the collisions is irrelevant.
+where $\tr_{\text{E}}$ is the partial trace over all ancillary qubits. Notice
+that as PCEGs commute the order of the collisions is irrelevant.
 % \begin{itemize}

### 2022-11-09 documentos/arxiv/quantum_classical.tex
luego ordeno

--- 2022-05-03 documentos/quantum_classical.tex
@@
 \label{quantum_classical}
-A Quantum-classical (QC) channel is defined by using an orthonormal basis in the Hilbert space.
-Let $B=\left\{ \ket{\psi_i} \right\}$ such a basis in $\hilbert$ with $\dim(\hilbert)=2^N$, the QC channel associated to $B$ is
+A quantum-classical (QC) channel is defined by using an orthonormal basis in
+the Hilbert space. Let $B=\left\{ \ket{\psi_i} \right\}$ be such a basis in
+$\hilbert$ with $\dim(\hilbert)=2^N$; the QC channel associated to $B$ is
 \begin{equation}
@@
 \end{equation}
-this is, QC channels project density matrices onto the corresponding diagonal matrix in the basis $B$~\cite{nathanson2007pauli}.
+that is, QC channels project density matrices onto the corresponding diagonal
+matrix in the basis $B$~\cite{nathanson2007pauli}.
 
-Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set of commuting Pauli strings denoted by $\text{set}(B)$, such set contains $2^N$ elements (including the identity), and there are $2^N+1$ of such sets~\cite{Lawrence2002}.
-Now we proceed to demonstrate that the QCs defined in this way are \pce{} channels with $2^N$ $1$s on their diagonal.
+Consider now that the basis $B$ is the simultaneous eigenbasis of a maximal set
+of commuting Pauli strings denoted by $\text{set}(B)$; such a set contains $2^N$
+elements (including the identity), and there are $2^N+1$ of such
+sets~\cite{Lawrence2002}. Now we proceed to demonstrate that the QCs defined in
+this way are \pce{} channels with $2^N$ $1$s on their diagonal.
 
-First we compute the components of $\mcE^{\text{QC}}_B$ in the basis $2^{-N/2}\left\{\sigma_{\vec \alpha}\right\}$,
+First we compute the components of $\mcE^{\text{QC}}_B$ in the basis
+$2^{-N/2}\left\{\sigma_{\vec \alpha}\right\}$:
 \begin{equation}
@@
 \end{equation}
-To evaluate the components, observe that $\bra{\psi_i}\sigma_{\vec k} \ket{\psi_i}^2=1 \ \ \forall \sigma_{\vec k}\in \text{set}(B)$, and from the formula for the purity of $\ket{\psi_i}$,
+To evaluate the components, observe that $\bra{\psi_i}\sigma_{\vec k}
+\ket{\psi_i}^2=1 \ \ \forall \sigma_{\vec k}\in \text{set}(B)$, and from the
+formula for the purity of $\ket{\psi_i}$,
 \begin{equation}
@@
 \end{equation}
-it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall \sigma_{\vec k'} \not\in \text{set}(B)$ since there are only positive terms in the sum, and $2^N$ of them are already equal to $1$.
-Therefore,
+it follows that $\bra{\psi_i} \sigma_{\vec k'} \ket{\psi_i}=0 \ \ \forall
+\sigma_{\vec k'} \not\in \text{set}(B)$ since there are only positive terms in
+the sum, and $2^N$ of them are already equal to $1$. Therefore,
 \begin{align}
@@
 To compute $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}$ for $\sigma_{\vec k}, \sigma_{\vec l} \in \text{set}(B)$ with $\vec k \neq \vec l$, observe that $\left(\mcE^{\text{QC}}_B\right)_{\vec k \vec l}=\left(\mcE^{\text{QC}}_B\right)_{\vec l \vec k}$, \ie{} the matrix corresponding to $\mcE^{\text{QC}}$ is an orthogonal projector.
-Thus, consider the block,
+Thus, considering the block,
 \begin{equation}

### 2022-11-09 documentos/arxiv/qudits.tex
luego ordeno

\section{Higher dimensional systems} % {{{
\todo{Alejo o Jose Alfredo escriben aca. Se ponen de acuerdo y dejan a un responsable}
\begin{itemize}
\item Discuss what happens with general $d$ level systems and why it does not work
\item Linealidad de los eigenvalores de la matriz de Choi en función de las
$\tau_{j_1\ldots,j_n}$ de canales `\textit{component erasing}' de qudits. 
\item Discuss what happens with general $(2^k)^{\otimes n}$ level systems and
why it does work
\end{itemize}

\textcolor{jacolor}{
\begin{enumerate}
	\item Explicar cómo nuestro trabajo se generaliza trivialmente 
	para los sistemas de $d=(2^k)^{\otimes n}$ niveles.
	\item Describir el problema de $d=3$ con las matrices de Gell-Mann. El 
	problema es la no linealidad de los eigenvalores de la matriz de Choi en 
	función de las $\taus$.
	\begin{itemize}
		\item A diferencia de los PCE de qubits, la matriz de Choi de GMCE de qutrits
		no se diagonaliza con las matrices de GellMan.  
		\item El bloque problemático es el asociado a las matrices de GellMann diagonales.
		\item Mencionar sobre los operadores de Weyl.
	\end{itemize}
\end{enumerate}
}

% }}}

### 2022-11-09 documentos/arxiv/vector_space.tex
luego ordeno

--- 2022-09-15 documentos/vector_space.tex
@@
 This follows from restricting the sum \eref{eq:tau:is:A:p}
-to $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
+to the indices $\vec\beta$ such that $\lambda_{\vec\beta}\ne 0$,
+given in \eref{eq:condition:lambda:zero:Phi}. 
 Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three

### 2023-03-14 ideas.tex
luego borrar

\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[dvispnames]{xcolor}
\usepackage{bbold}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\newcommand{\mcG}{\mathcal{G}}
\newcommand{\one}{\mathbb{1}}

\title{Ideas}
\begin{document}
\maketitle

Un documento con algunas ideas no concretadas. Falta jugar para ver qué sale.

\section{FM (y CG?) + PCEs}
\begin{itemize}
\item Proceso a considerar
	\begin{enumerate}
		\item Evolución bajo Hamiltoniano $H$
		\item Abrir el sistema para medirlo y ocurre decoherencia descrita por PCEs
		\item Medida FM
	\end{enumerate}
\end{itemize}

Para 2 qubits:

Decoherencia: 
\begin{align}\label{eq:decoherence}
D(\rho) = p'\rho + (1-p')\mathcal G_{\vec \alpha}(\rho),
\end{align}
con $p'$ la probabilidad de que sobre el estado $\rho$ no ocurra ningún proceso
de decoherencia, y $\mathcal G_{\vec \alpha}$ un generador PCE {\color{red} (obviamente este no es un proceso de decoherencia general modelado por PCEs, pero es una primera aproximación)}.

FM: 
\begin{align}\label{eq:FM}
\mathcal F(\rho) = p\rho+ (1 - p)S(\rho),
\end{align}
con $p$ la probabilidad de medir al estado real y $S$ el operador de swap.

Entonces si abrimos el sistema luego de que ha evolucionado bajo un Hamiltoniano $H$, ocurre un proceso de decohrencia \eqref{eq:decoherence} y luego se hace una FM, el estado final sería
\begin{align}\label{eq:all}
\mathcal F \Big[ D(\rho) \Big] = p \rho + pp'\Big\{ S\Big(\mcG_{\vec\alpha}(\rho)\Big) - S(\rho) \Big\} + (1-p)S\Big(\mcG_{\vec\alpha}(\rho)\Big),
\end{align}
naturalmente, si ningún proceso de decoherencia ocurre \textit{i.e.} $\mcG_{\vec\alpha} = \one$, entonces \eqref{eq:all} se reduce a \eqref{eq:FM}.
\begin{itemize}
\item ¿Puede ser positivo el efecto de la decoherencia en algún sentido? Tomografía, por ejemplo. Suponiendo que queremos saber cuál es el estado después de la evolución del sistema bajo $H$
\item Caso límite: $p=0$ \textit{i.e.} el detector siempre confunde a las partículas 1 y 2. En este caso \eqref{eq:all} se reduce a 
\begin{align}\label{eq:limit:case:1}
\mathcal F \Big[ D(\rho) \Big] = S\Big(\mcG_{\vec\alpha}(\rho)\Big).
\end{align} 
\end{itemize}

\end{document}

### 2023-03-17 ideas.tex
Trabajando en ideas

@@
 \usepackage{bbold}
+\usepackage{physics}
 \usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
@@
 \newcommand{\mcG}{\mathcal{G}}
+\newcommand{\mcF}{\mathcal{F}}
 \newcommand{\one}{\mathbb{1}}
@@
 
+Si ahora además incluimos el coarse graining. Partamos del caso más sencillo 
+de 2 qubits, cuyo estado genérico escribimos como 
+\begin{align}
+\rho = \frac{1}{4}\sum_{\alpha,\beta} r_{\alpha\beta}\,\sigma_\alpha \otimes \sigma_\beta. 
+\end{align}
+Vamos a suponer que este es el estado que queremos medir. Sin embargo, 
+contamos con un detector que \textit{por alguna razón} induce decoherencia
+y que además puede resolver únicamente estados de grano grueso. Es decir, 
+para el caso de 2 qubits nuestro detector puede únicamente medir estados 
+de una partícula. Finalmente, el estado que realmente medimos es
+\begin{align}
+\rho_{\text{eff}} = \Tr_1 \big[\mcF\big(\mcG (\rho)\big)\big].
+\end{align}
+Por lo tanto, nos interesa saber si podríamos medir más de lo que podríamos
+medir sin los efectos de decoherencia, o sea, con un estado efectivo 
+\begin{align}
+\rho_{\text{eff}} &=\Tr_2 \big[\mcF\big(\rho\big)\big] \\
+&= \frac{1}{4}\sum_{\alpha, \beta} r_{\alpha\beta} \Tr_2 \big( \sigma_\beta \otimes \sigma_\alpha \big) \\
+&= \frac{1}{4}\sum_{\alpha, \beta} r_{\beta\alpha} \Tr_2 \big( \sigma_\alpha \otimes \sigma_\beta \big) \\
+&= \frac{1}{2}\sum_{\alpha, \beta} r_{\beta\alpha} \sigma_\alpha \delta_{0,\beta} \\
+&= \frac{1}{2}\sum_{\alpha} r_{0\alpha} \sigma_\alpha.
+\end{align}
+Nuestro detector sólo puede medir a la partícula 1. No obstante, vemos que
+bajo la acción del coarse graining tenemos acceso a las componentes 
+locales del qubit 2, $\expval{\sigma_\alpha}=r_{0\alpha}$.
+
+\begin{align}
+\Tr_1 \big[\mcF\big(\mcG (\rho)\big)\big] &= \frac{1}{4}\sum_{\alpha, \beta} \tau_{\alpha\beta}r_{\alpha\beta} \Tr_2 \big( \sigma_\beta \otimes \sigma_\alpha \big) \\
+&= \frac{1}{4}\sum_{\alpha, \beta} \tau_{\beta\alpha}r_{\beta\alpha} \Tr_2 \big( \sigma_\alpha \otimes \sigma_\beta \big) \\
+&= \frac{1}{2}\sum_{\alpha, \beta} \tau_{\beta\alpha}r_{\beta\alpha} \sigma_\alpha \delta_{0,\beta} \\
+&= \frac{1}{2}\sum_{\alpha} \tau_{0\alpha}r_{0\alpha} \sigma_\alpha.
+\end{align}
+
 \end{document}
